### 2021-05-17 general.tex
initial

\documentclass[11pt]{amsart}

\usepackage{macros, setspace}

\def\U{{\rm U}}

%trying this out
%\usepackage[upint]{stix}
\usepackage{cmupint}

\def\brian#1{{\textcolor{blue!65!red}{BRW: {#1}}}}
\def\owen#1{{\textcolor{green!65!black}{BRW: {#1}}}}

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
\title{General definitions}

\spacing{1.25}

\begin{document}
\maketitle

\section{Holomorphic factorization}

Consider the unitary affine group 
\[
\U(n) \ltimes \RR^{2n} \subset {\rm Aff}(\RR^{2n}) .
\]
Its complexified Lie algebra is
\[
{\rm Lie}_{\CC} (\U(n) \ltimes \RR^{2n}) \simeq \mathfrak{u}(n) \ltimes \CC^{2n}
\]
with $\CC^{2n}$ spanned by the translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$.

This abelian Lie algebra $\CC^{2n}$ contains both the holomorphic and anti-holomorphic translations. 
For a holomorphic factorization algebra we want to consider translation invariant factorization algebras whereby only the holomorphic translations act nontrivially. 
A homotopical way to encode this is to introduce the dg Lie algebra $\CC^{n}_{\rm hol}$ concentrated in degrees zero and $(-1)$. 
In degree zero, this dg Lie algebra is $2n$-dimensional spanned by all translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$.
The degree $(-1)$ piece is $n$-dimensional spanned by elements $\{\Bar{\eta}_i\}$. 
The differential is simply $\d \Bar{\eta}_i = \partial_{\zbar_i}$.

Its immediate to see that $\CC^n_{\rm hol}$ is quasi-isomorphic to the abelian Lie algebra spanned by the {\em holomorphic} translations $\{\partial_{z_i}\}$.

\begin{dfn}
An $n$-dimensional {\em holomorphic factorization algebra} is a smoothly~\footnote{\brian{recall smooth}}~$\U(n) \ltimes \RR^{2n}$-equivariant factorization algebra $\cF$ on $\CC^n$ together with an extension of the complex Lie algebra of infinitesimal symmetries
\[
{\rm Lie}_{\CC} (\U(n) \ltimes \RR^{2n}) = \mathfrak{gl}(n) \ltimes \CC^{2n}
\]
to the dg Lie algebra 
\[
\mathfrak{gl}(n) \ltimes \CC^{n}_{\rm hol} .
\]
\end{dfn}

Let $D^n(r)$ be an $n$-disk supported at the origin in $\CC^n$. 
By definition, if $\cF$ is an $n$-dimensional holomorphic factorization algebra then $\cF(D^n (r))$ is a $\U(n)$-representation. 
Consider the maximal torus $\U(1)^{\times n} \subset \U(n)$ which encodes the $S^1$ rotation in each coordinate. 
Let $\cF_{(k_1,\ldots, k_n)}(r) \subset \cF(D^n(r))$ be the eigenspace of weight $(k_1,\ldots, k_n)$ with respect to the action by this subgroup. 
By assumption, this is a sub cochain complex.

Let ${\rm rad} \colon \CC^n \setminus \{0\} \to \RR_{>0}$ be the radial projection.
Similarly as in the case of an $n$-disk, for $r < s$ let $\cF_{(k_1,\ldots, k_n)}(r<s) \subset \cF_{(k_1,\ldots, k_n)}\left({\rm rad}^{-1}(r, s) \right)$ denote the eigenspace of weight $(k_1,\ldots, k_n)$ with respect to the action by $\U(1)^{\times n}$.

We say that a holomorphic factorization algebra $\cF$ is {\em nice} if for every quadruple of positive real numbers $0 < r' < r < s < s'$ and sequence of integers $(k_1, \ldots, k_n)$ the following conditions hold:
\begin{itemize}
\item the natural map 
\[
\cF_{(k_1,\ldots, k_n)}(r) \xto{\simeq} \cF_{(k_1,\ldots, k_n)}(s)
\]
induced from the embedding of disks $D^n(r) \hookrightarrow D^n (s)$ is a quasi-isomorphism.
\item the natural map
\[ 
\cF_{(k_1,\ldots, k_n)}\left(r < s \right) \to \cF_{(k_1,\ldots, k_n)}\left(r' < s' \right) 
\]
induced from the embedding of open sets ${\rm rad}^{-1}(r,s) \hookrightarrow {\rm rad}^{-1} (r',s')$ is a quasi-isomorphism.
\end{itemize}

\begin{dfn}
Suppose that $\cF$ is a nice $n$-dimensional holomorphic factorization algebra. 
Define the following cochain complexes:
\begin{itemize}
\item[(1)] 
The {\em state space} of $\cF$ is the cochain complex
\[
\sfV_{\cF} \define \oplus_{k_1,\ldots, k_n} \cF_{(k_1,\ldots, k_n)}(1) .
\]
\item[(2)]
The $S^{2n-1}$-{\em operators} (or simply, spherical operators) of $\cF$ is the cochain complex
\[
\oint_{S^{2n-1}} \cF \define \oplus_{k_1,\ldots, k_n} \cF _{(k_1,\ldots, k_n)}\left(1 < 2\right) .
\]
\end{itemize}
\end{dfn}

\begin{thm}
Suppose that $\cF$ is a nice $n$-dimensional holomorphic factorization algebra. 
Then
\begin{itemize}
\item The cochain complex of spherical operators $\oint_{S^{2n-1}} \cF$ has the structure of an $A_\infty$ algebra.
\item The state space $\sfV_\cF$ is an $A_\infty$-module for $\oint_{S^{2n-1}} \cF$. 
\end{itemize}
\end{thm}

\section{State-operator/descent}

In complex dimension one holomorphic factorization algebras recover the theory of vertex algebras. 
Paramount to this relationship is pinning down the geometric meaning of the {\em state-operator} map
\[
Y \colon \sfV \to {\rm End}(\sfV)[[z,z^{-1}]] .
\]
\brian{interpret}

Suppose that $\cF$ is a holomorphic factorization algebra. 
In particular, $\cF$ is translation invariant implying, in particular, that there is an identification of the value of $\cF$ on an $n$-disk centered at zero and any translate of it.
In this way, if $\cO \in \sfV = \sfV_{\cF}$ is an element of the state space then we obtain a smooth function $z \mapsto \cO(z,\zbar)$ obtained by translating the state space to the disk centered at $z$.

In other words, we can use translation invariance to define a translation invariant vector bundle $\cV$ (valued in cochain complexes) whose fiber over zero is $\sfV$. 
In fact, by the axioms of a holomorphic factorization algebra this is actually a holomorphic vector bundle.

Define the Dolbeault valued operator $\cO \in \Omega^{0,\bu}(\CC^n, \sfV)$. 
\[
\Tilde{\cO} (z,\zbar) \define \exp \bigg( \d \zbar_i \, \Bar{\eta}_i \bigg) \cO(z, \zbar) 
\]
\brian{``holomorphic descent''}

Of course, the Dolbeault complex with values in any holomorphic vector bundle forms a sheaf. 
Applied to the inclusion $\CC^n \setminus \Bar{D}_r(0) \hookrightarrow \CC^n$, where $\Bar{D}_r(0)$ is the closed $n$-disk centered at zero, we obtain a restriction map 
\[
\Omega^{0,\bu}(\CC^n, \sfV) \to \Omega^{0,\bu}\left(\CC^n \setminus \Bar{D}^n_r(0), \sfV\right) .
\]
In particular, given any state $\cO$ we obtain an element on the right hand side of this map that we still denote by $\Tilde{\cO}(z, \zbar)$.

Given another state $\cO'$ we can consider the $z$-dependent factorization product $\cO \star \Tilde{\cO}(z,\zbar)$. 
This factorization product makes sense as we can assume that $\cO'$ lives in the value of the factorization algebra of a disk of radius $\leq r$.

Finally, suppose that $\alpha \in \sfA_n$ is of cohomological degree $k$. 
Define the linear map
\[
Y_\alpha (\cO) \colon \sfV \to \cF(D^n_R(0))[??]
\]
by sending an element $\cO'$ to 
\[
\oint_{S^{2n-1}} \d^n z \wedge \alpha (z,\zbar) \wedge \big[\Tilde{\cO}(z,\zbar) \star \cO'\big]  
\]
where $S^{2n-1}$ is any sphere of radius $R \geq r$.

\begin{lem}
The image of $Y_\alpha(\cO)$ is a subspace of $\sfV \subset \cF(D^n_R(0))$. 
In other words, $Y_{\alpha}(\cO)$ determines an endomorphism of $\sfV$. 
\end{lem}

As it stands, the endomorphism $Y_\alpha$ depends on a lot of data: the specific homotopies $\eta$, the radius of the sphere $S^{2n-1}$, etc.. 
In cohomology, however, we do get a well-defined map 
\[
Y \colon H^\bu(\sfV) \to {\rm End}(H^\bu(\sfV)) \otimes H^\bu(\sfA_n)^\vee [1-n]
\]
which sends $[\cO] \in H^\bu(\sfV)$ and $[\alpha] \in H^\bu(\sfA_n)$ to the endomorphism $[Y_\alpha(\cO)]$ which is independent of all the choices mentioned above.

\end{document}

### 2021-05-26 PartII.tex
written stuff by O

\documentclass[11pt]{amsart}

\usepackage{macros, setspace}

\def\U{{\rm U}}
\def\mc{\mathcal}
\def\mcol{\, | \,}
\def\ot{\otimes}
\def\Disj{\operatorname{Disj}}
\def\Open{\operatorname{Open}}
\def\Vect{\operatorname{Vect}}

%trying this out
%\usepackage[upint]{stix}
%\usepackage{cmupint}

\def\brian#1{{\textcolor{blue!65!red}{BRW: {#1}}}}
\def\owen#1{{\textcolor{green!65!black}{OGG: {#1}}}}

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}

\title{Part II}

\spacing{1.25}

\begin{document}
\maketitle

\section{Factorization algebras and quantum field theory}
\label{prefactorization_algebras}

A key idea for us is that much of the content in field theories --- both classical and quantum --- are captured by factorization algebras.
We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
With the notion in hand, we will describe several examples and several situations where factorization algebras have already appeared in mathematics and physics, 
albeit in a different formulation.
Finally, we will sketch the main theorem of \cite{CG2}, 
which explains a precise and general relationship between quantum field theories and factorization algebras.

\subsection{The essential idea of a prefactorization algebra}

Let $M$ be a topological space and let $\mc{C}^\otimes$ be a symmetric monoidal category. 
In this paper $M$ is always a smooth manifold (typically a complex manifold) and $\mc{C}$ is ${\rm Vect}$ or ${\rm dgVect}$, with the usual tensor product as the symmetric monoidal product.

A {\em prefactorization algebra} $\cF$ on $M$ taking values in cochain complexes is a rule that assigns a cochain complex $\cF(U)$ to each open set $U \subset M$ along with the following maps and compatibilities.
\begin{itemize}
\item  There is a cochain map $m_V^U: \cF(U) \rightarrow \cF(V)$ for each inclusion $U \subset V$.

\item There is a cochain map $m_V^{U_1,\ldots,U_n} : \cF(U_1) \otimes \cdots \otimes \cF(U_n) \rightarrow \cF(V)$ for every finite collection of open sets where each $U_i \subset V$ and the $U_i$ are pairwise disjoint. The following picture represents the situation.
\begin{center}
 \begin{minipage}[c]{3cm}
 \begin{tikzpicture}[scale=0.25]
 \draw (0,0) circle (5);
 \draw (-1.5,2) circle(1.3) node {$U_1$};
 \draw (-2.2,-1.5) circle (1.5) node {$U_2$};
 \draw (0, -3) node {\tiny$\dots$};
 \draw (2.1,-1) circle (1.8) node {$U_n$};
 \draw (2.1, 3) node {$V$};
 \end{tikzpicture}
 \end{minipage}
\hspace{0.7cm} $\rightsquigarrow$ \hspace{0.5cm}
 \begin{minipage}[c]{8cm}
$\cF(U_1)\otimes\dots\otimes\cF(U_n)\xto{m_V^{U_1,\ldots,U_n}}\cF(V),$
 \end{minipage}
\end{center}

\item The maps are compatible in the obvious way, so that if $U_{i,1}\sqcup\cdots\sqcup U_{i,n_i}\subseteq V_i$ and $V_1\sqcup\cdots\sqcup V_k\subseteq W$, the following diagram commutes.
\begin{center}
\begin{tikzcd}[column sep=small]
{\bigotimes}^{k}_{i=1}{\bigotimes}^{n_i}_{j=1}\cF(U_j) \arrow{dr} \arrow{rr} &   &{\bigotimes}^k_{i=1}\cF(V_i) \arrow{dl}\\
&\cF(W)  &
\end{tikzcd}
\end{center}
\end{itemize}

For an explicit example of the associativity, consider the following picture.
\begin{center}
\hspace{-1cm}
\begin{minipage}{3cm}
{\tiny
\begin{center}
\begin{tikzpicture}[scale=0.35]
 % big circle:
\draw (0,0) circle (6);
\draw (2.4, 3.3) node {$W$};
 % circle V_1:
\draw [style=loosely dashed] (-2.2,1.6) circle (2.5);
\draw (-2.4, 2.8) node {$V_1$};
 % circle V_2:
\draw [style=loosely dashed] (2.4,-1.5) circle (2.6);
\draw (3.2, 0) node {$V_2$};
 % small circles:
\draw (-2.5, 0.8) circle (1) node {$U_{1,1}$};
\draw (-0.8, 1.8) circle (0.8) node {$U_{1,2}$};
\draw (2.5,-1.5) circle (0.9) node {$U_{2,1}$};
%\draw (2.9, -2.1) circle (1.1) node {$U_{2,2}$};
\end{tikzpicture}
\end{center}
}
 \end{minipage}
 \hspace{1.3cm} $\rightsquigarrow$ \hspace{-0.1cm}
\begin{minipage}{8cm}
\begin{tikzcd}[column sep=small]
\cF(U_{1,1}) \otimes \cF(U_{1,2}) \otimes \cF(U_{2,1}) \arrow{dr} \arrow{r}  & \cF(V_1) \otimes \cF(V_2) \arrow{d}\\
&\cF(W) 
\end{tikzcd}
\end{minipage}

The case of $k=n_1=2$, $n_2 = 1$.
\end{center}

This definition bears analogies to familiar objects in mathematics.
On the one hand, $\cF$ resembles a {\em precosheaf}, which is a functor from opens in $M$ to a category like ${\rm Vect}$ or ${\rm dgVect}$.
(A presheaf is a functor out of the opposite category to opens in $M$.) 
Here, however, $\cF$ also assign values to disjoint unions of opens, and it uses the tensor product rather than direct sum.
This feature leads to the other analogy: $\cF$ resembles an algebra, as
the multilinear maps look like multiplications.
These maps let us multiply elements from disjoint regions to get an element in a larger region.

Note that these axioms imply that $\cF(\emptyset)$ is a commutative algebra. 
We say that $\cF$ is a \emph{unital} prefactorization algebra  if $\cF(\emptyset)$ is a unital commutative algebra. In this case, $\cF(U)$ is a pointed cochain complex by the image of the unit $1 \in \cF(\emptyset)$ under the structure map $\cF(\emptyset) \to \cF(U)$. In practice, for our examples, $\cF(\emptyset)$ is $\CC$, $\RR$, $\CC[[\hbar]]$, or $\RR[[\hbar]]$.

\begin{eg}\label{ex:associativealgebra}
The crucial example to bear in mind is an associative algebra. Every associative algebra $A$ defines a prefactorization algebra $\cF_A$ on $\RR$, as follows. To each open interval $(a,b)$, we set $\cF_A( (a,b) ) = A$. To any open set $U = \coprod_j I_j$, where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$. The structure maps simply arise from the multiplication map for $A$. Figure ~\ref{fig:assasfact} displays the structure of $\cF_A$. Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra. 
%(One takes an infinite tensor products of unital algebras, as follows. Given an infinite set $I$, consider the poset of finite subsets of $I$, ordered by inclusion. For each finite subset $J \subset I$, we can take the tensor product $A^J = \bigotimes_{j \in J} A$. For $J \hookrightarrow J'$, we define a map $A^J \to A^{J'}$ by tensoring with the identity $1 \in A$ for every $j \in J' \backslash J$. Then $A^I$ is the colimit over this poset.) 
~\hfill$\Diamond$
\end{eg}

%\begin{figure}
%\begin{center}
% \begin{minipage}{3cm}
% \begin{tikzpicture}[scale=0.75]
% \begin{scope}[line cap=round,ultra thick]
% \draw (-2.5,0) -- (-1.5,0); 
% \draw (-1,0) -- (-0.5,0); 
% \draw (1,0) -- (2,0); 
% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
% \draw (-2.75,-2) -- (-0.25,-2); 
% \draw (0.75,-2) -- (2.5,-2);  
% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
% \draw (-3,-4) -- (3,-4); 
% \end{scope}
% \end{tikzpicture}
% \end{minipage}
%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
% \begin{minipage}{8cm}
% \begin{tikzcd}[cramped,column sep=tiny]
%a \otimes b \otimes c \arrow[mapsto]{d} & \in & A \otimes A \otimes A \arrow{d} \\
%ab \otimes c \arrow[mapsto]{d} & \in & A \otimes A \arrow{d} \\
%abc  & \in &A 
%\end{tikzcd}
%\end{minipage}
%\end{center}

\begin{figure}
\begin{center}
 \begin{tikzpicture} 
 \begin{scope}[line cap=round,ultra thick]
 \draw (-2.5,1) -- (-1.5,1); 
 \draw (-1,1) -- (-0.5,1); 
 \draw (1,1) -- (2,1); 
 \draw[->,semithick] (0,0.75) -- (0,0.25);
 \draw (-2.75,-0.1) -- (-0.25,-0.1); 
 \draw (0.75,-0.1) -- (2.5,-0.1);  
 \draw[->,semithick] (0,-0.35) -- (0,-0.85);
 \draw (-3,-1.2) -- (3,-1.2); 
 \end{scope}

\node at (4,0) {$\rightsquigarrow$ };

\node at (7,0){
\begin{tikzcd}[cramped,column sep=tiny]
a \otimes b \otimes c \arrow[mapsto]{d} & \in & A \otimes A \otimes A \arrow{d} \\
ab \otimes c \arrow[mapsto]{d} & \in & A \otimes A \arrow{d} \\
abc  & \in &A 
\end{tikzcd}
};
\end{tikzpicture}
\end{center}
\caption{The prefactorization algebra $\cF_A$ of an associative algebra $A$}
\label{fig:assasfact}
\end{figure}

\begin{eg}\label{ex:SymOfCosheaf}
Another important example for us is the symmetric algebra of a precosheaf. 
Let $F$ be a precosheaf of vector spaces on a space $X$. 
For example, consider $F = C^\infty_c$ the compactly supported smooth functions on a manifold. The functor $\cF  = \Sym F: U \mapsto \Sym(F(U))$ defines a precosheaf of commutative algebras, but it also a prefactorization algebra. For instance, if $U$ and $V$ are disjoint opens, we see that
\begin{align*}
\cF(U \sqcup V) = \Sym F(U \sqcup V) & \cong \Sym (F(U) \oplus F(V)) \\ & \cong \Sym(F(U)) \otimes \Sym(F(V)) = \cF(U) \otimes \cF(V),
\end{align*}
and these isomorphisms provide the structure maps for $\cF$.~\hfill$\Diamond$
\end{eg}

We will now sketch another way of phrasing this idea, but the reader who is content with this definition and eager to see examples should feel free to jump ahead, referring back as needed.

\subsection{Prefactorization algebras as algebras over an operad}
\label{sec:disj}

The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
See \owen{add citations}

\begin{dfn}
Let $\Disj_M$ denote the following colored operad associated to~$M$: 
\begin{itemize}
\item The colors (or objects) consist of all open subsets of $M$. 
\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$. If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point. Otherwise, the set of maps is empty.
\item The composition of maps is defined in the obvious way. 
\end{itemize}
\end{dfn}

\begin{dfn}
Let $\mc{C}$ be a colored operad. 
A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
\end{dfn}

In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories.

\begin{rmk} 
If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
~\hfill$\Diamond$ 
\end{rmk}

Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$.

\begin{dfn}
We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
\end{dfn}

\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
\label{AssAsFact}

We explained above how an associative algebra provides a prefactorization algebra on the real line. There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras. Here we will characterize those that do arise from associative algebras.

\begin{dfn}
Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
\end{dfn}

It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.

\begin{lem}\label{locally_constant_is_associative}
Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
\end{lem}

One can got further, however, and also capture modules, essentially by marking the line with points.
For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.

Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$. 
We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure.

Pick a point $p \in \RR$. On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$. Likewise, on the half-line $\{x \in \RR \mid p < x\}$, $\cF_M$ is given by $\cF_B$. Intervals containing $p$ are determined, though, by $M$. When we consider an interval $I = (t_0,t_1)$ such that $t_0 < p < t_1$, we set $\cF_M(I)  = M$. The structure maps are also determined by the bimodule structure. For example, given 
\[
s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
\]
we have
\begin{align*}
\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
&= A \ot M \ot B
\end{align*}
and the inclusion of these three intervals into $(s_0,u_1)$ is the map
\[
\begin{array}{ccc}
\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
a \ot m \ot b & \mapsto & amb
\end{array}.
\]
The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.

%\begin{figure}
%\begin{center}
% \begin{minipage}{3cm}
% \begin{tikzpicture}[scale=0.75]
% \begin{scope}[line cap=round,ultra thick]
% \draw (-2.5,0) -- (-1.5,0); 
% \draw (-1,0) -- (0.5,0); 
% \draw[fill=black] (0,0) circle (0.07);
% \draw (1.5,0) -- (2.5,0); 
% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
% \draw (-2.75,-2) -- (0.75,-2); 
% \draw[fill=black] (0,-2) circle (0.07);
% \draw (1.25,-2) -- (2.75,-2);  
% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
% \draw (-3,-4) -- (3,-4);
% \draw[fill=black] (0,-4) circle (0.07); 
% \end{scope}
% \end{tikzpicture}
% \end{minipage}
%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
% \begin{minipage}{8cm}
% \begin{tikzcd}[cramped,column sep=tiny]
%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
%amb  & \in &M 
%\end{tikzcd}
%\end{minipage}
%\end{center}
%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
%\label{fig:bimodasfact}
%\end{figure}

\begin{figure}
\begin{center}
 \begin{tikzpicture}
 \begin{scope}[line cap=round,ultra thick]
 \draw (-2.5,1) -- (-1.5,1); 
 \draw (-1,1) -- (0.5,1); 
 \draw[fill=black] (0,1) circle (0.07);
 \draw (1.5,1) -- (2.5,1); 
 \draw[->,semithick] (0,0.75) -- (0,0.25);
 \draw (-2.75,-0.1) -- (0.75,-0.1); 
 \draw[fill=black] (0,-0.1) circle (0.07);
 \draw (1.25,-0.1) -- (2.75,-0.1);  
 \draw[->,semithick] (0,-0.35) -- (0,-0.85);
 \draw (-3,-1.2) -- (3,-1.2);
 \draw[fill=black] (0,-1.2) circle (0.07); 
 \end{scope}

\node at (4,0){$\rightsquigarrow$};

\node at (7,0) {
\begin{tikzcd}[cramped,column sep=tiny]
a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
amb  & \in &M 
\end{tikzcd}
};

\end{tikzpicture}
\end{center}
\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
\label{fig:bimodasfact}
\end{figure}

\subsection{Factorization algebras}

We are now in a position to define factorization algebras,
which are prefactorization algebras whose behavior on large open sets is determined by their behavior on small open sets.
To give a precise description, we introduce a Grothendieck topology due to Michael Weiss~\owen{cite  \cite{Weiss} and it is explained nicely and further developed in \cite{BoavidaWeiss}}.

\begin{dfn}
Let $U$ be an open set. A collection of open sets $\mathfrak{U} = \{ U_i \mid i \in I\}$ is a {\em Weiss cover} of $U$ if for any finite collection of points $\{x_1,\ldots,x_k\}$ in $U$, there is an open set $U_i \in \mathfrak{U}$ such that $\{x_1,\ldots,x_k\} \subset U_i$.
\end{dfn}

The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$.

\begin{rmk}
A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens. It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$. For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection 
\[
\{ U_i^n \mid i \in I\}
\]
provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
\end{rmk}

\begin{eg}\label{WeissAsExponential}
For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$. One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disk. Alternatively, the collection of opens $\{ M \setminus q \mcol q \in M\}$ is a Weiss cover of $M$. One can also produce a Weiss cover of a manifold with countably many elements. Fix a Riemannian metric on $M$. Pick a collection of points $\{q_n\in M \mcol n \in \NN\}$ such that the union of the unit ``discs'' $D_1(q_n) = \{ q \in M \mcol \d(q_n,q) < 1\}$ covers $M$. (Such an open may not be homeomorphic to a disc if the injectivity radius of $q_n$ is less than 1.)  Consider the collection of all ``discs'' $\fD = \{ D_{1/m}(q_n) \mcol m \in \NN, n \in \NN\}$.  The collection of all finite, pairwise disjoint union of elements of $\fD$ is a countable Weiss cover.~\hfill $\Diamond$ 
\end{eg}

Now that we have a notion of cover, we can formulate the local-to-global property for factorization algebras,
which amounts to being a cosheaf for the Weiss topology.
For concreteness' sake, we will continue to have our prefactorization algebras take values in ${\rm dgVect}$,
but it is straightforward to generalize by allowing the values to live in, say, a symmetric monoidal $\infty$-category.

Let us provide the definition of a homotopy cosheaf. 
Let $\Phi$ be a precosheaf on $M$ with values in cochain complexes. Let $\mathfrak{U} = \{U_i \mid i \in I\}$ be a cover of some open subset $U$ of $M$.  Consider the cochain complex with values in cochain complexes whose $-k$th term is 
\[
\bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}),
\]
and note that this term has an ``internal'' differential arising from $\Phi$. The ``external'' differential is the alternating sum of the structure maps arising from inclusion of $k+1$-fold intersections into $k$-fold intersections. The \emph{\v{C}ech complex of $\mathfrak{U}$ with coefficients in $\Phi$} is the totalization of this double complex:
$$
\check{C}(\mathfrak{U}, \Phi) = \bigoplus_{k=0}^\infty \left( \bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}) [ k]   \right).
$$
There is a natural map from the $0$th term (of the double complex) to $\Phi(U)$ given by the sum of the structure maps $\Phi(U_i) \to \Phi(U)$. Thus, the \v{C}ech complex possesses a natural map to $\Phi(U)$. We say that $\Phi$ is a \emph{homotopy cosheaf} if the natural map from the \v{C}ech complex to $\Phi(U)$ is a quasi-isomorphism for every open $U \subset M$ and every open cover of $U$. This \v{C}ech complex is simply the dual of the \v{C}ech complex for sheaves of cochain complexes.
In more sophisticated language, the \v{C}ech complex describes the homotopy colimit of $\Phi$ on this simplicial diagram.

We can now define our main object of interest.

\begin{dfn}
A \emph{factorization algebra} is a prefactorization algebra $\cF$ on $M$ valued in $\Ch$ \owen{change to dgVect?}, with the property that for every open set $U \subset X$ and Weiss cover $\mathfrak{U}$ of $U$, the natural map
$$
\check{C}(\mathfrak{U},\cF) \to \cF(U)
$$
is a quasi-isomorphism. That is, $\cF$ is a homotopy cosheaf with respect to the Weiss topology.
\end{dfn}

We also formulate a multiplicativity condition, as follows.

\begin{dfn}
A factorization algebra $\cF$ is \emph{multiplicative} if for every pair $U,V$ of disjoint open subsets of $M$, the structure map
$$
\cF(U) \otimes \cF(V) \to \cF(U \sqcup V) 
$$
is a quasi-isomorphism.
\end{dfn}

As verification that this notion has some real content, let's consider a first, interesting case.
We already explained how to produce a locally constant prefactorization algebra $\cF_A$ on $\RR$ from a dg associative algebra $A$.
We could ask about working on the circle $S^1$ instead of $\RR$.
This construction tells us what to assign to every proper open subset of $S^1$: for instance, to each open interval, we assign $A$.
The \v{C}ech complex should then tell us what to assign to the whole circle.
Remarkably, this construction recovers a well-known invariant: the Hochschild chains ${\rm Hoch}_*(A)$ of~$A$.

\begin{thm}[\owen{citations}]
The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
\[
{\rm Hoch}_*(A) \simeq \check{C}(\mathfrak{U},\cF_A)
\]
for any Weiss cover of~$S^1$.
\end{thm}

The reader can check by hand that for an ordinary algebra $A$, the value on the circle is $A/[A,A] = {\rm HH}_0(A)$.
This theorem tells us that factorization homology can be seen as a generalization of Hochschild homology,
where one simultaneously generalizes the circle to an arbitrary closed manifold and an algebra to a factorization algebra.

It can be hard to check whether a given $\cF$ is a homotopy cosheaf, since computing the \v{C}ech complex is typically difficult.
There are some useful abstract results, such as the fact that a factorization algebra is determined by its behavior on a basis for the Weiss topology.
But there is also a rich source of examples in differential geometry, and hence from physics.

Given a vector bundle $E \to M$ (possibly a graded vector bundle), 
let $E^{\boxtimes m} \to M^m$ denote the external product of $E$ with itself $m$ times.
Let $\cE_c(U)$ denote compactly supported sections of $E$ over $U$, 
and similarly let $\cE^{\boxtimes m}_c(U^m)$ denote compactly supported sections of $E^{\boxtimes m}$ over $U^m$.
Let $\Sym^m(\cE_c)(U)$ denote the sections that are invariant under the action of the symmetric group $S_m$ on~$U^m$.
We define a functor $\Sym(\cE_c): \Open(M) \to \Vect$ by
\[
\Sym(\cE_c)(U) = \bigoplus_m \Sym^m(\cE_c)(U),
\]
which is a kind of symmetric algebra on $\cE_c(U)$.
(Those familiar with functional analysis will note that taking sections of the product bundles is a nice way of completing the algebraic tensor product of sections on each component bundle.)
This construction is actually a cosheaf for the Weiss topology, just as $\cE_c$ is a cosheaf for the ordinary topology;
in this sense, the Weiss topology is an ``exponentiation'' of the ordinary topology just as $\Sym(V)$ is an ``exponentiation'' of a vector space~$V$.
We have seen in Example~\ref{ex:SymOfCosheaf} how $\Sym(\cE_c)$ determines a prefactorization algebra,
so the following theorem should be plausible.

\begin{thm}[\owen{cite book}]
For $E \to M$ a graded vector bundle, the functor $\Sym(\cE_c)$ encodes a factorization algebra on $M$.
If we equip $\cE_c$ with a differential operator $d$ of degree 1 suc that $d^2 = 0$ so that $(\cE_c, d)$ is a cosheaf of differential complexes,
then $(\Sym(\cE_c), d)$ is a factorization algebra, where $d$ denotes the natural extension.
\end{thm}

Two examples of differential complexes play a key role in applications: 
\begin{itemize}
\item the de Rham complex $(\Omega^*, d)$ on a smooth manifold, which is relevant for topological field theories, and 
\item the Dolbeault complex $(\Omega^{0,*}, \dbar)$ on a complex manifold, which is relevant for holomorphic field theories.
\end{itemize}
One can take, of course, these complexes with sections in a flat vector bundle (for the de Rham case) or a holomorphic vector bundle (for the Dolbeault case).

\subsection{Algebras over the little disks operad}

Associative algebras are familiar to every mathematician, but as we have just seen, they reflect and encode one-dimensional geometry.
It is then natural to ask about higher-dimensional versions of algebra.
Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-disks operad,
which we now describe and relate to prefactorization algebras on~$\RR^n$.
In relation to the subject of this paper, we mention that $E_n$ algebras arise naturally from $n$-dimensional topological field theories;
we will soon introduce a holomorphic analog of $E_n$ algebras relevant to holomorphic field theories,
modeled on the discussion here.

Fix a dimension $n$. 
Let $D^n(x,r)$ denote the open disk of radius $r$ centered at $x \in \RR^n$,
and let $D^n$ denote the unit disk~$D^n(0,1)$.

\begin{dfn}
Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint disks:
\[
E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the disks $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disk $D^n$\end{tabular}}\right\}.
\]
\end{dfn}

When $n = 1$, the operad encodes the idea of associative multiplication:
we get pictures much like those we drew earlier with intervals, 
except that now we can slide and stretch the intervals because we have a space of operations.
More accurately, $E_1$ is a model for associative algebras up to homotopy; 
it is closely related to the $A_\infty$ operad. \owen{Let me check how people compare these.}

For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
If one fixes a direction, such as a coordinate axis, and works with disks lined up in this direction,
one sees an $E_1$ structure.

\owen{Add picture? We drew 2d pictures earlier.}

An algebra over this operad is called an $E_n$-algebra.
A classic example from topology is given by taking the $n$-fold based loop space
\[
\Omega^n_x(X) = \{ \gamma: \overline{D^n} \to X \mcol \gamma(\partial \overline{D^n}) = x\}
\]
of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disk.
Maps that send the boundary of a disk to the base point can be extended naturally to bigger disks: just send the rest of the big disk to the basepoint.
\owen{Should I spell out the structure of the algebra?}
Examples include \owen{What to mention?}

Factorization algebras on $\RR^n$ and $E_n$ algebras should be closely related,
as can be seen by drawing pictures of the configurations of disks that control operations.

\begin{dfn}
A factorization algebra $\cF$ on an $n$-manifold $M$ is \emph{locally constant} if for each inclusion of open disks $D \subset D'$, then the map $\cF(D) \to \cF(D')$ is a quasi-isomorphism.
\end{dfn}

For $M = \RR$, we have already discussed how locally constant factorization algebras relate to associative algebras, starting with Example~\ref{ex:associativealgebra}.
Lurie has shown the following vast extension of this example. (See section 5.4.5 of \cite{LurieHA}, particularly Theorem 5.4.5.9.)

\begin{thm}\label{thm:locisen}
There is an equivalence of $(\infty,1)$-categories between $E_n$ algebras and locally constant factorization algebras on~$\RR^n$.  
\end{thm}

We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do. A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}. We emphasize that higher categories are necessary for a rigorous development of these constructions and comparisons, although we will not emphasize that point in our discussion below, which is expository in nature.

\begin{rmk}
This theorem, together with our work in these two books, builds an explicit bridge between topology and physics. Topological field theories in the physicist's sense, such as perturbative Chern-Simons theory, produce locally constant factorization algebras, which can then be viewed as $E_n$ algebras and analyzed using the powerful machinery of modern homotopy theory. Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.~\hfill $\Diamond$
\end{rmk}

\begin{rmk}
We have shown how thinking about prefactorization algebras on a real line ``decorated'' with points (i.e., with a kind of stratification) reflects familiar algebraic objects like bimodules. By moving into higher dimensions and allowing more interesting submanifolds and stratifications, one generalizes this familiar algebra into new, largely-unexplored directions. See \cite{AyalaFrancisTanaka} for an extensive development of these ideas in the setting of locally constant factorization algebras.
~\hfill $\Diamond$
\end{rmk}

\subsection{How factorization algebras appear in QFT}

In \cite{CG1, CG2} a systematic relationship is provided between field theories and factorization algebras.
The slogan is 
\begin{quote}
the observables of a field theory living on a manifold $M$ form a factorization algebra on~$M$. 
\end{quote}
To make a mathematical statement, one needs to be precise about what a field theory is.
From hereon, whenever we speak of a classical or quantum field theory, we will mean the definitions articulated in \cite{CosBook,CG1, CG2}, which encompass the Euclidean versions of many field theories studied in physics and mathematics.
Those books use the Batalin-Vilkovisky (BV) formalism for quantization, a homological method generalizing the BRST approach and widely regarded as the most powerful and general way to quantize gauge theories.

\begin{thm}
\label{main}
The observables of a classical field theory on $M$ form a factorization algebra $\Obs^{cl}$ that assigns to every open set, a 1-shifted Poisson algebra (i.e., a commutative dg algebra equipped with a Poisson bracket of cohomological degree one). A BV quantization of this theory yields a factorization algebra $\Obs^q$ that is a flat deformation of $\Obs^{cl}$ over~$\RR[[\hbar]]$.
\end{thm}

This theorem provides an elegant interpretation of BV quantization as a kind of deformation quantization. In the setting of mechanics (or one-dimensional field theory, since a particle has a worldline), deformation quantization explains the transition from classical to quantum as deforming the observables from a Poisson algebra to an associative algebra. 
This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra.

In \cite{CG1}, there are several examples of this formalism in action:
\begin{itemize}
\item Basic examples from quantum mechanics, such as the harmonic oscillator, and it is shown how to recover the Weyl algebra and the Hamiltonians from factorization algebras living on~$\RR$. 
\item Scalar field theory on $\RR^n$, where it is shown how the usual correlation functions are encoded in the factorization algebra on~$\RR^n$ and how canonical quantization appears via pushforward of factorization algebras.
\item The free $\beta\gamma$ system on $\CC$---a basic example of a chiral conformal field theory---is constructed and its usual vertex algebra is extracted from the factorization algebra.
\item Abelian Chern-Simons theory, where it is shown how dimensional reduction along a closed surface $\Sigma$ produces the Weyl algebra on the symplectic vector space $H^1(\Sigma)$ and how line operators form a (very simple!) braided monoidal category.
\end{itemize}
These examples, while not complicated, exhibit in detail how factorization algebras provide a bridge from action functionals to algebra in a broad sense.

This formalism has shown its power in a number of nontrivial applications:
\begin{itemize}
\item Grady, Li, and Li \cite{GLL} give a direct connection between Fedosov quantization and the factorization algebra of a 1-dimensional field theory.
%\item Gorbounov, Williams and I \cite{GGW} constructed rigorously a 2-dimensional QFT depending on a Calabi-Yau manifold $X$, known as the curved $\beta\gamma$ system, and showed the factorization algebra recovers the chiral differential operators of~$X$.
\item Li and Li \cite{LiLi} constructed the topological B-model and show the factorization algebra recovers the expected topological vertex algebra (see \cite{LiVOA} for a deeper treatment).
\item Costello, Francis, and Gwilliam \cite{CFG} have shown how the factorization algebra of Chern-Simons theory for $\fg$ encodes a quantum group $U_\hbar \fg$ over~$\CC[[\hbar]]$.
\item Rabinovich \cite{RabAxial} showed how the local index theorem and the axial anomaly are simultaneously captured by quantizing free fermions (associated to Dirac operators). Subsequently, he recovered the Quillen determinant line~\cite{RabDet}.
\item Costello \cite{CosYangian} introduced a 4-dimensional gauge theory whose factorization algebra recovers the Yangian,
and subsequently gave extensive applications to quantum integrable systems with Witten and Yamazaki \cite{CWY1,CWY2, CY}.
\end{itemize}
There are others, connected with central topics such as mirror symmetry and the AdS/CFT correspondence, 
and we will discuss holomorphic field theories extensively below.

Thanks to the efforts of people who have adopted this BV/factorization framework,
we now also understand its connection to many important structural aspects of QFT, 
such as asymptotic freedom \cite{EWY}, current algebras \cite{GWcurr}, the Anderson-Higgs mechanism \cite{EG}, and the CS/WZW correspondence~\cite{GRW, CosDimGai}.
In each case this enriched mathematical language offers a new and (we would argue) clarifying point of view.
In turn, physics offers new vistas or rich applications for mathematicians to explore.

\subsection{Chiral conformal field theories and vertex algebras}

\owen{I want to discuss how VOAs relate to factorization algebras, notably our CDO project, Si's results, and Brueggeman's thesis. We should also gesture at the Beilinson-Drinfeld approach.}

\end{document}

### 2021-05-26 whatis.tex
written stuff by O

\documentclass[11pt]{amsart}

\usepackage{macros, setspace}

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
\title{What is a holomorphic field theory}

\def\g{{\mathfrak g}}

\def\brian#1{{\textcolor{blue!65!red}{BRW: {#1}}}}
\def\owen#1{{\textcolor{green!65!black}{BRW: {#1}}}}

\usepackage[upint]{stix}

\begin{document}
\maketitle

\spacing{1.25}

%"classical field theory", don't mention BV.

%the way we discussed previously, this section seemed to be mostly geometric.

%Motivational overview

The most important field theories in physics involve a metric on a manifold (whether Riemannian or Lorentzian), and hence geometry has had a clear role in physics.
In recent decades attention has expanded to include {\em topological} field theories (or TFTs), 
in which --- to simplify --- only the underlying smooth topology of the manifold matters.
There are, however, theories that depend on a complex structure on the manifold,
and as one might hope, these are particularly beautiful, 
just as complex variables is a particularly beautiful wing of analysis.
In essence, such {\em holomorphic} field theories have variational PDE (or ``equations of motion'') that are holomorphic:
the PDE only involves derivatives in the holomorphic coordinates (i.e., the $\partial/\partial z_j$) and has holomorphic coefficients.
These theories admit independent motivations from mathematics and physics,
which we sketch before giving more careful definitions.

The mathematical motivation is simple:
for most holomorphic classical field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
and it is natural to hope that its quantization is equally interesting.
A well-known example is holomorphic Chern-Simons theory,
which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
As a somewhat mundane example, let $\RR\Hol(X,V)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $V$.
(For $V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
One can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
and this derived moduli space encodes solutions to
a theory known as the $\beta\gamma$ system with target $V$.
(The name is silly: it's due to the original notation people used.)
Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.

An essential example for us is ``holomorphic BF theory,''
which is a gauge theory for holomorphic principal $G$-bundles on a complex manifold $X$.
From the perspective of derived geometry, its solutions form the derived moduli space~$T^*[-1] \RR\Bun_G(X)$.

A physical motivation comes from supersymmetric field theories, 
which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a Lie supergroup known as a super Poincar\'e group.
The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
with larger $\cN$ denoting a bigger supergroup. 
Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.

For us, the crucial point is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
As an example, $\cN=1$ supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory, namely a holomorphic BF theory.
It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one, 
much as TFTs have enriched the understanding of supersymmetric theories.
In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''

As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), holomorphic field theories appear as chiral conformal field theories (CFTs) on 2-dimensional manifolds --- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- and have had a strong impact in mathematics.
It is natural to explore higher-dimensional analogs.

The overarching goal of this paper is \owen{continue}

cluster of projects is to bring into sharp mathematical form some of the deep insights into gauge theory offered by physics.
So far, most mathematical effort has focused on classical gauge theory,
but the quantum aspects are profoundly interesting.
We expect that these holomorphic examples will be particularly tractable and beautiful but also useful in offering insights even for non-holomorphic theories.

\subsection{Preliminary notions}

%complex geometry, dolbeault, dg stuff.

\subsection{Precise definitions}

%this section aimed at mathematicians
%emphasize connection with (derived) complex geometry

\subsection{Examples from physics}
%this section aimed at physicists
%twists of SUSY theories
%Owen has some nice thoughts about globalization as it related to SUSY/THF.

Every supersymmetric field theory produces HFTs through a process called {\em twisting},
so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.
As we will explain later, many interesting phenomena for supersymmetric theories have analogs for HFTs.

By definition, a supersymmetric field theory on $\RR^d$ is a theory that is acted upon by a super Poincar\'{e} algebra. 
In this paper we restrict our attention to Euclidean field theories and work in Riemannian signature,
hence for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
\[
\mathfrak{so}(d) \ltimes \ft
\]
where $\ft$ is the super Lie algebra of {\em supertranslations} whose even part $\ft^0 = \RR^d$ is the Lie algebra of ordinary translations and whose odd part $\ft^1$ is a sum of spin representations. 
While the Lie algebra $\RR^d$ of ordinary translations is abelian, the Lie algebra $\ft$ carries a nontrivial (super) Lie bracket,
and this Lie bracket is defined in terms of a $\mathfrak{so}(d)$-equivariant non-degenerate symmetric pairing
\[
\Gamma : {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
\]
by the formula $[Q, Q'] = \Gamma(Q, Q')$.

By a {\em supercharge}, one means an odd supertranslation $Q \in \ft$, and
a {\em twist} is a (nonzero) supercharge $Q$ such that $[Q,Q] = Q^2 = 0$. 
The classification of all twists is a completely algebraic question,
and we refer to~\autocite{ESsusy} for a complete classification of all twists in dimensions from $1$ to~$10$.

If a Lagrangian field theory $\cT$ has $\ft$ as a symmetry, 
then a choice of twist $Q$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^Q$.
If $S$ denotes the action functional of $\cT$, then the action functional $S^Q$ of $\cT^Q$ has the form
\[
S^Q(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(Q \cdot \varphi \right) + \cdots 
\]
where the deformation arises from how $Q$ acts on the theory 
(the $\cdots$ leaves room for terms non-linear in $Q$).
For extensive details on how the twisted theory is defined we refer to~\autocite{CostelloHolomorphic, ESW}.

Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}. 
These twisted theories are analogs of BF theory and Chern--Simons theory,
exactly the kinds of theories we have already discussed, so long as one includes purely topological and purely holomorphic theories. 
We will describe a few examples in detail in the BV formalism in Section~\ref{sec:twistedsusybv},
but we want to indicate now what our main theorem implies about some interesting examples.

For our purposes here, a crucial property of a twist $Q$ is the dimension $k_Q$ of its image ${\rm Im} \; \Gamma(Q, \cdot) \subset \RR^d$,
which we call the number of {\em invariant} directions of~$Q$.
By the non-degeneracy of the pairing $\Gamma$, it follows that $k_Q \geq \frac{d}{2}$.
If the number of invariant directions is maximal with $k_Q = d$, then the twisted theory $\cT^Q$ is purely topological. 
If the number of invariant directions is minimal with $k_Q = \frac{d}{2}$, then the twisted theory $\cT^Q$ is purely holomorphic.

As a representative example of how twisting behaves, 
consider four-dimensional supersymmetric Yang--Mills theory with $\cN=2$ supersymmetry,
which means the odd part $\ft^1$ is eight-dimensional. 
%The sum of two copies of the spin representations.
%\owen{Did I get that right?}
We only consider here the pure gauge theory with Lie algebra~$\fg$. 
Then we have the bounds $2 \leq k_Q \leq 4$, and each value gives a different, well-known field theory:
\begin{itemize}
\item When $k_Q = 4$, the twisted theory is the topological field theory on $\RR^4$ known as {\it Donaldson--Witten theory} \autocite{WittenTQFT};
\item When $k_Q = 3$, the twisted theory is the THFT studied by Kapustin in \autocite{Kapustin};
\item When $k_Q = 2$, the twisted theory is holomorphic BF theory on $\CC^2$ with values in a graded Lie algebra $\fg[\ep]$, where $\ep$ is a parameter of cohomological degree~$1$.
\end{itemize}
We will describe these theories completely later in Section~\ref{sec:twistedsusybv},
but our main theorem implies the following.

\begin{thm}[\owen{cite GRW, maybe also mention our work with Chris?}]
Donaldson--Witten theory, the Kapustin twist, and holomorphic BF theory for $\fg[\epsilon]$ each admit an exact and finite quantization at one loop.
\end{thm}

In other words, by a judicious choice of gauge-fixing, 
we find that the one-loop Feynman diagrams have no UV divergences.
Moreover, no higher loop diagrams appear (for combinatorial reasons),
and the action functional satisfies the quantum master equation.
See Section~\ref{sec: susytwist revisited} for some further discussion.

\subsection{Background}

Although holomorphic field theories had already appeared in practice,
my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
He did the following:
\begin{itemize}
\item gave a precise definition of a holomorphic field theory in the BV formalism,
modeled on and compatible with Costello's approach;
\item established key analytic results about holomorphic renormalization, 
showing that it is highly manageable, with no counterterms to 1-loop; and
\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
\end{itemize}
These apply to all holomorphic theories on $\CC^n$,
but the techniques typically extend to more general complex manifolds.

This foundational work was motivated in large part by our joint effort to generalize to complex $n$-folds results about chiral conformal theories on Riemann surfaces.
A first fruit of our work \cite{GWcurr} is an examination of higher-dimensional {\em current algebras},
which are factorization algebras that generalize the Kac-Moody vertex algebras that play a crucial role in contemporary representation theory.
We show, for instance, that these current algebras arise as the quantization of symmetries of holomorphic field theories, 
much as the affine Lie algebras are symmetries of CFTs on Riemann surfaces.
In addition, we show that encoded in our factorization algebras are the higher Kac-Moody Lie algebras $\widehat{\g}_{d,\theta}$ of Faonte-Hennion-Kapranov~\cite{FHK}. 
It is striking to find this rigid skeleton of algebra under the meat of our analysis,
as our work is strongly differential-geometric in flavor.
Moreover, as their work provides a direct connection with the derived algebraic geometry of $\RR Bun_G(X)$,
there emerges a beautiful generalization of the fertile interactions between algebraic geometry, representation theory, and physics that have grown around bundles on Riemann surfaces.
(The prospect looms that in higher dimensions,
one might find a correspondence between conformal blocks and nonabelian theta functions.)

A second fruit is a collaboration of Williams with the physicist Ingmar Saberi \cite{SabWil1,SabWil2}.
They have carefully worked out the holomorphic twists of several supersymmetric theories
and given a novel approach, via factorization algebras, to the results of Beem et al \cite{Beem}.
Particularly important for this proposal,
they have shown how important invariants (notably the ``supersymmetric index") of the untwisted, supersymmetric theory can be computed simply in the holomorphic twist.

\end{document}

### 2021-05-26 PartII.tex
test

@@
 
+\subsection{$E_n$ algebras from topological field theories}
+
+Although our focus in this paper is on holomorphic field theories and factorization algebras,
+it might be helpful to describe some motivating results about topological field theories and factorization algebras.
+Elliott and Safronov have \owen{not sure how much to say here, but I'm going to take a stab at writing a synoptic theorem}
+
+If one examines theories like Chern-Simons theory on $\RR^3$ or the Poisson $\sigma$-model on $\RR^2$, 
+one discovers a general format for constructing theories that was formalized by \cite{AKSZ}.
+In a nutshell, the field theory is factored into two parts: 
+the de Rham complex of the source or ``spacetime'' manifold, 
+and a Lie algebra-type object encoding a gauge Lie algebra or a ``target'' for a $\sigma$-model.
+
+\begin{dfn}
+A classical {\em AKSZ-type theory} on $\RR^d$ is a determined by an $L_\infty$-algebra $\fg$ equipped with a cyclic pairing $\langle-,-\rangle$ of degree $3-d$.
+Its {\em equation of motion} is the Maurer-Cartan equation 
+\[
+0 = \d A + \frac{1}{2} [A,A] + \frac{1}{3!}[A,A,A]_3 + \cdots = \sum_{k=1}^\infty \frac{1}{k!} [A, \ldots, A]_k
+\]
+of the $L_\infty$ algebra $\Omega^*(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
+The {\em action functional} is the expression
+\[
+S(A) = \int_{\RR^d} \sum_{k=1}^\infty \frac{1}{{k+1}!} \langle A, [A, \ldots, A]_k \rangle
+\]
+\end{dfn}
+
+Ordinary Chern-Simons theory on $\RR^3$ arises from taking $\fg$ to be a semisimple Lie algebra and a choice of invariant pairing.
+In that case, and using $\Tr$ to denote the pairing, the action functional is the familiar
+\[
+S(A) = \int_{\RR^3}  \frac{1}{2}\Tr ( A, \d A ) + \frac{1}{3!} \Tr( A, [A, A])
+\]
+and the equation of motion asks for connections with zero curvature.
+
+Many other theories can be expressed in this style, and we suggest \owen{lots of papers} for examples.
+Elliott and Safronov characterize and exhibit topological twists of supersymmetric theories as AKSZ-type theories.
+
+\begin{thm}[\cite{CG2;ElliottSafronov}]
+For a classical AKSZ-type theory on $\RR^d$, the observables 
+\[
+\Obs^{cl}(U) = \clie^*(\Omega^*(U) \otimes \fg)
+\]
+form a locally constant factorization algebra and hence determine an $E_d$ algebra~$\cA^{cl}$.
+A quantization, if it exists, determines a deformation $\cA^q$ of this $E_d$ algebra.
+
+Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
+More generally, given a map of Lie groups $G \to SO(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.
+\end{thm}
+
+Scheimbauer's thesis then provides a functorial field theory in the sense of Atiyah, Segal, and Lurie.
+
+\begin{thm}
+Given a homotopically $SO(d)$-trivial quantization of a classical AKSZ theory on $\RR^d$, 
+factorization homology of the quantum observables 
+\[
+\int_{-} \cA^q : {\rm Bord}^{or}_d \to {\rm Alg}^{or}_d
+\]
+determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of framed $E_d$ algebras.
+\end{thm}
+
+\owen{I should double-check whether Claudia or someone else has described this oriented Morita category ...}
+
 \subsection{Chiral conformal field theories and vertex algebras}

### 2021-06-02 PartII.tex
updating by O

@@
 Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
-More generally, given a map of Lie groups $G \to SO(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.
 \end{thm}
+
+More generally, given a map of Lie groups $G \to O(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.
 
@@
 \[
-\int_{-} \cA^q : {\rm Bord}^{or}_d \to {\rm Alg}^{or}_d
+\int_{-} \cA^q : {\rm Bord}^{or}_d \to {\rm Alg}_d
 \]
-determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of framed $E_d$ algebras.
+determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of $E_d$ algebras.
 \end{thm}
 
-\owen{I should double-check whether Claudia or someone else has described this oriented Morita category ...}
-
-\subsection{Chiral conformal field theories and vertex algebras}
-
-\owen{I want to discuss how VOAs relate to factorization algebras, notably our CDO project, Si's results, and Brueggeman's thesis. We should also gesture at the Beilinson-Drinfeld approach.}
+A similar claim applies to the general case with a map $G \to O(d)$.
 

### 2021-06-02 PartIII.tex
updating by O

--- 2021-05-26 PartII.tex
@@
 
-\title{Part II}
+\title{Part III}
 
@@
 
-\section{Factorization algebras and quantum field theory}
-\label{prefactorization_algebras}
+\section{Vertex algebras and higher-dimensional analogs \owen{Crappy title}}
 
-A key idea for us is that much of the content in field theories --- both classical and quantum --- are captured by factorization algebras.
-We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
-With the notion in hand, we will describe several examples and several situations where factorization algebras have already appeared in mathematics and physics, 
-albeit in a different formulation.
-Finally, we will sketch the main theorem of \cite{CG2}, 
-which explains a precise and general relationship between quantum field theories and factorization algebras.
-
-\subsection{The essential idea of a prefactorization algebra}
-
-Let $M$ be a topological space and let $\mc{C}^\otimes$ be a symmetric monoidal category. 
-In this paper $M$ is always a smooth manifold (typically a complex manifold) and $\mc{C}$ is ${\rm Vect}$ or ${\rm dgVect}$, with the usual tensor product as the symmetric monoidal product.
-
-A {\em prefactorization algebra} $\cF$ on $M$ taking values in cochain complexes is a rule that assigns a cochain complex $\cF(U)$ to each open set $U \subset M$ along with the following maps and compatibilities.
-\begin{itemize}
-\item  There is a cochain map $m_V^U: \cF(U) \rightarrow \cF(V)$ for each inclusion $U \subset V$.
-
-\item There is a cochain map $m_V^{U_1,\ldots,U_n} : \cF(U_1) \otimes \cdots \otimes \cF(U_n) \rightarrow \cF(V)$ for every finite collection of open sets where each $U_i \subset V$ and the $U_i$ are pairwise disjoint.
-The following picture represents the situation.
-\begin{center}
- \begin{minipage}[c]{3cm}
- \begin{tikzpicture}[scale=0.25]
- \draw (0,0) circle (5);
- \draw (-1.5,2) circle(1.3) node {$U_1$};
- \draw (-2.2,-1.5) circle (1.5) node {$U_2$};
- \draw (0, -3) node {\tiny$\dots$};
- \draw (2.1,-1) circle (1.8) node {$U_n$};
- \draw (2.1, 3) node {$V$};
- \end{tikzpicture}
- \end{minipage}
-\hspace{0.7cm} $\rightsquigarrow$ \hspace{0.5cm}
- \begin{minipage}[c]{8cm}
-$\cF(U_1)\otimes\dots\otimes\cF(U_n)\xto{m_V^{U_1,\ldots,U_n}}\cF(V),$
- \end{minipage}
-\end{center}
-
-\item The maps are compatible in the obvious way, so that if $U_{i,1}\sqcup\cdots\sqcup U_{i,n_i}\subseteq V_i$ and $V_1\sqcup\cdots\sqcup V_k\subseteq W$, the following diagram commutes.
-\begin{center}
-\begin{tikzcd}[column sep=small]
-{\bigotimes}^{k}_{i=1}{\bigotimes}^{n_i}_{j=1}\cF(U_j) \arrow{dr} \arrow{rr} &   &{\bigotimes}^k_{i=1}\cF(V_i) \arrow{dl}\\
-&\cF(W)  &
-\end{tikzcd}
-\end{center}
-\end{itemize}
-
-For an explicit example of the associativity, consider the following picture.
-\begin{center}
-\hspace{-1cm}
-\begin{minipage}{3cm}
-{\tiny
-\begin{center}
-\begin{tikzpicture}[scale=0.35]
- % big circle:
-\draw (0,0) circle (6);
-\draw (2.4, 3.3) node {$W$};
- % circle V_1:
-\draw [style=loosely dashed] (-2.2,1.6) circle (2.5);
-\draw (-2.4, 2.8) node {$V_1$};
- % circle V_2:
-\draw [style=loosely dashed] (2.4,-1.5) circle (2.6);
-\draw (3.2, 0) node {$V_2$};
- % small circles:
-\draw (-2.5, 0.8) circle (1) node {$U_{1,1}$};
-\draw (-0.8, 1.8) circle (0.8) node {$U_{1,2}$};
-\draw (2.5,-1.5) circle (0.9) node {$U_{2,1}$};
-%\draw (2.9, -2.1) circle (1.1) node {$U_{2,2}$};
-\end{tikzpicture}
-\end{center}
-}
- \end{minipage}
- \hspace{1.3cm} $\rightsquigarrow$ \hspace{-0.1cm}
-\begin{minipage}{8cm}
-\begin{tikzcd}[column sep=small]
-\cF(U_{1,1}) \otimes \cF(U_{1,2}) \otimes \cF(U_{2,1}) \arrow{dr} \arrow{r}  & \cF(V_1) \otimes \cF(V_2) \arrow{d}\\
-&\cF(W) 
-\end{tikzcd}
-\end{minipage}
-
-The case of $k=n_1=2$, $n_2 = 1$.
-\end{center}
-
-This definition bears analogies to familiar objects in mathematics.
-On the one hand, $\cF$ resembles a {\em precosheaf}, which is a functor from opens in $M$ to a category like ${\rm Vect}$ or ${\rm dgVect}$.
-(A presheaf is a functor out of the opposite category to opens in $M$.) 
-Here, however, $\cF$ also assign values to disjoint unions of opens, and it uses the tensor product rather than direct sum.
-This feature leads to the other analogy: $\cF$ resembles an algebra, as
-the multilinear maps look like multiplications.
-These maps let us multiply elements from disjoint regions to get an element in a larger region.
-
-Note that these axioms imply that $\cF(\emptyset)$ is a commutative algebra. 
-We say that $\cF$ is a \emph{unital} prefactorization algebra  if $\cF(\emptyset)$ is a unital commutative algebra.
-In this case, $\cF(U)$ is a pointed cochain complex by the image of the unit $1 \in \cF(\emptyset)$ under the structure map $\cF(\emptyset) \to \cF(U)$.
-In practice, for our examples, $\cF(\emptyset)$ is $\CC$, $\RR$, $\CC[[\hbar]]$, or $\RR[[\hbar]]$.
-
-\begin{eg}\label{ex:associativealgebra}
-The crucial example to bear in mind is an associative algebra.
-Every associative algebra $A$ defines a prefactorization algebra $\cF_A$ on $\RR$, as follows.
-To each open interval $(a,b)$, we set $\cF_A( (a,b) ) = A$.
-To any open set $U = \coprod_j I_j$, where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$.
-The structure maps simply arise from the multiplication map for $A$.
-Figure ~\ref{fig:assasfact} displays the structure of $\cF_A$.
-Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra.
-%(One takes an infinite tensor products of unital algebras, as follows.
-Given an infinite set $I$, consider the poset of finite subsets of $I$, ordered by inclusion.
-For each finite subset $J \subset I$, we can take the tensor product $A^J = \bigotimes_{j \in J} A$.
-For $J \hookrightarrow J'$, we define a map $A^J \to A^{J'}$ by tensoring with the identity $1 \in A$ for every $j \in J' \backslash J$.
-Then $A^I$ is the colimit over this poset.)
-~\hfill$\Diamond$
-\end{eg}
-
-%\begin{figure}
-%\begin{center}
-% \begin{minipage}{3cm}
-% \begin{tikzpicture}[scale=0.75]
-% \begin{scope}[line cap=round,ultra thick]
-% \draw (-2.5,0) -- (-1.5,0); 
-% \draw (-1,0) -- (-0.5,0); 
-% \draw (1,0) -- (2,0); 
-% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
-% \draw (-2.75,-2) -- (-0.25,-2); 
-% \draw (0.75,-2) -- (2.5,-2);  
-% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
-% \draw (-3,-4) -- (3,-4); 
-% \end{scope}
-% \end{tikzpicture}
-% \end{minipage}
-%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
-% \begin{minipage}{8cm}
-% \begin{tikzcd}[cramped,column sep=tiny]
-%a \otimes b \otimes c \arrow[mapsto]{d} & \in & A \otimes A \otimes A \arrow{d} \\
-%ab \otimes c \arrow[mapsto]{d} & \in & A \otimes A \arrow{d} \\
-%abc  & \in &A 
-%\end{tikzcd}
-%\end{minipage}
-%\end{center}
-
-\begin{figure}
-\begin{center}
- \begin{tikzpicture} 
- \begin{scope}[line cap=round,ultra thick]
- \draw (-2.5,1) -- (-1.5,1); 
- \draw (-1,1) -- (-0.5,1); 
- \draw (1,1) -- (2,1); 
- \draw[->,semithick] (0,0.75) -- (0,0.25);
- \draw (-2.75,-0.1) -- (-0.25,-0.1); 
- \draw (0.75,-0.1) -- (2.5,-0.1);  
- \draw[->,semithick] (0,-0.35) -- (0,-0.85);
- \draw (-3,-1.2) -- (3,-1.2); 
- \end{scope}
-
-\node at (4,0) {$\rightsquigarrow$ };
-
-\node at (7,0){
-\begin{tikzcd}[cramped,column sep=tiny]
-a \otimes b \otimes c \arrow[mapsto]{d} & \in & A \otimes A \otimes A \arrow{d} \\
-ab \otimes c \arrow[mapsto]{d} & \in & A \otimes A \arrow{d} \\
-abc  & \in &A 
-\end{tikzcd}
-};
-\end{tikzpicture}
-\end{center}
-\caption{The prefactorization algebra $\cF_A$ of an associative algebra $A$}
-\label{fig:assasfact}
-\end{figure}
-
-\begin{eg}\label{ex:SymOfCosheaf}
-Another important example for us is the symmetric algebra of a precosheaf. 
-Let $F$ be a precosheaf of vector spaces on a space $X$. 
-For example, consider $F = C^\infty_c$ the compactly supported smooth functions on a manifold.
-The functor $\cF  = \Sym F: U \mapsto \Sym(F(U))$ defines a precosheaf of commutative algebras, but it also a prefactorization algebra.
-For instance, if $U$ and $V$ are disjoint opens, we see that
-\begin{align*}
-\cF(U \sqcup V) = \Sym F(U \sqcup V) & \cong \Sym (F(U) \oplus F(V)) \\ & \cong \Sym(F(U)) \otimes \Sym(F(V)) = \cF(U) \otimes \cF(V),
-\end{align*}
-and these isomorphisms provide the structure maps for $\cF$.~\hfill$\Diamond$
-\end{eg}
-
-We will now sketch another way of phrasing this idea, but the reader who is content with this definition and eager to see examples should feel free to jump ahead, referring back as needed.
-
-\subsection{Prefactorization algebras as algebras over an operad}
-\label{sec:disj}
-
-The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
-A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
-See \owen{add citations}
-
-\begin{dfn}
-Let $\Disj_M$ denote the following colored operad associated to~$M$: 
-\begin{itemize}
-\item The colors (or objects) consist of all open subsets of $M$. 
-\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$.
-If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point.
-Otherwise, the set of maps is empty.
-\item The composition of maps is defined in the obvious way. 
-\end{itemize}
-\end{dfn}
-
-\begin{dfn}
-Let $\mc{C}$ be a colored operad. 
-A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
-\end{dfn}
-
-In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
-Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories.
-
-\begin{rmk} 
-If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
-Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
-~\hfill$\Diamond$ 
-\end{rmk}
-
-Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$.
-
-\begin{dfn}
-We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
-\end{dfn}
-
-\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
-\label{AssAsFact}
-
-We explained above how an associative algebra provides a prefactorization algebra on the real line.
-There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras.
-Here we will characterize those that do arise from associative algebras.
-
-\begin{dfn}
-Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
-We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
-\end{dfn}
-
-It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.
-
-\begin{lem}\label{locally_constant_is_associative}
-Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
-Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
-\end{lem}
-
-One can got further, however, and also capture modules, essentially by marking the line with points.
-For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.
-
-Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$.
-We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure.
-
-Pick a point $p \in \RR$.
-On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$.
-Likewise, on the half-line $\{x \in \RR \mid p < x\}$, $\cF_M$ is given by $\cF_B$.
-Intervals containing $p$ are determined, though, by $M$.
-When we consider an interval $I = (t_0,t_1)$ such that $t_0 < p < t_1$, we set $\cF_M(I)  = M$.
-The structure maps are also determined by the bimodule structure.
-For example, given
-\[
-s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
-\]
-we have
-\begin{align*}
-\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
-&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
-&= A \ot M \ot B
-\end{align*}
-and the inclusion of these three intervals into $(s_0,u_1)$ is the map
-\[
-\begin{array}{ccc}
-\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
-a \ot m \ot b & \mapsto & amb
-\end{array}.
-\]
-The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.
-
-%\begin{figure}
-%\begin{center}
-% \begin{minipage}{3cm}
-% \begin{tikzpicture}[scale=0.75]
-% \begin{scope}[line cap=round,ultra thick]
-% \draw (-2.5,0) -- (-1.5,0); 
-% \draw (-1,0) -- (0.5,0); 
-% \draw[fill=black] (0,0) circle (0.07);
-% \draw (1.5,0) -- (2.5,0); 
-% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
-% \draw (-2.75,-2) -- (0.75,-2); 
-% \draw[fill=black] (0,-2) circle (0.07);
-% \draw (1.25,-2) -- (2.75,-2);  
-% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
-% \draw (-3,-4) -- (3,-4);
-% \draw[fill=black] (0,-4) circle (0.07); 
-% \end{scope}
-% \end{tikzpicture}
-% \end{minipage}
-%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
-% \begin{minipage}{8cm}
-% \begin{tikzcd}[cramped,column sep=tiny]
-%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
-%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
-%amb  & \in &M 
-%\end{tikzcd}
-%\end{minipage}
-%\end{center}
-%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
-%\label{fig:bimodasfact}
-%\end{figure}
-
-\begin{figure}
-\begin{center}
- \begin{tikzpicture}
- \begin{scope}[line cap=round,ultra thick]
- \draw (-2.5,1) -- (-1.5,1); 
- \draw (-1,1) -- (0.5,1); 
- \draw[fill=black] (0,1) circle (0.07);
- \draw (1.5,1) -- (2.5,1); 
- \draw[->,semithick] (0,0.75) -- (0,0.25);
- \draw (-2.75,-0.1) -- (0.75,-0.1); 
- \draw[fill=black] (0,-0.1) circle (0.07);
- \draw (1.25,-0.1) -- (2.75,-0.1);  
- \draw[->,semithick] (0,-0.35) -- (0,-0.85);
- \draw (-3,-1.2) -- (3,-1.2);
- \draw[fill=black] (0,-1.2) circle (0.07); 
- \end{scope}
-
-\node at (4,0){$\rightsquigarrow$};
-
-\node at (7,0) {
-\begin{tikzcd}[cramped,column sep=tiny]
-a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
-am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
-amb  & \in &M 
-\end{tikzcd}
-};
-
-\end{tikzpicture}
-\end{center}
-\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
-\label{fig:bimodasfact}
-\end{figure}
-
-\subsection{Factorization algebras}
-
-We are now in a position to define factorization algebras,
-which are prefactorization algebras whose behavior on large open sets is determined by their behavior on small open sets.
-To give a precise description, we introduce a Grothendieck topology due to Michael Weiss~\owen{cite  \cite{Weiss} and it is explained nicely and further developed in \cite{BoavidaWeiss}}.
-
-\begin{dfn}
-Let $U$ be an open set.
-A collection of open sets $\mathfrak{U} = \{ U_i \mid i \in I\}$ is a {\em Weiss cover} of $U$ if for any finite collection of points $\{x_1,\ldots,x_k\}$ in $U$, there is an open set $U_i \in \mathfrak{U}$ such that $\{x_1,\ldots,x_k\} \subset U_i$.
-\end{dfn}
-
-The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$.
-
-\begin{rmk}
-A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens.
-It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$.
-For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection
-\[
-\{ U_i^n \mid i \in I\}
-\]
-provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
-\end{rmk}
-
-\begin{eg}\label{WeissAsExponential}
-For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$.
-One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disk.
-Alternatively, the collection of opens $\{ M \setminus q \mcol q \in M\}$ is a Weiss cover of $M$.
-One can also produce a Weiss cover of a manifold with countably many elements.
-Fix a Riemannian metric on $M$.
-Pick a collection of points $\{q_n\in M \mcol n \in \NN\}$ such that the union of the unit ``discs'' $D_1(q_n) = \{ q \in M \mcol \d(q_n,q) < 1\}$ covers $M$.
-(Such an open may not be homeomorphic to a disc if the injectivity radius of $q_n$ is less than 1.)  Consider the collection of all ``discs'' $\fD = \{ D_{1/m}(q_n) \mcol m \in \NN, n \in \NN\}$.
-The collection of all finite, pairwise disjoint union of elements of $\fD$ is a countable Weiss cover.~\hfill $\Diamond$
-\end{eg}
-
-Now that we have a notion of cover, we can formulate the local-to-global property for factorization algebras,
-which amounts to being a cosheaf for the Weiss topology.
-For concreteness' sake, we will continue to have our prefactorization algebras take values in ${\rm dgVect}$,
-but it is straightforward to generalize by allowing the values to live in, say, a symmetric monoidal $\infty$-category.
-
-Let us provide the definition of a homotopy cosheaf. 
-Let $\Phi$ be a precosheaf on $M$ with values in cochain complexes.
-Let $\mathfrak{U} = \{U_i \mid i \in I\}$ be a cover of some open subset $U$ of $M$.
-Consider the cochain complex with values in cochain complexes whose $-k$th term is
-\[
-\bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}),
-\]
-and note that this term has an ``internal'' differential arising from $\Phi$.
-The ``external'' differential is the alternating sum of the structure maps arising from inclusion of $k+1$-fold intersections into $k$-fold intersections.
-The \emph{\v{C}ech complex of $\mathfrak{U}$ with coefficients in $\Phi$} is the totalization of this double complex:
-$$
-\check{C}(\mathfrak{U}, \Phi) = \bigoplus_{k=0}^\infty \left( \bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}) [ k]   \right).
-$$
-There is a natural map from the $0$th term (of the double complex) to $\Phi(U)$ given by the sum of the structure maps $\Phi(U_i) \to \Phi(U)$.
-Thus, the \v{C}ech complex possesses a natural map to $\Phi(U)$.
-We say that $\Phi$ is a \emph{homotopy cosheaf} if the natural map from the \v{C}ech complex to $\Phi(U)$ is a quasi-isomorphism for every open $U \subset M$ and every open cover of $U$.
-This \v{C}ech complex is simply the dual of the \v{C}ech complex for sheaves of cochain complexes.
-In more sophisticated language, the \v{C}ech complex describes the homotopy colimit of $\Phi$ on this simplicial diagram.
-
-We can now define our main object of interest.
-
-\begin{dfn}
-A \emph{factorization algebra} is a prefactorization algebra $\cF$ on $M$ valued in $\Ch$ \owen{change to dgVect?}, with the property that for every open set $U \subset X$ and Weiss cover $\mathfrak{U}$ of $U$, the natural map
-$$
-\check{C}(\mathfrak{U},\cF) \to \cF(U)
-$$
-is a quasi-isomorphism. That is, $\cF$ is a homotopy cosheaf with respect to the Weiss topology.
-\end{dfn}
-
-We also formulate a multiplicativity condition, as follows.
-
-\begin{dfn}
-A factorization algebra $\cF$ is \emph{multiplicative} if for every pair $U,V$ of disjoint open subsets of $M$, the structure map
-$$
-\cF(U) \otimes \cF(V) \to \cF(U \sqcup V) 
-$$
-is a quasi-isomorphism.
-\end{dfn}
-
-As verification that this notion has some real content, let's consider a first, interesting case.
-We already explained how to produce a locally constant prefactorization algebra $\cF_A$ on $\RR$ from a dg associative algebra $A$.
-We could ask about working on the circle $S^1$ instead of $\RR$.
-This construction tells us what to assign to every proper open subset of $S^1$: for instance, to each open interval, we assign $A$.
-The \v{C}ech complex should then tell us what to assign to the whole circle.
-Remarkably, this construction recovers a well-known invariant: the Hochschild chains ${\rm Hoch}_*(A)$ of~$A$.
-
-\begin{thm}[\owen{citations}]
-The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
-\[
-{\rm Hoch}_*(A) \simeq \check{C}(\mathfrak{U},\cF_A)
-\]
-for any Weiss cover of~$S^1$.
-\end{thm}
-
-The reader can check by hand that for an ordinary algebra $A$, the value on the circle is $A/[A,A] = {\rm HH}_0(A)$.
-This theorem tells us that factorization homology can be seen as a generalization of Hochschild homology,
-where one simultaneously generalizes the circle to an arbitrary closed manifold and an algebra to a factorization algebra.
-
-It can be hard to check whether a given $\cF$ is a homotopy cosheaf, since computing the \v{C}ech complex is typically difficult.
-There are some useful abstract results, such as the fact that a factorization algebra is determined by its behavior on a basis for the Weiss topology.
-But there is also a rich source of examples in differential geometry, and hence from physics.
-
-Given a vector bundle $E \to M$ (possibly a graded vector bundle), 
-let $E^{\boxtimes m} \to M^m$ denote the external product of $E$ with itself $m$ times.
-Let $\cE_c(U)$ denote compactly supported sections of $E$ over $U$, 
-and similarly let $\cE^{\boxtimes m}_c(U^m)$ denote compactly supported sections of $E^{\boxtimes m}$ over $U^m$.
-Let $\Sym^m(\cE_c)(U)$ denote the sections that are invariant under the action of the symmetric group $S_m$ on~$U^m$.
-We define a functor $\Sym(\cE_c): \Open(M) \to \Vect$ by
-\[
-\Sym(\cE_c)(U) = \bigoplus_m \Sym^m(\cE_c)(U),
-\]
-which is a kind of symmetric algebra on $\cE_c(U)$.
-(Those familiar with functional analysis will note that taking sections of the product bundles is a nice way of completing the algebraic tensor product of sections on each component bundle.)
-This construction is actually a cosheaf for the Weiss topology, just as $\cE_c$ is a cosheaf for the ordinary topology;
-in this sense, the Weiss topology is an ``exponentiation'' of the ordinary topology just as $\Sym(V)$ is an ``exponentiation'' of a vector space~$V$.
-We have seen in Example~\ref{ex:SymOfCosheaf} how $\Sym(\cE_c)$ determines a prefactorization algebra,
-so the following theorem should be plausible.
-
-\begin{thm}[\owen{cite book}]
-For $E \to M$ a graded vector bundle, the functor $\Sym(\cE_c)$ encodes a factorization algebra on $M$.
-If we equip $\cE_c$ with a differential operator $d$ of degree 1 suc that $d^2 = 0$ so that $(\cE_c, d)$ is a cosheaf of differential complexes,
-then $(\Sym(\cE_c), d)$ is a factorization algebra, where $d$ denotes the natural extension.
-\end{thm}
-
-Two examples of differential complexes play a key role in applications: 
-\begin{itemize}
-\item the de Rham complex $(\Omega^*, d)$ on a smooth manifold, which is relevant for topological field theories, and 
-\item the Dolbeault complex $(\Omega^{0,*}, \dbar)$ on a complex manifold, which is relevant for holomorphic field theories.
-\end{itemize}
-One can take, of course, these complexes with sections in a flat vector bundle (for the de Rham case) or a holomorphic vector bundle (for the Dolbeault case).
-
-\subsection{Algebras over the little disks operad}
-
-Associative algebras are familiar to every mathematician, but as we have just seen, they reflect and encode one-dimensional geometry.
-It is then natural to ask about higher-dimensional versions of algebra.
-Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-disks operad,
-which we now describe and relate to prefactorization algebras on~$\RR^n$.
-In relation to the subject of this paper, we mention that $E_n$ algebras arise naturally from $n$-dimensional topological field theories;
-we will soon introduce a holomorphic analog of $E_n$ algebras relevant to holomorphic field theories,
-modeled on the discussion here.
-
-Fix a dimension $n$. 
-Let $D^n(x,r)$ denote the open disk of radius $r$ centered at $x \in \RR^n$,
-and let $D^n$ denote the unit disk~$D^n(0,1)$.
-
-\begin{dfn}
-Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint disks:
-\[
-E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the disks $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disk $D^n$\end{tabular}}\right\}.
-\]
-\end{dfn}
-
-When $n = 1$, the operad encodes the idea of associative multiplication:
-we get pictures much like those we drew earlier with intervals, 
-except that now we can slide and stretch the intervals because we have a space of operations.
-More accurately, $E_1$ is a model for associative algebras up to homotopy; 
-it is closely related to the $A_\infty$ operad. \owen{Let me check how people compare these.}
-
-For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
-If one fixes a direction, such as a coordinate axis, and works with disks lined up in this direction,
-one sees an $E_1$ structure.
-
-\owen{Add picture? We drew 2d pictures earlier.}
-
-An algebra over this operad is called an $E_n$-algebra.
-A classic example from topology is given by taking the $n$-fold based loop space
-\[
-\Omega^n_x(X) = \{ \gamma: \overline{D^n} \to X \mcol \gamma(\partial \overline{D^n}) = x\}
-\]
-of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disk.
-Maps that send the boundary of a disk to the base point can be extended naturally to bigger disks: just send the rest of the big disk to the basepoint.
-\owen{Should I spell out the structure of the algebra?}
-Examples include \owen{What to mention?}
-
-Factorization algebras on $\RR^n$ and $E_n$ algebras should be closely related,
-as can be seen by drawing pictures of the configurations of disks that control operations.
-
-\begin{dfn}
-A factorization algebra $\cF$ on an $n$-manifold $M$ is \emph{locally constant} if for each inclusion of open disks $D \subset D'$, then the map $\cF(D) \to \cF(D')$ is a quasi-isomorphism.
-\end{dfn}
-
-For $M = \RR$, we have already discussed how locally constant factorization algebras relate to associative algebras, starting with Example~\ref{ex:associativealgebra}.
-Lurie has shown the following vast extension of this example. (See section 5.4.5 of \cite{LurieHA}, particularly Theorem 5.4.5.9.)
-
-\begin{thm}\label{thm:locisen}
-There is an equivalence of $(\infty,1)$-categories between $E_n$ algebras and locally constant factorization algebras on~$\RR^n$.  
-\end{thm}
-
-We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do.
-A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}.
-We emphasize that higher categories are necessary for a rigorous development of these constructions and comparisons, although we will not emphasize that point in our discussion below, which is expository in nature.
-
-\begin{rmk}
-This theorem, together with our work in these two books, builds an explicit bridge between topology and physics.
-Topological field theories in the physicist's sense, such as perturbative Chern-Simons theory, produce locally constant factorization algebras, which can then be viewed as $E_n$ algebras and analyzed using the powerful machinery of modern homotopy theory.
-Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology.
-Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.~\hfill $\Diamond$
-\end{rmk}
-
-\begin{rmk}
-We have shown how thinking about prefactorization algebras on a real line ``decorated'' with points (i.e., with a kind of stratification) reflects familiar algebraic objects like bimodules.
-By moving into higher dimensions and allowing more interesting submanifolds and stratifications, one generalizes this familiar algebra into new, largely-unexplored directions.
-See \cite{AyalaFrancisTanaka} for an extensive development of these ideas in the setting of locally constant factorization algebras.
-~\hfill $\Diamond$
-\end{rmk}
-
-\subsection{How factorization algebras appear in QFT}
-
-In \cite{CG1, CG2} a systematic relationship is provided between field theories and factorization algebras.
-The slogan is 
-\begin{quote}
-the observables of a field theory living on a manifold $M$ form a factorization algebra on~$M$. 
-\end{quote}
-To make a mathematical statement, one needs to be precise about what a field theory is.
-From hereon, whenever we speak of a classical or quantum field theory, we will mean the definitions articulated in \cite{CosBook,CG1, CG2}, which encompass the Euclidean versions of many field theories studied in physics and mathematics.
-Those books use the Batalin-Vilkovisky (BV) formalism for quantization, a homological method generalizing the BRST approach and widely regarded as the most powerful and general way to quantize gauge theories.
-
-\begin{thm}
-\label{main}
-The observables of a classical field theory on $M$ form a factorization algebra $\Obs^{cl}$ that assigns to every open set, a 1-shifted Poisson algebra (i.e., a commutative dg algebra equipped with a Poisson bracket of cohomological degree one).
-A BV quantization of this theory yields a factorization algebra $\Obs^q$ that is a flat deformation of $\Obs^{cl}$ over~$\RR[[\hbar]]$.
-\end{thm}
-
-This theorem provides an elegant interpretation of BV quantization as a kind of deformation quantization.
-In the setting of mechanics (or one-dimensional field theory, since a particle has a worldline), deformation quantization explains the transition from classical to quantum as deforming the observables from a Poisson algebra to an associative algebra.
-This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra.
-
-In \cite{CG1}, there are several examples of this formalism in action:
-\begin{itemize}
-\item Basic examples from quantum mechanics, such as the harmonic oscillator, and it is shown how to recover the Weyl algebra and the Hamiltonians from factorization algebras living on~$\RR$. 
-\item Scalar field theory on $\RR^n$, where it is shown how the usual correlation functions are encoded in the factorization algebra on~$\RR^n$ and how canonical quantization appears via pushforward of factorization algebras.
-\item The free $\beta\gamma$ system on $\CC$---a basic example of a chiral conformal field theory---is constructed and its usual vertex algebra is extracted from the factorization algebra.
-\item Abelian Chern-Simons theory, where it is shown how dimensional reduction along a closed surface $\Sigma$ produces the Weyl algebra on the symplectic vector space $H^1(\Sigma)$ and how line operators form a (very simple!) braided monoidal category.
-\end{itemize}
-These examples, while not complicated, exhibit in detail how factorization algebras provide a bridge from action functionals to algebra in a broad sense.
-
-This formalism has shown its power in a number of nontrivial applications:
-\begin{itemize}
-\item Grady, Li, and Li \cite{GLL} give a direct connection between Fedosov quantization and the factorization algebra of a 1-dimensional field theory.
-%\item Gorbounov, Williams and I \cite{GGW} constructed rigorously a 2-dimensional QFT depending on a Calabi-Yau manifold $X$, known as the curved $\beta\gamma$ system, and showed the factorization algebra recovers the chiral differential operators of~$X$.
-\item Li and Li \cite{LiLi} constructed the topological B-model and show the factorization algebra recovers the expected topological vertex algebra (see \cite{LiVOA} for a deeper treatment).
-\item Costello, Francis, and Gwilliam \cite{CFG} have shown how the factorization algebra of Chern-Simons theory for $\fg$ encodes a quantum group $U_\hbar \fg$ over~$\CC[[\hbar]]$.
-\item Rabinovich \cite{RabAxial} showed how the local index theorem and the axial anomaly are simultaneously captured by quantizing free fermions (associated to Dirac operators).
-Subsequently, he recovered the Quillen determinant line~\cite{RabDet}.
-\item Costello \cite{CosYangian} introduced a 4-dimensional gauge theory whose factorization algebra recovers the Yangian,
-and subsequently gave extensive applications to quantum integrable systems with Witten and Yamazaki \cite{CWY1,CWY2, CY}.
-\end{itemize}
-There are others, connected with central topics such as mirror symmetry and the AdS/CFT correspondence, 
-and we will discuss holomorphic field theories extensively below.
-
-Thanks to the efforts of people who have adopted this BV/factorization framework,
-we now also understand its connection to many important structural aspects of QFT, 
-such as asymptotic freedom \cite{EWY}, current algebras \cite{GWcurr}, the Anderson-Higgs mechanism \cite{EG}, and the CS/WZW correspondence~\cite{GRW, CosDimGai}.
-In each case this enriched mathematical language offers a new and (we would argue) clarifying point of view.
-In turn, physics offers new vistas or rich applications for mathematicians to explore.
+So how do factorization algebras appear in holomorphic field theories?
 
@@
 
+\subsection{Higher Kac-Moody algebras and their free field realizations}
+
+\subsection{Holomorphic $\sigma$-models and higher-dimensional chiral differential operators}
+
+\subsection{Work with Ingmar \owen{not the title}}
+
 \end{document}

### 2021-06-02 algebra.tex
removed dumb titles

--- 2021-06-02 PartIII.tex
@@
 
-\section{Vertex algebras and higher-dimensional analogs \owen{Crappy title}}
-
-So how do factorization algebras appear in holomorphic field theories?
-
-\subsection{Chiral conformal field theories and vertex algebras}
-
-\owen{I want to discuss how VOAs relate to factorization algebras, notably our CDO project, Si's results, and Brueggeman's thesis. We should also gesture at the Beilinson-Drinfeld approach.}
-
-\subsection{Higher Kac-Moody algebras and their free field realizations}
-
-\subsection{Holomorphic $\sigma$-models and higher-dimensional chiral differential operators}
-
-\subsection{Work with Ingmar \owen{not the title}}
-
 \end{document}

### 2021-06-04 PartI.tex
changes

--- 2021-05-26 whatis.tex
@@
 \date{\today}
-\title{What is a holomorphic field theory}
+\title{Part I}
 
@@
 
-\usepackage[upint]{stix}
+%\usepackage[upint]{stix}
 
@@
 %Motivational overview
+
+\section{What is a holomorphic field theory}
 
@@
 The mathematical motivation is simple:
-for most holomorphic classical field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
+for most classical holomorphic field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
 and it is natural to hope that its quantization is equally interesting.
@@
 which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
-As a somewhat mundane example, let $\RR\Hol(X,V)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $V$.
-(For $V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
-One can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
-and this derived moduli space encodes solutions to
-a theory known as the $\beta\gamma$ system with target $V$.
-(The name is silly: it's due to the original notation people used.)
-Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
-
-An essential example for us is ``holomorphic BF theory,''
-which is a gauge theory for holomorphic principal $G$-bundles on a complex manifold $X$.
-From the perspective of derived geometry, its solutions form the derived moduli space~$T^*[-1] \RR\Bun_G(X)$.
+Other classes of examples are afforded by holomorphic variants of familiar AKSZ $\sigma$-models; the relevant moduli space being the derived mapping space between complex manifolds.
 
@@
 which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a Lie supergroup known as a super Poincar\'e group.
-The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
-with larger $\cN$ denoting a bigger supergroup. 
+%The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
+%with larger $\cN$ denoting a bigger supergroup. 
 Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.
-
-For us, the crucial point is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
+The relevance to the models we study is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
 even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
-As an example, $\cN=1$ supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory, namely a holomorphic BF theory.
+As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by $\RR \Bun_G(X)$.
 It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one,
@@
 
+Let us begin with the example of holomorphic Chern--Simons theory, which we have already said describes the moduli space of
+
+Maurer--Cartan elements describe deformations of the trivial holomorphic $G$-bundle. 
+When $X$ is a Calabi--Yai three-fold, and $\fg$ is equipped with an invariant pairing, this formal moduli space has a very special property: it arises from the variational problem of an action functional, namely
+\[
+S = \int_X \Omega \wedge {\rm CS}(A) 
+\]
+where $\Omega$ is the holomorphic volume form and ${\rm CS}(A)$ is the Chern--Simons Lagrangian for the connection $(0,1)$-form $A$.
+
+We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.
+
+\begin{dfn}
+A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is the data:
+\begin{itemize}
+\item A graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$. 
+\item A holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$.
+\end{itemize}
+This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
+\end{dfn}
+
+Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
+If $V$ is a holomorphic dg Lie algebra then $\Omega^{0,\bu}(X, V)$ has the induced structure of a dg Lie algebra. 
+The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms.
+
+Formal moduli spaces arise from the space of Maurer--Cartan elements of a dg Lie algebra.
+In our case, this dg Lie algebra will always be of the form $\Omega^{0,\bu}(X, V)$.
+For example, the Maurer--Cartan elements of the dg Lie algebra $\Omega^{0,\bu}(X, \fg)$ recovers formal deformations of the trivial holomorphic $G$-bundle.  
+This arises from the holomorphic Lie algebra on $X$ whose underlying vector bundle is trivial with fiber $\fg$.
+
+As another example, consider the holomorphic tangent bundle $V = \T_X$. 
+The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
+A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
+\[
+\dbar \mu + \frac12 [\mu,\mu] = 0 .
+\]
+This recovers the classical picture describing formal deformations of complex structures on~$X$.
+
 %this section aimed at mathematicians
@@
 
-Every supersymmetric field theory produces HFTs through a process called {\em twisting},
-so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.
-As we will explain later, many interesting phenomena for supersymmetric theories have analogs for HFTs.
+Any even dimensional supersymmetric field theory produces a holomorphic field theory through a process called twisting,
+so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.\footnote{Strictly speaking, this requires the existence of of more than two chiral supercharges.
+So, theories with 2d $\cN = (n,m)$ supersymmetry, $n,m \leq 1$, do not admit holomorphic twists.}
+As we will explain later, many interesting phenomena for supersymmetric theories have analogs in holomorphic field theory.
 
 By definition, a supersymmetric field theory on $\RR^d$ is a theory that is acted upon by a super Poincar\'{e} algebra. 
-In this paper we restrict our attention to Euclidean field theories and work in Riemannian signature,
+We focus on Euclidean field theories and work in Riemannian signature,
 hence for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
-\[
-\mathfrak{so}(d) \ltimes \ft
-\]
+$\mathfrak{so}(d) \ltimes \ft$
 where $\ft$ is the super Lie algebra of {\em supertranslations} whose even part $\ft^0 = \RR^d$ is the Lie algebra of ordinary translations and whose odd part $\ft^1$ is a sum of spin representations.
@@
 Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}.
-These twisted theories are analogs of BF theory and Chern--Simons theory,
-exactly the kinds of theories we have already discussed, so long as one includes purely topological and purely holomorphic theories. 
+These twisted theories are analogs of BF theory and Chern--Simons theory, so long as one includes purely topological and purely holomorphic theories. 
 We will describe a few examples in detail in the BV formalism in Section~\ref{sec:twistedsusybv},
@@
 
+\subsection{More examples of holomorphic field theories}
+
+\begin{itemize}
+\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
+For instance, the closed string field theory of the topological B-model is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
+This theory is defined on any Calabi--Yau manifold. 
+The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.  
+\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
+Often, the theory you start with on the nilpotence variety is holomorphic \cite{SWpure}. 
+\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
+For instance, holomorphic BF theory on twistor space associated to $\RR^4$ is equivalent to a self-dual limit of Yang--Mills theory. 
+\end{itemize}
+
 \end{document}

### 2021-06-04 PartIII.tex
changes

@@
 
+\subsection{Holomorphic factorization algebras}
+
+We restrict ourselves to theories defined on complex affine space.
+Let 
+\beqn\label{eqn:affine}
+\U(n) \ltimes \RR^{2n} \subset {\rm Aff}(\RR^{2n}) .
+\eeqn
+be the unitary affine group. 
+A holomorphic factorization algebra on $\CC^n$ is a factorization algebra with an action by the unitary affine group where the anti-holomorphic translations act trivially (at least up to homotopy).
+
+The (complexified) Lie algebra of \eqref{eqn:affine} is $\mathfrak{gl}(n) \ltimes \CC^{2n}$
+with $\CC^{2n}$ spanned by the holomorphic and anti-holomorphic translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$. 
+A homotopical way to encode holomorphicity is to introduce the {\em dg} Lie algebra $\CC^{n}_{\rm hol}$ which in degree zero is the $2n$-dimensional space spanned by all translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$, and in degree $(-1)$ is an $n$-dimensional space spanned by elements $\{\Bar{\eta}_i\}$.
+The differential is simply $\d \Bar{\eta}_i = \partial_{\zbar_i}$. 
+Its immediate to see that $\CC^n_{\rm hol}$ is quasi-isomorphic to the abelian Lie algebra spanned by the {\em holomorphic} translations $\{\partial_{z_i}\}$.
+
+\begin{dfn}
+An $n$-dimensional {\em holomorphic factorization algebra} is a smoothly~\footnote{\brian{recall smooth}} affine equivariant factorization algebra $\cF$ on $\CC^n$ together with an extension of the complex Lie algebra of infinitesimal symmetries
+to the dg Lie algebra $
+\mathfrak{gl}(n) \ltimes \CC^{n}_{\rm hol}$. 
+\end{dfn}
+
+As an example, consider the `enveloping' type factorization algebra which is built out of the Dolbeault complex on $\CC^n$; it assigns to an open set $U \subset \CC^n$ the cochain complex
+\[
+{\rm Sym} \left(\Omega^{0,\bu}_c(U)\right) .
+\]
+This factorization algebra is clearly affine equivariant. 
+Trivialization for the anti-holomorphic translation $\frac{\partial}{\partial \zbar_i}$ is given by the contraction of a Dolbeault form by the corresponding vector field:
+\beqn\label{eqn:triv}
+\Bar{\eta}_i = \frac{\partial}{\partial \zbar_i} \vee (-).
+\eeqn
+
 \subsection{Chiral conformal field theories and vertex algebras}
@@
 
+\subsection{Holomorphic $\sigma$-models and higher-dimensional chiral differential operators}
+
+From a geometric perspective, holomorphic $\sigma$-models form an extremely natural class of holomorphic field theories defined in arbitrary complex dimensions.
+
+We turn our attention to the holomorphic $\sigma$-model of maps $\CC^n$ to the $(n-1)$-shifted cotangent bundle $\T^*[n-1] Y$ of a complex manifold $X$. 
+Being a holomorphic AKSZ model, this theory a priori depends on the holomorphic volume form on $\CC^n$; but there is a 
+\brian{not sure if this is discussed elsewhere}
+\[
+{\rm Map}(\CC^n, \T^*[n-1] X) \simeq \T^*[-1] {\rm Map}(\CC^n, X) .
+\]
+
 \subsection{Higher Kac-Moody algebras and their free field realizations}
-
-\subsection{Holomorphic $\sigma$-models and higher-dimensional chiral differential operators}
 

### 2021-06-04 intro.tex
rename sections
removed dumb titles

--- 2021-05-26 whatis.tex
@@
 \date{\today}
-\title{What is a holomorphic field theory}
+%\title{Part I}
 
@@
 
-\usepackage[upint]{stix}
+%\usepackage[upint]{stix}
 
 \begin{document}
-\maketitle
+%\maketitle
 

### 2021-06-04 algebra.tex
first subsection about algebra in QM

@@
 
-\title{Part III}
+%\title{Part III}
 
@@
 \begin{document}
-\maketitle
+%\maketitle
+
+\section{Algebras from holomorphic field theories}
+
+In this section we describe  associative algebras and their ``higher'' generalizations, like $A_\infty$ algebras, related to holomorphic field theories,
+following the relationship of associative algebras to quantum mechanics and of vertex algebras to chiral conformal field theory.
+A particular focus is upon higher Kac-Moody algebras \cite{FHK},
+as these offer a tantalizing direction to explore in search of analogs of the rich connections between representation theory, algebraic geometry, and physics familiar to those who have worked with loop groups.
+Later --- and it is a central point of this survey --- we will explain how factorization algebras provide a direct conduit from holomorphic field theories to these algebraic constructions.
+
+\subsection{Algebras in mechanics}
+
+A key feature of quantum mechanics is that the observables (or operators) live in an associative algebra.
+In many cases this associative algebra is a deformation of a commutative algebra, typically arising as functions on a manifold or variety.
+The quintessential example is the Weyl algebra
+\[
+\CC \langle x, p \rangle /(xp - px = i \hbar),
+\] 
+which is generated by observables $x$ (``position'') and $p$ (``momentum'') for a quantum particle moving along a line.
+There is a parameter $\hbar$, which if sent to zero, recovers a commutative algebra $\CC [ x, p ]$ of complex-valued polynomial functions on the cotangent bundle $T^* \RR$ of the real line~$\RR$.
+This example will be a model for much of what we discuss in this paper.
+So far we have ignored a lot of features of quantum mechanics (e.g., $\ast$-structures, Hilbert spaces, unitarity) that are important in physics,
+and we will continue to do so.
+
+There are some features of this example that we would like to foreground. 
+First, the commutative algebra arises as functions on a {\em symplectic} space,
+which is the usual mathematical setting for classical mechanics (aside from more subtle situations that require Poisson geometry).
+Second, the symplectic form $\omega = \d x \wedge \d p$ equips this algebra 
+with a Poisson bracket where $\{ x, p \} = 1$,
+which controls the deformation to the Weyl algebra: following Dirac, we promote the Poisson relation to a commutator relation.
+These two features motivate the deformation quantization problem: 
+given a symplectic (or Poisson) manifold,
+describe deformations of its commutative algebra of functions to an associative algebra with the requirement that, to first order,  the commutator recovers the Poisson bracket.
+Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics (see, e.g., \owen{what?} as a starting place).
+
+Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\owen{ref the general overview}), 
+and it might help the reader to bear in mind a variant of this question:
+given a classical holomorphic field theory, what are the natural deformations of its algebra of functions?
+Many of the results we discuss later can be seen as generalizations of phenomena associated with deformation quantization.
+
+In particular, consider how symmetries appear in mechanics.
+Let $X$ be a symplectic manifold encoding the ``phase space'' of a classical mechanical system,
+and let $\{-,-\}$ denote the Poisson bracket on $C^\infty(X)$.
+If a Lie group $G$ acts on $X$ by symplectomorphisms (i.e., respects the symplectic structure),
+there is a map of Lie algebras $\rho: \fg \to {\rm SympVect}(X)$ so that an ``infinitesimal symmetry'' $x \in \fg$ acts by a symplectic vector field.
+In many cases, such infinitesimal symmetries are realized as observables: 
+there is a map of Lie algebras $H_\rho: \fg \to C^\infty(X)$ such that $\{ H_\rho(x), - \} = \rho(x)$.
+One says that each element $x$ has a Hamiltonian function $H_\rho(x)$ whose associated Hamiltonian vector field is $\rho(X)$.
+Classic examples include the momenta for $T^* \RR^n$ arising from translation and rotational symmetry.
+
+How does this set-up fit into the deformation quantization view?
+First, note that the free commutative algebra $\Sym(\fg)$ has a canonical Poisson bracket by defining $ \{x, y \}   = [x, y]$ for generators $x, y \in \fg$ and extending by the Leibniz rule.
+Hence the Hamiltonian map $H_\rho$ extends to a Poisson map $H_\rho: \Sym(\fg) \to C^\infty(X)$.
+We can then ask: does this map quantize? That is, can we compatibly deform the domain and range of the maps to interesting associative algebras as well as deforming to a map of associative algebras?
+Here it might be useful to recognize that the enveloping algebra $U\fg$ is a natural deformation quantization of $\Sym(\fg)$, thanks to the Poincar\'e-Birkhoff-Witt theorem.
+Thus our question might be reformulated to asking whether there is an associative algebra map $H^q_\rho: U\fg \to C^\infty(X)^q$, where $C^\infty(X)^q$ is a deformation quantization, such that $H^q_\rho$ recovers $H_\rho$ in the classical limit.
+Such a map is sometimes called a {\em quantum moment map},
+as $H_\rho$ is the pullback of (polynomial) functions along a moment map~$\mu_\rho: X \to \fg^*$.
+
+This class of questions appears throughout mathematics,
+and it has played a key role in geometric representation theory and the theory of $D$-modules, where $D$ denotes a ring of differential operators.
+After all, for any manifold $X$, the algebra of differential operators $D_X$ is a natural deformation quantization of functions on $T^* X$.
+Hence, for any $G$-manifold $X$, it is natural to ask whether there is a representation $\fg \to D_X$ deforming the canonical Poisson representation.
+In this spirit, we will search for analogues of the kind of mathematics that has grown out of results by Beilinson-Bernstein \owen{cite}, Kashiwara \owen{cite}, and others.
+
+\subsection{A first step in the holomorphic direction}
+
+\subsection{Algebras in higher dimensions }
 

### 2021-06-04 holfactalg.tex
removed dumb titles

--- 2021-06-02 PartIII.tex
@@
 \begin{document}
-\maketitle
+%\maketitle
 
@@
 
-So how do factorization algebras appear in holomorphic field theories?
+So what role  factorization algebras appear in holomorphic field theories?
+
+\subsection{Holomorphic factorization algebras}
+
+We restrict ourselves to theories defined on complex affine space.
+Let 
+\beqn\label{eqn:affine}
+\U(n) \ltimes \RR^{2n} \subset {\rm Aff}(\RR^{2n}) .
+\eeqn
+be the unitary affine group. 
+A holomorphic factorization algebra on $\CC^n$ is a factorization algebra with an action by the unitary affine group where the anti-holomorphic translations act trivially (at least up to homotopy).
+
+The (complexified) Lie algebra of \eqref{eqn:affine} is $\mathfrak{gl}(n) \ltimes \CC^{2n}$
+with $\CC^{2n}$ spanned by the holomorphic and anti-holomorphic translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$. 
+A homotopical way to encode holomorphicity is to introduce the {\em dg} Lie algebra $\CC^{n}_{\rm hol}$ which in degree zero is the $2n$-dimensional space spanned by all translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$, and in degree $(-1)$ is an $n$-dimensional space spanned by elements $\{\Bar{\eta}_i\}$.
+The differential is simply $\d \Bar{\eta}_i = \partial_{\zbar_i}$. 
+Its immediate to see that $\CC^n_{\rm hol}$ is quasi-isomorphic to the abelian Lie algebra spanned by the {\em holomorphic} translations $\{\partial_{z_i}\}$.
+
+\begin{dfn}
+An $n$-dimensional {\em holomorphic factorization algebra} is a smoothly~\footnote{\brian{recall smooth}} affine equivariant factorization algebra $\cF$ on $\CC^n$ together with an extension of the complex Lie algebra of infinitesimal symmetries
+to the dg Lie algebra $
+\mathfrak{gl}(n) \ltimes \CC^{n}_{\rm hol}$. 
+\end{dfn}
+
+As an example, consider the `enveloping' type factorization algebra which is built out of the Dolbeault complex on $\CC^n$; it assigns to an open set $U \subset \CC^n$ the cochain complex
+\[
+{\rm Sym} \left(\Omega^{0,\bu}_c(U)\right) .
+\]
+This factorization algebra is clearly affine equivariant. 
+Trivialization for the anti-holomorphic translation $\frac{\partial}{\partial \zbar_i}$ is given by the contraction of a Dolbeault form by the corresponding vector field:
+\beqn\label{eqn:triv}
+\Bar{\eta}_i = \frac{\partial}{\partial \zbar_i} \vee (-).
+\eeqn
 

### 2021-06-19 algebra.tex
algebra.tex

@@
 as these offer a tantalizing direction to explore in search of analogs of the rich connections between representation theory, algebraic geometry, and physics familiar to those who have worked with loop groups.
-Later --- and it is a central point of this survey --- we will explain how factorization algebras provide a direct conduit from holomorphic field theories to these algebraic constructions.
+In a later section --- and it is a central point of this survey --- we will explain how factorization algebras provide a direct conduit from holomorphic field theories to these algebraic constructions.
+Throughout this section, we will be a bit cavalier with certain subtleties (e.g., about infinite-dimensional spaces and functions on them), 
+emphasizing concepts and motivations over mathematical precision.
+We will be a bit long-winded in the first two subsections, to provide motivations,
+so that in the final subsection, we can rapidly sketch these higher Kac-Moody and Weyl algebras.
 
@@
 and we will continue to do so.
+Note as well that there are many more observables and we have only discussed subalgebras of all observables (at the classical level, just polynomials in $p$, $q$);
+we will often focus on such tractable subalgebras.
 
@@
 
+What could provide the {\em holomorphic} analog of the story above?
+Let us indicate one possible answer before we motivate it.
+
+Let $V$ be a finite-dimensional complex vector space, equipped with a symplectic pairing $\omega$ that is complex-valued.
+We can view $V$ as $T^* L$ for some Lagrangian vector subspace $L \subset V$, if we wish.
+Then we posit for the relevant phase space, the ``symplectic complex manifold'' $V[z,z^{-1}]$,
+by which we mean the $V$-valued Laurent polynomials in a coordinate $z$ on the punctured plane $\CC^\times = \CC -\{0\}$.
+The space encodes algebraic maps from the variety $\CC^\times$ to $V$,
+so we view it as a kind of algebraic loop space of~$V$.
+(There are clearly variations on this idea, such as the holomorphic loop space of all holomorphic maps from $\CC^\times$ to~$V$.)
+
+Observables for this classical theory then consist of algebraic functions on $V[z,z^{-1}]$, 
+which happens to be a vector space.
+That is, we want to produce a symmetric algebra on the linear dual to this vector space.
+Recall that Laurent series $\CC((z))$ provide a model of the linear dual to Laurent polynomials via the residue pairing: if $p(z) = \sum_{n = -i}^j a_n z^n$ is a Laurent polynomial and $f(z) = \sum_{m = -k}^\infty b_m z^m$ is a Laurent series, then the pairing is
+\[
+(f, p) = \Res_{z=0}(f p) = \sum_{m+n=-1} a_n b_m.
+\]
+Thus $V^* ((z))$, the $V^*$-valued Laurent series, are a linear dual to $V[z,z^{-1}]$ by combining the residue pairing with the evaluation pairing between $V$ and its linear dual~$V^*$.
+The symmetric algebra $\Sym(V^* ((z)))$ thus encodes a class of observables that we will denote $\cO(V[z,z^{-1}])$.
+(Again, there are clearly alternative algebras to consider.)
+When we quantize, this algebra will be related to a well-known vertex algebra.
+
+There is one last feature we would like to point out, before we turn to explaining our interest in this space and algebra.
+The inclusion $\CC^\times \hookrightarrow \CC$ means that any algebraic map  $\phi: \CC \to V$ restricts to an algebraic map $\phi: \CC^\times \to V$.
+In our notation, this restriction map is the inclusion $V[z] \hookrightarrow V[z,z^{-1}]$ of $V$-valued polynomials in $V$-valued Laurent polynomials.
+In terms of observables, there is a quotient map $\cO(V[z,z^{-1}]) \to \cO(V[z])$, since observables on the loop space restrict to observables on~$V[z]$.
+When we quantize, this relationship will produce the underlying vector space (or Fock space, or vacuum module) of the vertex algebra.
+
+Now we will discuss why we might focus on these constructions,
+and in what sense they are holomorphic versions of usual mechanics.
+
+Let us start by offering a motivation for the ``answers'' (e.g., $\RR[q,p]$ as classical observables) in the setting of standard classical mechanics.
+The model problem in mechanics is to describe a point particle moving in $\RR^n$,
+subject to some forces that specify the differential equations governing the particle's motion.
+(We call these the ``equations of motion.'')
+Newton's law says that this equation is second order, so that a solution (i.e., trajectory) is specified by giving the position and velocity of a particle at one instant in time.
+
+There is another view, which generalizes more naturally to field theories and which is dubbed the Lagrangian formalism.
+Here one notes that there is a space of all imaginable trajectories, namely the path space ${\rm Map}(\RR, \RR^n)$, where we view the source $\RR$ as ``time,''
+and there is a subspace of trajectories realized by the particle, namely solutions to the equations of motion.
+This subspace is, in some sense, the critical set of an action functional; 
+the variational calculus provides the relevant mathematical framework.
+The space of solutions is naturally isomorphic to $T \RR^n$,
+where an isomorphism is given by fixing an instant $t_0$ in time $\RR$ and then sending a solution $\phi$ to the pair $(\phi(t_0), \dot{\phi}(t_0))$, the position and velocity of the solution at~$t_0$.
+With a little care, one finds that the variational calculus equips $T \RR^n$ with a natural symplectic form and a symplectomorphism $T\RR^n \cong T^* \RR^n$, with its canonical symplectic form. 
+Putting everything together, we have a natural symplectomorphism of $T^* \RR^n$ with the space of solutions.
+The observables of the classical system are the algebra of functions on the space of solutions,
+and so this isomorphism tells us that functions on $T^* \RR^n$ provide the observables.
+The polynomial functions on $T^* \RR^n$ are a subalgebra of all observables, 
+and they suffice to distinguish distinct solutions.
+
+This view generalizes nicely to the holomorphic setting,
+and it amounts to using the Lagrangian formalism to study the holomorphic field theories we have already introduced.
+In this model case, we replace the path space ${\rm Map}(\RR, \RR^n)$ by ${\rm Map}(\CC^\times, \CC^n)$ or, if one wishes, ${\rm Map}(S, \CC^n)$ with $S$ a Riemann surface.
+We start with $\CC^\times$ since it has a ``time'' direction given by the radial coordinate ($t$ becomes $r = e^t)$),
+letting us view ${\rm Map}(\CC^\times, \CC^n)$ as  ${\rm Map}(\RR, \Map(S^1,\CC^n))$, namely mechanics into the loop space of $\CC^n$.
+We replace Newton's equations of motion with a holomorphic version
+so that the space of solutions is given by holomorphic maps from $\CC^\times$ into $\CC^n$.
+If we wish to focus on a more algebraic version, as we did at the beginning,
+we could restrict to the algebraic maps from $\CC^\times$ into~$\CC^n$,
+which sit inside the holomorphic maps.
+
+A confession is necessary here, because this replacement is a bit misleading.
+The holomorphic version of the model case, known as the free $\beta\gamma$ system,
+actually has holomorphic maps into $T^* \CC^n$ as the space of solutions.
+The algebraic maps are precisely $T^* \CC^n$-valued Laurent polynomials.
+
+We now turn to quantization, and our phase space will be, for simplicity, the algebraic loop space $V[z,z^{-1}]$ of a symplectic complex vector space $V$.
+Following the case of mechanics, we might ask for a deformation of $\cO(V[z,z^{-1}])$ into an associative algebra.
+A subtlety here is that $\cO(V[z,z^{-1}])$ does not possess a Poisson bracket, 
+due to the  infinite-dimensionality of $V[z,z^{-1}]$.
+The naive formulas from functions on a finite-dimensional symplectic vector space only make sense on a subset of observables here.
+One workaround is to replace $V[z,z^{-1}]$ with $V((z))$, the $V$-valued Laurent series,
+which we view as ``formal loops in $V$.''
+There is manifestly an inclusion $V[z,z^{-1}] \hookrightarrow V((z))$ and hence an algebra map $\cO(V((z))) \to \cO(V[z,z^{-1}])$
+where 
+\[
+\cO(V((z))) = \Sym(V^* [z,z^{-1}]).
+\]
+On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\omega^* \otimes \Res$ on $V^* [z,z^{-1}]$.
+Hence for $\cO(V((z)))$, we can ask for a deformation quantization,
+and there is a nice answer: 
+the Heisenberg commutation relations determine a Weyl algebra $W_{V}$ for this formal loop space.
+As a vector space $W_V$ is isomorphic to $\cO(V((z)))$, 
+just as the simplest Weyl algebra is isomorphic to $\CC[p,q]$ as a vector space,
+but the product structure is modified by quantization.
+We expect, by analogy with the simplest case, that any quantization of a bigger algebra (e.g., for observables of the holomorphic loop space) contains this quantization as its algebraic skeleton.
+
+The subspace of ``contractible formal loops" $V[[z]]$ inside $V((z))$ produces a module for $\cO(V((z)))$ given by $\cO(V[[z]]$. 
+(This module is in fact a quotient algebra.)
+One can quantize this module to a module ${\rm Vac}_V$ for $W_V$,
+where as a vector space, it is still $\cO(V[[z]])$.
+This module structure means there is a map of algebras $W_V \to \End({\rm Vac}_V)$,
+so we have a natural ``Hilbert space'' or Fock module for~$W_V$.
+
+It is a remarkable fact, suggested by physicists, that there is also a map
+\[
+Y: {\rm Vac}_V \to \End({\rm Vac}_V)[[z, z^{-1}]],
+\]
+known as the {\em vertex operator} or {\em state-field correspondence},
+which is closely related to the $W_V$-action.
+The intuition behind $Y$ is that for any map $\phi: \CC^\times \to V$ and for any point $w \in \CC^\times$, 
+there is a restriction of $\phi$ to a little disk around $w$.
+That is, there is a restriction map $r_w: V[z,z^{-1}] \to V[[t]]$, where $t$ is the local coordinate $t = z-w$.
+Hence there is a $w$-dependent map $\cO(V[[t]]) \to \cO(V[z,z^{-1}])$ by pulling back a function along $r_w$;
+this map determines a $w$-dependent action of $\cO(V[[t]])$ on $\cO(V[[z]])$.
+One can, in essence, quantize this map, by trying to extend the formulas of the $W_V$-action,
+and this leads to the map~$Y$.
+If one axiomatizes the behavior of $Y$, one is led to the notion of a vertex algebra.
+
+Let us briefly comment on how symmetries extend to the holomorphic setting.
+In other words, we wish to explain how the affine Lie algebras $\widehat{\fg}$ and free field realizations arise in analogy with our discussion of quantum moment maps.
+
+Suppose now that $G$ is a complex Lie group and it acts on the symplectic complex vector space $V$ by holomorphic symplectomorphisms.
+Then $G$ also acts on the algebraic loop space $V[z,z^{-1}]$ as a ``global'' symmetry:
+the action is independent of $z$.
+On the other hand, if we consider the infinitesimal action $\fg \to {\rm SympVect}(V)$,
+there is, in fact, a natural extension to a ``local'' symmetry $\fg[z,z^{-1}] \to {\rm SympVect}(V[z,z^{-1}])$.
+Geometrically, we let a $\fg$-valued function $x(z)$ act pointwise on the algebraic loop space.
+
 \subsection{Algebras in higher dimensions }

### 2021-06-19 algebra.tex
added 1d holomorphic motivation

@@
 Suppose now that $G$ is a complex Lie group and it acts on the symplectic complex vector space $V$ by holomorphic symplectomorphisms.
-Then $G$ also acts on the algebraic loop space $V[z,z^{-1}]$ as a ``global'' symmetry:
+Then $G$ also acts on the algebraic loop space $V[z,z^{-1}]$ and also on formal loops $V((z))$ as a ``global'' symmetry:
 the action is independent of $z$.
 On the other hand, if we consider the infinitesimal action $\fg \to {\rm SympVect}(V)$,
-there is, in fact, a natural extension to a ``local'' symmetry $\fg[z,z^{-1}] \to {\rm SympVect}(V[z,z^{-1}])$.
-Geometrically, we let a $\fg$-valued function $x(z)$ act pointwise on the algebraic loop space.
+there is, in fact, a natural extension to a ``local'' symmetry $\fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
+Geometrically, we let a $\fg$-valued function $x(z)$ act pointwise (on the formal disk) on the formal loop space.
+
+\owen{OK, my plan is to say that there is an obstruction to lifting the moment map to a quantum moment map, leading to the central extension.}
 

### 2021-06-22 algebra.tex
finished 1d holo subsection

@@
 the action is independent of $z$.
-On the other hand, if we consider the infinitesimal action $\fg \to {\rm SympVect}(V)$,
-there is, in fact, a natural extension to a ``local'' symmetry $\fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
-Geometrically, we let a $\fg$-valued function $x(z)$ act pointwise (on the formal disk) on the formal loop space.
+On the other hand, if we consider the infinitesimal action $\rho: \fg \to {\rm SympVect}(V)$,
+there is, in fact, a natural extension to a ``local'' symmetry $\rho^{\rm loc}: \fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
+Geometrically, a $\fg$-valued function $x(z)$ acts pointwise (with respect to the formal disk) on the formal loop space.
+(Although the algebraic loop space is not symplectic in a strict sense,
+there is still a local symmetry as $\fg[z,z^{-1}]$ maps to vector fields on the algebraic loop space.)
+This action factors through a map $H_\rho^{\rm loc}: \fg[z,z^{-1}] \to \cO(V((z)))$,
+and hence is Hamiltonian.
+Thus the loop algebra $\fg[z,z^{-1}]$ arises naturally as symmetries of a classical holomorphic field theory.
 
-\owen{OK, my plan is to say that there is an obstruction to lifting the moment map to a quantum moment map, leading to the central extension.}
+When we try to quantize, we run into an interesting phenomenon:
+the Hamiltonian action $H_\rho^{\rm loc}$ does not extend as a Lie algebra map into the Weyl algebra $W_V$,
+although it makes sense as a linear map.
+The failure to respect the brackets determines, however, a cocycle on the loop algebra
+by
+\[
+\alpha_V( x \otimes f(z) , y \otimes g(z)) = \Tr_V(xy) \Res(f \, \partial_z g).
+\]
+\owen{Check conventions.}
+There is thus a central extension of the loop algebra 
+\[
+\CC c \to \widehat{\fg} \to \fg[z,z^{-1}]
+\]
+with a Lie algebra map
+\[
+\widehat{H}^{\rm loc}_\rho: \widehat{\fg} \to W_V,
+\]
+sometimes called {\em free field realization} of the affine Lie algebra~$\widehat{\fg}$.
+This relationship --- and its extension to a map between the vertex algebras associated to $\widehat{\fg}$ and $V$ --- is a modest \owen{better adjective?} extract of the rich dialogue that has developed between representation theory, the physics of chiral conformal field theory, and the complex geometry of Riemann surfaces.
 

### 2021-06-22 algebra.tex
added FHK stuff

@@
 \def\Vect{\operatorname{Vect}}
+\def\pAA{\mathring{\AA}}
+\def\jou{{\mathtt{j}}}
 
@@
 \]
-with a Lie algebra map
+so that 
+\[
+[x \otimes f, y \otimes g] = [x,y] \otimes fg + \alpha_V( x \otimes f , y \otimes g) c,
+\]
+and there is a Lie algebra map
 \[
@@
 sometimes called {\em free field realization} of the affine Lie algebra~$\widehat{\fg}$.
-This relationship --- and its extension to a map between the vertex algebras associated to $\widehat{\fg}$ and $V$ --- is a modest \owen{better adjective?} extract of the rich dialogue that has developed between representation theory, the physics of chiral conformal field theory, and the complex geometry of Riemann surfaces.
+This relationship --- and its extension to a map between the vertex algebras associated to $\widehat{\fg}$ and $V$ --- is a modest \owen{better adjective?} extract of the rich dialogue that has developed between complex analysis, representation theory, and the physics of chiral conformal field theory.
+(To get Riemann surfaces into the game, we will need a richer framework than ordinary algebra.)
+
+\owen{Discuss modules?}
 
@@
 
+The story we have just told admits a natural extension to higher complex dimensions,
+but it requires a first step in the direction of derived geometry.
+
+Let $V$ denote a complex vector space (no longer required to be symplectic).
+The naive idea is to replace the algebraic loop space $\Map(\CC^\times,  V)$ with a higher-dimensional analog $\Map(\CC^d -\{0\}, V)$.
+If one considers ordinary algebraic or holomorphic maps for $d > 1$, 
+then every such map extends across the origin, by Hartogs' lemma,
+so this seems uninteresting.
+One should notice, however, that punctured affine space $\mathring{\AA}^d = \CC^d -\{0\}$ is, as a scheme, not affine, 
+and so the {\em derived} global sections of the structure sheaf $\cO_{\rm alg}$ are interesting:
+\[
+\RR \Gamma(\pAA^d, \cO_{\rm alg}) = H^* (\mathring{\AA}^d, \cO_{\rm alg}) 
+= \begin{cases} 
+0, & * \neq 0, d-1 \\ 
+\CC[z_1,\ldots,z_d], & * = 0 \\ 
+\CC[z_1^{-1},\ldots,z_d^{-1}] \frac{1}{z_1 \cdots z_d}, & * = d-1 
+\end{cases},
+\]
+where we are providing a natural basis for the cohomology 
+that aims to emphasize analogies with the $d=1$ case.
+When $d=1$, note that this computation recovers the Laurent polynomials,
+so when $d > 1$, 
+we view the cohomology in degree $d-1$ as providing the derived replacement of the polar part of the Laurent polynomials.
+Checking this computation is a straightforward exercise in algebraic geometry;
+for instance, use the cover by the affine opens of the form $\AA^d \setminus \{z_i =0\}$.
+\owen{I want to discuss the module structure on the $d-1$-component.}
+
+A similar result holds in analytic geometry, of course,
+so that we have a natural map
+\[
+\RR \Gamma(\pAA^d, \cO_{\rm alg}) \to \RR \Gamma(\pAA^d, \cO_{\rm an}) \simeq \Omega^{0,*}(\pAA^d)
+\]
+that replaces our inclusion of Laurent polynomials into the Dolbeault complex on~$\pAA^d$.
+
+There is a natural analog of the residue map as well.
+Just as $\CC^\times$ deformation-retracts onto the unit circle,
+the punctured affine space $\pAA^d$ retracts onto the unit sphere $S^{2d-1}$.
+The Bochner-Martinelli kernel 
+\[
+\omega_{BM} = \frac{(d-1)!}{(2 \pi i)^d} \frac{1}{(z\zbar)^d} \sum_{i=1}^d (-1)^{i-1} \zbar_i \d \zbar_1 \wedge \cdots \wedge \Hat{\d \zbar_i} \wedge \cdots \wedge \d \zbar_d
+\]
+determines a cohomology class of degree $d-1$, and we identify it with $1/z_1 \cdots z_d$ in our basis above,
+so that $\omega_{BM}$ generates its cohomology group under multiplication by polynomials in the $z_j^{-1}$.
+When $d = 1$, note that $\omega_{BM} = (1/2\pi i)\d z/z$, the kernel in the Cauchy residue formula.
+It is also quick to check that
+\[
+\omega_{BM} \wedge \d z_1 \wedge \cdots \wedge \d z_d
+\]
+pulls back to a volume form on the unit sphere $S^{2d-1}$.
+Hence, we define a residue map
+\[
+\Res: \RR \Gamma(\pAA^d, \cO_{\rm alg})  \to \CC
+\]
+by
+\[
+\Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d z_1 \wedge \cdots \wedge \d z_d.
+\]
+When $d =1$, this formula reduces to the usual residue map.
+\owen{That's a bit misleading, maybe, but the integral really does only care about the cohomology class.}
+
+The ingredients are thus in place to mimic the construction of the Weyl algebra for the formal loop space, of the affine Lie algebras, and of free field realization, but now with $\pAA^d$ in place of $\pAA^1 = \CC^\times$.
+Reversing our treatment above, we first discuss the higher Kac-Moody algebras, 
+following Faonte-Hennion-Kapranov \cite{FHK},
+before discussing holomorphic field theory.
+
+It is important to have an explicit dg commutative algebra that models the derived global sections,
+and not just the cohomology groups.
+There is a beautiful, explicit dg model $A_d$ for the algebraic version derived global sections due to Faonte-Hennion-Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities.
+In fact, they provide a model $A^{p,*}_d$ for the algebraic $p$-forms as well.
+We will gloss their definition, referring the interested reader to their lucid paper for details.
+
+Let $a_d$ denote the algebra  
+\[
+\CC[z_1,\ldots,z_d, z_1^*,\ldots,z_d^*][(z z^*)^{-1}]
+\]
+defined by localizing the polynomial algebra with respect to $zz^* = \sum_i z_i z^*_i$.
+View this algebra $a_d$ as concentrated in bidegree $(0,0)$.
+Consider the bigraded-commutative algebra $R^{*,*}_d$ over $a_d$ that is freely generated in bidegree $(1,0)$ by elements
+\[
+\d z_1,\ldots , \d z_d,
+\] 
+and in bidegree $(0,1)$ by
+\[
+\d z_1^*,\ldots, \d z_d^*.
+\]
+Note the close resemblance with the Dolbeault complex $\Omega^{*,*}(\CC^d)$ by thinking of $z_j^*$ as $\zbar_j$.
+There is a subalgebra $A^{*,*}_d$ inside $\omega \in R^{p,m}_d$ and a natural pair of differentials $\partial$ and $\dbar$ that behave like the corresponding differentials in the Dolbeault complex.
+We denote the subcomplex with $p=0$~by 
+\[
+(A_d, \dbar) = (\bigoplus_{q = 0}^d A_d^{q}[-q], \dbar),
+\] 
+and it has the structure of a dg commutative algebra.
+For $p>0$, the complex $A^{p,*}_d = (\oplus_q A^{p,q}[-q], \dbar)$ is a dg module for $(A_d, \dbar)$.
+
+The following proposition summarizes key properties of the dg algebra $A_d$ and its dg modules $A_{d}^{p,*}$,
+by aggregating several results of~\cite{FHK}.
+
+\begin{prop}[\cite{FHK}, Section 1]
+\label{prop: Ad} $\;$
+\begin{enumerate}
+\item
+The dg commutative algebra $(A_d,\dbar)$ is a model for $\RR \Gamma(\pAA^d, \sO_{\rm alg})$:
+\[
+A_d \simeq \RR\Gamma(\pAA^{d}, \sO^{alg}) .
+\]
+Similarly, $(A_d^{p,*},\dbar) \simeq \RR \Gamma(\pAA^{d}, \Omega^{p}_{\rm alg})$.
+\item There is a dense map of commutative bigraded algebras
+\[
+\jou : A^{*,*}_d \to \Omega^{*,*}(\CC^d \setminus \{0\}),
+\]
+and the map intertwines with the $\dbar$ and $\partial$ differentials on both sides.
+\item There is a unique $\GL_d$-equivariant residue map
+\[
+{\rm Res}_{z=0} : A_d^{d,d-1} \to \CC
+\]
+such that for any $\omega \in A^{d,d-1}_d$,
+\[
+{\rm Res}_{z=0} (\omega) = \oint_{S^{2d-1}} \jou(\omega)
+\]
+where $S^{2d-1}$ is any sphere centered at the origin in $\CC^d$. 
+\item There is a representative $\omega_{BM}^{\rm alg}$ of the Bochner-Martinelli kernel such that
+\[
+\Res_{z=0} \left(f(z) \omega_{BM}^{alg}(z,z^*) \d z_1 \cdots \d z_d\right) = f(0)
+\]
+for any $f (z) \in \CC[z_1,\ldots,z_d]$. 
+\end{enumerate}
+\end{prop}
+
+We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\pAA^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disk) into $\fg$,
+just as $\fg[z,z^{-1}]$ provides a kind of loop algebra.
+
+\begin{dfn}
+For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$A_d \otimes \fg$.
+Following \cite{FHK} we denote it by~$\fg^\bullet_d$.
+\end{dfn}
+
+There are natural central extensions of this sphere algebra as {\em $L_\infty$ algebras},
+parallel to the affine Lie algebras appearing as central extensions of the loop algebra.
+An $L_\infty$ algebra is a generalization of a Lie algebra;
+it is graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k: L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi condition for a standard Lie algebra.
+For an overview (and actual definition!) we recommend \owen{add citations}.
+
+In our setting of $\fg^\bullet_d$, Faonte-Hennion-Kapranov introduced central extensions that only affect the $d$-bracket.
+For any $\fg$-invariant degree $d+1$ polynomial  $\theta \in \Sym^{d+1}(\fg^*)^\fg$,  the FHK  cocycle is
+\[
+\label{fhk cocycle}
+\begin{array}{cccc}
+\theta_{\rm FHK} : & (A_d \tensor \fg)^{\tensor (d+1)} & \to & \CC\\ 
+& a_0 \otimes \cdots \otimes a_d & \mapsto & \Res_{z=0} \theta(a_0,\partial a_1,\ldots,\partial a_d)
+\end{array}.
+\]
+This cocycle has cohomological degree $2$ and so determines an unshifted central extension as $L_\infty$ algebras
+\[
+\CC c \to \widetilde{\fg}^\bullet_{d, \theta} \to \fg^\bullet_d ,
+\]
+so that the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
+
 \end{document}

### 2022-07-10 2021/algebra.tex
putting old stuff into its own folder

--- 2021-06-22 algebra.tex
@@
 
+\begin{rmk}
+We have only spoken of symplectic manifolds, and emphasized vector spaces,
+but fermions play a crucial role in quantum mechanics too.
+Here the symmetric algebra on a symplectic vector space (as classical observables) 
+is replaced by an exterior algebra on an inner product space,
+which can be seen as a symmetric algebra on an {\em odd} vector space
+(i.e., a super vector space with purely odd component).
+The deformation quantization of the exterior algebra is then a Clifford algebra.
+We will set fermions aside for the remainder of this section,
+but the discussion below extends easily to them and fermions appear naturally in the study of holomorphic field theories.
+\end{rmk}
+
 \subsection{A first step in the holomorphic direction}
@@
 and there is a nice answer: 
-the Heisenberg commutation relations determine a Weyl algebra $W_{V}$ for this formal loop space.
-As a vector space $W_V$ is isomorphic to $\cO(V((z)))$, 
+the Heisenberg commutation relations determine a Weyl algebra $W[V]$ for this formal loop space.
+As a vector space $W[V]$ is isomorphic to $\cO(V((z)))$, 
 just as the simplest Weyl algebra is isomorphic to $\CC[p,q]$ as a vector space,
@@
 (This module is in fact a quotient algebra.)
-One can quantize this module to a module ${\rm Vac}_V$ for $W_V$,
+One can quantize this module to a module ${\rm Vac}[V]$ for $W[V]$,
 where as a vector space, it is still $\cO(V[[z]])$.
-This module structure means there is a map of algebras $W_V \to \End({\rm Vac}_V)$,
-so we have a natural ``Hilbert space'' or Fock module for~$W_V$.
+This module structure means there is a map of algebras $W[V] \to \End({\rm Vac}[V])$,
+so we have a natural ``Hilbert space'' or Fock module for~$W[V]$.
 
@@
 \[
-Y: {\rm Vac}_V \to \End({\rm Vac}_V)[[z, z^{-1}]],
+Y: {\rm Vac}[V] \to \End({\rm Vac}[V])[[z, z^{-1}]],
 \]
 known as the {\em vertex operator} or {\em state-field correspondence},
-which is closely related to the $W_V$-action.
+which is closely related to the $W[V]$-action.
 The intuition behind $Y$ is that for any map $\phi: \CC^\times \to V$ and for any point $w \in \CC^\times$, 
@@
 this map determines a $w$-dependent action of $\cO(V[[t]])$ on $\cO(V[[z]])$.
-One can, in essence, quantize this map, by trying to extend the formulas of the $W_V$-action,
+One can, in essence, quantize this map, by trying to extend the formulas of the $W[V]$-action,
 and this leads to the map~$Y$.
@@
 When we try to quantize, we run into an interesting phenomenon:
-the Hamiltonian action $H_\rho^{\rm loc}$ does not extend as a Lie algebra map into the Weyl algebra $W_V$,
+the Hamiltonian action $H_\rho^{\rm loc}$ does not extend as a Lie algebra map into the Weyl algebra $W[V]$,
 although it makes sense as a linear map.
@@
 \[
-\widehat{H}^{\rm loc}_\rho: \widehat{\fg} \to W_V,
+\widehat{H}^{\rm loc}_\rho: \widehat{\fg} \to W[V],
 \]
@@
 it is graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k: L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi condition for a standard Lie algebra.
-For an overview (and actual definition!) we recommend \owen{add citations}.
+For an overview (and an actual definition!) we recommend \owen{add citations}.
 
@@
 so that the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
+They dubbed these the {\em higher Kac-Moody algebras}, 
+as they specialize to the affine Lie algebras when~$d =1$.
+
+These $L_\infty$ algebras are not just introduced on a whim.
+In \cite{FHK} they are shown to appear naturally in various contexts,
+notably in studying the derived moduli of $G$-bundles on a complex varieties of dimension~$d$.
+\owen{Other applications?}
+
+In addition to the higher Kac-Moody algebras, there are also natural higher analogs of the Weyl algebra of the loop space.
+These appear as the observables for a holomorphic field theory known as a $\beta\gamma$ system.
+
+Let $V$ be a symplectic complex vector space and consider the formal sphere algebra $A^{\wedge}_d \otimes V$,
+where $A^{\wedge}_d$ denotes the completion of $A_d$ (i.e., where polynomials in $z_j$ and $z_j^*$ are replaced by formal power series).
+\owen{Should we introduce a pithy notation?}
+Then there is a dg commutative algebra of functions on this space,
+which we denote $\cO(A^{\wedge}_d \otimes  V)$,
+and it has a kind of Poisson bracket, arising from the residue pairing on $A^{\wedge}_d$ and the symplectic form on $V$,
+just as $\cO(V((z)))$ has a Poisson bracket.
+It will not surprise the reader to learn that there is a natural deformation quantization $W_d[V]$ into a dg Weyl algebra.
+A physicist would interpret this algebra as the canonical and radial quantization of the theory on~$\CC^d - \{0\}$.
+
+If $V$ is a representation of a Lie algebra $\fg$,
+there is a local symmetry 
+\[
+\fg^\bullet_d \to \cO(A^{\wedge}_d \otimes V),
+\]
+just as $\fg[z,z^{-1}]$ acts on $\cO(V((z)))$. 
+One can ask if this action lifts to a quantum symmetry.
+The obstruction is, remarkably, an FHK cocycle:
+\[
+\alpha_{V,d}(x_1 \otimes f_1, \ldots, x_{d+1} \otimes f_{d+1}) = \Tr_V( x_1 \cdots x_{d+1}) \Res(f_1 \partial f_2 \cdots \partial f_{d+1}).
+\]
+\owen{Fix conventions}
+In this sense, the higher Kac-Moody algebras admit a higher free field realization,
+but a richer story is possible once we have a higher version of vertex algebras.
+We will return to this topic once we have the rich language of factorization algebras.
 

### 2022-07-10 draft.tex
putting together our raw ingredients

\documentclass[11pt]{amsart}

\usepackage{macros, setspace}

\spacing{1.25}

\usepackage{parskip}
\setlength{\parindent}{18pt}
\setlength{\parindent}{0cm}

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
%\title{Part I}

\def\g{{\mathfrak g}}
\def\U{{\rm U}}
\def\mc{\mathcal}
\def\mcol{\, | \,}
\def\ot{\otimes}
\def\Disj{\operatorname{Disj}}
\def\Open{\operatorname{Open}}
\def\Vect{\operatorname{Vect}}
\def\pAA{\mathring{\AA}}
\def\jou{{\mathtt{j}}}
\def\bgamma{{\mathbf{\gamma}}}
\def\bbeta{{\mathbf{\beta}}}
\def\CDO{{\cC\cD}}
\def\SU{{\rm SU}}
\def\sfa{\mathsf{a}}

\renewcommand{\op}{\operatorname}

\def\brian#1{{\textcolor{blue!65!red}{BW: {#1}}}}
\def\owen#1{{\textcolor{violet!65!black}{OG: {#1}}}}

%\usepackage[upint]{stix}

\begin{document}
%\maketitle

\owen{Notation to explain: dg = differential graded, PDE = partial differential equations}

\section{What is a holomorphic field theory? Why study them?}

The most important field theories in physics involve a metric on a manifold (whether Riemannian or Lorentzian), and hence geometry has had a clear role in physics.
In recent decades attention has expanded to include {\em topological} field theories (or TFTs), 
in which --- to simplify --- only the underlying smooth topology of the manifold matters.
There are, however, theories that depend on a complex structure on the manifold,
and as one might hope, these are particularly beautiful, 
just as complex variables is a particularly beautiful wing of analysis.
In essence, such {\em holomorphic} field theories have variational PDE (or ``equations of motion'') that are holomorphic:
the PDE only involves derivatives in the holomorphic coordinates (i.e., the $\partial/\partial z_j$) and has holomorphic coefficients.
These theories admit independent motivations from mathematics and physics,
which we sketch before giving more careful definitions.

The mathematical motivation is simple:
for most classical holomorphic field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
and it is natural to hope that its quantization is equally interesting.
A well-known example is holomorphic Chern-Simons theory,
which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
Other classes of examples are afforded by holomorphic variants of familiar AKSZ $\sigma$-models; the relevant moduli space being the derived mapping space between complex manifolds.

A physical motivation comes from supersymmetric field theories, 
which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a Lie supergroup known as a super Poincar\'e group.
%The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
%with larger $\cN$ denoting a bigger supergroup. 
Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.
The relevance to the models we study is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by $\RR \Bun_G(X)$. 
It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one, 
much as TFTs have enriched the understanding of supersymmetric theories.
In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''

As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), holomorphic field theories appear as chiral conformal field theories (CFTs) on 2-dimensional manifolds --- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- and have had a strong impact in mathematics.
It is natural to explore higher-dimensional analogs.

The overarching goal of this paper is \owen{continue}
a cluster of projects is to bring into sharp mathematical form some of the deep insights into gauge theory offered by physics.
So far, most mathematical effort has focused on classical gauge theory,
but the quantum aspects are profoundly interesting.
We expect that these holomorphic examples will be particularly tractable and beautiful but also useful in offering insights even for non-holomorphic theories.

\subsection{Preliminary notions}

%complex geometry, dolbeault, dg stuff.

\subsection{Precise definitions}

Let us begin with the example of holomorphic Chern--Simons theory, 
which we have already said describes the moduli space of Maurer--Cartan elements describe deformations of the trivial holomorphic $G$-bundle. 
When $X$ is a Calabi--Yau three-fold and $\fg$ is equipped with an invariant pairing, 
this formal moduli space has a very special property: 
it arises from the variational problem of an action functional, namely
\[
S = \int_X \Omega \wedge {\rm CS}(A) 
\]
where $\Omega$ is the holomorphic volume form and ${\rm CS}(A)$ is the Chern--Simons Lagrangian for the connection $(0,1)$-form $A$.

We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.

\begin{dfn}
A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is
\begin{itemize}
\item a graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$, and
\item a holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$. 
\end{itemize}
This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
\end{dfn}

Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
If $V$ is a holomorphic dg Lie algebra, 
then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms.

Formal moduli spaces arise from the space of Maurer--Cartan elements of a dg Lie algebra.
In our case, this dg Lie algebra will always be of the form $\Omega^{0,\bu}(X, V)$.
For example, the Maurer--Cartan elements of the dg Lie algebra $\Omega^{0,\bu}(X, \fg)$ recovers formal deformations of the trivial holomorphic $G$-bundle.  
This arises from the holomorphic Lie algebra on $X$ whose underlying vector bundle is trivial with fiber $\fg$.

As another example, consider the holomorphic tangent bundle $V = \T_X$. 
The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
\[
\dbar \mu + \frac12 [\mu,\mu] = 0 .
\]
This recovers the classical picture describing formal deformations of complex structures on~$X$.

%this section aimed at mathematicians
%emphasize connection with (derived) complex geometry

\subsection{Examples from physics}
%this section aimed at physicists
%twists of SUSY theories
%Owen has some nice thoughts about globalization as it related to SUSY/THF.

\owen{Mention main classes of field theories (scalar and sigma models, fermions as matter, gauge theories for ``forces'', gravity, and their combinations) and how there are holomorphic analogs}

\subsection{Examples from supersymmetric field theories}

Any even dimensional supersymmetric field theory produces a holomorphic field theory through a process called twisting,
so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.\footnote{Strictly speaking, this requires the existence of of more than two chiral supercharges. So, theories with 2d $\cN = (n,m)$ supersymmetry, $n,m \leq 1$, do not admit holomorphic twists.}
As we will explain later, many interesting phenomena for supersymmetric theories have analogs in holomorphic field theory.

By definition, a supersymmetric field theory on $\RR^d$ is a theory that is acted upon by a super Poincar\'{e} algebra. 
We focus on Euclidean field theories and work in Riemannian signature,
hence for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
$\mathfrak{so}(d) \ltimes \ft$
where $\ft$ is the super Lie algebra of {\em supertranslations} whose even part $\ft^0 = \RR^d$ is the Lie algebra of ordinary translations and whose odd part $\ft^1$ is a sum of spin representations. 
While the Lie algebra $\RR^d$ of ordinary translations is abelian, the Lie algebra $\ft$ carries a nontrivial (super) Lie bracket,
and this Lie bracket is defined in terms of a $\mathfrak{so}(d)$-equivariant non-degenerate symmetric pairing
\[
\Gamma : {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
\]
by the formula $[Q, Q'] = \Gamma(Q, Q')$.

By a {\em supercharge}, one means an odd supertranslation $Q \in \ft$, and
a {\em twist} is a (nonzero) supercharge $Q$ such that $[Q,Q] = Q^2 = 0$. 
The classification of all twists is a completely algebraic question,
and we refer to~\autocite{ESsusy} for a complete classification of all twists in dimensions from $1$ to~$10$.

If a Lagrangian field theory $\cT$ has $\ft$ as a symmetry, 
then a choice of twist $Q$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^Q$.
If $S$ denotes the action functional of $\cT$, then the action functional $S^Q$ of $\cT^Q$ has the form
\[
S^Q(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(Q \cdot \varphi \right) + \cdots 
\]
where the deformation arises from how $Q$ acts on the theory 
(the $\cdots$ leaves room for terms non-linear in $Q$).
For extensive details on how the twisted theory is defined we refer to~\autocite{CostelloHolomorphic, ESW}.

Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}. 
These twisted theories are analogs of BF theory and Chern--Simons theory, so long as one includes purely topological and purely holomorphic theories. 
We will describe a few examples in detail in the BV formalism in Section~\ref{sec:twistedsusybv},
but we want to indicate now what our main theorem implies about some interesting examples.

For our purposes here, a crucial property of a twist $Q$ is the dimension $k_Q$ of its image ${\rm Im} \; \Gamma(Q, \cdot) \subset \RR^d$,
which we call the number of {\em invariant} directions of~$Q$.
By the non-degeneracy of the pairing $\Gamma$, it follows that $k_Q \geq \frac{d}{2}$.
If the number of invariant directions is maximal with $k_Q = d$, then the twisted theory $\cT^Q$ is purely topological. 
If the number of invariant directions is minimal with $k_Q = \frac{d}{2}$, then the twisted theory $\cT^Q$ is purely holomorphic.

As a representative example of how twisting behaves, 
consider four-dimensional supersymmetric Yang--Mills theory with $\cN=2$ supersymmetry,
which means the odd part $\ft^1$ is eight-dimensional. 
%The sum of two copies of the spin representations.
%\owen{Did I get that right?}
We only consider here the pure gauge theory with Lie algebra~$\fg$. 
Then we have the bounds $2 \leq k_Q \leq 4$, and each value gives a different, well-known field theory:
\begin{itemize}
\item When $k_Q = 4$, the twisted theory is the topological field theory on $\RR^4$ known as {\it Donaldson--Witten theory} \autocite{WittenTQFT};
\item When $k_Q = 3$, the twisted theory is the THFT studied by Kapustin in \autocite{Kapustin};
\item When $k_Q = 2$, the twisted theory is holomorphic BF theory on $\CC^2$ with values in a graded Lie algebra $\fg[\ep]$, where $\ep$ is a parameter of cohomological degree~$1$.
\end{itemize}
We will describe these theories completely later in Section~\ref{sec:twistedsusybv},
but our main theorem implies the following.

\begin{thm}[\owen{cite GRW, maybe also mention our work with Chris?}]
Donaldson--Witten theory, the Kapustin twist, and holomorphic BF theory for $\fg[\epsilon]$ each admit an exact and finite quantization at one loop.
\end{thm}

In other words, by a judicious choice of gauge-fixing, 
we find that the one-loop Feynman diagrams have no UV divergences.
Moreover, no higher loop diagrams appear (for combinatorial reasons),
and the action functional satisfies the quantum master equation.
See Section~\ref{sec: susytwist revisited} for some further discussion.

\subsection{Background}

Although holomorphic field theories had already appeared in practice,
my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
He did the following:
\begin{itemize}
\item gave a precise definition of a holomorphic field theory in the BV formalism,
modeled on and compatible with Costello's approach;
\item established key analytic results about holomorphic renormalization, 
showing that it is highly manageable, with no counterterms to 1-loop; and
\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
\end{itemize}
These apply to all holomorphic theories on $\CC^n$,
but the techniques typically extend to more general complex manifolds.

This foundational work was motivated in large part by our joint effort to generalize to complex $n$-folds results about chiral conformal theories on Riemann surfaces.
A first fruit of our work \cite{GWcurr} is an examination of higher-dimensional {\em current algebras},
which are factorization algebras that generalize the Kac-Moody vertex algebras that play a crucial role in contemporary representation theory.
We show, for instance, that these current algebras arise as the quantization of symmetries of holomorphic field theories, 
much as the affine Lie algebras are symmetries of CFTs on Riemann surfaces.
In addition, we show that encoded in our factorization algebras are the higher Kac-Moody Lie algebras $\widehat{\g}_{d,\theta}$ of Faonte-Hennion-Kapranov~\cite{FHK}. 
It is striking to find this rigid skeleton of algebra under the meat of our analysis,
as our work is strongly differential-geometric in flavor.
Moreover, as their work provides a direct connection with the derived algebraic geometry of $\RR Bun_G(X)$,
there emerges a beautiful generalization of the fertile interactions between algebraic geometry, representation theory, and physics that have grown around bundles on Riemann surfaces.
(The prospect looms that in higher dimensions,
one might find a correspondence between conformal blocks and nonabelian theta functions.)

A second fruit is a collaboration of Williams with the physicist Ingmar Saberi \cite{SabWil1,SabWil2}.
They have carefully worked out the holomorphic twists of several supersymmetric theories
and given a novel approach, via factorization algebras, to the results of Beem et al \cite{Beem}.
Particularly important for this proposal,
they have shown how important invariants (notably the ``supersymmetric index") of the untwisted, supersymmetric theory can be computed simply in the holomorphic twist.

\subsection{More examples of holomorphic field theories}

\begin{itemize}
\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
For instance, the closed string field theory of the topological B-model is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
This theory is defined on any Calabi--Yau manifold. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.  
\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory you start with on the nilpotence variety is holomorphic \cite{SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, holomorphic BF theory on twistor space associated to $\RR^4$ is equivalent to a self-dual limit of Yang--Mills theory. 
\end{itemize}

\section{Algebra and holomorphic field theories}

In this section we describe  associative algebras and their ``higher'' generalizations, like $A_\infty$ algebras, related to holomorphic field theories,
following the relationship of associative algebras to quantum mechanics and of vertex algebras to chiral conformal field theory.
A particular focus is upon higher Kac-Moody algebras \cite{FHK},
as these offer a tantalizing direction to explore in search of analogs of the rich connections between representation theory, algebraic geometry, and physics familiar to those who have worked with loop groups.
In a later section --- and it is a central point of this survey --- we will explain how factorization algebras provide a direct conduit from holomorphic field theories to these algebraic constructions.
Throughout this section, we will be a bit cavalier with certain subtleties (e.g., about infinite-dimensional spaces and functions on them), 
emphasizing concepts and motivations over mathematical precision.
We will be a bit long-winded in the first two subsections, to provide motivations,
so that in the final subsection, we can rapidly sketch these higher Kac-Moody and Weyl algebras.

\subsection{Algebras in mechanics}

A key feature of quantum mechanics is that the observables (or operators) live in an associative algebra.
In many cases this associative algebra is a deformation of a commutative algebra, typically arising as functions on a manifold or variety.
The quintessential example is the Weyl algebra
\[
\CC \langle x, p \rangle /(xp - px = i \hbar),
\] 
which is generated by observables $x$ (``position'') and $p$ (``momentum'') for a quantum particle moving along a line.
There is a parameter $\hbar$, which if sent to zero, recovers a commutative algebra $\CC [ x, p ]$ of complex-valued polynomial functions on the cotangent bundle $T^* \RR$ of the real line~$\RR$.
This example will be a model for much of what we discuss in this paper.
So far we have ignored a lot of features of quantum mechanics (e.g., $\ast$-structures, Hilbert spaces, unitarity) that are important in physics,
and we will continue to do so.
Note as well that there are many more observables and we have only discussed subalgebras of all observables (at the classical level, just polynomials in $p$, $q$);
we will often focus on such tractable subalgebras.

There are some features of this example that we would like to foreground. 
First, the commutative algebra arises as functions on a {\em symplectic} space,
which is the usual mathematical setting for classical mechanics (aside from more subtle situations that require Poisson geometry).
Second, the symplectic form $\omega = \d x \wedge \d p$ equips this algebra 
with a Poisson bracket where $\{ x, p \} = 1$,
which controls the deformation to the Weyl algebra: following Dirac, we promote the Poisson relation to a commutator relation.
These two features motivate the deformation quantization problem: 
given a symplectic (or Poisson) manifold,
describe deformations of its commutative algebra of functions to an associative algebra with the requirement that, to first order,  the commutator recovers the Poisson bracket.
Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics (see, e.g., \owen{what?} as a starting place).

Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\owen{ref the general overview}), 
and it might help the reader to bear in mind a variant of this question:
given a classical holomorphic field theory, what are the natural deformations of its algebra of functions?
Many of the results we discuss later can be seen as generalizations of phenomena associated with deformation quantization.

In particular, consider how symmetries appear in mechanics.
Let $X$ be a symplectic manifold encoding the ``phase space'' of a classical mechanical system,
and let $\{-,-\}$ denote the Poisson bracket on $C^\infty(X)$.
If a Lie group $G$ acts on $X$ by symplectomorphisms (i.e., respects the symplectic structure),
there is a map of Lie algebras $\rho: \fg \to {\rm SympVect}(X)$ so that an ``infinitesimal symmetry'' $x \in \fg$ acts by a symplectic vector field.
In many cases, such infinitesimal symmetries are realized as observables: 
there is a map of Lie algebras $H_\rho: \fg \to C^\infty(X)$ such that $\{ H_\rho(x), - \} = \rho(x)$.
One says that each element $x$ has a Hamiltonian function $H_\rho(x)$ whose associated Hamiltonian vector field is $\rho(X)$.
Classic examples include the momenta for $T^* \RR^n$ arising from translation and rotational symmetry.

How does this set-up fit into the deformation quantization view?
First, note that the free commutative algebra $\Sym(\fg)$ has a canonical Poisson bracket by defining $ \{x, y \}   = [x, y]$ for generators $x, y \in \fg$ and extending by the Leibniz rule.
Hence the Hamiltonian map $H_\rho$ extends to a Poisson map $H_\rho: \Sym(\fg) \to C^\infty(X)$.
We can then ask: does this map quantize? That is, can we compatibly deform the domain and range of the maps to interesting associative algebras as well as deforming to a map of associative algebras?
Here it might be useful to recognize that the enveloping algebra $U\fg$ is a natural deformation quantization of $\Sym(\fg)$, thanks to the Poincar\'e-Birkhoff-Witt theorem.
Thus our question might be reformulated to asking whether there is an associative algebra map $H^q_\rho: U\fg \to C^\infty(X)^q$, where $C^\infty(X)^q$ is a deformation quantization, such that $H^q_\rho$ recovers $H_\rho$ in the classical limit.
Such a map is sometimes called a {\em quantum moment map},
as $H_\rho$ is the pullback of (polynomial) functions along a moment map~$\mu_\rho: X \to \fg^*$.

This class of questions appears throughout mathematics,
and it has played a key role in geometric representation theory and the theory of $D$-modules, where $D$ denotes a ring of differential operators.
After all, for any manifold $X$, the algebra of differential operators $D_X$ is a natural deformation quantization of functions on $T^* X$.
Hence, for any $G$-manifold $X$, it is natural to ask whether there is a representation $\fg \to D_X$ deforming the canonical Poisson representation.
In this spirit, we will search for analogues of the kind of mathematics that has grown out of results by Beilinson-Bernstein \owen{cite}, Kashiwara \owen{cite}, and others.

\begin{rmk}
We have only spoken of symplectic manifolds, and emphasized vector spaces,
but fermions play a crucial role in quantum mechanics too.
Here the symmetric algebra on a symplectic vector space (as classical observables) 
is replaced by an exterior algebra on an inner product space,
which can be seen as a symmetric algebra on an {\em odd} vector space
(i.e., a super vector space with purely odd component).
The deformation quantization of the exterior algebra is then a Clifford algebra.
We will set fermions aside for the remainder of this section,
but the discussion below extends easily to them and fermions appear naturally in the study of holomorphic field theories.
\end{rmk}

\subsection{A first step in the holomorphic direction}

What could provide the {\em holomorphic} analog of the story above?
Let us indicate one possible answer before we motivate it.

\owen{Add pictures!}

Let $V$ be a finite-dimensional complex vector space, equipped with a symplectic pairing $\omega$ that is complex-valued.
We can view $V$ as $T^* L$ for some Lagrangian vector subspace $L \subset V$, if we wish.
Then we posit for the relevant phase space, the ``symplectic complex manifold'' $V[z,z^{-1}]$,
by which we mean the $V$-valued Laurent polynomials in a coordinate $z$ on the punctured plane $\CC^\times = \CC -\{0\}$.
The space encodes algebraic maps from the variety $\CC^\times$ to $V$,
so we view it as a kind of algebraic loop space of~$V$.
(There are clearly variations on this idea, such as the holomorphic loop space of all holomorphic maps from $\CC^\times$ to~$V$.)

Observables for this classical theory then consist of algebraic functions on $V[z,z^{-1}]$, 
which happens to be a vector space.
That is, we want to produce a symmetric algebra on the linear dual to this vector space.
Recall that Laurent series $\CC((z))$ provide a model of the linear dual to Laurent polynomials via the residue pairing: if $p(z) = \sum_{n = -i}^j a_n z^n$ is a Laurent polynomial and $f(z) = \sum_{m = -k}^\infty b_m z^m$ is a Laurent series, then the pairing is
\[
(f, p) = \Res_{z=0}(f p) = \sum_{m+n=-1} a_n b_m.
\]
Thus $V^* ((z))$, the $V^*$-valued Laurent series, are a linear dual to $V[z,z^{-1}]$ by combining the residue pairing with the evaluation pairing between $V$ and its linear dual~$V^*$.
The symmetric algebra $\Sym(V^* ((z)))$ thus encodes a class of observables that we will denote $\cO(V[z,z^{-1}])$.
(Again, there are clearly alternative algebras to consider.)
When we quantize, this algebra will be related to a well-known vertex algebra.

There is one last feature we would like to point out, before we turn to explaining our interest in this space and algebra.
The inclusion $\CC^\times \hookrightarrow \CC$ means that any algebraic map  $\phi: \CC \to V$ restricts to an algebraic map $\phi: \CC^\times \to V$.
In our notation, this restriction map is the inclusion $V[z] \hookrightarrow V[z,z^{-1}]$ of $V$-valued polynomials in $V$-valued Laurent polynomials.
In terms of observables, there is a quotient map $\cO(V[z,z^{-1}]) \to \cO(V[z])$, since observables on the loop space restrict to observables on~$V[z]$.
When we quantize, this relationship will produce the underlying vector space (or Fock space, or vacuum module) of the vertex algebra.

Now we will discuss why we might focus on these constructions,
and in what sense they are holomorphic versions of usual mechanics.

Let us start by offering a motivation for the ``answers'' (e.g., $\RR[q,p]$ as classical observables) in the setting of standard classical mechanics.
The model problem in mechanics is to describe a point particle moving in $\RR^n$,
subject to some forces that specify the differential equations governing the particle's motion.
(We call these the ``equations of motion.'')
Newton's law says that this equation is second order, so that a solution (i.e., trajectory) is specified by giving the position and velocity of a particle at one instant in time.

There is another view, which generalizes more naturally to field theories and which is dubbed the Lagrangian formalism.
Here one notes that there is a space of all imaginable trajectories, namely the path space ${\rm Map}(\RR, \RR^n)$, where we view the source $\RR$ as ``time,''
and there is a subspace of trajectories realized by the particle, namely solutions to the equations of motion.
This subspace is, in some sense, the critical set of an action functional; 
the variational calculus provides the relevant mathematical framework.
The space of solutions is naturally isomorphic to $T \RR^n$,
where an isomorphism is given by fixing an instant $t_0$ in time $\RR$ and then sending a solution $\phi$ to the pair $(\phi(t_0), \dot{\phi}(t_0))$, the position and velocity of the solution at~$t_0$.
With a little care, one finds that the variational calculus equips $T \RR^n$ with a natural symplectic form and a symplectomorphism $T\RR^n \cong T^* \RR^n$, with its canonical symplectic form. 
Putting everything together, we have a natural symplectomorphism of $T^* \RR^n$ with the space of solutions.
The observables of the classical system are the algebra of functions on the space of solutions,
and so this isomorphism tells us that functions on $T^* \RR^n$ provide the observables.
The polynomial functions on $T^* \RR^n$ are a subalgebra of all observables, 
and they suffice to distinguish distinct solutions.

This view generalizes nicely to the holomorphic setting,
and it amounts to using the Lagrangian formalism to study the holomorphic field theories we have already introduced.
In this model case, we replace the path space ${\rm Map}(\RR, \RR^n)$ by ${\rm Map}(\CC^\times, \CC^n)$ or, if one wishes, ${\rm Map}(S, \CC^n)$ with $S$ a Riemann surface.
We start with $\CC^\times$ since it has a ``time'' direction given by the radial coordinate ($t$ becomes $r = e^t)$),
letting us view ${\rm Map}(\CC^\times, \CC^n)$ as  ${\rm Map}(\RR, \Map(S^1,\CC^n))$, namely mechanics into the loop space of $\CC^n$.
We replace Newton's equations of motion with a holomorphic version
so that the space of solutions is given by holomorphic maps from $\CC^\times$ into $\CC^n$.
If we wish to focus on a more algebraic version, as we did at the beginning,
we could restrict to the algebraic maps from $\CC^\times$ into~$\CC^n$,
which sit inside the holomorphic maps.

A confession is necessary here, because this replacement is a bit misleading.
The holomorphic version of the model case, known as the free $\beta\gamma$ system,
actually has holomorphic maps into $T^* \CC^n$ as the space of solutions.
The algebraic maps are precisely $T^* \CC^n$-valued Laurent polynomials.

We now turn to quantization, and our phase space will be, for simplicity, the algebraic loop space $V[z,z^{-1}]$ of a symplectic complex vector space $V$.
Following the case of mechanics, we might ask for a deformation of $\cO(V[z,z^{-1}])$ into an associative algebra.
A subtlety here is that $\cO(V[z,z^{-1}])$ does not possess a Poisson bracket, 
due to the  infinite-dimensionality of $V[z,z^{-1}]$.
The naive formulas from functions on a finite-dimensional symplectic vector space only make sense on a subset of observables here.
One workaround is to replace $V[z,z^{-1}]$ with $V((z))$, the $V$-valued Laurent series,
which we view as ``formal loops in $V$.''
There is manifestly an inclusion $V[z,z^{-1}] \hookrightarrow V((z))$ and hence an algebra map $\cO(V((z))) \to \cO(V[z,z^{-1}])$
where 
\[
\cO(V((z))) = \Sym(V^* [z,z^{-1}]).
\]
On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\omega^* \otimes \Res$ on $V^* [z,z^{-1}]$.
Hence for $\cO(V((z)))$, we can ask for a deformation quantization,
and there is a nice answer: 
the Heisenberg commutation relations determine a Weyl algebra $W[V]$ for this formal loop space.
As a vector space $W[V]$ is isomorphic to $\cO(V((z)))$, 
just as the simplest Weyl algebra is isomorphic to $\CC[p,q]$ as a vector space,
but the product structure is modified by quantization.
We expect, by analogy with the simplest case, that any quantization of a bigger algebra (e.g., for observables of the holomorphic loop space) contains this quantization as its algebraic skeleton.

The subspace of ``contractible formal loops" $V[[z]]$ inside $V((z))$ produces a module for $\cO(V((z)))$ given by $\cO(V[[z]]$. 
(This module is in fact a quotient algebra.)
One can quantize this module to a module ${\rm Vac}[V]$ for $W[V]$,
where as a vector space, it is still $\cO(V[[z]])$.
This module structure means there is a map of algebras $W[V] \to \End({\rm Vac}[V])$,
so we have a natural ``Hilbert space'' or Fock module for~$W[V]$.

It is a remarkable fact, suggested by physicists, that there is also a map
\[
Y: {\rm Vac}[V] \to \End({\rm Vac}[V])[[z, z^{-1}]],
\]
known as the {\em vertex operator} or {\em state-field correspondence},
which is closely related to the $W[V]$-action.
The intuition behind $Y$ is that for any map $\phi: \CC^\times \to V$ and for any point $w \in \CC^\times$, 
there is a restriction of $\phi$ to a little disk around $w$.
That is, there is a restriction map $r_w: V[z,z^{-1}] \to V[[t]]$, where $t$ is the local coordinate $t = z-w$.
Hence there is a $w$-dependent map $\cO(V[[t]]) \to \cO(V[z,z^{-1}])$ by pulling back a function along $r_w$;
this map determines a $w$-dependent action of $\cO(V[[t]])$ on $\cO(V[[z]])$.
One can, in essence, quantize this map, by trying to extend the formulas of the $W[V]$-action,
and this leads to the map~$Y$.
If one axiomatizes the behavior of $Y$, one is led to the notion of a vertex algebra.

Let us briefly comment on how symmetries extend to the holomorphic setting.
In other words, we wish to explain how the affine Lie algebras $\widehat{\fg}$ and free field realizations arise in analogy with our discussion of quantum moment maps.

Suppose now that $G$ is a complex Lie group and it acts on the symplectic complex vector space $V$ by holomorphic symplectomorphisms.
Then $G$ also acts on the algebraic loop space $V[z,z^{-1}]$ and also on formal loops $V((z))$ as a ``global'' symmetry:
the action is independent of $z$.
On the other hand, if we consider the infinitesimal action $\rho: \fg \to {\rm SympVect}(V)$,
there is, in fact, a natural extension to a ``local'' symmetry $\rho^{\rm loc}: \fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
Geometrically, a $\fg$-valued function $x(z)$ acts pointwise (with respect to the formal disk) on the formal loop space.
(Although the algebraic loop space is not symplectic in a strict sense,
there is still a local symmetry as $\fg[z,z^{-1}]$ maps to vector fields on the algebraic loop space.)
This action factors through a map $H_\rho^{\rm loc}: \fg[z,z^{-1}] \to \cO(V((z)))$,
and hence is Hamiltonian.
Thus the loop algebra $\fg[z,z^{-1}]$ arises naturally as symmetries of a classical holomorphic field theory.

When we try to quantize, we run into an interesting phenomenon:
the Hamiltonian action $H_\rho^{\rm loc}$ does not extend as a Lie algebra map into the Weyl algebra $W[V]$,
although it makes sense as a linear map.
The failure to respect the brackets determines, however, a cocycle on the loop algebra
by
\[
\alpha_V( x \otimes f(z) , y \otimes g(z)) = \Tr_V(xy) \Res(f \, \partial_z g).
\]
\owen{Check conventions.}
There is thus a central extension of the loop algebra 
\[
\CC c \to \widehat{\fg} \to \fg[z,z^{-1}]
\]
so that 
\[
[x \otimes f, y \otimes g] = [x,y] \otimes fg + \alpha_V( x \otimes f , y \otimes g) c,
\]
and there is a Lie algebra map
\[
\widehat{H}^{\rm loc}_\rho: \widehat{\fg} \to W[V],
\]
sometimes called {\em free field realization} of the affine Lie algebra~$\widehat{\fg}$.
This relationship --- and its extension to a map between the vertex algebras associated to $\widehat{\fg}$ and $V$ --- is a modest \owen{better adjective?} extract of the rich dialogue that has developed between complex analysis, representation theory, and the physics of chiral conformal field theory.
(To get Riemann surfaces into the game, we will need a richer framework than ordinary algebra.)

\owen{Discuss modules?}

\subsection{Algebras in higher dimensions }

The story we have just told admits a natural extension to higher complex dimensions,
but it requires a first step in the direction of derived geometry.

Let $V$ denote a complex vector space (no longer required to be symplectic).
The naive idea is to replace the algebraic loop space $\Map(\CC^\times,  V)$ with a higher-dimensional analog $\Map(\CC^d -\{0\}, V)$.
If one considers ordinary algebraic or holomorphic maps for $d > 1$, 
then every such map extends across the origin, by Hartogs' lemma,
so this seems uninteresting.
One should notice, however, that punctured affine space $\mathring{\AA}^d = \CC^d -\{0\}$ is, as a scheme, not affine, 
and so the {\em derived} global sections of the structure sheaf $\cO_{\rm alg}$ are interesting:
\[
H^*(\RR \Gamma(\pAA^d, \cO_{\rm alg})) = H^* (\mathring{\AA}^d, \cO_{\rm alg}) 
= \begin{cases} 
0, & * \neq 0, d-1 \\ 
\CC[z_1,\ldots,z_d], & * = 0 \\ 
\CC[z_1^{-1},\ldots,z_d^{-1}] \frac{1}{z_1 \cdots z_d}, & * = d-1 
\end{cases},
\]
where we are providing a natural basis for the cohomology 
that aims to emphasize analogies with the $d=1$ case.
When $d=1$, note that this computation recovers the Laurent polynomials,
so when $d > 1$, 
we view the cohomology in degree $d-1$ as providing the derived replacement of the polar part of the Laurent polynomials.
Checking this computation is a straightforward exercise in algebraic geometry;
for instance, use the cover by the affine opens of the form $\AA^d \setminus \{z_i =0\}$.
\owen{I want to discuss the module structure on the $d-1$-component.}

A similar result holds in analytic geometry, of course,
so that we have a natural map
\[
\RR \Gamma(\pAA^d, \cO_{\rm alg}) \to \RR \Gamma(\pAA^d, \cO_{\rm an}) \simeq \Omega^{0,*}(\pAA^d)
\]
that replaces our inclusion of Laurent polynomials into the Dolbeault complex on~$\pAA^d$.

There is a natural analog of the residue map as well.
Just as $\CC^\times$ deformation-retracts onto the unit circle,
the punctured affine space $\pAA^d$ retracts onto the unit sphere $S^{2d-1}$.
The Bochner-Martinelli kernel 
\[
\omega_{BM} = \frac{(d-1)!}{(2 \pi i)^d} \frac{1}{(z\zbar)^d} \sum_{i=1}^d (-1)^{i-1} \zbar_i\, \d \zbar_1 \wedge \cdots \wedge \Hat{\d \zbar_i} \wedge \cdots \wedge \d \zbar_d
\]
determines a cohomology class of degree $d-1$, and we identify it with $1/z_1 \cdots z_d$ in our basis above,
so that $\omega_{BM}$ generates its cohomology group under multiplication by polynomials in the $z_j^{-1}$.
When $d = 1$, note that $\omega_{BM} = (1/2\pi i)\d z/z$, the kernel in the Cauchy residue formula.
It is also quick to check that
\[
\omega_{BM} \wedge \d z_1 \wedge \cdots \wedge \d z_d
\]
pulls back to a volume form on the unit sphere $S^{2d-1}$.
Hence, we define a residue map
\[
\Res: \RR \Gamma(\pAA^d, \cO_{\rm alg})  \to \CC
\]
by
\[
\Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d z_1 \wedge \cdots \wedge \d z_d.
\]
When $d =1$, this formula reduces to the usual residue map.
\owen{That's a bit misleading, maybe, but the integral really does only care about the cohomology class.}

The ingredients are thus in place to mimic the construction of the Weyl algebra for the formal loop space, of the affine Lie algebras, and of free field realization, but now with $\pAA^d$ in place of $\pAA^1 = \CC^\times$.
Reversing our treatment above, we first discuss the higher Kac-Moody algebras, 
following Faonte-Hennion-Kapranov \cite{FHK},
before discussing holomorphic field theory.

It is important to have an explicit dg commutative algebra that models the derived global sections,
and not just the cohomology groups.
There is a beautiful, explicit dg model $A_d$ for the algebraic version derived global sections due to Faonte-Hennion-Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities. 
In fact, they provide a model $A^{p,*}_d$ for the algebraic $p$-forms as well.
We will gloss their definition, referring the interested reader to their lucid paper for details.

Let $a_d$ denote the algebra  
\[
\CC[z_1,\ldots,z_d, z_1^*,\ldots,z_d^*][(z z^*)^{-1}]
\]
defined by localizing the polynomial algebra with respect to $zz^* = \sum_i z_i z^*_i$.
View this algebra $a_d$ as concentrated in bidegree $(0,0)$.
Consider the bigraded-commutative algebra $R^{*,*}_d$ over $a_d$ that is freely generated in bidegree $(1,0)$ by elements
\[
\d z_1,\ldots , \d z_d,
\] 
and in bidegree $(0,1)$ by
\[
\d z_1^*,\ldots, \d z_d^*.
\]
Note the close resemblance with the Dolbeault complex $\Omega^{*,*}(\CC^d)$ by thinking of $z_j^*$ as $\zbar_j$.
There is a subalgebra $A^{*,*}_d$ inside $\omega \in R^{p,m}_d$ and a natural pair of differentials $\partial$ and $\dbar$ that behave like the corresponding differentials in the Dolbeault complex.
We denote the subcomplex with $p=0$~by 
\[
(A_d, \dbar) = (\bigoplus_{q = 0}^d A_d^{q}[-q], \dbar),
\] 
and it has the structure of a dg commutative algebra.
For $p>0$, the complex $A^{p,*}_d = (\oplus_q A^{p,q}[-q], \dbar)$ is a dg module for $(A_d, \dbar)$.

The following proposition summarizes key properties of the dg algebra $A_d$ and its dg modules $A_{d}^{p,*}$,
by aggregating several results of~\cite{FHK}.

\begin{prop}[\cite{FHK}, Section 1]
\label{prop: Ad} $\;$
\begin{enumerate}
\item
The dg commutative algebra $(A_d,\dbar)$ is a model for $\RR \Gamma(\pAA^d, \sO_{\rm alg})$:
\[
A_d \simeq \RR\Gamma(\pAA^{d}, \sO^{alg}) .
\]
Similarly, $(A_d^{p,*},\dbar) \simeq \RR \Gamma(\pAA^{d}, \Omega^{p}_{\rm alg})$.
\item There is a dense map of commutative bigraded algebras
\[
\jou : A^{*,*}_d \to \Omega^{*,*}(\CC^d \setminus \{0\}),
\]
and the map intertwines with the $\dbar$ and $\partial$ differentials on both sides.
\item There is a unique $\GL_d$-equivariant residue map
\[
{\rm Res}_{z=0} : A_d^{d,d-1} \to \CC
\]
such that for any $\omega \in A^{d,d-1}_d$,
\[
{\rm Res}_{z=0} (\omega) = \oint_{S^{2d-1}} \jou(\omega)
\]
where $S^{2d-1}$ is any sphere centered at the origin in $\CC^d$. 
\item There is a representative $\omega_{BM}^{\rm alg}$ of the Bochner-Martinelli kernel such that
\[
\Res_{z=0} \left(f(z) \omega_{BM}^{alg}(z,z^*) \d z_1 \cdots \d z_d\right) = f(0)
\]
for any $f (z) \in \CC[z_1,\ldots,z_d]$. 
\end{enumerate}
\end{prop}

We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\pAA^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disk) into $\fg$,
just as $\fg[z,z^{-1}]$ provides a kind of loop algebra.

\begin{dfn}
For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$A_d \otimes \fg$.
Following \cite{FHK} we denote it by~$\fg^\bullet_d$.
\end{dfn}

There are natural central extensions of this sphere algebra as {\em $L_\infty$ algebras},
parallel to the affine Lie algebras appearing as central extensions of the loop algebra.
An $L_\infty$ algebra is a generalization of a Lie algebra;
it is graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k: L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi condition for a standard Lie algebra.
For an overview (and an actual definition!) we recommend \owen{add citations}.

In our setting of $\fg^\bullet_d$, Faonte-Hennion-Kapranov introduced central extensions that only affect the $d$-bracket.
For any $\fg$-invariant degree $d+1$ polynomial  $\theta \in \Sym^{d+1}(\fg^*)^\fg$,  the FHK  cocycle is
\[
\label{fhk cocycle}
\begin{array}{cccc}
\theta_{\rm FHK} : & (A_d \tensor \fg)^{\tensor (d+1)} & \to & \CC\\ 
& a_0 \otimes \cdots \otimes a_d & \mapsto & \Res_{z=0} \theta(a_0,\partial a_1,\ldots,\partial a_d)
\end{array}.
\]
This cocycle has cohomological degree $2$ and so determines an unshifted central extension as $L_\infty$ algebras
\[
\CC c \to \widetilde{\fg}^\bullet_{d, \theta} \to \fg^\bullet_d ,
\]
so that the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
They dubbed these the {\em higher Kac-Moody algebras}, 
as they specialize to the affine Lie algebras when~$d =1$.

These $L_\infty$ algebras are not just introduced on a whim.
In \cite{FHK} they are shown to appear naturally in various contexts,
notably in studying the derived moduli of $G$-bundles on a complex varieties of dimension~$d$.
\owen{Other applications?}

In addition to the higher Kac-Moody algebras, there are also natural higher analogs of the Weyl algebra of the loop space.
These appear as the observables for a holomorphic field theory known as a $\beta\gamma$ system.

Let $V$ be a symplectic complex vector space and consider the formal sphere algebra $A^{\wedge}_d \otimes V$,
where $A^{\wedge}_d$ denotes the completion of $A_d$ (i.e., where polynomials in $z_j$ and $z_j^*$ are replaced by formal power series).
\owen{Should we introduce a pithy notation?}
Then there is a dg commutative algebra of functions on this space,
which we denote $\cO(A^{\wedge}_d \otimes  V)$,
and it has a kind of Poisson bracket, arising from the residue pairing on $A^{\wedge}_d$ and the symplectic form on $V$,
just as $\cO(V((z)))$ has a Poisson bracket.
It will not surprise the reader to learn that there is a natural deformation quantization $W_d[V]$ into a dg Weyl algebra.
A physicist would interpret this algebra as the canonical and radial quantization of the theory on~$\CC^d - \{0\}$.

If $V$ is a representation of a Lie algebra $\fg$,
there is a local symmetry 
\[
\fg^\bullet_d \to \cO(A^{\wedge}_d \otimes V),
\]
just as $\fg[z,z^{-1}]$ acts on $\cO(V((z)))$. 
One can ask if this action lifts to a quantum symmetry.
The obstruction is, remarkably, an FHK cocycle:
\[
\alpha_{V,d}(x_1 \otimes f_1, \ldots, x_{d+1} \otimes f_{d+1}) = \Tr_V( x_1 \cdots x_{d+1}) \Res(f_1 \partial f_2 \cdots \partial f_{d+1}).
\]
\owen{Fix conventions}
In this sense, the higher Kac-Moody algebras admit a higher free field realization,
but a richer story is possible once we have a higher version of vertex algebras.
We will return to this topic once we have the rich language of factorization algebras.

\section{Factorization algebras and holomorphic field theories}
\label{prefactorization_algebras}

A key idea for us is that much of the content in field theories --- both classical and quantum --- are captured by factorization algebras.
We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
With the notion in hand, we will describe several examples and several situations where factorization algebras have already appeared in mathematics and physics, 
albeit in a different formulation.
Finally, we will sketch the main theorem of \cite{CG2}, 
which explains a precise and general relationship between quantum field theories and factorization algebras.

\subsection{The essential idea of a prefactorization algebra}

Let $M$ be a topological space and let $\mc{C}^\otimes$ be a symmetric monoidal category. 
In this paper $M$ is always a smooth manifold (typically a complex manifold) and $\mc{C}$ is ${\rm Vect}$ or ${\rm dgVect}$, with the usual tensor product as the symmetric monoidal product.

A {\em prefactorization algebra} $\cF$ on $M$ taking values in cochain complexes is a rule that assigns a cochain complex $\cF(U)$ to each open set $U \subset M$ along with the following maps and compatibilities.
\begin{itemize}
\item  There is a cochain map $m_V^U: \cF(U) \rightarrow \cF(V)$ for each inclusion $U \subset V$.

\item There is a cochain map $m_V^{U_1,\ldots,U_n} : \cF(U_1) \otimes \cdots \otimes \cF(U_n) \rightarrow \cF(V)$ for every finite collection of open sets where each $U_i \subset V$ and the $U_i$ are pairwise disjoint. The following picture represents the situation.
\begin{center}
 \begin{minipage}[c]{3cm}
 \begin{tikzpicture}[scale=0.25]
 \draw (0,0) circle (5);
 \draw (-1.5,2) circle(1.3) node {$U_1$};
 \draw (-2.2,-1.5) circle (1.5) node {$U_2$};
 \draw (0, -3) node {\tiny$\dots$};
 \draw (2.1,-1) circle (1.8) node {$U_n$};
 \draw (2.1, 3) node {$V$};
 \end{tikzpicture}
 \end{minipage}
\hspace{0.7cm} $\rightsquigarrow$ \hspace{0.5cm}
 \begin{minipage}[c]{8cm}
$\cF(U_1)\otimes\dots\otimes\cF(U_n)\xto{m_V^{U_1,\ldots,U_n}}\cF(V),$
 \end{minipage}
\end{center}

\item The maps are compatible in the obvious way, so that if $U_{i,1}\sqcup\cdots\sqcup U_{i,n_i}\subseteq V_i$ and $V_1\sqcup\cdots\sqcup V_k\subseteq W$, the following diagram commutes.
\begin{center}
\begin{tikzcd}[column sep=small]
{\bigotimes}^{k}_{i=1}{\bigotimes}^{n_i}_{j=1}\cF(U_j) \arrow{dr} \arrow{rr} &   &{\bigotimes}^k_{i=1}\cF(V_i) \arrow{dl}\\
&\cF(W)  &
\end{tikzcd}
\end{center}
\end{itemize}

For an explicit example of the associativity, consider the following picture.
\begin{center}
\hspace{-1cm}
\begin{minipage}{3cm}
{\tiny
\begin{center}
\begin{tikzpicture}[scale=0.35]
 % big circle:
\draw (0,0) circle (6);
\draw (2.4, 3.3) node {$W$};
 % circle V_1:
\draw [style=loosely dashed] (-2.2,1.6) circle (2.5);
\draw (-2.4, 2.8) node {$V_1$};
 % circle V_2:
\draw [style=loosely dashed] (2.4,-1.5) circle (2.6);
\draw (3.2, 0) node {$V_2$};
 % small circles:
\draw (-2.5, 0.8) circle (1) node {$U_{1,1}$};
\draw (-0.8, 1.8) circle (0.8) node {$U_{1,2}$};
\draw (2.5,-1.5) circle (0.9) node {$U_{2,1}$};
%\draw (2.9, -2.1) circle (1.1) node {$U_{2,2}$};
\end{tikzpicture}
\end{center}
}
 \end{minipage}
 \hspace{1.3cm} $\rightsquigarrow$ \hspace{-0.1cm}
\begin{minipage}{8cm}
\begin{tikzcd}[column sep=small]
\cF(U_{1,1}) \otimes \cF(U_{1,2}) \otimes \cF(U_{2,1}) \arrow{dr} \arrow{r}  & \cF(V_1) \otimes \cF(V_2) \arrow{d}\\
&\cF(W) 
\end{tikzcd}
\end{minipage}

The case of $k=n_1=2$, $n_2 = 1$.
\end{center}

This definition bears analogies to familiar objects in mathematics.
On the one hand, $\cF$ resembles a {\em precosheaf}, which is a functor from opens in $M$ to a category like ${\rm Vect}$ or ${\rm dgVect}$.
(A presheaf is a functor out of the opposite category to opens in $M$.) 
Here, however, $\cF$ also assign values to disjoint unions of opens, and it uses the tensor product rather than direct sum.
This feature leads to the other analogy: $\cF$ resembles an algebra, as
the multilinear maps look like multiplications.
These maps let us multiply elements from disjoint regions to get an element in a larger region.

Note that these axioms imply that $\cF(\emptyset)$ is a commutative algebra. 
We say that $\cF$ is a \emph{unital} prefactorization algebra  if $\cF(\emptyset)$ is a unital commutative algebra. In this case, $\cF(U)$ is a pointed cochain complex by the image of the unit $1 \in \cF(\emptyset)$ under the structure map $\cF(\emptyset) \to \cF(U)$. In practice, for our examples, $\cF(\emptyset)$ is $\CC$, $\RR$, $\CC[[\hbar]]$, or $\RR[[\hbar]]$.

\begin{eg}\label{ex:associativealgebra}
The crucial example to bear in mind is an associative algebra. Every associative algebra $A$ defines a prefactorization algebra $\cF_A$ on $\RR$, as follows. To each open interval $(a,b)$, we set $\cF_A( (a,b) ) = A$. To any open set $U = \coprod_j I_j$, where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$. The structure maps simply arise from the multiplication map for $A$. Figure ~\ref{fig:assasfact} displays the structure of $\cF_A$. Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra. 
%(One takes an infinite tensor products of unital algebras, as follows. Given an infinite set $I$, consider the poset of finite subsets of $I$, ordered by inclusion. For each finite subset $J \subset I$, we can take the tensor product $A^J = \bigotimes_{j \in J} A$. For $J \hookrightarrow J'$, we define a map $A^J \to A^{J'}$ by tensoring with the identity $1 \in A$ for every $j \in J' \backslash J$. Then $A^I$ is the colimit over this poset.) 
~\hfill$\Diamond$
\end{eg}

%\begin{figure}
%\begin{center}
% \begin{minipage}{3cm}
% \begin{tikzpicture}[scale=0.75]
% \begin{scope}[line cap=round,ultra thick]
% \draw (-2.5,0) -- (-1.5,0); 
% \draw (-1,0) -- (-0.5,0); 
% \draw (1,0) -- (2,0); 
% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
% \draw (-2.75,-2) -- (-0.25,-2); 
% \draw (0.75,-2) -- (2.5,-2);  
% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
% \draw (-3,-4) -- (3,-4); 
% \end{scope}
% \end{tikzpicture}
% \end{minipage}
%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
% \begin{minipage}{8cm}
% \begin{tikzcd}[cramped,column sep=tiny]
%a \otimes b \otimes c \arrow[mapsto]{d} & \in & A \otimes A \otimes A \arrow{d} \\
%ab \otimes c \arrow[mapsto]{d} & \in & A \otimes A \arrow{d} \\
%abc  & \in &A 
%\end{tikzcd}
%\end{minipage}
%\end{center}

\begin{figure}
\begin{center}
 \begin{tikzpicture} 
 \begin{scope}[line cap=round,ultra thick]
 \draw (-2.5,1) -- (-1.5,1); 
 \draw (-1,1) -- (-0.5,1); 
 \draw (1,1) -- (2,1); 
 \draw[->,semithick] (0,0.75) -- (0,0.25);
 \draw (-2.75,-0.1) -- (-0.25,-0.1); 
 \draw (0.75,-0.1) -- (2.5,-0.1);  
 \draw[->,semithick] (0,-0.35) -- (0,-0.85);
 \draw (-3,-1.2) -- (3,-1.2); 
 \end{scope}

\node at (4,0) {$\rightsquigarrow$ };

\node at (7,0){
\begin{tikzcd}[cramped,column sep=tiny]
a \otimes b \otimes c \arrow[mapsto]{d} & \in & A \otimes A \otimes A \arrow{d} \\
ab \otimes c \arrow[mapsto]{d} & \in & A \otimes A \arrow{d} \\
abc  & \in &A 
\end{tikzcd}
};
\end{tikzpicture}
\end{center}
\caption{The prefactorization algebra $\cF_A$ of an associative algebra $A$}
\label{fig:assasfact}
\end{figure}

\begin{eg}\label{ex:SymOfCosheaf}
Another important example for us is the symmetric algebra of a precosheaf. 
Let $F$ be a precosheaf of vector spaces on a space $X$. 
For example, consider $F = C^\infty_c$ the compactly supported smooth functions on a manifold. The functor $\cF  = \Sym F: U \mapsto \Sym(F(U))$ defines a precosheaf of commutative algebras, but it also a prefactorization algebra. For instance, if $U$ and $V$ are disjoint opens, we see that
\begin{align*}
\cF(U \sqcup V) = \Sym F(U \sqcup V) & \cong \Sym (F(U) \oplus F(V)) \\ & \cong \Sym(F(U)) \otimes \Sym(F(V)) = \cF(U) \otimes \cF(V),
\end{align*}
and these isomorphisms provide the structure maps for $\cF$.~\hfill$\Diamond$
\end{eg}

We will now sketch another way of phrasing this idea, but the reader who is content with this definition and eager to see examples should feel free to jump ahead, referring back as needed.

\subsection{Prefactorization algebras as algebras over an operad}
\label{sec:disj}

The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
See \owen{add citations}

\begin{dfn}
Let $\Disj_M$ denote the following colored operad associated to~$M$: 
\begin{itemize}
\item The colors (or objects) consist of all open subsets of $M$. 
\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$. If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point. Otherwise, the set of maps is empty.
\item The composition of maps is defined in the obvious way. 
\end{itemize}
\end{dfn}

\begin{dfn}
Let $\mc{C}$ be a colored operad. 
A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
\end{dfn}

In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories.

\begin{rmk} 
If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
~\hfill$\Diamond$ 
\end{rmk}

Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$.

\begin{dfn}
We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
\end{dfn}

\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
\label{AssAsFact}

We explained above how an associative algebra provides a prefactorization algebra on the real line. There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras. Here we will characterize those that do arise from associative algebras.

\begin{dfn}
Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
\end{dfn}

It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.

\begin{lem}\label{locally_constant_is_associative}
Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
\end{lem}

One can got further, however, and also capture modules, essentially by marking the line with points.
For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.

Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$. 
We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure.

Pick a point $p \in \RR$. On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$. Likewise, on the half-line $\{x \in \RR \mid p < x\}$, $\cF_M$ is given by $\cF_B$. Intervals containing $p$ are determined, though, by $M$. When we consider an interval $I = (t_0,t_1)$ such that $t_0 < p < t_1$, we set $\cF_M(I)  = M$. The structure maps are also determined by the bimodule structure. For example, given 
\[
s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
\]
we have
\begin{align*}
\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
&= A \ot M \ot B
\end{align*}
and the inclusion of these three intervals into $(s_0,u_1)$ is the map
\[
\begin{array}{ccc}
\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
a \ot m \ot b & \mapsto & amb
\end{array}.
\]
The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.

%\begin{figure}
%\begin{center}
% \begin{minipage}{3cm}
% \begin{tikzpicture}[scale=0.75]
% \begin{scope}[line cap=round,ultra thick]
% \draw (-2.5,0) -- (-1.5,0); 
% \draw (-1,0) -- (0.5,0); 
% \draw[fill=black] (0,0) circle (0.07);
% \draw (1.5,0) -- (2.5,0); 
% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
% \draw (-2.75,-2) -- (0.75,-2); 
% \draw[fill=black] (0,-2) circle (0.07);
% \draw (1.25,-2) -- (2.75,-2);  
% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
% \draw (-3,-4) -- (3,-4);
% \draw[fill=black] (0,-4) circle (0.07); 
% \end{scope}
% \end{tikzpicture}
% \end{minipage}
%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
% \begin{minipage}{8cm}
% \begin{tikzcd}[cramped,column sep=tiny]
%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
%amb  & \in &M 
%\end{tikzcd}
%\end{minipage}
%\end{center}
%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
%\label{fig:bimodasfact}
%\end{figure}

\begin{figure}
\begin{center}
 \begin{tikzpicture}
 \begin{scope}[line cap=round,ultra thick]
 \draw (-2.5,1) -- (-1.5,1); 
 \draw (-1,1) -- (0.5,1); 
 \draw[fill=black] (0,1) circle (0.07);
 \draw (1.5,1) -- (2.5,1); 
 \draw[->,semithick] (0,0.75) -- (0,0.25);
 \draw (-2.75,-0.1) -- (0.75,-0.1); 
 \draw[fill=black] (0,-0.1) circle (0.07);
 \draw (1.25,-0.1) -- (2.75,-0.1);  
 \draw[->,semithick] (0,-0.35) -- (0,-0.85);
 \draw (-3,-1.2) -- (3,-1.2);
 \draw[fill=black] (0,-1.2) circle (0.07); 
 \end{scope}

\node at (4,0){$\rightsquigarrow$};

\node at (7,0) {
\begin{tikzcd}[cramped,column sep=tiny]
a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
amb  & \in &M 
\end{tikzcd}
};

\end{tikzpicture}
\end{center}
\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
\label{fig:bimodasfact}
\end{figure}

\subsection{Factorization algebras}

We are now in a position to define factorization algebras,
which are prefactorization algebras whose behavior on large open sets is determined by their behavior on small open sets.
To give a precise description, we introduce a Grothendieck topology due to Michael Weiss~\owen{cite  \cite{Weiss} and it is explained nicely and further developed in \cite{BoavidaWeiss}}.

\begin{dfn}
Let $U$ be an open set. A collection of open sets $\mathfrak{U} = \{ U_i \mid i \in I\}$ is a {\em Weiss cover} of $U$ if for any finite collection of points $\{x_1,\ldots,x_k\}$ in $U$, there is an open set $U_i \in \mathfrak{U}$ such that $\{x_1,\ldots,x_k\} \subset U_i$.
\end{dfn}

The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$.

\begin{rmk}
A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens. It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$. For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection 
\[
\{ U_i^n \mid i \in I\}
\]
provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
\end{rmk}

\begin{eg}\label{WeissAsExponential}
For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$. One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disk. Alternatively, the collection of opens $\{ M \setminus q \mcol q \in M\}$ is a Weiss cover of $M$. One can also produce a Weiss cover of a manifold with countably many elements. Fix a Riemannian metric on $M$. Pick a collection of points $\{q_n\in M \mcol n \in \NN\}$ such that the union of the unit ``discs'' $D_1(q_n) = \{ q \in M \mcol \d(q_n,q) < 1\}$ covers $M$. (Such an open may not be homeomorphic to a disc if the injectivity radius of $q_n$ is less than 1.)  Consider the collection of all ``discs'' $\fD = \{ D_{1/m}(q_n) \mcol m \in \NN, n \in \NN\}$.  The collection of all finite, pairwise disjoint union of elements of $\fD$ is a countable Weiss cover.~\hfill $\Diamond$ 
\end{eg}

Now that we have a notion of cover, we can formulate the local-to-global property for factorization algebras,
which amounts to being a cosheaf for the Weiss topology.
For concreteness' sake, we will continue to have our prefactorization algebras take values in ${\rm dgVect}$,
but it is straightforward to generalize by allowing the values to live in, say, a symmetric monoidal $\infty$-category.

Let us provide the definition of a homotopy cosheaf. 
Let $\Phi$ be a precosheaf on $M$ with values in cochain complexes. Let $\mathfrak{U} = \{U_i \mid i \in I\}$ be a cover of some open subset $U$ of $M$.  Consider the cochain complex with values in cochain complexes whose $-k$th term is 
\[
\bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}),
\]
and note that this term has an ``internal'' differential arising from $\Phi$. The ``external'' differential is the alternating sum of the structure maps arising from inclusion of $k+1$-fold intersections into $k$-fold intersections. The \emph{\v{C}ech complex of $\mathfrak{U}$ with coefficients in $\Phi$} is the totalization of this double complex:
$$
\check{C}(\mathfrak{U}, \Phi) = \bigoplus_{k=0}^\infty \left( \bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}) [ k]   \right).
$$
There is a natural map from the $0$th term (of the double complex) to $\Phi(U)$ given by the sum of the structure maps $\Phi(U_i) \to \Phi(U)$. Thus, the \v{C}ech complex possesses a natural map to $\Phi(U)$. We say that $\Phi$ is a \emph{homotopy cosheaf} if the natural map from the \v{C}ech complex to $\Phi(U)$ is a quasi-isomorphism for every open $U \subset M$ and every open cover of $U$. This \v{C}ech complex is simply the dual of the \v{C}ech complex for sheaves of cochain complexes.
In more sophisticated language, the \v{C}ech complex describes the homotopy colimit of $\Phi$ on this simplicial diagram.

We can now define our main object of interest.

\begin{dfn}
A \emph{factorization algebra} is a prefactorization algebra $\cF$ on $M$ valued in $\Ch$ \owen{change to dgVect?}, with the property that for every open set $U \subset X$ and Weiss cover $\mathfrak{U}$ of $U$, the natural map
$$
\check{C}(\mathfrak{U},\cF) \to \cF(U)
$$
is a quasi-isomorphism. That is, $\cF$ is a homotopy cosheaf with respect to the Weiss topology.
\end{dfn}

We also formulate a multiplicativity condition, as follows.

\begin{dfn}
A factorization algebra $\cF$ is \emph{multiplicative} if for every pair $U,V$ of disjoint open subsets of $M$, the structure map
$$
\cF(U) \otimes \cF(V) \to \cF(U \sqcup V) 
$$
is a quasi-isomorphism.
\end{dfn}

As verification that this notion has some real content, let's consider a first, interesting case.
We already explained how to produce a locally constant prefactorization algebra $\cF_A$ on $\RR$ from a dg associative algebra $A$.
We could ask about working on the circle $S^1$ instead of $\RR$.
This construction tells us what to assign to every proper open subset of $S^1$: for instance, to each open interval, we assign $A$.
The \v{C}ech complex should then tell us what to assign to the whole circle.
Remarkably, this construction recovers a well-known invariant: the Hochschild chains ${\rm Hoch}_*(A)$ of~$A$.

\begin{thm}[\owen{citations}]
The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
\[
{\rm Hoch}_*(A) \simeq \check{C}(\mathfrak{U},\cF_A)
\]
for any Weiss cover of~$S^1$.
\end{thm}

The reader can check by hand that for an ordinary algebra $A$, the value on the circle is $A/[A,A] = {\rm HH}_0(A)$.
This theorem tells us that factorization homology can be seen as a generalization of Hochschild homology,
where one simultaneously generalizes the circle to an arbitrary closed manifold and an algebra to a factorization algebra.

It can be hard to check whether a given $\cF$ is a homotopy cosheaf, since computing the \v{C}ech complex is typically difficult.
There are some useful abstract results, such as the fact that a factorization algebra is determined by its behavior on a basis for the Weiss topology.
But there is also a rich source of examples in differential geometry, and hence from physics.

Given a vector bundle $E \to M$ (possibly a graded vector bundle), 
let $E^{\boxtimes m} \to M^m$ denote the external product of $E$ with itself $m$ times.
Let $\cE_c(U)$ denote compactly supported sections of $E$ over $U$, 
and similarly let $\cE^{\boxtimes m}_c(U^m)$ denote compactly supported sections of $E^{\boxtimes m}$ over $U^m$.
Let $\Sym^m(\cE_c)(U)$ denote the sections that are invariant under the action of the symmetric group $S_m$ on~$U^m$.
We define a functor $\Sym(\cE_c): \Open(M) \to \Vect$ by
\[
\Sym(\cE_c)(U) = \bigoplus_m \Sym^m(\cE_c)(U),
\]
which is a kind of symmetric algebra on $\cE_c(U)$.
(Those familiar with functional analysis will note that taking sections of the product bundles is a nice way of completing the algebraic tensor product of sections on each component bundle.)
This construction is actually a cosheaf for the Weiss topology, just as $\cE_c$ is a cosheaf for the ordinary topology;
in this sense, the Weiss topology is an ``exponentiation'' of the ordinary topology just as $\Sym(V)$ is an ``exponentiation'' of a vector space~$V$.
We have seen in Example~\ref{ex:SymOfCosheaf} how $\Sym(\cE_c)$ determines a prefactorization algebra,
so the following theorem should be plausible.

\begin{thm}[\owen{cite book}]
For $E \to M$ a graded vector bundle, the functor $\Sym(\cE_c)$ encodes a factorization algebra on $M$.
If we equip $\cE_c$ with a differential operator $d$ of degree 1 suc that $d^2 = 0$ so that $(\cE_c, d)$ is a cosheaf of differential complexes,
then $(\Sym(\cE_c), d)$ is a factorization algebra, where $d$ denotes the natural extension.
\end{thm}

Two examples of differential complexes play a key role in applications: 
\begin{itemize}
\item the de Rham complex $(\Omega^*, d)$ on a smooth manifold, which is relevant for topological field theories, and 
\item the Dolbeault complex $(\Omega^{0,*}, \dbar)$ on a complex manifold, which is relevant for holomorphic field theories.
\end{itemize}
One can take, of course, these complexes with sections in a flat vector bundle (for the de Rham case) or a holomorphic vector bundle (for the Dolbeault case).

\subsection{Algebras over the little disks operad}

Associative algebras are familiar to every mathematician, but as we have just seen, they reflect and encode one-dimensional geometry.
It is then natural to ask about higher-dimensional versions of algebra.
Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-disks operad,
which we now describe and relate to prefactorization algebras on~$\RR^n$.
In relation to the subject of this paper, we mention that $E_n$ algebras arise naturally from $n$-dimensional topological field theories;
we will soon introduce a holomorphic analog of $E_n$ algebras relevant to holomorphic field theories,
modeled on the discussion here.

Fix a dimension $n$. 
Let $D^n(x,r)$ denote the open disk of radius $r$ centered at $x \in \RR^n$,
and let $D^n$ denote the unit disk~$D^n(0,1)$.

\begin{dfn}
Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint disks:
\[
E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the disks $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disk $D^n$\end{tabular}}\right\}.
\]
\end{dfn}

When $n = 1$, the operad encodes the idea of associative multiplication:
we get pictures much like those we drew earlier with intervals, 
except that now we can slide and stretch the intervals because we have a space of operations.
More accurately, $E_1$ is a model for associative algebras up to homotopy; 
it is closely related to the $A_\infty$ operad. \owen{Let me check how people compare these.}

For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
If one fixes a direction, such as a coordinate axis, and works with disks lined up in this direction,
one sees an $E_1$ structure.

\owen{Add picture? We drew 2d pictures earlier.}

An algebra over this operad is called an $E_n$-algebra.
A classic example from topology is given by taking the $n$-fold based loop space
\[
\Omega^n_x(X) = \{ \gamma: \overline{D^n} \to X \mcol \gamma(\partial \overline{D^n}) = x\}
\]
of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disk.
Maps that send the boundary of a disk to the base point can be extended naturally to bigger disks: just send the rest of the big disk to the basepoint.
\owen{Should I spell out the structure of the algebra?}
Examples include \owen{What to mention?}

Factorization algebras on $\RR^n$ and $E_n$ algebras should be closely related,
as can be seen by drawing pictures of the configurations of disks that control operations.

\begin{dfn}
A factorization algebra $\cF$ on an $n$-manifold $M$ is \emph{locally constant} if for each inclusion of open disks $D \subset D'$, then the map $\cF(D) \to \cF(D')$ is a quasi-isomorphism.
\end{dfn}

For $M = \RR$, we have already discussed how locally constant factorization algebras relate to associative algebras, starting with Example~\ref{ex:associativealgebra}.
Lurie has shown the following vast extension of this example. (See section 5.4.5 of \cite{LurieHA}, particularly Theorem 5.4.5.9.)

\begin{thm}\label{thm:locisen}
There is an equivalence of $(\infty,1)$-categories between $E_n$ algebras and locally constant factorization algebras on~$\RR^n$.  
\end{thm}

We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do. A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}. We emphasize that higher categories are necessary for a rigorous development of these constructions and comparisons, although we will not emphasize that point in our discussion below, which is expository in nature.

\begin{rmk}
This theorem, together with our work in these two books, builds an explicit bridge between topology and physics. Topological field theories in the physicist's sense, such as perturbative Chern-Simons theory, produce locally constant factorization algebras, which can then be viewed as $E_n$ algebras and analyzed using the powerful machinery of modern homotopy theory. Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.~\hfill $\Diamond$
\end{rmk}

\begin{rmk}
We have shown how thinking about prefactorization algebras on a real line ``decorated'' with points (i.e., with a kind of stratification) reflects familiar algebraic objects like bimodules. By moving into higher dimensions and allowing more interesting submanifolds and stratifications, one generalizes this familiar algebra into new, largely-unexplored directions. See \cite{AyalaFrancisTanaka} for an extensive development of these ideas in the setting of locally constant factorization algebras.
~\hfill $\Diamond$
\end{rmk}

\subsection{How factorization algebras appear in QFT}

In \cite{CG1, CG2} a systematic relationship is provided between field theories and factorization algebras.
The slogan is 
\begin{quote}
the observables of a field theory living on a manifold $M$ form a factorization algebra on~$M$. 
\end{quote}
To make a mathematical statement, one needs to be precise about what a field theory is.
From hereon, whenever we speak of a classical or quantum field theory, we will mean the definitions articulated in \cite{CosBook,CG1, CG2}, which encompass the Euclidean versions of many field theories studied in physics and mathematics.
Those books use the Batalin-Vilkovisky (BV) formalism for quantization, a homological method generalizing the BRST approach and widely regarded as the most powerful and general way to quantize gauge theories.

\begin{thm}
\label{main}
The observables of a classical field theory on $M$ form a factorization algebra $\Obs^{cl}$ that assigns to every open set, a 1-shifted Poisson algebra (i.e., a commutative dg algebra equipped with a Poisson bracket of cohomological degree one). A BV quantization of this theory yields a factorization algebra $\Obs^q$ that is a flat deformation of $\Obs^{cl}$ over~$\RR[[\hbar]]$.
\end{thm}

This theorem provides an elegant interpretation of BV quantization as a kind of deformation quantization. In the setting of mechanics (or one-dimensional field theory, since a particle has a worldline), deformation quantization explains the transition from classical to quantum as deforming the observables from a Poisson algebra to an associative algebra. 
This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra.

In \cite{CG1}, there are several examples of this formalism in action:
\begin{itemize}
\item Basic examples from quantum mechanics, such as the harmonic oscillator, and it is shown how to recover the Weyl algebra and the Hamiltonians from factorization algebras living on~$\RR$. 
\item Scalar field theory on $\RR^n$, where it is shown how the usual correlation functions are encoded in the factorization algebra on~$\RR^n$ and how canonical quantization appears via pushforward of factorization algebras.
\item The free $\beta\gamma$ system on $\CC$---a basic example of a chiral conformal field theory---is constructed and its usual vertex algebra is extracted from the factorization algebra.
\item Abelian Chern-Simons theory, where it is shown how dimensional reduction along a closed surface $\Sigma$ produces the Weyl algebra on the symplectic vector space $H^1(\Sigma)$ and how line operators form a (very simple!) braided monoidal category.
\end{itemize}
These examples, while not complicated, exhibit in detail how factorization algebras provide a bridge from action functionals to algebra in a broad sense.

This formalism has shown its power in a number of nontrivial applications:
\begin{itemize}
\item Grady, Li, and Li \cite{GLL} give a direct connection between Fedosov quantization and the factorization algebra of a 1-dimensional field theory.
%\item Gorbounov, Williams and I \cite{GGW} constructed rigorously a 2-dimensional QFT depending on a Calabi-Yau manifold $X$, known as the curved $\beta\gamma$ system, and showed the factorization algebra recovers the chiral differential operators of~$X$.
\item Li and Li \cite{LiLi} constructed the topological B-model and show the factorization algebra recovers the expected topological vertex algebra (see \cite{LiVOA} for a deeper treatment).
\item Costello, Francis, and Gwilliam \cite{CFG} have shown how the factorization algebra of Chern-Simons theory for $\fg$ encodes a quantum group $U_\hbar \fg$ over~$\CC[[\hbar]]$.
\item Rabinovich \cite{RabAxial} showed how the local index theorem and the axial anomaly are simultaneously captured by quantizing free fermions (associated to Dirac operators). Subsequently, he recovered the Quillen determinant line~\cite{RabDet}.
\item Costello \cite{CosYangian} introduced a 4-dimensional gauge theory whose factorization algebra recovers the Yangian,
and subsequently gave extensive applications to quantum integrable systems with Witten and Yamazaki \cite{CWY1,CWY2, CY}.
\end{itemize}
There are others, connected with central topics such as mirror symmetry and the AdS/CFT correspondence, 
and we will discuss holomorphic field theories extensively below.

Thanks to the efforts of people who have adopted this BV/factorization framework,
we now also understand its connection to many important structural aspects of QFT, 
such as asymptotic freedom \cite{EWY}, current algebras \cite{GWcurr}, the Anderson-Higgs mechanism \cite{EG}, and the CS/WZW correspondence~\cite{GRW, CosDimGai}.
In each case this enriched mathematical language offers a new and (we would argue) clarifying point of view.
In turn, physics offers new vistas or rich applications for mathematicians to explore.

\subsection{$E_n$ algebras from topological field theories}

Although our focus in this paper is on holomorphic field theories and factorization algebras,
it might be helpful to describe some motivating results about topological field theories and factorization algebras.
Elliott and Safronov have \owen{not sure how much to say here, but I'm going to take a stab at writing a synoptic theorem}

If one examines theories like Chern-Simons theory on $\RR^3$ or the Poisson $\sigma$-model on $\RR^2$, 
one discovers a general format for constructing theories that was formalized by \cite{AKSZ}.
In a nutshell, the field theory is factored into two parts: 
the de Rham complex of the source or ``spacetime'' manifold, 
and a Lie algebra-type object encoding a gauge Lie algebra or a ``target'' for a $\sigma$-model.

\begin{dfn}
A classical {\em AKSZ-type theory} on $\RR^d$ is a determined by an $L_\infty$-algebra $\fg$ equipped with a cyclic pairing $\langle-,-\rangle$ of degree $3-d$.
Its {\em equation of motion} is the Maurer-Cartan equation 
\[
0 = \d A + \frac{1}{2} [A,A] + \frac{1}{3!}[A,A,A]_3 + \cdots = \sum_{k=1}^\infty \frac{1}{k!} [A, \ldots, A]_k
\]
of the $L_\infty$ algebra $\Omega^*(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
The {\em action functional} is the expression
\[
S(A) = \int_{\RR^d} \sum_{k=1}^\infty \frac{1}{{k+1}!} \langle A, [A, \ldots, A]_k \rangle
\]
\end{dfn}

Ordinary Chern-Simons theory on $\RR^3$ arises from taking $\fg$ to be a semisimple Lie algebra and a choice of invariant pairing.
In that case, and using $\Tr$ to denote the pairing, the action functional is the familiar
\[
S(A) = \int_{\RR^3}  \frac{1}{2}\Tr ( A, \d A ) + \frac{1}{3!} \Tr( A, [A, A])
\]
and the equation of motion asks for connections with zero curvature.

Many other theories can be expressed in this style, and we suggest \owen{lots of papers} for examples.
Elliott and Safronov characterize and exhibit topological twists of supersymmetric theories as AKSZ-type theories.

\begin{thm}[\cite{CG2;ElliottSafronov}]
For a classical AKSZ-type theory on $\RR^d$, the observables 
\[
\Obs^{cl}(U) = \clie^*(\Omega^*(U) \otimes \fg)
\]
form a locally constant factorization algebra and hence determine an $E_d$ algebra~$\cA^{cl}$.
A quantization, if it exists, determines a deformation $\cA^q$ of this $E_d$ algebra.

Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
\end{thm}

More generally, given a map of Lie groups $G \to O(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.

Scheimbauer's thesis then provides a functorial field theory in the sense of Atiyah, Segal, and Lurie.

\begin{thm}
Given a homotopically $SO(d)$-trivial quantization of a classical AKSZ theory on $\RR^d$, 
factorization homology of the quantum observables 
\[
\int_{(-)} \cA^q \colon {\rm Bord}^{or}_d \to {\rm Alg}_d
\]
determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of $E_d$ algebras.
\end{thm}

A similar claim applies to the general case with a map $G \to O(d)$.

\section{Vista: Holomorphic $\sigma$-models and higher algebras of differential operators}

We have already met the higher dimensional $\beta\gamma$ system on $\CC^n$.
This is an $n$-dimensional holomorphic system described by an $n$-dimensional translation invariant factorization algebra.
In part, the fields of this system constituted a holomorphic map $\gamma \colon \CC^n \to \CC^N$ together with its conjugate field $\beta$.

\brian{background on CDO's}

\begin{dfn}\label{dfn:cdo}
A {\em sheaf of $n$-CDOs} on a manifold $X$ (of complex dimension $N$) is a sheaf of $n$-dimensional holomorphically translation invariant factorization algebras whose restriction to any $n$-disk is equivalent to the $n$-dimensional $\beta\gamma$ system (with target $\CC^N$). 
\end{dfn}

\begin{thm}\label{thm:cdo}
Suppose $X$ is a complex manifold satisfying 
\[
{\rm ch}_{n+1} (\T_X) = 0 \in H^{n+1} \big(X , \Omega^{n+1,cl}_X\big).
\]
Then, the set of equivalence classes of higher dimensional CDO's on $X$ is a torsor for the group $H^n \big(X , \Omega^{n+1, cl}_X\big)$. 
If ${\rm ch}_{n+1}(\T_X) \ne 0$ then there does not exist a sheaf of higher CDO's on $X$. 
\end{thm}

\begin{rmk}
When $n=1$ we \cite{GGW} \brian{finish}
\end{rmk}

We can reformulate this theorem to stress the role of the higher dimensional holomorphic OPE. 
An alternative to Definition \ref{dfn:cdo} would be to first take the cohomology of the state space of the $\beta\gamma$ system to obtain the structure of a holomorphic $\PP_n$ algebra.
Then, one can define a sheaf of higher CDO's as a sheaf of holomorphic $\PP_n$ algebras which is locally of the form \eqref{eqn:bgope}. 
Theorem \ref{thm:cdo} still applies to show that a necessary condition for such a sheaf to exist is the vanishing of the $(n+1)$ component of the Chern character of $X$. 
The global sections of such a sheaf will give rise to a single holomorphic $\PP_n$ algebra.

Let's unravel this approach in the case $n=2$. 
Label the local coordinate on the target by $\{w^i\}_{i=1,\ldots,N}$.

The cohomology of the state space of the $2$-dimensional $\beta\gamma$ system is a graded polynomial algebra of the form
%\[
%\CC\big[\partial_{z_i}^{\bu \geq 0} \gamma, \partial^{\bu\geq 0}_{z_i} \beta \big]
%\]
\[
\CC\bigg[\gamma^i[k,\ell] \; , \; \beta_j [k,\ell] \bigg]_{k,\ell \geq 0} .
\]
For $k,\ell \geq 0$ and $i,j=1,\ldots N$ the generator $\gamma^i[k,\ell]$ is of cohomological degree zero and the generator $\beta_j[k,\ell]$ is of cohomological degree $1$.

The higher OPEs $\{\gamma^i[k,\ell], \gamma^j [p,q]\}^{r,s} = 0$, $\{\beta^i[k,\ell], \beta^j [p,q]\}^{r,s} = 0$ all vanish. 
There is a nontrivial higher OPE between $\gamma^i$ and $\beta_j$, the simplest of such reads
\[
\big\{\gamma^i[0,0] , \beta_j[-1,-1] \big\}[r,s] = \delta_{r,0} \delta_{s,0} .
\]
In general, 
\beqn\label{eqn:bgope}
\big\{\gamma^i[k,\ell] , \beta_j[p-1,q-1] \big\}[r,s] = \delta_{r,k+p} \delta_{s,\ell+q} .
\eeqn

\subsubsection{Global sections, an example}

We give a concrete description of 2-CDO's on the manifold $X = \PP^1$.
In this case there is a unique sheaf of 2-CDO's that we denote by $2\CDO_{\PP^1}$ (here we are using the holomorphic $\PP_2$ description as the cohomology of the observables of the $\beta\gamma$ system on a $2$-disk).
Consider the standard description of $\PP^1 = U \cup V$ where $U = {\rm Spec}(\CC[\gamma])$ and $V = {\rm Spec}(\CC[\gamma^{-1}])$.

On $U$, $2\CDO_{\PP^1}(U)$ is the graded polynomial algebra $\CC[\gamma[k,\ell], \beta[p,q]]$. 
On the intersection $U \cup V$ we glue by the transition function
\begin{align*}
\Tilde{\gamma} [k,\ell] & \define \gamma^{-1} [k,\ell] \\
\Tilde{\beta} [p,q] & \define - \sum_{i+j+k=p} \sum_{i'+j'+k'=q} \gamma[i,i'] \gamma[j,j'] \beta[k,k'] + 2 \gamma[p+1, q] + 2 \gamma[p, q+1] .
\end{align*}
\brian{need to fix that I think}

We can gain further insight into the structure of $2\CDO_{\PP^1}$ by the following result. 
Classically, the target $\PP^1$ has an obvious geometric symmetry by the Lie algebra $\sl(2)$ which further lifts to a symmetry by the dg Lie algebra $\fa_2 \otimes \sl(2)$.

\begin{prop}
The graded vector space $H^\bu \big(\PP^1 \; , \; 2 \CDO_{\PP^1}\big)$ is a module for the graded Lie algebra $H^\bu(\sfA_2) \otimes \sl(2)$
\end{prop}

\begin{rmk}
This result is to be contrasted with the case of ordinary CDO's on $\PP^1$. 
Classically, the one-dimensional $\beta\gamma$ system of maps $\CC \to \PP^1$ has a symmetry by the current algebra $\sfA_1 \otimes \sl(2) = \sl(2)[z,z^{-1}]$. 
At the quantum level, the global sections of ordinary CDO's over $\PP^1$ is a representation for affine Kac--Moody algebra $\Hat{\sl}_2$ at the {\em critical level} \cite[Theorem 5.7]{MSV}. 
In fact, it is isomorphic to a direct sum of two copies of the vacuum representation at the critical level.
This proposition shows that the classical $\sl(2)$-valued $S^3$-currents of global sections of 2-CDO's on $\PP^1$ acquire no such central extension. 
\end{rmk}

Instead of $\PP^1$ let's consider $\PP^2$ thought of as the Grassmannian of lines in $\CC^3$. 
Since $\ch_3(\T_{\PP^2})$ is trivial
the $\beta\gamma$ system of maps $\CC^2 \to \PP^2$ exists at the quantum level and we get a sheaf of 2-CDO's that we denote $2\CDO_{\PP^2}$. \footnote{The sheaf of ordinary CDO's is {\em not defined} on $\PP^2$.}

The classical $\beta\gamma$ system has, as a symmetry algebra, the $\sl(3)$-valued $S^3$ currents $\sfA_2 \otimes \sl(3)$. 
This is {\em not} a symmetry at the quantum level, rather a {\em higher dimensional Kac--Moody algebra} acts instead.

Let $\theta \in {\rm Sym}^3(\sl(3))$ denote the invariant polynomial $(A,B,C) \mapsto {\rm tr}(ABC)$, where the trace is computed in the {\em defining} representation.
Given $\theta$ we define, as in Section \ref{sec:KM}, the $2$-dimensional Kac--Moody algebra as the $L_\infty$ algebra central extension
\[
0 \to \CC K \to \Hat{\sl(3)}_{2,\theta} \to \sfA_2 \otimes \sl(3) \to 0 .
\]

\begin{prop}
The graded vector space $H^\bu \big(\PP^2 \; , \; 2 \CDO_{\PP^2}\big)$ is a module for the $L_\infty$ algebra $\Hat{\sl(3)}_{2, \theta}$ whereby the central element $K$ acts by multiplication by some nonzero scalar. 
\end{prop}

\subsubsection{Chiralization of the B-model}

In a precise sense, one can view the higher dimensional $\beta\gamma$ system as a holomorphic refinement of a familiar algebra in topological field theory.

\begin{prop}
Let $X$ be a complex manifold with ${\rm ch}_{3}(\T_X) = 0$ and let $2\CDO_X$ be a sheaf of $2$-CDO's on $X$. 
There is an equivalence of sheaves on $X$
\[
{\rm Zhu}_{\EE_2} \big(2\CDO_X) \simeq {\rm PV}^{\bu}_X \define \bigoplus_{i\geq 0} {\rm PV}^i_X [-i] .
\]
Furthermore, the underlying $\PP_2$-structure of the left hand side agrees with the standard Gerstenhaber structure on polyvector fields.
\end{prop}

\begin{rmk}
In this sense, $2\CDO_X$ is a `chiralization' of the sheaf of polyvector fields.
It is distinct from a more standard one coming from the holomorphic twist of the two-dimensional $\cN=(2,2)$ supersymmetric $\sigma$-model.
\end{rmk}

The expert reader will identify the sheaf appearing in the statement of this proposition as local observables of the topological $B$-model on $\RR^2$ with target $X$. 
At the level of quantum field theories, the statement of this proposition is no surprise. 
The key point is that the Zhu algebra (and its $\EE_n$ generalization) is an instance of ``dimensional reduction'' from a holomorphic theory to a topological one.

On one hand, one considers the $\beta\gamma$ of maps from the two-dimensional complex manifold $\CC^\times \times \CC^\times$ with target manifold $X$:
\[
\T^*[-1] {\rm Map}\left(\CC_\dbar^\times \times \CC_\dbar^\times , X\right) \; \simeq \; {\rm Map}\left(\CC_\dbar^\times \times \CC_\dbar^\times , \T^*[1] X\right) .
\]
In this identification we have used the obvious Calabi--Yau form on $\CC^\times \times \CC^\times$. 
The dimensional reduction of this mapping space along the `doubled' radial projection $\CC^\times \times \CC^\times \to \RR \times \RR$ is precisely the AKSZ description of the ordinary $B$-model with target $X$
\[
{\rm Map}\left(\RR^2_{\rm dR} , \T^*[1] X\right)
\]
in agreement with the proposition above.

\subsubsection{Homogenous spaces}

Suppose that $N$ is a unipotent subgroup of $G$.
For $j \geq 1$ one has
\[
H^j \left( G / N \, ; \, \Omega^{n+1,cl}_{G/N} \right) \; \simeq \; H_{\rm dR}^{j+n+1} \big(G / N \big)
\]

\section{Vista: Seiberg duality and its consequences}

The field content of 4d $\cN=1$ supersymmetric Yang--Mills theory is:
\begin{itemize}
\item a `vector multiplet' which consists of a gauge field $A$ together with some fermions $\lambda$ all taking values in a Lie algebra $\fg$;
\item a `matter multiplet' (usually called the chiral multiplet) which consists of a scalar $\phi$ together with some fermions $\psi$ all transforming in some representation $V$ of $\fg$. 
Additionally, there is a `superpotential' $W$ which is a $\fg$-invariant polynomial on~$V$. 
\end{itemize}

From hereon we fix a nonzero, square zero supercharge of the 4d $\cN=1$ supersymmetry algebra for which we wish to twist by. 
The twist of 4d $\cN=1$ supersymmetric Yang--Mills theory has been characterized in \cite{CosYangian, ESW, SWchar}. 
It is a holomorphic field theory on $\CC^2$ consisting of a `vector' part and a 'matter' part.
As a moduli space, it can be described in the following way (we will give a description in terms of fields and action functionals afterwards).

Let's consider the matter part. 
Recall that the derived critical locus ${\rm Crit}(W)$ of any function on $V$ has a $(-1)$-shifted symplectic structure. 
As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
From now on, we forget the $\ZZ$-grading and view this locus as equipped with an odd symplectic structure. 
Before coupling to the gauge theory, the matter part of the holomorphic twist is the derived mapping space ${\rm Map}(\CC^2_{\dbar}, {\rm Crit}(W))$ which is equipped with an odd symplectic structure by the AKSZ construction.

Since $W$ is $\fg$-invariant, the critical locus has a residual Hamiltonian $\fg$ action. 
There is a version of Hamiltonian reduction for odd symplectic manifolds, see \cite{Pavel, Kevin, who else}. 
Denote this reduction by ${\rm Crit}(W) \sslash \fg$. 
As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$.

In total, the holomorphic twist is equivalent to the following derived mapping space
\[
{\rm Map}(\CC^2_{\dbar} \; , \; {\rm Crit}(W) \sslash \fg) 
\]
which is equipped with an odd symplectic structure.

In essence, all of the holomorphic theories we consider below will be special cases of this gauged linear mapping space on $\CC^2$. 
We slightly refine notation and associate a holomorphic theory $\cT(G, V, Z, W)$ on $\CC^2$ associated to the following data:
\begin{itemize}
\item a Lie group $G$, this is the gauge group. 
Its complexified Lie algebra is $\fg = {\rm Lie}_\CC (G)$;
\item a complex $G$-representation $V$, this is where the `chiral quark matter' lives;
\item a complex vector space $Z$ where the `mesons' live.
This is not acted upon by the group $G$. 
\item a polynomial $W \in {\rm Sym}(V \oplus \Bar{V} \oplus Z)$.
\end{itemize}

\begin{dfn}
{\em Holomorphic QCD} associated to the data $(G,V,Z,W)$ as above is the holomorphic field theory on $\CC^2$ with fields:
\begin{itemize}
\item The gauge fields are those of holomorphic BF theory valued in $\fg$, which we denote by
\[
A \in \Omega^{0,\bu}(\CC^2 , \fg)[1] , \quad B \in \Omega^{2,\bu}(\CC^2, \fg^*) .
\]
\item The `matter fields' consist of a holomorphic $\beta\gamma$ system valued in $V$, which we denote by
\[
Q \in \Omega^{0,\bu}(\CC^2 , V) , \quad P \in \Omega^{2,\bu}(\CC^2 , V^*)[1] ,
\]
a holomorphic $\beta\gamma$ system valued in the complex conjugate representation $\Bar{V}$, which we denote by
\[
\Tilde{Q} \in \Omega^{0,\bu}(\CC^2 , \Bar{V}) , \quad \Tilde{P} \in \Omega^{2,\bu}(\CC^2 , \Bar{V}^*) [1],
\]
and a $\beta\gamma$ system valued in the vector space $Z$, which we denote by
\[
M \in \Omega^{0,\bu}(\CC^2 , Z) , \quad L \in \Omega^{2,\bu}(\CC^2 , Z^*) [1] .
\]
\end{itemize}

The action functional is
\[
\int B F^{0,2}_A + \int P \dbar_A Q + \int \Tilde{P} \dbar_A \Tilde{Q} + \int \d^2 z \; W(Q, \Tilde{Q}, M) + \int L \dbar M
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator. 
We will refer to this theory by $\cT(G,V,Z,W)$.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators.} 
\end{dfn}

\begin{rmk}
This theory is only $\ZZ/2$-graded, so all fields are considered only as `even' or 'odd'--for instance the component of the gauge field $A^{0,1}$ is even while the component of the matter field $Q^{0,1}$ is odd. 
Only in the case that $W = 0$ can one lift the theory to a $\ZZ$-grading.
\end{rmk}

\begin{rmk}
Note that the fields $M$ are `uncharged' under the gauge group.
The only coupling $M$ has to the other fields is through the superpotential $W$. 
\end{rmk}

Our long term goal is to show that two special cases of holomorphic QCD are {\em dual}.
We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
Following physics terminology, will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
Also, suppose $N_c, N_f$ are integers with $N_f \geq N_c \geq 2$.
%Also, let $N_{\rm mes} \geq 0$ be some integer.  
%{\em Type A} holomorphic QCD is 
%\[
%\cT_{A} (N_c, N_f, N_{\rm mes},W) = \cT\left(G = \SU(N_c) \, , \, V = (\CC^{N_c})^{\oplus N_f} \, , \, Z = \CC^{\oplus N_{\rm mes}} \, , \, W\right) .
%\]

First, we have the `electric' theory which is the following holomorphic QCD
\[
\cT_{\sfE} (N_c , N_f) \define \cT\big(\SU(N_c) \, ,\, (\CC^{N_c})^{\oplus N_f} \, ,\, Z = 0 \, , \, W = 0\big) .
\]

%\begin{dfn}
%Suppose $\cT_A (N_c, N_f, N_{\rm mes}, W)$ is a type A holomorphic QCD. 
%Define the {\em dual} type A holomorphic QCD to be
%\[
%\Hat{\cT}_{A} (N_c, N_f, N_{\rm mes}, W) \define \cT_{A} (N_f - N_c, N_f, N_{\rm mes} + N_{f}^2 , W + 
%\]
%\end{dfn}

Second, we have the `magnetic' theory. 
In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
Our notation is $q,\Tilde{q}$ for elements of the vector spaces $V, \Bar{V}$ and $m\in Z$.
The magnetic theory is
\[
\cT_{\sfM} (N_c, N_f) \define \cT\big(\SU(N_f - N_c) \, , \, (\CC^{N_f - N_c})^{\oplus N_f} \, , \, \CC^{\oplus N^2_f} \, , \, W = m q \Tilde{q} \big)
\]
In the definition of $W = m q \Tilde{q}$ we are using the natural contractions which we can describe explicitly as follows.
Choose a basis $\{q_a^i\}$ for $V = (\CC^{N_f - N_c})^{\oplus N_f}$, $a = 1,\ldots, N_f - N_c$, $i=1,\ldots N_f$ and a dual basis $\{\Tilde{q}_i^a\}$ for $\Bar{V}$.
Also, let $\{m_i^j\}$ be a basis for $\CC^{\oplus N_f^2}$. 
Then the cubic polynomial $W$ is
\[
W = \sum_{i,j,a} m^i_j q_i^a \Tilde{q}^i_a .
\]

\begin{thm}
Both $\cT_{\sfE}(N_c, N_f)$ and $\cT_{\sfM}(N_c, N_f)$ exist at the quantum level. 
That is, the anomaly to a perturbative BV quantization vanishes.
In fact, the quantization is one-loop exact. 
\end{thm}

\begin{conj}
There is an equivalence of $2$-dimensional holomorphic factorization algebras
\[
\Obs_{\sfE}(N_f, N_c) \simeq \Obs_{\sfM} (N_f, N_c)  .
\]
\end{conj}

The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$ graded.
We fix some notation for the fields of the electric and magnetic theories. 
The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$.

With respect to a basis for $\CC^{N_f}$ we denote the matter fields of the electric theory as
\[
Q^i\; , \; P_i \; , \; \Tilde{Q}_i \; , \; \Tilde{P}^i , \quad i = 1, \ldots, N_f.
\]
Each of these fields are Dolbeault forms that are valued in the fundamental $\SU(N_c)$ representation.

The matter fields of the magnetic theory will be denoted by lower case letters to avoid confusion
\[
q^i\; , \; p_i \; , \; \Tilde{q}_i \; , \; \Tilde{p}^i , \quad i = 1, \ldots, N_f.
\]
Again, each of these fields are Dolbeault valued but this time they each transform under the fundamental $\SU(N_f-N_c)$ representation. 
On the magnetic side one also has the `meson' fields $M_{i}^j$, which are scalars under the gauge group.

\subsubsection{Flavor symmetries}

Holomorphic QCD enjoys a few familiar holomorphic symmetries in the style that we discussed in this note.

The first is a holomorphic `flavor' symmetry, which will manifest itself as a symmetry by the $2$-dimensional holomorphic current algebra. 
Consider the Lie algebra $\sl(N_f)$.

The holomorphic background field $\fa = (\fa_i^j) \in \Omega^{0,\bu}(\CC^2 , \sl(N_f))$ naturally couples to both the electric and magnetic theory in the following ways:
\[
I^F_\sfE = \int P_j \fa_i^j Q^i , \qquad I^F_\sfM = \int \Tilde{p}_j \sfa_j^i \Tilde{q}^j + \int L^k_j \sfa_i^j M^i_k . 
\]

This determines a classical symmetry of both sides of the duality by the local Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(N_f))$. 
In particular, the two state spaces form a module for the $S^3$-current algebra $\sfA_2 \otimes \sl(N_f)$ at the classical level.
A natural question is whether this symmetry persists at the quantum level. 
The answer is {\em yes}, but on both sides of the duality one must take into account central extensions.
These central extensions give rise to symmetries by higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ which act on the electric and magnetic sides, respectively.
Here $\theta_\sfE, \theta_\sfM$ are invariant cubic polynomials on the Lie algebra $\sl(N_f)$.

\begin{prop}
The central extensions of the dual theories agree $\theta_\sfE = \theta_\sfM$. 
In particular, the state spaces $\sfV_\sfE, \sfV_\sfM$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(N_f)}_{2,\theta}$.
\end{prop}

\begin{proof}[Sketch of proof]
This boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section \ref{sec:renorm}. 
For this calculation the gauge algebra $\sl(N_c)$ plays a minimal role. 
The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by the background gauge field $\sfa$.

In the electric case there are $N_c$ of such diagrams, all the internal edges are labeled by $Q-P$ propagators. 
This gives rise to the local anomaly
\beqn\label{eqn:electricflavor}
N_c \frac16 \int \op{tr}_{N_f} \left(\sfa \partial \sfa \partial \sfa\right) 
\eeqn
where $\op{tr}_{N_f}$ denotes the trace in the fundamental $\sl(N_f)$-representation.

The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: (a) those with 
internal edges labeled by $\Tilde{q}-\Tilde{p}$ propagators and (b) those will internal edges labeled by $M-L$ propagators. 
There are $(N_f - N_c)$ copies of diagram (a) which gives rise to the term
\[
(N_f - N_c) \frac16 \int \op{tr}_{\Bar{N_f}} \left(\sfa \partial \sfa \partial \sfa\right) .
\]
Here, $\op{tr}_{\Bar{N_f}}$ denotes the trace in the anti-fundamental representation. 
There are $N_f$ copies of diagram (b) which gives rise to the term
\[
N_f \frac16\int \op{tr}_{N_f} \left(\sfa \partial \sfa \partial \sfa\right) 
\]
Since $\op{tr}_{\Bar{N_f}} (X^3) = - \op{tr}_{N_f} (X^3)$ for any $X \in \sl(N_f)$, we see that the sum of these two terms agrees with the electric side \eqref{eqn:electricflavor}.
\end{proof}

There is also a `tilded' version of the flavor symmetry for the same Lie algebra $\sl(N_f)$ but where the local Noether currents read $\int \Tilde{P}^i \Tilde{\sfa}_i^j \Tilde{Q}^i$ and $\int \Tilde{p}^i \Tilde{\sfa}_i^j \Tilde{q}^i$.
An analogous result holds for this symmetry.

\subsubsection{Twisted superconformal symmetry}

The physical statement of Seiberg duality is that dual theories flow to the same superconformal fixed point in the infrared limit. 
This only makes sense when the integers $N_c,N_f$ satisfy appropriate bounds ensuring that such a superconformal fixed point exists.

We will describe how this `superconformal window'--the bounds where one expects such flows to exist--appears from the point of view of holomorphic QCD.

We start off with the (complexified) 4d $\cN=1$ superconformal algebra $\sl(4|1)$.
This super Lie algebra is the defining symmetry of a 4d $\cN=1$ superconformal field theory. 
The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
Inside of this algebra is the Cartan generator $\Delta$ of scaling transformations in $\RR^4$.

Fix a nonzero square-zero supercharge $\cQ$. 
Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
In \cite{SWsuco} the second author and Saberi show that there is a quasi-isomorphism of dg Lie algebras
\[
\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) .
\]
Thus, if one starts with a superconformal theory, one knows that at the level of the holomorphic twist the Lie algebra $\sl(3)$ will act.  
In this sense, $\sl(3)$ is the `residual' superconformal symmetry at the level of the twist. 
Inside of this twisted algebra $\sl(3)$ we have the ``holomorphic scaling'' operator $\Delta^{hol} = z_i \partial_{z_i}$, which is simply the holomorphic Euler vector field.  
In fact, the entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$.\footnote{Endowed by the description of $\CC \PP^2$ as an ${\rm SL}(3)$-homogenous space.}
Classically in the holomorphic twist this symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.

\begin{thm}[\cite{SWsuco}] \label{thm:swsuco}
Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ which resolves the Lie algebra of \ul{all} holomorphic vector fields on $\CC^2$. 
This local Lie algebra is a classical symmetry of any theory of holomorphic QCD. 
\end{thm}

We ask when this classical symmetry persists at the quantum level. 
Let us first consider the electric theory.

Naively, the symmetry of holomorphic vector fields is obvious: all fields are described in terms of a Dolbeault complex resolving trivial holomorphic vector bundles of various ranks. 
Therefore, holomorphic vector fields act naturally by Lie derivative everywhere. 
In particular, the Euler vector field $\Delta^{hol}$ acts diagonally in the natural way.

On the gauge fields, this naive action is consistent with the one present in the untwisted theory. 
For the matter fields, however, the action at the untwisted level is {\em not} compatible with this naive one. 
This can even be seen at the level of the holomorphic Euler vector field: naively the field $Q = z_1^n z_2^m \otimes v \in \Omega^0 (\CC^2$ transforms like $\Delta^{hol}(Q) = (n+m) Q$.
However, to be compatible with dimension scaling in the untwisted theory one actually has 
\[
\Delta^{hol}(Q) = \left(n + m + \frac23\right) Q .
\]
What this says is that as a representation for infinitesimal holomorphic diffeomorphisms the fields $Q, P$ do not take values in the trivial vector bundle, but actually take values in some line bundle.  
In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of \cite{WittenTwist} one finds that the $\beta\gamma$ matter fields live in
\[
Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes (\CC^{N_c})^{\oplus N_f} , \quad P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes (\CC^{N_c})^{\oplus N_f}
\]
and similarly for $\Tilde{Q}, \Tilde{P}$.

\begin{prop}
Consider the symmetry of the electric and magnetic theories $\cT_{\sfE / \sfM}(N_c,N_f)$ by the local Lie algebra of holomorphic vector fields described by Theorem \ref{thm:swsuco}. 
There is an anomaly for this symmetry to exist at the quantum level and it is proportional to the local functional
\[
\left(N_f - 3N_c\right) \frac12 \int \partial_{z_i} X_i \op{Tr} (\partial A \partial A)  .
\]
where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form valued vector field and $A$ is a gauge field.
\end{prop}

In particular, for the {\em same value} $N_f = 3 N_c$ both the electric and magnetic theories are endowed with an action by holomorphic vector fields at the quantum level.

\end{document}

### 2022-07-10 draft.tex
added dedication title and some minor reminders

@@
 \date{\today}
-%\title{Part I}
+\title{Holomorphic field theories and higher algebra}
 
@@
 \begin{document}
-%\maketitle
+
+\dedicatory{To Yuri Manin, with great admiration.}
+
+\maketitle
+
+\owen{mention some history (e.g., Manin!) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
 
@@
 \subsection{Examples from supersymmetric field theories}
+
+\owen{Revise to explain SYM as source for some examples above, but also add brief discussions of newer examples like twisted SUGRA and exotic super Lie algebras}
 
@@
 
-\subsection{Background}
+\owen{More examples}
+
+\begin{itemize}
+\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
+For instance, the closed string field theory of the topological B-model is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
+This theory is defined on any Calabi--Yau manifold. 
+The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.  
+\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
+Often, the theory you start with on the nilpotence variety is holomorphic \cite{SWpure}. 
+\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
+For instance, holomorphic BF theory on twistor space associated to $\RR^4$ is equivalent to a self-dual limit of Yang--Mills theory. 
+\end{itemize}
+
+\subsection{An extended aside on perturbative quantization}
+
+\owen{Sketch Brian's main results --- and Si's! --- and compare them with configuration space method of A-S and K for TFTs, subsequently developed by others}
 
@@
 they have shown how important invariants (notably the ``supersymmetric index") of the untwisted, supersymmetric theory can be computed simply in the holomorphic twist.
-
-\subsection{More examples of holomorphic field theories}
-
-\begin{itemize}
-\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
-For instance, the closed string field theory of the topological B-model is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
-This theory is defined on any Calabi--Yau manifold. 
-The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.  
-\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
-Often, the theory you start with on the nilpotence variety is holomorphic \cite{SWpure}. 
-\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
-For instance, holomorphic BF theory on twistor space associated to $\RR^4$ is equivalent to a self-dual limit of Yang--Mills theory. 
-\end{itemize}
 
@@
 
-\section{Vista: Holomorphic $\sigma$-models and higher algebras of differential operators}
+\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and free field realization}
 

### 2022-07-10 draft.tex
small edits

@@
 \maketitle
+\tableofcontents
 
@@
 
-The most important field theories in physics involve a metric on a manifold (whether Riemannian or Lorentzian), and hence geometry has had a clear role in physics.
+The most important field theories in physics involve a metric on a manifold (whether Riemannian or Lorentzian), and hence geometry has long had a clear role in physics.
 In recent decades attention has expanded to include {\em topological} field theories (or TFTs), 
@@
 just as complex variables is a particularly beautiful wing of analysis.
-In essence, such {\em holomorphic} field theories have variational PDE (or ``equations of motion'') that are holomorphic:
+In essence, such {\em holomorphic} field theories have variational partial differential equations (i.e., ``equations of motion'') that are holomorphic:
 the PDE only involves derivatives in the holomorphic coordinates (i.e., the $\partial/\partial z_j$) and has holomorphic coefficients.
@@
 
-\subsection{Examples from physics}
+\subsection{Examples}
+
+\owen{Mention main classes of field theories (scalar and sigma models, fermions as matter, gauge theories for ``forces'', gravity, and their combinations) and how there are holomorphic analogs}
+
+In traditional physics there are a few basic types of field theories, 
+and they can be assembled into combinations in natural ways,
+of which the Standard Model offers a nice example.
+The basic types are\footnote{For the experts, we remark that we focus above on the core field content, and ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
+\begin{itemize}
+\item {\em Scalar} field theories where the fields are maps from $M$ to a vector space $V$, or natural generalizations like taking sections of a vector bundle $V \to M$.
+The Higgs boson appears as part of a scalar field theory.
+\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space or, typically, a section of a spinor bundle.
+Such theories are often used to describe matter, such as electron fields.
+\item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
+\item $\sigma$-models where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
+\item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
+\end{itemize}
+The Standard Model involves the first three types,
+and the different fields interact in intricate ways.
+
+There are holomorphic versions of all these basic types, 
+and we now spell out some simple examples.
+To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
+we describe them in several ways: 
+in terms of PDE and action functionals but also as moduli spaces.
+We do not offer a thorough justification of the dictionary, for which see \owen{cite who?}
+
+For an example that mixes several types and that is a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks,
+see Section~\ref{sec: seiberg}.
+One motivation for us to explore holomorphic field theories is that one can translate physical insights and conjectures (such as Seiberg duality) into surprising predictions in the holomorphic setting,
+which is typically much cleaner and more accessible.
+(One might also hope that progress in the holomorphic setting then feeds back useful insights to physics.)
+
+\subsubsection{Holomorphic scalar field theories}
+
+% beta gamma systems
+
+\subsubsection{Holomorphic fermionic field theories}
+
+% bc systems
+
+\subsubsection{Holomorphic gauge theories}
+
+% BF and CS
+
+\subsubsection{Holomorphic $\sigma$-models}
+
+% curved beta gamma
+
+\subsubsection{Holomorphic gravity}
+
+% Kodaira-Spencer
+
+\subsection{Examples from supersymmetric field theories}
+
 %this section aimed at physicists
@@
 %Owen has some nice thoughts about globalization as it related to SUSY/THF.
-
-\owen{Mention main classes of field theories (scalar and sigma models, fermions as matter, gauge theories for ``forces'', gravity, and their combinations) and how there are holomorphic analogs}
-
-\subsection{Examples from supersymmetric field theories}
 
@@
 \section{Vista: Seiberg duality and its consequences}
+\label{sec: seiberg}
 

### 2022-07-11 draft.tex
added subsections to fill in

@@
 which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
+As a somewhat mundane example, let $\RR\Hol(X,V)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $V$.
+(For $V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
+One can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
+and this derived moduli space encodes solutions to
+a theory known as the $\beta\gamma$ system with target $V$.
+(The name is silly: it's due to the original notation people used.)
+Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
 Other classes of examples are afforded by holomorphic variants of familiar AKSZ $\sigma$-models; the relevant moduli space being the derived mapping space between complex manifolds.
@@
 \owen{Discuss modules?}
+
+\subsection{Reduction vs chiralization}
+
+\owen{We should introduce the idea here and revisit later}
 
@@
 
+\subsection{Toric (KK) reduction vs. chiralization}
+
+\owen{revisit this theme, and discuss the "modes" algebra}
+
+\subsection{Operator product expansion and holomorphic Poisson algebras}
+
+\owen{discuss OPE and explain the shifted Poisson structure}
+
 \section{Holomorphic $\sigma$-models, higher algebras of differential operators, and free field realization}

### 2022-07-15 draft.tex
revisions of seiberg section

@@
 
-\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and free field realization}
+\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and higher free field realization}
+
+\owen{We should also discuss how these can reduce to LG B-models, as precursor to the Hori-Tong dualities.}
 
@@
 
-The field content of 4d $\cN=1$ supersymmetric Yang--Mills theory is:
+A major endeavor in theoretical physics is to develop a deep and effective understanding of theories like quantum chromodynamics (QCD), which governs the behavior of quarks and gluons.
+One natural approach is to study theories that are close cousins but that are easier to analyze,
+and a notable way is to look for theories with the same ingredients but with larger groups of symmetries.
+Supersymmetric Yang--Mills theories are quite appealing in this regard,
+and there have been remarkable successes in this direction.
+A well-known high point is the work of Seiberg and Witten on 4-dimensional $\cN =2$ supersymmetric Yang--Mills theory,
+where they explained how confinement could be realized by a version of the Mandelstam-'t Hooft mechanism (i.e., a kind of electromagnetic duality identifies confinement with a Meissner-type effect).
+Their work offered powerful new tools that opened up much subsequent progress,
+and even impacted mathematics through the Seiberg-Witten equations (which is related to the topologically twisted versions of $\cN=2$ theory).
+
+The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
+There too Seiberg offered inspiring and powerful insights typically referred to as {\em Seiberg duality}.
+These ideas have had a large impact in theoretical physics \owen{give the citation number on that paper},
+but the impact in mathematics is much more muted,
+possibly due to the lack of a topological twist of $\cN=1$ theories.
+Such theories do admit {\em holomorphic} twists, however, 
+and so we explore here what holomorphic Seiberg duality might mean and what its consequences could be in mathematics.
+In our opinion this direction could be quite fruitful and we welcome others to join us in exploring it.
+
+We begin this section by describing the holomorphic twist of $\cN=1$ supersymmetric Yang--Mills theory,
+and then we offer a holomorphic version of Seiberg duality, 
+initially conjectured by Richard Eager.
+We explain our first efforts in this direction and how it offers evidence for the conjecture;
+we then refine Eager's version.
+We also explain how this duality, when compactified along Riemann surfaces,
+should produce equivalences between different kinds of 2-dimensional B-model theories;
+these reductions are related to work of Hori and Hori--Tong \owen{citations} and its mathematical development by Ed Segal, \owen{list others}.
+
+\subsection{Holomorphic QCD}
+
+The field content of 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory is:
 \begin{itemize}
@@
 
-From hereon we fix a nonzero, square zero supercharge of the 4d $\cN=1$ supersymmetry algebra for which we wish to twist by. 
-The twist of 4d $\cN=1$ supersymmetric Yang--Mills theory has been characterized in \cite{CosYangian, ESW, SWchar}. 
+From hereon we fix a nonzero, square zero supercharge of the 4-dimensional $\cN=1$ supersymmetry algebra for which we wish to twist by. 
+The twist of 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory has been characterized in \cite{CosYangian, ESW, SWchar}. 
 It is a holomorphic field theory on $\CC^2$ consisting of a `vector' part and a 'matter' part.
@@
 
-Our long term goal is to show that two special cases of holomorphic QCD are {\em dual}.
+\subsection{A first pass at Seiberg duality}
+
+Our long-term goal is to show that two special cases of holomorphic QCD are {\em dual}.
+The notion of duality can refer to several kinds of relationships,
+but loosely speaking it means that some aspects of the two theories are equivalent under some dictionary or correspondence.
+We will postpone saying something precise till we have some terminology in place.
+
 We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
-Following physics terminology, will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
-Also, suppose $N_c, N_f$ are integers with $N_f \geq N_c \geq 2$.
+Following physics terminology, we will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
+Also, let $N_c, N_f$ denote integers where $N_f \geq N_c \geq 2$.
 %Also, let $N_{\rm mes} \geq 0$ be some integer.  
@@
 
+The usual Seiberg duality states how certain ``electric'' and ``magnetic'' versions of SQCD ($\cN=1$ supersymmetric QCD) should be equivalent.
+Our electric and magnetic holomorphic QCDs are precisely the holomorphic twists of those that appear in Seiberg duality.
+In \cite{Eager} Richard Eager suggested that Seiberg duality should survive after taking the holomorphic twist.
+
+\begin{conj}
+There is an equivalence of $2$-dimensional holomorphic factorization algebras
+\[
+\Obs_{\sfE}(N_f, N_c) \simeq \Obs_{\sfM} (N_f, N_c)  .
+\]
+\end{conj}
+
+The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$-graded.
+
+One appealing aspect of Eager's conjecture is that it is mathematically precise:
+duality would mean giving an equivalence of factorization algebras.
+It is analogous to claiming that two vertex algebras are equivalent,
+such as in the well-known boson-fermion correspondence.
+In this sense it is a target at which a mathematician can aim,
+rather than the more amorphous statements of duality that one often finds in the physics literature.
+In that literature, however, there is guidance on what map of factorization algebras provides the equivalence,
+which we describe in the next section.
+
+In general, Eager's suggestion opens up a fascinating vein of inquiry:
+\begin{quote}
+how do physical results about supersymmetric gauge theories behave under twisting?
+\end{quote}
+We have found, so far, that they often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
+In \cite{EGW} we and Chris Elliott explored twists of $\cN=4$ supersymmetric Yang--Mills theory,
+provided their quantizations, and began analyzing their factorization algebras.
+Following Eager, we can ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
+
+\subsection{Evidence for holomorphic Seiberg duality}
+
+We now turn to examining evidence for the conjecture, which will, in turn, allow us to refine it.
+The first piece of evidence involves the classical field theories:
+\begin{quote}
+$\bullet$ Each theory has a moduli stack of vacua, and there is a natural isomorphism between \owen{the affinizations?} the spaces for theories dual according to the conjecture.
+\end{quote}
+This map of stacks determines a map of factorization algebras of classical observables,
+and it should deform to the map between the factorization algebras for the quantum theories.
+As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{BW work}.
+There are then two further pieces of evidence when these quantum theories are examined:
+\begin{enumerate}
+\item There are {\em flavor} symmetries that act on each theory, and these can be matched under the duality. Under quantization, these have isomorphic anomalies.
+\item There are {\em spacetime} symmetries that act on each theory, notably isometries, and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields.
+Under quantization, these have isomorphic anomalies.
+\end{enumerate}
+This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
+We now turn to fleshing out the assertions above.
+
+\subsubsection{Moduli of vacua and quantization}
+
+It is fruitful, and standard in physics, to identify the simplest solutions to the equations of motion for a theory.
+Here that means a solution that is translation-invariant on $\CC^2$ (i.e., a constant solution),
+and we call such a solution a {\em classical vacuum}.
+Thus each theory has an associated {\em moduli space of classical vacua},
+which we describe in the next subsection.
+Each vacuum determines a perturbative field theory that one could try to quantize,
+and we have shown the following.
+(Many arguments are close cousins of~\cite{EGW}, where we quantize every twist over a moduli of vacua of the $\cN=4$ supersymmetric Yang--Mills theory.)
+
 \begin{thm}
-Both $\cT_{\sfE}(N_c, N_f)$ and $\cT_{\sfM}(N_c, N_f)$ exist at the quantum level. 
+Both $\cT_{\sfE}(N_c, N_f)$ and $\cT_{\sfM}(N_c, N_f)$ exist at the quantum level for any choice of classical vacuum. 
 That is, the anomaly to a perturbative BV quantization vanishes.
@@
 
-\begin{conj}
-There is an equivalence of $2$-dimensional holomorphic factorization algebras
-\[
-\Obs_{\sfE}(N_f, N_c) \simeq \Obs_{\sfM} (N_f, N_c)  .
-\]
-\end{conj}
-
-The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$ graded.
+\subsubsection{Flavor symmetries}
+
 We fix some notation for the fields of the electric and magnetic theories. 
@@
 On the magnetic side one also has the `meson' fields $M_{i}^j$, which are scalars under the gauge group.
-
-\subsubsection{Flavor symmetries}
 
@@
 
-We start off with the (complexified) 4d $\cN=1$ superconformal algebra $\sl(4|1)$.
-This super Lie algebra is the defining symmetry of a 4d $\cN=1$ superconformal field theory. 
+We start off with the (complexified) 4-dimensional $\cN=1$ superconformal algebra $\sl(4|1)$.
+This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
 The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
@@
 
+\subsection{A second pass at holomorphic Seiberg duality, and its relations to Hori-Tong duality}
+
 \end{document}

### 2022-08-12 draft.tex
section 1

@@
 
-\spacing{1.25}
+\spacing{1.1}
 
@@
 \def\sfa{\mathsf{a}}
+\def\del{\partial}
+\def\til{\Tilde}
 
@@
 \owen{Notation to explain: dg = differential graded, PDE = partial differential equations}
+
+\brian{we need to make sure to cite nekrasov}
 
@@
 A well-known example is holomorphic Chern-Simons theory,
-which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
-As a somewhat mundane example, let $\RR\Hol(X,V)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $V$.
-(For $V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
+which lives on a Calabi-Yau 3-fold~$X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on~$X$.
+As a somewhat mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
+(For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
 One can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
@@
 even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
-As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by $\RR \Bun_G(X)$.
+As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.
 It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one,
@@
 
-As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), holomorphic field theories appear as chiral conformal field theories (CFTs) on 2-dimensional manifolds --- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- and have had a strong impact in mathematics.
+As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), holomorphic field theories appear as chiral conformal field theories (CFTs) on two-dimensional manifolds --- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- and have had a strong impact in mathematics.
 It is natural to explore higher-dimensional analogs.
@@
 
-%complex geometry, dolbeault, dg stuff.
+A theory is usually described, in part, in terms of a space of fields which comprise some possibly nonlinear space like a mapping space or the space of connections. 
+In perturbative field theory, which describes the formal neighborhood of the theory at points in such spaces, the fields $\Phi$ are typically described by the smooth sections of a bundle on spacetime.
+The equations of motion which dictate the dynamics of the particular model are encoded by a partial differential equation heuristically of the form 
+\[
+\sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
+\]
+where $D_k$ is a $k$-ary polydifferential operator.
+As an example of a Euclidean theory, the $\phi^4$-theory on a Riemannian four-manifold $M$ is described by the equation
+\[
+\Delta \phi + \frac{1}{3!} \phi^3 = 0 
+\]
+where $\Phi = \phi$ is simply a smooth function on $M$.
+
+In a {\em holomorphic theory} one starts with a complex manifold $X$ as the spacetime.
+This means, in part, that the complexified tangent bundle of $X$ decomposes as a sum of vector bundles $\T_X \oplus \Bar{\T}_X$ where $\T_X$ (respectively $\Bar{T}_X$) is the holomorphic (respectively anti-holomorphic) tangent bundle.
+In local coordinates sections of $\T_X$ have the form $f^i \del / \del z_i$ whereas sections of $\Bar{\T}_X$ have the form $f^i \del / \del \zbar_i$.
+
+Globally, holomorphic theories are described like in the usual case by mapping spaces or spaces of connections.
+The key feature in a holomorphic theory is that the equations of motion dictate that fields be holomorphic.
+Perturbatively, where fields are sections of some holomorphic vector bundle $V$, we can make this precise. 
+Prescribing a holomorphic structure on a vector bundle $V$ is equivalent to the data of a $\dbar$-operator
+\beqn
+\dbar \colon \Omega^{0,q}(X, V) \to \Omega^{0,q+1}(X,V) 
+\eeqn
+where $\Omega^{0,q}(X,V)$ is the space of smooth sections of the vector bundle $\wedge^q\Bar{T}_X^* \otimes V$. 
+Holomorphicity of $V$ boils down to the requirement that $\dbar \circ \dbar = 0$.
+The Dolbeault complex of $V$ is the resulting complex $(\Omega^{0,\bu}(X, V), \dbar)$ where $\Omega^{0,q}(X,V)$ sits in degree $+q$.
+A standard result in complex geometry is that the Dolbeault complex is a resolution for the sheaf of holomorphic sections of the holomorphic vector bundle $V$.
+In the case that $V$ is the trivial bundle $\ul{\CC}$ the Dolbeault complex $\Omega^{0,\bu}(X)$ is a resolution for the sheaf of holomorphic functions on $X$.
+
+The fields of a holomorphic theory are given by elements of the Dolbeault complex $\Omega^{0,\bu}(X,V)$.
+The equations of motion in a holomorphic theory take the form
+\beqn
+\dbar \Phi + \sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
+\eeqn
+where $D_k$ are $k$-ary {\em holomorphic} polydifferential operators.
+This means that in local coordinates $D_k$ only depend on the holomorphic coordinates $\{z_i\}$ and involve only holomorphic derivatives $\del / \del z_i$.
 
@@
 which we have already said describes the moduli space of Maurer--Cartan elements describe deformations of the trivial holomorphic $G$-bundle. 
-When $X$ is a Calabi--Yau three-fold and $\fg$ is equipped with an invariant pairing, 
+When $X$ is a Calabi--Yau three-fold and $\fg$ is equipped with an invariant pairing $\<\cdot , \cdot \>$, 
 this formal moduli space has a very special property: 
 it arises from the variational problem of an action functional, namely
-\[
+\beqn
 S = \int_X \Omega \wedge {\rm CS}(A) 
-\]
-where $\Omega$ is the holomorphic volume form and ${\rm CS}(A)$ is the Chern--Simons Lagrangian for the connection $(0,1)$-form $A$.
+\eeqn
+where $\Omega$ is the holomorphic volume form and 
+\beqn
+{\rm CS}(A) = \frac12 \< A ,\d A \> + \frac16 \<A , [A,A]\>
+\eeqn
+is the Chern--Simons Lagrangian for the connection $(0,1)$-form $A$.
+Notice that due to the presence of the holomorphic volume form $\Omega$ on the $\dbar$ operator contributes to the kinetic term and so the action can be written as 
+\beqn
+S = \int_X \Omega \wedge \left(\frac12 \< A ,\dbar A \> + \frac16 \<A , [A,A]\>\right) .
+\eeqn
 
@@
 \subsection{Examples}
-
-\owen{Mention main classes of field theories (scalar and sigma models, fermions as matter, gauge theories for ``forces'', gravity, and their combinations) and how there are holomorphic analogs}
 
@@
 
-% beta gamma systems
-
-\subsubsection{Holomorphic fermionic field theories}
-
-% bc systems
+The most elementary holomorphic field theory is a generalization of the so-called `$\beta\gamma$ system' which is primarily studied in the context of string theory.
+The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on $X$.
+The fields of the theory consist of pairs 
+\begin{align*}
+\gamma & \in \Gamma(X,V)\\
+\beta & \in \Omega^{n,n-1}(X,V^*) .
+\end{align*}
+The action functional is 
+\beqn
+\int_X \beta \wedge \dbar \gamma 
+\eeqn
+which utilizes the natural pairing between $V$ and $V^*$. 
+The theory is free, just like the ordinary $\beta\gamma$ system on Riemann surfaces.
+
+Notice that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
+\beqn
+\beta \mapsto \beta + \dbar \eta , \quad \eta \in \Omega^{n,n-2}(X,V^*)
+\eeqn
+For this model to be well-posed at the quantum level we must include the ghosts $\eta$.
+Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
 
@@
 
-% BF and CS
+We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
+There is a related holomorphic gauge theory which is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure.
+
+If $n$ is the complex dimension of $X$, the fields consist of pairs $(A,B)$ where $A$ is a $(0,1)$ connection on a principal $G$-bundle $P \to X$ and
+\beqn
+B \in \Omega^{n,n-2}(X, \fg_P^*) ,
+\eeqn
+where $\fg_P$ is the adjoint bundle of $P$. 
+The action functional is 
+\beqn
+S(A,B) = \int_X B \wedge F_A 
+\eeqn
+where $F_A$ is the curvature of the connection $A$.
+From this formula, it is clear that the model we are describing is a holomorphic analog of topological $BF$ theory. 
+Notice that by form types this action can be written as
+\beqn
+S(A,B) = \int_X B \wedge \left(\dbar A + \frac12 [A,A] \right) .
+\eeqn
 
@@
 
-% curved beta gamma
+If $X,Y$ are any two complex manifolds there is a theory whose fields consist, in part, of the derived moduli space of smooth maps $\RR {\rm Map}(X,Y)$ and whose equations of motion dictate that such maps be holomorphic.
+This is a nonlinear generalization of the $\beta\gamma$ system we just introduced.
+
+The precise space of fields, in cohomological degree zero, consist of pairs $(\gamma, \beta)$ where $\gamma \colon X \to Y$ is a smooth map and 
+\[
+\beta \in \Omega^{n,n-1}(X, f^* \T^*_Y) 
+\]
+where $\T^*_Y$ is the holomorphic cotangent bundle of $Y$. 
+The action functional is the familiar one
+\beqn
+\int_X \beta \dbar \gamma .
+\eeqn
 
@@
 
-% Kodaira-Spencer
-
-\subsection{Examples from supersymmetric field theories}
+Perturbatively, any model of gravity describes, in part, deformations of the moduli space of metric structures on a given manifold. 
+There is a holomorphic avatar of this which describes deformations of complex structure.
+The fields consist of pairs $(\mu, \eta)$ where
+\begin{align*}
+\mu & \in \Omega^{0,1}(X, \T_X) \\
+\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
+\end{align*}
+The action functional is
+\beqn
+\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
+\eeqn
+where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.
+
+In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
+Let $X$ be a complex threefold equipped with a Calabi--Yau structure where we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
+Kodaira--Spencer theory is the holomorphic theory whose fields consist of $(0,1)$ forms on $X$ with values in the holomorphic tangent bundle $\T_X$
+\beqn
+\mu \in \Omega^{0,1}(X,\T_X) .
+\eeqn 
+A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
+The action functional is very similar to the Chern--Simons action
+\beqn
+S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
+\eeqn
+The integrand is not defined globally.
+In the integral we use the Calabi--Yau form to identify the integrand with 
+\brian{finish}
+
+\subsection{Local version and examples from supersymmetric field theories}
 
@@
 
-\owen{Revise to explain SYM as source for some examples above, but also add brief discussions of newer examples like twisted SUGRA and exotic super Lie algebras}
+There is the following local characterization of a holomorphic field theory which allows us to connect directly to supersymmetric field theories. 
+Suppose that our spacetime is $\CC^n = \RR^{2n}$ and assume that the theory we are considering is translation invariant, meaning that there is an action buy the $2n$-dimensional Lie algebra spanned by the vector fields $\del / \del {z_i}, \del / \del {\zbar_i}$ for $i=1,\ldots,n$.
+In a holomorphic theory we require that the anti-holomorphic vector fields $\del / \del {\zbar_i}$ act homotopically trivial. 
+In the derived world this is prescribed by the data of homotopy trivializations for such vector fields.
 
@@
 and this Lie bracket is defined in terms of a $\mathfrak{so}(d)$-equivariant non-degenerate symmetric pairing
-\[
-\Gamma : {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
-\]
+\beqn
+\label{e:Gamma}
+\Gamma \colon {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
+\eeqn
 by the formula $[Q, Q'] = \Gamma(Q, Q')$.
@@
 These twisted theories are analogs of BF theory and Chern--Simons theory, so long as one includes purely topological and purely holomorphic theories.
-We will describe a few examples in detail in the BV formalism in Section~\ref{sec:twistedsusybv},
-but we want to indicate now what our main theorem implies about some interesting examples.
-
-For our purposes here, a crucial property of a twist $Q$ is the dimension $k_Q$ of its image ${\rm Im} \; \Gamma(Q, \cdot) \subset \RR^d$,
-which we call the number of {\em invariant} directions of~$Q$.
-By the non-degeneracy of the pairing $\Gamma$, it follows that $k_Q \geq \frac{d}{2}$.
-If the number of invariant directions is maximal with $k_Q = d$, then the twisted theory $\cT^Q$ is purely topological. 
-If the number of invariant directions is minimal with $k_Q = \frac{d}{2}$, then the twisted theory $\cT^Q$ is purely holomorphic.
+In even dimensions $d = 2n$, basic properties of the supersymmetry algebra guarantee that there exists a twist rendering the theory holomorphic.\footnote{This fails in one example where the dimension and amount of supersymmetry is too small, namely for $\cN=(1,0)$ supersymmetry in two dimensions.}
+Indeed, so long as a twisted supercharge is nonzero $Q \ne 0$ one see that the image of the map $[Q,-] = \Gamma(Q,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
+A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly $n$ and we declare the the image of $Q$ is spanned by the anti-holomorphic vector fields $\{\del / \del \zbar_i\}$.
+This fits with the local characterization mentioned at the beginning of the subsection since in this case there exists homotopies $\{\eta_i\}$ with the property that 
+\beqn
+[Q,\eta_i] = \frac{\del}{\del \zbar_i} .
+\eeqn
+
+%For our purposes here, a crucial property of a twist $Q$ is the dimension $k_Q$ of its image ${\rm Im} \; \Gamma(Q, \cdot) \subset \RR^d$,
+%which we call the number of {\em invariant} directions of~$Q$.
+%By the non-degeneracy of the pairing $\Gamma$, it follows that $k_Q \geq \frac{d}{2}$.
+%If the number of invariant directions is maximal with $k_Q = d$, then the twisted theory $\cT^Q$ is purely topological. 
+%If the number of invariant directions is minimal with $k_Q = \frac{d}{2}$, then the twisted theory $\cT^Q$ is purely holomorphic.
 
 As a representative example of how twisting behaves, 
-consider four-dimensional supersymmetric Yang--Mills theory with $\cN=2$ supersymmetry,
-which means the odd part $\ft^1$ is eight-dimensional. 
+consider pure four-dimensional supersymmetric Yang--Mills theory with $\cN=1$ supersymmetry.
+The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional and there exists a unique holomorphic twist $Q$ up to equivalence. 
 %The sum of two copies of the spin representations.
 %\owen{Did I get that right?}
-We only consider here the pure gauge theory with Lie algebra~$\fg$. 
-Then we have the bounds $2 \leq k_Q \leq 4$, and each value gives a different, well-known field theory:
-\begin{itemize}
-\item When $k_Q = 4$, the twisted theory is the topological field theory on $\RR^4$ known as {\it Donaldson--Witten theory} \autocite{WittenTQFT};
-\item When $k_Q = 3$, the twisted theory is the THFT studied by Kapustin in \autocite{Kapustin};
-\item When $k_Q = 2$, the twisted theory is holomorphic BF theory on $\CC^2$ with values in a graded Lie algebra $\fg[\ep]$, where $\ep$ is a parameter of cohomological degree~$1$.
-\end{itemize}
-We will describe these theories completely later in Section~\ref{sec:twistedsusybv},
-but our main theorem implies the following.
+
+Then, the holomorphic twist
 
@@
 \owen{We should introduce the idea here and revisit later}
+\brian{Explain dimensional reduction vs compactification.
+From topological AKSZ theory to holomorphic one.}
 

### 2022-08-12 draft.tex
not sure what i did

--- 2022-07-15 draft.tex
@@
 even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
-As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by $\RR \Bun_G(X)$.
+As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to a holomorphic field theory whose moduli space is described, in part, by $\RR \Bun_G(X)$.
 It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one,
@@
 
-%complex geometry, dolbeault, dg stuff.
+\brian{complex geometry, dolbeault, dg stuff.}
 
@@
 
-A key idea for us is that much of the content in field theories --- both classical and quantum --- are captured by factorization algebras.
+\owen{Much of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}
+
+A key idea for us is that much of the content in field theories --- both classical and quantum --- is captured by factorization algebras.
 We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
@@
 
-An algebra over this operad is called an $E_n$-algebra.
+An algebra over this operad is called an {\em $E_n$-algebra}.
 A classic example from topology is given by taking the $n$-fold based loop space
@@
 
+This theorem, together with work in these two books, builds an explicit bridge between topology and physics.
+Topological field theories in the physicist's sense, such as perturbative Chern-Simons theory, produce locally constant factorization algebras, which can then be viewed as $E_n$ algebras and analyzed using the powerful machinery of modern homotopy theory.
+Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology.
+Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.
+
+\begin{rmk}
 We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do.
 A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}.
-We emphasize that higher categories are necessary for a rigorous development of these constructions and comparisons, although we will not emphasize that point in our discussion below, which is expository in nature.
-
-\begin{rmk}
-This theorem, together with our work in these two books, builds an explicit bridge between topology and physics.
-Topological field theories in the physicist's sense, such as perturbative Chern-Simons theory, produce locally constant factorization algebras, which can then be viewed as $E_n$ algebras and analyzed using the powerful machinery of modern homotopy theory.
-Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology.
-Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.~\hfill $\Diamond$
+We emphasize that higher categories are necessary for a rigorous development of these constructions and comparisons, although we will not emphasize that point in our discussion below, which is expository in nature.~\hfill $\Diamond$
 \end{rmk}
@@
 The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
-There too Seiberg offered inspiring and powerful insights typically referred to as {\em Seiberg duality}.
-These ideas have had a large impact in theoretical physics \owen{give the citation number on that paper},
+There too Seiberg offered inspiring and powerful insights,
+and one of his leading contributions is referred to as {\em Seiberg duality}.
+It has had a large impact in theoretical physics \owen{give the citation number on that paper},
 but the impact in mathematics is much more muted,
-possibly due to the lack of a topological twist of $\cN=1$ theories.
+possibly due to the lack of a topological twist for any $\cN=1$ theory.
 Such theories do admit {\em holomorphic} twists, however, 
@@
 Following Eager, we can ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
+\owen{This should be rephrased, and we should mention more people, like Philsang and Surya. We can mention pre-S-duality things (like our work and the EY stuff) and S-duality stuff.}
+
+\owen{Add a remark (?) about Kevin and Si's work on twisted holography and other related directions.}
 
@@
 
+\owen{I want to describe here, at least briefly, what the moduli stack is.
+I'm not sure the stacks are equivalent, but I think they have equivalent affinizations.
+I wonder if we can exhibit an equivalence of the "quantum" affinizations.}
+
 It is fruitful, and standard in physics, to identify the simplest solutions to the equations of motion for a theory.

### 2022-08-19 draft.tex
adding polydiscs section

--- 2022-08-12 draft.tex
@@
 
+\brian{complex geometry, dolbeault, dg stuff.}
+
 A theory is usually described, in part, in terms of a space of fields which comprise some possibly nonlinear space like a mapping space or the space of connections. 
@@
 
+\section{Algebraic structures parametrized by configuration spaces}
+
+Associative algebras arise in quantum mechanics, we have argued, because the spacetime of a mechanical system is a line (``time'').
+If we organize the observables (or operators) by when they happen in time,
+it corresponds to writing them left-to-right as products in an algebra.
+A natural question to ask then is what kind of higher algebraic structure captures how observables behave for theories in higher dimensions?
+The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in Section~\ref{sec fact alg},
+but there are nice answers for two special classes of theories that we will develop now:
+\begin{itemize}
+\item For a topological field theory on $\RR^d$ (which we'll define in a moment),
+the observables form an algebra over the {\em little $d$-disks operad}~$\Disc_d$ (sometimes also known as the $E_d$ operad). 
+Equivalently, one says the observables are an $E_d$-algebra. 
+This notion was introduced by algebraic topologists in the 1960s, 
+so there is a rich body of work to draw upon.
+\item For a holomorphic field theory on $\CC^d$,
+the observables form an algebra over the $d$-polydiscs operad~$\PDisc_d$.
+This notion was introduced only recently in~\cite{CG1}.
+\end{itemize}
+We will make the assertions above precise (in part by adding some natural but necessary hypotheses on a theory)
+and develop them in parallel.
+As a particularly illuminating example, we will explore the $d=1$ case rather closely and explain in what sense a vertex algebra is a kind of ``holomorphic associative algebra.''
+We will also discuss the polydiscs algebras for which the higher Kac-Moody algebras are a Lie-algebraic shadow.
+
+Before jumping into the main story, we mention a motivation for talking about $E_d$- and $\PDisc_d$-algebras in parallel.
+By dealing with both, we are suggesting, of course, that there is a natural analogy and hence a useful transfer of intuition between the settings of topological and holomorphic field theories.
+But there is a stronger, technical relationship that we'll develop via a version of dimensional reduction.
+From each holomorphic field theory in complex dimension $d$, 
+we'll extract an $E_d$-algebra.
+This construction generalizes the relationship between the Kac-Moody vertex algebra of a Lie algebra $\fg$ at level $k$ and the central extension of the loop algebra~$L\fg$.
+We expect this correspondence to bear rich fruit.
+\owen{that metaphor's a bit fruity}
+
+\subsection{Generalizing associative algebras for topological field theories}
+
+We want to describe the algebraic structures that appear in $d$-dimensional topological field theories,
+as a model for holomorphic field theories.
+It will be helpful to use the language of operads, which are an efficient and powerful tool for defining and studying algebraic structures,
+so we will gloss the key ideas of operads briefly and then turn to describing the operads relevant to TFTs.
+A more extensive discussion can be found in \cite{CG1}, with \cite{ES} studying the topological setting in an elegant way.
+
+An associative algebra is, by definition, a vector space $A$ with a linear map $\mu: A\otimes A \to A$ satisfying that the linear map $\mu \circ (\id \otimes \mu): A^{\otimes 3} \to A$ equals the linear map $\mu \circ (\mu \otimes \id)$.
+(Let's ignore the other data and conditions for the moment.)
+Nearly all flavors of algebras --- Lie, Poisson, and so on --- have a similar definition:
+one has a collection of multilinear maps that satisfy some relations.
+An operad is a way of specifying such data, so there is an associative operad $Ass$,
+a Lie operad $Lie$, and so on.
+
+Before sketching the definition, we give a concrete example.
+Let $V$ be a vector space.
+Then every $n$-fold multilinear operator on $V$ is an element of $\Hom(V^{\otimes n}, V)$;
+that vector space parametrizes all possible $n$-ary operations on $V$.
+One can also compose such operations to produce new ones.
+For instance, given $\mu : V^{\otimes m} \to V$ and $\nu: V^{\otimes m} \to V$, we can put the output of $\mu$ into the $i$th input of $\nu$ to produce a new operation
+\[
+\begin{array}{cccc}
+\nu \circ_i \mu: & V^{\otimes m+n-1} & \to & V\\
+& v_1 \otimes \cdots \otimes v_{m+n-1} & \mapsto & \nu(v_1 \otimes \cdots \otimes \mu(v_i, \ldots, v_m), v_{m+1}, \ldots, v_{m+n-1})
+\end{array}
+\]
+\owen{finish the formula! make it agree with conventional formulas}
+where $i$ can run over any index between 1 and $n$.
+We call this collection of data the {\em endomorphism operad of $V$}, denote $\End_V$.
+It consists of 
+\begin{itemize}
+\item a list of vector spaces labelling $n$-ary operations, with 
+\[
+\End_V(n)= \Hom(V^{\otimes n}, V),
+\]
+with $n \in \NN$, and
+\item a list of linear maps
+\[
+\circ_i : \End_V(n) \otimes \End_V(m) \to \End_V(n+m-1)
+\]
+for every pair $n$ and $m$ and where $1 \leq i \leq n$.
+\end{itemize}
+There are certain natural relations when one does multiple compositions, like $\mu \circ_i (\nu \circ_j \pi)$, arising from how multilinear maps compose.
+
+Just as the model case of an associative algebra is $\End(V) = \Hom(V,V)$ (the ring of square matrices),
+the endomorphism operad is the model case of operads.
+A linear operad $P$ consists of a list of vectors $\left(P(n) \right)_{n \in \NN}$, where each $P(n)$ is a vector space describing $n$-ary operations, and a list of linear maps $\left(\circ_i\right)$.
+We will not describe the relations, but resemble those of an endomorphism operad.
+
+\begin{rmk}
+The reader might ask why the adjective {\em linear} was appended before {\em operad}.
+The reason is that we discussed algebraic operations on vector spaces,
+but one can, of course, discuss analogs in other settings.
+For instance, a monoid is a set $M$ with a multiplication map satisfying an associativity constraint.
+One can talk about operads in sets (``an operad in sets $P$ has a set $P(n)$ of $n$-ary operations for every $n \in \NN$ \dots'') or in topological spaces or in dg vector spaces.
+In fact, the theory works in any symmetric monoidal category. 
+For the most part, we will work with vector spaces below.
+\end{rmk}
+
+Let us now raise another useful analogy.
+To define a module for an associative algebra $A$, one specifies an algebra map $\rho: A \to \End(V)$.
+This map encodes how $A$ acts on $V$.
+Similarly, to give an algebra for an operad $P$, one specifies an operad map $\rho: P \to \End_V$.
+This map picks out specific multilinear operations on $V$ that will satisfy the relations we want.
+For instance, if $Pois$ is the Poisson operad, then $Pois(2) \cong \CC^2$ and this vector space is spanned by an element $\cdot$, the commutative product, and $\{\}$, the Poisson bracket.
+Given a $P$-algebra $V$, the map $\rho(2): Pois(2) \to \End_V(2)$ thus tells us both the commutative and Poisson bracket put upon~$V$.
+(The reader might enjoy trying to work out $Pois(3)$ and how to get elements there by composing binary operations.)
+Alternatively, by applying the hom-tensor adjunction to $\rho(2)$, we have a map
+\[
+Pois(2) \otimes V^{\otimes 2} \to V
+\]
+that evaluates a binary operation with a pair of inputs.
+
+By working at the level of operads, one can obtain universal results that hold for all algebras over a given operad.
+For example, there is an operad map $b: Lie \to Pois$ that, at the level of the binary operations, includes the bracket, 
+and this map induces the functor $b^*: \Alg_{Pois} \to \Alg_{Lie}$ where a Poisson algebra is ``forgotten'' to a Lie algebra.
+
+So far we have only discussed putting algebraic structures on a single vector space $V$,
+but it is possible to allow collections of vector spaces.
+For instance, the pair of an algebra and a module provides an example of ``two-colored operad'' as the collection always consists of two vector spaces.
+When one allows multiple objects, one works with {\em colored operads} or, as an alternative terminology, {\em multicategories}.
+
+\begin{rmk}
+For motivational introductions, we recommend \cite{StashAMS} and \cite{Val12}.
+For systematic development of the theory, one might start with \cite{LodVal}, \owen{others}
+Operads now have an extensive literature, and there is a body of deep results (such as Koszul duality) with far-reaching consequences throughout mathematics.
+\end{rmk}
+
+With this language to hand, we now turn to generalizing associative algebras for the setting of topological field theories. 
+Our goal is to formulate a colored operad that captures the behavior of the observables of a topological field theory.
+
+The heuristic idea is straightforward.
+Given a field theory $\cT$ on $\RR^d$, there is a vector space (or possibly dg vector space) $\Obs_\cT(D_r(x))$ of measurements one can make in the open disk $D_r(x)$ of radius $r$ around the point $x$.
+Any measurement in a small disk should provide a measurement on a bigger disk,
+so there is a map $\Obs_\cT(D_r(x)) \to \Obs_\cT(D_R(y))$ whenever $D_r(x) \subset D_R(y)$.
+Thus we have a collection of vector spaces labeled by the disks in $\RR^d$,
+and we have identified a class of unary operations determined by inclusion.
+
+There should also be natural $n$-ary operations encoding how to combine observables from several distinct disks to give an observable on a big disk.
+Start with $n$ disks $D_{r_1}(x_1)$, \dots , $D_{r_n}(x_n)$ whose closures are pairwise disjoint, and let $D_R(y)$ be a big disk containing all the smaller disks.
+Then we want a map
+\[
+\Obs_\cT(D_{r_1}(x_1)) \otimes \cdots \otimes \Obs_\cT(D_{r_n}(x_n)) \to \Obs_\cT(D_R(y)).
+\]
+In the limit when the big disk is all of $\RR^d$ (i.e., $R = \infty$) and the input radii $r_i$ are very small, 
+this map should encode the $n$-point functions beloved of physicists.
+
+So far we have described a structure that observables should have for any field theory on~$\RR^d$.
+For a topological field theory, we expect that the size of a disk does not matter:
+for any inclusion $D_r(x) \subset D_R(y)$, the map $\Obs_\cT(D_r(x)) \to \Obs_\cT(D_R(y))$ is an equivalence.
+This condition implies that we can always shrink the input radius as small as we want and we can always take the output radius to be a fixed value, say $R =1$.
+In other words, the unary operations are parametrized by a point in the unit disk;
+we have a local system of isomorphisms.
+
+For $n$-ary operations we can likewise shrink the input radii as small as we want.
+Thus the $n$-ary operations should be parametrized by the configuration space of $n$ points inside the unit disk.
+(Rather, we can recover all $n$-ary operations knowing this information.)
+We expect that these $n$-ary operations should also define a local system.
+
+Our list of expectations is motivated by the examples of topological field theories that physicists typically give, rather than the Atiyah-Segal approach in terms of functors out of bordism categories.
+Loosely speaking, a classical field theory (defined by a Lagrangian density, also known as an action functional) is ``topological'' if solutions to the equations of motion do not depend on the geometry of the spacetime manifold but only on its smooth structure (or other differential-topological features, like orientations).
+A model example is Chern-Simons theory on oriented 3-manifolds for compact Lie group~$G$:
+the space of solutions to the equations of motion on $M$ is the moduli space of flat $G$-bundles on $M$.
+The observables for a classical field theory on $M$ means the commutative algebra of functions on solutions to the equations of motion on $M$.
+In particular, for $M$ a disk, the size of the disk will not affect the algebra of observables,
+and inclusions of disks leads to isomorphisms of observables.
+Several of these features extend to the quantum field theories that arise by quantizing such topological classical theories;
+the observables continue to form a vector space but are not commutative algebras anymore.
+(See \cite{CG1, CG2} for a precise mathematical formulation of this idea, which is a natural extension of deformation quantization to higher dimensions.)
+
+\begin{rmk}
+There are examples of TFTs from physics where the solutions do not satisfy this condition,
+such as the $A$-model of mirror symmetry.
+In such cases, however, the observables are typically the de Rham complex (or some other model for cohomology) of the space of solutions,
+and these observables do satisfy the conditions we've specified.
+\end{rmk}
+
+We are now in a position to offer a nice operad that should describe the observables of a topological field theory.
+This operad was introduced by algebraic topologists for wholly distinct purposes (understanding $d$-fold based loop spaces),
+so a remarkable dialogue has opened between topologists and physicists.
+We will start, following the topologists, in the category $Top$ of topological spaces
+where we use the cartesian product for the symmetric monoidal structure.
+An operad in this category will be called a {\em topological operad}.
+
+\begin{dfn}
+The {\em little $d$-disks operad} $\Disc_d$ is the topological operad whose space of $n$-ary operations is
+\begin{align*}
+\Disc_d(n) = \{ (x_1, \ldots, x_n; r_1, &\ldots, r_n)  \in D_1(0)^n \times (0,1)^n \;|\; \\
+&\text{the closure of the disks $\overline{D_{r_i}(x_i)}$ is pairwise disjoint}\}.
+\end{align*}
+The composition $\mu \circ_i \nu$ is given by rescaling the unit disk that labels the output of $\nu$ to $r_i$ and then embedding it into the disk~$D_{r_i}(x_i)$.
+\end{dfn}
+
+\owen{Draw some 2d pictures and unpack a little. Mention pair of pants \& OPE} 
+In this sense, it captures the dependence on the disks.
+
+Observables, however, are supposed to live in vector spaces or dg vector spaces,
+so we need to explain how to get algebras in that setting.
+Thankfully, it is straightforward to get a linear version of this operad a dg operad (i.e., operad with values in dg vector spaces and using the tensor product as the symmetric monoidal product).
+One simply takes the singular chain complex on each space of operations:
+for each natural number $n$, take $C_*(\Disc_d(n); \CC)$ and take the induced chain map 
+\[
+C_*(\circ_i): C_*(\Disc_d(n); \CC) \otimes C_*(\Disc_d(m); \CC) \to C_*(\Disc_d(n+m-1); \CC)
+\]
+to produce a dg operad we denote~$C_*(\Disc_d)$.
+(Note that as we always want to work with cochain complexes, we regrade the usual singular chains $C_*(X, \CC)$ to sit in nonpositive cohomological degrees. 
+Likewise the composition $C_*(\circ_i)$ is then a cochain map.)
+
+\begin{dfn}
+An {\em algebra over the little $d$-disks operad} (or little $d$-disks algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_*(\Disc_d)$.
+\end{dfn}
+
+We can state now encapsulate our expectations from above:
+\begin{quote}
+the observables of a topological field theory on $\RR^d$ are a little $d$-disks algebra.
+\end{quote}
+There is a setting where a precise version of this statement was proven, by Elliott and Safronov, for a mathematically well-defined class of Lagrangian field theories.
+
+\owen{give a nice version of their statement, with this as a first attempt}
+
+\begin{thm}[\cite{EllSaf},\owen{precise location}]
+Let $\cT$ be a classical field theory on $\RR^d$ in the sense of~\cite{CosBook},
+and let its observables be constructed following~\cite{CG2}.
+If the theory satisfies 
+\begin{enumerate}
+\item[(i)] $\cT$ is equivariant under the action of the translation group,
+\item[(ii)] the action of the translation Lie algebra is homotopically trivialized, and
+\item[(iii)] the extension of observables along an inclusion of disks is a quasi-isomorphism,
+\end{enumerate}
+then the observables form a little $d$-disks algebra.
+\end{thm}
+
+The notion from \cite{CosBook} articulates Lagrangian field theories whose linearized equations of motion are elliptic in nature;
+it uses (and mathematically articulates) the Batalin-Vilkovisky formalism,
+which is inherently homological.
+In particular, there is an underlying graded vector space of ``fields,''
+and the observables are a dg commutative algebra given a symmetric algebra on the linear dual to the fields and equipped with a differential $d_\cT$ that is determined by the Lagrangian density of the theory.
+Item (ii) above then means that each vector field $\partial_i$ acts by a degree 0 cochain map $D_i$ on the observables and there is a degree one cochain homotopy $\eta_i$ on the observables such that $[d_\cT, \eta_i]~=~D_i$.
+
+This theorem applies to many well-known examples from physics, such as 
+\begin{itemize}
+\item the topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies);
+\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook});
+\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi}; and
+\item the Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW},
+\end{itemize}
+among other examples of topological AKSZ theories, such as BF theories.
+
+For physicists, we note that the proof uses a version of Witten descent.
+Indeed, descent can be used to produce interesting operations in these disk algebras,
+so that many familiar constructions from the physical approach to TFTs fit cleanly and easily into this framework.
+
+\owen{Stuff about formality? functorial field theories?}
+
+\subsection{Generalizing algebras for holomorphic field theories}
+
+We now turn to the problem of describing observables of a holomorphic field theory on~$\CC^d$,
+and we follow an approach similar to the topological case just discussed.
+
+In the setting of a holomorphic field theory, we expect the observables to have a nontrivial dependence on the radius of a disk.
+Consider, for example, that 
+when $D_r(x) \subset D_R(y) \subset \CC$ are open disks in the plane,
+the restriction map of holomorphic functions
+\[
+\cO(D_R(y))\to \cO(D_r(x))
+\]
+is not an isomorphism,
+and the sheaf $\cO$ provides a fundamental model for how the solutions of the equations of motion should behave for a holomorphic field theory.
+We will assume, however, that a holomorphic theory is equivariant under translations of $\CC^d$ and that the observables in a disk $D_r(X)$ are equivalent to the observables in a translate~$D_r(x+z)$.
+Thus, we will have a colored operad whose colors are labeled by radii~$r \in (0,\infty)$,
+as we merely have to specify the observables on a disk~$D_r(0)$.
+
+We now introduce a small tweak.
+Instead of working with disks, we work with polydisks: for $w = (w_1, \ldots, w_d) \in \CC^d$, the polydisk of radius $r$ around $w$~is
+\[
+PD_r(w) = \{ z \in \CC^d \;|\; |z_i - w_i| < r \text{ for all $i$}\}.
+\]
+We work with polydisks because it is easier to describe holomorphic functions on a polydisk than on a disk;
+one can borrow results from single-variable complex analysis.
+With this notion in hand, we introduce our main character.
+
+\begin{dfn}
+The {$d$-polydisks operad} $\PDisc_d$ is the colored operad in the category of complex manifolds where each positive real number $r \in (0,\infty)$ is a color 
+and where there is a complex manifold of $n$-ary operations
+\begin{align*}
+\PDisc_d(r_1, \ldots, r_n| R) = \{ (w_1, \ldots,& w_n) \in PD_R(0)^n \;|\; 
+\text{the closure of the polydisks $\overline{PD_{r_i}(w_i)}$}\\ 
+&\text{ is pairwise disjoint and each is contained in $PD_R(0)$}\}
+\end{align*}
+for any list of radii $r_1,\ldots, r_n, R$.
+This manifold is always an open subset of~$PD_R(0)^n$. 
+(Note that the manifold is empty for many values.)
+There is a composition
+\[
+\circ_i: \PDisc_d(r_1, \ldots, r_n| R) \times \PDisc_d(s_1, \ldots, s_m| S) \to \PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R)
+\]
+only when $r_i = S$, 
+and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
+(Composition is not defined if the radii do not match.)
+\end{dfn}
+
+We are again thinking about configuration spaces --- here of polydisks inside larger polydisks --- but we are remembering the complex structure explicitly.
+To describe observables, we want to produce a dg colored operad that encodes the holomorphic nature of this situation.
+We do {\em not} want to take singular chains, which would only remember the homotopy type;
+instead, we choose to take the Dolbeault complex of each configuration space.
+Note, however, that taking the Dolbeault complex is a contravariant functor,
+so we get a {\em co}\/operad rather than an operad.
+This notion bears the same relationship to operad as a coalgebra does to an algebra;
+one simply reverses all the arrows and asks for an appropriate variant of the relations.
+For instance, there is a composition
+\begin{align}
+\label{pdcirc}
+\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, &\ldots, s_m, r_{i+1}, \ldots, r_n| R)) \to \\
+&\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
+\end{align}
+\owen{I don't know how to eliminate the two numbers}
+when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
+(Composition is not defined if the radii do not match.)
+
+An important technical point arises here: 
+we need to be careful about functional analysis.
+The wedge product map
+\[
+\Omega^{0,*}(X) \otimes \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
+\]
+is not a quasi-isomorphism in general (unlike with de Rham complexes),
+but the completed projective tensor product as topological vector spaces 
+\[
+\Omega^{0,*}(X) \widehat{\otimes}_\pi \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
+\]
+is an isomorphism.
+(We use here the standard Fr\'echet topology on smooth functions, extended to sections of vector bundles.)
+Hence we should work in some category of cochain complexes of well-behaved topological vector spaces, such as convenient vector spaces, or something related.
+This requirement makes sense when geometry matters (e.g., using the Dolbeault complex) and not just topology.
+For an extensive discussion of these issues, see the appendices of~\cite{CG1}.
+From hereon we will ignore function-analytic aspects and write $\otimes$,
+with an appropriate symmetric monoidal category left implicit.
+
+\begin{dfn}
+The {\em $d$-polydisks dg cooperad} is the colored operad in the category of dg vector spaces where each positive real number $r \in (0,\infty)$ is a color 
+and where there is a dg vector space of $n$-ary cooperations
+\[
+\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) 
+\]
+for any list of radii $r_1,\ldots, r_n, R$.
+There is a composition
+\[
+\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R))\to \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
+\]
+only when $r_i = S$, 
+and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
+(Composition is not defined if the radii do not match.)
+\end{dfn}
+
+An algebra $A$ over this cooperad means that for each radius~$r$, 
+there is a dg vector space $A(r)$, and for any list of radii $r_1,\ldots, r_n, R$,
+there is a cochain map
+\[
+\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) .
+\]
+To invest the map $\alpha$ with more meaning, 
+pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
+For instance, for any inputs $a_i \in A(r_i)$ and any cocycle $\omega \in \Omega^{0,k}(\PDisc_d(r_1, \ldots, r_n| R))$, we get an element in $A(R)$~by
+\[
+\int_T \alpha(a_1 \otimes \cdot \otimes a_n) \wedge \omega,
+\]
+where we have suppressed distracting notation from~$\alpha$.
+
+We will now examine the case $d=1$ in some detail and relate such algebras to vertex algebras.
+Afterward, we explain how holomorphic field theories produce such algebras,
+by a result analogous to Elliott and Safronov's.
+In particular, a holomorphic version of Witten descent gives a useful method for producing interesting observables for holomorphic field theories.
+
+\subsubsection{Vertex algebras from the $d=1$ case}
+
+In the case $d=1$, it is possible to relate polydisks algebras to vertex algebras.
+More precisely, when the polydisk algebra has a nice action of the rotation group~$U(1)$,
+one can extract a vertex algebra: 
+see Chapter 5 of~\cite{CG1} for a detailed treatment and examples like the free $\beta\gamma$ system and the Kac-Moody vertex algebras.
+Here we will analyze the cohomology of the cooperad and what kind of information it encodes, with a view towards motivating the relationship to vertex algebras.
+
+It is easiest to work with extremal values of the radii.
+We take the output radius to be $R = \infty$,
+so that the outputs are observables on all of~$\CC$.
+We take the input radii to be $r_i = 0$,
+so that the inputs are observables supported at the points $w_i$.
+(A physicist might call these ``local operators.'')
+This input value is not allowed in the definition, but it arises as a natural limit.
+In any case, it is natural to think about the complex manifold ${\rm Conf}_n(\CC)$ of configurations of $n$ distinct points in~$\CC$:
+it is
+\[
+{\rm Conf}_n(\CC) = \CC^n \setminus \{\text{union of the diagonals $\{ w_i = w_j\}$}\}.
+\]
+Note that for any finite and nonzero values of radii, there is an inclusion
+\[
+\PDisc_d(r_1, \ldots, r_n| R) \hookrightarrow {\rm Conf}_n(\CC).
+\]
+We now turn to examining the Dolbeault cohomology.
+
+It is easy to see
+\[
+{\rm Conf}_n(\CC) \cong \CC \times (\CC^\times)^{n-1}
+\]
+by sending a configuration $(w_1,\ldots, w_n)$ to $(w_1, w_2 - w_1, \ldots, w_n-w_{n-1})$.
+(We could replace $w_1$ by any $w_j$, or even the sum of them all.)
+Hence, the Dolbeault cohomology consists of holomorphic functions on this space;
+there is no higher cohomology.
+Inside the holomorphic functions, as a dense but understandable subalgebra, are the algebraic functions:
+\[
+\CC[w_1, (w_1 - w_2)^{\pm 1}, \ldots, (w_n - w_{n-1})^{\pm 1}] \subset H^{0,*}({\rm Conf}_n(\CC)).
+\]
+Here $(w_j - w_{j-1})^{\pm 1}$ means that the function $1/(w_j - w_{j-1})$ is also a generator.
+Each such algebraic function provides an operation on $H^*(A)$, where $A$ denotes a polydisk algebra.
+
+Let us unravel things in the special case of two points.
+For simplicity, we will fix $w_1 = 0$ so that we focus on where place the other point $w_2 \in \CC^\times$.
+We will use $z$ to denote this point $w_2$.
+Then the binary co-operations are parametrized by $\CC[z, z^{-1}]$.
+Let 
+\[
+V = \lim_{r \to 0} H^*(A(D_r(0)))
+\]
+denote the cohomological observables ``supported at the origin.''
+(It would be better to take the homotopy limit of the $A(D_r(0))$,
+but we leave the experienced reader to make such adjustments.)
+For any two elements $a, b \in V$,
+we then have an element
+\[
+a
+\]
+
+\subsubsection{Polydisks algebras from holomorphic field theories}
+
+Let 
+\[
+\ft_\CC = \CC \otimes_\RR \ft = \text{span}_{\CC}\{\partial/\partial z_1, \ldots, \partial/\partial z_d, \partial/\partial \zbar_1, \ldots, \partial/\partial \zbar_d  \}
+\]
+denote the complexification of the Lie algebra~$\ft$ of translations.
+Let $\ft_{\zbar}$ denote the subalgebra spanned by all the~$\partial/\partial \zbar_i$.
+
+\begin{thm}[\cite{CG1},\owen{precise location}]
+Let $\cT$ be a classical field theory on $\CC^d$ in the sense of~\cite{CosBook},
+and let its observables be constructed following~\cite{CG2}.
+If the theory satisfies 
+\begin{enumerate}
+\item[(i)] $\cT$ is equivariant under the action of the translation group and
+\item[(ii)] the action of the Lie algebra $\ft_{\zbar}$ is homotopically trivialized,
+\end{enumerate}
+then the observables form a $d$-polydisks algebra.
+\end{thm}
+
+This result is analogous to Elliott and Safronov's, although it predated (and inspired) it.
+It applies to the theories that are the focus of this survey.
+One can mimic the version of Witten descent for the topological case to produce observables from local observables.
+
+\subsubsection{From topological to holomorphic}
+
+We remark on a simple consequence of this toolkit that may nonetheless be useful:
+one can view a topological field theory on $\RR^{2d}$ as a special kind of holomorphic field theory on~$\CC^{d}$.
+This situation has been exploited to good effect in the $d=1$ case,
+where people sometimes present an $E_2$-algebra as a dg vertex algebra with extra data and special properties \owen{citations? discussion of applications?}.
+
+The essential idea is simple.
+On a complex manifold $X$, there is a cochain map
+\[
+\Omega^*(X) \to \Omega^{0,*}(X)
+\]
+where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
+If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
+we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
+Hence an algebra over the cooperad $\Omega^*(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,*}(\PDisc_d)$.
+Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
+\begin{enumerate}
+\item algebras over the dg operad $C_*(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^*(\PDisc_d)$, as $\infty$-categories, and
+\item $E_{2d}$-algebras are equivalent to the algebras over $C_*(\PDisc_d)$ such that an inclusion of a polydisk is always a quasi-isomorphism (the ``locally constant'' algebras).
+\end{enumerate}
+The second item holds because any configuration space of polydisks is weakly equivalent, as a topological space, to the analogous configuration space of disks.
+Thus we have sketched the following result.
+
+\begin{thm}
+The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydisks cooperad~$\Omega^{0,*}(\PDisc_d)$.
+\end{thm}
+
+In Section~\ref{???} we will examine another relationship --- generalizing the compactification/chiralization on $\CC$ --- that yields an $E_d$ algebra from a $\PDisc_d$-algebra.
+
 \section{Factorization algebras and holomorphic field theories}

### 2022-08-19 draft.tex
trying to flesh out VOA discussion

@@
 \[
-\int_T \alpha(a_1 \otimes \cdot \otimes a_n) \wedge \omega,
+\int_T \alpha(a_1 \otimes \cdots \otimes a_n) \wedge \omega,
 \]
@@
 We will use $z$ to denote this point $w_2$.
-Then the binary co-operations are parametrized by $\CC[z, z^{-1}]$.
+Then we have binary co-operations parametrized by $\CC[z, z^{-1}]$.
 Let 
@@
 but we leave the experienced reader to make such adjustments.)
-For any two elements $a, b \in V$,
-we then have an element
-\[
-a
-\]
+For any two elements $a, b \in V$ and for any $n \in \ZZ$,
+we then obtain an element
+\[
+a_{(n)} b = \int_{|z| = r} \alpha(a,b)\, z^{-n-1} \d z
+\]
+in $H^*(A(D_R(0))$ for any radius $R > r$.
+(The choice to match $n$ with $z^{-n-1}$ is conventional.)
+Any holomorphic function $f \in D_R(0) \setminus \{0\}$ also defines a map
+\[
+\int_{|z| = r} \alpha(a,b)\, f(z) \d z 
+\]
+and, if $f$ is meromorphic at the origin, then its Laurent expansion
+\[
+f(z) = c_{-N} z^{-N} + \cdots + c_0 + c_1 z + \cdots
+\]
+guarantees that we have
+\[
+\int_{|z| = r} \alpha(a,b)\, f(z) \d z = \sum_{n=-\infty}^{N-1} c_{-n-1} a_{(n)} b.
+\]
+
+\owen{I think I should swap the location of $a$ and $b$ to match VOA conventions.}
 

### 2022-08-19 draft.tex
added reminder about how to truncate fact alg seciton
copied vacua stuff into document

@@
 \owen{Much of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}
+
+\owen{We can cut this sharply now.
+My main concerns are (1) to mention working on arbitrary complex manifolds and not just $\CC^d$, (2) to mention Beilinson-Drinfeld's approach, and (3) to explain chiralization/reduction for $d > 1$.}
 
@@
 
+\owen{new version}
+
+It is common in physics to study field theories defined on the spacetime $\RR^n$.
+As the underlying spacetime $\RR^n$ is a group under addition (i.e., it is the translation group),
+it is natural to ask for field theories with an action by translations.
+That is, since the fields are sections of a fiber bundle over $RR^n$,
+one can ask for an equivariant fiber bundle and ask for the equations of motion (or action functional) to be equivariant under translations.
+In practice, physicists often work with field theories whose equations of motion are differential equations with constant coefficients.
+(Nearly all the examples we've discussed in this survey satisfy this condition.)
+
+Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
+A {\em classical vacuum} for the theory is a solution that this translation-invariant,
+i.e., a constant solution.
+As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
+\[
+\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
+\]
+given by the substack of constant solutions.
+We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.
+
+Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
+For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
+\[
+\cM_{\rm vac} \cong T^*[1-d]X.
+\]
+(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
+For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
+\[
+\cM_{\rm vac} \cong V/G
+\]
+where $V$ is a (graded) $G$-representation and $V/G$ denotes the quotient stack.
+The factor $V$ arises from solutions for the non-gauge field, which are sections of some associated vector bundle,
+while the quotient by $G$ arises from the gauge transformation.
+For another example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ has \owen{true?}
+\[
+\cM_{\rm vac} \cong \fg/G,
+\]
+the adjoint quotient stack of the group.
+For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
+\[
+\cM_{\rm vac} \cong X/G
+\]
+where $X$ is a derived stack with a $G$-action and $X/G$ denotes the quotient stack.
+
+In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
+Instead, they have worked with a GIT quotient.
+For instance, in the setting of a gauge theory with stack $V/G$ of classical vacua, it means they work with
+\[
+V//G = \Spec(\cO(V)^G),
+\]
+the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
+This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
+We will call it the moduli {\em space} of classical vacua and denote it by~$M_{rm vac}(\cT)$.
+
+It is familiar to geometers that this affinization forgets interesting information about the stack because an invariant function must be constant on the closure of any orbit.
+Thus, the canonical map
+\[
+V/G \to V//G
+\]
+often collapses orbits together.
+An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $\gl_N/ GL_N$, whose affinization is
+\[
+\gl_N//GL_N \cong \CC^N/S_N,
+\]
+by the Chevalley restriction theorem.
+The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
+In other words, the canonical map collapses together Jordan blocks with the same diagonal entries.
+For this reason, it loses details about the classical vacua remembered by the stack quotient.
+
+\begin{rmk}
+The physicists' focus on the moduli space is not unreasonable:
+one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
+The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
+On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion, whereas the space cannot distinguish between some vacua.
+Moreover, the stack encodes much more data about the theory near each vacuum.
+For instance, it remembers ``enhanced symmetries'' (such as the residual gauge fields) at each vacuum.
+\end{rmk}
+
+For the holomorphic QCD theory \owen{write data} the moduli stack of classical vacua is \owen{write it}
+The moduli space is a well-known variety
+\[
+M_{rm vac}(\cT) \cong \Gr(N_f, N_c)
+\]
+by using classical invariant theory. \owen{show?}
+A similar computation on the putative dual shows the following.
+
+\begin{prop}
+Seiberg dual theories have isomorphic moduli spaces.
+\end{prop}
+
+This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
+
+\owen{Sketch proof}: This is the first and second fundamental theorem of classical invariant theory!
+
+\begin{rmk}
+In the physics literature this isomorphism is given by explicitly matching gauge-invariant functions, which are often called mesons or baryons, as they can be identified with the data that identifies such particles.
+These meson and baryons are precisely the usual generators of the ring of invariant functions, so an isomorphism of generators determines the desired isomorphism of rings. 
+One must check that the relations are satisfied;
+here it explains the superpotential on the magnetic side.
+\end{rmk}
+
+We want to point out, however, that {\em the moduli stacks are not isomorphic}.
+A quick check is to note that there are orbits with different stabilizer groups.
+Consider, for instance, the origin in each vector space.
+On the electric side its stabilizer is $SL(N_c)$ and on the magnetic side it is $SL(N_f - N_c)$.
+Thus each theory has a vacuum whose associated perturbative classical theory has no partner on the other side.
+Hence Seiberg duality cannot hold at the stack level for the classical theories.
+
 \subsubsection{Flavor symmetries}
@@
 
+******** Discussion about quantization **********
+
+On the other hand, there is an open locus where the moduli stacks are equivalent:
+the semi-stable points of $V/G$ \owen{fix description, as it's possibly just the stable locus}.
+This locus determines the space $V//G$ and hence we have the isomorphism desired.
+Let us try to unravel what this equivalence means for the field theories, both classical and quantum.
+
+Consider any semistable point $x$ in $V/G$.
+We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
+For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x (V//G)$ \owen{Elaborate}. 
+Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
+because there is an explicit identification of the tangent space to the corresponding point in the moduli space of the dual theory.
+Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
+Hence on the semistable locus of $V/G$, we can guarantee an equivalence of quantizations.
+
+This identification breaks down on the unstable locus, raising the following question.
+
+{\bf Question:}
+At the quantum level, what happens on the unstable locus?
+
+In a related vein, we want to know what correspondence of quantum factorization algebras we expect from Seiberg duality. 
+The mismatch for the moduli stack of classical vacua must be fixed somehow.
+
+We note that in the physics literature, there are a number of modifications that are explored in this setting.
+For instance, there are ``instanton corrections'' that cannot be found by perturbative techniques, although they can be treated in a mathematically precise way. 
+\owen{Mention others? RG flow, symmetry breaking, ...}
+It is interesting to wonder how these would appear in the holomorphic setting.
+
+\owen{Other things: affinization as polydiscs algebras, comparison with mirror symmetry (note A-model involves instanton corrections)}
+
+* Explain that you get a sheaf of polydiscs algebras over the moduli stack.
+We can view this as presenting a ``quantization of the moduli stack'' $\cM_{vac}^{\rm q}$ There is thus an ``affinization'' of the quantum moduli stack.
+
+Conjecture: There is an equivalence of affinizations of the quantum moduli stacks for Seiberg dual theories.
+
+This process probably looks away from the unstable locus in the same way that the classical part does.
+
 \end{document}

### 2022-08-21 draft.tex
added more reminders to myself

@@
 
-\dedicatory{To Yuri Manin, with great admiration.}
+\dedicatory{To Yuri Manin, with gratitude and admiration.}
 
@@
 The intuition behind $Y$ is that for any map $\phi: \CC^\times \to V$ and for any point $w \in \CC^\times$, 
-there is a restriction of $\phi$ to a little disk around $w$.
+there is a restriction of $\phi$ to a little disc around $w$.
 That is, there is a restriction map $r_w: V[z,z^{-1}] \to V[[t]]$, where $t$ is the local coordinate $t = z-w$.
@@
 there is, in fact, a natural extension to a ``local'' symmetry $\rho^{\rm loc}: \fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
-Geometrically, a $\fg$-valued function $x(z)$ acts pointwise (with respect to the formal disk) on the formal loop space.
+Geometrically, a $\fg$-valued function $x(z)$ acts pointwise (with respect to the formal disc) on the formal loop space.
 (Although the algebraic loop space is not symplectic in a strict sense,
@@
 
-We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\pAA^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disk) into $\fg$,
+We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\pAA^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disc) into $\fg$,
 just as $\fg[z,z^{-1}]$ provides a kind of loop algebra.
@@
 \item For a topological field theory on $\RR^d$ (which we'll define in a moment),
-the observables form an algebra over the {\em little $d$-disks operad}~$\Disc_d$ (sometimes also known as the $E_d$ operad). 
+the observables form an algebra over the {\em little $d$-discs operad}~$\Disc_d$ (sometimes also known as the $E_d$ operad). 
 Equivalently, one says the observables are an $E_d$-algebra. 
@@
 The heuristic idea is straightforward.
-Given a field theory $\cT$ on $\RR^d$, there is a vector space (or possibly dg vector space) $\Obs_\cT(D_r(x))$ of measurements one can make in the open disk $D_r(x)$ of radius $r$ around the point $x$.
-Any measurement in a small disk should provide a measurement on a bigger disk,
+Given a field theory $\cT$ on $\RR^d$, there is a vector space (or possibly dg vector space) $\Obs_\cT(D_r(x))$ of measurements one can make in the open disc $D_r(x)$ of radius $r$ around the point $x$.
+Any measurement in a small disc should provide a measurement on a bigger disc,
 so there is a map $\Obs_\cT(D_r(x)) \to \Obs_\cT(D_R(y))$ whenever $D_r(x) \subset D_R(y)$.
-Thus we have a collection of vector spaces labeled by the disks in $\RR^d$,
+Thus we have a collection of vector spaces labeled by the discs in $\RR^d$,
 and we have identified a class of unary operations determined by inclusion.
 
-There should also be natural $n$-ary operations encoding how to combine observables from several distinct disks to give an observable on a big disk.
-Start with $n$ disks $D_{r_1}(x_1)$, \dots , $D_{r_n}(x_n)$ whose closures are pairwise disjoint, and let $D_R(y)$ be a big disk containing all the smaller disks.
+There should also be natural $n$-ary operations encoding how to combine observables from several distinct discs to give an observable on a big disc.
+Start with $n$ discs $D_{r_1}(x_1)$, \dots , $D_{r_n}(x_n)$ whose closures are pairwise disjoint, and let $D_R(y)$ be a big disc containing all the smaller discs.
 Then we want a map
@@
 \]
-In the limit when the big disk is all of $\RR^d$ (i.e., $R = \infty$) and the input radii $r_i$ are very small, 
+In the limit when the big disc is all of $\RR^d$ (i.e., $R = \infty$) and the input radii $r_i$ are very small, 
 this map should encode the $n$-point functions beloved of physicists.
@@
 So far we have described a structure that observables should have for any field theory on~$\RR^d$.
-For a topological field theory, we expect that the size of a disk does not matter:
+For a topological field theory, we expect that the size of a disc does not matter:
 for any inclusion $D_r(x) \subset D_R(y)$, the map $\Obs_\cT(D_r(x)) \to \Obs_\cT(D_R(y))$ is an equivalence.
 This condition implies that we can always shrink the input radius as small as we want and we can always take the output radius to be a fixed value, say $R =1$.
-In other words, the unary operations are parametrized by a point in the unit disk;
+In other words, the unary operations are parametrized by a point in the unit disc;
 we have a local system of isomorphisms.
@@
 For $n$-ary operations we can likewise shrink the input radii as small as we want.
-Thus the $n$-ary operations should be parametrized by the configuration space of $n$ points inside the unit disk.
+Thus the $n$-ary operations should be parametrized by the configuration space of $n$ points inside the unit disc.
 (Rather, we can recover all $n$-ary operations knowing this information.)
@@
 The observables for a classical field theory on $M$ means the commutative algebra of functions on solutions to the equations of motion on $M$.
-In particular, for $M$ a disk, the size of the disk will not affect the algebra of observables,
-and inclusions of disks leads to isomorphisms of observables.
+In particular, for $M$ a disc, the size of the disc will not affect the algebra of observables,
+and inclusions of discs leads to isomorphisms of observables.
 Several of these features extend to the quantum field theories that arise by quantizing such topological classical theories;
@@
 \begin{dfn}
-The {\em little $d$-disks operad} $\Disc_d$ is the topological operad whose space of $n$-ary operations is
+The {\em little $d$-discs operad} $\Disc_d$ is the topological operad whose space of $n$-ary operations is
 \begin{align*}
 \Disc_d(n) = \{ (x_1, \ldots, x_n; r_1, &\ldots, r_n)  \in D_1(0)^n \times (0,1)^n \;|\; \\
-&\text{the closure of the disks $\overline{D_{r_i}(x_i)}$ is pairwise disjoint}\}.
+&\text{the closure of the discs $\overline{D_{r_i}(x_i)}$ is pairwise disjoint}\}.
 \end{align*}
-The composition $\mu \circ_i \nu$ is given by rescaling the unit disk that labels the output of $\nu$ to $r_i$ and then embedding it into the disk~$D_{r_i}(x_i)$.
+The composition $\mu \circ_i \nu$ is given by rescaling the unit disc that labels the output of $\nu$ to $r_i$ and then embedding it into the disc~$D_{r_i}(x_i)$.
 \end{dfn}
@@
 \owen{Draw some 2d pictures and unpack a little. Mention pair of pants \& OPE} 
-In this sense, it captures the dependence on the disks.
+In this sense, it captures the dependence on the discs.
 
@@
 \begin{dfn}
-An {\em algebra over the little $d$-disks operad} (or little $d$-disks algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_*(\Disc_d)$.
+An {\em algebra over the little $d$-discs operad} (or little $d$-discs algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_*(\Disc_d)$.
 \end{dfn}
+
+\owen{Perhaps mention classic examples like $n$-fold loop spaces or Hochschild cohomology?}
 
@@
 \begin{quote}
-the observables of a topological field theory on $\RR^d$ are a little $d$-disks algebra.
+the observables of a topological field theory on $\RR^d$ are a little $d$-discs algebra.
 \end{quote}
@@
 \item[(ii)] the action of the translation Lie algebra is homotopically trivialized, and
-\item[(iii)] the extension of observables along an inclusion of disks is a quasi-isomorphism,
+\item[(iii)] the extension of observables along an inclusion of discs is a quasi-isomorphism,
 \end{enumerate}
-then the observables form a little $d$-disks algebra.
+then the observables form a little $d$-discs algebra.
 \end{thm}
@@
 among other examples of topological AKSZ theories, such as BF theories.
+In all these examples, the underlying elliptic complex is a version of the de Rham complex.
 
 For physicists, we note that the proof uses a version of Witten descent.
-Indeed, descent can be used to produce interesting operations in these disk algebras,
+Indeed, descent can be used to produce interesting operations in these disc algebras,
 so that many familiar constructions from the physical approach to TFTs fit cleanly and easily into this framework.
@@
 
-In the setting of a holomorphic field theory, we expect the observables to have a nontrivial dependence on the radius of a disk.
+In the setting of a holomorphic field theory, we expect the observables to have a nontrivial dependence on the radius of a disc.
 Consider, for example, that 
-when $D_r(x) \subset D_R(y) \subset \CC$ are open disks in the plane,
+when $D_r(x) \subset D_R(y) \subset \CC$ are open discs in the plane,
 the restriction map of holomorphic functions
@@
 and the sheaf $\cO$ provides a fundamental model for how the solutions of the equations of motion should behave for a holomorphic field theory.
-We will assume, however, that a holomorphic theory is equivariant under translations of $\CC^d$ and that the observables in a disk $D_r(X)$ are equivalent to the observables in a translate~$D_r(x+z)$.
+We will assume, however, that a holomorphic theory is equivariant under translations of $\CC^d$ and that the observables in a disc $D_r(X)$ are equivalent to the observables in a translate~$D_r(x+z)$.
 Thus, we will have a colored operad whose colors are labeled by radii~$r \in (0,\infty)$,
-as we merely have to specify the observables on a disk~$D_r(0)$.
+as we merely have to specify the observables on a disc~$D_r(0)$.
 
 We now introduce a small tweak.
-Instead of working with disks, we work with polydisks: for $w = (w_1, \ldots, w_d) \in \CC^d$, the polydisk of radius $r$ around $w$~is
+Instead of working with discs, we work with polydiscs: for $w = (w_1, \ldots, w_d) \in \CC^d$, the polydisc of radius $r$ around $w$~is
 \[
@@
 \]
-We work with polydisks because it is easier to describe holomorphic functions on a polydisk than on a disk;
+We work with polydiscs because it is easier to describe holomorphic functions on a polydisc than on a disc;
 one can borrow results from single-variable complex analysis.
@@
 \begin{dfn}
-The {$d$-polydisks operad} $\PDisc_d$ is the colored operad in the category of complex manifolds where each positive real number $r \in (0,\infty)$ is a color 
+The {$d$-polydiscs operad} $\PDisc_d$ is the colored operad in the category of complex manifolds where each positive real number $r \in (0,\infty)$ is a color 
 and where there is a complex manifold of $n$-ary operations
@@
 \PDisc_d(r_1, \ldots, r_n| R) = \{ (w_1, \ldots,& w_n) \in PD_R(0)^n \;|\; 
-\text{the closure of the polydisks $\overline{PD_{r_i}(w_i)}$}\\ 
+\text{the closure of the polydiscs $\overline{PD_{r_i}(w_i)}$}\\ 
 &\text{ is pairwise disjoint and each is contained in $PD_R(0)$}\}
@@
 only when $r_i = S$, 
-and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
+and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
 (Composition is not defined if the radii do not match.)
@@
 
-We are again thinking about configuration spaces --- here of polydisks inside larger polydisks --- but we are remembering the complex structure explicitly.
+We are again thinking about configuration spaces --- here of polydiscs inside larger polydiscs --- but we are remembering the complex structure explicitly.
 To describe observables, we want to produce a dg colored operad that encodes the holomorphic nature of this situation.
@@
 \owen{I don't know how to eliminate the two numbers}
-when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
+when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
 (Composition is not defined if the radii do not match.)
@@
 \begin{dfn}
-The {\em $d$-polydisks dg cooperad} is the colored operad in the category of dg vector spaces where each positive real number $r \in (0,\infty)$ is a color 
+The {\em $d$-polydiscs dg cooperad} is the colored operad in the category of dg vector spaces where each positive real number $r \in (0,\infty)$ is a color 
 and where there is a dg vector space of $n$-ary cooperations
@@
 
-In the case $d=1$, it is possible to relate polydisks algebras to vertex algebras.
-More precisely, when the polydisk algebra has a nice action of the rotation group~$U(1)$,
+In the case $d=1$, it is possible to relate polydiscs algebras to vertex algebras.
+More precisely, when the polydisc algebra has a nice action of the rotation group~$U(1)$,
 one can extract a vertex algebra: 
@@
 there is no higher cohomology.
-Inside the holomorphic functions, as a dense but understandable subalgebra, are the algebraic functions:
-\[
-\CC[w_1, (w_1 - w_2)^{\pm 1}, \ldots, (w_n - w_{n-1})^{\pm 1}] \subset H^{0,*}({\rm Conf}_n(\CC)).
-\]
-Here $(w_j - w_{j-1})^{\pm 1}$ means that the function $1/(w_j - w_{j-1})$ is also a generator.
-Each such algebraic function provides an operation on $H^*(A)$, where $A$ denotes a polydisk algebra.
+Inside the holomorphic functions 
+\[
+\cO({\rm Conf}_n(\CC)) = H^{0,*}({\rm Conf}_n(\CC)),
+\] 
+as a dense but understandable subalgebra, are the algebraic functions:
+\[
+\cO_{\rm alg}({\rm Conf}_n(\CC)) = \CC[w_1, (w_1 - w_2)^{\pm 1}, \ldots, (w_n - w_{n-1})^{\pm 1}].
+\]
+Here $(w_j - w_{j-1})^{\pm 1}$ means that the function $1/(w_j - w_{j-1})$ is a generator, 
+as is $(w_j - w_{j-1})$.
+Each such algebraic function provides an operation on $H^*(A)$, where $A$ denotes a polydisc algebra.
 
@@
 
-\owen{I think I should swap the location of $a$ and $b$ to match VOA conventions.}
-
-\subsubsection{Polydisks algebras from holomorphic field theories}
+\owen{I think I should swap the location of $a$ and $b$ to match VOA conventions.
+I want to explain that taking the extremal radii means we cannot compose, which leads to the complicated VOA formulas.}
+
+\subsubsection{Revisiting the higher Kac-Moody algebras}
+
+\owen{I want to mention here that we have a polydisc version}
+
+\subsubsection{Polydiscs algebras from holomorphic field theories}
 
@@
 \end{enumerate}
-then the observables form a $d$-polydisks algebra.
+then the observables form a $d$-polydiscs algebra.
 \end{thm}
@@
 \item algebras over the dg operad $C_*(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^*(\PDisc_d)$, as $\infty$-categories, and
-\item $E_{2d}$-algebras are equivalent to the algebras over $C_*(\PDisc_d)$ such that an inclusion of a polydisk is always a quasi-isomorphism (the ``locally constant'' algebras).
+\item $E_{2d}$-algebras are equivalent to the algebras over $C_*(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
 \end{enumerate}
-The second item holds because any configuration space of polydisks is weakly equivalent, as a topological space, to the analogous configuration space of disks.
+The second item holds because any configuration space of polydiscs is weakly equivalent, as a topological space, to the analogous configuration space of discs.
 Thus we have sketched the following result.
@@
 \begin{thm}
-The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydisks cooperad~$\Omega^{0,*}(\PDisc_d)$.
+There is a forgetful functor
+\[
+\Alg_{E_{2d}} \to  \Alg_{\PDisc_2}.
+\]
 \end{thm}
+
+The primary interest for us is the following consequence.
+
+\begin{cor}
+The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,*}(\PDisc_d)$.
+\end{cor}
 
@@
 For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$.
-One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disk.
+One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
 Alternatively, the collection of opens $\{ M \setminus q \mcol q \in M\}$ is a Weiss cover of $M$.
@@
 
-\subsection{Algebras over the little disks operad}
+\subsection{Algebras over the little discs operad}
 
@@
 It is then natural to ask about higher-dimensional versions of algebra.
-Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-disks operad,
+Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-discs operad,
 which we now describe and relate to prefactorization algebras on~$\RR^n$.
@@
 Fix a dimension $n$. 
-Let $D^n(x,r)$ denote the open disk of radius $r$ centered at $x \in \RR^n$,
-and let $D^n$ denote the unit disk~$D^n(0,1)$.
+Let $D^n(x,r)$ denote the open disc of radius $r$ centered at $x \in \RR^n$,
+and let $D^n$ denote the unit disc~$D^n(0,1)$.
 
 \begin{dfn}
-Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint disks:
-\[
-E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the disks $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disk $D^n$\end{tabular}}\right\}.
+Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint discs:
+\[
+E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the discs $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disc $D^n$\end{tabular}}\right\}.
 \]
@@
 For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
-If one fixes a direction, such as a coordinate axis, and works with disks lined up in this direction,
+If one fixes a direction, such as a coordinate axis, and works with discs lined up in this direction,
 one sees an $E_1$ structure.
@@
 \]
-of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disk.
-Maps that send the boundary of a disk to the base point can be extended naturally to bigger disks: just send the rest of the big disk to the basepoint.
+of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disc.
+Maps that send the boundary of a disc to the base point can be extended naturally to bigger discs: just send the rest of the big disc to the basepoint.
 \owen{Should I spell out the structure of the algebra?}
@@
 Factorization algebras on $\RR^n$ and $E_n$ algebras should be closely related,
-as can be seen by drawing pictures of the configurations of disks that control operations.
+as can be seen by drawing pictures of the configurations of discs that control operations.
 
 \begin{dfn}
-A factorization algebra $\cF$ on an $n$-manifold $M$ is \emph{locally constant} if for each inclusion of open disks $D \subset D'$, then the map $\cF(D) \to \cF(D')$ is a quasi-isomorphism.
+A factorization algebra $\cF$ on an $n$-manifold $M$ is \emph{locally constant} if for each inclusion of open discs $D \subset D'$, then the map $\cF(D) \to \cF(D')$ is a quasi-isomorphism.
 \end{dfn}
@@
 \begin{dfn}\label{dfn:cdo}
-A {\em sheaf of $n$-CDOs} on a manifold $X$ (of complex dimension $N$) is a sheaf of $n$-dimensional holomorphically translation invariant factorization algebras whose restriction to any $n$-disk is equivalent to the $n$-dimensional $\beta\gamma$ system (with target $\CC^N$).
+A {\em sheaf of $n$-CDOs} on a manifold $X$ (of complex dimension $N$) is a sheaf of $n$-dimensional holomorphically translation invariant factorization algebras whose restriction to any $n$-disc is equivalent to the $n$-dimensional $\beta\gamma$ system (with target $\CC^N$).
 \end{dfn}
@@
 We give a concrete description of 2-CDO's on the manifold $X = \PP^1$.
-In this case there is a unique sheaf of 2-CDO's that we denote by $2\CDO_{\PP^1}$ (here we are using the holomorphic $\PP_2$ description as the cohomology of the observables of the $\beta\gamma$ system on a $2$-disk).
+In this case there is a unique sheaf of 2-CDO's that we denote by $2\CDO_{\PP^1}$ (here we are using the holomorphic $\PP_2$ description as the cohomology of the observables of the $\beta\gamma$ system on a $2$-disc).
 Consider the standard description of $\PP^1 = U \cup V$ where $U = {\rm Spec}(\CC[\gamma])$ and $V = {\rm Spec}(\CC[\gamma^{-1}])$.

### 2022-08-24 draft.tex
edited section on fact algs

@@
 
+This operad was invented by algebraic topologists to capture the rich structure of the $d$-fold based loop space $\Omega^d X$ of a pointed space $(X,x)$.
+(The usual homotopy group $\pi_d(X)$ is a shadow of this richer structure.)
+Thus there is a deep reservoir of tools and results for studying algebras over the little discs operads in algebraic topology.
+
 Observables, however, are supposed to live in vector spaces or dg vector spaces,
@@
 
-This theorem applies to many well-known examples from physics, such as 
+\owen{Actually say what kind of $d$-discs algebras one gets.}
+This theorem applies to many well-known examples from physics:
 \begin{itemize}
-\item the topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies);
-\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook});
-\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi}; and
-\item the Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW},
+\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra.
+It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
+\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
+\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
+\item Each Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming the coadjoint quotient stack~$\fg^*/G$.
 \end{itemize}
-among other examples of topological AKSZ theories, such as BF theories.
+It applies to other examples of topological AKSZ theories, such as BF theories.
 In all these examples, the underlying elliptic complex is a version of the de Rham complex.
@@
 \owen{Stuff about formality? functorial field theories?}
+
+This theorem builds an explicit bridge between topology and physics. 
+Thanks to the theorem of Elliott and Safronov, we know that most topological field theories in the physicist's sense provide $E_n$ algebras,
+but they can thus be analyzed using the powerful machinery of modern homotopy theory. 
+Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. 
+Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.
 
@@
 \begin{dfn}
+\label{dfn pdisc}
 The {\em $d$-polydiscs dg cooperad} is the colored operad in the category of dg vector spaces where each positive real number $r \in (0,\infty)$ is a color 
@@
 
+\owen{Improve!}
 An algebra $A$ over this cooperad means that for each radius~$r$, 
@@
 pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
-For instance, for any inputs $a_i \in A(r_i)$ and any cocycle $\omega \in \Omega^{0,k}(\PDisc_d(r_1, \ldots, r_n| R))$, we get an element in $A(R)$~by
-\[
-\int_T \alpha(a_1 \otimes \cdots \otimes a_n) \wedge \omega,
+For instance, for any inputs $a_i \in A(r_i)$, we get an element in $A(R)$~by
+\[
+\int_T \alpha(a_1 \otimes \cdots \otimes a_n),
 \]
@@
 We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
-With the notion in hand, we will describe several examples and several situations where factorization algebras have already appeared in mathematics and physics, 
-albeit in a different formulation.
-Finally, we will sketch the main theorem of \cite{CG2}, 
+Their local structure encompasses the behavior we saw in the preceding section, where $E_d$ algebras captured topological field theories on $\RR^d$ and $\PDisc_d$ algebras captured holomorphic field theories on~$\CC^d$.
+Factorization algebras allow one to work on smooth manifolds, and complex manifolds, more generally;
+their global behavior encompasses constructions like Hochschild homology and conformal blocks.
+We will then sketch the main theorem of \cite{CG2}, 
 which explains a precise and general relationship between quantum field theories and factorization algebras.
+Finally, we describe some special features and interesting applications of factorization algebras of holomorphic field theories.
+
+\begin{rmk}
+Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
+and their version has had great success in algebraic geometry and representation theory,
+particularly in the setting of the geometric Langlands program.
+Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of smooth manifolds,
+developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
+for questions in algebraic topology.
+Motivated by all this work, Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
+\end{rmk}
 
@@
 In this paper $M$ is always a smooth manifold (typically a complex manifold) and $\mc{C}$ is ${\rm Vect}$ or ${\rm dgVect}$, with the usual tensor product as the symmetric monoidal product.
-
+(As mentioned in the paragraph before Definition~\ref{dfn pdisc}, one needs to deal with issues of functional analysis for applications to QFT, but we will not discuss those aspects here.
+In brief, for purposes of holomorphic field theories, we use an $\infty$-category obtained from working with cochain complexes of differentiable vector spaces, with extensive treatment in~\cite{CG1}.)
+
+\begin{dfn}
 A {\em prefactorization algebra} $\cF$ on $M$ taking values in cochain complexes is a rule that assigns a cochain complex $\cF(U)$ to each open set $U \subset M$ along with the following maps and compatibilities.
@@
 \end{itemize}
+\end{dfn}
 
@@
 On the one hand, $\cF$ resembles a {\em precosheaf}, which is a functor from opens in $M$ to a category like ${\rm Vect}$ or ${\rm dgVect}$.
-(A presheaf is a functor out of the opposite category to opens in $M$.) 
+(A presheaf is a functor out of the opposite category to opens in~$M$.) 
 Here, however, $\cF$ also assign values to disjoint unions of opens, and it uses the tensor product rather than direct sum.
@@
 
-Note that these axioms imply that $\cF(\emptyset)$ is a commutative algebra. 
-We say that $\cF$ is a \emph{unital} prefactorization algebra  if $\cF(\emptyset)$ is a unital commutative algebra.
+%Note that these axioms imply that $\cF(\emptyset)$ is a commutative algebra. 
+%We say that $\cF$ is a \emph{unital} prefactorization algebra if $\cF(\emptyset)$ is a unital commutative algebra.
 In this case, $\cF(U)$ is a pointed cochain complex by the image of the unit $1 \in \cF(\emptyset)$ under the structure map $\cF(\emptyset) \to \cF(U)$.
@@
 \begin{eg}\label{ex:associativealgebra}
-The crucial example to bear in mind is an associative algebra.
 Every associative algebra $A$ defines a prefactorization algebra $\cF_A$ on $\RR$, as follows.
@@
 
-We will now sketch another way of phrasing this idea, but the reader who is content with this definition and eager to see examples should feel free to jump ahead, referring back as needed.
-
-\subsection{Prefactorization algebras as algebras over an operad}
-\label{sec:disj}
-
-The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
-A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
-See \owen{add citations}
-
-\begin{dfn}
-Let $\Disj_M$ denote the following colored operad associated to~$M$: 
-\begin{itemize}
-\item The colors (or objects) consist of all open subsets of $M$. 
-\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$.
+There is another, more sophisticated way to phrase prefactorization algebras, using the framework of operads.
+Associated to each topological space $M$, there is a colored operad $\Disj_M$ such that a prefactorization algebra is an algebra over~$\Disj_M$.
+For a discussion, see Chapter 3 of~\cite{CG1};
+related ideas are developed in~\cite{AF, LurieHA, Ginot}.
+
+%\subsection{Prefactorization algebras as algebras over an operad}
+%\label{sec:disj}
+%
+%The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
+%A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
+%See \owen{add citations}
+%
+%\begin{dfn}
+%Let $\Disj_M$ denote the following colored operad associated to~$M$: 
+%\begin{itemize}
+%\item The colors (or objects) consist of all open subsets of $M$. 
+%\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$.
 If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point.
 Otherwise, the set of maps is empty.
-\item The composition of maps is defined in the obvious way. 
-\end{itemize}
-\end{dfn}
-
-\begin{dfn}
-Let $\mc{C}$ be a colored operad. 
-A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
-\end{dfn}
-
-In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
-Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories.
-
-\begin{rmk} 
-If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
-Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
-~\hfill$\Diamond$ 
-\end{rmk}
-
-Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$.
-
-\begin{dfn}
-We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
-\end{dfn}
-
-\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
-\label{AssAsFact}
-
-We explained above how an associative algebra provides a prefactorization algebra on the real line.
+%\item The composition of maps is defined in the obvious way. 
+%\end{itemize}
+%\end{dfn}
+%
+%\begin{dfn}
+%Let $\mc{C}$ be a colored operad. 
+%A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
+%\end{dfn}
+%
+%In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
+%Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories. 
+%
+%\begin{rmk} 
+%If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
+%Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
+%~\hfill$\Diamond$ 
+%\end{rmk}
+%
+%Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$. 
+%
+%\begin{dfn}
+%We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
+%\end{dfn}
+%
+%\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
+%\label{AssAsFact}
+%
+%We explained above how an associative algebra provides a prefactorization algebra on the real line.
 There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras.
 Here we will characterize those that do arise from associative algebras.
-
-\begin{dfn}
-Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
-We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
-\end{dfn}
-
-It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.
-
-\begin{lem}\label{locally_constant_is_associative}
-Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
-Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
-\end{lem}
-
-One can got further, however, and also capture modules, essentially by marking the line with points.
-For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.
-
-Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$.
-We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure.
-
-Pick a point $p \in \RR$.
+% 
+%\begin{dfn}
+%Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
+%We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
+%\end{dfn}
+%
+%It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.
+%
+%\begin{lem}\label{locally_constant_is_associative}
+%Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
+%Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
+%\end{lem}
+%
+%One can got further, however, and also capture modules, essentially by marking the line with points.
+%For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.
+%
+%Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$.
+%We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure. 
+%
+%Pick a point $p \in \RR$.
 On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$.
@@
 For example, given
-\[
-s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
-\]
-we have
-\begin{align*}
-\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
-&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
-&= A \ot M \ot B
-\end{align*}
-and the inclusion of these three intervals into $(s_0,u_1)$ is the map
-\[
-\begin{array}{ccc}
-\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
-a \ot m \ot b & \mapsto & amb
-\end{array}.
-\]
-The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.
-
+%\[
+%s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
+%\]
+%we have
+%\begin{align*}
+%\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
+%&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
+%&= A \ot M \ot B
+%\end{align*}
+%and the inclusion of these three intervals into $(s_0,u_1)$ is the map
+%\[
+%\begin{array}{ccc}
+%\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
+%a \ot m \ot b & \mapsto & amb
+%\end{array}.
+%\]
+%The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.
+%
+%%\begin{figure}
+%%\begin{center}
+%% \begin{minipage}{3cm}
+%% \begin{tikzpicture}[scale=0.75]
+%% \begin{scope}[line cap=round,ultra thick]
+%% \draw (-2.5,0) -- (-1.5,0); 
+%% \draw (-1,0) -- (0.5,0); 
+%% \draw[fill=black] (0,0) circle (0.07);
+%% \draw (1.5,0) -- (2.5,0); 
+%% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
+%% \draw (-2.75,-2) -- (0.75,-2); 
+%% \draw[fill=black] (0,-2) circle (0.07);
+%% \draw (1.25,-2) -- (2.75,-2);  
+%% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
+%% \draw (-3,-4) -- (3,-4);
+%% \draw[fill=black] (0,-4) circle (0.07); 
+%% \end{scope}
+%% \end{tikzpicture}
+%% \end{minipage}
+%%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
+%% \begin{minipage}{8cm}
+%% \begin{tikzcd}[cramped,column sep=tiny]
+%%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
+%%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
+%%amb  & \in &M 
+%%\end{tikzcd}
+%%\end{minipage}
+%%\end{center}
+%%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
+%%\label{fig:bimodasfact}
+%%\end{figure}
+%
 %\begin{figure}
 %\begin{center}
-% \begin{minipage}{3cm}
-% \begin{tikzpicture}[scale=0.75]
+% \begin{tikzpicture}
 % \begin{scope}[line cap=round,ultra thick]
-% \draw (-2.5,0) -- (-1.5,0); 
-% \draw (-1,0) -- (0.5,0); 
-% \draw[fill=black] (0,0) circle (0.07);
-% \draw (1.5,0) -- (2.5,0); 
-% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
-% \draw (-2.75,-2) -- (0.75,-2); 
-% \draw[fill=black] (0,-2) circle (0.07);
-% \draw (1.25,-2) -- (2.75,-2);  
-% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
-% \draw (-3,-4) -- (3,-4);
-% \draw[fill=black] (0,-4) circle (0.07); 
+% \draw (-2.5,1) -- (-1.5,1); 
+% \draw (-1,1) -- (0.5,1); 
+% \draw[fill=black] (0,1) circle (0.07);
+% \draw (1.5,1) -- (2.5,1); 
+% \draw[->,semithick] (0,0.75) -- (0,0.25);
+% \draw (-2.75,-0.1) -- (0.75,-0.1); 
+% \draw[fill=black] (0,-0.1) circle (0.07);
+% \draw (1.25,-0.1) -- (2.75,-0.1);  
+% \draw[->,semithick] (0,-0.35) -- (0,-0.85);
+% \draw (-3,-1.2) -- (3,-1.2);
+% \draw[fill=black] (0,-1.2) circle (0.07); 
 % \end{scope}
-% \end{tikzpicture}
-% \end{minipage}
-%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
-% \begin{minipage}{8cm}
-% \begin{tikzcd}[cramped,column sep=tiny]
+%
+%\node at (4,0){$\rightsquigarrow$};
+%
+%\node at (7,0) {
+%\begin{tikzcd}[cramped,column sep=tiny]
 %a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
@@
 %\end{tikzcd}
-%\end{minipage}
+%};
+%
+%\end{tikzpicture}
 %\end{center}
@@
 
-\begin{figure}
-\begin{center}
- \begin{tikzpicture}
- \begin{scope}[line cap=round,ultra thick]
- \draw (-2.5,1) -- (-1.5,1); 
- \draw (-1,1) -- (0.5,1); 
- \draw[fill=black] (0,1) circle (0.07);
- \draw (1.5,1) -- (2.5,1); 
- \draw[->,semithick] (0,0.75) -- (0,0.25);
- \draw (-2.75,-0.1) -- (0.75,-0.1); 
- \draw[fill=black] (0,-0.1) circle (0.07);
- \draw (1.25,-0.1) -- (2.75,-0.1);  
- \draw[->,semithick] (0,-0.35) -- (0,-0.85);
- \draw (-3,-1.2) -- (3,-1.2);
- \draw[fill=black] (0,-1.2) circle (0.07); 
- \end{scope}
-
-\node at (4,0){$\rightsquigarrow$};
-
-\node at (7,0) {
-\begin{tikzcd}[cramped,column sep=tiny]
-a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
-am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
-amb  & \in &M 
-\end{tikzcd}
-};
-
-\end{tikzpicture}
-\end{center}
-\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
-\label{fig:bimodasfact}
-\end{figure}
-
 \subsection{Factorization algebras}
@@
 The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$. 
-
-\begin{rmk}
-A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens.
+Note that Weiss covers are required to ``know'' about every configuration of finitely many points,
+and so they often contain many opens.
+For a smooth $n$-manifold $M$, one cover is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
+
+%\begin{rmk}
+%A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens.
 It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$.
 For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection
-\[
-\{ U_i^n \mid i \in I\}
-\]
-provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
-\end{rmk}
-
-\begin{eg}\label{WeissAsExponential}
-For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$.
+%\[
+%\{ U_i^n \mid i \in I\}
+%\]
+%provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
+%\end{rmk}
+%
+%\begin{eg}\label{WeissAsExponential}
+%For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$.
 One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
@@
 The collection of all finite, pairwise disjoint union of elements of $\fD$ is a countable Weiss cover.~\hfill $\Diamond$
-\end{eg}
-
-Now that we have a notion of cover, we can formulate the local-to-global property for factorization algebras,
-which amounts to being a cosheaf for the Weiss topology.
-For concreteness' sake, we will continue to have our prefactorization algebras take values in ${\rm dgVect}$,
-but it is straightforward to generalize by allowing the values to live in, say, a symmetric monoidal $\infty$-category.
-
-Let us provide the definition of a homotopy cosheaf. 
-Let $\Phi$ be a precosheaf on $M$ with values in cochain complexes.
-Let $\mathfrak{U} = \{U_i \mid i \in I\}$ be a cover of some open subset $U$ of $M$.
-Consider the cochain complex with values in cochain complexes whose $-k$th term is
-\[
-\bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}),
-\]
-and note that this term has an ``internal'' differential arising from $\Phi$.
-The ``external'' differential is the alternating sum of the structure maps arising from inclusion of $k+1$-fold intersections into $k$-fold intersections.
-The \emph{\v{C}ech complex of $\mathfrak{U}$ with coefficients in $\Phi$} is the totalization of this double complex:
-$$
-\check{C}(\mathfrak{U}, \Phi) = \bigoplus_{k=0}^\infty \left( \bigoplus_{\stackrel{j_0,\ldots, j_k \in I}{j_i \text{ all distinct}}} \Phi (U_{j_0} \cap \cdots \cap U_{j_k}) [ k]   \right).
-$$
-There is a natural map from the $0$th term (of the double complex) to $\Phi(U)$ given by the sum of the structure maps $\Phi(U_i) \to \Phi(U)$.
-Thus, the \v{C}ech complex possesses a natural map to $\Phi(U)$.
-We say that $\Phi$ is a \emph{homotopy cosheaf} if the natural map from the \v{C}ech complex to $\Phi(U)$ is a quasi-isomorphism for every open $U \subset M$ and every open cover of $U$.
-This \v{C}ech complex is simply the dual of the \v{C}ech complex for sheaves of cochain complexes.
-In more sophisticated language, the \v{C}ech complex describes the homotopy colimit of $\Phi$ on this simplicial diagram.
-
-We can now define our main object of interest.
+%\end{eg}
+
+Now that we have a notion of cover, we can formulate the local-to-global property for factorization algebras.
 
 \begin{dfn}
-A \emph{factorization algebra} is a prefactorization algebra $\cF$ on $M$ valued in $\Ch$ \owen{change to dgVect?}, with the property that for every open set $U \subset X$ and Weiss cover $\mathfrak{U}$ of $U$, the natural map
-$$
-\check{C}(\mathfrak{U},\cF) \to \cF(U)
-$$
-is a quasi-isomorphism. That is, $\cF$ is a homotopy cosheaf with respect to the Weiss topology.
+A \emph{factorization algebra} is a prefactorization algebra $\cF$ on $M$ with values in a symmetric monoidal category $\cC^\otimes$ that is a cosheaf for the Weiss topology.
 \end{dfn}
 
-We also formulate a multiplicativity condition, as follows.
-
-\begin{dfn}
-A factorization algebra $\cF$ is \emph{multiplicative} if for every pair $U,V$ of disjoint open subsets of $M$, the structure map
-$$
-\cF(U) \otimes \cF(V) \to \cF(U \sqcup V) 
-$$
-is a quasi-isomorphism.
-\end{dfn}
+Being a cosheaf means that for any open set $U \subset M$ and any Weiss cover $\{ U_\alpha\}$ of $U$,
+the value of $\cF(U)$ can be reconstructed using the \v{C}ech complex:
+\[
+\cF(U) \xto{\simeq} \check{C}(\mathfrak{U},\cF).
+\]
+Replacing cochain complexes with some other category (or $\infty$-category), one needs to take a (homotopy) colimit over the \v{C}ech nerve of the Weiss cover.
 
@@
 
-It can be hard to check whether a given $\cF$ is a homotopy cosheaf, since computing the \v{C}ech complex is typically difficult.
-There are some useful abstract results, such as the fact that a factorization algebra is determined by its behavior on a basis for the Weiss topology.
-But there is also a rich source of examples in differential geometry, and hence from physics.
-
-Given a vector bundle $E \to M$ (possibly a graded vector bundle), 
-let $E^{\boxtimes m} \to M^m$ denote the external product of $E$ with itself $m$ times.
-Let $\cE_c(U)$ denote compactly supported sections of $E$ over $U$, 
-and similarly let $\cE^{\boxtimes m}_c(U^m)$ denote compactly supported sections of $E^{\boxtimes m}$ over $U^m$.
-Let $\Sym^m(\cE_c)(U)$ denote the sections that are invariant under the action of the symmetric group $S_m$ on~$U^m$.
-We define a functor $\Sym(\cE_c): \Open(M) \to \Vect$ by
-\[
-\Sym(\cE_c)(U) = \bigoplus_m \Sym^m(\cE_c)(U),
-\]
-which is a kind of symmetric algebra on $\cE_c(U)$.
-(Those familiar with functional analysis will note that taking sections of the product bundles is a nice way of completing the algebraic tensor product of sections on each component bundle.)
-This construction is actually a cosheaf for the Weiss topology, just as $\cE_c$ is a cosheaf for the ordinary topology;
-in this sense, the Weiss topology is an ``exponentiation'' of the ordinary topology just as $\Sym(V)$ is an ``exponentiation'' of a vector space~$V$.
-We have seen in Example~\ref{ex:SymOfCosheaf} how $\Sym(\cE_c)$ determines a prefactorization algebra,
-so the following theorem should be plausible.
-
-\begin{thm}[\owen{cite book}]
-For $E \to M$ a graded vector bundle, the functor $\Sym(\cE_c)$ encodes a factorization algebra on $M$.
-If we equip $\cE_c$ with a differential operator $d$ of degree 1 suc that $d^2 = 0$ so that $(\cE_c, d)$ is a cosheaf of differential complexes,
-then $(\Sym(\cE_c), d)$ is a factorization algebra, where $d$ denotes the natural extension.
-\end{thm}
-
-Two examples of differential complexes play a key role in applications: 
-\begin{itemize}
-\item the de Rham complex $(\Omega^*, d)$ on a smooth manifold, which is relevant for topological field theories, and 
-\item the Dolbeault complex $(\Omega^{0,*}, \dbar)$ on a complex manifold, which is relevant for holomorphic field theories.
-\end{itemize}
-One can take, of course, these complexes with sections in a flat vector bundle (for the de Rham case) or a holomorphic vector bundle (for the Dolbeault case).
-
-\subsection{Algebras over the little discs operad}
-
-Associative algebras are familiar to every mathematician, but as we have just seen, they reflect and encode one-dimensional geometry.
-It is then natural to ask about higher-dimensional versions of algebra.
-Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-discs operad,
-which we now describe and relate to prefactorization algebras on~$\RR^n$.
-In relation to the subject of this paper, we mention that $E_n$ algebras arise naturally from $n$-dimensional topological field theories;
-we will soon introduce a holomorphic analog of $E_n$ algebras relevant to holomorphic field theories,
-modeled on the discussion here.
-
-Fix a dimension $n$. 
-Let $D^n(x,r)$ denote the open disc of radius $r$ centered at $x \in \RR^n$,
-and let $D^n$ denote the unit disc~$D^n(0,1)$.
-
-\begin{dfn}
-Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint discs:
-\[
-E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the discs $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disc $D^n$\end{tabular}}\right\}.
-\]
-\end{dfn}
-
-When $n = 1$, the operad encodes the idea of associative multiplication:
-we get pictures much like those we drew earlier with intervals, 
-except that now we can slide and stretch the intervals because we have a space of operations.
-More accurately, $E_1$ is a model for associative algebras up to homotopy; 
-it is closely related to the $A_\infty$ operad. \owen{Let me check how people compare these.}
-
-For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
-If one fixes a direction, such as a coordinate axis, and works with discs lined up in this direction,
-one sees an $E_1$ structure.
-
-\owen{Add picture? We drew 2d pictures earlier.}
-
-An algebra over this operad is called an {\em $E_n$-algebra}.
-A classic example from topology is given by taking the $n$-fold based loop space
-\[
-\Omega^n_x(X) = \{ \gamma: \overline{D^n} \to X \mcol \gamma(\partial \overline{D^n}) = x\}
-\]
-of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disc.
-Maps that send the boundary of a disc to the base point can be extended naturally to bigger discs: just send the rest of the big disc to the basepoint.
-\owen{Should I spell out the structure of the algebra?}
-Examples include \owen{What to mention?}
+%Many examples of factorization algebras satisfy an additional and desirable property,
+%which motivates the name ``factorization algebra.''
+%
+%\begin{dfn}
+%A factorization algebra $\cF$ is \emph{multiplicative} if for every pair $U,V$ of disjoint open subsets of $M$, the structure map
+%$$
+%\cF(U) \otimes \cF(V) \to \cF(U \sqcup V) 
+%$$
+%is a quasi-isomorphism.
+%\end{dfn}
+
+\subsection{How factorization algebras appear in QFT}
+
+%Associative algebras are familiar to every mathematician, but as we have just seen, they reflect and encode one-dimensional geometry.
+%It is then natural to ask about higher-dimensional versions of algebra.
+%Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-discs operad,
+%which we now describe and relate to prefactorization algebras on~$\RR^n$.
+%In relation to the subject of this paper, we mention that $E_n$ algebras arise naturally from $n$-dimensional topological field theories;
+%we will soon introduce a holomorphic analog of $E_n$ algebras relevant to holomorphic field theories,
+%modeled on the discussion here.
+%
+%Fix a dimension $n$. 
+%Let $D^n(x,r)$ denote the open disc of radius $r$ centered at $x \in \RR^n$,
+%and let $D^n$ denote the unit disc~$D^n(0,1)$.
+%
+%\begin{dfn}
+%Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint discs:
+%\[
+%E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the discs $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disc $D^n$\end{tabular}}\right\}.
+%\]
+%\end{dfn}
+%
+%When $n = 1$, the operad encodes the idea of associative multiplication:
+%we get pictures much like those we drew earlier with intervals, 
+%except that now we can slide and stretch the intervals because we have a space of operations.
+%More accurately, $E_1$ is a model for associative algebras up to homotopy; 
+%it is closely related to the $A_\infty$ operad. \owen{Let me check how people compare these.}
+%
+%For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
+%If one fixes a direction, such as a coordinate axis, and works with discs lined up in this direction,
+%one sees an $E_1$ structure.
+%
+%\owen{Add picture? We drew 2d pictures earlier.}
+%
+%An algebra over this operad is called an {\em $E_n$-algebra}.
+%A classic example from topology is given by taking the $n$-fold based loop space
+%\[
+%\Omega^n_x(X) = \{ \gamma: \overline{D^n} \to X \mcol \gamma(\partial \overline{D^n}) = x\}
+%\]
+%of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disc.
+%Maps that send the boundary of a disc to the base point can be extended naturally to bigger discs: just send the rest of the big disc to the basepoint.
+%\owen{Should I spell out the structure of the algebra?}
+%Examples include \owen{What to mention?}
 
@@
 
-This theorem, together with work in these two books, builds an explicit bridge between topology and physics.
-Topological field theories in the physicist's sense, such as perturbative Chern-Simons theory, produce locally constant factorization algebras, which can then be viewed as $E_n$ algebras and analyzed using the powerful machinery of modern homotopy theory.
-Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology.
-Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.
-
 \begin{rmk}
 We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do.
-A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}.
-We emphasize that higher categories are necessary for a rigorous development of these constructions and comparisons, although we will not emphasize that point in our discussion below, which is expository in nature.~\hfill $\Diamond$
+A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}.~\hfill $\Diamond$
 \end{rmk}
 
-\begin{rmk}
-We have shown how thinking about prefactorization algebras on a real line ``decorated'' with points (i.e., with a kind of stratification) reflects familiar algebraic objects like bimodules.
-By moving into higher dimensions and allowing more interesting submanifolds and stratifications, one generalizes this familiar algebra into new, largely-unexplored directions.
-See \cite{AyalaFrancisTanaka} for an extensive development of these ideas in the setting of locally constant factorization algebras.
-~\hfill $\Diamond$
-\end{rmk}
-
-\subsection{How factorization algebras appear in QFT}
-
-In \cite{CG1, CG2} a systematic relationship is provided between field theories and factorization algebras.
+This perspective suggests that factorization algebras offer a natural generalization to field theories on manifolds, and not just on Euclidean spaces.
+Indeed \cite{CG1, CG2} provide a systematic relationship between field theories and factorization algebras.
 The slogan is 
@@
 \end{quote}
+To physicists, this claim should not be so surprising, upon some reflection:
+the Weiss cosheaf gluing axiom offers a precise version of the idea that a quantum field theory can be fully encoded by all its $n$-point functions.
+
 To make a mathematical statement, one needs to be precise about what a field theory is.
-From hereon, whenever we speak of a classical or quantum field theory, we will mean the definitions articulated in \cite{CosBook,CG1, CG2}, which encompass the Euclidean versions of many field theories studied in physics and mathematics.
+Here, we will mean the definitions articulated in \cite{CosBook,CG1, CG2}, which encompass the Euclidean versions of many field theories studied in physics and mathematics.
 Those books use the Batalin-Vilkovisky (BV) formalism for quantization, a homological method generalizing the BRST approach and widely regarded as the most powerful and general way to quantize gauge theories.
@@
 
-In \cite{CG1}, there are several examples of this formalism in action:
-\begin{itemize}
-\item Basic examples from quantum mechanics, such as the harmonic oscillator, and it is shown how to recover the Weyl algebra and the Hamiltonians from factorization algebras living on~$\RR$. 
-\item Scalar field theory on $\RR^n$, where it is shown how the usual correlation functions are encoded in the factorization algebra on~$\RR^n$ and how canonical quantization appears via pushforward of factorization algebras.
-\item The free $\beta\gamma$ system on $\CC$---a basic example of a chiral conformal field theory---is constructed and its usual vertex algebra is extracted from the factorization algebra.
-\item Abelian Chern-Simons theory, where it is shown how dimensional reduction along a closed surface $\Sigma$ produces the Weyl algebra on the symplectic vector space $H^1(\Sigma)$ and how line operators form a (very simple!) braided monoidal category.
-\end{itemize}
-These examples, while not complicated, exhibit in detail how factorization algebras provide a bridge from action functionals to algebra in a broad sense.
-
-This formalism has shown its power in a number of nontrivial applications:
-\begin{itemize}
-\item Grady, Li, and Li \cite{GLL} give a direct connection between Fedosov quantization and the factorization algebra of a 1-dimensional field theory.
-%\item Gorbounov, Williams and I \cite{GGW} constructed rigorously a 2-dimensional QFT depending on a Calabi-Yau manifold $X$, known as the curved $\beta\gamma$ system, and showed the factorization algebra recovers the chiral differential operators of~$X$.
-\item Li and Li \cite{LiLi} constructed the topological B-model and show the factorization algebra recovers the expected topological vertex algebra (see \cite{LiVOA} for a deeper treatment).
-\item Costello, Francis, and Gwilliam \cite{CFG} have shown how the factorization algebra of Chern-Simons theory for $\fg$ encodes a quantum group $U_\hbar \fg$ over~$\CC[[\hbar]]$.
-\item Rabinovich \cite{RabAxial} showed how the local index theorem and the axial anomaly are simultaneously captured by quantizing free fermions (associated to Dirac operators).
+This theorem is also a key connection between field theories and higher algebras.
+\owen{I feel like I should say a little more, but not a lot more. I've commented out some old versions of this.}
+
+%In \cite{CG1}, there are several examples of this formalism in action:
+%\begin{itemize}
+%\item Basic examples from quantum mechanics, such as the harmonic oscillator, and it is shown how to recover the Weyl algebra and the Hamiltonians from factorization algebras living on~$\RR$. 
+%\item Scalar field theory on $\RR^n$, where it is shown how the usual correlation functions are encoded in the factorization algebra on~$\RR^n$ and how canonical quantization appears via pushforward of factorization algebras.
+%\item The free $\beta\gamma$ system on $\CC$---a basic example of a chiral conformal field theory---is constructed and its usual vertex algebra is extracted from the factorization algebra.
+%\item Abelian Chern-Simons theory, where it is shown how dimensional reduction along a closed surface $\Sigma$ produces the Weyl algebra on the symplectic vector space $H^1(\Sigma)$ and how line operators form a (very simple!) braided monoidal category.
+%\end{itemize}
+%These examples, while not complicated, exhibit in detail how factorization algebras provide a bridge from action functionals to algebra in a broad sense. 
+%
+%This formalism has shown its power in a number of nontrivial applications:
+%\begin{itemize}
+%\item Grady, Li, and Li \cite{GLL} give a direct connection between Fedosov quantization and the factorization algebra of a 1-dimensional field theory.
+%%\item Gorbounov, Williams and I \cite{GGW} constructed rigorously a 2-dimensional QFT depending on a Calabi-Yau manifold $X$, known as the curved $\beta\gamma$ system, and showed the factorization algebra recovers the chiral differential operators of~$X$.
+%\item Li and Li \cite{LiLi} constructed the topological B-model and show the factorization algebra recovers the expected topological vertex algebra (see \cite{LiVOA} for a deeper treatment).
+%\item Costello, Francis, and Gwilliam \cite{CFG} have shown how the factorization algebra of Chern-Simons theory for $\fg$ encodes a quantum group $U_\hbar \fg$ over~$\CC[[\hbar]]$.
+%\item Rabinovich \cite{RabAxial} showed how the local index theorem and the axial anomaly are simultaneously captured by quantizing free fermions (associated to Dirac operators).
 Subsequently, he recovered the Quillen determinant line~\cite{RabDet}.
-\item Costello \cite{CosYangian} introduced a 4-dimensional gauge theory whose factorization algebra recovers the Yangian,
-and subsequently gave extensive applications to quantum integrable systems with Witten and Yamazaki \cite{CWY1,CWY2, CY}.
-\end{itemize}
-There are others, connected with central topics such as mirror symmetry and the AdS/CFT correspondence, 
-and we will discuss holomorphic field theories extensively below.
-
-Thanks to the efforts of people who have adopted this BV/factorization framework,
-we now also understand its connection to many important structural aspects of QFT, 
-such as asymptotic freedom \cite{EWY}, current algebras \cite{GWcurr}, the Anderson-Higgs mechanism \cite{EG}, and the CS/WZW correspondence~\cite{GRW, CosDimGai}.
-In each case this enriched mathematical language offers a new and (we would argue) clarifying point of view.
-In turn, physics offers new vistas or rich applications for mathematicians to explore.
-
-\subsection{$E_n$ algebras from topological field theories}
-
-Although our focus in this paper is on holomorphic field theories and factorization algebras,
-it might be helpful to describe some motivating results about topological field theories and factorization algebras.
-Elliott and Safronov have \owen{not sure how much to say here, but I'm going to take a stab at writing a synoptic theorem}
-
-If one examines theories like Chern-Simons theory on $\RR^3$ or the Poisson $\sigma$-model on $\RR^2$, 
-one discovers a general format for constructing theories that was formalized by \cite{AKSZ}.
-In a nutshell, the field theory is factored into two parts: 
-the de Rham complex of the source or ``spacetime'' manifold, 
-and a Lie algebra-type object encoding a gauge Lie algebra or a ``target'' for a $\sigma$-model.
-
-\begin{dfn}
-A classical {\em AKSZ-type theory} on $\RR^d$ is a determined by an $L_\infty$-algebra $\fg$ equipped with a cyclic pairing $\langle-,-\rangle$ of degree $3-d$.
-Its {\em equation of motion} is the Maurer-Cartan equation 
-\[
-0 = \d A + \frac{1}{2} [A,A] + \frac{1}{3!}[A,A,A]_3 + \cdots = \sum_{k=1}^\infty \frac{1}{k!} [A, \ldots, A]_k
-\]
-of the $L_\infty$ algebra $\Omega^*(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
-The {\em action functional} is the expression
-\[
-S(A) = \int_{\RR^d} \sum_{k=1}^\infty \frac{1}{{k+1}!} \langle A, [A, \ldots, A]_k \rangle
-\]
-\end{dfn}
-
-Ordinary Chern-Simons theory on $\RR^3$ arises from taking $\fg$ to be a semisimple Lie algebra and a choice of invariant pairing.
-In that case, and using $\Tr$ to denote the pairing, the action functional is the familiar
-\[
-S(A) = \int_{\RR^3}  \frac{1}{2}\Tr ( A, \d A ) + \frac{1}{3!} \Tr( A, [A, A])
-\]
-and the equation of motion asks for connections with zero curvature.
-
-Many other theories can be expressed in this style, and we suggest \owen{lots of papers} for examples.
-Elliott and Safronov characterize and exhibit topological twists of supersymmetric theories as AKSZ-type theories.
-
-\begin{thm}[\cite{CG2;ElliottSafronov}]
-For a classical AKSZ-type theory on $\RR^d$, the observables 
-\[
-\Obs^{cl}(U) = \clie^*(\Omega^*(U) \otimes \fg)
-\]
-form a locally constant factorization algebra and hence determine an $E_d$ algebra~$\cA^{cl}$.
-A quantization, if it exists, determines a deformation $\cA^q$ of this $E_d$ algebra.
-
-Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
-\end{thm}
+%\item Costello \cite{CosYangian} introduced a 4-dimensional gauge theory whose factorization algebra recovers the Yangian,
+%and subsequently gave extensive applications to quantum integrable systems with Witten and Yamazaki \cite{CWY1,CWY2, CY}.
+%\end{itemize}
+%There are others, connected with central topics such as mirror symmetry and the AdS/CFT correspondence, 
+%and we will discuss holomorphic field theories extensively below.
+%
+%Thanks to the efforts of people who have adopted this BV/factorization framework,
+%we now also understand its connection to many important structural aspects of QFT, 
+%such as asymptotic freedom \cite{EWY}, current algebras \cite{GWcurr}, the Anderson-Higgs mechanism \cite{EG}, and the CS/WZW correspondence~\cite{GRW, CosDimGai}.
+%In each case this enriched mathematical language offers a new and (we would argue) clarifying point of view.
+%In turn, physics offers new vistas or rich applications for mathematicians to explore.
+
+%\subsection{$E_n$ algebras from topological field theories}
+%
+%Although our focus in this paper is on holomorphic field theories and factorization algebras,
+%it might be helpful to describe some motivating results about topological field theories and factorization algebras.
+%Elliott and Safronov have \owen{not sure how much to say here, but I'm going to take a stab at writing a synoptic theorem}
+%
+%If one examines theories like Chern-Simons theory on $\RR^3$ or the Poisson $\sigma$-model on $\RR^2$, 
+%one discovers a general format for constructing theories that was formalized by \cite{AKSZ}.
+%In a nutshell, the field theory is factored into two parts: 
+%the de Rham complex of the source or ``spacetime'' manifold, 
+%and a Lie algebra-type object encoding a gauge Lie algebra or a ``target'' for a $\sigma$-model.
+%
+%\begin{dfn}
+%A classical {\em AKSZ-type theory} on $\RR^d$ is a determined by an $L_\infty$-algebra $\fg$ equipped with a cyclic pairing $\langle-,-\rangle$ of degree $3-d$.
+%Its {\em equation of motion} is the Maurer-Cartan equation 
+%\[
+%0 = \d A + \frac{1}{2} [A,A] + \frac{1}{3!}[A,A,A]_3 + \cdots = \sum_{k=1}^\infty \frac{1}{k!} [A, \ldots, A]_k
+%\]
+%of the $L_\infty$ algebra $\Omega^*(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
+%The {\em action functional} is the expression
+%\[
+%S(A) = \int_{\RR^d} \sum_{k=1}^\infty \frac{1}{{k+1}!} \langle A, [A, \ldots, A]_k \rangle
+%\]
+%\end{dfn}
+%
+%Ordinary Chern-Simons theory on $\RR^3$ arises from taking $\fg$ to be a semisimple Lie algebra and a choice of invariant pairing.
+%In that case, and using $\Tr$ to denote the pairing, the action functional is the familiar
+%\[
+%S(A) = \int_{\RR^3}  \frac{1}{2}\Tr ( A, \d A ) + \frac{1}{3!} \Tr( A, [A, A])
+%\]
+%and the equation of motion asks for connections with zero curvature.
+%
+%Many other theories can be expressed in this style, and we suggest \owen{lots of papers} for examples.
+%Elliott and Safronov characterize and exhibit topological twists of supersymmetric theories as AKSZ-type theories.
+%
+%\begin{thm}[\cite{CG2;ElliottSafronov}]
+%For a classical AKSZ-type theory on $\RR^d$, the observables 
+%\[
+%\Obs^{cl}(U) = \clie^*(\Omega^*(U) \otimes \fg)
+%\]
+%form a locally constant factorization algebra and hence determine an $E_d$ algebra~$\cA^{cl}$.
+%A quantization, if it exists, determines a deformation $\cA^q$ of this $E_d$ algebra.
+%
+%Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
+%\end{thm}
 

### 2022-08-29 draft.tex
merge error

--- 2022-08-21 draft.tex
@@
 \def\Vect{\operatorname{Vect}}
-\def\pAA{\mathring{\AA}}
 \def\jou{{\mathtt{j}}}
@@
 \def\til{\Tilde}
+\def\Sol{\text{Sol}}
+\def\Spec{\text{Spec}}
 
@@
 consider pure four-dimensional supersymmetric Yang--Mills theory with $\cN=1$ supersymmetry.
-The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional and there exists a unique holomorphic twist $Q$ up to equivalence. 
-%The sum of two copies of the spin representations.
-%\owen{Did I get that right?}
-
-Then, the holomorphic twist
-
-\begin{thm}[\owen{cite GRW, maybe also mention our work with Chris?}]
-Donaldson--Witten theory, the Kapustin twist, and holomorphic BF theory for $\fg[\epsilon]$ each admit an exact and finite quantization at one loop.
-\end{thm}
+The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional and there exists a unique holomorphic twist $Q$ (up to equivalence).
+In this dimension, with this amount of supersymmetry, there does not exist a topological twist.
+The holomorphic twist of the theory with respect to $Q$ is equivalent to holomorphic BF theory on $\CC^2$.
+
+This ends our discussion of twisting supersymmetric gauge theories.
+There are many other appearances of holomorphic field theories in the context of supersymmetry.
+Here is a (very) non-exhaustive list.
+
+\begin{itemize}
+\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
+For instance, the closed string field theory of the topological B-model on a Calabi--Yau threefold is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
+This theory is defined on any Calabi--Yau manifold. 
+The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
+\item
+It is possible to make sense of Kodaira--Spencer theory in other dimensions.
+In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
+\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
+Often, the theory you start with on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
+\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
+For instance, holomorphic BF theory on (super) twistor space associated to $\RR^4$ is equivalent to a self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
+\end{itemize}
+
+\subsection{An extended aside on perturbative quantization}
+
+So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
+In the topological setting, renormalization is very well-controlled.
+The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
 
@@
 
-\owen{More examples}
-
-\begin{itemize}
-\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
-For instance, the closed string field theory of the topological B-model is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
-This theory is defined on any Calabi--Yau manifold. 
-The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.  
-\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
-Often, the theory you start with on the nilpotence variety is holomorphic \cite{SWpure}. 
-\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
-For instance, holomorphic BF theory on twistor space associated to $\RR^4$ is equivalent to a self-dual limit of Yang--Mills theory. 
-\end{itemize}
-
-\subsection{An extended aside on perturbative quantization}
-
-\owen{Sketch Brian's main results --- and Si's! --- and compare them with configuration space method of A-S and K for TFTs, subsequently developed by others}
-
 Although holomorphic field theories had already appeared in practice,
@@
 \begin{itemize}
-\item gave a precise definition of a holomorphic field theory in the BV formalism,
-modeled on and compatible with Costello's approach;
 \item established key analytic results about holomorphic renormalization, 
@@
 
-In this section we describe  associative algebras and their ``higher'' generalizations, like $A_\infty$ algebras, related to holomorphic field theories,
+In this section we describe  associative algebras and their ``homotopical'' generalizations, like $A_\infty$ algebras, related to holomorphic field theories,
 following the relationship of associative algebras to quantum mechanics and of vertex algebras to chiral conformal field theory.
@@
 If a Lie group $G$ acts on $X$ by symplectomorphisms (i.e., respects the symplectic structure),
-there is a map of Lie algebras $\rho: \fg \to {\rm SympVect}(X)$ so that an ``infinitesimal symmetry'' $x \in \fg$ acts by a symplectic vector field.
+there is a map of Lie algebras $\rho \colon\fg \to {\rm SympVect}(X)$ so that an ``infinitesimal symmetry'' $x \in \fg$ acts by a symplectic vector field.
 In many cases, such infinitesimal symmetries are realized as observables: 
-there is a map of Lie algebras $H_\rho: \fg \to C^\infty(X)$ such that $\{ H_\rho(x), - \} = \rho(x)$.
+there is a map of Lie algebras $H_\rho \colon \fg \to C^\infty(X)$ such that $\{ H_\rho(x), - \} = \rho(x)$.
 One says that each element $x$ has a Hamiltonian function $H_\rho(x)$ whose associated Hamiltonian vector field is $\rho(X)$.
@@
 Such a map is sometimes called a {\em quantum moment map},
-as $H_\rho$ is the pullback of (polynomial) functions along a moment map~$\mu_\rho: X \to \fg^*$.
+as $H_\rho$ is the pullback of (polynomial) functions along a moment map~$\mu_\rho \colon X \to \fg^*$.
 
@@
 Then we posit for the relevant phase space, the ``symplectic complex manifold'' $V[z,z^{-1}]$,
-by which we mean the $V$-valued Laurent polynomials in a coordinate $z$ on the punctured plane $\CC^\times = \CC -\{0\}$.
-The space encodes algebraic maps from the variety $\CC^\times$ to $V$,
+by which we mean the $V$-valued Laurent polynomials in a coordinate~$z$.
+The space encodes algebraic maps from the variety $\CC^\times = \CC \setminus 0$ to $V$,
 so we view it as a kind of algebraic loop space of~$V$.
@@
 There is one last feature we would like to point out, before we turn to explaining our interest in this space and algebra.
-The inclusion $\CC^\times \hookrightarrow \CC$ means that any algebraic map  $\phi: \CC \to V$ restricts to an algebraic map $\phi: \CC^\times \to V$.
+The inclusion $\CC^\times \hookrightarrow \CC$ means that any algebraic map  $\phi: \CC \to V$ restricts to an algebraic map $\phi \colon \CC^\times \to V$.
 In our notation, this restriction map is the inclusion $V[z] \hookrightarrow V[z,z^{-1}]$ of $V$-valued polynomials in $V$-valued Laurent polynomials.
@@
 The algebraic maps are precisely $T^* \CC^n$-valued Laurent polynomials.
+\footnote{One can extract the algebraic model from the holomorphic model by taking formal power series expansions at the level of observables.}
 
@@
 
-The subspace of ``contractible formal loops" $V[[z]]$ inside $V((z))$ produces a module for $\cO(V((z)))$ given by $\cO(V[[z]]$. 
+The subspace of ``contractible formal loops" $V[[z]]$ inside $V((z))$ produces a module for $\cO(V((z)))$ given by $\cO(V[[z]])$. 
 (This module is in fact a quotient algebra.)
@@
 \[
-Y: {\rm Vac}[V] \to \End({\rm Vac}[V])[[z, z^{-1}]],
+Y \colon {\rm Vac}[V] \to \End({\rm Vac}[V])[[z, z^{-1}]],
 \]
@@
 the action is independent of $z$.
-On the other hand, if we consider the infinitesimal action $\rho: \fg \to {\rm SympVect}(V)$,
-there is, in fact, a natural extension to a ``local'' symmetry $\rho^{\rm loc}: \fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
+On the other hand, if we consider the infinitesimal action $\rho \colon \fg \to {\rm SympVect}(V)$,
+there is, in fact, a natural extension to a ``local'' symmetry $\rho^{\rm loc} \colon \fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
 Geometrically, a $\fg$-valued function $x(z)$ acts pointwise (with respect to the formal disc) on the formal loop space.
@@
 \]
-\owen{Check conventions.}
 There is thus a central extension of the loop algebra 
@@
 \[
-\widehat{H}^{\rm loc}_\rho: \widehat{\fg} \to W[V],
-\]
-sometimes called {\em free field realization} of the affine Lie algebra~$\widehat{\fg}$.
-This relationship --- and its extension to a map between the vertex algebras associated to $\widehat{\fg}$ and $V$ --- is a modest \owen{better adjective?} extract of the rich dialogue that has developed between complex analysis, representation theory, and the physics of chiral conformal field theory.
+\widehat{H}^{\rm loc}_\rho \colon \widehat{\fg} \to W[V] .
+\]
+This is an example of a {\em free field realization} for the affine Lie algebra~$\widehat{\fg}$.
+This relationship --- and its extension to a map between the vertex algebras associated to $\widehat{\fg}$ and $V$ --- is small part of the rich dialogue that has developed between complex analysis, representation theory, and the physics of chiral conformal field theory.
 (To get Riemann surfaces into the game, we will need a richer framework than ordinary algebra.)
@@
 
-\subsection{Reduction vs chiralization}
-
-\owen{We should introduce the idea here and revisit later}
-\brian{Explain dimensional reduction vs compactification.
-From topological AKSZ theory to holomorphic one.}
+\subsection{Reduction vs. chiralization}
+
+In physics, the relationship between the Weyl algebra on generators $p,q$ and its loopy version $W[V]$ is through a process called `dimensional reduction'.
+The key idea is that to any quantum mechanical system there is an algebra of operators---the loopy version of the Weyl algebra arises from a quantum mechanical system on the infinite-dimensional space of loops in the symplectic vector space $V$.
+We will unpack this statement in the language of fields and Lagrangians.
+
+The ordinary Weyl algebra on a symplectic vector space $V$ arises from the quantization of ordinary mechanics on the symplectic vector space $V$.
+We can also include a Hamiltonian $H \in \cO(V)$ which acts on the Weyl algebra by the commutator $[H,-]$.
+If we understand the fields of this system as smooth maps $\phi = \phi(t)$ valued in $V$, then the Lagrangian description of this system is 
+\[
+L_{1d} (\phi) = \omega(\phi , \d \phi) + H(\phi) \d t ,
+\]
+where $\d \colon C^\infty(\RR) \otimes V \to \Omega^1(\RR) \otimes V$ is the de Rham differential.
+
+The chiral version of this setup is to look at fields $\phi = \phi(z,\zbar)$ valued in $V$ where $(z,\zbar) \in \CC^\times$.
+The action functional is 
+\[
+L_{2d}(\phi) = \omega(\phi, \dbar \phi) \d z ,
+\]
+where $\dbar \colon C^\infty(\CC^\times)\otimes V \to \Omega^{0,1}(\CC^\times) \otimes V$ is the Dolbeault differential.
+
+We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of `compactification'. 
+It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
+Then, compactification involves integrating out the remaining circle direction.
+Concretely, any smooth function on $\CC^\times$ can be decomposed in polar coordinates as
+\[
+\phi(r,\theta) = \sum_{k \in \ZZ} \phi_k(r) e^{2 \pi i k \theta} ,
+\]
+where $\phi_k(r)$ is a smooth function depending only on the radius $r \in \RR_+$.
+Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
+We interpret $\sum_{k \in \ZZ} \phi_k(t)$ as smooth map from $\RR$ to the formal (free) loop space $LV = V[z,z^{-1}]$.
+
+At the level of Lagrangians we can integrate $L_{2d}(\phi)$ over $S^1$ to obtain the following infinite sum of one-dimensional Lagrangians
+\beqn
+L_{1d}(\phi_k, k \in \ZZ) = \sum_{k\in \ZZ} \phi_{-k} \d \phi_{k} + k \phi_k \phi_{-k} \d t .
+\eeqn 
+Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
+In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian which encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.
 
@@
 so this seems uninteresting.
-One should notice, however, that punctured affine space $\mathring{\AA}^d = \CC^d -\{0\}$ is, as a scheme, not affine, 
+One should notice, however, that punctured affine space $\mathring{\CC}^d = \CC^d -\{0\}$ is, as a scheme, not affine, 
 and so the {\em derived} global sections of the structure sheaf $\cO_{\rm alg}$ are interesting:
 \[
-H^*(\RR \Gamma(\pAA^d, \cO_{\rm alg})) = H^* (\mathring{\AA}^d, \cO_{\rm alg}) 
+H^*(\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg})) = H^* (\mathring{\AA}^d, \cO_{\rm alg}) 
 = \begin{cases} 
@@
 that aims to emphasize analogies with the $d=1$ case.
-When $d=1$, note that this computation recovers the Laurent polynomials,
+When $d=1$, note that this recovers the Laurent polynomials,
 so when $d > 1$, 
@@
 Checking this computation is a straightforward exercise in algebraic geometry;
-for instance, use the cover by the affine opens of the form $\AA^d \setminus \{z_i =0\}$.
+for instance, use the cover by the affine opens of the form $\AA^d - \{z_i =0\}$.
 \owen{I want to discuss the module structure on the $d-1$-component.}
@@
 \[
-\RR \Gamma(\pAA^d, \cO_{\rm alg}) \to \RR \Gamma(\pAA^d, \cO_{\rm an}) \simeq \Omega^{0,*}(\pAA^d)
-\]
-that replaces our inclusion of Laurent polynomials into the Dolbeault complex on~$\pAA^d$.
+\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg}) \to \RR \Gamma(\mathring{\CC}^d, \cO_{\rm an}) \simeq \Omega^{0,\bu}(\mathring{\CC}^d)
+\]
+that replaces our inclusion of Laurent polynomials into the Dolbeault complex on~$\mathring{\CC}^d$.
 
@@
 Just as $\CC^\times$ deformation-retracts onto the unit circle,
-the punctured affine space $\pAA^d$ retracts onto the unit sphere $S^{2d-1}$.
+the punctured affine space $\mathring{\CC}^d$ retracts onto the unit sphere $S^{2d-1}$.
 The Bochner-Martinelli kernel 
@@
 \]
-determines a cohomology class of degree $d-1$, and we identify it with $1/z_1 \cdots z_d$ in our basis above,
+determines a cohomology class of degree $d-1$, and we identify it with $1/(z_1 \cdots z_d)$ in our basis above,
 so that $\omega_{BM}$ generates its cohomology group under multiplication by polynomials in the $z_j^{-1}$.
@@
 \[
-\Res: \RR \Gamma(\pAA^d, \cO_{\rm alg})  \to \CC
+\Res \colon \RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg})  \to \CC[1-d]
 \]
@@
 \]
-When $d =1$, this formula reduces to the usual residue map.
-\owen{That's a bit misleading, maybe, but the integral really does only care about the cohomology class.}
-
-The ingredients are thus in place to mimic the construction of the Weyl algebra for the formal loop space, of the affine Lie algebras, and of free field realization, but now with $\pAA^d$ in place of $\pAA^1 = \CC^\times$.
+
+The ingredients are almost in place to mimic the construction of the Weyl algebra for the formal loop space, of the affine Lie algebras, and of free field realization, but now with $\mathring{\CC}^d$ in place of $\mathring{\CC}^1 = \CC^\times$.
+We must be careful about parity, however. 
+In dimension $d = 1$, the Laurent polynomials valued in a symplectic vector space $V[z,z^{-1}]$ again has the structure of a symplectic vector space via the residue. 
+Because of the appearance of the cohomological shift in the higher dimensional residue it is no longer the case that $V \otimes \RR\Gamma(\mathring{\CC}^d, \cO_{alg})$ is symplectic if $V$ is.
+
+Let's consider the case $d = 2$ for concreteness. 
+The residue map $\Res$ above is then of cohomological degree $-1$. 
+Thus, to get a symplectic pairing on $V \otimes \RR\Gamma(\mathring{\CC}^d, \cO_{alg})$ via the residue we can ask that $V$ is equipped with a {\em $1$-shifted symplectic structure}. 
+A typical example of such a space is $V = \T^*[1] L = L \oplus L^*[1]$, where $L$ is any vector space.
+
 Reversing our treatment above, we first discuss the higher Kac-Moody algebras, 
@@
 \item
-The dg commutative algebra $(A_d,\dbar)$ is a model for $\RR \Gamma(\pAA^d, \sO_{\rm alg})$:
-\[
-A_d \simeq \RR\Gamma(\pAA^{d}, \sO^{alg}) .
-\]
-Similarly, $(A_d^{p,*},\dbar) \simeq \RR \Gamma(\pAA^{d}, \Omega^{p}_{\rm alg})$.
+The dg commutative algebra $(A_d,\dbar)$ is a model for $\RR \Gamma(\mathring{\CC}^d, \sO_{\rm alg})$:
+\[
+A_d \simeq \RR\Gamma(\mathring{\CC}^{d}, \sO^{alg}) .
+\]
+Similarly, $(A_d^{p,*},\dbar) \simeq \RR \Gamma(\mathring{\CC}^{d}, \Omega^{p}_{\rm alg})$.
 \item There is a dense map of commutative bigraded algebras
@@
 
-We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\pAA^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disc) into $\fg$,
+We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\mathring{\CC}^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disc) into $\fg$,
 just as $\fg[z,z^{-1}]$ provides a kind of loop algebra.

### 2022-08-30 draft.tex
unsaved changes
finished subsubsection on funcotrial tfts

@@
 
-\owen{mention some history (e.g., Manin!) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
+\owen{mention some history (e.g., Manin!
+Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
 
@@
 One can mimic the version of Witten descent for the topological case to produce observables from local observables.
+
+\subsection{Operator product expansion and holomorphic Poisson algebras}
+
+\owen{discuss OPE and explain the shifted Poisson structure}
 
@@
 
-\subsection{Factorization algebras}
+\subsection{Meet factorization algebras}
 
@@
 and so they often contain many opens.
-For a smooth $n$-manifold $M$, one cover is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
+For a smooth $n$-manifold $M$, a useful Weiss cover is the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
+(If one has a metric on the manifold, one can work with unions of ``small'' discs.)
 
@@
 
-The reader can check by hand that for an ordinary algebra $A$, the value on the circle is $A/[A,A] = {\rm HH}_0(A)$.
 This theorem tells us that factorization homology can be seen as a generalization of Hochschild homology,
@@
 \end{quote}
-To physicists, this claim should not be so surprising, upon some reflection:
-the Weiss cosheaf gluing axiom offers a precise version of the idea that a quantum field theory can be fully encoded by all its $n$-point functions.
+To physicists, this claim should not be so surprising:
+the Weiss cosheaf condition offers a precise version of the idea that a quantum field theory can be fully encoded by all its $n$-point functions.
 
@@
 
-More generally, given a map of Lie groups $G \to O(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.
-
-Scheimbauer's thesis then provides a functorial field theory in the sense of Atiyah, Segal, and Lurie.
+\subsubsection{Relating to the Atiyah-Segal approach to TFTs}
+
+Atiyah \cite{AtiTFT} offered a mathematical definition for topological field theories that uses symmetric monoidal functors out of bordism categories.
+His approach was inspired by Segal's definition of a conformal field theory \cite{SegCFT},
+and these notions have subsequently undergone extensive development.
+Notably, Baez and Dolan \cite{BaeDol} suggested and advocated for fully extended TFTs; 
+their vision was revisited by Lurie \cite{LurieTFT}, who used modern machinery to provide a roadmap for using fully extended TFTs and for proving the cobordism hypothesis.
+
+An important suggestion from \cite{LurieTFT} is that factorization homology allows one to produce nontrivial examples: 
+every $E_d$ algebra provides a fully extended $d$-dimensional framed TFT,
+albeit taking values in a higher analogue of the Morita bicategory (which works for the $d=1$ case).
+Scheimbauer \cite{Scheim} implemented Lurie's suggestion.
 
 \begin{thm}
-Given a homotopically $SO(d)$-trivial quantization of a classical AKSZ theory on $\RR^d$, 
-factorization homology of the quantum observables 
-\[
-\int_{(-)} \cA^q \colon {\rm Bord}^{or}_d \to {\rm Alg}_d
-\]
-determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of $E_d$ algebras.
+For any $E_d$ algebra $A$, the functor
+\[
+\int_{(-)} A \colon {\rm Bord}^{or}_d \to {\rm Alg}_d
+\]
+determines a fully extended framed $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of $E_d$ algebras.
 \end{thm}
 
-A similar claim applies to the general case with a map $G \to O(d)$.
+In combination with the theorem of Elliott and Safronov, we can connect action functionals --- the physicist's usual description of a field theory --- to Atiyah-Segal functorial field theories.
+
+\begin{cor}
+For any Lagrangian field theory satisfying the hypotheses of Theorem~\ref{}, 
+there is a fully extended framed $d$-dimensional field theory 
+given by $\int_{(-)} \cA^q$ where $\cA^q$ denotes the $E_d$ algebra of quantum observables.
+\end{cor}
+
+More generally, given a map of Lie groups $G \to O(d)$ and a compatible $G$-action on the theory, 
+a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra and, by Lurie's work, a $G$-framed fully extended $d$-dimensional TFT.
+It is interesting to ask how these kinds of functorial field theories intertwine with the better-known examples.
+
+In this survey we use factorization algebras to capture the rich algebraic structure of holomorphic field theories,
+but these connections with functorial TFTs raise the question of producing functorial holomorphic field theories.
 
@@
 \owen{revisit this theme, and discuss the "modes" algebra}
-
-\subsection{Operator product expansion and holomorphic Poisson algebras}
-
-\owen{discuss OPE and explain the shifted Poisson structure}
 

### 2022-08-30 draft.tex
sec 2 done

@@
 \renewcommand{\op}{\operatorname}
+\def\lie#1{\ensuremath{\mathfrak{#1}}}
 
@@
 and there is a Lie algebra map
-\[
+\beqn\label{eqn:freefield1}
 \widehat{H}^{\rm loc}_\rho \colon \widehat{\fg} \to W[V] .
-\]
+\eeqn
 This is an example of a {\em free field realization} for the affine Lie algebra~$\widehat{\fg}$.
@@
 Let $V$ denote a complex vector space (no longer required to be symplectic).
-The naive idea is to replace the algebraic loop space $\Map(\CC^\times,  V)$ with a higher-dimensional analog $\Map(\CC^d -\{0\}, V)$.
+The naive idea is to replace the algebraic loop space $\Map(\CC^\times,  V)$, or its formal version $\Map(\Hat{D}^\times, V)$, with a higher-dimensional analog $\Map(\CC^d -\{0\}, V)$.
 If one considers ordinary algebraic or holomorphic maps for $d > 1$, 
@@
 \[
-H^*(\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg})) = H^* (\mathring{\AA}^d, \cO_{\rm alg}) 
+H^\bu(\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg})) = H^\bu (\mathring{\AA}^d, \cO) 
 = \begin{cases} 
-0, & * \neq 0, d-1 \\ 
-\CC[z_1,\ldots,z_d], & * = 0 \\ 
-\CC[z_1^{-1},\ldots,z_d^{-1}] \frac{1}{z_1 \cdots z_d}, & * = d-1 
-\end{cases},
-\]
-where we are providing a natural basis for the cohomology 
+0, & \bu \neq 0, d-1 \\ 
+\CC[z_1,\ldots,z_d], & \bu = 0 \\ 
+\CC[z_1^{-1},\ldots,z_d^{-1}] \frac{1}{z_1 \cdots z_d}, & \bu = d-1 
+\end{cases} .
+\]
+Here $\mathring{\AA}^d$ stands for punctured affine space as a scheme. 
+We are providing a natural basis for the cohomology 
 that aims to emphasize analogies with the $d=1$ case.
@@
 Checking this computation is a straightforward exercise in algebraic geometry;
-for instance, use the cover by the affine opens of the form $\AA^d - \{z_i =0\}$.
-\owen{I want to discuss the module structure on the $d-1$-component.}
+for instance, use the cover by the affine opens of the form $\CC^d - \{z_i =0\}$.
+The full cohomology has the structure of a commutative algebra. 
+In degree zero, the algebra structure is the ordinary one on functions, or polynomials.
+The module structure in the basis above is given by the apparent multiplication: $z_i^k \cdot z_i^{-l-1} = z_i^{k-l-1}$ if $k < l$ and zero otherwise.
 
@@
 \[
-\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg}) \to \RR \Gamma(\mathring{\CC}^d, \cO_{\rm an}) \simeq \Omega^{0,\bu}(\mathring{\CC}^d)
-\]
-that replaces our inclusion of Laurent polynomials into the Dolbeault complex on~$\mathring{\CC}^d$.
-
-There is a natural analog of the residue map as well.
-Just as $\CC^\times$ deformation-retracts onto the unit circle,
-the punctured affine space $\mathring{\CC}^d$ retracts onto the unit sphere $S^{2d-1}$.
-The Bochner-Martinelli kernel 
-\[
-\omega_{BM} = \frac{(d-1)!}{(2 \pi i)^d} \frac{1}{(z\zbar)^d} \sum_{i=1}^d (-1)^{i-1} \zbar_i\, \d \zbar_1 \wedge \cdots \wedge \Hat{\d \zbar_i} \wedge \cdots \wedge \d \zbar_d
-\]
-determines a cohomology class of degree $d-1$, and we identify it with $1/(z_1 \cdots z_d)$ in our basis above,
-so that $\omega_{BM}$ generates its cohomology group under multiplication by polynomials in the $z_j^{-1}$.
-When $d = 1$, note that $\omega_{BM} = (1/2\pi i)\d z/z$, the kernel in the Cauchy residue formula.
-It is also quick to check that
-\[
-\omega_{BM} \wedge \d z_1 \wedge \cdots \wedge \d z_d
-\]
-pulls back to a volume form on the unit sphere $S^{2d-1}$.
-Hence, we define a residue map
-\[
-\Res \colon \RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg})  \to \CC[1-d]
-\]
-by
-\[
+\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg}) \to \RR \Gamma(\mathring{\CC}^d, \cO_{\rm an}) \simeq \Omega^{0,\bu}(\mathring{\CC}^d).
+\]
+We can also replace punctured affine space $\mathring{\AA}^d$ by the punctured formal disk
+$\mathring{\DD}^d$.
+Here the cohomology is identical to the above formula except in degree zero polynomials are replaced by power series.
+
+It is important to have an explicit dg commutative algebra that models the derived global sections for functions on punctured formal disk,
+and not just the cohomology groups.
+There is a beautiful, explicit dg model $\sfA^\bu_d$ for the formal version derived global sections due to Faonte-Hennion-Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities.
+While we won't go into details about this model, we remark on a few important points all of which we take from \cite{FHK}:
+\begin{itemize}
+\item The complex $\sfA^\bu_d$ is concentrated in degrees $0,\ldots,d-1$ and its cohomology is the same as the cohomology of $\RR \Gamma(\mathring{\DD}^d, \cO)$ described above.
+\item There is a polynomial version $\sfA_{d,poly}^\bu$ and explicit embeddings of commutative dg algebras 
+\beqn
+\sfA_{d}^\bu \hookleftarrow \sfA_{d,poly}^\bu \hookrightarrow \Omega^{0,\bu}(\CC^d - 0) .
+\eeqn
+The left embedding replaces the inclusion of Laurent polynomials into Laurent series.
+The right embedding replaces the inclusion of Laurent polynomials into the Dolbeault complex on $\CC^\times$.
+\item There is a higher residue map $\text{Res} \colon \sfA_d^{\bu} \to \CC[-d+1]$ which is compatible with integration over the $2d-1$ sphere
+\beqn
+\label{eq:res}
 \Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d z_1 \wedge \cdots \wedge \d z_d.
-\]
-
-The ingredients are almost in place to mimic the construction of the Weyl algebra for the formal loop space, of the affine Lie algebras, and of free field realization, but now with $\mathring{\CC}^d$ in place of $\mathring{\CC}^1 = \CC^\times$.
+\eeqn
+\end{itemize}
+
+%In fact, they provide a model $A^{p,*}_d$ for the algebraic $p$-forms as well.
+%We will gloss their definition, referring the interested reader to their lucid paper for details.
+
+%There is a natural analog of the residue map as well.
+%Just as $\CC^\times$ deformation-retracts onto the unit circle,
+%the punctured affine space $\mathring{\CC}^d$ retracts onto the unit sphere $S^{2d-1}$.
+%The Bochner-Martinelli kernel 
+%\[
+%\omega_{BM} = \frac{(d-1)!}{(2 \pi i)^d} \frac{1}{(z\zbar)^d} \sum_{i=1}^d (-1)^{i-1} \zbar_i\, \d \zbar_1 \wedge \cdots \wedge \Hat{\d \zbar_i} \wedge \cdots \wedge \d \zbar_d
+%\]
+%determines a cohomology class of degree $d-1$, and we identify it with $1/(z_1 \cdots z_d)$ in our basis above,
+%so that $\omega_{BM}$ generates its cohomology group under multiplication by polynomials in the $z_j^{-1}$.
+%When $d = 1$, note that $\omega_{BM} = (1/2\pi i)\d z/z$, the kernel in the Cauchy residue formula.
+%It is also quick to check that
+%\[
+%\omega_{BM} \wedge \d z_1 \wedge \cdots \wedge \d z_d
+%\]
+%pulls back to a volume form on the unit sphere $S^{2d-1}$.
+%Hence, we define a residue map
+%\[
+%\Res \colon \RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg})  \to \CC[1-d]
+%\]
+%by
+%\[
+%\Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d z_1 \wedge \cdots \wedge \d z_d.
+%\]
+
+The ingredients are in place to mimic the construction of the Weyl algebra for the formal loop space, of the affine Lie algebras, and of free field realization, but now with $\mathring{\CC}^d$ in place of $\mathring{\CC}^1 = \CC^\times$.
 We must be careful about parity, however. 
 In dimension $d = 1$, the Laurent polynomials valued in a symplectic vector space $V[z,z^{-1}]$ again has the structure of a symplectic vector space via the residue. 
-Because of the appearance of the cohomological shift in the higher dimensional residue it is no longer the case that $V \otimes \RR\Gamma(\mathring{\CC}^d, \cO_{alg})$ is symplectic if $V$ is.
-
-Let's consider the case $d = 2$ for concreteness. 
-The residue map $\Res$ above is then of cohomological degree $-1$. 
-Thus, to get a symplectic pairing on $V \otimes \RR\Gamma(\mathring{\CC}^d, \cO_{alg})$ via the residue we can ask that $V$ is equipped with a {\em $1$-shifted symplectic structure}. 
-A typical example of such a space is $V = \T^*[1] L = L \oplus L^*[1]$, where $L$ is any vector space.
-
-Reversing our treatment above, we first discuss the higher Kac-Moody algebras, 
-following Faonte-Hennion-Kapranov \cite{FHK},
-before discussing holomorphic field theory.
-
-It is important to have an explicit dg commutative algebra that models the derived global sections,
-and not just the cohomology groups.
-There is a beautiful, explicit dg model $A_d$ for the algebraic version derived global sections due to Faonte-Hennion-Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities.
-In fact, they provide a model $A^{p,*}_d$ for the algebraic $p$-forms as well.
-We will gloss their definition, referring the interested reader to their lucid paper for details.
-
-Let $a_d$ denote the algebra  
-\[
-\CC[z_1,\ldots,z_d, z_1^*,\ldots,z_d^*][(z z^*)^{-1}]
-\]
-defined by localizing the polynomial algebra with respect to $zz^* = \sum_i z_i z^*_i$.
-View this algebra $a_d$ as concentrated in bidegree $(0,0)$.
-Consider the bigraded-commutative algebra $R^{*,*}_d$ over $a_d$ that is freely generated in bidegree $(1,0)$ by elements
-\[
-\d z_1,\ldots , \d z_d,
-\] 
-and in bidegree $(0,1)$ by
-\[
-\d z_1^*,\ldots, \d z_d^*.
-\]
-Note the close resemblance with the Dolbeault complex $\Omega^{*,*}(\CC^d)$ by thinking of $z_j^*$ as $\zbar_j$.
-There is a subalgebra $A^{*,*}_d$ inside $\omega \in R^{p,m}_d$ and a natural pair of differentials $\partial$ and $\dbar$ that behave like the corresponding differentials in the Dolbeault complex.
-We denote the subcomplex with $p=0$~by 
-\[
-(A_d, \dbar) = (\bigoplus_{q = 0}^d A_d^{q}[-q], \dbar),
-\] 
-and it has the structure of a dg commutative algebra.
-For $p>0$, the complex $A^{p,*}_d = (\oplus_q A^{p,q}[-q], \dbar)$ is a dg module for $(A_d, \dbar)$.
-
-The following proposition summarizes key properties of the dg algebra $A_d$ and its dg modules $A_{d}^{p,*}$,
-by aggregating several results of~\cite{FHK}.
-
-\begin{prop}[\cite{FHK}, Section 1]
-\label{prop: Ad} $\;$
-\begin{enumerate}
-\item
-The dg commutative algebra $(A_d,\dbar)$ is a model for $\RR \Gamma(\mathring{\CC}^d, \sO_{\rm alg})$:
-\[
-A_d \simeq \RR\Gamma(\mathring{\CC}^{d}, \sO^{alg}) .
-\]
-Similarly, $(A_d^{p,*},\dbar) \simeq \RR \Gamma(\mathring{\CC}^{d}, \Omega^{p}_{\rm alg})$.
-\item There is a dense map of commutative bigraded algebras
-\[
-\jou : A^{*,*}_d \to \Omega^{*,*}(\CC^d \setminus \{0\}),
-\]
-and the map intertwines with the $\dbar$ and $\partial$ differentials on both sides.
-\item There is a unique $\GL_d$-equivariant residue map
-\[
-{\rm Res}_{z=0} : A_d^{d,d-1} \to \CC
-\]
-such that for any $\omega \in A^{d,d-1}_d$,
-\[
-{\rm Res}_{z=0} (\omega) = \oint_{S^{2d-1}} \jou(\omega)
-\]
-where $S^{2d-1}$ is any sphere centered at the origin in $\CC^d$. 
-\item There is a representative $\omega_{BM}^{\rm alg}$ of the Bochner-Martinelli kernel such that
-\[
-\Res_{z=0} \left(f(z) \omega_{BM}^{alg}(z,z^*) \d z_1 \cdots \d z_d\right) = f(0)
-\]
-for any $f (z) \in \CC[z_1,\ldots,z_d]$. 
-\end{enumerate}
-\end{prop}
-
-We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\mathring{\CC}^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disc) into $\fg$,
-just as $\fg[z,z^{-1}]$ provides a kind of loop algebra.
+Because of the appearance of the cohomological shift in the higher dimensional residue it is no longer the case that 
+\beqn
+V \otimes \RR\Gamma(\mathring{\DD}^d, \cO) \simeq V \otimes \sfA_d
+\eeqn
+is symplectic if $V$ is.
+
+The residue map $\Res$ in equation \eqref{eq:res} is of cohomological degree $1-d$. 
+Thus, to get a symplectic pairing on $V \otimes \sfA_d$ via the residue we can ask that $V$ is equipped with a {\em $(d-1)$-shifted symplectic structure}. 
+A typical example of such a space is $V = \T^*[d-1] L = L \oplus L^*[d-1]$, where $L$ is any vector space.
+
+Let $\omega_V$ be a $(d-1)$-shifted symplectic pairing on the graded vector space $V$. 
+Then $\omega_V$ extends to a map $\til \omega_V \colon (V \otimes \sfA_2)^{\otimes 2} \to \sfA_d$ where we use the algebra structure on $\sfA_d$. 
+We then obtain a ($0$-shifted) symplectic pairing on $V \otimes \sfA_d$ by the formula
+\beqn
+\label{eqn:omega}
+\omega(a,b) = \Res ( \til \omega_V (a,b) ) .
+\eeqn
+As in the construction of the ordinary Weyl algebra, we can think about $\omega$ as defining two-cocycle on the (abelian) dg Lie algebra $V \otimes \sfA_d$.
+In particular, $\omega$ determines a central extension of dg Lie algebras
+\beqn
+\CC \to \lie{h}_d[V] \to V \otimes \sfA_d .
+\eeqn
+From here, we can define the higher-dimensional analog of the Weyl algebra.
 
 \begin{dfn}
-For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$A_d \otimes \fg$.
+Let $V$ be a $(d-1)$-symplectic graded vector space. 
+Then, the $d$-dimensional Weyl algebra $W_d[V]$ is the enveloping algebra of the dg Lie algebra $\lie{h}_d [V]$ where we set the central term equal to the unit.
+\end{dfn}
+
+There is a close relationship of the higher dimensional Weyl algebra to the higher dimensional $\beta\gamma$ system on $\CC^d - 0$ just as the loopy Weyl algebra is related to the $\beta\gamma$ system on $\CC^\times$.
+
+The trick of turning providing a higher dimensional version of the Weyl algebra can be easily modified to obtain higher dimensional version of current, or loop, algebras. 
+This is one of the starting points of \cite{FHK} in their construction of higher dimensional Kac--Moody algebras.
+
+\begin{dfn}
+For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$\fg \otimes \sfA_d$.
 Following \cite{FHK} we denote it by~$\fg^\bullet_d$.
@@
 An $L_\infty$ algebra is a generalization of a Lie algebra;
-it is graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k: L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi condition for a standard Lie algebra.
+it is graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k \colon L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi condition for a standard Lie algebra.
 For an overview (and an actual definition!) we recommend \owen{add citations}.
 
-In our setting of $\fg^\bullet_d$, Faonte-Hennion-Kapranov introduced central extensions that only affect the $d$-bracket.
-For any $\fg$-invariant degree $d+1$ polynomial  $\theta \in \Sym^{d+1}(\fg^*)^\fg$,  the FHK  cocycle is
+In our setting of $\fg^\bullet_d$, Faonte-Hennion-Kapranov introduced central extensions of the sphere algebra that only affect the $d$-bracket.
+For any $\fg$-invariant degree $d+1$ polynomial $\theta \in \Sym^{d+1}(\fg^*)^\fg$, the cocycle which defines the $L_\infty$ central extension is
 \[
@@
 \theta_{\rm FHK} : & (A_d \tensor \fg)^{\tensor (d+1)} & \to & \CC\\ 
-& a_0 \otimes \cdots \otimes a_d & \mapsto & \Res_{z=0} \theta(a_0,\partial a_1,\ldots,\partial a_d)
+& a_0 \otimes \cdots \otimes a_d & \mapsto & \Res \left(\theta(a_0,\partial a_1,\ldots,\partial a_d)\right)
 \end{array}.
 \]
-This cocycle has cohomological degree $2$ and so determines an unshifted central extension as $L_\infty$ algebras
+This cocycle has total cohomological degree $+2$ as an element in the Lie algebra cohomology of $\fg^\bu_{d}$ and so determines a central extension of $L_\infty$ algebras
 \[
@@
 
-In addition to the higher Kac-Moody algebras, there are also natural higher analogs of the Weyl algebra of the loop space.
-These appear as the observables for a holomorphic field theory known as a $\beta\gamma$ system.
-
-Let $V$ be a symplectic complex vector space and consider the formal sphere algebra $A^{\wedge}_d \otimes V$,
-where $A^{\wedge}_d$ denotes the completion of $A_d$ (i.e., where polynomials in $z_j$ and $z_j^*$ are replaced by formal power series).
-\owen{Should we introduce a pithy notation?}
-Then there is a dg commutative algebra of functions on this space,
-which we denote $\cO(A^{\wedge}_d \otimes  V)$,
-and it has a kind of Poisson bracket, arising from the residue pairing on $A^{\wedge}_d$ and the symplectic form on $V$,
-just as $\cO(V((z)))$ has a Poisson bracket.
-It will not surprise the reader to learn that there is a natural deformation quantization $W_d[V]$ into a dg Weyl algebra.
-A physicist would interpret this algebra as the canonical and radial quantization of the theory on~$\CC^d - \{0\}$.
-
+With the higher dimensional Weyl and Kac--Moody algebras in place, a natural question to ask is whether there are higher dimensional versions of the free field realization as in \eqref{eqn:freefield1}.
 If $V$ is a representation of a Lie algebra $\fg$,
@@
 \[
-\fg^\bullet_d \to \cO(A^{\wedge}_d \otimes V),
-\]
-just as $\fg[z,z^{-1}]$ acts on $\cO(V((z)))$. 
+\fg^\bullet_d \to \cO(V \otimes \sfA^{\bu}_d),
+\]
+just as $\fg((z))$ acts on $\cO(V((z)))$. 
 One can ask if this action lifts to a quantum symmetry.
-The obstruction is, remarkably, an FHK cocycle:
-\[
-\alpha_{V,d}(x_1 \otimes f_1, \ldots, x_{d+1} \otimes f_{d+1}) = \Tr_V( x_1 \cdots x_{d+1}) \Res(f_1 \partial f_2 \cdots \partial f_{d+1}).
-\]
-\owen{Fix conventions}
+The obstruction, see \cite{GWkm}, is one of the cocycles we discussed above:
+\[
+x_0 \otimes f_0, \ldots, x_{d} \otimes f_{d} \mapsto \Tr_V( x_0 \cdots x_{d}) \Res(f_0 \partial f_1 \cdots \partial f_{d}).
+\]
+That is, the invariant degree $(d+1)$ polynomial on $\fg$ which determines the $L_\infty$ extension of the sphere algebra $\fg_d^\bu$ is given by ${\rm Tr}_V (x_0 \cdots x_{d})$.
 In this sense, the higher Kac-Moody algebras admit a higher free field realization,

### 2022-09-01 draft.tex
change the notation for twists

@@
 \item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
-\item $\sigma$-models where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
+\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
 \item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
@@
 \eeqn
-by the formula $[Q, Q'] = \Gamma(Q, Q')$.
-
-By a {\em supercharge}, one means an odd supertranslation $Q \in \ft$, and
-a {\em twist} is a (nonzero) supercharge $Q$ such that $[Q,Q] = Q^2 = 0$. 
+by the formula $[\cQ, \cQ'] = \Gamma(\cQ, \cQ')$.
+
+By a {\em supercharge}, one means an odd supertranslation $\cQ \in \ft$, and
+a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
 The classification of all twists is a completely algebraic question,
-and we refer to~\autocite{ESsusy} for a complete classification of all twists in dimensions from $1$ to~$10$.
+and we refer to~\autocite{ESsusy} for a complete classification of all twists \owen{of SYM?} in dimensions from $1$ to~$10$.
 
 If a Lagrangian field theory $\cT$ has $\ft$ as a symmetry, 
-then a choice of twist $Q$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^Q$.
-If $S$ denotes the action functional of $\cT$, then the action functional $S^Q$ of $\cT^Q$ has the form
-\[
-S^Q(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(Q \cdot \varphi \right) + \cdots 
-\]
-where the deformation arises from how $Q$ acts on the theory 
-(the $\cdots$ leaves room for terms non-linear in $Q$).
+then a choice of twist $\cQ$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^\cQ$.
+If $S$ denotes the action functional of $\cT$, then the action functional $S^\cQ$ of $\cT^\cQ$ has the form
+\[
+S^\cQ(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(\cQ \cdot \varphi \right) + \cdots 
+\]
+where the deformation arises from how $\cQ$ acts on the theory 
+(the $\cdots$ leaves room for terms non-linear in $\cQ$).
 For extensive details on how the twisted theory is defined we refer to~\autocite{CostelloHolomorphic, ESW}.
@@
 In even dimensions $d = 2n$, basic properties of the supersymmetry algebra guarantee that there exists a twist rendering the theory holomorphic.\footnote{This fails in one example where the dimension and amount of supersymmetry is too small, namely for $\cN=(1,0)$ supersymmetry in two dimensions.}
-Indeed, so long as a twisted supercharge is nonzero $Q \ne 0$ one see that the image of the map $[Q,-] = \Gamma(Q,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
-A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly $n$ and we declare the the image of $Q$ is spanned by the anti-holomorphic vector fields $\{\del / \del \zbar_i\}$.
+Indeed, so long as a twisted supercharge is nonzero $\cQ \ne 0$ one see that the image of the map $[\cQ,-] = \Gamma(\cQ,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
+A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly $n$ and we declare the the image of $\cQ$ is spanned by the anti-holomorphic vector fields $\{\del / \del \zbar_i\}$.
 This fits with the local characterization mentioned at the beginning of the subsection since in this case there exists homotopies $\{\eta_i\}$ with the property that 
 \beqn
-[Q,\eta_i] = \frac{\del}{\del \zbar_i} .
+[\cQ,\eta_i] = \frac{\del}{\del \zbar_i} .
 \eeqn
@@
 consider pure four-dimensional supersymmetric Yang--Mills theory with $\cN=1$ supersymmetry.
-The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional and there exists a unique holomorphic twist $Q$ (up to equivalence).
+The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional and there exists a unique holomorphic twist $\cQ$ (up to equivalence).
 In this dimension, with this amount of supersymmetry, there does not exist a topological twist.
-The holomorphic twist of the theory with respect to $Q$ is equivalent to holomorphic BF theory on $\CC^2$.
+The holomorphic twist of the theory with respect to $\cQ$ is equivalent to holomorphic BF theory on $\CC^2$.
 

### 2022-09-18 draft.tex
revised the dfn of holomorphic qcd

@@
 
-The field content of 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory is:
+A 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory depends on a choice of compact Lie group $G$, with Lie algebra $\fg$, 
+and it lives on  the spacetime $M=\RR^4$.
+The field content of the theory~is
 \begin{itemize}
-\item a `vector multiplet' which consists of a gauge field $A$ together with some fermions $\lambda$ all taking values in a Lie algebra $\fg$;
-\item a `matter multiplet' (usually called the chiral multiplet) which consists of a scalar $\phi$ together with some fermions $\psi$ all transforming in some representation $V$ of $\fg$. 
-Additionally, there is a `superpotential' $W$ which is a $\fg$-invariant polynomial on~$V$. 
+\item a {\it vector multiplet} that consists of a gauge field $A \in \Omega^1(M) \otimes \fg $ together with some fermions $\lambda \in C^\infty(M) \otimes \fg$, and
+\item a {\it matter multiplet} (often called the chiral multiplet), depending on a choice of a representation $V$ of $\fg$, that consists of a scalar $\phi \in C^\infty(M) \otimes V$ together with some fermions $\psi \in C^\infty(M) \otimes V$.
+Additionally, there is a {\it superpotential} $W \in \cO(V)^\fg$, a $G$-invariant polynomial on~$V$. 
 \end{itemize}
-
-From hereon we fix a nonzero, square zero supercharge of the 4-dimensional $\cN=1$ supersymmetry algebra for which we wish to twist by. 
-The twist of 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory has been characterized in \cite{CosYangian, ESW, SWchar}. 
-It is a holomorphic field theory on $\CC^2$ consisting of a `vector' part and a 'matter' part.
-As a moduli space, it can be described in the following way (we will give a description in terms of fields and action functionals afterwards).
-
-Let's consider the matter part. 
-Recall that the derived critical locus ${\rm Crit}(W)$ of any function on $V$ has a $(-1)$-shifted symplectic structure. 
-As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
-From now on, we forget the $\ZZ$-grading and view this locus as equipped with an odd symplectic structure. 
-Before coupling to the gauge theory, the matter part of the holomorphic twist is the derived mapping space ${\rm Map}(\CC^2_{\dbar}, {\rm Crit}(W))$ which is equipped with an odd symplectic structure by the AKSZ construction.
-
-Since $W$ is $\fg$-invariant, the critical locus has a residual Hamiltonian $\fg$ action. 
-There is a version of Hamiltonian reduction for odd symplectic manifolds, see \cite{Pavel, Kevin, who else}. 
-Denote this reduction by ${\rm Crit}(W) \sslash \fg$. 
-As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$.
-
-In total, the holomorphic twist is equivalent to the following derived mapping space
-\[
-{\rm Map}(\CC^2_{\dbar} \; , \; {\rm Crit}(W) \sslash \fg) 
-\]
-which is equipped with an odd symplectic structure.
-
-In essence, all of the holomorphic theories we consider below will be special cases of this gauged linear mapping space on $\CC^2$. 
-We slightly refine notation and associate a holomorphic theory $\cT(G, V, Z, W)$ on $\CC^2$ associated to the following data:
+We always work with super vector spaces, so a fermion means an element of an odd vector space while a boson means an even element.
+Thus, we view a fermion $\lambda$ as living in $\Pi (C^\infty(M) \otimes \fg)$,
+where $\Pi$ denotes odd parity.
+
+From hereon we fix a nonzero, square zero supercharge $\cQ$ of the 4-dimensional $\cN=1$ supersymmetry algebra.
+This element determines a complex structure on $\RR^4$.
+We also use it to twist the supersymmetric theory to produce a holomorphic field theory on $\CC^2$.
+This twist also has a ``vector'' part and a ``matter'' part.
+This twist of 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory has been analyzed and described in \cite{CosYangian, ESW, SWchar}, within that framework for (primarily perturbative) field theory.
+
+This twist has a moduli-theoretic description that we now sketch;
+we call a point in such a moduli space a {\it solution to the equations of motion}. 
+(We give later a description in terms of fields and action functionals.)
+Let $G_\CC$ denote the complex Lie group associated to $G$,
+and let $\fg_\CC$ denotes its complex Lie algebra.
+
+The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
+A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of a shift of the adjoint bundle ${\mathrm ad}(\cP) \to X$.
+\owen{rephrase the second part?}
+The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
+
+\def\Sslash{\!\sslash\!}
+
+A twisted matter multiplet also defines a field theory on any complex surface $X$. 
+\owen{Is it a cotangent theory? It looks like a twisted cotangent theory.}
+The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
+(It is the Koszul complex associated to the Jacobi ring of $W$.)
+This description makes manifest an odd symplectic structure on ${\rm Crit}^d(W)$,
+as polyvector fields are an odd Poisson algebra via the Schouten bracket.
+%As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
+By itself (i.e., before coupling to a gauge theory) the twisted matter multiplet corresponds to the mapping space ${\rm Map}(X, {\rm Crit}^d(W))$.
+
+Since $W$ is $G_\CC$-invariant, the critical locus has a residual Hamiltonian $G_\CC$-action. 
+There is a version of Hamiltonian reduction for odd symplectic manifolds \cite{Pavel, Kevin, who else},
+which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
+%As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
+The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
+\[
+{\rm Map}(X , {\rm Crit}^d(W) \Sslash G_\CC), 
+\]
+which comes equipped with an odd symplectic structure.
+
+We wish to study a holomorphic analog of supersymmetric chromodynamics.
+We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
+The matter fields will consist of two types: quarks and antiquarks.
+We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
+
+%All of the holomorphic theories we consider below will be special cases of this gauged linear mapping space with $X = \CC^2$. 
+%We slightly refine notation and associate a holomorphic theory $\cT(G, V, Z, W)$ on $\CC^2$ associated to the following data:
+%\begin{itemize}
+%\item a Lie group $G$, this is the gauge group. 
+%Its complexified Lie algebra is $\fg = {\rm Lie}_\CC (G)$;
+%\item a complex $G$-representation $V$, this is where the `chiral quark matter' lives;
+%\item a complex vector space $Z$ where the `mesons' live.
+%This is not acted upon by the group $G$. 
+%\item a polynomial $W \in {\rm Sym}(V \oplus \Bar{V} \oplus Z)$.
+%\end{itemize}
+
+\begin{dfn}
+A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
 \begin{itemize}
-\item a Lie group $G$, this is the gauge group. 
-Its complexified Lie algebra is $\fg = {\rm Lie}_\CC (G)$;
-\item a complex $G$-representation $V$, this is where the `chiral quark matter' lives;
-\item a complex vector space $Z$ where the `mesons' live.
-This is not acted upon by the group $G$. 
-\item a polynomial $W \in {\rm Sym}(V \oplus \Bar{V} \oplus Z)$.
+\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, which we denote by
+\[
+A \in \Omega^{0,\bu}(\CC^2 , \sl(N))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\CC^2, \sl(N)^*);
+\]
+\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in $V_Q = \sl(N)^{\oplus F}$, which we denote by
+\[
+Q \in \Omega^{0,\bu}(\CC^2 , V_Q) \quad\text{and}\quad R \in \Omega^{2,\bu}(\CC^2 , V_Q^*)[1];
+\]
+\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation $V^*_Q = (\sl(N)^*)^{\oplus F}$, which we denote by
+\[
+\Tilde{Q} \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad \Tilde{R} \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
+\]
 \end{itemize}
+\owen{I'm not sure I like this use of tilde for antiquarks}
+
+The action functional is
+\[
+S_{QCD} = \int B F^{0,2}_A + \int R \,\dbar_A Q + \int \Tilde{R} \,\dbar_A \Tilde{Q},
+\]
+where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator. 
+We will denote this theory by $\cT(N,F)$.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.}
+\end{dfn}
+
+To formulate Seiberg duality, we will need to allow auxiliary matter fields that we call ``mesons.''
 
 \begin{dfn}
-{\em Holomorphic QCD} associated to the data $(G,V,Z,W)$ as above is the holomorphic field theory on $\CC^2$ with fields:
-\begin{itemize}
-\item The gauge fields are those of holomorphic BF theory valued in $\fg$, which we denote by
-\[
-A \in \Omega^{0,\bu}(\CC^2 , \fg)[1] , \quad B \in \Omega^{2,\bu}(\CC^2, \fg^*) .
-\]
-\item The `matter fields' consist of a holomorphic $\beta\gamma$ system valued in $V$, which we denote by
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , V) , \quad P \in \Omega^{2,\bu}(\CC^2 , V^*)[1] ,
-\]
-a holomorphic $\beta\gamma$ system valued in the complex conjugate representation $\Bar{V}$, which we denote by
-\[
-\Tilde{Q} \in \Omega^{0,\bu}(\CC^2 , \Bar{V}) , \quad \Tilde{P} \in \Omega^{2,\bu}(\CC^2 , \Bar{V}^*) [1],
-\]
-and a $\beta\gamma$ system valued in the vector space $Z$, which we denote by
-\[
-M \in \Omega^{0,\bu}(\CC^2 , Z) , \quad L \in \Omega^{2,\bu}(\CC^2 , Z^*) [1] .
-\]
-\end{itemize}
-
+A holomorphic QCD theory {\em with mesons}, denoted $\cT(N,F, V_M, Q)$, is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
+\[
+M \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad N \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
+\]
 The action functional is
 \[
-\int B F^{0,2}_A + \int P \dbar_A Q + \int \Tilde{P} \dbar_A \Tilde{Q} + \int \d^2 z \; W(Q, \Tilde{Q}, M) + \int L \dbar M
-\]
-where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator. 
-We will refer to this theory by $\cT(G,V,Z,W)$.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators.}
+S_{QCDwM} = S_{QCD} + \int N \,\dbar M + \int \d^2 z \; W(Q, \Tilde{Q}, M) .
+\] 
 \end{dfn}
 
+Note that the fields $M$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
+The only coupling that the meson $M$ has to the other fields is through the superpotential~$W$.
+
 \begin{rmk}
-This theory is only $\ZZ/2$-graded, so all fields are considered only as `even' or 'odd'--for instance the component of the gauge field $A^{0,1}$ is even while the component of the matter field $Q^{0,1}$ is odd.
-Only in the case that $W = 0$ can one lift the theory to a $\ZZ$-grading.
-\end{rmk}
-
-\begin{rmk}
-Note that the fields $M$ are `uncharged' under the gauge group.
-The only coupling $M$ has to the other fields is through the superpotential $W$. 
+This theory is only $\ZZ/2$-graded, so all fields are considered merely as even or odd.
+For instance the component of the gauge field $A^{0,1}$ is even while the component of the matter field $Q^{0,1}$ is odd. 
+Only when $W = 0$ can one lift the theory to a $\ZZ$-grading.
 \end{rmk}

### 2022-09-18 draft.tex
rephrased electric and magnetic theories

@@
 We wish to study a holomorphic analog of supersymmetric chromodynamics.
+We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
 We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
 The matter fields will consist of two types: quarks and antiquarks.
-We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
+Let $V_N$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
+so $V_N = \CC^N$ with its natural left action.
 
@@
 \begin{itemize}
-\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, which we denote by
+\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, whose fields are
 \[
@@
 \]
-\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in $V_Q = \sl(N)^{\oplus F}$, which we denote by
+\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in 
+\[
+V_Q = \Hom(\CC^F, V_N) \cong (V_N)^{\oplus F},
+\] 
+whose fields are
 \[
@@
 \]
-\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation $V^*_Q = (\sl(N)^*)^{\oplus F}$, which we denote by
-\[
-\Tilde{Q} \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad \Tilde{R} \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
+\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation 
+\[
+V^*_Q = \Hom(V_N, \CC^F) \cong (V_N^*)^{\oplus F}, 
+\]
+whose fields are
+\[
+q \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad r \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
 \]
 \end{itemize}
-\owen{I'm not sure I like this use of tilde for antiquarks}
 
@@
 \[
-S_{QCD} = \int B F^{0,2}_A + \int R \,\dbar_A Q + \int \Tilde{R} \,\dbar_A \Tilde{Q},
+S_{QCD} = \int B F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
 \]
@@
 \begin{dfn}
-A holomorphic QCD theory {\em with mesons}, denoted $\cT(N,F, V_M, Q)$, is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
+A holomorphic QCD theory {\em with mesons}, denoted $\cT(N,F, V_M, W)$, is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
 \[
@@
 The notion of duality can refer to several kinds of relationships,
-but loosely speaking it means that some aspects of the two theories are equivalent under some dictionary or correspondence.
-We will postpone saying something precise till we have some terminology in place.
-
-We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
-Following physics terminology, we will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
-Also, let $N_c, N_f$ denote integers where $N_f \geq N_c \geq 2$.
+but loosely speaking it means that some aspects of the two theories are equivalent under correspondence.
+We will postpone saying anything precise till we have some terminology in place.
+
+%We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
+%Following physics terminology, we will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
+%Also, let $N_c, N_f$ denote integers where $N_f \geq N_c \geq 2$.
 %Also, let $N_{\rm mes} \geq 0$ be some integer.  
@@
 
-First, we have the `electric' theory which is the following holomorphic QCD
-\[
-\cT_{\sfE} (N_c , N_f) \define \cT\big(\SU(N_c) \, ,\, (\CC^{N_c})^{\oplus N_f} \, ,\, Z = 0 \, , \, W = 0\big) .
-\]
-
-%\begin{dfn}
-%Suppose $\cT_A (N_c, N_f, N_{\rm mes}, W)$ is a type A holomorphic QCD. 
-%Define the {\em dual} type A holomorphic QCD to be
+Fix a positive integer $F$, for flavor.
+There will be two theories. 
+We call one side {\em electric} and the other {\em magnetic}.
+The electric theory is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
+{\it We restrict to $F \geq N \geq 2$.}
+The magnetic theory is the holomorphic QCD with $\Tilde{N} = F-N$ colors and $F$ flavors, but with mesons $\Tilde{M}$ where $$\Tilde{V}_M = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\Tilde{W} =  \Tr(\Tilde{q} \Tilde{M}  \Tilde{Q}).$$
+Again, we require $\Tilde{N} \geq 2$.
+\owen{Please double-check that formula.}
+%In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
+%Our notation is $q,\Tilde{q}$ for elements of the vector spaces $V, \Bar{V}$ and $m\in Z$.
+%The magnetic theory is
 %\[
-%\Hat{\cT}_{A} (N_c, N_f, N_{\rm mes}, W) \define \cT_{A} (N_f - N_c, N_f, N_{\rm mes} + N_{f}^2 , W + 
+%\cT_{\sfM} (N_c, N_f) \define \cT\big(\SU(N_f - N_c) \, , \, (\CC^{N_f - N_c})^{\oplus N_f} \, , \, \CC^{\oplus N^2_f} \, , \, W = m q \Tilde{q} \big)
 %\]
-%\end{dfn}
-
-Second, we have the `magnetic' theory. 
-In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
-Our notation is $q,\Tilde{q}$ for elements of the vector spaces $V, \Bar{V}$ and $m\in Z$.
-The magnetic theory is
-\[
-\cT_{\sfM} (N_c, N_f) \define \cT\big(\SU(N_f - N_c) \, , \, (\CC^{N_f - N_c})^{\oplus N_f} \, , \, \CC^{\oplus N^2_f} \, , \, W = m q \Tilde{q} \big)
-\]
-In the definition of $W = m q \Tilde{q}$ we are using the natural contractions which we can describe explicitly as follows.
-Choose a basis $\{q_a^i\}$ for $V = (\CC^{N_f - N_c})^{\oplus N_f}$, $a = 1,\ldots, N_f - N_c$, $i=1,\ldots N_f$ and a dual basis $\{\Tilde{q}_i^a\}$ for $\Bar{V}$.
-Also, let $\{m_i^j\}$ be a basis for $\CC^{\oplus N_f^2}$. 
-Then the cubic polynomial $W$ is
-\[
-W = \sum_{i,j,a} m^i_j q_i^a \Tilde{q}^i_a .
-\]
+%In the definition of $W = m q \Tilde{q}$ we are using the natural contractions which we can describe explicitly as follows.
+%Choose a basis $\{q_a^i\}$ for $V = (\CC^{N_f - N_c})^{\oplus N_f}$, $a = 1,\ldots, N_f - N_c$, $i=1,\ldots N_f$ and a dual basis $\{\Tilde{q}_i^a\}$ for $\Bar{V}$.
+%Also, let $\{m_i^j\}$ be a basis for $\CC^{\oplus N_f^2}$. 
+%Then the cubic polynomial $W$ is
+%\[
+%W = \sum_{i,j,a} m^i_j q_i^a \Tilde{q}^i_a .
+%\]
 

### 2022-09-19 draft.tex
slowly working through duality section

@@
 A well-known high point is the work of Seiberg and Witten on 4-dimensional $\cN =2$ supersymmetric Yang--Mills theory,
-where they explained how confinement could be realized by a version of the Mandelstam-'t Hooft mechanism (i.e., a kind of electromagnetic duality identifies confinement with a Meissner-type effect).
+where they explained how confinement could be realized by a version of the Mandelstam-'t Hooft mechanism (i.e., a kind of electromagnetic duality identifies confinement with a Meissner effect).
 Their work offered powerful new tools that opened up much subsequent progress,
@@
 The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
-There too Seiberg offered inspiring and powerful insights,
+There too Seiberg offered inspiring and powerful insights about SQCD ($\cN=1$ supersymmetric QCD),
 and one of his leading contributions is referred to as {\em Seiberg duality}.
@@
 which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
+\owen{I'm not sure we even need this.}
 %As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
@@
 which comes equipped with an odd symplectic structure. 
+\owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}
 
@@
 The matter fields will consist of two types: quarks and antiquarks.
-Let $V_N$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
-so $V_N = \CC^N$ with its natural left action.
+Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
+so $\underline{N} = \CC^N$ with its natural left action.
+\owen{That's kind of crappy notation. Let's discuss.}
 
@@
 \[
-V_Q = \Hom(\CC^F, V_N) \cong (V_N)^{\oplus F},
+V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F},
 \] 
@@
 \[
-V^*_Q = \Hom(V_N, \CC^F) \cong (V_N^*)^{\oplus F}, 
+V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F}, 
 \]
@@
 \[
-S_{QCD} = \int B F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
+S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
 \]
@@
 
-Fix a positive integer $F$, for flavor.
 There will be two theories. 
 We call one side {\em electric} and the other {\em magnetic}.
-The electric theory is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
-{\it We restrict to $F \geq N \geq 2$.}
-The magnetic theory is the holomorphic QCD with $\Tilde{N} = F-N$ colors and $F$ flavors, but with mesons $\Tilde{M}$ where $$\Tilde{V}_M = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\Tilde{W} =  \Tr(\Tilde{q} \Tilde{M}  \Tilde{Q}).$$
-Again, we require $\Tilde{N} \geq 2$.
+
+\begin{dfn}
+Fix a positive integer $F$, for flavor, and fix integers $N$ and $\check{N}$ such that $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
+
+The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
+We denote it by~$\cT_{\sfE}(F, N)$.
+
+The {\em magnetic theory} is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\check{W} =  \Tr(\check{q} \check{M}  \check{Q}),$$
+where we compose the linear maps before tracing over~$V_{\check{N}}$.
+We denote this theory by~$\cT_{\sfM}(F, \check{N})$.
+\end{dfn}
+
 \owen{Please double-check that formula.}
@@
 
-The usual Seiberg duality states how certain ``electric'' and ``magnetic'' versions of SQCD ($\cN=1$ supersymmetric QCD) should be equivalent.
-Our electric and magnetic holomorphic QCDs are precisely the holomorphic twists of those that appear in Seiberg duality.
-In \cite{Eager} Richard Eager suggested that Seiberg duality should survive after taking the holomorphic twist.
-
-\begin{conj}
-There is an equivalence of $2$-dimensional holomorphic factorization algebras
-\[
-\Obs_{\sfE}(N_f, N_c) \simeq \Obs_{\sfM} (N_f, N_c)  .
-\]
+The usual Seiberg duality states how certain ``electric'' and ``magnetic'' versions of SQCD should be equivalent.
+The electric and magnetic holomorphic QCDs are precisely the holomorphic twists of those that appear in Seiberg duality,
+and so Richard Eager suggested that Seiberg duality should survive after taking the holomorphic twist.
+
+\begin{conj}[\cite{Eager}]
+Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
+Construct a quantization of the theories $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$.
+There is an equivalence of 2-dimensional holomorphic factorization algebras
+\[
+\Obs_{\sfE} \simeq \Obs_{\sfM}  
+\]
+where these are the observables of the electric and magnetic theories, respectively.
 \end{conj}
@@
 \begin{quote}
-how do physical results about supersymmetric gauge theories behave under twisting?
+how do physical results about supersymmetric gauge theories behave under twisting to holomorphic or topological theories?
 \end{quote}
-We have found, so far, that they often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
+We have found, so far, that these results often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
 In \cite{EGW} we and Chris Elliott explored twists of $\cN=4$ supersymmetric Yang--Mills theory,
@@
 
+\begin{rmk}
+Our discussion here is ahistorical.
+Witten initiated this vein of research for topological twists \cite{},
+and Costello pushed it for holomorphic twists, particularly in the setting of holography \cite{}.
+Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
 \owen{Add a remark (?) about Kevin and Si's work on twisted holography and other related directions.}
+\end{rmk}
 
@@
 The first piece of evidence involves the classical field theories:
-\begin{quote}
-$\bullet$ Each theory has a moduli stack of vacua, and there is a natural isomorphism between \owen{the affinizations?} the spaces for theories dual according to the conjecture.
-\end{quote}
-This map of stacks determines a map of factorization algebras of classical observables,
+\begin{enumerate}
+\item[(1)] Each theory has a moduli space of vacua, and there is a natural isomorphism between the spaces for theories dual according to the conjecture.
+\end{enumerate}
+This map determines a map of factorization algebras of classical observables,
 and it should deform to the map between the factorization algebras for the quantum theories.
+(There are some interesting geometric subtleties --- about stacks versus their affinizations --- that we discuss below.)
+
 As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{BW work}.
@@
 \begin{enumerate}
-\item There are {\em flavor} symmetries that act on each theory, and these can be matched under the duality. Under quantization, these have isomorphic anomalies.
-\item There are {\em spacetime} symmetries that act on each theory, notably isometries, and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields.
+\item[(2)] There are {\em flavor} symmetries that act on each theory, and these can be matched under the duality. Under quantization, these have isomorphic anomalies.
+\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields.
 Under quantization, these have isomorphic anomalies.
@@
 This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
-We now turn to fleshing out the assertions above.
+We now turn to fleshing out these assertions.
 
@@
 \begin{thm}
-Both $\cT_{\sfE}(N_c, N_f)$ and $\cT_{\sfM}(N_c, N_f)$ exist at the quantum level for any choice of classical vacuum. 
+Both $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F, \check{N})$ exist at the quantum level for any choice of classical vacuum. 
 That is, the anomaly to a perturbative BV quantization vanishes.
@@
 it is natural to ask for field theories with an action by translations.
-That is, since the fields are sections of a fiber bundle over $RR^n$,
+That is, since the fields are sections of a fiber bundle over $\RR^n$,
 one can ask for an equivariant fiber bundle and ask for the equations of motion (or action functional) to be equivariant under translations.
@@
 where $V$ is a (graded) $G$-representation and $V/G$ denotes the quotient stack.
-The factor $V$ arises from solutions for the non-gauge field, which are sections of some associated vector bundle,
-while the quotient by $G$ arises from the gauge transformation.
-For another example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ has \owen{true?}
-\[
-\cM_{\rm vac} \cong \fg/G,
-\]
-the adjoint quotient stack of the group.
+The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
+the quotient by $G$ arises from the gauge transformation.
+For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has \owen{true?}
+\[
+\cM_{\rm vac} \cong \fg^*/G,
+\]
+the coadjoint quotient stack of the group.
+(We are working in a $\ZZ/2$-graded world here.)
 For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
@@
 \[
-V//G = \Spec(\cO(V)^G),
+V\Sslash G = \Spec(\cO(V)^G),
 \]
@@
 This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
-We will call it the moduli {\em space} of classical vacua and denote it by~$M_{rm vac}(\cT)$.
+We will call it the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
+(Note that the font of M changes between stack and space.)
 
@@
 \[
-V/G \to V//G
+V/G \to V\Sslash G
 \]
@@
 \[
-\gl_N//GL_N \cong \CC^N/S_N,
+\gl_N \Sslash GL_N \cong \CC^N/S_N,
 \]
@@
 \[
-M_{rm vac}(\cT) \cong \Gr(N_f, N_c)
+M_{\rm vac}(\cT) \cong \Gr(N_f, N_c)
 \]

### 2022-09-20 draft.tex
small changes in SD sec

@@
 It is analogous to claiming that two vertex algebras are equivalent,
-such as in the well-known boson-fermion correspondence.
+such as in the well-known boson-fermion correspondence or in the correspondence between the chiral rings of the A- and B-models of mirror symmetry.
 In this sense it is a target at which a mathematician can aim,
@@
 
-\owen{new version}
-
 It is common in physics to study field theories defined on the spacetime $\RR^n$.
@@
 Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
-A {\em classical vacuum} for the theory is a solution that this translation-invariant,
+A {\em classical vacuum} for the theory is a solution that is translation-invariant,
 i.e., a constant solution.
@@
 Instead, they have worked with a GIT quotient.
-For instance, in the setting of a gauge theory with stack $V/G$ of classical vacua, it means they work with
+For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with
 \[
@@
 This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
-We will call it the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
+In practice physicists work ordinary schemes (i.e., without any derived directions), although one can also study the derived affine scheme that is the best approximation to a derived stack.
+We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
 (Note that the font of M changes between stack and space.)
@@
 
-For the holomorphic QCD theory \owen{write data} the moduli stack of classical vacua is \owen{write it}
-The moduli space is a well-known variety
-\[
-M_{\rm vac}(\cT) \cong \Gr(N_f, N_c)
-\]
-by using classical invariant theory. \owen{show?}
-A similar computation on the putative dual shows the following.
+For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
+the moduli stack of classical vacua is 
+\[
+\cM_{\rm vac} \cong T^*[1] \left(V_Q \oplus V_Q^*)/SL(N)\right).
+\]
+By contrast the moduli space is a well-known variety, 
+\[
+M_{\rm vac}(\cT) \cong \Gr(F, N),
+\]
+the affine cone of a Grassmannian \owen{under Pl\"ucker embedding? need to check.} 
+This result follows from classical invariant theory.
+(The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q$, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
+Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)
+The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.
 
@@
 
+One sees the need for the superpotential in order to obtain this result;
+the mesons are added to remember nontrivial relations.
 This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
-
-\owen{Sketch proof}: This is the first and second fundamental theorem of classical invariant theory!
 
@@
 In the physics literature this isomorphism is given by explicitly matching gauge-invariant functions, which are often called mesons or baryons, as they can be identified with the data that identifies such particles.
-These meson and baryons are precisely the usual generators of the ring of invariant functions, so an isomorphism of generators determines the desired isomorphism of rings. 
+These meson and baryons are precisely the usual generators of the ring of invariant functions, 
+so an isomorphism of generators determines the desired isomorphism of rings. 
 One must check that the relations are satisfied;

### 2022-09-20 draft.tex
partway through explaining invariant theory

@@
 \[
-V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F},
+V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F} \cong \CC^{NF},
 \] 
@@
 \[
-V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F}, 
+V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F} \cong \CC^{NF}, 
 \]
@@
 \[
-q \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad r \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
+Q^\dag \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad R^\dag \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
 \]
 \end{itemize}
+(The superscript $\dag$ does not mean we apply an operation to $Q$ or $R$; 
+it is simply to remind us that these fields are the ``antiparticles''.)
 
@@
 We denote it by~$\cT_{\sfE}(F, N)$.
-
-The {\em magnetic theory} is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\check{W} =  \Tr(\check{q} \check{M}  \check{Q}),$$
+We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
+
+The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
+(and $\check{L}$ for the partner field to $\check{M}$).
+We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
+The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{M}  \check{Q}),$$
 where we compose the linear maps before tracing over~$V_{\check{N}}$.
-We denote this theory by~$\cT_{\sfM}(F, \check{N})$.
 \end{dfn}
@@
 
+This claim should seem rather surprising.
+In many ways these theories look, on their face, like very different theories:
+the gauge groups $SL(N)$ and $SL(\check{N})$ are (usually) different, and
+one side has mesons and the other does not.
+But this feature also makes the conjecture powerful.
+
 The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$-graded.
@@
 \]
-By contrast the moduli space is a well-known variety, 
-\[
-M_{\rm vac}(\cT) \cong \Gr(F, N),
+By contrast the moduli space is a variety already well-studied in classical algebraic geometry.
+The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q $, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
+
+\[
+M_{\rm vac}(\cT) \cong ,
 \]
@@
 This result follows from classical invariant theory.
-(The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q$, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
+(
 Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)

### 2022-09-21 draft.tex
finished full pass through moduli subsection

@@
 For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
-the moduli stack of classical vacua is 
-\[
-\cM_{\rm vac} \cong T^*[1] \left(V_Q \oplus V_Q^*)/SL(N)\right).
-\]
-By contrast the moduli space is a variety already well-studied in classical algebraic geometry.
-The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q $, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
-
-\[
-M_{\rm vac}(\cT) \cong ,
-\]
-the affine cone of a Grassmannian \owen{under Pl\"ucker embedding? need to check.} 
-This result follows from classical invariant theory.
-(
-Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)
+the derived stack of classical vacua is 
+\[
+\cM_{\rm vac}(F,N) \cong T^*[1] \left(V_Q \oplus V_Q^*/SL(N)\right).
+\]
+By contrast the moduli space $M_{\rm vac}$ is a variety already well-studied in classical algebraic geometry.
+Before we jump to the full space, let's examine a simpler case involving just the quarks.
+A vacuum for the quark field is an element of $V_Q = \Hom(\CC^F, \CC^N)$,
+and it is a classic result of invariant theory that
+\[
+\Hom(\CC^F, \CC^N)\Sslash SL(N) \cong \widehat{{\rm Gr}(F, N)} \subset \Lambda^N \CC^F
+\]
+where ${\rm Gr}(F, N)$ denotes the Grassmannian of $N$-planes in $\CC^F$ and the hat indicates we take the affine cone with respect to this standard Pl\"ucker embedding.
+For the full problem, we have both quarks and antiquarks, so
+\begin{align*}
+M_{\rm vac}(F,N) 
+&\cong V_Q \oplus V_Q^*\Sslash SL(N) \\
+&= \Hom(\CC^F, \CC^N) \oplus \Hom(\CC^N, \CC^F)\Sslash SL(N),
+\end{align*}
+whose ring of functions is also computed by the fundamental theorems of invariant theory.
+Those theorems tell us that the GIT quotient is a closed conical subvariety
+\[
+M_{\rm vac}(F,N)  \hookrightarrow \Lambda^N \CC^F \times \Lambda^N (\CC^F)^* \times \End(\CC^F)
+\]
+where a pair of matrices $(X,Y) \in \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)$ goes to $(\Lambda^N X, \Lambda^N Y, YX)$, with $\Lambda^N X$ denoting the wedge product of the rows of $X$ (and of columns for $Y$).
+The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem.
+In other words,
+\[
+M_{\rm vac}(F,N) \hookrightarrow \widehat{{\rm Gr}(F, N)} \times \widehat{{\rm Gr}(F, N)} \times {\rm R}(F,N)
+\]
+with ${\rm R}(F,N) \subset \End(\CC^F)$ the matrices with rank bounded above by~$N$.
 The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.
+
+Note that $\check{N} = F-N$, so $\widehat{{\rm Gr}(F, N)} \cong \widehat{{\rm Gr}(F, \check{N})}$,
+but ${\rm R}(F,N)$ is not isomorphic to ${\rm R}(F,\check{N})$ except when $N = \check{N}$.
+Hence one should not be optimistic that $M_{\rm vac}(F,N) \cong M_{\rm vac}(F,\check{N})$.
+To ``fix'' this issue, one might try to slightly modify the dual side, which Seiberg did by adding the meson fields.
+Hence the following holds.
 
@@
 
-One sees the need for the superpotential in order to obtain this result;
-the mesons are added to remember nontrivial relations.
 This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
+One disocvers the need for mesons and the superpotential in order to obtain this result.
 
 \begin{rmk}
-In the physics literature this isomorphism is given by explicitly matching gauge-invariant functions, which are often called mesons or baryons, as they can be identified with the data that identifies such particles.
+In the physics literature this isomorphism is given by explicitly matching gauge-invariant functions, 
+which are often called mesons or baryons, 
+as they can be identified with the data that identifies such particles.
 These meson and baryons are precisely the usual generators of the ring of invariant functions, 
@@
 One must check that the relations are satisfied;
-here it explains the superpotential on the magnetic side.
+this requirement explains the superpotential on the magnetic side.
 \end{rmk}
@@
 Consider, for instance, the origin in each vector space.
-On the electric side its stabilizer is $SL(N_c)$ and on the magnetic side it is $SL(N_f - N_c)$.
+On the electric side its stabilizer is $SL(N)$ and on the magnetic side it is $SL(\check{N})$.
 Thus each theory has a vacuum whose associated perturbative classical theory has no partner on the other side.

### 2022-09-22 draft.tex
tiny addition about variant dualites
more minor improvements

@@
 where we compose the linear maps before tracing over~$V_{\check{N}}$.
+\owen{Please double-check that formula.}
 \end{dfn}
 
-\owen{Please double-check that formula.}
+Note that the lower bound on $N$ and $\check{N}$ is simply to ensure that we have nontrivial gauge groups.
 %In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
@@
 
-The usual Seiberg duality states how certain ``electric'' and ``magnetic'' versions of SQCD should be equivalent.
+Seiberg duality states how certain ``electric'' and ``magnetic'' versions of SQCD should be equivalent.
 The electric and magnetic holomorphic QCDs are precisely the holomorphic twists of those that appear in Seiberg duality,
@@
 
+\begin{rmk}
+The statement is an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$-graded.
+\end{rmk}
+
 This claim should seem rather surprising.
@@
 one side has mesons and the other does not.
-But this feature also makes the conjecture powerful.
-
-The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$-graded.
+Of course, relating quite different theories also makes the conjecture powerful.
 
@@
 \begin{enumerate}
-\item[(2)] There are {\em flavor} symmetries that act on each theory, and these can be matched under the duality. Under quantization, these have isomorphic anomalies.
-\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields.
+\item[(2)] There are {\em flavor} symmetries by $SL(F)$ that act on the quarks and antiquarks of each theory, 
+and these can be matched under the duality. 
+For the classical holomorphic theories, these symmetries enhance to an action of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
 Under quantization, these have isomorphic anomalies.
+\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, 
+and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields. Under quantization, these have isomorphic anomalies.
 \end{enumerate}
@@
 \subsubsection{Moduli of vacua and quantization}
-
-\owen{I want to describe here, at least briefly, what the moduli stack is.
-I'm not sure the stacks are equivalent, but I think they have equivalent affinizations.
-I wonder if we can exhibit an equivalence of the "quantum" affinizations.}
 
@@
 Instead, they have worked with a GIT quotient.
-For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with
+For instance, if the moduli stack of classical vacua were $V/G$, it means physicists work with
 \[
@@
 This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
-In practice physicists work ordinary schemes (i.e., without any derived directions), although one can also study the derived affine scheme that is the best approximation to a derived stack.
 We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
 (Note that the font of M changes between stack and space.)
+
+\begin{rmk}
+In practice physicists work ordinary schemes (i.e., without any derived directions), 
+although one can also study the derived affine scheme that is the best approximation to a derived stack.
+Below we will always provide an ordinary scheme as the moduli {\em space}.
+\end{rmk}
 
@@
 The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
-On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion, whereas the space cannot distinguish between some vacua.
+In other words, the possible classical states --- viewed as suitable linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
+On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
+and hence records much more about the classical theory; 
+the space cannot distinguish between some vacua because it collapses orbits.
 Moreover, the stack encodes much more data about the theory near each vacuum.
@@
 The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem.
+\owen{I'm trying to find a completely careful and explicit statement of the $SL(N)$ case.}
 In other words,
@@
 This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
-One disocvers the need for mesons and the superpotential in order to obtain this result.
+The proof boils down to checking that the mesons and the superpotential on the magnetic side ensure the isomorphism.
 

### 2022-09-23 draft.tex
raised q about statement of duality
merge

--- 2022-09-20 draft.tex
@@
 
-\begin{dfn}
+\begin{dfn}[\cite{FHK}]
 For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$\fg \otimes \sfA_d$.
-Following \cite{FHK} we denote it by~$\fg^\bullet_d$.
+We denote it by~$\fg^\bullet_d$.
 \end{dfn}
@@
 \[
-{\rm Hoch}_*(A) \simeq \check{C}(\mathfrak{U},\cF_A)
+{\rm Hoch}_\bu(A) \simeq \check{C}(\mathfrak{U},\cF_A)
 \]
@@
 
+\subsection{Examples of holomorphic factorization algebras}
+
 \subsection{Toric (KK) reduction vs. chiralization}
@@
 
-We have already met the higher dimensional $\beta\gamma$ system on $\CC^n$.
-This is an $n$-dimensional holomorphic system described by an $n$-dimensional translation invariant factorization algebra.
-In part, the fields of this system constituted a holomorphic map $\gamma \colon \CC^n \to \CC^N$ together with its conjugate field $\beta$.
-
-\brian{background on CDO's}
+A sheaf of chiral differential operators is a `chiralization' the familiar sheaf of differential operators on a complex manifold \cite{}.
+It is a sheaf of vertex algebras $\CDO_X$ on a complex manifold $X$ which satisfies the property that under the Zhu construction one has an isomorphism of sheaves of associative algebras
+\beqn
+\text{Zhu}(\CDO_X) \simeq \cD_X
+\eeqn
+where $\cD_X$ is the sheaf of differential operators.
+
+Unlike the sheaf of differential operators, one needs to fix additional data in order to define a sheaf of chiral differential operators. 
+For a smooth complex manifold $X$, one of the main results of \cite{} is that the obstruction to the existence of such a sheaf is given by
+\beqn
+\ch_2(\T_X) \in H^{2}(X, \Omega^{2,cl}_X) 
+\eeqn
+and the space of all such algebras of chiral differential operators is a torsor for the group $H^{1}(X, \Omega^{2,cl}_X)$.
+Here $\Omega^{2,cl}_X$ is the sheaf of closed holomorphic two-forms on $X$.
+
+Locally, on an affine patch in $X$, the vertex algebra $\CDO_X$ is equivalent to $N$-copies of the familiar $\beta\gamma$ vertex algebra, where $N = \dim_\CC(X)$. 
+We have seen that there is a natural generalization of the $\beta\gamma$ system to a holomorphic factorization algebra in any dimension.
 
@@
 
-\begin{rmk}
-When $n=1$ we \cite{GGW} \brian{finish}
-\end{rmk}
+Anticipated by Witten, and proved in \cite{GGW}, the sheaf of chiral differential operators is given by the algebra of local operators of a familiar chiral CFT: the $\beta\gamma$ system of maps $\CC \to X$.
+In this note, we have described a higher dimensional analog of this system as a holomorphic $\sigma$-model of maps $\CC^n \to X$. 
+We have already met the higher dimensional $\beta\gamma$ system on $\CC^n$.
+This is an $n$-dimensional holomorphic system described by an $n$-dimensional translation invariant factorization algebra.
+In part, the fields of this system constituted a holomorphic map $\gamma \colon \CC^n \to \CC^N$ together with its conjugate field $\beta$. ''
 
@@
 and let $\fg_\CC$ denotes its complex Lie algebra.
+We assume that $\fg_\CC$ is equipped with a non-degenerate symmetric invariant pairing and will freely identify $\fg_\CC$ with its linear dual using this data.
 
 The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
-A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of a shift of the adjoint bundle ${\mathrm ad}(\cP) \to X$.
-\owen{rephrase the second part?}
+It will be convenient for us to assume that $X$ is equipped with a holomorphic volume form that we denote by $\Omega_X$. 
+A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle ${\mathrm ad}(\cP) \to X$.
 The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
+\brian{got rid of the term `shifted' section. Also, to write theory like this we use a CY structure, which I've now fixed.e}
 
@@
 \owen{Is it a cotangent theory? It looks like a twisted cotangent theory.}
-The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
+\brian{right, $i_{dW}$ is the `twist'.}
+The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$ \brian{How do you feel about the notation $\RR \text{Crit}(W)$?}, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
 (It is the Koszul complex associated to the Jacobi ring of $W$.)
@@
 %As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
-By itself (i.e., before coupling to a gauge theory) the twisted matter multiplet corresponds to the mapping space ${\rm Map}(X, {\rm Crit}^d(W))$.
+By itself (i.e., before coupling to a gauge theory) the twisted matter multiplet corresponds to the mapping space ${\rm Map}(X, {\rm Crit}^d(W))$.\footnote{Notice that AKSZ formalism equips this mapping space with a $1$-shifted symplectic structure as opposed to the desired $(-1)$-shifted symplectic structure.
+Hereon we totalize all gradings to $\ZZ/2$.}
 
@@
 which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
-\owen{I'm not sure we even need this.}
+\owen{I'm not sure we even need this.} \brian{Probably if we want to cite a model for it, I think its fine to list the references here though.}
 %As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
@@
 \owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}
+\brian{That's already in this hamiltonian reduction. 
+If $V$ is $(-1)$ shifted symplectic then I think the tangent space of $V \Sslash G$ should be
+\beqn
+\lie{g}[1] \oplus V \oplus \lie{g}^*[-2] .
+\eeqn
+Since we're forgetting to $\ZZ/2$ this is just $\Pi \lie{g} \oplus (V \oplus \lie{g})$.
+}
 
@@
 \[
-V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F} \cong \CC^{NF},
+V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F},
 \] 
@@
 \[
-V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F} \cong \CC^{NF}, 
+V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F}, 
 \]
@@
 \[
-Q^\dag \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad R^\dag \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
+q \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad r \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
 \]
 \end{itemize}
-(The superscript $\dag$ does not mean we apply an operation to $Q$ or $R$; 
-it is simply to remind us that these fields are the ``antiparticles''.)
 
@@
 where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
-We will denote this theory by $\cT(N,F)$.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.}
+%We will denote this theory by $\cT(N,F)$.
+\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
 \end{dfn}
@@
 \begin{dfn}
-A holomorphic QCD theory {\em with mesons}, denoted $\cT(N,F, V_M, W)$, is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
+A holomorphic QCD theory {\em with mesons}
+%, denoted $\cT(N,F, V_M, W)$, 
+is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
 \[
@@
 \] 
+Notice that to write down the superpotential term we are utilizing the holomorphic volume form $\Omega_X = \d^2 z$. 
 \end{dfn}
@@
 We denote it by~$\cT_{\sfE}(F, N)$.
-We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
-
-The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
-(and $\check{L}$ for the partner field to $\check{M}$).
-We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
-The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{M}  \check{Q}),$$
+
+The {\em magnetic theory} is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\check{W} =  \Tr(\check{q} \check{M}  \check{Q}),$$
 where we compose the linear maps before tracing over~$V_{\check{N}}$.
+We denote this theory by~$\cT_{\sfM}(F, \check{N})$.
 \end{dfn}
 
-\owen{Please double-check that formula.}
 %In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
@@
 
-This claim should seem rather surprising.
-In many ways these theories look, on their face, like very different theories:
-the gauge groups $SL(N)$ and $SL(\check{N})$ are (usually) different, and
-one side has mesons and the other does not.
-But this feature also makes the conjecture powerful.
-
 The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$-graded.
@@
 the quotient by $G$ arises from the gauge transformation.
-For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has \owen{true?}
+For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
 \[
@@
 (We are working in a $\ZZ/2$-graded world here.)
+Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$\fg / G$. 
 For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
@@
 For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with 
+\brian{I don't like this notation, its confusing since it looks like symplectic reduction which has already appeared. 
+What about $[V/G]$?}
 \[
@@
 
-For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
+For the holomorphic QCD theory with $F$ flavors and $N$ colors (without mesons), 
 the moduli stack of classical vacua is 
@@
 \]
-By contrast the moduli space is a variety already well-studied in classical algebraic geometry.
-The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q $, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
-
-\[
-M_{\rm vac}(\cT) \cong ,
+By contrast the moduli space is a well-known variety, 
+\[
+M_{\rm vac}(\cT) \cong \Gr(F, N),
 \]
@@
 This result follows from classical invariant theory.
-(
+(The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q$, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
 Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)

### 2022-09-23 draft.tex

--- 2022-09-22 draft.tex
@@
 Note that the lower bound on $N$ and $\check{N}$ is simply to ensure that we have nontrivial gauge groups.
+
 %In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
@@
 
+\owen{Do we want $F > N+1$?
+The physicists break things into several cases.
+In particular, I think the moduli is unchanged under quantization only if $F$ is big enough relative to $N$ and $\check{N}$.}
+
 \begin{rmk}
@@
 Instead, they have worked with a GIT quotient.
-For instance, if the moduli stack of classical vacua were $V/G$, it means physicists work with
+For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with 
+\brian{I don't like this notation, its confusing since it looks like symplectic reduction which has already appeared. 
+What about $[V/G]$?}
 \[
@@
 
-For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
-the derived stack of classical vacua is 
+For the holomorphic QCD theory with $F$ flavors and $N$ colors (without mesons), 
+the moduli stack of classical vacua is 
 \[
@@
 Those theorems tell us that the GIT quotient is a closed conical subvariety
+>>>>>>> 46317a9ff2fa2a1a491852a8c6266ecf16d084c0
 \[

### 2022-09-27 draft.tex
partway through flavor symmetry

@@
 \[
-M \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad N \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
+\mu \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad \nu \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
 \]
@@
 \[
-S_{QCDwM} = S_{QCD} + \int N \,\dbar M + \int \d^2 z \; W(Q, \Tilde{Q}, M) .
+S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, \Tilde{Q}, \mu) .
 \] 
@@
 
-Note that the fields $M$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
-The only coupling that the meson $M$ has to the other fields is through the superpotential~$W$.
+Note that the fields $\mu$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
+The only coupling that the meson $\mu$ has to the other fields is through the superpotential~$W$.
 
@@
 
-The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
+The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
 (and $\check{L}$ for the partner field to $\check{M}$).
 We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
-The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{M}  \check{Q}),$$
+The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
 where we compose the linear maps before tracing over~$V_{\check{N}}$.
@@
 \[
-\cM_{\rm vac} \cong V/G
-\]
-where $V$ is a (graded) $G$-representation and $V/G$ denotes the quotient stack.
+\cM_{\rm vac} \cong [V/G]
+\]
+where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
 The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
@@
 \[
-\cM_{\rm vac} \cong X/G
-\]
-where $X$ is a derived stack with a $G$-action and $X/G$ denotes the quotient stack.
+\cM_{\rm vac} \cong [X/G]
+\]
+where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.
 
@@
 Instead, they have worked with a GIT quotient.
-For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with 
+For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
 \brian{I don't like this notation, its confusing since it looks like symplectic reduction which has already appeared. 
-What about $[V/G]$?}
+What about $[V/G]$?} \owen{I'm happy to do that, but symplectic reduction is the GIT quotient.}
 \[
@@
 \[
-V/G \to V\Sslash G
+[V/G] \to V\Sslash G
 \]
 often collapses orbits together.
-An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $\gl_N/ GL_N$, whose affinization is
-\[
-\gl_N \Sslash GL_N \cong \CC^N/S_N,
-\]
-by the Chevalley restriction theorem.
+An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$, whose affinization is
+\[
+\gl_N \Sslash GL_N \cong \CC^N,
+\]
+by the Chevalley restriction theorem $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
+(The rightmost algebra is symmetric polynomials.)
 The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
@@
 Those theorems tell us that the GIT quotient is a closed conical subvariety
->>>>>>> 46317a9ff2fa2a1a491852a8c6266ecf16d084c0
 \[
@@
 where a pair of matrices $(X,Y) \in \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)$ goes to $(\Lambda^N X, \Lambda^N Y, YX)$, with $\Lambda^N X$ denoting the wedge product of the rows of $X$ (and of columns for $Y$).
-The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem.
-\owen{I'm trying to find a completely careful and explicit statement of the $SL(N)$ case.}
-In other words,
+The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem, such as that the pairing of $\Lambda^N X$ and $\Lambda^N Y$ can be related to $\Lambda^N (YX)$.
+(See Chapter 2, Section C of \cite{Weyl}.)
+In other words, we have a closed subvariety
 \[
@@
 with ${\rm R}(F,N) \subset \End(\CC^F)$ the matrices with rank bounded above by~$N$.
-The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.
+The moduli space for the magnetic theory is a bit more complicated but follows from classical invariant theory as well.
 
@@
 
-We fix some notation for the fields of the electric and magnetic theories. 
-The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$.
-
-With respect to a basis for $\CC^{N_f}$ we denote the matter fields of the electric theory as
-\[
-Q^i\; , \; P_i \; , \; \Tilde{Q}_i \; , \; \Tilde{P}^i , \quad i = 1, \ldots, N_f.
-\]
-Each of these fields are Dolbeault forms that are valued in the fundamental $\SU(N_c)$ representation.
-
-The matter fields of the magnetic theory will be denoted by lower case letters to avoid confusion
-\[
-q^i\; , \; p_i \; , \; \Tilde{q}_i \; , \; \Tilde{p}^i , \quad i = 1, \ldots, N_f.
-\]
-Again, each of these fields are Dolbeault valued but this time they each transform under the fundamental $\SU(N_f-N_c)$ representation. 
-On the magnetic side one also has the `meson' fields $M_{i}^j$, which are scalars under the gauge group.
-
-Holomorphic QCD enjoys a few familiar holomorphic symmetries in the style that we discussed in this note.
-
-The first is a holomorphic `flavor' symmetry, which will manifest itself as a symmetry by the $2$-dimensional holomorphic current algebra. 
-Consider the Lie algebra $\sl(N_f)$.
-
-The holomorphic background field $\fa = (\fa_i^j) \in \Omega^{0,\bu}(\CC^2 , \sl(N_f))$ naturally couples to both the electric and magnetic theory in the following ways:
-\[
-I^F_\sfE = \int P_j \fa_i^j Q^i , \qquad I^F_\sfM = \int \Tilde{p}_j \sfa_j^i \Tilde{q}^j + \int L^k_j \sfa_i^j M^i_k . 
-\]
-
-This determines a classical symmetry of both sides of the duality by the local Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(N_f))$. 
-In particular, the two state spaces form a module for the $S^3$-current algebra $\sfA_2 \otimes \sl(N_f)$ at the classical level.
+The quarks of the electric theory take values in $\Hom(\CC^F, \CC^N)$ and hence have a canonical action of $SL(F)$ by precomposition.
+We view each factor $\CC$ inside $\CC^F$ as a different ``flavor'' of quark, so this action mixes flavors.
+The antiquarks take values in $\Hom(\CC^N, \CC^F)$ and so have a canonical action of $SL(F)$ by postcomposition.
+The action functional is invariant for this action, and thus $SL(F)$ acts naturally on the space of solutions to the equations of motion.
+This symmetry is known as {\em flavor} symmetry.
+The magnetic theory has an analogous flavor symmetry, where $SL(F)$ acts on the mesons by conjugation.
+\owen{Right?}
+
+%We fix some notation for the fields of the electric and magnetic theories. 
+%The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$. 
+%
+%With respect to a basis for $\CC^{N_f}$ we denote the matter fields of the electric theory as
+%\[
+%Q^i\; , \; P_i \; , \; \Tilde{Q}_i \; , \; \Tilde{P}^i , \quad i = 1, \ldots, N_f.
+%\]
+%Each of these fields are Dolbeault forms that are valued in the fundamental $\SU(N_c)$ representation. 
+%
+%The matter fields of the magnetic theory will be denoted by lower case letters to avoid confusion
+%\[
+%q^i\; , \; p_i \; , \; \Tilde{q}_i \; , \; \Tilde{p}^i , \quad i = 1, \ldots, N_f.
+%\]
+%Again, each of these fields are Dolbeault valued but this time they each transform under the fundamental $\SU(N_f-N_c)$ representation. 
+%On the magnetic side one also has the `meson' fields $M_{i}^j$, which are scalars under the gauge group.
+%
+%Holomorphic QCD enjoys a few familiar holomorphic symmetries in the style that we discussed in this note.
+
+For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,*}(\CC^2, \sl(F))$, 
+which we call a $2$-dimensional holomorphic current algebra.
+It acts by wedging the forms and applying $\sl(F)$ to the relevant vector space, such as~$\Hom(\CC^F,\CC^N)$.
+
+%The holomorphic background field $\fa = (\fa_i^j) \in \Omega^{0,\bu}(\CC^2 , \sl(N_f))$ naturally couples to both the electric and magnetic theory in the following ways:
+%\[
+%I^F_\sfE = \int P_j \fa_i^j Q^i , \qquad I^F_\sfM = \int \Tilde{p}_j \sfa_j^i \Tilde{q}^j + \int L^k_j \sfa_i^j M^i_k . 
+%\]
+%
+%This determines a classical symmetry of both sides of the duality by the local Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(N_f))$. 
+%In particular, the two state spaces form a module for the $S^3$-current algebra $\sfA_2 \otimes \sl(N_f)$ at the classical level.
+
 A natural question is whether this symmetry persists at the quantum level. 
-The answer is {\em yes}, but on both sides of the duality one must take into account central extensions.
-These central extensions give rise to symmetries by higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ which act on the electric and magnetic sides, respectively.
-Here $\theta_\sfE, \theta_\sfM$ are invariant cubic polynomials on the Lie algebra $\sl(N_f)$.
+The answer is {\em yes}, but on both sides of the duality one must use a central extension of the current algebra as an $L_\infty$ algebra.
+The extension arises because the symmetry has an anomaly under quantization (on either side of the duality),
+and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
+(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - \{0\}$.)
 
 \begin{prop}
-The central extensions of the dual theories agree $\theta_\sfE = \theta_\sfM$. 
+The central extensions of the dual theories agree: 
+\[
+\theta_\sfE = \theta_\sfM.
+\] 
 In particular, the state spaces $\sfV_\sfE, \sfV_\sfM$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(N_f)}_{2,\theta}$.
@@
 \begin{proof}[Sketch of proof]
-This boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section \ref{sec:renorm}. 
-For this calculation the gauge algebra $\sl(N_c)$ plays a minimal role. 
-The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by the background gauge field $\sfa$.
-
-In the electric case there are $N_c$ of such diagrams, all the internal edges are labeled by $Q-P$ propagators. 
+This boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
+For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
+The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element $\sfa$ of the current algebra, which we treat as a background gauge field.
+
+In the electric case there are $N$ such diagrams, with all the internal edges are labeled by $Q-R$ propagators. 
 This gives rise to the local anomaly
 \beqn\label{eqn:electricflavor}
-N_c \frac16 \int \op{tr}_{N_f} \left(\sfa \partial \sfa \partial \sfa\right) 
+N \frac16 \int \op{tr}_{\underline{F}} \left(\sfa \partial \sfa \partial \sfa\right) 
 \eeqn
-where $\op{tr}_{N_f}$ denotes the trace in the fundamental $\sl(N_f)$-representation.
-
-The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: (a) those with 
-internal edges labeled by $\Tilde{q}-\Tilde{p}$ propagators and (b) those will internal edges labeled by $M-L$ propagators. 
-There are $(N_f - N_c)$ copies of diagram (a) which gives rise to the term
-\[
-(N_f - N_c) \frac16 \int \op{tr}_{\Bar{N_f}} \left(\sfa \partial \sfa \partial \sfa\right) .
-\]
+where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.
+
+The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: 
+\begin{itemize}
+\item[(a)] those with  internal edges labeled by $\check{Q}-\check{R}$ propagators and 
+\item[(b)] those will internal edges labeled by $\check{\mu}-\check{\nu}$ propagators. 
+\end{itemize}
+There are $\check{N} = F - N$ copies of diagram (a), which gives rise to the term
+\[
+\check{N} \frac16 \int \op{tr}_{\Bar{\underline{F}}} \left(\sfa \partial \sfa \partial \sfa\right) .
+\]
+\owen{Continue from here}
 Here, $\op{tr}_{\Bar{N_f}}$ denotes the trace in the anti-fundamental representation. 

### 2022-09-27 draft.tex
revised flavor symmetry

@@
 where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
+\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
 %We will denote this theory by $\cT(N,F)$.
@@
 
+An analogous result holds for the flavor symmetry on the antiquarks.
+
 \begin{proof}[Sketch of proof]
-This boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
+The argument boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
 For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
-The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element $\sfa$ of the current algebra, which we treat as a background gauge field.
+The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,*}(\CC^2, \sl(F))$, which we treat as a background gauge field.
+In formulas, we couples to both the electric and magnetic theory via interactions
+\[
+I^F_\sfE = \int (R, \sfa Q)  \qquad\text{and}\qquad I^F_\sfM = \int (\check{R}, \sfa \check{Q}) + \int (\check{\nu}, \sfa \check{\mu}),
+\]
+where we use parentheses $(-,-)$ to denote the pairings in BF and $\beta\gamma$ theories.
 
@@
 \beqn\label{eqn:electricflavor}
-N \frac16 \int \op{tr}_{\underline{F}} \left(\sfa \partial \sfa \partial \sfa\right) 
+ \frac{N}{16} \int \op{tr}_{\underline{F}} \left(\sfa \, \partial \sfa \, \partial \sfa\right) 
 \eeqn
@@
 \[
-\check{N} \frac16 \int \op{tr}_{\Bar{\underline{F}}} \left(\sfa \partial \sfa \partial \sfa\right) .
-\]
-\owen{Continue from here}
-Here, $\op{tr}_{\Bar{N_f}}$ denotes the trace in the anti-fundamental representation. 
-There are $N_f$ copies of diagram (b) which gives rise to the term
-\[
-N_f \frac16\int \op{tr}_{N_f} \left(\sfa \partial \sfa \partial \sfa\right) 
-\]
-Since $\op{tr}_{\Bar{N_f}} (X^3) = - \op{tr}_{N_f} (X^3)$ for any $X \in \sl(N_f)$, we see that the sum of these two terms agrees with the electric side \eqref{eqn:electricflavor}.
+ \frac{\check{N}}{16} \int \op{tr}_{\underline{F}^*} \left(\sfa \, \partial \sfa \, \partial \sfa\right) .
+\]
+Here, $\op{tr}_{\underline{F}^*}$ denotes the trace in the dual to the fundamental representation. 
+There are $F$ copies of diagram (b), which gives rise to the term
+\[
+\frac{F}{16}\int \op{tr}_{\underline{F}} \left(\sfa\, \partial \sfa \, \partial \sfa\right).
+\]
+Since $\op{tr}_{\underline{F}^*} (T^3) = - \op{tr}_{\underline{F}} (T^3)$ for any $T \in \sl(F)$, 
+we see that the sum of these two terms agrees with \eqref{eqn:electricflavor} on the electric side.
 \end{proof}
-
-There is also a `tilded' version of the flavor symmetry for the same Lie algebra $\sl(N_f)$ but where the local Noether currents read $\int \Tilde{P}^i \Tilde{\sfa}_i^j \Tilde{Q}^i$ and $\int \Tilde{p}^i \Tilde{\sfa}_i^j \Tilde{q}^i$.
-An analogous result holds for this symmetry.
 

### 2022-09-27 draft.tex
first pass at scft part

@@
 \begin{prop}
-The central extensions of the dual theories agree: 
+There is an anomaly at the quantum level for the holomorphic flavor symmetry action for both the electric and magnetic theories,
+and they agree: they are labeled by the same cocycle 
 \[
@@
 The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,*}(\CC^2, \sl(F))$, which we treat as a background gauge field.
-In formulas, we couples to both the electric and magnetic theory via interactions
+In formulas, we couple the current algebra to both the electric and magnetic theory via interactions
 \[
@@
 
-The physical statement of Seiberg duality is that dual theories flow to the same superconformal fixed point in the infrared limit. 
-This only makes sense when the integers $N_c,N_f$ satisfy appropriate bounds ensuring that such a superconformal fixed point exists.
-
-We will describe how this `superconformal window'--the bounds where one expects such flows to exist--appears from the point of view of holomorphic QCD.
-
-We start off with the (complexified) 4-dimensional $\cN=1$ superconformal algebra $\sl(4|1)$.
+In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories flow to the same superconformal fixed point in the infrared limit. 
+These values are known as the ``superconformal window'',
+and we will explore how it appears from the point of view of holomorphic QCD.
+
+Consider the (complexified) 4-dimensional $\cN=1$ superconformal algebra $\sl(4|1)$.
 This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
 The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
-Inside of this algebra is the Cartan generator $\Delta$ of scaling transformations in $\RR^4$.
+Inside of this algebra is the Cartan generator $\Delta$ of scaling transformations in~$\RR^4$.
 
@@
 \]
-Thus, if one starts with a superconformal theory, one knows that at the level of the holomorphic twist the Lie algebra $\sl(3)$ will act.  
-In this sense, $\sl(3)$ is the `residual' superconformal symmetry at the level of the twist. 
-Inside of this twisted algebra $\sl(3)$ we have the ``holomorphic scaling'' operator $\Delta^{hol} = z_i \partial_{z_i}$, which is simply the holomorphic Euler vector field.  
-In fact, the entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$.\footnote{Endowed by the description of $\CC \PP^2$ as an ${\rm SL}(3)$-homogenous space.}
-Classically in the holomorphic twist this symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.
-
-\begin{thm}[\cite{SWsuco}] \label{thm:swsuco}
-Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ which resolves the Lie algebra of \ul{all} holomorphic vector fields on $\CC^2$. 
-This local Lie algebra is a classical symmetry of any theory of holomorphic QCD. 
+Thus, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ will act on the holomorphically twisted theory.  
+In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
+Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator $\Delta^{hol} = \sum_i z_i \partial_{z_i}$, which is simply the holomorphic Euler vector field.  
+In fact, the entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
+where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an ${\rm SL}(3)$-homogenous space.
+In the holomorphic twist as a classical theory, 
+this symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.
+
+\begin{thm}[\cite{SWsuco}] 
+\label{thm:swsuco}
+Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
+This local Lie algebra is a classical symmetry of any holomorphic QCD theory. 
 \end{thm}
 
-We ask when this classical symmetry persists at the quantum level. 
-Let us first consider the electric theory.
-
+We now ask when this classical symmetry persists at the quantum level.
+
+Consider first the electric theory. 
 Naively, the symmetry of holomorphic vector fields is obvious: all fields are described in terms of a Dolbeault complex resolving trivial holomorphic vector bundles of various ranks. 
@@
 For the matter fields, however, the action at the untwisted level is {\em not} compatible with this naive one. 
-This can even be seen at the level of the holomorphic Euler vector field: naively the field $Q = z_1^n z_2^m \otimes v \in \Omega^0 (\CC^2$ transforms like $\Delta^{hol}(Q) = (n+m) Q$.
-However, to be compatible with dimension scaling in the untwisted theory one actually has 
+The issue can be seen already just for the holomorphic Euler vector field.
+Naively, the field $Q = z_1^n z_2^m \otimes v \in \Omega^0 (\CC^2$ transforms like $\Delta^{hol}(Q) = (n+m) Q$;
+but to be compatible with dimension scaling in the untwisted theory, one needs
 \[
@@
 \]
-What this says is that as a representation for infinitesimal holomorphic diffeomorphisms the fields $Q, P$ do not take values in the trivial vector bundle, but actually take values in some line bundle.
-In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of \cite{WittenTwist} one finds that the $\beta\gamma$ matter fields live in
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes (\CC^{N_c})^{\oplus N_f} , \quad P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes (\CC^{N_c})^{\oplus N_f}
-\]
-and similarly for $\Tilde{Q}, \Tilde{P}$.
+What this constraint means is that, as a representation for holomorphic vector fields, the quark fields $Q$, $R$ take values in some interesting line bundle and not in the trivial vector bundle.  
+In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of \cite{WittenTwist}, 
+one finds that the quark fields are
+\[
+Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes V_Q 
+\] 
+and
+\[ P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes V_Q^*,
+\]
+and similarly for the antiquark ${Q}^\dag$ and~${P}^\dag$.
 
 \begin{prop}
-Consider the symmetry of the electric and magnetic theories $\cT_{\sfE / \sfM}(N_c,N_f)$ by the local Lie algebra of holomorphic vector fields described by Theorem \ref{thm:swsuco}. 
-There is an anomaly for this symmetry to exist at the quantum level and it is proportional to the local functional
-\[
-\left(N_f - 3N_c\right) \frac12 \int \partial_{z_i} X_i \op{Tr} (\partial A \partial A)  .
-\]
-where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form valued vector field and $A$ is a gauge field.
+For either an electric theory $\cT_{\sfE}(F,N)$ or magnetic theory $\cT_{\sfM}(F,N)$,
+the symmetry by the local Lie algebra of holomorphic vector fields, described by Theorem~\ref{thm:swsuco}
+has an anomaly to exist at the quantum level. 
+It is proportional to the local functional
+\[
+\left(F - 3N\right) \frac12 \int \partial_{z_i} X_i \op{Tr} (\partial A \, \partial A)  .
+\]
+where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form-valued vector field and $A$ is a gauge field.
+
+In particular, when $F = 3N$, the symmetry lifts to the quantum level.
 \end{prop}
 
-In particular, for the {\em same value} $N_f = 3 N_c$ both the electric and magnetic theories are endowed with an action by holomorphic vector fields at the quantum level.
+\owen{I'm not clear how this intertwines with duality. It looks like the anomalies don't match?}
 

### 2022-09-29 draft.tex
merge

--- 2022-09-27 draft.tex
@@
 \[
-\mu \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad \nu \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
+M \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad N \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
 \]
@@
 \[
-S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, \Tilde{Q}, \mu) .
+S_{QCDwM} = S_{QCD} + \int N \,\dbar M + \int \d^2 z \; W(Q, \Tilde{Q}, M) .
 \] 
@@
 
-Note that the fields $\mu$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
-The only coupling that the meson $\mu$ has to the other fields is through the superpotential~$W$.
+Note that the fields $M$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
+The only coupling that the meson $M$ has to the other fields is through the superpotential~$W$.
 
@@
 
-The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
+The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
 (and $\check{L}$ for the partner field to $\check{M}$).
 We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
-The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
+The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{M}  \check{Q}),$$
 where we compose the linear maps before tracing over~$V_{\check{N}}$.
@@
 In particular, I think the moduli is unchanged under quantization only if $F$ is big enough relative to $N$ and $\check{N}$.}
+\brian{I expect we want a similar condition, but I was never able to understand how that appears at the level of factorization algebras.}
 
@@
 \[
-\cM_{\rm vac} \cong [V/G]
-\]
-where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
+\cM_{\rm vac} \cong V/G
+\]
+where $V$ is a (graded) $G$-representation and $V/G$ denotes the quotient stack.
 The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
@@
 \[
-\cM_{\rm vac} \cong [X/G]
-\]
-where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.
+\cM_{\rm vac} \cong X/G
+\]
+where $X$ is a derived stack with a $G$-action and $X/G$ denotes the quotient stack.
 
@@
 Instead, they have worked with a GIT quotient.
-For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
+For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with 
 \brian{I don't like this notation, its confusing since it looks like symplectic reduction which has already appeared. 
-What about $[V/G]$?} \owen{I'm happy to do that, but symplectic reduction is the GIT quotient.}
+What about $[V/G]$?}
 \[
@@
 \[
-[V/G] \to V\Sslash G
+V/G \to V\Sslash G
 \]
 often collapses orbits together.
-An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$, whose affinization is
-\[
-\gl_N \Sslash GL_N \cong \CC^N,
-\]
-by the Chevalley restriction theorem $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
-(The rightmost algebra is symmetric polynomials.)
+An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $\gl_N/ GL_N$, whose affinization is
+\[
+\gl_N \Sslash GL_N \cong \CC^N/S_N,
+\]
+by the Chevalley restriction theorem.
 The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
@@
 where a pair of matrices $(X,Y) \in \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)$ goes to $(\Lambda^N X, \Lambda^N Y, YX)$, with $\Lambda^N X$ denoting the wedge product of the rows of $X$ (and of columns for $Y$).
-The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem, such as that the pairing of $\Lambda^N X$ and $\Lambda^N Y$ can be related to $\Lambda^N (YX)$.
-(See Chapter 2, Section C of \cite{Weyl}.)
-In other words, we have a closed subvariety
+The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem.
+\owen{I'm trying to find a completely careful and explicit statement of the $SL(N)$ case.}
+In other words,
 \[
@@
 with ${\rm R}(F,N) \subset \End(\CC^F)$ the matrices with rank bounded above by~$N$.
-The moduli space for the magnetic theory is a bit more complicated but follows from classical invariant theory as well.
+The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.
 
@@
 
-The quarks of the electric theory take values in $\Hom(\CC^F, \CC^N)$ and hence have a canonical action of $SL(F)$ by precomposition.
-We view each factor $\CC$ inside $\CC^F$ as a different ``flavor'' of quark, so this action mixes flavors.
-The antiquarks take values in $\Hom(\CC^N, \CC^F)$ and so have a canonical action of $SL(F)$ by postcomposition.
-The action functional is invariant for this action, and thus $SL(F)$ acts naturally on the space of solutions to the equations of motion.
-This symmetry is known as {\em flavor} symmetry.
-The magnetic theory has an analogous flavor symmetry, where $SL(F)$ acts on the mesons by conjugation.
-\owen{Right?}
-
-%We fix some notation for the fields of the electric and magnetic theories. 
-%The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$. 
-%
-%With respect to a basis for $\CC^{N_f}$ we denote the matter fields of the electric theory as
-%\[
-%Q^i\; , \; P_i \; , \; \Tilde{Q}_i \; , \; \Tilde{P}^i , \quad i = 1, \ldots, N_f.
-%\]
-%Each of these fields are Dolbeault forms that are valued in the fundamental $\SU(N_c)$ representation. 
-%
-%The matter fields of the magnetic theory will be denoted by lower case letters to avoid confusion
-%\[
-%q^i\; , \; p_i \; , \; \Tilde{q}_i \; , \; \Tilde{p}^i , \quad i = 1, \ldots, N_f.
-%\]
-%Again, each of these fields are Dolbeault valued but this time they each transform under the fundamental $\SU(N_f-N_c)$ representation. 
-%On the magnetic side one also has the `meson' fields $M_{i}^j$, which are scalars under the gauge group.
-%
-%Holomorphic QCD enjoys a few familiar holomorphic symmetries in the style that we discussed in this note.
-
-For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,*}(\CC^2, \sl(F))$, 
-which we call a $2$-dimensional holomorphic current algebra.
-It acts by wedging the forms and applying $\sl(F)$ to the relevant vector space, such as~$\Hom(\CC^F,\CC^N)$.
-
-%The holomorphic background field $\fa = (\fa_i^j) \in \Omega^{0,\bu}(\CC^2 , \sl(N_f))$ naturally couples to both the electric and magnetic theory in the following ways:
-%\[
-%I^F_\sfE = \int P_j \fa_i^j Q^i , \qquad I^F_\sfM = \int \Tilde{p}_j \sfa_j^i \Tilde{q}^j + \int L^k_j \sfa_i^j M^i_k . 
-%\]
-%
-%This determines a classical symmetry of both sides of the duality by the local Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(N_f))$. 
-%In particular, the two state spaces form a module for the $S^3$-current algebra $\sfA_2 \otimes \sl(N_f)$ at the classical level.
-
+We fix some notation for the fields of the electric and magnetic theories. 
+The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$.
+
+With respect to a basis for $\CC^{N_f}$ we denote the matter fields of the electric theory as
+\[
+Q^i\; , \; P_i \; , \; \Tilde{Q}_i \; , \; \Tilde{P}^i , \quad i = 1, \ldots, N_f.
+\]
+Each of these fields are Dolbeault forms that are valued in the fundamental $\SU(N_c)$ representation.
+
+The matter fields of the magnetic theory will be denoted by lower case letters to avoid confusion
+\[
+q^i\; , \; p_i \; , \; \Tilde{q}_i \; , \; \Tilde{p}^i , \quad i = 1, \ldots, N_f.
+\]
+Again, each of these fields are Dolbeault valued but this time they each transform under the fundamental $\SU(N_f-N_c)$ representation. 
+On the magnetic side one also has the `meson' fields $M_{i}^j$, which are scalars under the gauge group.
+
+Holomorphic QCD enjoys a few familiar holomorphic symmetries in the style that we discussed in this note.
+
+The first is a holomorphic `flavor' symmetry, which will manifest itself as a symmetry by the $2$-dimensional holomorphic current algebra. 
+Consider the Lie algebra $\sl(N_f)$.
+
+The holomorphic background field $\fa = (\fa_i^j) \in \Omega^{0,\bu}(\CC^2 , \sl(N_f))$ naturally couples to both the electric and magnetic theory in the following ways:
+\[
+I^F_\sfE = \int P_j \fa_i^j Q^i , \qquad I^F_\sfM = \int \Tilde{p}_j \sfa_j^i \Tilde{q}^j + \int L^k_j \sfa_i^j M^i_k . 
+\]
+
+This determines a classical symmetry of both sides of the duality by the local Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(N_f))$. 
+In particular, the two state spaces form a module for the $S^3$-current algebra $\sfA_2 \otimes \sl(N_f)$ at the classical level.
 A natural question is whether this symmetry persists at the quantum level. 
-The answer is {\em yes}, but on both sides of the duality one must use a central extension of the current algebra as an $L_\infty$ algebra.
-The extension arises because the symmetry has an anomaly under quantization (on either side of the duality),
-and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
-(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - \{0\}$.)
+The answer is {\em yes}, but on both sides of the duality one must take into account central extensions.
+These central extensions give rise to symmetries by higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ which act on the electric and magnetic sides, respectively.
+Here $\theta_\sfE, \theta_\sfM$ are invariant cubic polynomials on the Lie algebra $\sl(N_f)$.
 
 \begin{prop}
-The central extensions of the dual theories agree: 
-\[
-\theta_\sfE = \theta_\sfM.
-\] 
+The central extensions of the dual theories agree $\theta_\sfE = \theta_\sfM$. 
 In particular, the state spaces $\sfV_\sfE, \sfV_\sfM$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(N_f)}_{2,\theta}$.
@@
 \begin{proof}[Sketch of proof]
-This boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
-For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
-The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element $\sfa$ of the current algebra, which we treat as a background gauge field.
-
-In the electric case there are $N$ such diagrams, with all the internal edges are labeled by $Q-R$ propagators. 
+This boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section \ref{sec:renorm}. 
+For this calculation the gauge algebra $\sl(N_c)$ plays a minimal role. 
+The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by the background gauge field $\sfa$.
+
+In the electric case there are $N_c$ of such diagrams, all the internal edges are labeled by $Q-P$ propagators. 
 This gives rise to the local anomaly
 \beqn\label{eqn:electricflavor}
-N \frac16 \int \op{tr}_{\underline{F}} \left(\sfa \partial \sfa \partial \sfa\right) 
+N_c \frac16 \int \op{tr}_{N_f} \left(\sfa \partial \sfa \partial \sfa\right) 
 \eeqn
-where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.
-
-The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: 
-\begin{itemize}
-\item[(a)] those with  internal edges labeled by $\check{Q}-\check{R}$ propagators and 
-\item[(b)] those will internal edges labeled by $\check{\mu}-\check{\nu}$ propagators. 
-\end{itemize}
-There are $\check{N} = F - N$ copies of diagram (a), which gives rise to the term
-\[
-\check{N} \frac16 \int \op{tr}_{\Bar{\underline{F}}} \left(\sfa \partial \sfa \partial \sfa\right) .
-\]
-\owen{Continue from here}
+where $\op{tr}_{N_f}$ denotes the trace in the fundamental $\sl(N_f)$-representation.
+
+The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: (a) those with 
+internal edges labeled by $\Tilde{q}-\Tilde{p}$ propagators and (b) those will internal edges labeled by $M-L$ propagators. 
+There are $(N_f - N_c)$ copies of diagram (a) which gives rise to the term
+\[
+(N_f - N_c) \frac16 \int \op{tr}_{\Bar{N_f}} \left(\sfa \partial \sfa \partial \sfa\right) .
+\]
 Here, $\op{tr}_{\Bar{N_f}}$ denotes the trace in the anti-fundamental representation. 

### 2022-09-29 draft.tex
small changes i hadnt saved

--- 2022-09-27 draft.tex
@@
 particularly in the setting of the geometric Langlands program.
-Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of smooth manifolds,
+Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of  manifolds,
 developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
 for questions in algebraic topology.
-Motivated by all this work, Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
+Motivated by these efforts (and benefiting from conversations as those works were in progress), 
+Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
 \end{rmk}
@@
 On the other hand, there is an open locus where the moduli stacks are equivalent:
-the semi-stable points of $V/G$ \owen{fix description, as it's possibly just the stable locus}.
-This locus determines the space $V//G$ and hence we have the isomorphism desired.
+the semi-stable points of $[V/G]$ \owen{fix description, as it's possibly just the stable locus}.
+This locus determines the space $V\Sslash G$ and hence we have the isomorphism desired.
 Let us try to unravel what this equivalence means for the field theories, both classical and quantum.
 
-Consider any semistable point $x$ in $V/G$.
+Consider any semistable point $x$ in $[V/G]s$.
 We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
@@
 Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
-Hence on the semistable locus of $V/G$, we can guarantee an equivalence of quantizations.
+Hence on the semistable locus of $[V/G]$, we can guarantee an equivalence of quantizations.
 

### 2022-09-30 draft.tex
edits to seiberg

--- 2022-09-27 draft.tex
@@
 \owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
+\brian{BTW, I think you've now switched from lower case $r,q$ for antiquarks to $R^\dag, Q^\dag$, is that right?
+}
 %We will denote this theory by $\cT(N,F)$.
@@
 \[
-S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, \Tilde{Q}, \mu) .
+S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, Q^\dag, \mu) .
 \] 
@@
 For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
-\brian{I don't like this notation, its confusing since it looks like symplectic reduction which has already appeared. 
-What about $[V/G]$?} \owen{I'm happy to do that, but symplectic reduction is the GIT quotient.}
 \[
@@
 \begin{rmk}
-In the physics literature this isomorphism is given by explicitly matching gauge-invariant functions, 
+In the literature this isomorphism is given by explicitly matching gauge-invariant functions, 
 which are often called mesons or baryons, 
@@
 The magnetic theory has an analogous flavor symmetry, where $SL(F)$ acts on the mesons by conjugation.
-\owen{Right?}
 
@@
 
-For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,*}(\CC^2, \sl(F))$, 
+For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(F))$, 
 which we call a $2$-dimensional holomorphic current algebra.
 It acts by wedging the forms and applying $\sl(F)$ to the relevant vector space, such as~$\Hom(\CC^F,\CC^N)$.
-
-%The holomorphic background field $\fa = (\fa_i^j) \in \Omega^{0,\bu}(\CC^2 , \sl(N_f))$ naturally couples to both the electric and magnetic theory in the following ways:
-%\[
-%I^F_\sfE = \int P_j \fa_i^j Q^i , \qquad I^F_\sfM = \int \Tilde{p}_j \sfa_j^i \Tilde{q}^j + \int L^k_j \sfa_i^j M^i_k . 
-%\]
-%
-%This determines a classical symmetry of both sides of the duality by the local Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(N_f))$. 
-%In particular, the two state spaces form a module for the $S^3$-current algebra $\sfA_2 \otimes \sl(N_f)$ at the classical level.
+On local observables, the $S^3$-mode algebra $\lie{sl}(F) \otimes \sfA_2$ (which is the algebraic version of $\sl(F) \otimes \Omega^{0,\bu}(\CC^2 - 0)$) acts at the classical level.
 
@@
 and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
-(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - \{0\}$.)
+(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - 0$.)
 
@@
 \] 
-In particular, the state spaces $\sfV_\sfE, \sfV_\sfM$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(N_f)}_{2,\theta}$.
+In particular, the local observables $\Obs_{\sfE} (0), \Obs_{\sfM} (0)$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(F)}_{2,\theta}$ which is a central extension of the $S^3$-mode algebra $\sl(F) \otimes \sfA_2$.
 \end{prop}
@@
 For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
-The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,*}(\CC^2, \sl(F))$, which we treat as a background gauge field.
+The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,\bu}(\CC^2, \sl(F))$, which we treat as a background gauge field.
 In formulas, we couple the current algebra to both the electric and magnetic theory via interactions
@@
 Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
-This local Lie algebra is a classical symmetry of any holomorphic QCD theory. 
+This local Lie algebra is a classical symmetry of the holomorphic QCD theory (in particular, the holomorphic twist of any four-dimensional supersymmetric QCD). 
 \end{thm}
@@
 The issue can be seen already just for the holomorphic Euler vector field.
-Naively, the field $Q = z_1^n z_2^m \otimes v \in \Omega^0 (\CC^2$ transforms like $\Delta^{hol}(Q) = (n+m) Q$;
+Naively, the field $Q = z_1^n z_2^m \otimes v$ transforms like $\Delta^{hol}(Q) = (n+m) Q$;
 but to be compatible with dimension scaling in the untwisted theory, one needs
@@
 \]
-and similarly for the antiquark ${Q}^\dag$ and~${P}^\dag$.
+and similarly for the antiquarks ${Q}^\dag$ and~${P}^\dag$.
 
@@
 \[
-\left(F - 3N\right) \frac12 \int \partial_{z_i} X_i \op{Tr} (\partial A \, \partial A)  .
+ \frac{F - 3N}{2} \int \partial_{z_i} X_i \op{Tr} (\partial A \, \partial A)  .
 \]
@@
 \owen{I'm not clear how this intertwines with duality. It looks like the anomalies don't match?}
+\brian{
+I'm not sure how to interpret this, so we may want to leave it out. 
+The thing I don't understand is what we can glean about `scale' at the level of the holomorphic twist. 
+I was hopeful about this computation since it's curious that this anomaly vanishes precisely at the upper bound of the `conformal window', but I'm not sure how to see the full window at the level of the twist.
+Any thoughts?
+}
 

### 2022-10-02 draft.tex
revised the scft discussion

@@
 Under quantization, these have isomorphic anomalies.
-\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, 
-and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields. Under quantization, these have isomorphic anomalies.
+\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and these can be matched under duality.
 \end{enumerate}
@@
 In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories flow to the same superconformal fixed point in the infrared limit. 
-These values are known as the ``superconformal window'',
-and we will explore how it appears from the point of view of holomorphic QCD.
+This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window''
+(note that it is preserved under swapping $N \leftrightarrow F-N$).
+Here we will explore how it appears from the point of view of holomorphic QCD.
 
@@
 In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
-Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator $\Delta^{hol} = \sum_i z_i \partial_{z_i}$, which is simply the holomorphic Euler vector field.  
-In fact, the entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
+The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
 where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an ${\rm SL}(3)$-homogenous space.
+(In a moment we will discuss how all holomorphic vector fields act on the theories.)
+
+Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator $\Delta^{\rm hol} = \sum_i z_i \partial_{z_i}$, which is simply the holomorphic Euler vector field.  
+We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
+Consider the electric theory. 
+On the gauge fields, $\Delta^{\rm hol}$ acts by the Lie derivative,
+but on matter fields, the action via Lie derivative is {\em not} what one obtains from the untwisted theory.
+Given a quark field $Q = z_1^n z_2^m \otimes v$, 
+one needs
+\[
+\Delta^{hol}(Q) = \left(n + m + \frac23\right) Q 
+\]
+to be compatible with dimension scaling in the untwisted theory.
+What this constraint means is that, as a representation for holomorphic vector fields, 
+the quark fields $Q$, $R$ take values in some interesting holomorphic vector bundle and not in the trivial vector bundle.  
+In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of~\cite{WittenTwist}, 
+one finds that the quark fields are
+\[
+Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes V_Q 
+\] 
+and
+\[ P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes V_Q^*,
+\]
+where $K$ denotes the canonical bundle.
+(The antiquarks ${Q}^\dag$ and~${P}^\dag$ live in a similar twisted bundle.) 
+\owen{Maybe we should discuss what this means for globalization: we need the canonical bundle to have cube roots!}
+
+This action of $\sl(3)$ extends to the quantizations, on both sides of the putative duality, by direct verification.
+In fact it holds for all holomorphic QCD theories, not just those in the superconformal window.
+
+\begin{lmm}
+The action of $\sl(3)$ on $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$ extends to their quantizations.
+\end{lmm}
+
 In the holomorphic twist as a classical theory,
-this symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.
+this $\sl(3)$-symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.
+In fact, this enhancement also works for all holomorphic QCD theories, not just those in the superconformal window.
+\owen{Am I understanding that correctly?}
 
@@
 Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
-This local Lie algebra is a classical symmetry of the holomorphic QCD theory (in particular, the holomorphic twist of any four-dimensional supersymmetric QCD). 
+This local Lie algebra is a classical symmetry of {\em any} holomorphic QCD theory. 
 \end{thm}
 
-We now ask when this classical symmetry persists at the quantum level.
-
-Consider first the electric theory. 
-Naively, the symmetry of holomorphic vector fields is obvious: all fields are described in terms of a Dolbeault complex resolving trivial holomorphic vector bundles of various ranks. 
-Therefore, holomorphic vector fields act naturally by Lie derivative everywhere. 
-In particular, the Euler vector field $\Delta^{hol}$ acts diagonally in the natural way.
-
-On the gauge fields, this naive action is consistent with the one present in the untwisted theory. 
-For the matter fields, however, the action at the untwisted level is {\em not} compatible with this naive one. 
-The issue can be seen already just for the holomorphic Euler vector field.
-Naively, the field $Q = z_1^n z_2^m \otimes v$ transforms like $\Delta^{hol}(Q) = (n+m) Q$;
-but to be compatible with dimension scaling in the untwisted theory, one needs
-\[
-\Delta^{hol}(Q) = \left(n + m + \frac23\right) Q .
-\]
-What this constraint means is that, as a representation for holomorphic vector fields, the quark fields $Q$, $R$ take values in some interesting line bundle and not in the trivial vector bundle.  
-In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of \cite{WittenTwist}, 
-one finds that the quark fields are
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes V_Q 
-\] 
-and
-\[ P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes V_Q^*,
-\]
-and similarly for the antiquarks ${Q}^\dag$ and~${P}^\dag$.
+We now ask when this classical symmetry persists at the quantum level, and an interesting anomaly emerges.
 
 \begin{prop}
-For either an electric theory $\cT_{\sfE}(F,N)$ or magnetic theory $\cT_{\sfM}(F,N)$,
+For an electric theory $\cT_{\sfE}(F,N)$,
 the symmetry by the local Lie algebra of holomorphic vector fields, described by Theorem~\ref{thm:swsuco}
-has an anomaly to exist at the quantum level. 
+has an anomaly to lift to the quantum level. 
 It is proportional to the local functional
 \[
- \frac{F - 3N}{2} \int \partial_{z_i} X_i \op{Tr} (\partial A \, \partial A)  .
+\frac{F - 3N}{2} \int {\rm div}(X) \op{Tr} (\partial A \, \partial A)  .
 \]
 where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form-valued vector field and $A$ is a gauge field.
-
-In particular, when $F = 3N$, the symmetry lifts to the quantum level.
 \end{prop}
 
-\owen{I'm not clear how this intertwines with duality. It looks like the anomalies don't match?}
-\brian{
-I'm not sure how to interpret this, so we may want to leave it out. 
-The thing I don't understand is what we can glean about `scale' at the level of the holomorphic twist. 
-I was hopeful about this computation since it's curious that this anomaly vanishes precisely at the upper bound of the `conformal window', but I'm not sure how to see the full window at the level of the twist.
-Any thoughts?
-}
+The first factor ${\rm div}(X)$ denotes the divergence $\sum_i\partial_{z_i} X_i$ of the vector field~$X$.
+We thus deduce the following.
+
+\begin{cor}
+Only when $F = 3N$ do all holomorphic vector fields lift to a symmetry lifts at the quantum level.
+There is, however, a symmetry of {\em divergence-free} holomorphic vector fields at the quantum level for any values of $F$ and~$N$.
+\end{cor}
+
+We will discuss how these enhanced symmetries might intertwine with duality below.
 
 \subsection{A second pass at holomorphic Seiberg duality, and its relations to Hori-Tong duality}
+
+\owen{Add section with conjecture about local spacetime symmetry and its quantization}
+and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields. Under quantization, these have isomorphic anomalies.
 

### 2022-10-03 draft.tex
added some improvements to final subsections

@@
 In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories flow to the same superconformal fixed point in the infrared limit. 
-This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window''
-(note that it is preserved under swapping $N \leftrightarrow F-N$).
+This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
+(Note that it is preserved under swapping $N \leftrightarrow F-N$.)
 Here we will explore how it appears from the point of view of holomorphic QCD.
@@
 
-\subsection{A second pass at holomorphic Seiberg duality, and its relations to Hori-Tong duality}
-
-\owen{Add section with conjecture about local spacetime symmetry and its quantization}
-and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields. Under quantization, these have isomorphic anomalies.
+\owen{Should we check that the quantum magnetic theory also has a divergence-free symmetry?}
+
+\subsection{A relation to Hori-Tong duality}
+
+A beautiful maneuver of physics is compactification, where one takes a field theory $\cT$ in $n$ dimensions and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
+We have already worked with a factorization algebra version of these maneuvers: 
+pushing forward along the map $\rho: \C^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
+For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
+We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.
+
+\begin{lmm}
+For a holomorphic QCD theory, this compactification is a Landau-Ginzburg B-model for \owen{finish! would it be easier just to spell out what happens to matter, gauge, and the QCD?}
+\end{lmm}
+
+Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
+or at least of $E_2$-algebras.
+
+\begin{conj}
+\owen{Unpack in some detail.}
+\end{conj}
+
+This conjecture is essentially due to Hori and Tong. \owen{Add some history, cite some references.}
+
+\subsection{A second pass at holomorphic Seiberg duality}
+
+In our attempts above to explore (and test) Eager's conjecture, we developed insights and highlighted issues that help to refine it.
 
@@
 On the other hand, there is an open locus where the moduli stacks are equivalent:
-the semi-stable points of $[V/G]$ \owen{fix description, as it's possibly just the stable locus}.
+the semi-stable points of the moduli stacks $\cM_{\rm vac}$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
 This locus determines the space $V\Sslash G$ and hence we have the isomorphism desired.
@@
 
-Consider any semistable point $x$ in $[V/G]s$.
+Consider any semistable point $x$.
 We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
-For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x (V//G)$ \owen{Elaborate}. 
+For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x \cM_{\rm vac}$ \owen{Elaborate: more accurately, it's into the formal neighborhood}.
 Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
@@
 Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
-Hence on the semistable locus of $[V/G]$, we can guarantee an equivalence of quantizations.
-
-This identification breaks down on the unstable locus, raising the following question.
-
-{\bf Question:}
+Hence on the semistable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.
+
+This identification breaks down on the unstable locus, raising the following question:
+\begin{quote}
 At the quantum level, what happens on the unstable locus? 
+\end{quote}
+Each unstable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
+and hence its quantization is more involved that at a semistable point and depends nontrivially the gauge group.
 
 In a related vein, we want to know what correspondence of quantum factorization algebras we expect from Seiberg duality. 
-The mismatch for the moduli stack of classical vacua must be fixed somehow.
+The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.
 
@@
 
-\owen{Other things: affinization as polydiscs algebras, comparison with mirror symmetry (note A-model involves instanton corrections)}
+\owen{Other things: affinization as polydiscs algebras}
 
@@
 
-Conjecture: There is an equivalence of affinizations of the quantum moduli stacks for Seiberg dual theories.
-
-This process probably looks away from the unstable locus in the same way that the classical part does.
+\begin{conj}
+There is an equivalence of affinizations of the quantum moduli stacks for Seiberg dual theories.
+That is, the quantum moduli spaces are isomorphic.
+\end{conj}
+
+This process probably ``looks away'' from the unstable locus in much the way that it does at the classical level,
+which provided our identification of moduli spaces of classical vacua.
+
+*********** Discuss enhanced spacetime symmetries ****************
+
+\owen{Add section with conjecture about local spacetime symmetry and its quantization}
+and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields. Under quantization, these have isomorphic anomalies.
 

### 2022-10-03 draft.tex
stupid macros

@@
 
-\begin{lmm}
+\begin{lem}
 The action of $\sl(3)$ on $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$ extends to their quantizations.
-\end{lmm}
+\end{lem}
 
@@
 We have already worked with a factorization algebra version of these maneuvers: 
-pushing forward along the map $\rho: \C^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
+pushing forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
 For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
@@
 
-\begin{lmm}
+\begin{lem}
 For a holomorphic QCD theory, this compactification is a Landau-Ginzburg B-model for \owen{finish! would it be easier just to spell out what happens to matter, gauge, and the QCD?}
-\end{lmm}
+\end{lem}
 

### 2022-11-10 draft.tex
tried to improve end of SD section

@@
 Their work offered powerful new tools that opened up much subsequent progress,
-and even impacted mathematics through the Seiberg-Witten equations (which is related to the topologically twisted versions of $\cN=2$ theory).
+and even impacted mathematics through the Seiberg-Witten equations (which are related to the topologically twisted versions of $\cN=2$ theory).
 
@@
 It will be convenient for us to assume that $X$ is equipped with a holomorphic volume form that we denote by $\Omega_X$. 
-A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle ${\mathrm ad}(\cP) \to X$.
+A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle $\mathrm{ad}(\cP) \to X$.
 The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
@@
 \owen{I'm not sure we even need this.} \brian{Probably if we want to cite a model for it, I think its fine to list the references here though.}
+\owen{Part of my concern is that Hamiltonian reduction is a version of GIT, and hence it is {\em not} stacky. The stack quotient seems more appropriate to me.}
 %As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
@@
 \[
-S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
-\]
-where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
+S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag,
+\]
+where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.}
 \owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
-\brian{BTW, I think you've now switched from lower case $r,q$ for antiquarks to $R^\dag, Q^\dag$, is that right?
-}
 %We will denote this theory by $\cT(N,F)$.
-\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
 \end{dfn}
@@
 \] 
-Notice that to write down the superpotential term we are utilizing the holomorphic volume form $\Omega_X = \d^2 z$. 
+Notice that to write down the superpotential term, we are utilizing the holomorphic volume form~$\Omega_X = \d^2 z$. 
 \end{dfn}
@@
 Note that the fields $\mu$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
+Hence we use $\dbar$ rather than $\dbar_A$.
 The only coupling that the meson $\mu$ has to the other fields is through the superpotential~$W$.
@@
 The notion of duality can refer to several kinds of relationships,
-but loosely speaking it means that some aspects of the two theories are equivalent under correspondence.
+but loosely speaking it means that some aspects of the two theories are equivalent under some correspondence.
 We will postpone saying anything precise till we have some terminology in place.
@@
 
-The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
+The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors and {\em without} mesons.
 We denote it by~$\cT_{\sfE}(F, N)$.
@@
 The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
-(and $\check{L}$ for the partner field to $\check{M}$).
+(and $\check{\nu}$ for the partner field to $\check{\mu}$).
 We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
@@
 Witten initiated this vein of research for topological twists \cite{},
-and Costello pushed it for holomorphic twists, particularly in the setting of holography \cite{}.
+and Costello advocated it for holomorphic twists, particularly in the setting of holography \cite{}.
 Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
@@
 Thus each theory has an associated {\em moduli space of classical vacua},
-which we describe in the next subsection.
+which we describe below.
 Each vacuum determines a perturbative field theory that one could try to quantize,
@@
 \[
-\cM_{\rm vac} \cong \fg^*/G,
+\cM_{\rm vac} \cong [\fg^*/G],
 \]
@@
 (We are working in a $\ZZ/2$-graded world here.)
-Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$\fg / G$. 
+Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
 For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
@@
 often collapses orbits together.
-An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$, whose affinization is
-\[
-\gl_N \Sslash GL_N \cong \CC^N,
-\]
-by the Chevalley restriction theorem $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
+An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$.
+Its affinization is
+\[
+\gl_N \Sslash GL_N \cong \CC^N
+\]
+by the Chevalley restriction theorem, 
+which says $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
 (The rightmost algebra is symmetric polynomials.)
@@
 The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
-In other words, the possible classical states --- viewed as suitable linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
+In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
 On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
@@
 By contrast the moduli space $M_{\rm vac}$ is a variety already well-studied in classical algebraic geometry.
-Before we jump to the full space, let's examine a simpler case involving just the quarks.
+Before we describe the full space, let's examine a simpler case involving just the quarks.
 A vacuum for the quark field is an element of $V_Q = \Hom(\CC^F, \CC^N)$,
@@
 \begin{prop}
-There is an anomaly at the quantum level for the holomorphic flavor symmetry action for both the electric and magnetic theories,
-and they agree: they are labeled by the same cocycle 
+For both the electric and magnetic theories, there is an anomaly at the quantum level for the holomorphic flavor symmetry action.
+These anaomlies agree: they are labeled by the same cocycle 
 \[
@@
 
-A beautiful maneuver of physics is compactification, where one takes a field theory $\cT$ in $n$ dimensions and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+A beautiful maneuver used in physics is compactification:
+given a field theory $\cT$ in $n$ dimensions, one takes an $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
 A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
@@
 
-******** Discussion about quantization **********
-
+\subsubsection{Subtleties with vacua}
+
+We saw that the moduli stacks of classical vacua are not equivalent, due to points with interesting stabilizers.
 On the other hand, there is an open locus where the moduli stacks are equivalent:
 the semi-stable points of the moduli stacks $\cM_{\rm vac}$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
-This locus determines the space $V\Sslash G$ and hence we have the isomorphism desired.
+This locus determines the GIT quotients and hence explains the isomorphism we saw on the moduli spaces.
 Let us try to unravel what this equivalence means for the field theories, both classical and quantum.
@@
 We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
-For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x \cM_{\rm vac}$ \owen{Elaborate: more accurately, it's into the formal neighborhood}.
-Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
-because there is an explicit identification of the tangent space to the corresponding point in the moduli space of the dual theory.
+For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the formal neighborhood of $x$ inside the moduli stack of vacua. 
+The isomorphism of moduli spaces ensures that there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$,
+because there is an explicit identification of the formal neighborhood of $x$ with the formal neighborhood of $x_D$. 
 Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
 Hence on the semistable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.
+
+\begin{prop}
+The isomorphism between the semi-stable locus of the two moduli stacks determines an isomorphism between quantizations over those loci.
+\end{prop}
 
@@
 and hence its quantization is more involved that at a semistable point and depends nontrivially the gauge group.
-
-In a related vein, we want to know what correspondence of quantum factorization algebras we expect from Seiberg duality. 
 The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.
 
-We note that in the physics literature, there are a number of modifications that are explored in this setting.
+\subsubsection{A proposal}
+
+Recall that the moduli space arises from the moduli stack by affinization.
+In other words, we move from studying translation-invariant solutions (the stack) to studying ``states'' (multiplicative linear functionals on the stack of solutions).
+The moduli of classical states are isomorphic.
+We hope that something similar happens at the quantum level.
+In other words, there is a moduli stack of quantum vacua and a moduli space of quantum vacua,
+and we hope the spaces are isomorphic.
+We sketch the idea as follows.
+
+\begin{dfn}
+For a holomorphic QCD theory let $\cM^q_{\rm vac}(F,N)$ denote the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf of factorization algebras on $\CC^2$.
+The value at a solution $x$ is a quantization of the observables for the classical perturbative theory labeled by~$x$.
+(One could focus, for simplicity, on the sheaf of polydiscs algebras.)
+
+Let $M^q_{\rm vac}(F,N)$ denote the global sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
+It is a factorization algebra on~$\CC^2$.
+(Again, one could focus, for simplicity, on the polydiscs algebra.)
+\end{dfn}
+
+We view $M^q_{\rm vac}(F,N)$ as an affinization of $\cM^q_{\rm vac}(F,N)$.
+Optimistically, we refine Eager's conjecture to the following.
+
+\begin{conj}
+Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
+There is an equivalence of 2-dimensional holomorphic factorization algebras
+\[
+M^q_{\rm vac}(F,N)_{\sfE} \simeq M^q_{\rm vac}(F,\check{N})_{\sfM}.
+\]
+\end{conj}
+
+We note that there may be many quantizations possible, but our experience in $\cN=4$ case suggests that there is an ``obvious'' one.
+\owen{Feel free to reel back this overblown statement.}
+
+We note that in the physics literature, there are a number of issues that are relevant in this setting.
 For instance, there are ``instanton corrections'' that cannot be found by perturbative techniques, although they can be treated in a mathematically precise way. 
-\owen{Mention others? RG flow, symmetry breaking, ...}
 It is interesting to wonder how these would appear in the holomorphic setting.
-
-\owen{Other things: affinization as polydiscs algebras}
-
-* Explain that you get a sheaf of polydiscs algebras over the moduli stack.
-We can view this as presenting a ``quantization of the moduli stack'' $\cM_{vac}^{\rm q}$ There is thus an ``affinization'' of the quantum moduli stack.
-
-\begin{conj}
-There is an equivalence of affinizations of the quantum moduli stacks for Seiberg dual theories.
-That is, the quantum moduli spaces are isomorphic.
-\end{conj}
-
-This process probably ``looks away'' from the unstable locus in much the way that it does at the classical level,
-which provided our identification of moduli spaces of classical vacua.
 

### 2022-11-14 draft.tex
random

@@
 I want to explain that taking the extremal radii means we cannot compose, which leads to the complicated VOA formulas.}
+
+\subsubsection{Examples related to vertex algebras}
+
+We have just recalled that in the complex dimension one case, holomorphic  polydiscs algebras (with a compatible $U(1)$ action) correspond to vertex algebras.
+Let us briefly point out a few examples of this correspondence.
+
+Given a Lie algebra $\lie{g}$ we obtain a one-dimensional holomorphic disc algebra $A_{\lie{g}}$ by the following construction. 
+To a disk $D_r(z)$ of radius $r$ centered at $z \in \CC$ we attach the cochain complex
+\beqn
+A_{\lie{g}} (D_r(z)) = C_\bu \left(\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z)) \right) 
+\eeqn
+Here, $\Omega^{0,\bu}_c(D_r(z))$ denotes the Dolbeault complex of compactly supported $(0,\bu)$ forms on the disc.
+Because the space of $(0,\bu)$ forms define a commutative dg algebra, 
+the complex $\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z))$ has the natural structure of a dg Lie algebra---the complex on the right hand side is the Chevalley--Eilenberg complex which computes the Lie algebra homology of this dg Lie algebra.
+Using the formalism of factorization algebras (which we recall in the next section) it is shown in \cite{CG2} how to equip $A_{\lie{g}}$ with the structure of a holomorphic disc algebra.
+The corresponding vertex algebra is the Kac--Moody vertex algebra of $\fg$ at level zero. 
+To obtain the vertex algebra associated to a nonzero level $\kappa$ one can deform this holomorphic polydisc algebra $A_{\fg} \rightsquigarrow A_{\fg, \kappa}$.
+
+Let $V$ be a vector space.
+Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
+To a disc $D = D_r(z)$ this assigns the following cochain complex
+\beqn
+\Sym \left(\Omega^{1,\bu}_c(D) \otimes V^* [1] \oplus \Omega^{0,\bu}_c (D) \otimes V [1]\right) 
+\eeqn
+where the differential is $\dbar + \triangle$ which we will explain momentarily. 
+We denote the linear generators of this symmetric algebra by $\gamma \in \Omega^{1,\bu}_c(D) \otimes V^* [1]$ and $\beta \in \Omega^{0,\bu}_c(D) \otimes V^* [1]$.
+Now, for the differential, $\dbar$ is the familiar operator (which acts in the standard way on $(0,\bu)$ and $(1,\bu)$ forms) and $\triangle$ can be defined on $\Sym^2$ summand by the formula
+\beqn
+\triangle (\gamma \cdot \beta) = \int_D \<\gamma, \beta\> . 
+\eeqn
+The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.
 
@@
 This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra.
+In fact, in \cite{GLL,Si Kai and Zhengping} it is shown how BV quantization for one-dimensional quantum field theories connects with the ordinary theory of deformation quantization.
 

### 2022-11-16 draft.tex
revisions on moduli

--- 2022-11-10 draft.tex
@@
 provided their quantizations, and began analyzing their factorization algebras.
-Following Eager, we can ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
+Following Eager, one might can ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
 \owen{This should be rephrased, and we should mention more people, like Philsang and Surya. We can mention pre-S-duality things (like our work and the EY stuff) and S-duality stuff.}
@@
 This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
+It might be seen as parametrizing ``states'' rather than solutions, 
+as it is defined via functions on the solutions (see Remark~\ref{sols vs states} for more).
 We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
@@
 
-\begin{rmk}
+\begin{rmk}\label{sols vs states}
 The physicists' focus on the moduli space is not unreasonable:
@@
 \[
-\cM_{\rm vac}(F,N) \cong T^*[1] \left(V_Q \oplus V_Q^*/SL(N)\right).
+\cM_{\rm vac}(\cT_{\sfE}(F,N)) \cong T^*[1] \left(V_Q \times V_Q^*/SL(N)\right).
 \]
@@
 \begin{align*}
-M_{\rm vac}(F,N) 
-&\cong V_Q \oplus V_Q^*\Sslash SL(N) \\
-&= \Hom(\CC^F, \CC^N) \oplus \Hom(\CC^N, \CC^F)\Sslash SL(N),
+M_{\rm vac}(\cT_{\sfE}(F,N)) 
+&\cong V_Q \times V_Q^*\Sslash SL(N) \\
+&= \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)\Sslash SL(N),
 \end{align*}
@@
 \[
-M_{\rm vac}(F,N)  \hookrightarrow \Lambda^N \CC^F \times \Lambda^N (\CC^F)^* \times \End(\CC^F)
+M_{\rm vac}(\cT_{\sfE}(F,N))  \hookrightarrow \Lambda^N \CC^F \times \Lambda^N (\CC^F)^* \times \End(\CC^F)
 \]
@@
 \[
-M_{\rm vac}(F,N) \hookrightarrow \widehat{{\rm Gr}(F, N)} \times \widehat{{\rm Gr}(F, N)} \times {\rm R}(F,N)
+M_{\rm vac}(\cT_{\sfE}(F,N)) \hookrightarrow \widehat{{\rm Gr}(F, N)} \times \widehat{{\rm Gr}(F, N)} \times {\rm R}(F,N)
 \]
@@
 but ${\rm R}(F,N)$ is not isomorphic to ${\rm R}(F,\check{N})$ except when $N = \check{N}$.
-Hence one should not be optimistic that $M_{\rm vac}(F,N) \cong M_{\rm vac}(F,\check{N})$.
+Hence one should not be optimistic that $M_{\rm vac}(\cT_{\sfE}(F,N)) \cong M_{\rm vac}(\cT_{\sfE}(F,N))$.
 To ``fix'' this issue, one might try to slightly modify the dual side, which Seiberg did by adding the meson fields.
@@
 \begin{prop}
-Seiberg dual theories have isomorphic moduli spaces.
+Seiberg dual theories have isomorphic moduli spaces:
+\[
+M_{\rm vac}(\cT_{\sfE}(F,N)) \cong M_{\rm vac}(\cT_{\sfM}(F,\check{N})).
+\]
 \end{prop}
@@
 On the other hand, there is an open locus where the moduli stacks are equivalent:
-the semi-stable points of the moduli stacks $\cM_{\rm vac}$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
-This locus determines the GIT quotients and hence explains the isomorphism we saw on the moduli spaces.
+the semi-stable points of each moduli stack $\cM_{\rm vac}(\cT_{\sfE}(F,N))$ and $\cM_{\rm vac}(\cT_{\sfM}(F,\check{N}))$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
+This locus agrees with a dense open subset of the GIT quotient, 
+and the isomorphism of the moduli spaces determines an isomorphism between the stable locus of each stack.
 Let us try to unravel what this equivalence means for the field theories, both classical and quantum.
 
-Consider any semistable point $x$.
+Consider any semistable point $x$ in $\cM_{\rm vac}(\cT)$ for some holomorphic QCD theory.
 We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
 For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the formal neighborhood of $x$ inside the moduli stack of vacua. 
-The isomorphism of moduli spaces ensures that there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$,
+We can assemble these perturbative theories into a curved curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}$.
+
+\begin{prop}
+The semistable locus $\cM_{\rm vac}^{ss}(\cT)$ of the the moduli stack $\cM_{\rm vac}(\cT)$ parametrizes a family of holomorphic field theories on $\CC^2$, 
+and this family is isomorphic to the curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}(\cT)$.
+\end{prop}
+
+The isomorphism of moduli spaces then ensures that there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$,
 because there is an explicit identification of the formal neighborhood of $x$ with the formal neighborhood of $x_D$. 
@@
 \begin{prop}
-The isomorphism between the semi-stable locus of the two moduli stacks determines an isomorphism between quantizations over those loci.
+The semistable locus $\cM_{\rm vac}^{ss}$ of the the moduli stack $\cM_{\rm vac}$ parametrizes a family of holomorphic field theories on $\CC^2$, 
+and this family is isomorphic to the curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}$.
+
+The isomorphism between the semistable loci of the two moduli stacks determines an isomorphism between quantizations over those loci.
 \end{prop}
@@
 \begin{dfn}
-For a holomorphic QCD theory let $\cM^q_{\rm vac}(F,N)$ denote the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf of factorization algebras on $\CC^2$.
+For a holomorphic QCD theory let $\cM^q_{\rm vac}(F,N)$ denote the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf with values in factorization algebras on $\CC^2$.
 The value at a solution $x$ is a quantization of the observables for the classical perturbative theory labeled by~$x$.
-(One could focus, for simplicity, on the sheaf of polydiscs algebras.)
+(One could focus, for simplicity, on the sheaf with values in polydiscs algebras.)
 
@@
 
-*********** Discuss enhanced spacetime symmetries ****************
+\subsubsection{Enhanced spacetime symmetries}
 

### 2022-11-17 draft.tex
tightened up the final conjecture

@@
 On the other hand, there is an open locus where the moduli stacks are equivalent:
-the semi-stable points of each moduli stack $\cM_{\rm vac}(\cT_{\sfE}(F,N))$ and $\cM_{\rm vac}(\cT_{\sfM}(F,\check{N}))$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
-This locus agrees with a dense open subset of the GIT quotient, 
+take the points of each moduli stack $\cM_{\rm vac}(\cT_{\sfE}(F,N))$ and $\cM_{\rm vac}(\cT_{\sfM}(F,\check{N}))$ where the stabilizer is a finite group,
+in other words, the stable locus.
+We use $\cM_{\rm vac}(\cT)^s$ to denote this open locus in the moduli stack of a theory~$\cT$.
+This locus agrees with a dense open subset of the affinization (or GIT quotient), 
 and the isomorphism of the moduli spaces determines an isomorphism between the stable locus of each stack.
@@
 
-Consider any semistable point $x$ in $\cM_{\rm vac}(\cT)$ for some holomorphic QCD theory.
+Consider any stable point $x$ in $\cM_{\rm vac}(\cT)$ for some holomorphic QCD theory.
 We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
 For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the formal neighborhood of $x$ inside the moduli stack of vacua. 
-We can assemble these perturbative theories into a curved curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}$.
+(This argument is a version of the Higgs mechanism, as phrased using the BV formalism.
+See \cite{EG} for an expository account.)
+We can assemble these perturbative theories into a holomorphic $\sigma$-model from $\CC^2$ into~$\cM_{\rm vac}^{s}$,
+using the methods of~\cite{GGW, WilThesis}.
 
 \begin{prop}
-The semistable locus $\cM_{\rm vac}^{ss}(\cT)$ of the the moduli stack $\cM_{\rm vac}(\cT)$ parametrizes a family of holomorphic field theories on $\CC^2$, 
-and this family is isomorphic to the curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}(\cT)$.
+For each holomorphic QCD theory $\cT$, 
+the stable locus $\cM_{\rm vac}(\cT)^s$ of its moduli stack parametrizes a family of holomorphic field theories on $\CC^2$, 
+and this family is isomorphic to the holomorphic $\sigma$-model from $\CC^2$ into~$\cM_{\rm vac}(\cT)^s$.
 \end{prop}
+
+\owen{Is that true?}
+
+This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in \owen{reference section of this paper}.
 
@@
 Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
-Hence on the semistable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.
+Hence on the stable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.
 
 \begin{prop}
-The semistable locus $\cM_{\rm vac}^{ss}$ of the the moduli stack $\cM_{\rm vac}$ parametrizes a family of holomorphic field theories on $\CC^2$, 
-and this family is isomorphic to the curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}$.
-
-The isomorphism between the semistable loci of the two moduli stacks determines an isomorphism between quantizations over those loci.
+There is an isomorphism of these holomorphic $\sigma$-models for the electric theory $\cT_{\sfE}(F,N)$ and the magnetic theory $\cT_{\sfM}(F,\check{N})$, lifting the isomorphism between their moduli spaces.
+
+This isomorphism determines an isomorphism between quantizations of these holomorphic $\sigma$-models, and hence between quantizations of the holomorphic QCD theories over the stable loci.
 \end{prop}
 
-This identification breaks down on the unstable locus, raising the following question:
+In other words, Eager's conjecture is true over the stable loci: there is an isomorphism of sheaves of two-dimensional chiral differential operators.
+
+This identification breaks down on the non-stable locus, raising the following question:
 \begin{quote}
-At the quantum level, what happens on the unstable locus? 
+At the quantum level, what happens on the non-stable locus? 
 \end{quote}
-Each unstable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
-and hence its quantization is more involved that at a semistable point and depends nontrivially the gauge group.
+Each non-stable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
+and hence its quantization is more involved that at a stable point and depends nontrivially the gauge group.
 The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.
@@
 The moduli of classical states are isomorphic.
-We hope that something similar happens at the quantum level.
-In other words, there is a moduli stack of quantum vacua and a moduli space of quantum vacua,
+We hope that something similar happens at the quantum level:
+there is a moduli stack of quantum vacua and a moduli space of quantum vacua,
 and we hope the spaces are isomorphic.
-We sketch the idea as follows.
+We sketch the suggestion as follows.
 
 \begin{dfn}
-For a holomorphic QCD theory let $\cM^q_{\rm vac}(F,N)$ denote the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf with values in factorization algebras on $\CC^2$.
+For a holomorphic QCD theory let the {\em moduli stack of quantum vacua} $\cM^q_{\rm vac}(F,N)$ mean the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf with values in factorization algebras on $\CC^2$.
 The value at a solution $x$ is a quantization of the observables for the classical perturbative theory labeled by~$x$.
 (One could focus, for simplicity, on the sheaf with values in polydiscs algebras.)
-
-Let $M^q_{\rm vac}(F,N)$ denote the global sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
+\end{dfn}
+
+Bear in mind an important feature of this sheaf.
+Working on the stable locus $\cM_{\rm vac}(F,N)^{s}$, 
+we note that the sheaf of classical observables (as a sheaf with values in factorization algebras) has the property that its factorization homology on $\CC^2$ is the sheaf of {\em jets} of functions on $\cM_{\rm vac}(F,N)^{s}$.
+This sheaf has a natural flat connection, sometimes called the Grothendieck connection, and the horizontal sections are the structure sheaf $\cO$ of $\cM_{\rm vac}(F,N)^{s}$.
+In fact, as shown in \cite{GGW, WilThesis}, this flat connection makes sense even at the level of the factorization algebra,
+and not just on factorization homology.
+When we quantize, we wish to lift this flat connection as well.
+
+In fact, we expect that a version of this relationship extends to the whole stack $\cM_{\rm vac}(F,N)$,
+by using the methods of \cite{CPTVV}.
+In formulating the definition above, we are assuming that expectation holds.
+
+We now posit the following.
+
+\begin{dfn}
+Let {\em moduli space of quantum vacua} $M^q_{\rm vac}(F,N)$ mean the global horizontal sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
 It is a factorization algebra on~$\CC^2$.
@@
 
+\begin{rmk}
 We note that in the physics literature, there are a number of issues that are relevant in this setting.
@@
 It is interesting to wonder how these would appear in the holomorphic setting.
+\end{rmk}
 

### 2022-11-17 draft.tex
odds and ends

@@
 
-\owen{Much of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}
-
-\owen{We can cut this sharply now.
-My main concerns are (1) to mention working on arbitrary complex manifolds and not just $\CC^d$, (2) to mention Beilinson-Drinfeld's approach, and (3) to explain chiralization/reduction for $d > 1$.}
+\owen{Some of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}
+
+\owen{My main concerns are (1) to mention working on arbitrary complex manifolds and not just $\CC^d$, (2) to mention Beilinson-Drinfeld's approach, and (3) to explain chiralization/reduction for $d > 1$.}
 
@@
 
+\begin{rmk}
+The reader fond of higher abstract nonsense will note that we could have factorization algebras take values in other target categories (better, $\infty$-categories),
+not just vector spaces or cochain complexes.
+For instance, one might assign an $\infty$-category to each open set.
+This generalization is fruitful.
+In the Beilinson-Drinfeld style, it leads to chiral categories, which play an increasingly central role in the geometric Langlands program.
+In the style advocated above, it would likewise be useful for capturing notions like defects or extended operators from quantum field theory.
+\end{rmk}
+
 %\subsection{Prefactorization algebras as algebras over an operad}
@@
 
+\owen{Somewhere we should mention Henriques' work connecting factorization algebras with conformal nets,
+Daniel Bruegmann's thesis, and how the web of 2d CFT stuff should fit together.}
+
 \subsection{Toric (KK) reduction vs. chiralization}
@@
 The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
-\brian{got rid of the term `shifted' section. Also, to write theory like this we use a CY structure, which I've now fixed.e}
+(Note that $T^*[1]BG_{\CC}$ is the coadjoint quotient stack $[\fg_\CC^*/G_{\CC}]$.)
 
@@
 A twisted matter multiplet also defines a field theory on any complex surface $X$. 
-\owen{Is it a cotangent theory? It looks like a twisted cotangent theory.}
-\brian{right, $i_{dW}$ is the `twist'.}
-The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$ \brian{How do you feel about the notation $\RR \text{Crit}(W)$?}, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
+The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
 (It is the Koszul complex associated to the Jacobi ring of $W$.)
@@
 
-Since $W$ is $G_\CC$-invariant, the critical locus has a residual Hamiltonian $G_\CC$-action. 
-There is a version of Hamiltonian reduction for odd symplectic manifolds \cite{Pavel, Kevin, who else},
-which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
-\owen{I'm not sure we even need this.} \brian{Probably if we want to cite a model for it, I think its fine to list the references here though.}
-\owen{Part of my concern is that Hamiltonian reduction is a version of GIT, and hence it is {\em not} stacky. The stack quotient seems more appropriate to me.}
-%As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
 The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
 \[
-{\rm Map}(X , {\rm Crit}^d(W) \Sslash G_\CC), 
-\]
-which comes equipped with an odd symplectic structure. 
-\owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}
-\brian{That's already in this hamiltonian reduction. 
-If $V$ is $(-1)$ shifted symplectic then I think the tangent space of $V \Sslash G$ should be
-\beqn
-\lie{g}[1] \oplus V \oplus \lie{g}^*[-2] .
-\eeqn
-Since we're forgetting to $\ZZ/2$ this is just $\Pi \lie{g} \oplus (V \oplus \lie{g})$.
-}
+{\rm Map}(X , \left( \fg_\CC^*\times {\rm Crit}^d(W) \right)/ G_\CC), 
+\]
+where the target is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.
 
@@
 so $\underline{N} = \CC^N$ with its natural left action.
-\owen{That's kind of crappy notation. Let's discuss.}
 
@@
 where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.}
-\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
 %We will denote this theory by $\cT(N,F)$.

### 2022-11-23 draft.tex
small edits in SD section
merge draft

--- 2022-11-16 draft.tex
@@
 The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
-\brian{got rid of the term `shifted' section. Also, to write theory like this we use a CY structure, which I've now fixed.e}
 
@@
 A twisted matter multiplet also defines a field theory on any complex surface $X$. 
-\owen{Is it a cotangent theory? It looks like a twisted cotangent theory.}
-\brian{right, $i_{dW}$ is the `twist'.}
-The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$ \brian{How do you feel about the notation $\RR \text{Crit}(W)$?}, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
-(It is the Koszul complex associated to the Jacobi ring of $W$.)
+The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on the vector space $V$ equipped with the differential~$\iota_{\d W}$.
+(This is the Koszul complex associated to the Jacobi ring of $W$.)
 This description makes manifest an odd symplectic structure on ${\rm Crit}^d(W)$,
@@
 \owen{That's kind of crappy notation. Let's discuss.}
+\brian{Does it help us much? Or are you trying to use this to disambiguate what $\CC^N$ means.}
 
@@
 provided their quantizations, and began analyzing their factorization algebras.
-Following Eager, one might can ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
-\owen{This should be rephrased, and we should mention more people, like Philsang and Surya. We can mention pre-S-duality things (like our work and the EY stuff) and S-duality stuff.}
+One might can also ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
+The answer to this question has been studied by Surya Raghavendran and Philsang Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}.
+A further localization of $S$-duality has also been studied by Costello and Gaiotto \cite{CGholography}.
 
@@
 Our discussion here is ahistorical.
-Witten initiated this vein of research for topological twists \cite{},
-and Costello advocated it for holomorphic twists, particularly in the setting of holography \cite{}.
+Witten initiated this vein of research for twists which are topological \cite{WittenTwist},
+and Costello advocated holomorphic twists \cite{CostelloHol}.  
+Costello and Li initiated the use of holomorphic twists to study dualities particularly in the setting of the topological B-model \cite{CLbcov1,CLbcov2,CLbcov3}, and further extended this to non-topological strings \cite{CLsugra}.
 Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
-\owen{Add a remark (?) about Kevin and Si's work on twisted holography and other related directions.}
+These ideas are extensively used in the program of twisted holography \brian{this is a rabbit hole, not sure how many people to mention.}
 \end{rmk}
@@
 
-As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{BW work}.
+As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{Whol}.
 There are then two further pieces of evidence when these quantum theories are examined:
@@
 the coadjoint quotient stack of the group.
+\brian{The paragraph began with holomorphic theories, do you want to say twist of 4d N=1?}
 (We are working in a $\ZZ/2$-graded world here.)

### 2022-11-23 draft.tex

--- 2022-11-17 draft.tex
@@
 so $\underline{N} = \CC^N$ with its natural left action.
+\owen{That's kind of crappy notation. Let's discuss.}
+\brian{Does it help us much? Or are you trying to use this to disambiguate what $\CC^N$ means.}
 
@@
 using the methods of~\cite{GGW, WilThesis}.
+This emergence of a $\sigma$-model is reminiscent of chiral symmetry breaking.
 
@@
 This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in \owen{reference section of this paper}.
+\owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}
 

### 2022-11-29 draft.tex
su(2)

@@
 \def\Spec{\text{Spec}}
+\def\C{{\mathbb{C}}}
 
@@
 
-There will be two theories. 
+There will be two holomorphic theories on $\CC^2$. 
 We call one side {\em electric} and the other {\em magnetic}.
+These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, which justifies our terminology.
 
@@
 Fix a positive integer $F$, for flavor, and fix integers $N$ and $\check{N}$ such that $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
-
+\begin{itemize}
+\item
 The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors and {\em without} mesons.
@@
 We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
-
-The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
+\item
+The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ which take values in $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
 (and $\check{\nu}$ for the partner field to $\check{\mu}$).
@@
 where we compose the linear maps before tracing over~$V_{\check{N}}$.
-\owen{Please double-check that formula.}
+\end{itemize}
 \end{dfn}
@@
 
+\subsubsection{The duality functor}
+
+There is a way to define the dual of any supersymmetric QCD theory with mesons that satisfies the following properties:
+\begin{itemize}
+\item In the case that there are no mesons in the original theory, like in the electric theory, the dual agrees with the magnetic theory.
+\item The dual of the magnetic theory is equivalent to the original electric theory.
+In other words, the double dual of the electric theory is equivalent to itself. 
+\end{itemize}
+%In fact, more generally, the double dual of any supersymmetric QCD with mesons returns the same theory (up to equivalence). 
+Let us briefly remark how this general duality looks classically in the holomorphic context.
+
+Suppose that we have a holomorphic QCD theory with $N$ colors, $F$ flavors, and with mesons $\mu$ valued in some vector space $V_M$. 
+The superpotential is $W(QQ^\dagger, \mu)$.
+The dual theory is again a holomorphic QCD theory with mesons.
+Precisely the dual theory is holomorphic QCD with $F-N$ colors, $F$ flavors, and mesons valued in 
+\beqn
+(\mu, \til \mu) \in V_M \oplus \C^{F^2} .
+\eeqn
+The superpotential of this dual holomorphic QCD theory (whose quarks we label by $\til Q$) is 
+\beqn
+\til W (\mu, \til \mu, \til Q) = W|_{\til \mu = Q Q^\dagger}(\mu, \til \mu) + \Tr \til{Q}^\dagger \til{\mu} \til{Q} .
+\eeqn
+Notice that when $V_M = 0, W=0$ this agrees with the dual magnetic theory that we introduced above.
+
+Now, let's suppose we start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
+The superpotential is $W = \Tr \check{Q}^\dagger \check{\mu} \check{Q}$. 
+Taking the dual of this theory we obtain holomorphic QCD with $N$ colors and $F$ flavors as expected.
+However, we have mesons $\check{\mu}$ and $\til \mu$ both valued in $\End(\C^F)$. 
+The superpotential is simply
+\beqn
+\til W = \Tr \check \mu \til \mu + \Tr \til Q^\dagger \check{\mu} \til Q .
+\eeqn
+The first term arises from substituting $\til \mu = \check Q \check Q^\dagger$ in the original magnetic superpotential. 
+This term has the effect of making both $\mu,\check \mu$ massive, and hence they can be integrated out to obtain the original electric theory. 
+(In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)
+
 \subsection{Evidence for holomorphic Seiberg duality}
@@
 and these can be matched under the duality. 
-For the classical holomorphic theories, these symmetries enhance to an action of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
+For the classical holomorphic theories, these symmetries enhance to an action of infinite-dimensional algebra of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
 Under quantization, these have isomorphic anomalies.
@@
 \beqn\label{eqn:electricflavor}
- \frac{N}{16} \int \op{tr}_{\underline{F}} \left(\sfa \, \partial \sfa \, \partial \sfa\right) 
-\eeqn
-where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.
+ \frac{N}{16 \pi^2} \int \op{tr}_{\underline{F}} \left(\sfa \, \partial \sfa \, \partial \sfa\right) 
+\eeqn
+where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.\footnote{The overall analytic coefficient can be explicitly determined, see \cite{GWkm} for related computations.}
 
@@
 \[
- \frac{\check{N}}{16} \int \op{tr}_{\underline{F}^*} \left(\sfa \, \partial \sfa \, \partial \sfa\right) .
+ \frac{\check{N}}{16 \pi^2} \int \op{tr}_{\underline{F}^*} \left(\sfa \, \partial \sfa \, \partial \sfa\right) .
 \]
@@
 \[
-\frac{F}{16}\int \op{tr}_{\underline{F}} \left(\sfa\, \partial \sfa \, \partial \sfa\right).
+\frac{F}{16\pi^2}\int \op{tr}_{\underline{F}} \left(\sfa\, \partial \sfa \, \partial \sfa\right).
 \]
@@
 
+\subsubsection{$SU(2)$ SQCD}
+
+Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
+In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
+\beqn
+(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
+\eeqn
+This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.
+
+On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
+\beqn
+V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
+\eeqn
+There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
+Again the flavor symmetry group admits an enhancement to $SU(2F)$.
+
+Let's further consider some special cases for small values of flavors.
+
+$\bullet \ul{F=2}$. \brian{I'm confused}
+
+$\bullet \ul{F=3}$. 
+In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
+\beqn
+(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
+\eeqn
+In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
+If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
+\beqn
+W = \frac16 \Phi \wedge \Phi \wedge \Phi .
+\eeqn
+We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
+The critical locus of $W$ is simply the space of solutions to the equation
+\beqn
+\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
+\eeqn
+This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
+
+$\bullet \ul{F=4}$.
+This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
+On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
+On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
+
+We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
+For $F \geq 4$ the
+
 \subsection{A relation to Hori-Tong duality}
+
+A duality
+
+The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
+The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
+For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
 

### 2022-12-01 draft.tex
tiny tweaks in a quick read

@@
 This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
-It might be seen as parametrizing ``states'' rather than solutions, 
-as it is defined via functions on the solutions (see Remark~\ref{sols vs states} for more).
+This affinization might be seen as parametrizing ``states'' rather than solutions, 
+as it is defined via functions on the solutions (see Remark~\ref{sols vs states} for more on this aspect).
+
 We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
-(Note that the font of M changes between stack and space.)
+Note that the font of M changes between stack and space.
 
 \begin{rmk}
-In practice physicists work ordinary schemes (i.e., without any derived directions), 
+In practice physicists work with ordinary schemes (i.e., without any derived directions), 
 although one can also study the derived affine scheme that is the best approximation to a derived stack.
-Below we will always provide an ordinary scheme as the moduli {\em space}.
+Below we will always provide an ordinary scheme as the moduli {\em space},
+following the physicists.
 \end{rmk}
@@
 It is familiar to geometers that this affinization forgets interesting information about the stack because an invariant function must be constant on the closure of any orbit.
-Thus, the canonical map
+The canonical map
 \[
@@
 which says $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
-(The rightmost algebra is symmetric polynomials.)
+(The rightmost algebra is symmetric polynomials in the eigenvalues.)
 The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
@@
 where ${\rm Gr}(F, N)$ denotes the Grassmannian of $N$-planes in $\CC^F$ and the hat indicates we take the affine cone with respect to this standard Pl\"ucker embedding.
+
 For the full problem, we have both quarks and antiquarks, so
@@
 
-Note that $\check{N} = F-N$, so $\widehat{{\rm Gr}(F, N)} \cong \widehat{{\rm Gr}(F, \check{N})}$,
-but ${\rm R}(F,N)$ is not isomorphic to ${\rm R}(F,\check{N})$ except when $N = \check{N}$.
+Note that $\check{N} = F-N$, so ${\rm Gr}(F, N) \cong {\rm Gr}(F, \check{N})$ and a (partial) duality is apparent.
+On the other hand, ${\rm R}(F,N)$ is not isomorphic to ${\rm R}(F,\check{N})$ except when $N = \check{N}$.
 Hence one should not be optimistic that $M_{\rm vac}(\cT_{\sfE}(F,N)) \cong M_{\rm vac}(\cT_{\sfE}(F,N))$.
@@
 In the literature this isomorphism is given by explicitly matching gauge-invariant functions, 
-which are often called mesons or baryons, 
+which physics paper often call mesons or baryons, 
 as they can be identified with the data that identifies such particles.
@@
 
-\subsubsection{$SU(2)$ SQCD}
+\subsubsection{The special case of $SU(2)$ SQCD}
 

### 2022-12-02 draft.tex
weak version

@@
 
-\subsection{A relation to Hori-Tong duality}
-
-A duality
-
-The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
-The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
-For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
+\subsection{Two-dimensional TFTs by compactification}
 
@@
 \begin{lem}
-For a holomorphic QCD theory, this compactification is a Landau-Ginzburg B-model for \owen{finish! would it be easier just to spell out what happens to matter, gauge, and the QCD?}
+For a holomorphic QCD theory $\cT(F,N)$, this compactification is a Landau-Ginzburg B-model~$\cT(F,N)_2$.
+\owen{Not sure what's the best way to characterize which one we get.}
 \end{lem}
@@
 \begin{conj}
-\owen{Unpack in some detail.}
+There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
+the compactifications of the electric and magnetic holomorphic QCD theories.
 \end{conj}
 
-This conjecture is essentially due to Hori and Tong. \owen{Add some history, cite some references.}
+This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
+(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
+We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
+
+%A duality 
+%
+%The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
+%The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
+%For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
 

### 2022-12-06 draft.tex
b model

@@
 We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
-The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
+The superpotential is 
+\beqn\label{eqn:checkW}
+\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q})
+\eeqn
 where we compose the linear maps before tracing over~$V_{\check{N}}$.
@@
 
-A beautiful maneuver used in physics is compactification:
-given a field theory $\cT$ in $n$ dimensions, one takes an $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+A standard maneuver used in physics is compactification:
+given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
 A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
-We have already worked with a factorization algebra version of these maneuvers: 
-pushing forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
-For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
-We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.
-
-\begin{lem}
-For a holomorphic QCD theory $\cT(F,N)$, this compactification is a Landau-Ginzburg B-model~$\cT(F,N)_2$.
-\owen{Not sure what's the best way to characterize which one we get.}
-\end{lem}
+
+We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
+In other words, this is the $T^2$ compactification of the holomorphic theory.
+For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
+We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.
+
+Let's first consider the electric side which breaks up into holomorphic BF theory coupled to a complex two-dimensional $\beta\gamma$ system.
+The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
+This is the space whose algebra of functions is $\cO(\C^{NF}) ((z))((w))$ where $z,w$ are formal loop parameters which we imagine as describing the winding of the two circles we have compactified. 
+The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
+Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is $B GL(N)$).
+In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
+As a derived mapping space, this model is given by
+\beqn
+{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
+\eeqn
+The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack $\C^{NF} / GL(N)$.
+
+On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
+What results is a Landau--Ginzburg B-model whose target is the stack
+\beqn
+\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
+\eeqn
+The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
+The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in \eqref{eqn:checkW}.
 
@@
 \begin{conj}
-There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
-the compactifications of the electric and magnetic holomorphic QCD theories.
+There is an equivalence of $E_2$ algebras between:
+\begin{itemize} 
+\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$.
+\item (magnetic) the $E_2$ algebra which results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
+\end{itemize}
 \end{conj}
+
+%\begin{conj}
+%There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
+%the compactifications of the electric and magnetic holomorphic QCD theories.
+%\end{conj}
 

### 2022-12-13 draft.tex
sl3

@@
 initially conjectured by Richard Eager.
+We will point out an enrichment of this conjecture which accounts for a large symmetry enhancement that both sides of the theory enjoy after performing the holomorphic twist.
 We explain our first efforts in this direction and how it offers evidence for the conjecture;
@@
 
-\subsubsection{Flavor symmetries}
+\subsubsection{Flavor symmetry enhancement}
 
@@
 
-For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(F))$, 
-which we call a $2$-dimensional holomorphic current algebra.
+For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(F))$.
 It acts by wedging the forms and applying $\sl(F)$ to the relevant vector space, such as~$\Hom(\CC^F,\CC^N)$.
-On local observables, the $S^3$-mode algebra $\lie{sl}(F) \otimes \sfA_2$ (which is the algebraic version of $\sl(F) \otimes \Omega^{0,\bu}(\CC^2 - 0)$) acts at the classical level.
+On affine space, this dg Lie algebra is quasi-isomorphic to $\lie{sl}(F) \otimes \cO(\C^2)$, where $\cO(\C^2)$ denotes holomorphic functions on $\C^2$---this is like a current algebra in two complex dimensions.
+
+There is another dg Lie algebra obtained by evaluating the theory on punctured affine space $\C^2 - 0$.
+We recalled in \S \ref{sec:punctured} an algebraic model $\sfA_2$ for the dg algebra $\Omega^{0,\bu}(\C^2 - 0)$.
+The dg Lie algebra we assign to the punctured affine space, classically, is $\lie{sl}(F) \otimes \sfA_2$.
+Recall that we can think about elements of this algebra as being supported on three-spheres $S^3$ inside $\C^2 - 0$.
+This $S^3$-mode algebra acts on the local observables at the classical level.
 
@@
 and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
-(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - 0$.)
+(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(F)}_{2,\theta_{\sfE}}, \Hat{\sl(F)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - 0$.)
 
@@
 
-In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories flow to the same superconformal fixed point in the infrared limit. 
+A superconformal algebra is a simple super Lie algebra which contains both the ordinary algebra of infinitesimal conformal transformations and the super Lie algebra of supertranslations.
+It is a basic fact of life that all (super)conformal algebras in dimensions $\geq 3$ are finite-dimensional.
+Being a superconformal theory means that the theory admits a symmetry by a particular superconformal algebra---it is, generally speaking, a very rigid condition on a theory.
+
+The (complexified) $\cN=1$ superconformal in four-dimensions is $\sl(4|1)$.
+This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
+%The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
+Inside of this algebra is the Cartan generator $\Delta$ of which is an infinitesimal generator for scaling transformations in~$\RR^4$.
+
+Fix the same square-zero supercharge $\cQ$ inside of the four-dimensional $\cN=1$ supersymmetry algebra which we use to define the holomorphic twists of Seiberg dual gauge theories. 
+Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
+There is a quasi-isomorphism of dg Lie algebras
+\[
+\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) ,
+\]
+see \cite{SWsuco}, for example.
+So, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ is guaranteed to act on the holomorphically twisted theory. 
+In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
+The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
+where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an $SL(3)$-homogenous space.
+(In a moment we will discuss how all holomorphic vector fields act on the theories.)
+Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator 
+\beqn
+\Delta^{hol} = z_1 \del_{z_1} + z_2 \del_{z_2},
+\eeqn 
+which is simply the holomorphic Euler vector field.  
+We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
+
+Let's consider just a free theory consisting of a single chiral multiplet, for the moment.
+Here, the $R$-symmetry group is $U(1)$.
+The holomorphic supercharges breaks the $SO(4;\C)$ symmetry down to the group $MU(2)$ which is a double cover of $U(2)$.
+To perform the twist of a theory there are always two steps: the first is to `twist' the fields of the theory using the $R$-symmetry and the second is to deform the action by the supercharge $\cQ$.
+To have a consistent data to twist, one usually imposes the condition that with respect to the twisted $R$-symmetry action the supercharge $Q$ is invariant.
+The odd part of the four-dimensional $\cN = 1$ algebra is given by 
+\beqn
+S_+ \otimes W \oplus S_- \otimes W^*
+\eeqn
+where $W \cong \C$ is just a one-dimensional vector space and $S_{\pm}$ are the positive and negative semi-chiral spin representations of $\lie{so}(4;\C)$.
+We will take the square-zero supercharge to live in $\cQ \in S_+ \otimes W$.
+As an $MU(2)$ representation one has $S_+ \cong \det(L)^{+1/2} \oplus \det(L)^{-1/2}$.
+Thus, if $\cQ$ lies in the first summand, in order to make $\cQ$-invariant we must twist by the condition that $W$ has weight $-1/2$ under the $R$-symmetry.
+We will fix this twisting data.
+
+The basic components of the chiral multiplet is a pair of bosons $(\phi,\Bar{\phi})$, and a pair of fermions $(\psi_+, ,\psi_-)$ where $\psi_{+}$ takes values in $S_+$ and $\psi_-$ takes values in $S_-$.
+For a free theory, we may assign any $R$-charge to $\psi_+$ and this determines the $R$-charges of all remaining fields. 
+For example, if the $R$-charge of $\psi_+$ is $r$ then the $R$-charge of $\phi$ is $r+1$, the $R$-charge of $\psi_-$ is $-r$, and the $R$-charge of $\Bar{\phi}$ is $-r - 1$.
+
+If we twist using the data where $\cQ$ is invariant, then the particular choice of $r$ will dictate how the holomorphic scaling operator $\Delta^{hol}$ acts on the theory.
+One finds that the holomorphic twist of the free chiral theory (which is just a single quark in the above terminology) has fundamental field
+\[
+Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2}) 
+\] 
+where $K$ denotes the holomorphic canonical bundle.
+Of course, the canonical bundle on $\C^2$ is trivializable, so we obtain a theory with isomorphic space of fields for any choice of $r$; what changes is how the twisted superconformal symmetry algebra $\lie{sl}(3)$ acts.
+
+Now, let's consider the electric theory.
+We assume that the $R$-charges of the fermions in the quarks and anti-quark multiplets is the same.
+If this $R$-charge is $r$ then the twisted quarks and anti-quarks take the form
+\[
+Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q),\quad Q^\dagger \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q^*)
+\]
+where $V_Q \cong \C^{NF}$.
+In the untwisted theory the value $r$ is fixed by the condition that the $R$-symmetry is anomaly free.
+In the twisted theory, the value of $r$ is fixed by the condition that the action by the holomorphic scaling operator is anomaly free.
+This anomaly comes from a one-loop diagram with a single vertex labeled by $\Delta^{hol}$, and leads to the constraint that
+\beqn
+N + F r = 0 .
+\eeqn
+In other words, $r = - N / F$. 
+This is the exact condition one must require for $R$-symmetry to be anomaly free in the untwisted theory. 
+On the magnetic side the condition becomes $r = N/F - 1$.
+
+In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories are expected to flow to the same superconformal fixed point in the infrared limit. 
 This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
 (Note that it is preserved under swapping $N \leftrightarrow F-N$.)
-Here we will explore how it appears from the point of view of holomorphic QCD.
-
-Consider the (complexified) 4-dimensional $\cN=1$ superconformal algebra $\sl(4|1)$.
-This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
-The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
-Inside of this algebra is the Cartan generator $\Delta$ of scaling transformations in~$\RR^4$.
-
-Fix a nonzero square-zero supercharge $\cQ$. 
-Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
-In \cite{SWsuco} the second author and Saberi show that there is a quasi-isomorphism of dg Lie algebras
-\[
-\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) .
-\]
-Thus, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ will act on the holomorphically twisted theory.  
-In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
-The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
-where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an ${\rm SL}(3)$-homogenous space.
-(In a moment we will discuss how all holomorphic vector fields act on the theories.)
-
-Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator $\Delta^{\rm hol} = \sum_i z_i \partial_{z_i}$, which is simply the holomorphic Euler vector field.  
-We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
-Consider the electric theory. 
-On the gauge fields, $\Delta^{\rm hol}$ acts by the Lie derivative,
-but on matter fields, the action via Lie derivative is {\em not} what one obtains from the untwisted theory.
-Given a quark field $Q = z_1^n z_2^m \otimes v$, 
-one needs
-\[
-\Delta^{hol}(Q) = \left(n + m + \frac23\right) Q 
-\]
-to be compatible with dimension scaling in the untwisted theory.
-What this constraint means is that, as a representation for holomorphic vector fields, 
-the quark fields $Q$, $R$ take values in some interesting holomorphic vector bundle and not in the trivial vector bundle.  
-In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of~\cite{WittenTwist}, 
-one finds that the quark fields are
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes V_Q 
-\] 
-and
-\[ P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes V_Q^*,
-\]
-where $K$ denotes the canonical bundle.
-(The antiquarks ${Q}^\dag$ and~${P}^\dag$ live in a similar twisted bundle.) 
-\owen{Maybe we should discuss what this means for globalization: we need the canonical bundle to have cube roots!}
-
-This action of $\sl(3)$ extends to the quantizations, on both sides of the putative duality, by direct verification.
-In fact it holds for all holomorphic QCD theories, not just those in the superconformal window.
-
-\begin{lem}
-The action of $\sl(3)$ on $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$ extends to their quantizations.
-\end{lem}
-
-In the holomorphic twist as a classical theory,
-this $\sl(3)$-symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.
-In fact, this enhancement also works for all holomorphic QCD theories, not just those in the superconformal window.
-\owen{Am I understanding that correctly?}
-
-\begin{thm}[\cite{SWsuco}] 
-\label{thm:swsuco}
-Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
-This local Lie algebra is a classical symmetry of {\em any} holomorphic QCD theory. 
-\end{thm}
-
-We now ask when this classical symmetry persists at the quantum level, and an interesting anomaly emerges.
-
-\begin{prop}
-For an electric theory $\cT_{\sfE}(F,N)$,
-the symmetry by the local Lie algebra of holomorphic vector fields, described by Theorem~\ref{thm:swsuco}
-has an anomaly to lift to the quantum level. 
-It is proportional to the local functional
-\[
-\frac{F - 3N}{2} \int {\rm div}(X) \op{Tr} (\partial A \, \partial A)  .
-\]
-where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form-valued vector field and $A$ is a gauge field.
-\end{prop}
-
-The first factor ${\rm div}(X)$ denotes the divergence $\sum_i\partial_{z_i} X_i$ of the vector field~$X$.
-We thus deduce the following.
-
-\begin{cor}
-Only when $F = 3N$ do all holomorphic vector fields lift to a symmetry lifts at the quantum level.
-There is, however, a symmetry of {\em divergence-free} holomorphic vector fields at the quantum level for any values of $F$ and~$N$.
-\end{cor}
-
-We will discuss how these enhanced symmetries might intertwine with duality below.
-
-\owen{Should we check that the quantum magnetic theory also has a divergence-free symmetry?}
+It would be interesting to explore how it appears from the point of view of holomorphic QCD.
+
+%
+%This action of $\sl(3)$ extends to the quantizations, on both sides of the putative duality, by direct verification.
+%In fact it holds for all holomorphic QCD theories, not just those in the superconformal window.
+
+%\begin{lem}
+%The action of $\sl(3)$ on $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$ extends to their quantizations.
+%\end{lem}
+%
+%In the holomorphic twist as a classical theory,
+%this $\sl(3)$-symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.
+%In fact, this enhancement also works for all holomorphic QCD theories, not just those in the superconformal window.
+%\owen{Am I understanding that correctly?}
+%
+%\begin{thm}[\cite{SWsuco}] 
+%\label{thm:swsuco}
+%Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
+%This local Lie algebra is a classical symmetry of {\em any} holomorphic QCD theory. 
+%\end{thm}
+%
+%We now ask when this classical symmetry persists at the quantum level, and an interesting anomaly emerges.
+%
+%\begin{prop}
+%For an electric theory $\cT_{\sfE}(F,N)$,
+%the symmetry by the local Lie algebra of holomorphic vector fields, described by Theorem~\ref{thm:swsuco}
+%has an anomaly to lift to the quantum level. 
+%It is proportional to the local functional
+%\[
+%\frac{F - 3N}{2} \int {\rm div}(X) \op{Tr} (\partial A \, \partial A)  .
+%\]
+%where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form-valued vector field and $A$ is a gauge field.
+%\end{prop}
+%
+%The first factor ${\rm div}(X)$ denotes the divergence $\sum_i\partial_{z_i} X_i$ of the vector field~$X$.
+%We thus deduce the following.
+%
+%\begin{cor}
+%Only when $F = 3N$ do all holomorphic vector fields lift to a symmetry lifts at the quantum level.
+%There is, however, a symmetry of {\em divergence-free} holomorphic vector fields at the quantum level for any values of $F$ and~$N$.
+%\end{cor}
+%
+%We will discuss how these enhanced symmetries might intertwine with duality below.
+%
+%\owen{Should we check that the quantum magnetic theory also has a divergence-free symmetry?}
 
@@
 
-\subsection{Two-dimensional TFTs by compactification}
+\subsection{Two-dimensional TFTs by reduction}
 
@@
 \owen{Is that true?}
+\brian{I'm happy with this.}
 
@@
 \owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}
+\brian{that's a great question}
 

### 2022-12-22 draft.tex
getting up to date

--- 2022-12-06 draft.tex
@@
 \begin{cor}
-Only when $F = 3N$ do all holomorphic vector fields lift to a symmetry lifts at the quantum level.
-There is, however, a symmetry of {\em divergence-free} holomorphic vector fields at the quantum level for any values of $F$ and~$N$.
+{\em Divergence-free} holomorphic vector fields are a symmetry at the quantum level for any values of $F$ and~$N$.
+Only when $F = 3N$ do {\em all} holomorphic vector fields lift to a symmetry lifts at the quantum level.
 \end{cor}
@@
 \begin{dfn}
-Let {\em moduli space of quantum vacua} $M^q_{\rm vac}(F,N)$ mean the global horizontal sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
+Let the {\em moduli space of quantum vacua} $M^q_{\rm vac}(F,N)$ mean the global horizontal sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
 It is a factorization algebra on~$\CC^2$.

### 2023-01-16 draft.tex
reworking sd section

--- 2022-12-13 draft.tex
@@
 In particular, consider how symmetries appear in mechanics.
-Let $X$ be a symplectic manifold encoding the ``phase space'' of a classical mechanical system,
+Let $M$ be a symplectic manifold encoding the ``phase space'' of a classical mechanical system,
 and let $\{-,-\}$ denote the Poisson bracket on $C^\infty(X)$.
 If a Lie group $G$ acts on $X$ by symplectomorphisms (i.e., respects the symplectic structure),
-there is a map of Lie algebras $\rho \colon\fg \to {\rm SympVect}(X)$ so that an ``infinitesimal symmetry'' $x \in \fg$ acts by a symplectic vector field.
+there is a map of Lie algebras $\rho \colon\fg \to {\rm SympVect}(M)$ so that an ``infinitesimal symmetry'' $x \in \fg$ acts by a symplectic vector field.
 In many cases, such infinitesimal symmetries are realized as observables: 
-there is a map of Lie algebras $H_\rho \colon \fg \to C^\infty(X)$ such that $\{ H_\rho(x), - \} = \rho(x)$.
-One says that each element $x$ has a Hamiltonian function $H_\rho(x)$ whose associated Hamiltonian vector field is $\rho(X)$.
+there is a map of Lie algebras $H_\rho \colon \fg \to C^\infty(M)$ such that $\{ H_\rho(x), - \} = \rho(x)$.
+One says that each element $x$ has a Hamiltonian function $H_\rho(x)$ whose associated Hamiltonian vector field is $\rho(x)$.
 Classic examples include the momenta for $T^* \RR^n$ arising from translation and rotational symmetry.
@@
 First, note that the free commutative algebra $\Sym(\fg)$ has a canonical Poisson bracket by defining $ \{x, y \}   = [x, y]$ for generators $x, y \in \fg$ and extending by the Leibniz rule.
-Hence the Hamiltonian map $H_\rho$ extends to a Poisson map $H_\rho: \Sym(\fg) \to C^\infty(X)$.
+Hence the Hamiltonian map $H_\rho$ extends to a Poisson map $H_\rho: \Sym(\fg) \to C^\infty(M)$.
 We can then ask: does this map quantize? That is, can we compatibly deform the domain and range of the maps to interesting associative algebras as well as deforming to a map of associative algebras?
 Here it might be useful to recognize that the enveloping algebra $U\fg$ is a natural deformation quantization of $\Sym(\fg)$, thanks to the Poincar\'e-Birkhoff-Witt theorem.
-Thus our question might be reformulated to asking whether there is an associative algebra map $H^q_\rho: U\fg \to C^\infty(X)^q$, where $C^\infty(X)^q$ is a deformation quantization, such that $H^q_\rho$ recovers $H_\rho$ in the classical limit.
+Thus our question might be reformulated to asking whether there is an associative algebra map $H^q_\rho: U\fg \to C_\hbar^\infty(M)$, where $C_\hbar^\infty(X)$ is a deformation quantization, such that $H^q_\rho$ recovers $H_\rho$ in the classical limit.
 Such a map is sometimes called a {\em quantum moment map},
-as $H_\rho$ is the pullback of (polynomial) functions along a moment map~$\mu_\rho \colon X \to \fg^*$.
+as $H_\rho$ is the pullback of (polynomial) functions along a moment map~$\mu_\rho \colon M \to \fg^*$.
 
@@
 and it has played a key role in geometric representation theory and the theory of $D$-modules, where $D$ denotes a ring of differential operators.
-After all, for any manifold $X$, the algebra of differential operators $D_X$ is a natural deformation quantization of functions on $T^* X$.
-Hence, for any $G$-manifold $X$, it is natural to ask whether there is a representation $\fg \to D_X$ deforming the canonical Poisson representation.
+After all, for any manifold $M$, the algebra of differential operators $D_X$ is a natural deformation quantization of functions on $T^* M$.
+Hence, for any $G$-manifold $M$, it is natural to ask whether there is a representation $\fg \to D_M$ deforming the canonical Poisson representation.
 In this spirit, we will search for analogues of the kind of mathematics that has grown out of results by Beilinson-Bernstein \owen{cite}, Kashiwara \owen{cite}, and others.
@@
 
-\subsection{A first step in the holomorphic direction}
+\brian{something about states}
+So far we've recalled how quantization looks like for algebras.
+There is also a quantization for modules.
+Let $L \subset M$ be a Lagrangian submanifold.
+Then, functions $C^\infty(L)$ on $L$ are naturally a module for $C^\infty(M)$.
+The Fock module $F(L)$ associated to $L$ is defined to be the quotient of
+
+\subsection{A loopy version}
 
 What could provide the {\em holomorphic} analog of the story above?
-Let us indicate one possible answer before we motivate it.
-
-\owen{Add pictures!}
-
-Let $V$ be a finite-dimensional complex vector space, equipped with a symplectic pairing $\omega$ that is complex-valued.
-We can view $V$ as $T^* L$ for some Lagrangian vector subspace $L \subset V$, if we wish.
-Then we posit for the relevant phase space, the ``symplectic complex manifold'' $V[z,z^{-1}]$,
-by which we mean the $V$-valued Laurent polynomials in a coordinate~$z$.
-The space encodes algebraic maps from the variety $\CC^\times = \CC \setminus 0$ to $V$,
-so we view it as a kind of algebraic loop space of~$V$.
-(There are clearly variations on this idea, such as the holomorphic loop space of all holomorphic maps from $\CC^\times$ to~$V$.)
-
-Observables for this classical theory then consist of algebraic functions on $V[z,z^{-1}]$, 
-which happens to be a vector space.
-That is, we want to produce a symmetric algebra on the linear dual to this vector space.
-Recall that Laurent series $\CC((z))$ provide a model of the linear dual to Laurent polynomials via the residue pairing: if $p(z) = \sum_{n = -i}^j a_n z^n$ is a Laurent polynomial and $f(z) = \sum_{m = -k}^\infty b_m z^m$ is a Laurent series, then the pairing is
-\[
-(f, p) = \Res_{z=0}(f p) = \sum_{m+n=-1} a_n b_m.
-\]
-Thus $V^* ((z))$, the $V^*$-valued Laurent series, are a linear dual to $V[z,z^{-1}]$ by combining the residue pairing with the evaluation pairing between $V$ and its linear dual~$V^*$.
-The symmetric algebra $\Sym(V^* ((z)))$ thus encodes a class of observables that we will denote $\cO(V[z,z^{-1}])$.
+Let us indicate one possible answer before we motivate it from the point of view of holomorphic field theory.
+Roughly, the idea is that associated to any finite-dimensional symplectic space is another, infinite-dimensional, symplectic space of `loops' into the original symplectic space.
+
+%\owen{Add pictures!}
+
+Let $X$ be an algebraic variety defined over $\CC$, equipped with a symplectic form $\omega_X$.
+Then we posit for the relevant phase space, the ``symplectic space'' $LX$---the formal loop space of $X$.
+This is the space of maps $\Hat{D}^\times \to X$ from the formal punctured disk to $X$.
+%
+%Let $V$ be a finite-dimensional complex vector space, equipped with a symplectic pairing $\omega$ that is complex-valued.
+%We can view $V$ as $T^* L$ for some Lagrangian vector subspace $L \subset V$, if we wish.
+%Then we posit for the relevant phase space, the ``symplectic complex manifold'' $V[z,z^{-1}]$,
+%by which we mean the $V$-valued Laurent polynomials in a coordinate~$z$.
+%The space encodes algebraic maps from the variety $\CC^\times = \CC \setminus 0$ to $V$,
+%so we view it as a kind of algebraic loop space of~$V$.
+(There are clearly variations on this idea, such as the holomorphic loop space of all holomorphic maps from $\CC^\times$ to~$X$, when $X$ is a complex manifold.)
+
+When $X=V$ is a complex vector space equipped with a linear symplectic form $\omega_V$, we can identify $LX$ with the vector space $V((z))$ of $V$-valued Laurent series in a single variable.
+The symplectic form on this vector space is given in terms of the residue
+\beqn
+\omega_{LV} (f,g) = \underset{z=0}{\text{Res}} \, \omega_V(f,g) \d z .
+\eeqn
+One can get rid of the appearance of the holomorphic line element $\d z$ if we `twist' Laurent series by the square-root element $\d z^{1/2}$---in other words, we take sections of the line bundle $K^{1/2}_{D^\times}$.
+%Observables for this classical theory then consist of algebraic functions on $V[z,z^{-1}]$, 
+%which happens to be a vector space.
+%That is, we want to produce a symmetric algebra on the linear dual to this vector space.
+%Recall that Laurent series $\CC((z))$ provide a model of the linear dual to Laurent polynomials via the residue pairing: if $p(z) = \sum_{n = -i}^j a_n z^n$ is a Laurent polynomial and $f(z) = \sum_{m = -k}^\infty b_m z^m$ is a Laurent series, then the pairing is
+%\[
+%(f, p) = \Res_{z=0}(f p) = \sum_{m+n=-1} a_n b_m.
+%\]
+%Thus $V^* ((z))$, the $V^*$-valued Laurent series, are a linear dual to $V[z,z^{-1}]$ by combining the residue pairing with the evaluation pairing between $V$ and its linear dual~$V^*$.
+%The symmetric algebra $\Sym(V^* ((z)))$ thus encodes a class of observables that we will denote $\cO(V[z,z^{-1}])$.
 (Again, there are clearly alternative algebras to consider.)
@@
 
-There is one last feature we would like to point out, before we turn to explaining our interest in this space and algebra.
-The inclusion $\CC^\times \hookrightarrow \CC$ means that any algebraic map  $\phi: \CC \to V$ restricts to an algebraic map $\phi \colon \CC^\times \to V$.
-In our notation, this restriction map is the inclusion $V[z] \hookrightarrow V[z,z^{-1}]$ of $V$-valued polynomials in $V$-valued Laurent polynomials.
-In terms of observables, there is a quotient map $\cO(V[z,z^{-1}]) \to \cO(V[z])$, since observables on the loop space restrict to observables on~$V[z]$.
+There is a feature we would like to point out, before we turn to explaining our interest in this space and algebra.
+The inclusion $\Hat{D}^\times \hookrightarrow \Hat{D}$ means that any algebraic map  $\phi: \Hat{D} \to V$ restricts to an algebraic map $\phi \colon \Hat{D}^\times \to V$.
+In our notation, this restriction map is the inclusion $V[[z]] \hookrightarrow V((z))$ of $V$-valued power series in $V$-valued Laurent series.
+%In terms of observables, there is a quotient map $\cO(V[z,z^{-1}]) \to \cO(V[z])$, since observables on the loop space restrict to observables on~$V[z]$.
 When we quantize, this relationship will produce the underlying vector space (or Fock space, or vacuum module) of the vertex algebra.
@@
 In this model case, we replace the path space ${\rm Map}(\RR, \RR^n)$ by ${\rm Map}(\CC^\times, \CC^n)$ or, if one wishes, ${\rm Map}(S, \CC^n)$ with $S$ a Riemann surface.
-We start with $\CC^\times$ since it has a ``time'' direction given by the radial coordinate ($t$ becomes $r = e^t)$),
-letting us view ${\rm Map}(\CC^\times, \CC^n)$ as  ${\rm Map}(\RR, \Map(S^1,\CC^n))$, namely mechanics into the loop space of $\CC^n$.
+We start with $\CC^\times$ since it has a ``time'' direction given by the radial coordinate ($t$ becomes $r = e^t)$).
+Letting us view $\CC^\times$ as a cylinder $\RR \times S^1$, we can view the mapping space as  ${\rm Map}(\RR, \Map(S^1,\CC^n))$, namely mechanics into the loop space of $\CC^n$.
 We replace Newton's equations of motion with a holomorphic version
@@
 We now turn to quantization, and our phase space will be, for simplicity, the algebraic loop space $V[z,z^{-1}]$ of a symplectic complex vector space $V$.
-Following the case of mechanics, we might ask for a deformation of $\cO(V[z,z^{-1}])$ into an associative algebra.
-A subtlety here is that $\cO(V[z,z^{-1}])$ does not possess a Poisson bracket, 
-due to the  infinite-dimensionality of $V[z,z^{-1}]$.
-The naive formulas from functions on a finite-dimensional symplectic vector space only make sense on a subset of observables here.
-One workaround is to replace $V[z,z^{-1}]$ with $V((z))$, the $V$-valued Laurent series,
-which we view as ``formal loops in $V$.''
-There is manifestly an inclusion $V[z,z^{-1}] \hookrightarrow V((z))$ and hence an algebra map $\cO(V((z))) \to \cO(V[z,z^{-1}])$
-where 
-\[
-\cO(V((z))) = \Sym(V^* [z,z^{-1}]).
-\]
-On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\omega^* \otimes \Res$ on $V^* [z,z^{-1}]$.
-Hence for $\cO(V((z)))$, we can ask for a deformation quantization,
-and there is a nice answer: 
-the Heisenberg commutation relations determine a Weyl algebra $W[V]$ for this formal loop space.
+Following the case of mechanics, we might ask for a deformation of the Poisson algebra
+\beqn
+\cO\left( V((z)) \right) .
+\eeqn
+Like the symplectic form on $V((z))$, the Poisson bracket is given in terms of the residue pairing.
+%into an associative algebra.
+%A subtlety here is that $\cO(V[z,z^{-1}])$ does not possess a Poisson bracket, 
+%due to the  infinite-dimensionality of $V[z,z^{-1}]$.
+%The naive formulas from functions on a finite-dimensional symplectic vector space only make sense on a subset of observables here.
+%One workaround is to replace $V[z,z^{-1}]$ with $V((z))$, the $V$-valued Laurent series,
+%which we view as ``formal loops in $V$.''
+%There is manifestly an inclusion $V[z,z^{-1}] \hookrightarrow V((z))$ and hence an algebra map $\cO(V((z))) \to \cO(V[z,z^{-1}])$
+%where 
+%\[
+%\cO(V((z))) = \Sym(V^* [z,z^{-1}]).
+%\]
+%On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\omega^* \otimes \Res$ on $V^* [z,z^{-1}]$.
+%Hence for $\cO(V((z)))$, we can ask for a deformation quantization,
+%and there is a nice answer: 
+The standard Heisenberg commutation relations determine a Weyl algebra $W[V]$ for this formal loop space.
 As a vector space $W[V]$ is isomorphic to $\cO(V((z)))$, 
-just as the simplest Weyl algebra is isomorphic to $\CC[p,q]$ as a vector space,
+just as the simplest Weyl algebra is isomorphic to $\cO(V)$ as a vector space,
 but the product structure is modified by quantization.
@@
 Suppose now that $G$ is a complex Lie group and it acts on the symplectic complex vector space $V$ by holomorphic symplectomorphisms.
-Then $G$ also acts on the algebraic loop space $V[z,z^{-1}]$ and also on formal loops $V((z))$ as a ``global'' symmetry:
+Then $G$ also acts on the formal loop space $V((z))$ as a ``global'' symmetry:
 the action is independent of $z$.
 On the other hand, if we consider the infinitesimal action $\rho \colon \fg \to {\rm SympVect}(V)$,
-there is, in fact, a natural extension to a ``local'' symmetry $\rho^{\rm loc} \colon \fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
+there is, in fact, a natural extension to a ``local'' symmetry by the ``loop algebra'' 
+\beqn
+\rho^{\rm loc} \colon L \fg = \fg ((z)) \to {\rm SympVect}(V((z))) .
+\eeqn
 Geometrically, a $\fg$-valued function $x(z)$ acts pointwise (with respect to the formal disc) on the formal loop space.
-(Although the algebraic loop space is not symplectic in a strict sense,
-there is still a local symmetry as $\fg[z,z^{-1}]$ maps to vector fields on the algebraic loop space.)
-This action factors through a map $H_\rho^{\rm loc}: \fg[z,z^{-1}] \to \cO(V((z)))$,
+%(Although the algebraic loop space is not symplectic in a strict sense,
+%there is still a local symmetry as $\fg[z,z^{-1}]$ maps to vector fields on the algebraic loop space.)
+This action factors through a map $H_\rho^{\rm loc}: \fg((z)) \to \cO(V((z)))$,
 and hence is Hamiltonian.
-Thus the loop algebra $\fg[z,z^{-1}]$ arises naturally as symmetries of a classical holomorphic field theory.
+Thus the loop algebra $\fg((z))$ arises naturally as symmetries of a classical holomorphic field theory.
 
@@
 \[
-\CC c \to \widehat{\fg} \to \fg[z,z^{-1}]
+\CC K\to \widehat{\fg} \to \fg((z))
 \]
@@
 (To get Riemann surfaces into the game, we will need a richer framework than ordinary algebra.)
-
-\owen{Discuss modules?}
 
@@
 so this seems uninteresting.
-One should notice, however, that punctured affine space $\mathring{\CC}^d = \CC^d -\{0\}$ is, as a scheme, not affine, 
+One should notice, however, that punctured affine space $\mathring{D}^d = \Hat{D}^n -\{0\}$ is, as a scheme, not affine, 
 and so the {\em derived} global sections of the structure sheaf $\cO_{\rm alg}$ are interesting:
 \[
-H^\bu(\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg})) = H^\bu (\mathring{\AA}^d, \cO) 
-= \begin{cases} 
+H^\bu(\RR \Gamma(\mathring{D}^d, \cO)) = \begin{cases} 
 0, & \bu \neq 0, d-1 \\ 
-\CC[z_1,\ldots,z_d], & \bu = 0 \\ 
+\CC[[z_1,\ldots,z_d]], & \bu = 0 \\ 
 \CC[z_1^{-1},\ldots,z_d^{-1}] \frac{1}{z_1 \cdots z_d}, & \bu = d-1 
@@
 \]
-Here $\mathring{\AA}^d$ stands for punctured affine space as a scheme. 
+%Here $\mathring{\AA}^d$ stands for punctured affine space as a scheme. 
 We are providing a natural basis for the cohomology 
 that aims to emphasize analogies with the $d=1$ case.
-When $d=1$, note that this recovers the Laurent polynomials,
+When $d=1$, note that this recovers the Laurent series,
 so when $d > 1$, 
@@
 Checking this computation is a straightforward exercise in algebraic geometry;
-for instance, use the cover by the affine opens of the form $\CC^d - \{z_i =0\}$.
+for instance, use the cover by the affine opens which are the complements of the coordinate hyperplanes $\{z_i =0\}$.
 The full cohomology has the structure of a commutative algebra. 
@@
 
+There is also an algebraic version where we replace the formal disk by the affine space $\AA^d$ and its punctured version $\mathring{\AA}^d$.
 A similar result holds in analytic geometry, of course,
-so that we have a natural map
-\[
-\RR \Gamma(\mathring{\CC}^d, \cO_{\rm alg}) \to \RR \Gamma(\mathring{\CC}^d, \cO_{\rm an}) \simeq \Omega^{0,\bu}(\mathring{\CC}^d).
-\]
-We can also replace punctured affine space $\mathring{\AA}^d$ by the punctured formal disk
-$\mathring{\DD}^d$.
-Here the cohomology is identical to the above formula except in degree zero polynomials are replaced by power series.
+so that we have natural maps
+\[
+\RR \Gamma(\mathring{D}^d, \cO) \leftarrow \RR \Gamma(\mathring{\AA}^d, \cO) \to \RR \Gamma(\mathring{\CC}^d, \cO_{\rm an}) 
+\]
+given by the embedding of polynomials into power series and holomorphic functions, respectively.
 
@@
 \label{eq:res}
-\Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d z_1 \wedge \cdots \wedge \d z_d.
-\eeqn
+\Res(\alpha) = \oint_{S^{2d-1}} \alpha \wedge \d^d z,
+\eeqn
+under the above embeddings.
+Here $\d^d z = \d z_1 \wedge \cdots \wedge \d z_d$ is the standard holomorphic volume form.
 \end{itemize}
@@
 We must be careful about parity, however. 
-In dimension $d = 1$, the Laurent polynomials valued in a symplectic vector space $V[z,z^{-1}]$ again has the structure of a symplectic vector space via the residue. 
+In dimension $d = 1$, the Laurent polynomials valued in a symplectic vector space $V((z))$ again has the structure of a symplectic vector space via the residue. 
 Because of the appearance of the cohomological shift in the higher dimensional residue it is no longer the case that 
 \beqn
-V \otimes \RR\Gamma(\mathring{\DD}^d, \cO) \simeq V \otimes \sfA_d
+V \otimes \RR\Gamma(\mathring{D}^d, \cO) \simeq V \otimes \sfA_d
 \eeqn
@@
 Thus, to get a symplectic pairing on $V \otimes \sfA_d$ via the residue we can ask that $V$ is equipped with a {\em $(d-1)$-shifted symplectic structure}. 
-A typical example of such a space is $V = \T^*[d-1] L = L \oplus L^*[d-1]$, where $L$ is any vector space.
+A typical example of such a space is $V = T^*[d-1] L = L \oplus L^*[d-1]$, where $L$ is any vector space.
+\footnote{In the generality of shifted symplectic geometry, we expect that the derived mapping space $\text{Map}(\mathring{D}^n, X)$ is symplectic provided that $X$ is a $(d-1)$-shifted symplectic space.}
 
@@
 \label{eqn:omega}
-\omega(a,b) = \Res ( \til \omega_V (a,b) ) .
+\omega(a,b) = \Res ( \til \omega_V (a,b) \wedge \d^d z) .
 \eeqn
@@
 
-There is a close relationship of the higher dimensional Weyl algebra to the higher dimensional $\beta\gamma$ system on $\CC^d - 0$ just as the loopy Weyl algebra is related to the $\beta\gamma$ system on $\CC^\times$.
+There is a close relationship of the higher dimensional Weyl algebra to the higher dimensional $\beta\gamma$ system on $\CC^d - 0$ just as the loopy Weyl algebra is related to the $\beta\gamma$ system on~$\CC^\times$.
 
@@
 \begin{array}{cccc}
-\theta_{\rm FHK} : & (A_d \tensor \fg)^{\tensor (d+1)} & \to & \CC\\ 
+\theta_{\rm FHK} : & (\sfA_d \tensor \fg)^{\tensor (d+1)} & \to & \CC\\ 
 & a_0 \otimes \cdots \otimes a_d & \mapsto & \Res \left(\theta(a_0,\partial a_1,\ldots,\partial a_d)\right)
@@
 notably in studying the derived moduli of $G$-bundles on a complex varieties of dimension~$d$.
-\owen{Other applications?}
 
@@
 Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
-These ideas are extensively used in the program of twisted holography \brian{this is a rabbit hole, not sure how many people to mention.}
+These ideas are extensively used in the program of twisted holography, which is growing rapidly at the moment.
+(The interested reader might track the papers that cite those we have mentioned.)
 \end{rmk}
@@
 \item In the case that there are no mesons in the original theory, like in the electric theory, the dual agrees with the magnetic theory.
-\item The dual of the magnetic theory is equivalent to the original electric theory.
-In other words, the double dual of the electric theory is equivalent to itself. 
+\item The dual of the magnetic theory is equivalent to the original electric theory. In other words, the double dual of the electric theory is equivalent to itself. 
 \end{itemize}
@@
 (In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)
+
+\subsubsection{The special case of $SU(2)$ SQCD}
+
+\owen{I like the idea of analyzing a special case, but I'm not sure what lesson the reader is supposed to learn.}
+
+Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
+In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
+\beqn
+(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
+\eeqn
+This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.
+
+On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
+\beqn
+V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
+\eeqn
+There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
+Again the flavor symmetry group admits an enhancement to $SU(2F)$.
+
+Let's further consider some special cases for small values of flavors.
+
+$\bullet \ul{F=2}$. \brian{I'm confused}
+
+$\bullet \ul{F=3}$. 
+In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
+\beqn
+(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
+\eeqn
+In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
+If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
+\beqn
+W = \frac16 \Phi \wedge \Phi \wedge \Phi .
+\eeqn
+We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
+The critical locus of $W$ is simply the space of solutions to the equation
+\beqn
+\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
+\eeqn
+This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
+
+$\bullet \ul{F=4}$.
+This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
+On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
+On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
+
+We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
+For $F \geq 4$ the
 
@@
 This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
-We now turn to fleshing out these assertions.
+We now turn to fleshing out these assertions, but we will only discuss (1) and (2).
+Aspect (1) is necessary even to formulate a precise statement,
+and aspect (2) uses results --- notably the higher Kac-Moody algebras --- that we've already encountered in this survey.
+Spacetime symmetries involve similar tools and ideas, albeit in a modified form, much like similarities between studying the Virasoro algebra and affine Lie algebras.
 
@@
 
-\subsubsection{Twisted superconformal symmetry}
-
-A superconformal algebra is a simple super Lie algebra which contains both the ordinary algebra of infinitesimal conformal transformations and the super Lie algebra of supertranslations.
-It is a basic fact of life that all (super)conformal algebras in dimensions $\geq 3$ are finite-dimensional.
-Being a superconformal theory means that the theory admits a symmetry by a particular superconformal algebra---it is, generally speaking, a very rigid condition on a theory.
-
-The (complexified) $\cN=1$ superconformal in four-dimensions is $\sl(4|1)$.
-This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
-%The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
-Inside of this algebra is the Cartan generator $\Delta$ of which is an infinitesimal generator for scaling transformations in~$\RR^4$.
-
-Fix the same square-zero supercharge $\cQ$ inside of the four-dimensional $\cN=1$ supersymmetry algebra which we use to define the holomorphic twists of Seiberg dual gauge theories. 
-Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
-There is a quasi-isomorphism of dg Lie algebras
-\[
-\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) ,
-\]
-see \cite{SWsuco}, for example.
-So, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ is guaranteed to act on the holomorphically twisted theory. 
-In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
-The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
-where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an $SL(3)$-homogenous space.
-(In a moment we will discuss how all holomorphic vector fields act on the theories.)
-Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator 
-\beqn
-\Delta^{hol} = z_1 \del_{z_1} + z_2 \del_{z_2},
-\eeqn 
-which is simply the holomorphic Euler vector field.  
-We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
-
-Let's consider just a free theory consisting of a single chiral multiplet, for the moment.
-Here, the $R$-symmetry group is $U(1)$.
-The holomorphic supercharges breaks the $SO(4;\C)$ symmetry down to the group $MU(2)$ which is a double cover of $U(2)$.
-To perform the twist of a theory there are always two steps: the first is to `twist' the fields of the theory using the $R$-symmetry and the second is to deform the action by the supercharge $\cQ$.
-To have a consistent data to twist, one usually imposes the condition that with respect to the twisted $R$-symmetry action the supercharge $Q$ is invariant.
-The odd part of the four-dimensional $\cN = 1$ algebra is given by 
-\beqn
-S_+ \otimes W \oplus S_- \otimes W^*
-\eeqn
-where $W \cong \C$ is just a one-dimensional vector space and $S_{\pm}$ are the positive and negative semi-chiral spin representations of $\lie{so}(4;\C)$.
-We will take the square-zero supercharge to live in $\cQ \in S_+ \otimes W$.
-As an $MU(2)$ representation one has $S_+ \cong \det(L)^{+1/2} \oplus \det(L)^{-1/2}$.
-Thus, if $\cQ$ lies in the first summand, in order to make $\cQ$-invariant we must twist by the condition that $W$ has weight $-1/2$ under the $R$-symmetry.
-We will fix this twisting data.
-
-The basic components of the chiral multiplet is a pair of bosons $(\phi,\Bar{\phi})$, and a pair of fermions $(\psi_+, ,\psi_-)$ where $\psi_{+}$ takes values in $S_+$ and $\psi_-$ takes values in $S_-$.
-For a free theory, we may assign any $R$-charge to $\psi_+$ and this determines the $R$-charges of all remaining fields. 
-For example, if the $R$-charge of $\psi_+$ is $r$ then the $R$-charge of $\phi$ is $r+1$, the $R$-charge of $\psi_-$ is $-r$, and the $R$-charge of $\Bar{\phi}$ is $-r - 1$.
-
-If we twist using the data where $\cQ$ is invariant, then the particular choice of $r$ will dictate how the holomorphic scaling operator $\Delta^{hol}$ acts on the theory.
-One finds that the holomorphic twist of the free chiral theory (which is just a single quark in the above terminology) has fundamental field
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2}) 
-\] 
-where $K$ denotes the holomorphic canonical bundle.
-Of course, the canonical bundle on $\C^2$ is trivializable, so we obtain a theory with isomorphic space of fields for any choice of $r$; what changes is how the twisted superconformal symmetry algebra $\lie{sl}(3)$ acts.
-
-Now, let's consider the electric theory.
-We assume that the $R$-charges of the fermions in the quarks and anti-quark multiplets is the same.
-If this $R$-charge is $r$ then the twisted quarks and anti-quarks take the form
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q),\quad Q^\dagger \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q^*)
-\]
-where $V_Q \cong \C^{NF}$.
-In the untwisted theory the value $r$ is fixed by the condition that the $R$-symmetry is anomaly free.
-In the twisted theory, the value of $r$ is fixed by the condition that the action by the holomorphic scaling operator is anomaly free.
-This anomaly comes from a one-loop diagram with a single vertex labeled by $\Delta^{hol}$, and leads to the constraint that
-\beqn
-N + F r = 0 .
-\eeqn
-In other words, $r = - N / F$. 
-This is the exact condition one must require for $R$-symmetry to be anomaly free in the untwisted theory. 
-On the magnetic side the condition becomes $r = N/F - 1$.
-
-In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories are expected to flow to the same superconformal fixed point in the infrared limit. 
-This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
-(Note that it is preserved under swapping $N \leftrightarrow F-N$.)
-It would be interesting to explore how it appears from the point of view of holomorphic QCD.
+%\subsubsection{Twisted superconformal symmetry}
+%
+%\owen{I'm now pretty lost in how this section discusses evidence for Seiberg duality.}
+%
+%A superconformal algebra is a simple super Lie algebra which contains both the ordinary algebra of infinitesimal conformal transformations and the super Lie algebra of supertranslations.
+%It is a basic fact of life that all (super)conformal algebras in dimensions $\geq 3$ are finite-dimensional.
+%Being a superconformal theory means that the theory admits a symmetry by a particular superconformal algebra---it is, generally speaking, a very rigid condition on a theory. 
+%
+%The (complexified) $\cN=1$ superconformal in four-dimensions is $\sl(4|1)$.
+%This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
+%%The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
+%Inside of this algebra is the Cartan generator $\Delta$ of which is an infinitesimal generator for scaling transformations in~$\RR^4$.
+%
+%Fix the same square-zero supercharge $\cQ$ inside of the four-dimensional $\cN=1$ supersymmetry algebra which we use to define the holomorphic twists of Seiberg dual gauge theories. 
+%Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
+%There is a quasi-isomorphism of dg Lie algebras
+%\[
+%\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) ,
+%\]
+%see \cite{SWsuco}, for example.
+%So, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ is guaranteed to act on the holomorphically twisted theory. 
+%In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
+%The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
+%where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an $SL(3)$-homogenous space.
+%(In a moment we will discuss how all holomorphic vector fields act on the theories.)
+%Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator 
+%\beqn
+%\Delta^{hol} = z_1 \del_{z_1} + z_2 \del_{z_2},
+%\eeqn 
+%which is simply the holomorphic Euler vector field.  
+%We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
+%
+%Let's consider just a free theory consisting of a single chiral multiplet, for the moment.
+%Here, the $R$-symmetry group is $U(1)$.
+%The holomorphic supercharges breaks the $SO(4;\C)$ symmetry down to the group $MU(2)$, a double cover of $U(2)$.
+%To perform the twist of a theory there are always two steps: the first is to `twist' the fields of the theory using the $R$-symmetry and the second is to deform the action by the supercharge $\cQ$.
+%To have a consistent data to twist, one usually imposes the condition that with respect to the twisted $R$-symmetry action the supercharge $Q$ is invariant.
+%The odd part of the four-dimensional $\cN = 1$ algebra is given by 
+%\beqn
+%S_+ \otimes W \oplus S_- \otimes W^*
+%\eeqn
+%where $W \cong \C$ is just a one-dimensional vector space and $S_{\pm}$ are the positive and negative semi-chiral spin representations of $\lie{so}(4;\C)$.
+%We will take the square-zero supercharge to live in $\cQ \in S_+ \otimes W$.
+%As an $MU(2)$ representation one has $S_+ \cong \det(L)^{+1/2} \oplus \det(L)^{-1/2}$.
+%Thus, if $\cQ$ lies in the first summand, in order to make $\cQ$-invariant we must twist by the condition that $W$ has weight $-1/2$ under the $R$-symmetry.
+%We will fix this twisting data.
+%
+%The basic components of the chiral multiplet is a pair of bosons $(\phi,\Bar{\phi})$, and a pair of fermions $(\psi_+, ,\psi_-)$ where $\psi_{+}$ takes values in $S_+$ and $\psi_-$ takes values in $S_-$.
+%For a free theory, we may assign any $R$-charge to $\psi_+$ and this determines the $R$-charges of all remaining fields. 
+%For example, if the $R$-charge of $\psi_+$ is $r$ then the $R$-charge of $\phi$ is $r+1$, the $R$-charge of $\psi_-$ is $-r$, and the $R$-charge of $\Bar{\phi}$ is $-r - 1$. 
+%
+%If we twist using the data where $\cQ$ is invariant, then the particular choice of $r$ will dictate how the holomorphic scaling operator $\Delta^{hol}$ acts on the theory.
+%One finds that the holomorphic twist of the free chiral theory (which is just a single quark in the above terminology) has fundamental field
+%\[
+%Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2}) 
+%\] 
+%where $K$ denotes the holomorphic canonical bundle.
+%Of course, the canonical bundle on $\C^2$ is trivializable, so we obtain a theory with isomorphic space of fields for any choice of $r$; what changes is how the twisted superconformal symmetry algebra $\lie{sl}(3)$ acts.
+%
+%
+%Now, let's consider the electric theory.
+%We assume that the fermions in the quarks and anti-quark multiplets have the same $R$-charges.
+%If this $R$-charge is $r$, then the twisted quarks and anti-quarks take the form
+%\[
+%Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q) \quad\text{and}\quad Q^\dagger \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q^*)
+%\]
+%where $V_Q \cong \C^{NF}$.
+%In the untwisted theory the value $r$ is fixed by the condition that the $R$-symmetry is anomaly-free.
+%In the twisted theory, the value of $r$ is fixed by the condition that the action by the holomorphic scaling operator is anomaly-free.
+%This anomaly comes from a one-loop diagram with a single vertex labeled by $\Delta^{hol}$, and it leads to the constraint 
+%\beqn
+%N + F r = 0 .
+%\eeqn
+%In other words, $r = - N / F$. 
+%This condition matches the corresponding condition for $R$-symmetry to be anomaly-free in the untwisted theory. 
+%On the magnetic side the condition is $r = N/F - 1$.
+%
+%In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories are expected to flow to the same superconformal fixed point in the infrared limit. 
+%This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
+%(Note that it is preserved under swapping $N \leftrightarrow F-N$.)
+%It would be interesting to explore how it appears from the point of view of holomorphic QCD. 
+%
+%<<<<<<< HEAD
+%\begin{cor}
+%{\em Divergence-free} holomorphic vector fields are a symmetry at the quantum level for any values of $F$ and~$N$.
+%Only when $F = 3N$ do {\em all} holomorphic vector fields lift to a symmetry lifts at the quantum level.
+%\end{cor}
+%=======
+%>>>>>>> 8d2b48799f0de9991260e8451b5287400da94e98
 
@@
 
-\subsubsection{The special case of $SU(2)$ SQCD}
-
-Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
-In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
-\beqn
-(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
-\eeqn
-This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.
-
-On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
-\beqn
-V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
-\eeqn
-There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
-Again the flavor symmetry group admits an enhancement to $SU(2F)$.
-
-Let's further consider some special cases for small values of flavors.
-
-$\bullet \ul{F=2}$. \brian{I'm confused}
-
-$\bullet \ul{F=3}$. 
-In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
-\beqn
-(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
-\eeqn
-In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
-If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
-\beqn
-W = \frac16 \Phi \wedge \Phi \wedge \Phi .
-\eeqn
-We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
-The critical locus of $W$ is simply the space of solutions to the equation
-\beqn
-\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
-\eeqn
-This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
-
-$\bullet \ul{F=4}$.
-This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
-On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
-On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
-
-We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
-For $F \geq 4$ the
-
-\subsection{Two-dimensional TFTs by reduction}
-
-A standard maneuver used in physics is compactification:
-given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
-One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
-A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
-
-We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
-In other words, this is the $T^2$ compactification of the holomorphic theory.
-For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
-We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.
-
-Let's first consider the electric side which breaks up into holomorphic BF theory coupled to a complex two-dimensional $\beta\gamma$ system.
-The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
-This is the space whose algebra of functions is $\cO(\C^{NF}) ((z))((w))$ where $z,w$ are formal loop parameters which we imagine as describing the winding of the two circles we have compactified. 
-The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
-Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is $B GL(N)$).
-In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
-As a derived mapping space, this model is given by
-\beqn
-{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
-\eeqn
-The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack $\C^{NF} / GL(N)$.
-
-On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
-What results is a Landau--Ginzburg B-model whose target is the stack
-\beqn
-\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
-\eeqn
-The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
-The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in \eqref{eqn:checkW}.
-
-Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
-or at least of $E_2$-algebras.
-
-\begin{conj}
-There is an equivalence of $E_2$ algebras between:
-\begin{itemize} 
-\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$.
-\item (magnetic) the $E_2$ algebra which results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
-\end{itemize}
-\end{conj}
-
-%\begin{conj}
-%There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
-%the compactifications of the electric and magnetic holomorphic QCD theories.
-%\end{conj}
-
-This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
-(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
-We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
-
-%A duality 
-%
-%The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
-%The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
-%For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
-
 \subsection{A second pass at holomorphic Seiberg duality}
@@
 
-\owen{Is that true?}
-\brian{I'm happy with this.}
-
 This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in \owen{reference section of this paper}.
@@
 We note that there may be many quantizations possible, but our experience in $\cN=4$ case suggests that there is an ``obvious'' one.
-\owen{Feel free to reel back this overblown statement.}
 
@@
 
-\subsubsection{Enhanced spacetime symmetries}
-
-\owen{Add section with conjecture about local spacetime symmetry and its quantization}
-and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields. Under quantization, these have isomorphic anomalies.
+\subsubsection{Two intriguing possibilities}
+
+In discussions with Costello and Gaiotto, there appeared two suggestions that, while optimistic, would make studying these theories and this duality much more tractable.
+\begin{enumerate}
+
+\item For any space $M$ and any point $p \in M$, there is a canonical algebra map $\cO(M) \to \cO(M)^\wedge_p$ sending a function on $M$ to its ``Taylor expansion'' at $p$. 
+Sometimes this map is injective. 
+Similarly, there is a map of holomorphic factorization algebras from the moduli space of quantum vacua to the observables of a perturbative theory (e.g., at a point $x$ in the stable locus).
+One might ask if this map retains all essential information. 
+If it does, then holomorphic Seiberg duality can be analyzed via the correspondence between points on the stable loci.
+(Of course, one must characterize ``essential'' here with precision.)
+
+\item We have described a quantum Noether map from the (enhanced) flavor symmetries to the observables of holomorphic QCD. 
+Optimistically, these symmetries might ``saturate'': this current map might be essentially surjective.
+In that case, these theories could be analyzed via the representation theory of the flavor symmetries.
+Such a situation would be reminiscent of minimal models in the one-dimensional chiral conformal setting.
+
+\end{enumerate}
+Exploring these possibilities would likely lead to substantially deeper understanding of holomorphic Seiberg duality.
+One motivation for these suggestions comes from work on two-dimensional (0,2)-theories, such as \cite{DeduGuk, EagLocSha}.
+
+\subsection{Two-dimensional dualities by reduction}
+
+A standard maneuver used in physics is compactification:
+given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
+A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
+
+We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
+In other words, this is the $T^2$ compactification of the holomorphic theory.
+For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
+We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.
+
+Let's first consider the electric side, 
+which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
+The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
+The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
+where $z,w$ are formal loop parameters which we imagine as describing the winding of the two circles we have compactified. 
+The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
+Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
+In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
+As a derived mapping space, the moduli of solutions is given by
+\beqn
+{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
+\eeqn
+The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.
+
+On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
+What results is a Landau--Ginzburg B-model whose target is the stack
+\beqn
+\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
+\eeqn
+The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
+The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.
+
+Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
+or at least of $E_2$-algebras.
+
+\begin{conj}
+There is an equivalence of the following $E_2$ algebras:
+\begin{itemize} 
+\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
+\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
+\end{itemize}
+\end{conj}
+
+%\begin{conj}
+%There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
+%the compactifications of the electric and magnetic holomorphic QCD theories.
+%\end{conj}
+
+This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
+(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
+We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
+For instance, in this mathematical work, 
+one sees different choices of GIT quotients associated to the same stack yielding equivalent derived categories (and cousins),
+and these quotients only know about certain pieces of the stack,
+an issue we have flagged in our comparison of the moduli stack and the moduli space.
 

### 2023-01-16 draft.tex
hiding and removing comments in sd section

@@
 so $\underline{N} = \CC^N$ with its natural left action.
-\owen{That's kind of crappy notation. Let's discuss.}
-\brian{Does it help us much? Or are you trying to use this to disambiguate what $\CC^N$ means.}
 
@@
 
-\owen{Do we want $F > N+1$?
-The physicists break things into several cases.
-In particular, I think the moduli is unchanged under quantization only if $F$ is big enough relative to $N$ and $\check{N}$.}
-\brian{I expect we want a similar condition, but I was never able to understand how that appears at the level of factorization algebras.}
-
 \begin{rmk}
@@
 given by the substack of constant solutions.
-We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.
+We call it the {\em moduli stack of classical vacuum solutions} for the theory~$\cT$.
 
@@
 \begin{rmk}\label{sols vs states}
-The physicists' focus on the moduli space is not unreasonable:
+The physicists' focus on the moduli space is quite reasonable:
 one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
-The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
-In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
+The moduli space captures what can be seen by measurements (here, the ``vacuum expectation values'' of different vacua).
+In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by an affine scheme underlying the derived moduli stack.
 On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
-and hence records much more about the classical theory; 
-the space cannot distinguish between some vacua because it collapses orbits.
+and hence records much more about the classical theory.
+By contrast, the space cannot distinguish between some vacua because it collapses orbits.
 Moreover, the stack encodes much more data about the theory near each vacuum.
@@
 
-This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in \owen{reference section of this paper}.
-\owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}
-\brian{that's a great question}
+This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in Section~\owen{reference section of this paper}.
+%\owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}
+%\brian{that's a great question}
 
@@
 \beqn
-{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
+{\rm Map}\left(\RR^2, T^*[1] \left[ \C^{NF} / GL(N)\right]\right) .
 \eeqn
@@
 \beqn
-\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
+\left[\C^{(F-N)F} / GL(F-N) \right] \times \C^{F^2} .
 \eeqn
@@
 \begin{itemize} 
-\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
-\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
+\item (electric) the $E_2$ algebra of polyvector fields on the stack $[\C^{NF} / GL(N)]$, and 
+\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $[\C^{(F-N)F} / GL(F-N)] \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
 \end{itemize}

### 2023-01-18 draft.tex
cleaned up SD section for richard

@@
 \subsection{Algebras in higher dimensions }
+\label{subsec: FHK}
 
@@
 \section{Holomorphic $\sigma$-models, higher algebras of differential operators, and higher free field realization}
+\label{sec: higher CDO}
 
@@
 and one of his leading contributions is referred to as {\em Seiberg duality}.
-It has had a large impact in theoretical physics \owen{give the citation number on that paper},
+It has had a large impact in theoretical physics (with nearly two thousand citations),
 but the impact in mathematics is much more muted,
@@
 should produce equivalences between different kinds of 2-dimensional B-model theories;
-these reductions are related to work of Hori and Hori--Tong \owen{citations} and its mathematical development by Ed Segal, \owen{list others}.
+these reductions are related to work of Hori and Hori--Tong \cite{Hori, HorTon} and their mathematical offshoots \cite{Segal, etc}.
 
@@
 
-\subsubsection{The duality functor}
+\subsubsection{Extending the duality}
 
@@
 \begin{itemize}
-\item In the case that there are no mesons in the original theory, like in the electric theory, the dual agrees with the magnetic theory.
-\item The dual of the magnetic theory is equivalent to the original electric theory. In other words, the double dual of the electric theory is equivalent to itself. 
+\item In the case that there are no mesons in the original theory, as in the electric theory, the dual agrees with the magnetic theory.
+\item The dual of the magnetic theory is equivalent to the original electric theory. 
+In other words, the double dual of the electric theory is equivalent to itself. 
 \end{itemize}
 %In fact, more generally, the double dual of any supersymmetric QCD with mesons returns the same theory (up to equivalence). 
-Let us briefly remark how this general duality looks classically in the holomorphic context.
+Let us briefly remark how to state this more general duality in the holomorphic context.
 
@@
 The superpotential is $W(QQ^\dagger, \mu)$.
-The dual theory is again a holomorphic QCD theory with mesons.
-Precisely the dual theory is holomorphic QCD with $F-N$ colors, $F$ flavors, and mesons valued in 
+The dual theory should again be a holomorphic QCD theory with mesons:
+it is holomorphic QCD with $F-N$ colors, $F$ flavors, and with mesons valued in 
 \beqn
@@
 \eeqn
-Notice that when $V_M = 0, W=0$ this agrees with the dual magnetic theory that we introduced above.
-
-Now, let's suppose we start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
-The superpotential is $W = \Tr \check{Q}^\dagger \check{\mu} \check{Q}$. 
+Notice that when $V_M = 0, W=0$, this construction agrees with the dual magnetic theory that we introduced above.
+
+Now, let's check how it fits with the second condition we requested. 
+Start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
+The superpotential is $W = \Tr(\check{Q}^\dagger \check{\mu} \check{Q})$. 
 Taking the dual of this theory we obtain holomorphic QCD with $N$ colors and $F$ flavors as expected.
-However, we have mesons $\check{\mu}$ and $\til \mu$ both valued in $\End(\C^F)$. 
+However, we have mesons $\check{\mu}$ and $\til \mu$, both valued in $\End(\C^F)$. 
 The superpotential is simply
 \beqn
-\til W = \Tr \check \mu \til \mu + \Tr \til Q^\dagger \check{\mu} \til Q .
+\til W = \Tr( \check \mu \til \mu) + \Tr (\til Q^\dagger \check{\mu} \til Q ).
 \eeqn
 The first term arises from substituting $\til \mu = \check Q \check Q^\dagger$ in the original magnetic superpotential. 
-This term has the effect of making both $\mu,\check \mu$ massive, and hence they can be integrated out to obtain the original electric theory. 
+This term has the effect of equipping both the mesons $\mu$ and $\check \mu$ with mass, 
+and hence these fields can be integrated out to obtain the original electric theory. 
 (In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)
-
-\subsubsection{The special case of $SU(2)$ SQCD}
-
-\owen{I like the idea of analyzing a special case, but I'm not sure what lesson the reader is supposed to learn.}
-
-Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
-In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
-\beqn
-(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
-\eeqn
-This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.
-
-On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
-\beqn
-V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
-\eeqn
-There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
-Again the flavor symmetry group admits an enhancement to $SU(2F)$.
-
-Let's further consider some special cases for small values of flavors.
-
-$\bullet \ul{F=2}$. \brian{I'm confused}
-
-$\bullet \ul{F=3}$. 
-In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
-\beqn
-(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
-\eeqn
-In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
-If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
-\beqn
-W = \frac16 \Phi \wedge \Phi \wedge \Phi .
-\eeqn
-We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
-The critical locus of $W$ is simply the space of solutions to the equation
-\beqn
-\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
-\eeqn
-This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
-
-$\bullet \ul{F=4}$.
-This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
-On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
-On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
-
-We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
-For $F \geq 4$ the
 
@@
 the quotient by $G$ arises from the gauge transformation.
-For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
+For example, the holomorphic twist of pure $\cN =1$ Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
 \[
@@
 the coadjoint quotient stack of the group.
-\brian{The paragraph began with holomorphic theories, do you want to say twist of 4d N=1?}
 (We are working in a $\ZZ/2$-graded world here.)
-Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
+When $G$ is semisimple and using the invariant pairing on $\fg$, 
+we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
 For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
@@
 In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
-Instead, they have worked with a GIT quotient.
+Instead, they have worked with a variety arising as a GIT quotient.
 For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
@@
 \]
-By contrast the moduli space $M_{\rm vac}$ is a variety already well-studied in classical algebraic geometry.
+By contrast the moduli space $M_{\rm vac}$ analyzed by physicists is a variety already well-studied in classical algebraic geometry.
+We will now discuss the moduli spaces appearing in the physics literature on Seiberg duality.
+(There are some subtleties in relating the moduli spaces of the supersymmetric theories to the moduli stacks of their twists;
+we will not dwell on them here, but they need to be resolved to obtain a complete story.)
+
 Before we describe the full space, let's examine a simpler case involving just the quarks.
@@
 
-This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
+This relationship, which holds for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
 The proof boils down to checking that the mesons and the superpotential on the magnetic side ensure the isomorphism.
@@
 
+%\subsubsection{The special case of $SU(2)$ SQCD}
+%
+%\owen{I like the idea of analyzing a special case, but I'm not sure what lesson the reader is supposed to learn.}
+%
+%Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
+%In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
+%\beqn
+%(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
+%\eeqn
+%This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$. 
+%
+%On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
+%\beqn
+%V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
+%\eeqn
+%There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
+%Again the flavor symmetry group admits an enhancement to $SU(2F)$.
+%
+%Let's further consider some special cases for small values of flavors. 
+%
+%$\bullet \ul{F=2}$. \brian{I'm confused}
+%
+%$\bullet \ul{F=3}$. 
+%In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
+%\beqn
+%(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
+%\eeqn
+%In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
+%If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
+%\beqn
+%W = \frac16 \Phi \wedge \Phi \wedge \Phi .
+%\eeqn
+%We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
+%The critical locus of $W$ is simply the space of solutions to the equation
+%\beqn
+%\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
+%\eeqn
+%This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
+%
+%$\bullet \ul{F=4}$.
+%This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
+%On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
+%On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
+%
+%We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
+%For $F \geq 4$ the
+
 \subsubsection{Flavor symmetry enhancement}
@@
 There is another dg Lie algebra obtained by evaluating the theory on punctured affine space $\C^2 - 0$.
-We recalled in \S \ref{sec:punctured} an algebraic model $\sfA_2$ for the dg algebra $\Omega^{0,\bu}(\C^2 - 0)$.
+We recalled in Section~\ref{subsec: FHK} an algebraic model $\sfA_2$ for the dg algebra $\Omega^{0,\bu}(\C^2 - 0)$.
 The dg Lie algebra we assign to the punctured affine space, classically, is $\lie{sl}(F) \otimes \sfA_2$.
@@
 and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
-(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(F)}_{2,\theta_{\sfE}}, \Hat{\sl(F)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - 0$.)
+(In terms of Section~\ref{subsec: FHK}, these determine higher Kac--Moody algebras $\Hat{\sl(F)}_{2,\theta_{\sfE}}, \Hat{\sl(F)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - 0$.)
 
@@
 For both the electric and magnetic theories, there is an anomaly at the quantum level for the holomorphic flavor symmetry action.
-These anaomlies agree: they are labeled by the same cocycle 
+These anomlies agree: they are labeled by the same cocycle 
 \[
@@
 
-This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in Section~\owen{reference section of this paper}.
+This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in Section~\ref{sec: higher CDO}.
 %\owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}

### 2023-01-27 draft.tex
merge

--- 2023-01-16 draft.tex
@@
 The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
+Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on $X$.
 
@@
 Such theories are often used to describe matter, such as electron fields.
+\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
 \item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
-\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
 \item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
@@
 
-The most elementary holomorphic field theory is a generalization of the so-called `$\beta\gamma$ system' which is primarily studied in the context of string theory.
-The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on $X$.
+A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
+Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
+When $\Sigma$ is a surface this theory can be written in such a way that makes its complex structure apparent.
+First, we complexify the field $\phi$ which we can view as a pair of fields $\gamma, \Bar{\gamma}$.
+When we do this, we can split it up into its chiral and anti-chiral `sectors'.
+By chiral (anti-chiral) we mean part involving $\gamma$ ($\Bar{\gamma}$).
+The holomorphic part is described by the following action
+\beqn
+\int_\Sigma \beta \wedge \dbar \gamma
+\eeqn
+where $\beta$ is a $(1,0)$ form on $\Sigma$ and should be thought of as a Lagrange multiplier for the field $\del \Bar{\gamma}$ which we now think about as having its own degrees of freedom (this is called the first-order formalism).
+There is also a coupling between the chiral and anti-chiral sectors, 
+for more details we refer to \cite{Kapustin,GGW}. 
+This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta-\gamma$-\textit{system}.
+It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.
+
+There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta-\gamma$ system'.
+The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
+Above we took this bundle to be trivial.
 The fields of the theory consist of pairs 
@@
 \end{align*}
-The action functional is 
-\beqn
-\int_X \beta \wedge \dbar \gamma 
-\eeqn
-which utilizes the natural pairing between $V$ and $V^*$. 
-The theory is free, just like the ordinary $\beta\gamma$ system on Riemann surfaces.
-
-Notice that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
+The action functional is identical $\int_X \beta \wedge \dbar \gamma$.
+
+Notice that when $n = \dim_\C X > 1$ that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
 \beqn
@@
 Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
+This is one of the key differences between the ordinary $\beta-\gamma$ system and its higher dimensional version.
+Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.
 
@@
 \eeqn 
-
-\subsubsection{Holomorphic gravity}
+Solutions to the equations of motion describe, in part, holomorphic maps $X \to Y$, but there is also derived information contained in this model.
+
+\subsubsection{Holomorphic ``gravity''}
 
 Perturbatively, any model of gravity describes, in part, deformations of the moduli space of metric structures on a given manifold. 
-There is a holomorphic avatar of this which describes deformations of complex structure.
-The fields consist of pairs $(\mu, \eta)$ where
-\begin{align*}
-\mu & \in \Omega^{0,1}(X, \T_X) \\
-\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
-\end{align*}
-The action functional is
-\beqn
-\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
-\eeqn
-where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.
-
-In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
-Let $X$ be a complex threefold equipped with a Calabi--Yau structure where we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
-Kodaira--Spencer theory is the holomorphic theory whose fields consist of $(0,1)$ forms on $X$ with values in the holomorphic tangent bundle $\T_X$
+There is a holomorphic avatar of this which describes deformations of complex structure which has first appeared in the literature in work related to topological string theory on Calabi--Yau threefolds~\cite{BCOV}.
+Because of its relationship to complex structures, the theory is referred to as \textit{Kodaira--Spencer theory}.
+It has been mathematically championed in the works of Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
+In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; here we focus just on the more familiar three-dimensional version.
+%The fields consist of pairs $(\mu, \eta)$ where
+%\begin{align*}
+%\mu & \in \Omega^{0,1}(X, \T_X) \\
+%\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
+%\end{align*}
+%The action functional is
+%\beqn
+%\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
+%\eeqn
+%where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.
+
+%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
+Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
+The primary field of Kodaira spencer theory is a $(0,1)$ form on $X$ with values in the holomorphic tangent bundle $\T_X$
 \beqn
@@
 \eeqn
-The integrand is not defined globally.
-In the integral we use the Calabi--Yau form to identify the integrand with 
-\brian{finish}
-
+In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
+The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
+Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
+Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
+Forgoing the apparent global issues, we can still apply formal variational calculus to the action to obtain the equation of motion
+\beqn
+\dbar \mu + \frac12 [\mu,\mu] = 0 ,
+\eeqn
+where $[-,-]$ is the Schouten--Nijenhuis bracket (which reduces to just the natural bracket when restricted to vector fields).
+The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
 \subsection{Local version and examples from supersymmetric field theories}
@@
 a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
-The classification of all twists is a completely algebraic question,
-and we refer to~\autocite{ESsusy} for a complete classification of all twists \owen{of SYM?} in dimensions from $1$ to~$10$.
+The classification of twisting supercharges is a completely algebraic question,
+and we refer to~\autocite{ESsusy} for a complete classification for supersymmetry algebras in dimensions from $1$ to~$10$.
 
@@
 
-We now turn to quantization, and our phase space will be, for simplicity, the algebraic loop space $V[z,z^{-1}]$ of a symplectic complex vector space $V$.
+We now turn to quantization, and our phase space will be, for simplicity, the formal loop space $V((z))$ of a symplectic complex vector space $V$.
 Following the case of mechanics, we might ask for a deformation of the Poisson algebra
@@
 %\]
-%On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\omega^* \otimes \Res$ on $V^* [z,z^{-1}]$.
+%On this subalgebra, the naive Poisson bracket makes sense: it is given by extending the nondegenerate skew-symmetric pairing $\Omega^\bu \otimes \Res$ on $V^* [z,z^{-1}]$.
 %Hence for $\cO(V((z)))$, we can ask for a deformation quantization,
@@
 there is a restriction of $\phi$ to a little disc around $w$.
-That is, there is a restriction map $r_w: V[z,z^{-1}] \to V[[t]]$, where $t$ is the local coordinate $t = z-w$.
-Hence there is a $w$-dependent map $\cO(V[[t]]) \to \cO(V[z,z^{-1}])$ by pulling back a function along $r_w$;
+That is, there is a restriction map $r_w: V((z)) \to V[[t]]$, where $t$ is the local coordinate $t = z-w$.
+Hence there is a $w$-dependent map $\cO(V[[t]]) \to \cO(V((z)))$ by pulling back a function along $r_w$;
 this map determines a $w$-dependent action of $\cO(V[[t]])$ on $\cO(V[[z]])$.
@@
 Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
-We interpret $\sum_{k \in \ZZ} \phi_k(t)$ as smooth map from $\RR$ to the formal (free) loop space $LV = V[z,z^{-1}]$.
+We interpret $\sum_{k \in \ZZ} \phi_k(r)$ as smooth map from $\RR$ to the formal loop space $LV$.
 
@@
 \subsection{Algebras in higher dimensions }
+\label{s:alghigh}
 
@@
 and not just the cohomology groups.
-There is a beautiful, explicit dg model $\sfA^\bu_d$ for the formal version derived global sections due to Faonte-Hennion-Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities.
+There is a beautiful, explicit dg model $\sfA^\bu_d$ for the formal version derived global sections due to Faonte, Hennion, and Kapranov \cite{FHK} and based on the Jouanolou method for resolving singularities.
 While we won't go into details about this model, we remark on a few important points all of which we take from \cite{FHK}:
@@
 \begin{dfn}[\cite{FHK}]
+\label{dfn:sphere}
 For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$\fg \otimes \sfA_d$.
@@
 
-There are natural central extensions of this sphere algebra as {\em $L_\infty$ algebras},
+There are natural central extensions of this sphere algebra 
+%as {\em $L_\infty$ algebras},
 parallel to the affine Lie algebras appearing as central extensions of the loop algebra.
-An $L_\infty$ algebra is a generalization of a Lie algebra;
-it is graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k \colon L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi condition for a standard Lie algebra.
-For an overview (and an actual definition!) we recommend \owen{add citations}.
-
-In our setting of $\fg^\bullet_d$, Faonte-Hennion-Kapranov introduced central extensions of the sphere algebra that only affect the $d$-bracket.
-For any $\fg$-invariant degree $d+1$ polynomial $\theta \in \Sym^{d+1}(\fg^*)^\fg$, the cocycle which defines the $L_\infty$ central extension is
+They are given by the data of a $\fg$-invariant degree $d+1$ polynomial $\theta \in \Sym^{d+1}(\fg^*)^G$.
+The cocycle which defines the $L_\infty$ central extension is
 \[
@@
 \]
-This cocycle has total cohomological degree $+2$ as an element in the Lie algebra cohomology of $\fg^\bu_{d}$ and so determines a central extension of $L_\infty$ algebras
-\[
-\CC c \to \widetilde{\fg}^\bullet_{d, \theta} \to \fg^\bullet_d ,
-\]
-so that the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
-They dubbed these the {\em higher Kac-Moody algebras}, 
-as they specialize to the affine Lie algebras when~$d =1$.
-
-These $L_\infty$ algebras are not just introduced on a whim.
+This cocycle has total cohomological degree $+2$ as an element in the Lie algebra cohomology of $\fg^\bu_{d}$ and so determines a central extension of dg Lie algebras
+\[
+\CC c \to \Hat{\fg}^\bullet_{d, \theta} \to \fg^\bullet_d .
+\]
+There is a particularly nice model for this dg Lie algebra as an $L_\infty$ \textit{algebra} that we use in \cite{GWkm}.
+An $L_\infty$ algebra is a generalization of a dg Lie algebra;
+it is a graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k \colon L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi identity.
+For an overview (and an actual definition!) we recommend \owen{add citations}.
+In our setting the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
+%They dubbed these the {\em higher Kac-Moody algebras}, 
+%as they specialize to the affine Lie algebras when~$d =1$.
+
+The algebras $\Hat{\fg}^\bullet_{d, \theta}$ are not just introduced on a whim.
 In \cite{FHK} they are shown to appear naturally in various contexts,
@@
 One simply takes the singular chain complex on each space of operations:
-for each natural number $n$, take $C_*(\Disc_d(n); \CC)$ and take the induced chain map 
-\[
-C_*(\circ_i): C_*(\Disc_d(n); \CC) \otimes C_*(\Disc_d(m); \CC) \to C_*(\Disc_d(n+m-1); \CC)
-\]
-to produce a dg operad we denote~$C_*(\Disc_d)$.
-(Note that as we always want to work with cochain complexes, we regrade the usual singular chains $C_*(X, \CC)$ to sit in nonpositive cohomological degrees. 
-Likewise the composition $C_*(\circ_i)$ is then a cochain map.)
+for each natural number $n$, take $C_\bu(\Disc_d(n); \CC)$ and take the induced chain map 
+\[
+C_\bu(\circ_i): C_\bu(\Disc_d(n); \CC) \otimes C_\bu(\Disc_d(m); \CC) \to C_\bu(\Disc_d(n+m-1); \CC)
+\]
+to produce a dg operad we denote~$C_\bu(\Disc_d)$.
+(Note that as we always want to work with cochain complexes, we regrade the usual singular chains $C_\bu(X, \CC)$ to sit in nonpositive cohomological degrees. 
+Likewise the composition $C_\bu(\circ_i)$ is then a cochain map.)
 
 \begin{dfn}
-An {\em algebra over the little $d$-discs operad} (or little $d$-discs algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_*(\Disc_d)$.
+An {\em algebra over the little $d$-discs operad} (or little $d$-discs algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_\bu(\Disc_d)$.
 \end{dfn}
@@
 For instance, there is a composition
-\begin{align}
+\begin{multline}
 \label{pdcirc}
-\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, &\ldots, s_m, r_{i+1}, \ldots, r_n| R)) \to \\
-&\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
-\end{align}
+\circ_i: \Omega^{0,\bu}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R)) \to \\
+\Omega^{0,\bu}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,\bu}(\PDisc_d(s_1, \ldots, s_m| S))
+\end{multline}
 \owen{I don't know how to eliminate the two numbers}
+\brian{I like using multline instead of align}
 when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
@@
 \[
-\Omega^{0,*}(X) \otimes \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
+\Omega^{0,\bu}(X) \otimes \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
 \]
@@
 \[
-\Omega^{0,*}(X) \widehat{\otimes}_\pi \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
+\Omega^{0,\bu}(X) \widehat{\otimes}_\pi \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
 \]
@@
 \[
-\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) 
+\Omega^{0,\bu}(\PDisc_d(r_1, \ldots, r_n| R)) 
 \]
@@
 There is a composition
-\[
-\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R))\to \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
-\]
+\begin{multline}
+\circ_i \colon \Omega^{0,\bu}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R)) \to \\ \Omega^{0,\bu}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,\bu}(\PDisc_d(s_1, \ldots, s_m| S))
+\end{multline}
 only when $r_i = S$, 
@@
 \[
-\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) .
+\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,\bu}(\PDisc_d(r_1, \ldots, r_n| R)) .
 \]
@@
 \[
-\cO({\rm Conf}_n(\CC)) = H^{0,*}({\rm Conf}_n(\CC)),
+\cO({\rm Conf}_n(\CC)) = H^{0,\bu}({\rm Conf}_n(\CC)),
 \] 
@@
 We will use $z$ to denote this point $w_2$.
-Then we have binary co-operations parametrized by $\CC[z, z^{-1}]$.
+Then we have binary co-operations parametrized by the space $\C^\times$.
 Let 
@@
 \beqn
-A_{\lie{g}} (D_r(z)) = C_\bu \left(\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z)) \right) 
+\label{eqn:diskskm}
+A^{\lie{g}} (D_r(z)) = C_\bu \left(\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z)) \right) 
 \eeqn
@@
 The corresponding vertex algebra is the Kac--Moody vertex algebra of $\fg$ at level zero. 
-To obtain the vertex algebra associated to a nonzero level $\kappa$ one can deform this holomorphic polydisc algebra $A_{\fg} \rightsquigarrow A_{\fg, \kappa}$.
+To obtain the vertex algebra associated to a nonzero level $\kappa$ one can deform this holomorphic polydisc algebra $A^{\fg} \rightsquigarrow A^\fg_{\kappa}$.
 
 Let $V$ be a vector space.
-Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
+Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta-\gamma$ system with values in~$V$.
 To a disc $D = D_r(z)$ this assigns the following cochain complex
@@
 The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.
+The vertex algebra associated to this disk algebra is the familiar $\beta-\gamma$-vertex algebra.
 
@@
 
-\owen{I want to mention here that we have a polydisc version}
+It is apparent that the formula in \eqref{eqn:diskskm} makes sense for a (poly)disk of arbitrary complex dimension $d$.
+In this way, we obtain functor from Lie algebras to $d$-polydisks algebras $\fg \mapsto A^{\fg}_d$.
+(Here $A^{\fg}_1 = A^{\fg}$.)
+
+In this section we have mostly focused on disks.
+If we evaluate $A^{\lie{g}}_{d}$ on a punctured disk rather than a disk then we obtain a complex which receives a dense embedding from the complex
+\beqn
+\Sym \left(\lie{g}^\bu_{d}\right) 
+\eeqn
+where $\lie{g}^\bu_d$ is the higher sphere algebra from Definition \ref{dfn:sphere}.
+A natural question is how the Lie algebra structure appears; to address this we will use the language of factorization algebras in the next section.
+
+Given an invariant polynomial $\theta \in \Sym^{d+1}(\lie{g}^*)^G$ as in \S \ref{s:alghigh} we can obtain a twisted version of this $d$-polydisks algebra $A^{\lie{g}}_{d,\theta}$.
+At the level of the punctured disk this corresponds to the higher Kac--Moody algebra which is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
+This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra \cite{GWkm}.
 
@@
 \[
-\Omega^*(X) \to \Omega^{0,*}(X)
+\Omega^\bu(X) \to \Omega^{0,\bu}(X)
 \]
@@
 we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
-Hence an algebra over the cooperad $\Omega^*(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,*}(\PDisc_d)$.
+Hence an algebra over the cooperad $\Omega^\bu(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
 Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
 \begin{enumerate}
-\item algebras over the dg operad $C_*(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^*(\PDisc_d)$, as $\infty$-categories, and
-\item $E_{2d}$-algebras are equivalent to the algebras over $C_*(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
+\item algebras over the dg operad $C_\bu(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^\bu(\PDisc_d)$, as $\infty$-categories, and
+\item $E_{2d}$-algebras are equivalent to the algebras over $C_\bu(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
 \end{enumerate}
@@
 \begin{cor}
-The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,*}(\PDisc_d)$.
+The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
 \end{cor}
@@
 %\]
-%of the $L_\infty$ algebra $\Omega^*(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
+%of the $L_\infty$ algebra $\Omega^\bu(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
 %The {\em action functional} is the expression
@@
 %\[
-%\Obs^{cl}(U) = \clie^*(\Omega^*(U) \otimes \fg)
+%\Obs^{cl}(U) = \clie^*(\Omega^\bu(U) \otimes \fg)
 %\]
@@
 
-\subsubsection{The special case of $SU(2)$ SQCD}
-
-\owen{I like the idea of analyzing a special case, but I'm not sure what lesson the reader is supposed to learn.}
-
-Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
-In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
-\beqn
-(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
-\eeqn
-This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.
-
-On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
-\beqn
-V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
-\eeqn
-There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
-Again the flavor symmetry group admits an enhancement to $SU(2F)$.
-
-Let's further consider some special cases for small values of flavors.
-
-$\bullet \ul{F=2}$. \brian{I'm confused}
-
-$\bullet \ul{F=3}$. 
-In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
-\beqn
-(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
-\eeqn
-In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
-If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
-\beqn
-W = \frac16 \Phi \wedge \Phi \wedge \Phi .
-\eeqn
-We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
-The critical locus of $W$ is simply the space of solutions to the equation
-\beqn
-\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
-\eeqn
-This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
-
-$\bullet \ul{F=4}$.
-This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
-On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
-On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
-
-We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
-For $F \geq 4$ the
-
 \subsection{Evidence for holomorphic Seiberg duality}
@@
 This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
-We now turn to fleshing out these assertions, but we will only discuss (1) and (2).
-Aspect (1) is necessary even to formulate a precise statement,
-and aspect (2) uses results --- notably the higher Kac-Moody algebras --- that we've already encountered in this survey.
-Spacetime symmetries involve similar tools and ideas, albeit in a modified form, much like similarities between studying the Virasoro algebra and affine Lie algebras.
+We now turn to fleshing out these assertions.
 
@@
 
-%\subsubsection{Twisted superconformal symmetry}
-%
-%\owen{I'm now pretty lost in how this section discusses evidence for Seiberg duality.}
-%
-%A superconformal algebra is a simple super Lie algebra which contains both the ordinary algebra of infinitesimal conformal transformations and the super Lie algebra of supertranslations.
-%It is a basic fact of life that all (super)conformal algebras in dimensions $\geq 3$ are finite-dimensional.
-%Being a superconformal theory means that the theory admits a symmetry by a particular superconformal algebra---it is, generally speaking, a very rigid condition on a theory. 
-%
-%The (complexified) $\cN=1$ superconformal in four-dimensions is $\sl(4|1)$.
-%This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
-%%The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
-%Inside of this algebra is the Cartan generator $\Delta$ of which is an infinitesimal generator for scaling transformations in~$\RR^4$.
-%
-%Fix the same square-zero supercharge $\cQ$ inside of the four-dimensional $\cN=1$ supersymmetry algebra which we use to define the holomorphic twists of Seiberg dual gauge theories. 
-%Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
-%There is a quasi-isomorphism of dg Lie algebras
-%\[
-%\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) ,
-%\]
-%see \cite{SWsuco}, for example.
-%So, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ is guaranteed to act on the holomorphically twisted theory. 
-%In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
-%The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
-%where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an $SL(3)$-homogenous space.
-%(In a moment we will discuss how all holomorphic vector fields act on the theories.)
-%Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator 
-%\beqn
-%\Delta^{hol} = z_1 \del_{z_1} + z_2 \del_{z_2},
-%\eeqn 
-%which is simply the holomorphic Euler vector field.  
-%We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
-%
-%Let's consider just a free theory consisting of a single chiral multiplet, for the moment.
-%Here, the $R$-symmetry group is $U(1)$.
-%The holomorphic supercharges breaks the $SO(4;\C)$ symmetry down to the group $MU(2)$, a double cover of $U(2)$.
-%To perform the twist of a theory there are always two steps: the first is to `twist' the fields of the theory using the $R$-symmetry and the second is to deform the action by the supercharge $\cQ$.
-%To have a consistent data to twist, one usually imposes the condition that with respect to the twisted $R$-symmetry action the supercharge $Q$ is invariant.
-%The odd part of the four-dimensional $\cN = 1$ algebra is given by 
-%\beqn
-%S_+ \otimes W \oplus S_- \otimes W^*
-%\eeqn
-%where $W \cong \C$ is just a one-dimensional vector space and $S_{\pm}$ are the positive and negative semi-chiral spin representations of $\lie{so}(4;\C)$.
-%We will take the square-zero supercharge to live in $\cQ \in S_+ \otimes W$.
-%As an $MU(2)$ representation one has $S_+ \cong \det(L)^{+1/2} \oplus \det(L)^{-1/2}$.
-%Thus, if $\cQ$ lies in the first summand, in order to make $\cQ$-invariant we must twist by the condition that $W$ has weight $-1/2$ under the $R$-symmetry.
-%We will fix this twisting data.
-%
-%The basic components of the chiral multiplet is a pair of bosons $(\phi,\Bar{\phi})$, and a pair of fermions $(\psi_+, ,\psi_-)$ where $\psi_{+}$ takes values in $S_+$ and $\psi_-$ takes values in $S_-$.
-%For a free theory, we may assign any $R$-charge to $\psi_+$ and this determines the $R$-charges of all remaining fields. 
-%For example, if the $R$-charge of $\psi_+$ is $r$ then the $R$-charge of $\phi$ is $r+1$, the $R$-charge of $\psi_-$ is $-r$, and the $R$-charge of $\Bar{\phi}$ is $-r - 1$. 
-%
-%If we twist using the data where $\cQ$ is invariant, then the particular choice of $r$ will dictate how the holomorphic scaling operator $\Delta^{hol}$ acts on the theory.
-%One finds that the holomorphic twist of the free chiral theory (which is just a single quark in the above terminology) has fundamental field
-%\[
-%Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2}) 
-%\] 
-%where $K$ denotes the holomorphic canonical bundle.
-%Of course, the canonical bundle on $\C^2$ is trivializable, so we obtain a theory with isomorphic space of fields for any choice of $r$; what changes is how the twisted superconformal symmetry algebra $\lie{sl}(3)$ acts.
-%
-%
-%Now, let's consider the electric theory.
-%We assume that the fermions in the quarks and anti-quark multiplets have the same $R$-charges.
-%If this $R$-charge is $r$, then the twisted quarks and anti-quarks take the form
-%\[
-%Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q) \quad\text{and}\quad Q^\dagger \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q^*)
-%\]
-%where $V_Q \cong \C^{NF}$.
-%In the untwisted theory the value $r$ is fixed by the condition that the $R$-symmetry is anomaly-free.
-%In the twisted theory, the value of $r$ is fixed by the condition that the action by the holomorphic scaling operator is anomaly-free.
-%This anomaly comes from a one-loop diagram with a single vertex labeled by $\Delta^{hol}$, and it leads to the constraint 
-%\beqn
-%N + F r = 0 .
-%\eeqn
-%In other words, $r = - N / F$. 
-%This condition matches the corresponding condition for $R$-symmetry to be anomaly-free in the untwisted theory. 
-%On the magnetic side the condition is $r = N/F - 1$.
-%
-%In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories are expected to flow to the same superconformal fixed point in the infrared limit. 
-%This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
-%(Note that it is preserved under swapping $N \leftrightarrow F-N$.)
-%It would be interesting to explore how it appears from the point of view of holomorphic QCD. 
-%
-%<<<<<<< HEAD
-%\begin{cor}
-%{\em Divergence-free} holomorphic vector fields are a symmetry at the quantum level for any values of $F$ and~$N$.
-%Only when $F = 3N$ do {\em all} holomorphic vector fields lift to a symmetry lifts at the quantum level.
-%\end{cor}
-%=======
-%>>>>>>> 8d2b48799f0de9991260e8451b5287400da94e98
+\subsubsection{Twisted superconformal symmetry}
+
+\owen{I'm now pretty lost in how this section discusses evidence for Seiberg duality.}
+
+A superconformal algebra is a simple super Lie algebra which contains both the ordinary algebra of infinitesimal conformal transformations and the super Lie algebra of supertranslations.
+It is a basic fact of life that all (super)conformal algebras in dimensions $\geq 3$ are finite-dimensional.
+Being a superconformal theory means that the theory admits a symmetry by a particular superconformal algebra---it is, generally speaking, a very rigid condition on a theory.
+
+The (complexified) $\cN=1$ superconformal in four-dimensions is $\sl(4|1)$.
+This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
+%The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
+Inside of this algebra is the Cartan generator $\Delta$ of which is an infinitesimal generator for scaling transformations in~$\RR^4$.
+
+Fix the same square-zero supercharge $\cQ$ inside of the four-dimensional $\cN=1$ supersymmetry algebra which we use to define the holomorphic twists of Seiberg dual gauge theories. 
+Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
+There is a quasi-isomorphism of dg Lie algebras
+\[
+\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) ,
+\]
+see \cite{SWsuco}, for example.
+So, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ is guaranteed to act on the holomorphically twisted theory. 
+In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
+The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
+where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an $SL(3)$-homogenous space.
+(In a moment we will discuss how all holomorphic vector fields act on the theories.)
+Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator 
+\beqn
+\Delta^{hol} = z_1 \del_{z_1} + z_2 \del_{z_2},
+\eeqn 
+which is simply the holomorphic Euler vector field.  
+We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
+
+Let's consider just a free theory consisting of a single chiral multiplet, for the moment.
+Here, the $R$-symmetry group is $U(1)$.
+The holomorphic supercharges breaks the $SO(4;\C)$ symmetry down to the group $MU(2)$, a double cover of $U(2)$.
+To perform the twist of a theory there are always two steps: the first is to `twist' the fields of the theory using the $R$-symmetry and the second is to deform the action by the supercharge $\cQ$.
+To have a consistent data to twist, one usually imposes the condition that with respect to the twisted $R$-symmetry action the supercharge $Q$ is invariant.
+The odd part of the four-dimensional $\cN = 1$ algebra is given by 
+\beqn
+S_+ \otimes W \oplus S_- \otimes W^*
+\eeqn
+where $W \cong \C$ is just a one-dimensional vector space and $S_{\pm}$ are the positive and negative semi-chiral spin representations of $\lie{so}(4;\C)$.
+We will take the square-zero supercharge to live in $\cQ \in S_+ \otimes W$.
+As an $MU(2)$ representation one has $S_+ \cong \det(L)^{+1/2} \oplus \det(L)^{-1/2}$.
+Thus, if $\cQ$ lies in the first summand, in order to make $\cQ$-invariant we must twist by the condition that $W$ has weight $-1/2$ under the $R$-symmetry.
+We will fix this twisting data.
+
+The basic components of the chiral multiplet is a pair of bosons $(\phi,\Bar{\phi})$, and a pair of fermions $(\psi_+,\psi_-)$ where $\psi_{+}$ takes values in $S_+$ and $\psi_-$ takes values in $S_-$.
+For a free theory, we may assign any $R$-charge to $\psi_+$ and this determines the $R$-charges of all remaining fields. 
+For example, if the $R$-charge of $\psi_+$ is $r$ then the $R$-charge of $\phi$ is $r+1$, the $R$-charge of $\psi_-$ is $-r$, and the $R$-charge of $\Bar{\phi}$ is $-r - 1$.
+
+If we twist using the data where $\cQ$ is invariant, then the particular choice of $r$ will dictate how the holomorphic scaling operator $\Delta^{hol}$ acts on the theory.
+One finds that the holomorphic twist of the free chiral theory (which is just a single quark in the above terminology) has fundamental field
+\[
+Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2}) 
+\] 
+where $K$ denotes the holomorphic canonical bundle.
+Of course, the canonical bundle on $\C^2$ is trivializable, so we obtain a theory with isomorphic space of fields for any choice of $r$; what changes is how the twisted superconformal symmetry algebra $\lie{sl}(3)$ acts.
+
+Now, let's consider the electric theory.
+We assume that the fermions in the quarks and anti-quark multiplets have the same $R$-charges.
+If this $R$-charge is $r$, then the twisted quarks and anti-quarks take the form
+\[
+Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q) \quad\text{and}\quad Q^\dagger \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q^*)
+\]
+where $V_Q \cong \C^{NF}$.
+In the untwisted theory the value $r$ is fixed by the condition that the $R$-symmetry is anomaly-free.
+In the twisted theory, the value of $r$ is fixed by the condition that the action by the holomorphic scaling operator is anomaly-free.
+This anomaly comes from a one-loop diagram with a single vertex labeled by $\Delta^{hol}$, and it leads to the constraint 
+\beqn
+N + F r = 0 .
+\eeqn
+In other words, $r = - N / F$. 
+This condition matches the corresponding condition for $R$-symmetry to be anomaly-free in the untwisted theory. 
+On the magnetic side the condition is $r = N/F - 1$.
+
+In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories are expected to flow to the same superconformal fixed point in the infrared limit. 
+This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
+(Note that it is preserved under swapping $N \leftrightarrow F-N$.)
+It would be interesting to explore how it appears from the point of view of holomorphic QCD.
+
+\begin{cor}
+{\em Divergence-free} holomorphic vector fields are a symmetry at the quantum level for any values of $F$ and~$N$.
+Only when $F = 3N$ do {\em all} holomorphic vector fields lift to a symmetry lifts at the quantum level.
+\end{cor}
 
@@
 %
+
 %In the holomorphic twist as a classical theory,
@@
 
+\subsubsection{The special case of $SU(2)$ SQCD}
+
+\owen{I like the idea of analyzing a special case, but I'm not sure what lesson the reader is supposed to learn.}
+
+Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
+In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
+\beqn
+(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
+\eeqn
+This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.
+
+On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
+\beqn
+V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
+\eeqn
+There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
+Again the flavor symmetry group admits an enhancement to $SU(2F)$.
+
+Let's further consider some special cases for small values of flavors.
+
+$\bullet \ul{F=2}$. \brian{I'm confused}
+
+$\bullet \ul{F=3}$. 
+In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
+\beqn
+(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
+\eeqn
+In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
+If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
+\beqn
+W = \frac16 \Phi \wedge \Phi \wedge \Phi .
+\eeqn
+We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
+The critical locus of $W$ is simply the space of solutions to the equation
+\beqn
+\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
+\eeqn
+This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
+
+$\bullet \ul{F=4}$.
+This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
+On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
+On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
+
+We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
+For $F \geq 4$ the
+
+%A duality 
+%
+%The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
+%The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
+%For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
+
 \subsection{A second pass at holomorphic Seiberg duality}
@@
 Exploring these possibilities would likely lead to substantially deeper understanding of holomorphic Seiberg duality.
-One motivation for these suggestions comes from work on two-dimensional (0,2)-theories, such as \cite{DeduGuk, EagLocSha}.
 

### 2023-01-28 draft.tex
added a small remark in section 4

--- 2023-01-18 draft.tex
@@
 Their local structure encompasses the behavior we saw in the preceding section, where $E_d$ algebras captured topological field theories on $\RR^d$ and $\PDisc_d$ algebras captured holomorphic field theories on~$\CC^d$.
-Factorization algebras allow one to work on smooth manifolds, and complex manifolds, more generally;
-their global behavior encompasses constructions like Hochschild homology and conformal blocks.
+Factorization algebras allow one to work on smooth or complex manifolds and hence bring in global aspects of geometry.
+Their global behavior encompasses constructions like Hochschild homology (for $E_1$ algebras extended as factorization algebras on $S^1$) and conformal blocks (for $\PDisc_1$ algebras extended as factorization algebras to Riemann surfaces).
 We will then sketch the main theorem of \cite{CG2}, 
@@
 particularly in the setting of the geometric Langlands program.
-Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of  manifolds,
+Francis, Gaitsgory, and Lurie ported the spirit of this notion into the setting of manifolds,
 developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
@@
 Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
+These approaches share a common spirit but have important technical differences.
+A detailed comparison between the versions for locally constant factorization algebras exists \owen{good refs?},
+but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
+(See, however, section \owen{fill out } of \cite{HenKap} for important steps in that direction.)
 \end{rmk}

### 2023-06-01 highervertexops.tex
defs for vertexops

\documentclass[11pt]{amsart}

\usepackage{macros, setspace}

\spacing{1.1}

\usepackage{parskip}
\setlength{\parindent}{18pt}
\setlength{\parindent}{0cm}

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
\title{Holomorphic field theories and higher algebra}

\def\g{{\mathfrak g}}
\def\U{{\rm U}}
\def\mc{\mathcal}
\def\mcol{\, | \,}
\def\ot{\otimes}
\def\Disj{\operatorname{Disj}}
\def\Open{\operatorname{Open}}
\def\Vect{\operatorname{Vect}}
\def\jou{{\mathtt{j}}}
\def\bgamma{{\mathbf{\gamma}}}
\def\bbeta{{\mathbf{\beta}}}
\def\CDO{{\cC\cD}}
\def\SU{{\rm SU}}
\def\sfa{\mathsf{a}}
\def\del{\partial}
\def\til{\Tilde}
\def\Sol{\text{Sol}}
\def\Spec{\text{Spec}}
\def\C{{\mathbb{C}}}
\def\RHom{{\rm RHom}}

\renewcommand{\op}{\operatorname}
\def\lie#1{\ensuremath{\mathfrak{#1}}}

\def\brian#1{{\textcolor{blue!65!red}{BW: {#1}}}}
\def\owen#1{{\textcolor{violet!65!black}{OG: {#1}}}}

%\usepackage[upint]{stix}

\begin{document}

The goal here is to record higher-dimensional analogs of the ingredients for defining a {\em vertex operator}. We do not aspire (yet!) to give the higher-dimensional version of a vertex algebra.

Let $\cO_d$ denote a (preferably ``small'' or convenient) model of the derived sections of the structure sheaf (of {\em algebraic} functions) on the punctured affine space $\mathring{\AA}^d$.
When $d=1$, it is the Laurent polynomials~$\CC[z,z^{-1}]$.

Let $\widehat{\cO}_d$ denote a (preferably ``small'' or convenient) model of the derived sections of the structure sheaf (of {\em algebraic} functions) on the punctured formal disk $\mathring{\DD}^d$.
When $d=1$, it is the Laurent series $\CC((z))$.

Let $\cD_d$ denote a model of the derived ``distributions'' on the punctured affine space $\mathring{\AA}^d$. It is the linear dual to~$\cO_d$.
When $d=1$, it is $\CC[[z,z^{-1}]]$, which is a notation that indicates infinite formal sums in both directions. (This notation is poor because it suggests an algebra, but it is not.)
The pairing is via the residue pairing.

Let $\widehat{\cD}_d$ denote a model of the derived ``distributions'' on the punctured formal disk $\mathring{\DD}^d$. It is the linear dual to~$\widehat{\cO}_d$.
When $d=1$, it is again $\CC((z))$, via the residue pairing.

Let $V$ be a cochain complex, which we will treat as a {\em state space}.

A {\em field} is an element of 
\[
\RHom(V \otimes \widehat{\cO}_d, V) \cong \RHom(V, V \widehat{\otimes} \widehat{\cD}_d).
\]
When $d=1$, this becomes the usual version $\Hom(V, V((z)))$.

Note that a field can be seen as a distribution that eats a function on the formal disk and gives a linear operator on $V$ because
\[
\RHom(V \otimes \widehat{\cO}_d, V) \cong \RHom(\widehat{\cO}_d, \RHom(V,V)).
\]
This corresponds to a traditional notion of a ``quantum field'' as an operator-valued distribution.

For notation, if $z$ denotes a coordinate $(z_1,\ldots,z_d)$ for the formal disk $\DD^d$,
we write $a(z)$ for a field using that coordinate.

Given two fields $a(z)$ and $b(w)$, we have a commutator $[a(z),b(w)]$ that eats a

\end{document}

### 2023-07-27 highervertexops.tex
short note

@@
 
-The goal here is to record higher-dimensional analogs of the ingredients for defining a {\em vertex operator}. We do not aspire (yet!) to give the higher-dimensional version of a vertex algebra.
+The goal here is to record higher-dimensional analogs of the ingredients for defining a {\em field} in a holomorphic theory (i.e., a higher-dimensional {\em vertex operator}).
+We do not aspire (yet!) to give the higher-dimensional version of a vertex algebra.
 
-Let $\cO_d$ denote a (preferably ``small'' or convenient) model of the derived sections of the structure sheaf (of {\em algebraic} functions) on the punctured affine space $\mathring{\AA}^d$.
-When $d=1$, it is the Laurent polynomials~$\CC[z,z^{-1}]$.
+{\it Notations for spaces, functions, and distributions}
 
-Let $\widehat{\cO}_d$ denote a (preferably ``small'' or convenient) model of the derived sections of the structure sheaf (of {\em algebraic} functions) on the punctured formal disk $\mathring{\DD}^d$.
-When $d=1$, it is the Laurent series $\CC((z))$.
+Let $\cO_d$ denote a (preferably ``small'' or convenient) model of the derived sections of the structure sheaf (of {\em algebraic} functions) on the punctured affine space $\mathring{\AA}^d$.\\
+{\tiny When $d=1$, it is the Laurent polynomials~$\CC[z,z^{-1}]$.}
 
-Let $\cD_d$ denote a model of the derived ``distributions'' on the punctured affine space $\mathring{\AA}^d$. It is the linear dual to~$\cO_d$.
-When $d=1$, it is $\CC[[z,z^{-1}]]$, which is a notation that indicates infinite formal sums in both directions. (This notation is poor because it suggests an algebra, but it is not.)
+Let $\widehat{\cO}_d$ denote a (preferably ``small'' or convenient) model of the derived sections of the structure sheaf (of {\em algebraic} functions) on the punctured formal disk $\mathring{\DD}^d$.\\
+{\tiny When $d=1$, it is the Laurent series $\CC((z))$.}
+
+Let $\cD_d$ denote a model of the derived ``distributions'' on the punctured affine space $\mathring{\AA}^d$. It is the linear dual to~$\cO_d$.\\
+{\tiny When $d=1$, it is $\CC[[z,z^{-1}]]$, which is a notation that indicates infinite formal sums in both directions.
 The pairing is via the residue pairing.
+(This notation is poor because it suggests an algebra, but it is not.)}
 
-Let $\widehat{\cD}_d$ denote a model of the derived ``distributions'' on the punctured formal disk $\mathring{\DD}^d$. It is the linear dual to~$\widehat{\cO}_d$.
-When $d=1$, it is again $\CC((z))$, via the residue pairing.
+Let $\widehat{\cD}_d$ denote a model of the derived ``distributions'' on the punctured formal disk $\mathring{\DD}^d$. It is the linear dual to~$\widehat{\cO}_d$.\\
+{\tiny When $d=1$, it is again $\CC((z))$, via the residue pairing.}
+
+There are analogs of these constructions for products of affine or formal spaces with the fat diagonal removed.
+We will write here the two-variable version.
+
+Consider the space 
+\[
+\mathring{\AA}^{d}[2]= (\AA^d \times \AA^d) - \Delta_f{[2]}, 
+\]
+where $\Delta[2]_f$ denotes the fat diagonal
+\[
+\AA^d \times \{0\} \cup \{0\} \times \AA^d \cup \AA^{2d}_\Delta
+\]
+with
+\[
+ \AA^{2d}_\Delta = \{ (x,y) \in \AA^d \times \AA^d \; : \; x \neq y\}.
+\]
+Let $\mathring{\DD}^d[2]$ denote the corresponding formal space.
+
+Let $\cO_d{[2]}$ denote a model of the derived sections of the structure sheaf (of {\em algebraic} functions) on $\mathring{\AA}^d[2]$.
+
+Let $\widehat{\cO}_d{[2]}$ denote a model of the derived sections of the structure sheaf (of {\em algebraic} functions) on $\mathring{\DD}^d[2]$.
+
+Let $\cD_d[2]$ denote a model of the derived distributions on $\mathring{\AA}^d[2]$.
+
+Let $\widehat{\cD}_d[2]$ denote a model of the derived distributions on $\mathring{\DD}^d[2]$.
+\newpage
+
+{\it Operators}
 
@@
 \]
-When $d=1$, this becomes the usual version $\Hom(V, V((z)))$.
+When $d=1$, this definition becomes the usual version: $\Hom(V, V((z)))$.
 
@@
 
-Given two fields $a(z)$ and $b(w)$, we have a commutator $[a(z),b(w)]$ that eats a
+Given two fields $a(z)$ and $b(w)$, we have a commutator $[a(z),b(w)]$ that eats a function in $\widehat{\cO}_d[2]$ and returns an endomorphism of~$V$.
+
+Two fields are {\em mutually local} if there exists a nonnegative exponent $N \in \NN^d$ such that $(z-w)^N[a(z),b(w)]$ is cohomological to zero (i.e., it is exact).
+
+\owen{I suspect there's something better to say here, informed by your work with Nik. I'm least happy with this definition.}
+
+{\it Free field realizations}
+
+We want to show that the $L_\infty$-action of a higher Kac-Moody algebra on the state space of a free theory is via mutually local fields.
 

### 2023-07-28 highervertexops.tex
tiny additions

@@
 
-Two fields are {\em mutually local} if there exists a nonnegative exponent $N \in \NN^d$ such that $(z-w)^N[a(z),b(w)]$ is cohomological to zero (i.e., it is exact).
+Two fields are {\em mutually local} if there exists a natural number $N \in \NN$ and an element $f(z,w)$ of the ideal $(z_i-w_i)_{i =1}^d \subset \widehat{\cO}(\DD^d\times \DD^d)$ such that $f(z,w)[a(z),b(w)]$ is cohomologous to zero (i.e., it is exact).
 
+This condition recovers the usual notion of locality after passing to cohomology. 
 \owen{I suspect there's something better to say here, informed by your work with Nik. I'm least happy with this definition.}
+
+It is possible to formulate a representative of the ``delta function'' and one can hope that the usual formulas (e.g., describing the structure of the singular parts of commutators or OPEs) have analogs up to exact terms.
 

### 2023-08-04 highervertexops.tex
htpy data

@@
 \def\RHom{{\rm RHom}}
+%\def\sfR{\mathsf{R}}
+%\def\sfA{\mathsf{A}}
 
@@
 
+\newpage
+
+\section{A model for punctured affine space}
+
+Let $\sfR$ be the commutative algebra generated by variables $z_i,\lambda_i,i=1,2$ subject to the relation $\sum_i z_i \lambda_i = 1$.
+Recall that $\sfA$ is the graded commutative algebra freely generated over $\sfR$ by a degree $+1$ element $\omega$.
+Thus $\sfA = \sfR \oplus \sfR \omega [-1]$.
+
+The algebra $\sfR$ is naturally an $SU(2)$ representation where the $(z_1,z_2)$ transforms in the fundamental representation and $(\lambda_1,\lambda_2)$ transforms in the anti-fundamental representation.
+Explicitly, the raising and lowering operators are
+\beqn
+f = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2}, \quad e = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1} .
+\eeqn
+
+Let $V_{a,b} \subset \C[z_i,\lambda_i]$ be the space of all polynomials which are homogenous of order $a$ in the variables $z_i$ and homogenous of order $b$ in the variables $\lambda_i$.
+Consider the Laplacian operator
+\beqn
+\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}
+\eeqn
+and denote $H_{a,b} \subset V_{a,b}$ the harmonic polynomials of bidegree $(a,b)$.
+There is an orthogonal decomposition 
+\begin{align*}
+V_{a,b} & = H_{a,b} \oplus |(z,\lambda)|^2 V_{a-1,b-1} \\
+& = H_{a,b} \oplus |(z,\lambda)|^2 H_{a-1,b-1} \oplus |(z,\lambda)|^4 H_{a-2,b-2} \oplus \cdots 
+\end{align*}
+where $|(z,\lambda)|^2 = z_1 \lambda_1 + z_2 \lambda_2$.
+In particular, after imposing the relation $|(z,\lambda)|^2 = 1$ we see that every element in $\sfR$ can be written as a sum of elements in the images of $H_{a,b}$ under the natural projection $p \colon \C[z_i,\lambda_i] \to \sfR$.
+We therefore have a decomposition $\sfR = \oplus \sfR_{a,b}$ where $\sfR_{a,b} = p(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
+
+Each $\sfR_{a,b}$ is isomorphic to the irreducible $(a+b+1)$-dimensional $SU(2)$ representation where the highest weight vector is
+\beqn
+z_1^a \lambda_2^b \in \sfR_{a,b} .
+\eeqn
+A basis for $\sfR_{a,b}$ is obtained as
+\beqn
+\{z_1^a \lambda_2^b, f (z_1^a \lambda_2^b), f^2 (z_1^a \lambda_2^b), \ldots, f^{a+b} (z_1^a \lambda_2^b) \} .
+\eeqn
+Note that the $\dbar$-operator acts on the subspaces $\sfR_{a,b}$ in the following way
+\beqn
+\dbar \colon \sfR_{a,b} \to \sfR_{a+1,b-1} \omega .
+\eeqn
+
+\begin{eg}
+The space $\sfR_{a,0}$ consists of polynomials in $z_1,z_2$ of homogenous degree~$a$.
+The space $\sfR_{0,b}$ consists of polynomials in $\lambda_1,\lambda_2$ of homogenous degree $b$.
+The space $\sfR_{1,1}$ is three-dimensional with a basis given by
+\beqn
+z_1 \lambda_2, z_1 \lambda_1 - z_2 \lambda_2, z_2 \lambda_1 .
+\eeqn
+\end{eg}
+
+Define the involution $\Bar{(-)}$ on $\sfR$ by $\zbar_i = \lambda_i$ and consider the inner product on $\sfR$ given by the formula
+\beqn
+\<a,b\> = \op{Res} \left(\Bar{a} b \omega \right).
+\eeqn
+This inner product is $SU(2)$ invariant.
+
+\begin{eg}
+An orthonormal basis for $\sfR_{a,0}$ is
+\beqn
+e_m^{(a,0)} = \sqrt{\frac{(a+1)!}{m! (a-m)!}} z_1^m z_2^{a-m} , \quad m = 0,1,\ldots,a .
+\eeqn
+Likewise, an orthonormal basis for $\sfR_{0,b}$ is
+\beqn
+e_m^{(0,b)} = \sqrt{\frac{(a+1)!}{m! (a-m)!}} (-\lambda_1)^m \lambda_2^{a-m} , \quad m = 0,1,\ldots,b .
+\eeqn
+An orthonormal basis for $\sfR_{1,1}$ is
+\beqn
+e_2^{(1,1)} = \sqrt{6} z_1 \lambda_2, \quad e_1^{(1,1)} = \sqrt{3}(z_1 \lambda_1 - z_2 \lambda_2), \quad e_0^{(1,1)} = \sqrt{6} z_2 \lambda_1 .
+\eeqn
+\end{eg}
+
+Recall that 
+\beqn
+\Omega^{0,\bu}_b (S^3) = \big(\C[w_i,\Bar{w}_i, \xi_i] \slash (w_i \Bar{w}_i = 1, w_i \xi_i = 0), \quad \dbar_b = \xi_i \del_{\Bar{w}_i} \big) .
+\eeqn
+
+\begin{prop}
+There is a (dense) $SU(2)$-equivariant isomorphism of commutative dg algebras
+\beqn
+\Phi \colon \sfA_2 \to \Omega^{0,\bu}_b (S^3) 
+\eeqn
+defined by $\Phi(z_i) = w_i$, $\Phi(\lambda_i) = \Bar{w}_i$, and $\Phi (\omega) = \ep_{ij} \Bar{w}_i \xi_j \define \epsilon$.
+\end{prop}
+\begin{proof}
+In fact $\Phi$ maps the subspace $\sfR_{a,b}$ isomorphically to $\cH_{a,b}$ where $\cH_{a,b} \subset \Omega^{0,\bu}_b (S^3)$ is the space of harmonic polynomials which are of bidegree $(a,b)$ in the variables $(w_i,\Bar{w}_j)$.
+To see that the differentials are compatible we observe that
+\beqn
+\Phi(\dbar(\lambda_i)) = - \Phi(\ep_{ij} z_j \omega) = - \ep_{ij} w_j \epsilon = \xi_i = \dbar_b \Phi (\lambda_i) .
+\eeqn
+\end{proof}
+
+\subsection{Homotopy data}
+
+Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the obvious $SU(2)$ equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA_2$, $p \colon \sfA_2 \to \sfH_2$.
+
+\begin{rmk}
+The inclusion $i$ is a map of commutative dg algebras.
+Note that $p$ is not a map of algebras; for example
+\beqn
+p(z_1 \lambda_1) = \frac12
+\eeqn
+as $z_1 \lambda_1$ admits an orthogonal decomposition
+\beqn
+z_1 \lambda_1 = \frac12 (z_1 \lambda_1 - z_2 \lambda_2) + \frac12 .
+\eeqn
+\end{rmk}
+
+Define the degree $-1$ operator 
+\beqn
+H \colon \sfA_2 \to \sfA_2 [-1]
+\eeqn
+by the condition that $H|_{\sfR_{0,b}\omega} = 0$ and 
+\beqn
+H(z_1^a \lambda_2^b) = \frac{1}{(b+1)} z_1^{a-1} \lambda_2^{b+1} .
+\eeqn
+Extend this to all of $\sfA_2$ using $SU(2)$ equivariance.
+Note that for $a > 0$ this is an operator 
+\beqn
+H \colon \sfR_{a,b} \omega \to \sfR_{a-1,b+1} .
+\eeqn
+
+\begin{prop}
+The triple $(p,i,H)$ defines a special deformation retract between $\sfA$ and its cohomology.
+\end{prop}
+
+\section{Distributions on punctured affine space}
+
+The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
+\beqn
+\sfR = \C[z_i,\lambda_i] \slash (z_i \lambda_i = 1) .
+\eeqn
+Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by $z_1,z_2$.
+So I think
+\beqn
+\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (z_i \lambda_i) .
+\eeqn
+
+Let $\Hat{A}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
+The cohomology of $(\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
+
 \end{document}

### 2023-08-14 highervertexops.tex
working through your computations on A

--- 2023-07-28 highervertexops.tex
@@
 \begin{document}
+
+\section{Overview of definitions and goalds}
 
@@
 
+\newpage
+
+\section{A model for punctured affine space}
+
+We want a convenient and explicit model for the commutative algebra-up-to-homotopy $\RR \Gamma(\mathring{\AA}^2)$.
+Our approach follows the approach of Keyou Zeng but is written in a more algebraic style.
+We quickly recall his results before introducing our version.
+
+\subsection{Zeng's hyperplane approach}
+
+The punctured affine space $\mathring{\AA}^2$ contains a natural real hypersurface given by the unit sphere $S^3 = \{|w_1|^2 + |w_2|^2 = 1\}$, with the $w_i$ being holomorphic coordinates on $\AA^2$.
+The theory of CR manifolds provides an analogue of the Dolbeault complex, 
+and Zeng works with polynomial functions and forms within it:
+\beqn
+\Omega^{0,\bu}_b (S^3) = \big(\C[w_i,\Bar{w}_i, \xi_i] \slash (w_i \Bar{w}_i = 1, w_i \xi_i = 0) \big) .
+\eeqn
+with differential $\dbar_b = \xi_i \del_{\Bar{w}_i}$.
+\owen{I'm not sure why it must provide a model for $\RR \Gamma(\mathring{\AA}^2)$, but I give some heuristic reasoning. Maybe Zeng gives a reference or proof?}
+Note that one can see that polynomials in the coordinates, both holomorphic $w_i$ and antiholomorphic $\Bar{w}_i$, span the complex-valued polynomial functions on $\CC^2 \cong \RR^4$.
+Their restriction to the unit-sphere $S^3$ wholly determines their behavior as functions on affine space, and hence also on punctured affine space. 
+The elements $\xi_i$ correspond to $d\Bar{w}_i$ in the Dolbeault complex of punctured affine space.
+The differential $\dbar_b$ then imposes the constraint, in degree zero, that these functions be holomorphic,
+and its image is the image of $\dbar$ intersected with polynomial  forms in $d \Bar{w}_i$.
+Thus the cohomology of this complex $\Omega^{0,\bu}_b (S^3)$ is a model for $\RR \Gamma(\mathring{\AA}^2)$.
+
+Zeng analyzes this complex using the natural $SU(2)$-action on the 3-sphere, which is the restriction of the fundamental representation to this hypersurface.
+More accurately, $SU(2)$ acts on the linear span of $w_1$ and $w_2$ by the fundamental representation and on the linear span of $\Bar{w}_1$ and $\Bar{w}_2$ by the conjugate (or anti-fundamental) representation,
+and it respects the relation $\sum_i w_i \Bar{w}_i = 1$ and the differential $\dbar_b$, 
+so the action descends to the whole complex.
+One can decompose the complex into irreducible representations, 
+allowing one to identify the cohomology as a subcomplex.
+This construction yields an explicit deformation retraction of the $\dbar_b$-complex onto its cohomology.
+
+\subsection{An algebraic version}
+
+We mimic the construction but replace the role of $SU(2)$ by $SL(2)$.
+\owen{I mostly left things alone below, except for removing typos or modestly rewording things I found confusing.}
+
+Let $\sfR$ be the commutative algebra generated by variables $z_i,\lambda_i,i=1,2$ subject to the relation $\sum_i z_i \lambda_i = 1$.
+Let $\sfA$ be the graded commutative algebra freely generated over $\sfR$ by a degree $+1$ element $\omega$.
+Thus $\sfA = \sfR \oplus \sfR \omega [-1]$.
+Equip it with the differential
+\[
+\dbar(z_i) = 0 \quad\text{and}\quad \dbar(\lambda_i) = \epsilon_{ij} z_j \omega
+\]
+extended as a derivation.
+That is, $\dbar(\lambda_1) = z_2 \omega$ and $\dbar(\lambda_1) = -z_1 \omega$.
+
+We view the $z_i$ as the $w_i$ in Zeng's complex, and the $\lambda_i$ as the $\Bar{w}_i$.
+The element $\omega$ corresponds to $\Bar{w}_1\xi_2 - \Bar{w}_2\xi_1$.
+In fact, the key result is the following.
+
+\begin{prop}
+There is a $SU(2)$-equivariant isomorphism of commutative dg algebras
+\beqn
+\Phi \colon \sfA_2 \to \Omega^{0,\bu}_b (S^3) 
+\eeqn
+defined by $\Phi(z_i) = w_i$, $\Phi(\lambda_i) = \Bar{w}_i$, and $\Phi (\omega) = \ep_{ij} \Bar{w}_i \xi_j$.
+\end{prop}
+
+The algebra $\sfR$ is naturally an $SL(2)$ representation where the $(z_1,z_2)$ transform in the fundamental representation and $(\lambda_1,\lambda_2)$ transforms in the dual (or contragredient) representation.
+Explicitly, the lowering and raising operators are
+\beqn
+f = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2}, \quad e = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1} .
+\eeqn
+These actions determine an $SL(2)$-action on the space of all polynomials $\C[z_i,\lambda_i]$,
+which breaks up into a direct sum over the subspaces $V_{a,b}$ of polynomials that are homogenous of order $a$ in the variables $z_i$ and homogenous of order $b$ in the variables~$\lambda_i$.
+
+Consider the Laplacian operator
+\beqn
+\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}.
+\eeqn
+Let $H_{a,b} \subset V_{a,b}$ denote the harmonic polynomials of bidegree $(a,b)$.
+An example of a harmonic polynomial is $z_1^a \lambda_2^b$.
+A direct computation shows that there is a direct sum decomposition of representations
+\begin{align*}
+V_{a,b} & = H_{a,b} \oplus |(z,\lambda)|^2 V_{a-1,b-1} \\
+& = H_{a,b} \oplus |(z,\lambda)|^2 H_{a-1,b-1} \oplus |(z,\lambda)|^4 H_{a-2,b-2} \oplus \cdots 
+\end{align*}
+(Compare with the well-known construction of spherical harmonics.)
+
+Consider now  
+\[
+|(z,\lambda)|^2 \define z_1 \lambda_1 + z_2 \lambda_2, 
+\]
+which describes the evaluation pairing. 
+It is preserved by the $SL(2)$-action, and hence we see that the canonical quotient map 
+\[
+q: \C[z_i,\lambda_i] \to R = \C[z_i,\lambda_i]/(\C[z_i,\lambda_i] = 1)
+\]
+is $SL(2)$-equivariant.
+Moreover, inside $V_{a,b}$, any multiple of $|(z,\lambda)|^2$ is annihilated by $q$,
+so $R$ is spanned by the images of $H_{a,b}$.
+Thus, there is a direct sum decomposition $\sfR = \oplus \sfR_{a,b}$ where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
+
+\begin{lem}
+Each $\sfR_{a,b}$ is isomorphic to the irreducible $SL(2)$-representation of dimension $(a+b+1)$.
+Its highest weight vector is $z_1^a \lambda_2^b \in \sfR_{a,b}$, and a basis for $\sfR_{a,b}$ is obtained as
+\beqn
+\{z_1^a \lambda_2^b, f (z_1^a \lambda_2^b), f^2 (z_1^a \lambda_2^b), \ldots, f^{a+b} (z_1^a \lambda_2^b) \} .
+\eeqn
+\end{lem}
+
+\owen{We should write out the proof.}
+
+\begin{eg}
+The space $\sfR_{a,0}$ consists of polynomials in $z_1,z_2$ of homogenous degree~$a$.
+The space $\sfR_{0,b}$ consists of polynomials in $\lambda_1,\lambda_2$ of homogenous degree $b$.
+The space $\sfR_{1,1}$ is three-dimensional with a basis given by
+\beqn
+z_1 \lambda_2, z_1 \lambda_1 - z_2 \lambda_2, z_2 \lambda_1 .
+\eeqn
+\end{eg}
+
+By direct inspection, one finds that the $\dbar$-operator is $SL(2)$-equivariant.
+It maps $\sfR_{a,b}$ to $\sfR_{a+1,b-1} \omega$.
+
+%Define the involution $\Bar{(-)}$ on $\sfR$ by $\zbar_i = \lambda_i$ and consider the inner product on $\sfR$ given by the formula
+%\beqn
+%\<a,b\> = \op{Res} \left(\Bar{a} b \omega \right).
+%\eeqn
+%This inner product is $SU(2)$ invariant.
+%
+%\begin{eg}
+%An orthonormal basis for $\sfR_{a,0}$ is
+%\beqn
+%e_m^{(a,0)} = \sqrt{\frac{(a+1)!}{m! (a-m)!}} z_1^m z_2^{a-m} , \quad m = 0,1,\ldots,a .
+%\eeqn
+%Likewise, an orthonormal basis for $\sfR_{0,b}$ is
+%\beqn
+%e_m^{(0,b)} = \sqrt{\frac{(a+1)!}{m! (a-m)!}} (-\lambda_1)^m \lambda_2^{a-m} , \quad m = 0,1,\ldots,b .
+%\eeqn
+%An orthonormal basis for $\sfR_{1,1}$ is
+%\beqn
+%e_2^{(1,1)} = \sqrt{6} z_1 \lambda_2, \quad e_1^{(1,1)} = \sqrt{3}(z_1 \lambda_1 - z_2 \lambda_2), \quad e_0^{(1,1)} = \sqrt{6} z_2 \lambda_1 .
+%\eeqn
+%\end{eg}
+
+\begin{proof}[Proof of proposition]
+In fact $\Phi$ maps the subspace $\sfR_{a,b}$ isomorphically to $\cH_{a,b}$ where $\cH_{a,b} \subset \Omega^{0,\bu}_b (S^3)$ is the space of harmonic polynomials that are of bidegree $(a,b)$ in the variables $(w_i,\Bar{w}_j)$.
+To see that the differentials are compatible we observe that
+\beqn
+\Phi(\dbar(\lambda_i)) = - \Phi(\ep_{ij} z_j \omega) = - \ep_{ij} w_j \Phi (\omega) = \xi_i = \dbar_b \Phi (\lambda_i) .
+\eeqn
+\end{proof}
+
+\subsection{Homotopy data}
+
+Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA_2$, $p \colon \sfA_2 \to \sfH_2$.
+
+\begin{rmk}
+The inclusion $i$ is a map of commutative dg algebras.
+Note that $p$ is not a map of algebras; for example
+\beqn
+p(z_1 \lambda_1) = \frac12
+\eeqn
+as $z_1 \lambda_1$ admits an orthogonal decomposition
+\beqn
+z_1 \lambda_1 = \frac12 (z_1 \lambda_1 - z_2 \lambda_2) + \frac12 .
+\eeqn
+\end{rmk}
+
+Define the degree $-1$ operator 
+\beqn
+H \colon \sfA_2 \to \sfA_2 [-1]
+\eeqn
+by the condition that $H|_{\sfR_{0,b}\omega} = 0$ and 
+\beqn
+H(z_1^a \lambda_2^b) = \frac{1}{(b+1)} z_1^{a-1} \lambda_2^{b+1} .
+\eeqn
+Extend this to all of $\sfA_2$ using $SU(2)$ equivariance.
+Note that for $a > 0$ this is an operator 
+\beqn
+H \colon \sfR_{a,b} \omega \to \sfR_{a-1,b+1} .
+\eeqn
+
+\begin{prop}
+The triple $(p,i,H)$ defines a special deformation retract between $\sfA$ and its cohomology.
+\end{prop}
+
+\section{Distributions on punctured affine space}
+
+The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
+\beqn
+\sfR = \C[z_i,\lambda_i] \slash (z_i \lambda_i = 1) .
+\eeqn
+Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by $z_1,z_2$.
+So I think
+\beqn
+\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (z_i \lambda_i) .
+\eeqn
+
+Let $\Hat{A}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
+The cohomology of $(\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
+
 \end{document}

### 2023-08-15 highervertexops.tex
reminders of stuff to do

@@
 The theory of CR manifolds provides an analogue of the Dolbeault complex, 
-and Zeng works with polynomial functions and forms within it:
+and Zeng works with polynomial functions and polynomial forms within it:\footnote{Zeng claims to compute the CR cohomology but he in fact just works with the direct sum of the $SU(2)$-representations therein, and hence he works with this algebraic subcomplex instead.}
 \beqn
@@
 \eeqn
-with differential $\dbar_b = \xi_i \del_{\Bar{w}_i}$.
+where the $\xi_i$ have degree 1 (and represent $\d \Bar{w}_i$) and where the differential is $\dbar_b = \xi_i \del_{\Bar{w}_i}$.
 \owen{I'm not sure why it must provide a model for $\RR \Gamma(\mathring{\AA}^2)$, but I give some heuristic reasoning. Maybe Zeng gives a reference or proof?}
@@
 The element $\omega$ corresponds to $\Bar{w}_1\xi_2 - \Bar{w}_2\xi_1$.
-In fact, the key result is the following.
+In fact, the key result of this section is the following.
 
 \begin{prop}
-There is a $SU(2)$-equivariant isomorphism of commutative dg algebras
+There is a $SU(2)$-equivariant isomorphism of dg commutative algebras
 \beqn
-\Phi \colon \sfA_2 \to \Omega^{0,\bu}_b (S^3) 
+\Phi \colon \sfA \to \Omega^{0,\bu}_b (S^3) 
 \eeqn
@@
 
-The algebra $\sfR$ is naturally an $SL(2)$ representation where the $(z_1,z_2)$ transform in the fundamental representation and $(\lambda_1,\lambda_2)$ transforms in the dual (or contragredient) representation.
-Explicitly, the lowering and raising operators are
+This proposition guarantees that we have a well-behaved model for~$\RR \Gamma(\mathring{\AA}^2)$.
+
+The algebra $\sfR$ is naturally an $SL(2)$ representation where the linear span of $z_1$, $z_2$ transforms in the fundamental representation and the linear span of  $\lambda_1$, $\lambda_2$ transforms in the dual (or contragredient) representation.
+In particular, with respect to the standard Cartan subgroup, $z_1$ and $\lambda_2$ have weight 1 and $z_2$ and $\lambda_1$ have weight $-1$.
+For the Lie algebra, the lowering and raising operators are
 \beqn
-f = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2}, \quad e = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1} .
+f = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2} \quad\text{and}\quad e = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1}.
 \eeqn
@@
 which breaks up into a direct sum over the subspaces $V_{a,b}$ of polynomials that are homogenous of order $a$ in the variables $z_i$ and homogenous of order $b$ in the variables~$\lambda_i$.
+In $V_{a,b}$ , a highest weight vector is $z_1^a \lambda_2^b$.
+\owen{Can we identify the others?}
 
@@
 \beqn
-\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}.
+\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}
 \eeqn
+acting on $\C[z_i,\lambda_i]$.
+\owen{This isn't the image of the quadratic Casimir. In what sense is it the relevant Laplacian? On the other hand, it is a weight zero operator, even if it lowers the bigrading by (1,1).}
 Let $H_{a,b} \subset V_{a,b}$ denote the harmonic polynomials of bidegree $(a,b)$.
-An example of a harmonic polynomial is $z_1^a \lambda_2^b$.
-A direct computation shows that there is a direct sum decomposition of representations
+Examples of harmonic polynomials include $z_1^a \lambda_2^b$ for arbitrary $a,b$ and
+$z_1 \lambda_1 - z_2 \lambda_2$ for $a = 1 = b$.
+A direct computation shows that there is a direct sum decomposition \owen{of representations?}
 \begin{align*}
@@
 \[
-q: \C[z_i,\lambda_i] \to R = \C[z_i,\lambda_i]/(\C[z_i,\lambda_i] = 1)
+q: \C[z_i,\lambda_i] \to R = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
 \]
@@
 so $R$ is spanned by the images of $H_{a,b}$.
-Thus, there is a direct sum decomposition $\sfR = \oplus \sfR_{a,b}$ where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
+Thus, there is a direct sum decomposition $\sfR = \bigoplus_{a,b} \sfR_{a,b}$ where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
 
@@
 \end{lem}
-
-\owen{We should write out the proof.}
 
@@
 
+\begin{proof}
+\owen{We should write out the proof.}
+\end{proof}
+
 By direct inspection, one finds that the $\dbar$-operator is $SL(2)$-equivariant.
-It maps $\sfR_{a,b}$ to $\sfR_{a+1,b-1} \omega$.
+
+\begin{cor}
+The differential $\dbar$ is an isomorphism from $\sfR_{a,b}$ to $\sfR_{a+1,b-1} \omega$ for $b > 0$.
+Thus, the cohomology is 
+\[
+H^0(A) = \bigoplus_{a \in \NN} \sfR_{a,0}
+\]
+and
+\[
+H^1(A) = \bigoplus_{b \in \NN} \sfR_{0,b}.
+\]
+\end{cor}
+
+\begin{proof}
+For the first claim, note that the map is equivariant and nontrivial when $b > 0$. Thus by Schur's lemma it is an isomorphism.
+The description of cohomology follows by keeping the summands $\sfR_{a,b}$ that appear in the kernel (for $H^0$) and that do not appear in the image (for $H^1$).
+\end{proof}
 
@@
 
-Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA_2$, $p \colon \sfA_2 \to \sfH_2$.
+Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA_2$, $p \colon \sfA_2 \to \sfH_2$, given by the direct sum description of the corollary above.
 

### 2023-08-15 highervertexops.tex
describing anomaly in simple terms

@@
 
-\section{A model for punctured affine space}
+\section{Models for functions and distributions on punctured affine space}
 
@@
 
-Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA_2$, $p \colon \sfA_2 \to \sfH_2$, given by the direct sum description of the corollary above.
+Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA$, $p \colon \sfA \to \sfH$, given by the direct sum description of the corollary above.
 
-\begin{rmk}
-The inclusion $i$ is a map of commutative dg algebras.
-Note that $p$ is not a map of algebras; for example
+There is a canonical contracting homotopy 
+\beqn
+H \colon \sfA \to \sfA[-1]
+\eeqn 
+because for each $b > 0$, there is a canonical equivariant inverse $\sfR_{a,b} \to \sfR_{a+1,b-1} \omega$.
+Explicitly, send the highest weight vector $z_1^{a+1} \lambda_2^{b-1} \omega$ to the highest weight vector $z_1^{a} \lambda_2^{b}$ and then determine where other vector go via the lowering operator.
+For $b = 0$, $H|_{\sfR_{0,b}\omega} = 0$.
+
+\owen{Check the side conditions!}
+
+\begin{lem}
+The data $(i,p,H)$ determines a deformation retraction where $i$ is a map of dg commutative algebras.
+\end{lem}
+
+Note that $p$ is not a map of algebras. 
+For example,
 \beqn
@@
 \eeqn
-as $z_1 \lambda_1$ admits an orthogonal decomposition
+as $z_1 \lambda_1$ admits a decomposition
 \beqn
@@
 \eeqn
-\end{rmk}
 
-Define the degree $-1$ operator 
-\beqn
-H \colon \sfA_2 \to \sfA_2 [-1]
-\eeqn
-by the condition that $H|_{\sfR_{0,b}\omega} = 0$ and 
-\beqn
-H(z_1^a \lambda_2^b) = \frac{1}{(b+1)} z_1^{a-1} \lambda_2^{b+1} .
-\eeqn
-Extend this to all of $\sfA_2$ using $SU(2)$ equivariance.
-Note that for $a > 0$ this is an operator 
-\beqn
-H \colon \sfR_{a,b} \omega \to \sfR_{a-1,b+1} .
-\eeqn
-
-\begin{prop}
-The triple $(p,i,H)$ defines a special deformation retract between $\sfA$ and its cohomology.
-\end{prop}
-
-\section{Distributions on punctured affine space}
+\subsection{Distributions on punctured affine space}
 
@@
 
+\section{Recollection on anomalies for quantum moment maps}
+
+Let $V$ be a dg vector space and let $V^* = \Hom(V, \CC)$ denote its dual complex. 
+Consider the dg Poisson algebra $\cP = \Sym(V \oplus V^*)$ whose Poisson bracket extends the skew-symmetrized evaluation pairing on $V \oplus V^*$.
+We view $\cP$ as functions on the cotangent bundle~$T^* V$.
+Observe that the quadratic functions form a dg Lie subalgebra
+\[
+\cP_2 = (\Sym^2(V \oplus V^*), \{-,-\})
+\]
+of $\cP$.
+
+There is a natural deformation quantization of $\cP$ as a Weyl algebra $\cW$.
+Observe that there is a dg Lie subalgebra
+\[
+\cW_2 = (\Sym^2(V \oplus V^*) \oplus \Sym^0(V \oplus V^*), [-,-])
+\]
+of $\cW$.
+It is a central extension of $\cP_2$, and let $\omega \in H^2(\cP_2)$ denote the associated 2-cocycle.
+
+Suppose that there is a Lie algebra map $J: \fg \to \cP_2$.
+We view as a special class of symmetries for the free theory encoded by $\cP$:
+these are the symmetries where $\fg$ deforms the system to another {\em free} system.
+This situation appears in the free field realization we are studying.
+
+\begin{lem}
+Given a Lie algebra map $J: \fg \to \cP_2$, the obstruction to lifting it to a map of Lie algebras $\fg \to \cW_2$ is the 2-cocycle $J^* \omega \in H^2(\fg)$.
+\end{lem}
+
+We call $J^*\omega$ the {\em anomaly} for quantizing this symmetry.
+
+\begin{cor}
+If the anomaly $J^*\omega$ does not vanish, then there is an $L_\infty$ algebra map $J^q: \widehat{\fg} \to \cW_2$ out of the $L_\infty$ extension
+\[
+\CC \to \widehat{\fg} \to \fg.
+\]
+\end{cor}
+
 \end{document}

### 2023-08-15 highervertexops.tex
reworked rep thy stuff a little

@@
 
-The algebra $\sfR$ is naturally an $SL(2)$ representation where the linear span of $z_1$, $z_2$ transforms in the fundamental representation and the linear span of  $\lambda_1$, $\lambda_2$ transforms in the dual (or contragredient) representation.
-In particular, with respect to the standard Cartan subgroup, $z_1$ and $\lambda_2$ have weight 1 and $z_2$ and $\lambda_1$ have weight $-1$.
-For the Lie algebra, the lowering and raising operators are
+The algebra $\sfR$ is naturally an $SL(2)$ representation where the linear span $V_z$ of $z_1$, $z_2$ transforms in the fundamental representation  and the linear span $V_\lambda$ of  $\lambda_1$, $\lambda_2$ transforms in the dual (or contragredient) representation.
+In particular, with respect to the standard Cartan subgroup, $z_1$ and $\lambda_2$ have weight 1 and $z_2$ and $\lambda_1$ have weight~$-1$.
+
+Consider now the space of all polynomials
+\[
+\C[z_i,\lambda_i] = \Sym(V_z \oplus V_\lambda) \cong \Sym(V_z) \otimes \Sym(V_\lambda).
+\]
+The Lie algebra $\sl(2)$ acts by the lowering and raising operators
 \beqn
@@
 \eeqn
-These actions determine an $SL(2)$-action on the space of all polynomials $\C[z_i,\lambda_i]$,
-which breaks up into a direct sum over the subspaces $V_{a,b}$ of polynomials that are homogenous of order $a$ in the variables $z_i$ and homogenous of order $b$ in the variables~$\lambda_i$.
-In $V_{a,b}$ , a highest weight vector is $z_1^a \lambda_2^b$.
-\owen{Can we identify the others?}
+The space of polynomials breaks up into a direct sum over the subrepresentations 
+\[
+V_{a,b} = \Sym^a(V_z) \otimes \Sym^b(V_\lambda)
+\]
+of polynomials that are homogenous of order $a$ in the variables $z_i$ and homogenous of order $b$ in the variables~$\lambda_i$.
 
-Consider the Laplacian operator
+Recall that $\Sym^a(V_z)$ is an irreducible representation of dimension $a+1$ (and hence highest weight $a$) and $\Sym^b(V_\lambda)$ is an irreducible representation of dimension $b+1$ (and hence highest weight $a$).
+Let $I_m$ denote the irreducible representation of highest weight $m$ (and hence of dimension $m+1$).
+By standard facts about $SL(2)$, we see that $V_{a,b}$ decomposes as a direct sum of irreducible representations
+\[
+V_{a,b} \cong I_{a+b} \oplus I_{a+b-2} \oplus \cdots \oplus I_{a-b}
+\]
+for $a \geq b$. (The other situation can be seen by symmetry.)
+
+There is a more concrete way to describe this decomposition.
+Consider the differential operator
 \beqn
@@
 
-\begin{lem}
-Each $\sfR_{a,b}$ is isomorphic to the irreducible $SL(2)$-representation of dimension $(a+b+1)$.
-Its highest weight vector is $z_1^a \lambda_2^b \in \sfR_{a,b}$, and a basis for $\sfR_{a,b}$ is obtained as
-\beqn
-\{z_1^a \lambda_2^b, f (z_1^a \lambda_2^b), f^2 (z_1^a \lambda_2^b), \ldots, f^{a+b} (z_1^a \lambda_2^b) \} .
-\eeqn
-\end{lem}
-
 \begin{eg}
@@
 
-\begin{proof}
-\owen{We should write out the proof.}
-\end{proof}
+The following fact is quite useful for us.
+
+\begin{lem}
+Each $\sfR_{a,b}$ is isomorphic to the irreducible $SL(2)$-representation of dimension $(a+b+1)$.
+Its highest weight vector is $z_1^a \lambda_2^b \in \sfR_{a,b}$, and a basis for $\sfR_{a,b}$ is obtained as
+\beqn
+\{z_1^a \lambda_2^b, f (z_1^a \lambda_2^b), f^2 (z_1^a \lambda_2^b), \ldots, f^{a+b} (z_1^a \lambda_2^b) \} .
+\eeqn
+\end{lem}
+
+This lemma is proved by applying the description of the decomposition into irreducibles.
 
@@
 In fact $\Phi$ maps the subspace $\sfR_{a,b}$ isomorphically to $\cH_{a,b}$ where $\cH_{a,b} \subset \Omega^{0,\bu}_b (S^3)$ is the space of harmonic polynomials that are of bidegree $(a,b)$ in the variables $(w_i,\Bar{w}_j)$.
-To see that the differentials are compatible we observe that
+Now observe that
 \beqn
-\Phi(\dbar(\lambda_i)) = - \Phi(\ep_{ij} z_j \omega) = - \ep_{ij} w_j \Phi (\omega) = \xi_i = \dbar_b \Phi (\lambda_i) .
+\Phi(\dbar(\lambda_i)) = - \Phi(\ep_{ij} z_j \omega) = - \ep_{ij} w_j \Phi (\omega) = \xi_i = \dbar_b \Phi (\lambda_i) 
 \eeqn
+to see that the differentials are compatible.
 \end{proof}
@@
 \[
-\CC \to \widehat{\fg} \to \fg.
+\CC \to \widehat{\fg} \to \fg
 \]
+determined by $J^* \omega$.
 \end{cor}

### 2023-08-15 highervertexops.tex
tiny tweaks

@@
 
-There is a canonical contracting homotopy 
-\beqn
-H \colon \sfA \to \sfA[-1]
-\eeqn 
+There is a canonical contracting homotopy $H$ on $\sfA$ 
 because for each $b > 0$, there is a canonical equivariant inverse $\sfR_{a,b} \to \sfR_{a+1,b-1} \omega$.
@@
 \begin{lem}
-The data $(i,p,H)$ determines a deformation retraction where $i$ is a map of dg commutative algebras.
+The data $(i,p,H)$ determines a special deformation retraction where $i$ is a map of dg commutative algebras.
 \end{lem}

### 2023-08-15 highervertexops.tex
merge

@@
 \beqn
-\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (z_i \lambda_i) .
+\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (z_i \lambda_i=1) .
 \eeqn
 
-Let $\Hat{A}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
-The cohomology of $(\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
+Let $\Hat{\sfA}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
+The cohomology of $(\Hat\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
 

### 2023-08-16 highervertexops.tex
merge

@@
 \def\RHom{{\rm RHom}}
+\newcommand{\sff}{\mathsf{f}}
+\newcommand{\sfe}{\mathsf{e}}
 %\def\sfR{\mathsf{R}}
@@
 \beqn
-f = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2} \quad\text{and}\quad e = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1}.
+\sff = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2} \quad\text{and}\quad \sfe = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1}.
 \eeqn
@@
 \[
-q: \C[z_i,\lambda_i] \to R = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
+q \colon \C[z_i,\lambda_i] \to R = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
 \]
@@
 \beqn
-\{z_1^a \lambda_2^b, f (z_1^a \lambda_2^b), f^2 (z_1^a \lambda_2^b), \ldots, f^{a+b} (z_1^a \lambda_2^b) \} .
+\{z_1^a \lambda_2^b, \sff (z_1^a \lambda_2^b), \sff^2 (z_1^a \lambda_2^b), \ldots, \sff^{a+b} (z_1^a \lambda_2^b) \} .
 \eeqn
@@
 
+\subsection{Residues}
+
+Define
+\beqn
+\op{Res} \colon \sfA \to \C[1]
+\eeqn
+by the rules that $\op{Res}|_{\sfA^0} = 0$ and
+\beqn
+\op{Res} \left(f(z,\lambda) \omega \right) = p (f(z,\lambda)) (z=0) .
+\eeqn
+
+\begin{lem} The following are true regarding the higher algebraic residue:
+\begin{enumerate}
+\item The residue is $\lie{sl}(2)$ invariant.
+\item For $f \in \C[z_1,z_2]$ one has $\op{Res}(f \omega) = f(0)$.
+\item For any $f \in \sfA$ one has $\op{Res}(\dbar f) = 0$.
+\end{enumerate}
+\end{lem}
+\begin{proof}
+Item (1) holds since $p$ is the $\lie{sl}(2)$-equivariant projection. 
+For (2), note that for $f \in \C[z_1,z_2]$ that $p(f) = f$.
+
+Finally, observe that for $f = z_1^a \lambda_2^b$ we have
+\beqn
+\op{Res}(\dbar f) = \op{Res}(b z_1^{a+1} \lambda_2^{b-1}) .
+\eeqn
+For $b =0$ this expression clearly vanishes. 
+For $b = 1$ the right hand side is $p( z_1^{a+1})(0) = 0$ for all $a \geq 0$.
+Finally, for $b > 1$ one has $p(z_1^{a+1} \lambda_2^{b-1}) = 0$ for all $a \geq 0$.
+Using $\lie{sl}(2)$ invariance this proves (3).
+\end{proof}
+
 \subsection{Distributions on punctured affine space}

### 2023-08-17 highervertexops.tex
not sure what i did since i last pushed

--- 2023-08-15 highervertexops.tex
@@
 where the $\xi_i$ have degree 1 (and represent $\d \Bar{w}_i$) and where the differential is $\dbar_b = \xi_i \del_{\Bar{w}_i}$.
-\owen{I'm not sure why it must provide a model for $\RR \Gamma(\mathring{\AA}^2)$, but I give some heuristic reasoning. Maybe Zeng gives a reference or proof?}
-Note that one can see that polynomials in the coordinates, both holomorphic $w_i$ and antiholomorphic $\Bar{w}_i$, span the complex-valued polynomial functions on $\CC^2 \cong \RR^4$.
-Their restriction to the unit-sphere $S^3$ wholly determines their behavior as functions on affine space, and hence also on punctured affine space. 
+Note that one can see that polynomials in the coordinates, both holomorphic $w_i$ and antiholomorphic $\Bar{w}_i$, span the complex-valued polynomial functions on $\CC^2 \cong \RR^4$, i.e., as a real vector space.
+Their restriction to the unit-sphere $S^3$ wholly determines their behavior as functions on $\RR^4$, and hence also on punctured affine space. 
 The elements $\xi_i$ correspond to $d\Bar{w}_i$ in the Dolbeault complex of punctured affine space.
@@
 and its image is the image of $\dbar$ intersected with polynomial  forms in $d \Bar{w}_i$.
-Thus the cohomology of this complex $\Omega^{0,\bu}_b (S^3)$ is a model for $\RR \Gamma(\mathring{\AA}^2)$.
+Thus the cohomology of this complex $\Omega^{0,\bu}_b (S^3)$ is a model for $\RR \Gamma(\mathring{\AA}^2)$, by a result of~\cite{FHK}.
 
@@
 
-There is a more concrete way to describe this decomposition.
+There is a more concrete way to describe this decomposition, 
+modeled on the construction of spherical harmonics as representations of $SO(n)$.
 Consider the differential operator
@@
 \eeqn
-acting on $\C[z_i,\lambda_i]$.
-\owen{This isn't the image of the quadratic Casimir. In what sense is it the relevant Laplacian? On the other hand, it is a weight zero operator, even if it lowers the bigrading by (1,1).}
-Let $H_{a,b} \subset V_{a,b}$ denote the harmonic polynomials of bidegree $(a,b)$.
+acting on $\C[z_i,\lambda_i]$;
+it is inspired by the Laplacian on $\CC^2$ when we view $\lambda_i$ as a version of $\Bar{z_i}$.
+This operator has weight zero and, in fact, it is $SL(2)$-equivariant.
+\owen{I need to check this myself. If there's a slick way, we should include it.}
+On the other hand, it maps $V_{a,b}$ to $V_{a-1,b-1}$, i.e., it changes the bigrading by~$(-1,-1)$.
+
+Let $H_{a,b} = \ker \triangle|_{V_{a,b}}$ denote the ``harmonic'' polynomials of bidegree $(a,b)$.
 Examples of harmonic polynomials include $z_1^a \lambda_2^b$ for arbitrary $a,b$ and
@@
 \end{align*}
-(Compare with the well-known construction of spherical harmonics.)
+(Compare with the well-known )
 
@@
 \[
-q: \C[z_i,\lambda_i] \to R = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
+q: \C[z_i,\lambda_i] \to \sfR = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
 \]
@@
 
-Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA$, $p \colon \sfA \to \sfH$, given by the direct sum description of the corollary above.
+Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH \hookrightarrow \sfA$, $p \colon \sfA \to \sfH$, given by the direct sum description of the corollary above.
 
@@
 \beqn
-\sfR = \C[z_i,\lambda_i] \slash (z_i \lambda_i = 1) .
+\sfR = \C[z_i,\lambda_i] \slash (\sum_i z_i \lambda_i = 1) .
 \eeqn
@@
 \beqn
-\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (z_i \lambda_i) .
+\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (\sum_i z_i \lambda_i) .
 \eeqn
@@
 of $\cW$.
-It is a central extension of $\cP_2$, and let $\omega \in H^2(\cP_2)$ denote the associated 2-cocycle.
+It is a central extension of $\cP_2$; let $\omega \in H^2(\cP_2)$ denote the associated 2-cocycle.
 
@@
 \begin{lem}
-Given a Lie algebra map $J: \fg \to \cP_2$, the obstruction to lifting it to a map of Lie algebras $\fg \to \cW_2$ is the 2-cocycle $J^* \omega \in H^2(\fg)$.
+Given a Lie algebra map $J: \fg \to \cP_2$, the obstruction to $J$ being a map of Lie algebras $\fg \to \cW_2$ is the 2-cocycle $J^* \omega \in H^2(\fg)$.
 \end{lem}

### 2023-08-17 highervertexops.tex

@@
 \[
-q: \C[z_i,\lambda_i] \to \sfR = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
+q \colon \C[z_i,\lambda_i] \to \sfR = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
 \]
@@
 
-Let $\Hat{A}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
-The cohomology of $(\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
+Let $\Hat{\sfA}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
+The cohomology of $(\Hat\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
 

### 2023-08-17 highervertexops.tex
small tweaks in extension discussion

@@
 of $\cP$.
+Note that for $V$ a finite-dimensional vector space concentrated in degree zero,
+there is a natural identification $\cP_2 = \frak{sp}(T^*V)$, which plays an important role in corollary~\ref{cor:trivforsp}.
 
@@
 
+On the other hand, this phenomenon does not happen in the most traditional situations.
+
+\begin{cor}
+\label{cor:trivforsp}
+For $V$ a finite-dimensional vector space concentrated in degree zero, the anomaly $\omega$ is trivial as $\frak{sp}(T^* V) = \cP_2$ is simple and hence $H^2(\cP_2) = 0$.
+\end{cor}
+
+In other words, quadratic Hamiltonians (elements of $\cP_2$) admit a natural quantization (lift to $\cW_2$).
+Normal ordering offers a method, but there are other choices.
+
+\owen{I am not sure what the status is for infinite-dimensional vector spaces. It seems like functional analysis plays a nontrivial role.}
+
 \end{document}

### 2023-08-17 highervertexops.tex
more res

@@
 \beqn
-\op{Res} \colon \sfA \to \C[1]
+\op{Res} \colon \sfA \to \C[-1]
 \eeqn
@@
 
-\begin{lem} The following are true regarding the higher algebraic residue:
+\begin{lem}
+\label{lem:res} 
+The following are true regarding the higher algebraic residue:
 \begin{enumerate}
@@
 Using $\lie{sl}(2)$ invariance this proves (3).
+\end{proof}
+
+In the single-variable case, the residue map defines an identification
+\beqn
+\C((z)) \simeq \Omega^1 (\Hat{D})^\vee = \left(\C((z)) \d z\right)^\vee
+\eeqn
+where the right hand side is the continuous linear dual.
+Explicitly, this identification takes a Laurent series $f$ to the functional 
+\beqn
+g \d z \mapsto \op{Res}_{1d} (f g \d z) .
+\eeqn
+
+\begin{prop}
+The higher algebraic residue defines a cochain map
+\beqn
+\sfA \to \left(\sfA \, \d^2 z\right)^\vee [-1]
+\eeqn 
+which sends an element $a \in \sfA$ to the functional
+\beqn
+F_a \colon b \, \d^2 z \in \sfA\, \d^2 z \mapsto (-1)^{|a|} \Res(a b \, \d^2 z) .
+\eeqn
+\brian{weird sign, but I think it's there because of the $[-1]$ shift.}
+When extended to the completed version of punctured affine space, this assignment defines an isomorphism of cochain complexes 
+\beqn
+F \colon \Hat\sfA \simeq \left(\Hat\sfA \, \d^2 z\right)^\vee [-1] .
+\eeqn
+\end{prop}
+\begin{proof}
+Suppose that $a \in \sfA^0$. 
+Then
+\begin{align*}
+F_{\dbar a} (b \d^2 z) & = - \Res \left( (\dbar a) b \d^2 z \right) \\
+& = - \Res\left( \dbar(a b \d^2 z) \right) + \Res \left(a \dbar b \d^2 z\right) \\
+& = F_{a} (\dbar b \d^2 z) .
+\end{align*}
+In the final line we have used (3) from lemma \ref{lem:res}.
+If $a \in \sfA^1$ then $F_{\dbar a}(b \d^2 z) = 0 = F_{a} (\dbar b \d^2 z)$ for all $b$.
+
+\brian{Can you help me prove part 2?}
 \end{proof}

### 2023-08-17 highervertexops.tex
typo

@@
 This operator has weight zero and, in fact, it is $SL(2)$-equivariant.
-\owen{I need to check this myself. If there's a slick way, we should include it.}
+For example, notice that for any $g(z_i,\lambda_i)$ we have
+\begin{align*}
+(\del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2})(z_2 \del_{z_1} g - \lambda_1 \del_{\lambda_2}g )& = z_2 \del_{z_1}^2 \del_{\lambda_1} g - \del_{z_1} \del_{\lambda_2} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g \\ & \qquad + \del_{z_1} \del_{\lambda_2}  g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g
+\\ & = z_2 \del_{z_1}^2 \del_{\lambda_1} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g .
+\end{align*}
+Thus $[\triangle,\sff] = 0$.
+Similarly, one can show that $[\triangle, \sfe] = 0$.
+\owen{I need to check this myself. If there's a slick way, we should include it.} \brian{I gave a computational proof.}
 On the other hand, it maps $V_{a,b}$ to $V_{a-1,b-1}$, i.e., it changes the bigrading by~$(-1,-1)$.
@@
 
-\subsection{Residues}
+\subsection{The higher algebraic residue}
 
@@
 \eeqn
+This residue extends to the completion to give a map
+\beqn
+\op{Res} \colon \Hat\sfA \to \C[-1] .
+\eeqn
 
@@
 \item The residue is $\lie{sl}(2)$ invariant.
-\item For $f \in \C[z_1,z_2]$ one has $\op{Res}(f \omega) = f(0)$.
+\item For $f \in \C[[z_1,z_2]]$ one has $\op{Res}(f \omega) = f(0)$.
 \item For any $f \in \sfA$ one has $\op{Res}(\dbar f) = 0$.
+Thus $\op{Res}$ is a cochain map.
 \end{enumerate}

### 2023-08-17 highervertexops.tex
merge

@@
 %\def\sfA{\mathsf{A}}
+\newcommand{\laurent}{\Hat \sfA}
+\newcommand{\sfb}{\mathsf{b}}
+\newcommand{\sfc}{\mathsf{c}}
 
@@
 \eeqn
-as $z_1 \lambda_1$ admits a decomposition
+as $z_1 \lambda_1$ admits a $\lie{sl}(2)$-decomposition
 \beqn
@@
 \beqn
-\op{Res} \colon \Hat\sfA \to \C[-1] .
+\op{Res} \colon \laurent \to \C[-1] .
 \eeqn
@@
 \item For $f \in \C[[z_1,z_2]]$ one has $\op{Res}(f \omega) = f(0)$.
-\item For any $f \in \sfA$ one has $\op{Res}(\dbar f) = 0$.
+\item For any $f \in \laurent$ one has $\op{Res}(\dbar f) = 0$.
 Thus $\op{Res}$ is a cochain map.
@@
 
-\begin{prop}
+\begin{prop}\label{prop:res}
 The higher algebraic residue defines a cochain map
@@
 
+\section{Algebraic free field realization}
+
+Consider the vector space $V = \laurent$.
+Via the residue pairing we have an identification $V^\vee = \laurent \, \d^2 z [1]$, see proposition \ref{prop:res}.
+From hereon we use the notation $\laurent^{(2)} = \laurent \, \d^2 z$.
+We will denote linear elements in the corresponding Poisson algebra
+\beqn
+\cP = \Sym \left(\laurent  \oplus \laurent^{(2)}[1] \right) ,
+\eeqn
+by $(\sfb , \sfc)$.
+On these elements, the Poisson bracket reads
+\beqn
+\{\sfb ,\sfc\} = \Res(\sfb \sfc) .
+\eeqn
+The Lie algebra $\cP_2$ is spanned by symbols of the form $\sfb \sfb',\sfb \sfc, \sfc \sfc'$ where $\sfb,\sfb'\in \laurent$ and $\sfc,\sfc' \in \laurent^{(2)}[1]$.
+
+The algebra $\cP$ is the free commutative algebra generated by $\laurent \oplus \laurent^{(2)}[1]$.
+Alternatively, we can view, via the residue pairing, a linear element $(\sfb, \sfc) \in \laurent \oplus \laurent^{(2)}[1]$ as the functional
+\beqn
+(\sfb, \sfc) \colon \laurent^{(2)} [1] \oplus \laurent \to \C
+\eeqn
+defined by
+\beqn
+(\beta, \gamma) \mapsto (-1)^{|\sfb|} \Res(\sfb \beta) + (-1)^{|\sfc|} \Res(\sfc \gamma) .
+\eeqn
+Likewise, we can view a quadratic element in $\cP_2$ as a functional
+\beqn
+\Sym^2 \left(\laurent^{(2)} [1] \oplus \laurent \right) \to \C .
+\eeqn
+For example, the quadratic element $\sfb \sfc \in \cP_2$ corresponds to the quadratic functional
+\beqn
+\beta \gamma \mapsto (-1)^{|\sfb|+ |\sfc|} \Res (\sfb \beta) \Res(\sfc \gamma) ,
+\eeqn
+where $\beta \in \laurent^{(2)} [1]$ and $\gamma \in \laurent$.
+
+Let $J$ be the map
+\beqn
+J \colon \sfA \to \cP_2
+\eeqn
+defined by sending an element $a \in \sfA$ to the quadratic functional
+\beqn
+J_a (\beta \gamma) = \Res(\beta a \gamma) .
+\eeqn
+
+\begin{lem}
+The map $J$ is a cochain map.
+Furthermore, for any $a,a' \in \sfA$ we have $\{J_a, J_{a'}\} = 0$.
+Thus, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
+\end{lem}
+\begin{proof}
+For the first claim observe that
+\beqn
+J_{\dbar a} (\beta \gamma) = \Res(\beta (\dbar a) \gamma) = \pm \Res((\dbar \beta) a \gamma) \pm \Res(\beta a \dbar \gamma) = J_a (\dbar \beta \gamma) + (-1)^{|\beta|} J_a(\beta \dbar \gamma) 
+\eeqn
+by (3) in lemma \ref{lem:res}.
+\end{proof}
+
 \end{document}

### 2023-08-17 highervertexops.tex
expansion

@@
 so $R$ is spanned by the images of $H_{a,b}$.
-Thus, there is a direct sum decomposition $\sfR = \bigoplus_{a,b} \sfR_{a,b}$ where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
+Thus, there is a direct sum decomposition 
+\beqn
+\sfR = \bigoplus_{a,b} \sfR_{a,b}
+\eeqn
+where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
+We remark that this decomposition does \textit{not} respect the commutative product.
 
@@
 This lemma is proved by applying the description of the decomposition into irreducibles.
+In turn, any polynomial $f(z,\lambda) \in \sfR$ admits a decomposition of the form
+\beqn\label{eqn:expand}
+f(z, \lambda) = \sum_{a,b,k \geq 0} c_{k}^{ab} \sff^k (z_1^a \lambda_2^b) 
+\eeqn
+for some coefficients $c_k^{ab}$.
 
@@
 The differential $\dbar$ is an isomorphism from $\sfR_{a,b}$ to $\sfR_{a+1,b-1} \omega$ for $b > 0$.
-Thus, the cohomology is 
+Thus, the cohomology of $\sfA$ is 
 \[
-H^0(A) = \bigoplus_{a \in \NN} \sfR_{a,0}
+H^0(\sfA) = \bigoplus_{a \in \NN} \sfR_{a,0}
 \]
@@
 \[
-H^1(A) = \bigoplus_{b \in \NN} \sfR_{0,b}.
+H^1(\sfA) = \bigoplus_{b \in \NN} \sfR_{0,b}.
 \]
@@
 \beqn
-z_1 \lambda_1 = \frac12 (z_1 \lambda_1 - z_2 \lambda_2) + \frac12 .
+z_1 \lambda_1 =  \frac12  + \frac12 (z_1 \lambda_1 - z_2 \lambda_2).
 \eeqn
-
 \subsection{The higher algebraic residue}
@@
 \eeqn
+In terms of the expansion \eqref{eqn:expand} we have
+\beqn
+\op{Res} \left(f(z,\lambda) \omega \right) = c_{0}^{00} .
+\eeqn
+
 This residue extends to the completion to give a map
@@
 \beqn
-J \colon \sfA \to \cP_2
+J \colon \laurent \to \cP_2
 \eeqn
@@
 \begin{lem}
-The map $J$ is a cochain map.
-Furthermore, for any $a,a' \in \sfA$ we have $\{J_a, J_{a'}\} = 0$.
-Thus, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
+The following are true of the map $J$.
+\begin{enumerate}
+\item $J$ is a cochain map.
+\item $J$ is $\lie{sl}(2)$-equivariant.
+\item For $a,a' \in \laurent$ one has $\{J_a, J_{a'}\} = 0$.
+\end{enumerate}
+In particular, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
 \end{lem}

### 2023-08-18 highervertexops.tex
current

@@
 \eeqn
-defined by sending an element $a \in \sfA$ to the quadratic functional
+defined by sending an element $\alpha \in \sfA$ to the quadratic functional $J_\alpha \in \cP_2$ defined by
 \beqn
-J_a (\beta \gamma) = \Res(\beta a \gamma) .
+J_\alpha (\beta \gamma) = \Res(\beta \alpha \gamma) .
 \eeqn
@@
 \begin{lem}
-The following are true of the map $J$.
+Let $\alpha = z_1^m \lambda_2^n$.
+Then $J_\alpha$ corresponds to the infinite series
+\begin{multline}
+J_\alpha = \sum_{a,b \geq 0} \sum_{k=0}^{a+b} c_k^{a,b} \sff^k(z_1^{a+m}\lambda_2^{b+n} \omega) \cdot \sff^{a+b-k} (z_1^b \lambda_2^a) \d^2 z \\
++ \sum_{a,b \geq 0} \sum_{k=0}^{a+b} c_k^{a,b} \sff^k(z_1^{a+m}\lambda_2^{b+n}) \cdot \sff^{a+b-k} (z_1^b \lambda_2^a \omega) \d^2 z ,
+\end{multline}
+for some constants $c_{k}^{a,b}$.
+
+Similarly, let $\alpha = z_1^m \lambda_2^n \omega$.
+Then $J_\alpha$ corresponds to the infinite series
+\beqn
+J_\alpha = \sum_{a,b \geq 0} \sum_{k=0}^{a+b} c_k^{a,b} \sff^k(z_1^{a+m}\lambda_2^{b+n} \omega) \cdot \sff^{a+b-k} (z_1^b \lambda_2^a \omega) \d^2 z ,
+\eeqn
+which is of degree $+1$.
+\end{lem}
+
+\begin{prop}
+The following are true of the map $J$:
 \begin{enumerate}
@@
 In particular, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
-\end{lem}
+\end{prop}
 \begin{proof}

### 2023-08-18 highervertexops.tex
more polishing of the sl2 features of A

--- 2023-08-17 highervertexops.tex
@@
 
-Let $\sfR$ be the commutative algebra generated by variables $z_i,\lambda_i,i=1,2$ subject to the relation $\sum_i z_i \lambda_i = 1$.
+Let $\sfR$ be the commutative algebra generated by variables $z_i,\lambda_i,i=1,2$ subject to the relation $z_1\lambda_1 + z_2 \lambda_2 = 1$.
 Let $\sfA$ be the graded commutative algebra freely generated over $\sfR$ by a degree $+1$ element $\omega$.
@@
 By standard facts about $SL(2)$, we see that $V_{a,b}$ decomposes as a direct sum of irreducible representations
-\[
+\begin{equation}
+\label{eq:sl2decompV}
 V_{a,b} \cong I_{a+b} \oplus I_{a+b-2} \oplus \cdots \oplus I_{a-b}
-\]
+\end{equation}
 for $a \geq b$. (The other situation can be seen by symmetry.)
@@
 modeled on the construction of spherical harmonics as representations of $SO(n)$.
-Consider the differential operator
+Consider the element  
+\[
+|(z,\lambda)|^2 \define z_1 \lambda_1 + z_2 \lambda_2, 
+\]
+which describes the evaluation pairing. 
+It is fixed by the $SL(2)$-action, has weight zero, and bigrading $(1,1)$.
+Multiplication by this element produces an injection
+\[
+V_{a-1,b-1} \hookrightarrow V_{a,b}
+\]
+that is $SL(2)$-equivariant, so we know there is a decomposition 
+\[
+V_{a,b} \cong |(z,\lambda)|^2 V_{a-1,b-1} \oplus C_{a,b},
+\]
+where $C_{a,b}$ is a complementary subspace and representation.
+We can characterize this subrepresentation concretely using the differential operator
 \beqn
@@
 it is inspired by the Laplacian on $\CC^2$ when we view $\lambda_i$ as a version of $\Bar{z_i}$.
-This operator has weight zero and, in fact, it is $SL(2)$-equivariant.
-For example, notice that for any $g(z_i,\lambda_i)$ we have
+This operator has weight zero and, in fact, it is $SL(2)$-equivariant.\footnote{For example, notice that for any $g(z_i,\lambda_i)$ we have
 \begin{align*}
-(\del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2})(z_2 \del_{z_1} g - \lambda_1 \del_{\lambda_2}g )& = z_2 \del_{z_1}^2 \del_{\lambda_1} g - \del_{z_1} \del_{\lambda_2} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g \\ & \qquad + \del_{z_1} \del_{\lambda_2}  g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g
-\\ & = z_2 \del_{z_1}^2 \del_{\lambda_1} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g .
+\triangle \circ \sff(g) &= (\del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2})(z_2 \del_{z_1} g - \lambda_1 \del_{\lambda_2}g )\\
+&= z_2 \del_{z_1}^2 \del_{\lambda_1} g - \del_{z_1} \del_{\lambda_2} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g \\ & \qquad + \del_{z_1} \del_{\lambda_2}  g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g \\
+& = z_2 \del_{z_1}^2 \del_{\lambda_1} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g \\
+&=  \sff \circ \triangle(g)
 \end{align*}
 Thus $[\triangle,\sff] = 0$.
-Similarly, one can show that $[\triangle, \sfe] = 0$.
-\owen{I need to check this myself. If there's a slick way, we should include it.} \brian{I gave a computational proof.}
+Similarly, one can show that $[\triangle, \sfe] = 0$.)
+\owen{I need to check this myself. If there's a slick way, we should include it.} \brian{I gave a computational proof.}\owen{Thank you! I don't know why I'm so lazy about calculus.}}
 On the other hand, it maps $V_{a,b}$ to $V_{a-1,b-1}$, i.e., it changes the bigrading by~$(-1,-1)$.
@@
 $z_1 \lambda_1 - z_2 \lambda_2$ for $a = 1 = b$.
-A direct computation shows that there is a direct sum decomposition \owen{of representations?}
-\begin{align*}
-V_{a,b} & = H_{a,b} \oplus |(z,\lambda)|^2 V_{a-1,b-1} \\
-& = H_{a,b} \oplus |(z,\lambda)|^2 H_{a-1,b-1} \oplus |(z,\lambda)|^4 H_{a-2,b-2} \oplus \cdots 
-\end{align*}
-(Compare with the well-known )
+Direct computation shows that 
+\[
+V_{a,b}  = H_{a,b} \oplus |(z,\lambda)|^2 V_{a-1,b-1},
+\]
+and by iteratively applying this decomposition, we find
+there is a direct sum decomposition
+\[
+V_{a,b}  = H_{a,b} \oplus |(z,\lambda)|^2 H_{a-1,b-1} \oplus |(z,\lambda)|^4 H_{a-2,b-2} \oplus \cdots \oplus |(z,\lambda)|^{2b} H_{a-b,0} 
+\]
+when $a \geq b$.
+Thus $C_{a,b} = H_{a,b}$, and we also find $I_{a+b} = H_{a,b}$ by comparing with the decomposition~\eqref{eq:sl2decompV}.
 
-Consider now  
-\[
-|(z,\lambda)|^2 \define z_1 \lambda_1 + z_2 \lambda_2, 
-\]
-which describes the evaluation pairing. 
-It is preserved by the $SL(2)$-action, and hence we see that the canonical quotient map 
+In light of these facts, we see that the canonical quotient map 
 \[
@@
 Moreover, inside $V_{a,b}$, any multiple of $|(z,\lambda)|^2$ is annihilated by $q$,
-so $R$ is spanned by the images of $H_{a,b}$.
+so $\sfR$ is spanned by the images of $H_{a,b}$.
 Thus, there is a direct sum decomposition 
@@
 where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
-We remark that this decomposition does \textit{not} respect the commutative product.
+
+We emphasize that this decomposition does \textit{not} respect the commutative product.
 
@@
 \begin{cor}
-The differential $\dbar$ is an isomorphism from $\sfR_{a,b}$ to $\sfR_{a+1,b-1} \omega$ for $b > 0$.
+The differential $\dbar$ provides an isomorphism 
+\[
+\dbar_{a,b} \colon \sfR_{a,b} \xto{\cong} \sfR_{a+1,b-1} \omega
+\]
+for $b > 0$.
 Thus, the cohomology of $\sfA$ is 
@@
 There is a canonical contracting homotopy $H$ on $\sfA$ 
-because for each $b > 0$, there is a canonical equivariant inverse $\sfR_{a,b} \to \sfR_{a+1,b-1} \omega$.
+because for each $b > 0$, there is a canonical equivariant inverse map $\dbar_{a,b}^{-1}:  \sfR_{a+1,b-1} \omega \to \sfR_{a,b}$.
 Explicitly, send the highest weight vector $z_1^{a+1} \lambda_2^{b-1} \omega$ to the highest weight vector $z_1^{a} \lambda_2^{b}$ and then determine where other vector go via the lowering operator.
@@
 For example,
+the following three polynomials in $\C[z_i,\lambda_i]$ represent the same element in~$\sfR$:
 \beqn
-p(z_1 \lambda_1) = \frac12
+\frac12  + \frac12 (z_1 \lambda_1 - z_2 \lambda_2) \sim \frac12  + \frac12 (z_1 \lambda_1 - z_2 \lambda_2) + \frac12 (z_1 \lambda_1 + z_2 \lambda_2) \sim z_1 \lambda_1
 \eeqn
-as $z_1 \lambda_1$ admits a $\lie{sl}(2)$-decomposition
+so
 \beqn
-z_1 \lambda_1 =  \frac12  + \frac12 (z_1 \lambda_1 - z_2 \lambda_2).
+p(z_1 \lambda_1) = p\left(\frac12  + \frac12 (z_1 \lambda_1 - z_2 \lambda_2)\right) = \frac12.
 \eeqn
+
 \subsection{The higher algebraic residue}
@@
 \begin{enumerate}
-\item The residue is $\lie{sl}(2)$ invariant.
+\item The residue is $\lie{sl}(2)$-invariant.
 \item For $f \in \C[[z_1,z_2]]$ one has $\op{Res}(f \omega) = f(0)$.

### 2023-08-18 highervertexops.tex
small edits while reading new stuff

@@
 \eeqn 
-which sends an element $a \in \sfA$ to the functional
+that sends an element $a \in \sfA$ to the functional $F_a$ where 
 \beqn
-F_a \colon b \, \d^2 z \in \sfA\, \d^2 z \mapsto (-1)^{|a|} \Res(a b \, \d^2 z) .
+F_a(b \, \d^2 z) =  (-1)^{|a|} \Res(a b \, \d^2 z) .
 \eeqn
@@
 \end{prop}
+
 \begin{proof}
@@
 \begin{align*}
-F_{\dbar a} (b \d^2 z) & = - \Res \left( (\dbar a) b \d^2 z \right) \\
-& = - \Res\left( \dbar(a b \d^2 z) \right) + \Res \left(a \dbar b \d^2 z\right) \\
-& = F_{a} (\dbar b \d^2 z) .
+F_{\dbar a} (b\, \d^2 z) & = - \Res \left( (\dbar a) b \,\d^2 z \right) \\
+& = - \Res\left( \dbar(a b \,\d^2 z) \right) + \Res \left(a \dbar b \,\d^2 z\right) \\
+& = F_{a} (\dbar b \,\d^2 z) .
 \end{align*}
 In the final line we have used (3) from lemma \ref{lem:res}.
-If $a \in \sfA^1$ then $F_{\dbar a}(b \d^2 z) = 0 = F_{a} (\dbar b \d^2 z)$ for all $b$.
+If $a \in \sfA^1$ then $F_{\dbar a}(b \,\d^2 z) = 0 = F_{a} (\dbar b \,\d^2 z)$ for all $b$.
 
@@
 Consider the vector space $V = \laurent$.
-Via the residue pairing we have an identification $V^\vee = \laurent \, \d^2 z [1]$, see proposition \ref{prop:res}.
+Via the residue pairing we have an identification $V^\vee = \laurent \, \d^2 z [1]$ (see proposition \ref{prop:res}).
 From hereon we use the notation $\laurent^{(2)} = \laurent \, \d^2 z$.
@@
 The algebra $\cP$ is the free commutative algebra generated by $\laurent \oplus \laurent^{(2)}[1]$.
-Alternatively, we can view, via the residue pairing, a linear element $(\sfb, \sfc) \in \laurent \oplus \laurent^{(2)}[1]$ as the functional
-\beqn
-(\sfb, \sfc) \colon \laurent^{(2)} [1] \oplus \laurent \to \C
-\eeqn
-defined by
-\beqn
-(\beta, \gamma) \mapsto (-1)^{|\sfb|} \Res(\sfb \beta) + (-1)^{|\sfc|} \Res(\sfc \gamma) .
-\eeqn
-Likewise, we can view a quadratic element in $\cP_2$ as a functional
+We can view, via the residue pairing, a linear element $(\sfb, \sfc) \in \laurent \oplus \laurent^{(2)}[1]$ as the linear functional
+\[
+\begin{array}{cccc}
+(\sfb, \sfc) \colon & \laurent^{(2)} [1] \oplus \laurent & \to & \C\\
+& (\beta, \gamma) & \mapsto  &(-1)^{|\sfb|} \Res(\sfb \beta) + (-1)^{|\sfc|} \Res(\sfc \gamma) .
+\end{array}
+\]
+%\eeqn
+%defined by
+%\beqn
+%(\beta, \gamma) \mapsto (-1)^{|\sfb|} \Res(\sfb \beta) + (-1)^{|\sfc|} \Res(\sfc \gamma) .
+%\eeqn
+Likewise, we can view a quadratic element in $\cP_2$ as a linear functional
 \beqn

### 2023-08-18 highervertexops.tex
rearranged things and added place for me to insert some ideas

@@
 We emphasize that this decomposition does \textit{not} respect the commutative product.
+\owen{I'm confused what you mean here. Can you spell out what you mean in more detail?}
 
@@
 
+\subsection{Functions on punctured formal disk}
+
+The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
+\beqn
+\sfR = \C[z_i,\lambda_i] \slash (\sum_i z_i \lambda_i = 1) .
+\eeqn
+Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by~$z_1,z_2$:
+\beqn
+\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (\sum_i z_i \lambda_i) .
+\eeqn
+\owen{As you said originally, this second line takes the completion for the $z$s first and then adjoins the $\lambda$s, while your definition involves completing after adjoining the $\lambda$s.
+It's not clear those operations commute.}
+
+Let $\Hat{\sfA}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
+The cohomology of $(\Hat\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
+\owen{We need to be really careful about this, and it probably depends on what category of vector spaces (e.g., complete filtered?) we work in.
+The $SL(2)$-approach above manifestly breaks down, although it gives us useful information.}
+
 \subsection{The higher algebraic residue}
@@
 \beqn
-g \d z \mapsto \op{Res}_{1d} (f g \d z) .
+g \, \d z \mapsto \op{Res}_{1d} (f g \d z) .
 \eeqn
+In this way, distributions and functions on the punctured formal disk are isomorphic.
 
@@
 \end{proof}
-
-\subsection{Distributions on punctured affine space}
-
-The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
-\beqn
-\sfR = \C[z_i,\lambda_i] \slash (\sum_i z_i \lambda_i = 1) .
-\eeqn
-Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by $z_1,z_2$.
-So I think
-\beqn
-\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (\sum_i z_i \lambda_i) .
-\eeqn
-
-Let $\Hat{\sfA}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
-The cohomology of $(\Hat\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
-
-\section{Recollection on anomalies for quantum moment maps}
-
-Let $V$ be a dg vector space and let $V^* = \Hom(V, \CC)$ denote its dual complex. 
-Consider the dg Poisson algebra $\cP = \Sym(V \oplus V^*)$ whose Poisson bracket extends the skew-symmetrized evaluation pairing on $V \oplus V^*$.
-We view $\cP$ as functions on the cotangent bundle~$T^* V$.
-Observe that the quadratic functions form a dg Lie subalgebra
-\[
-\cP_2 = (\Sym^2(V \oplus V^*), \{-,-\})
-\]
-of $\cP$.
-Note that for $V$ a finite-dimensional vector space concentrated in degree zero,
-there is a natural identification $\cP_2 = \frak{sp}(T^*V)$, which plays an important role in corollary~\ref{cor:trivforsp}.
-
-There is a natural deformation quantization of $\cP$ as a Weyl algebra $\cW$.
-Observe that there is a dg Lie subalgebra
-\[
-\cW_2 = (\Sym^2(V \oplus V^*) \oplus \Sym^0(V \oplus V^*), [-,-])
-\]
-of $\cW$.
-It is a central extension of $\cP_2$; let $\omega \in H^2(\cP_2)$ denote the associated 2-cocycle.
-
-Suppose that there is a Lie algebra map $J: \fg \to \cP_2$.
-We view as a special class of symmetries for the free theory encoded by $\cP$:
-these are the symmetries where $\fg$ deforms the system to another {\em free} system.
-This situation appears in the free field realization we are studying.
-
-\begin{lem}
-Given a Lie algebra map $J: \fg \to \cP_2$, the obstruction to $J$ being a map of Lie algebras $\fg \to \cW_2$ is the 2-cocycle $J^* \omega \in H^2(\fg)$.
-\end{lem}
-
-We call $J^*\omega$ the {\em anomaly} for quantizing this symmetry.
-
-\begin{cor}
-If the anomaly $J^*\omega$ does not vanish, then there is an $L_\infty$ algebra map $J^q: \widehat{\fg} \to \cW_2$ out of the $L_\infty$ extension
-\[
-\CC \to \widehat{\fg} \to \fg
-\]
-determined by $J^* \omega$.
-\end{cor}
-
-On the other hand, this phenomenon does not happen in the most traditional situations.
-
-\begin{cor}
-\label{cor:trivforsp}
-For $V$ a finite-dimensional vector space concentrated in degree zero, the anomaly $\omega$ is trivial as $\frak{sp}(T^* V) = \cP_2$ is simple and hence $H^2(\cP_2) = 0$.
-\end{cor}
-
-In other words, quadratic Hamiltonians (elements of $\cP_2$) admit a natural quantization (lift to $\cW_2$).
-Normal ordering offers a method, but there are other choices.
-
-\owen{I am not sure what the status is for infinite-dimensional vector spaces. It seems like functional analysis plays a nontrivial role.}
 
@@
 
+\section{Recollection on anomalies for quantum moment maps}
+
+Let $V$ be a dg vector space and let $V^* = \Hom(V, \CC)$ denote its dual complex. 
+Consider the dg Poisson algebra $\cP = \Sym(V \oplus V^*)$ whose Poisson bracket extends the skew-symmetrized evaluation pairing on $V \oplus V^*$.
+We view $\cP$ as functions on the cotangent bundle~$T^* V$.
+Observe that the quadratic functions form a dg Lie subalgebra
+\[
+\cP_2 = (\Sym^2(V \oplus V^*), \{-,-\})
+\]
+of $\cP$.
+Note that for $V$ a finite-dimensional vector space concentrated in degree zero,
+there is a natural identification $\cP_2 = \frak{sp}(T^*V)$, which plays an important role in corollary~\ref{cor:trivforsp}.
+
+There is a natural deformation quantization of $\cP$ as a Weyl algebra $\cW$.
+Observe that there is a dg Lie subalgebra
+\[
+\cW_2 = (\Sym^2(V \oplus V^*) \oplus \Sym^0(V \oplus V^*), [-,-])
+\]
+of $\cW$.
+It is a central extension of $\cP_2$; let $\omega \in H^2(\cP_2)$ denote the associated 2-cocycle.
+
+Suppose that there is a Lie algebra map $J: \fg \to \cP_2$.
+We view as a special class of symmetries for the free theory encoded by $\cP$:
+these are the symmetries where $\fg$ deforms the system to another {\em free} system.
+This situation appears in the free field realization we are studying.
+
+\begin{lem}
+Given a Lie algebra map $J: \fg \to \cP_2$, the obstruction to $J$ being a map of Lie algebras $\fg \to \cW_2$ is the 2-cocycle $J^* \omega \in H^2(\fg)$.
+\end{lem}
+
+We call $J^*\omega$ the {\em anomaly} for quantizing this symmetry.
+
+\begin{cor}
+If the anomaly $J^*\omega$ does not vanish, then there is an $L_\infty$ algebra map $J^q: \widehat{\fg} \to \cW_2$ out of the $L_\infty$ extension
+\[
+\CC \to \widehat{\fg} \to \fg
+\]
+determined by $J^* \omega$.
+\end{cor}
+
+On the other hand, this phenomenon does not happen in the most traditional situations.
+
+\begin{cor}
+\label{cor:trivforsp}
+For $V$ a finite-dimensional vector space concentrated in degree zero, the anomaly $\omega$ is trivial as $\frak{sp}(T^* V) = \cP_2$ is simple and hence $H^2(\cP_2) = 0$.
+\end{cor}
+
+In other words, quadratic Hamiltonians (elements of $\cP_2$) admit a natural quantization (lift to $\cW_2$).
+Normal ordering offers a method, but there are other choices.
+
+\owen{I am not sure what the status is for infinite-dimensional vector spaces. It seems like functional analysis plays a nontrivial role.}
+
+\section{Recollections on one-dimensional algebraic free field realization}
+
 \end{document}

### 2023-08-19 highervertexops.tex
first pass at outlining strategy for 2cocycle

@@
 \newcommand{\sfc}{\mathsf{c}}
+\DeclareMathOperator{\colim}{colim}
 
@@
 
-\section{Overview of definitions and goalds}
+\section{Overview of definitions and goals}
 
@@
 
+Let $\CC^\infty$ denote the direct sum of countably many copies of $\CC$.
+We will fix a basis $\{x_n\}_{n \in \ZZ}$.
+This vector space can also be described as the colimit of finite-dimensional spaces under inclusion 
+\[
+\CC^{2N+1} \cong \bigoplus_{n = -N}^N \CC x_n \hookrightarrow \bigoplus_{n = -N-1}^{N+1} \CC x_n \cong \CC^{2N+3}.
+\]
+Later we will identify this vector space with Laurent polynomials $\CC[t,t^{-1}]$ by identifying $t^n$ with~$x_n$.
+
+There are then two distinct infinite-dimensional Lie algebras that naturally act on this space:
+\[
+\gl_\infty \hookrightarrow \End(\CC^\infty).
+\]
+Here
+\[
+\gl_\infty = \colim \gl_{2N+1} = \bigoplus_{m,n \in \ZZ} \Hom(\CC x_m, \CC x_n),
+\]
+and, in concrete terms, it corresponds to those matrices acting on $\CC^\infty$ that have finitely many nonzero entries.
+By contrast, 
+\[
+\End(\CC^\infty) = \Hom \left(\bigoplus_{m \in \ZZ} \CC x_m, \bigoplus_{n \in \ZZ} \CC x_n \right) \cong \prod_{m\in \ZZ} \bigoplus_{n \in \ZZ} \Hom(\CC x_m, \CC x_n),
+\]
+and, in concrete terms, it corresponds to those matrices where each column has finitely many nonzero entries but a row can have arbitrarily many nonzero entries.
+
+In between these two sits an interesting Lie algebra $\Bar{\gl}(\infty)$ consisting of matrices with finitely many nonzero {\em diagonals}.
+
+This Lie algebra has two features crucial for us:
+\begin{enumerate}
+\item It contains the shift operators $S_k: x_n \mapsto x_{n+k}$ and hence contains $\CC[t,t^{-1}]$ as a subalgebra (note that multiplication by $t^k$ corresponds to $S_k$).
+More generally, every loop algebra $\gl_N(\CC[t,t^{-1}])$ embeds into $\Bar{\gl}(\infty)$.
+\item It has a nontrivial 2-cocycle
+\end{enumerate}
+
 \end{document}

### 2023-08-21 highervertexops.tex
first attempt at defining cocycle

@@
 
-In between these two sits an interesting Lie algebra $\Bar{\gl}(\infty)$ consisting of matrices with finitely many nonzero {\em diagonals}.
+In between these two sits an interesting Lie algebra $\Bar{\gl}_\infty$ consisting of matrices with finitely many nonzero {\em diagonals}.
 
@@
 \item It contains the shift operators $S_k: x_n \mapsto x_{n+k}$ and hence contains $\CC[t,t^{-1}]$ as a subalgebra (note that multiplication by $t^k$ corresponds to $S_k$).
-More generally, every loop algebra $\gl_N(\CC[t,t^{-1}])$ embeds into $\Bar{\gl}(\infty)$.
-\item It has a nontrivial 2-cocycle
+More generally, every loop algebra $\gl_N(\CC[t,t^{-1}])$ embeds into~$\Bar{\gl}_\infty$.
+\item It has a nontrivial 2-cocycle $\Bar{\alpha}$ where
+\[
+\Bar{\alpha}(E_{ij}, E_{mn}) =
+\begin{cases}
+1, & i = n, j = m, i \leq 0, j \geq 1\\
+-1, & i = n, j = m, n \leq 0, m \geq 1\\
+0, & \text{otherwise}
+\end{cases}.
+\]
 \end{enumerate}
+These features interact because for any embedding $\iota$ of a loop algebra, 
+the pullback $\iota^*\Bar{\alpha}$ determines a nontrivial central extension: 
+it yields the famous affine Lie algebra using the residue pairing.
+(One can see $\Bar{\alpha}$ is nontrivial by using the fact that the affine Lie algebra is a nontrivial extension.)
+
+\begin{rmk}
+Kac and Peterson (as well as Date, Jimbo, et al) found this extension by $\Bar{\alpha}$ because they'd found that $\Bar{\gl}_\infty$ has a {\em projective} representation on the infinite wedge space.
+By the embedding fact, {\em every} affine Lie algebra also acts on the infinite wedge space.
+\end{rmk}
+
+\section{Trying to mimic this strategy}
+
+We will try to replicate the strategy above but replacing $\CC[t,t^{-1}]$ by $\sfH = H^\bullet(\sfA)$.
+Recall that
+\[
+\sfH^\bullet = 
+\begin{cases}
+\CC[z_1,z_2],&\bullet = 0\\
+\CC[z_1^{-1}, z_2^{-1}] \omega,&\bullet = 1\\
+0,&\text{otherwise}\\
+\end{cases}
+\]
+where $\omega$ denotes the Martinelli-Bochner form
+\[
+\frac{\zbar_2 \d\zbar_1 - \zbar_1 \d\zbar_2}{(2\pi i)^2|z_1 z_2|^2},
+\]
+which is the two-dimensional analog of $\d z/2\pi i z$.
+Note that we have a natural basis for $\sfH$ via monomials $z_1^a z_2^b$, with $a,b \in \NN$, and $z_1^{-a} z_2^{-b} \omega$, with $a,b \in \NN$.
+
+There is a natural {\em residue} operation on $\sfH$,
+which simply takes the coefficient on $\omega$ and vanishes on a nontrivial monomial times~$\omega$.
+In terms of calculus, it means that one wedges with $\d^2 z$ and then integrates over the unit ball.
+This residue determines a pairing on $\sfH$ by mimicking the one-dimensional case:
+\[
+(z_1^m z_2^n, z_1^{-k} z_2^{-l} \omega) =  \delta_{mk} \delta_{nl},
+\]
+which has degree -1 and hence vanishes between elements of the same degree.
+
+In a similar way, we introduce a trilinear form of degree -1 by
+\[
+\alpha_{(2)}( f, g, h \omega) = \int_{|z| \leq 1} \partial(f) \wedge \partial(g) \wedge h \omega.
+\]
+\owen{Up to a constant that I'll worry about later.}
+In terms of monomials, it is
+\[
+\alpha_{(2)}( z_1^a z_2^b , z_1^m z_2^n, z_1^{-k} z_2^{-l} \omega) = (an - bm) \delta_{(a+m-1)k} \delta_{(b+n-1)l}.
+\]
+This formula actually determines a nontrivial 2-cocycle on $\sfH$, viewed as an abelian graded  Lie algebra.
+
+We want to find a 2-cocycle $\Bar{\alpha}_{(2)}$ on a graded Lie algebra
+\[
+\Bar{\gl}_\infty^{(2)} \subset \End(\sfH)
+\]
+that pulls back to $\alpha_{(2)}$ along an embedding $\sfH \hookrightarrow \Bar{\gl}_\infty^{(2)}$ that factors the canonical inclusion $\sfH \hookrightarrow \End(\sfH)$ sending an element $a$ to left multiplication by~$a$.
+
+Here is a cheeky and inexplicit way to define $\Bar{\gl}_\infty^{(2)}$: take the smallest sub-associative algebra of $\End(\sfH)$ that contains both $\sfH$ and $\gl_\infty^{(2)}$ (which is simply the direct sum of the homs between basis elements).
+\owen{I think this works but it's ``smaller'' than the corresponding one-dimensional $\Bar{\gl_\infty}$.}
+
+We introduce the following notation for elements of $\gl_\infty^{(2)}$:
+\begin{itemize}
+\item Let $E^0_{ab, cd}$ denote the matrix sending $z_1^a z_2^b$ to $z_1^c z_2^d$.
+\item Let $E^+_{ab, cd}$ denote the matrix sending $z_1^a z_2^b$ to $z_1^{-c} z_2^{-d} \omega$.
+\item Let $E^-_{ab, cd}$ denote the matrix sending $z_1^{-a} z_2^{-b} \omega$ to $z_1^c z_2^d $.
+\end{itemize}
+Note that the superscript indicates whether the matrix has degree 0, +1, or -1, respectively.
+The subscripts $a,b,c,d$ are all nonnegative integers.
+
+Here is a guess for $\Bar{\alpha}_{(2)}$.
+It vanishes unless there are two entries of degree 0 and one entry of degree 1.
+We define
+\[
+\Bar{\alpha}(E^0_{ab}, E^0_{mn}, E^{+}_{kl}) = \delta_{(a+m)k} \delta_{(b+n)l}
+\]
+and impose the relevant sign for permuting the entries.
+\owen{This description is under-determined. I need to improve it.}
 

### 2023-08-22 highervertexops.tex
alternatives for 2d algebra

@@
 \]
-that pulls back to $\alpha_{(2)}$ along an embedding $\sfH \hookrightarrow \Bar{\gl}_\infty^{(2)}$ that factors the canonical inclusion $\sfH \hookrightarrow \End(\sfH)$ sending an element $a$ to left multiplication by~$a$.
+that pulls back to $\alpha_{(2)}$ along an embedding $\sfH \hookrightarrow \Bar{\gl}_\infty^{(2)}$ that factors the canonical inclusion $\sfH \hookrightarrow \End(\sfH)$ sending an element $x$ to left multiplication by~$x$.
+This situation would be parallel to the one-dimensional construction.
 
-Here is a cheeky and inexplicit way to define $\Bar{\gl}_\infty^{(2)}$: take the smallest sub-associative algebra of $\End(\sfH)$ that contains both $\sfH$ and $\gl_\infty^{(2)}$ (which is simply the direct sum of the homs between basis elements).
-\owen{I think this works but it's ``smaller'' than the corresponding one-dimensional $\Bar{\gl_\infty}$.}
+\subsection{Defining the Lie algebra}
+
+Here is a cheeky and inexplicit way to define a $\Bar{\gl}_\infty^{(2)}$: take the smallest sub-associative algebra of $\End(\sfH)$ that contains both $\sfH$ and $\gl_\infty^{(2)}$ (which is simply the direct sum of the homs between basis elements).
+\owen{I think this works but it's ``smaller'' than the corresponding one-dimensional $\Bar{\gl_\infty}$.
+We could instead ask to include derivatives also, so that we contain differential operators.}
+
+As an alternative, we characterize what we mean by ``diagonals,'' as follows.
 
@@
 \begin{itemize}
-\item Let $E^0_{ab, cd}$ denote the matrix sending $z_1^a z_2^b$ to $z_1^c z_2^d$.
-\item Let $E^+_{ab, cd}$ denote the matrix sending $z_1^a z_2^b$ to $z_1^{-c} z_2^{-d} \omega$.
-\item Let $E^-_{ab, cd}$ denote the matrix sending $z_1^{-a} z_2^{-b} \omega$ to $z_1^c z_2^d $.
+\item Let $E^{00}_{ab, cd}$ denote the matrix sending $z_1^a z_2^b$ to $z_1^c z_2^d$.
+\item Let $E^{11}_{ab, cd}$ denote the matrix sending $z_1^{-a} z_2^{-b} \omega$ to $z_1^{-c} z_2^{-d} \omega$.
+\item Let $E^{01}_{ab, cd}$ denote the matrix sending $z_1^a z_2^b$ to $z_1^{-c} z_2^{-d} \omega$.
+\item Let $E^{10}_{ab, cd}$ denote the matrix sending $z_1^{-a} z_2^{-b} \omega$ to $z_1^c z_2^d $.
 \end{itemize}
-Note that the superscript indicates whether the matrix has degree 0, +1, or -1, respectively.
+Note that the superscript $ij$ indicates whether the matrix the degree of the domain and codomain, respectively.
 The subscripts $a,b,c,d$ are all nonnegative integers.
+
+\begin{dfn}
+Given a matrix $M \in \End(\sfH)$, its {\em support} is the set of indices $(i, j; a, b, c, d)$ for which its coefficient $M_i$ are not zero.
+\end{dfn}
+
+For example, the support of $E^{00}_{ab, cd}$ is $(0,0,a, b,c, d)$, 
+while the support of the identity is $\{(i,i;a,b,a,b) \,: \, i \in \{0,1\}, a,b \in \NN\}$.
+
+Consider now the operators arising from multiplication.
+In the one-dimensional case, the support of such multiplication operators (or shift operators) characterizes the diagonals,
+so we examine the two-dimensional structure at play.
+\begin{itemize}
+\item Multiplying by $z_1^m z_2^n$ is a linear map sending $z_1^a z_2^b$ to $z_1^{m+a} z_2^{n+b}$ and sending $z_1^{-a} z_2^{-b} \omega$ to $z_1^{m-a} z_2^{n-b} \omega$ for $m -a \leq 0$ and $n-b \leq 0$ (otherwise, the element maps to zero).
+Its support is 
+\[
+\{(0,0;a,b,m+a,n+b) \,: \, a,b \in \NN\} \cup \{(1,1;a,b,a-m,b-n) \,: \, 0 \leq m \leq a, 0 \leq n \leq b\}.
+\]
+\item Multiplying by $z_1^{-m} z_2^{-n} \omega$ annihilates anything in degree 1 and sends $z_1^a z_2^b$ to $z_1^{a-m} z_2^{b-n}$ for $a-m \leq 0$ and $b-n \leq 0$ (otherwise, the elements maps to zero).
+Its support is 
+\[
+\{(0,1;a,b,m-a,n-b) \,: \, 0 \leq a \leq m, 0 \leq b \leq n\}.
+\]
+\end{itemize}
+In light of this support structure, we pose the following definition.
+
+\begin{dfn}
+A matrix $M in \End(\sfH)$ has {\em finitely many diagonals} if its support is equal to the union of finitely many multiplication operators.
+\end{dfn}
+
+One could then define $\Bar{\gl}_\infty^{(2)}$ as matrices with finitely many diagonals.
+
+\subsection{Defining the cocycle}
 

### 2024-08-19 draft.tex
fix epigraph

--- 2023-01-27 draft.tex
@@
 \usepackage{macros, setspace}
+\usepackage{epigraph}
 
@@
 
-\dedicatory{To Yuri Manin, with gratitude and admiration.}
+\dedicatory{In memory of Yuri Manin, with gratitude and admiration.}
 
 \maketitle
+
+\epigraph{\itshape The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
+
 \tableofcontents
@@
 for more details we refer to \cite{Kapustin,GGW}. 
-This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta-\gamma$-\textit{system}.
+This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta\gamma$-\textit{system}.
 It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.
 
-There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta-\gamma$ system'.
+There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta\gamma$ system'.
 The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
@@
 Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
-This is one of the key differences between the ordinary $\beta-\gamma$ system and its higher dimensional version.
+This is one of the key differences between the ordinary $\beta\gamma$ system and its higher dimensional version.
 Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.
@@
 The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
-\subsection{Local version and examples from supersymmetric field theories}
+
+\subsection{The local definition, and examples from supersymmetric field theories}
 
@@
 
-There is the following local characterization of a holomorphic field theory which allows us to connect directly to supersymmetric field theories. 
+There is the following local characterization of a holomorphic field theory, 
+which allows us to connect directly to supersymmetric field theories. 
 Suppose that our spacetime is $\CC^n = \RR^{2n}$ and assume that the theory we are considering is translation invariant, meaning that there is an action buy the $2n$-dimensional Lie algebra spanned by the vector fields $\del / \del {z_i}, \del / \del {\zbar_i}$ for $i=1,\ldots,n$.
@@
 \subsection{An extended aside on perturbative quantization}
+
+\owen{I suggest we mostly move this to a later section and expand it substantially.}
 
@@
 Let $V$ be a vector space.
-Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta-\gamma$ system with values in~$V$.
+Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
 To a disc $D = D_r(z)$ this assigns the following cochain complex
@@
 The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.
-The vertex algebra associated to this disk algebra is the familiar $\beta-\gamma$-vertex algebra.
+The vertex algebra associated to this disk algebra is the familiar $\beta\gamma$-vertex algebra.
 
@@
 
-\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and higher free field realization}
-
-\owen{We should also discuss how these can reduce to LG B-models, as precursor to the Hori-Tong dualities.}
-
-A sheaf of chiral differential operators is a `chiralization' the familiar sheaf of differential operators on a complex manifold \cite{}.
-It is a sheaf of vertex algebras $\CDO_X$ on a complex manifold $X$ which satisfies the property that under the Zhu construction one has an isomorphism of sheaves of associative algebras
-\beqn
-\text{Zhu}(\CDO_X) \simeq \cD_X
-\eeqn
-where $\cD_X$ is the sheaf of differential operators.
-
-Unlike the sheaf of differential operators, one needs to fix additional data in order to define a sheaf of chiral differential operators. 
-For a smooth complex manifold $X$, one of the main results of \cite{} is that the obstruction to the existence of such a sheaf is given by
-\beqn
-\ch_2(\T_X) \in H^{2}(X, \Omega^{2,cl}_X) 
-\eeqn
-and the space of all such algebras of chiral differential operators is a torsor for the group $H^{1}(X, \Omega^{2,cl}_X)$.
-Here $\Omega^{2,cl}_X$ is the sheaf of closed holomorphic two-forms on $X$.
-
-Locally, on an affine patch in $X$, the vertex algebra $\CDO_X$ is equivalent to $N$-copies of the familiar $\beta\gamma$ vertex algebra, where $N = \dim_\CC(X)$. 
-We have seen that there is a natural generalization of the $\beta\gamma$ system to a holomorphic factorization algebra in any dimension.
-
-\begin{dfn}\label{dfn:cdo}
-A {\em sheaf of $n$-CDOs} on a manifold $X$ (of complex dimension $N$) is a sheaf of $n$-dimensional holomorphically translation invariant factorization algebras whose restriction to any $n$-disc is equivalent to the $n$-dimensional $\beta\gamma$ system (with target $\CC^N$).
-\end{dfn}
-
-\begin{thm}\label{thm:cdo}
-Suppose $X$ is a complex manifold satisfying 
-\[
-{\rm ch}_{n+1} (\T_X) = 0 \in H^{n+1} \big(X , \Omega^{n+1,cl}_X\big).
-\]
-Then, the set of equivalence classes of higher dimensional CDO's on $X$ is a torsor for the group $H^n \big(X , \Omega^{n+1, cl}_X\big)$. 
-If ${\rm ch}_{n+1}(\T_X) \ne 0$ then there does not exist a sheaf of higher CDO's on $X$. 
-\end{thm}
-
-Anticipated by Witten, and proved in \cite{GGW}, the sheaf of chiral differential operators is given by the algebra of local operators of a familiar chiral CFT: the $\beta\gamma$ system of maps $\CC \to X$.
-In this note, we have described a higher dimensional analog of this system as a holomorphic $\sigma$-model of maps $\CC^n \to X$. 
-We have already met the higher dimensional $\beta\gamma$ system on $\CC^n$.
-This is an $n$-dimensional holomorphic system described by an $n$-dimensional translation invariant factorization algebra.
-In part, the fields of this system constituted a holomorphic map $\gamma \colon \CC^n \to \CC^N$ together with its conjugate field $\beta$. ''
-
-We can reformulate this theorem to stress the role of the higher dimensional holomorphic OPE. 
-An alternative to Definition \ref{dfn:cdo} would be to first take the cohomology of the state space of the $\beta\gamma$ system to obtain the structure of a holomorphic $\PP_n$ algebra.
-Then, one can define a sheaf of higher CDO's as a sheaf of holomorphic $\PP_n$ algebras which is locally of the form \eqref{eqn:bgope}. 
-Theorem \ref{thm:cdo} still applies to show that a necessary condition for such a sheaf to exist is the vanishing of the $(n+1)$ component of the Chern character of $X$. 
-The global sections of such a sheaf will give rise to a single holomorphic $\PP_n$ algebra.
-
-Let's unravel this approach in the case $n=2$. 
-Label the local coordinate on the target by $\{w^i\}_{i=1,\ldots,N}$.
-
-The cohomology of the state space of the $2$-dimensional $\beta\gamma$ system is a graded polynomial algebra of the form
-%\[
-%\CC\big[\partial_{z_i}^{\bu \geq 0} \gamma, \partial^{\bu\geq 0}_{z_i} \beta \big]
-%\]
-\[
-\CC\bigg[\gamma^i[k,\ell] \; , \; \beta_j [k,\ell] \bigg]_{k,\ell \geq 0} .
-\]
-For $k,\ell \geq 0$ and $i,j=1,\ldots N$ the generator $\gamma^i[k,\ell]$ is of cohomological degree zero and the generator $\beta_j[k,\ell]$ is of cohomological degree $1$.
-
-The higher OPEs $\{\gamma^i[k,\ell], \gamma^j [p,q]\}^{r,s} = 0$, $\{\beta^i[k,\ell], \beta^j [p,q]\}^{r,s} = 0$ all vanish. 
-There is a nontrivial higher OPE between $\gamma^i$ and $\beta_j$, the simplest of such reads
-\[
-\big\{\gamma^i[0,0] , \beta_j[-1,-1] \big\}[r,s] = \delta_{r,0} \delta_{s,0} .
-\]
-In general, 
-\beqn\label{eqn:bgope}
-\big\{\gamma^i[k,\ell] , \beta_j[p-1,q-1] \big\}[r,s] = \delta_{r,k+p} \delta_{s,\ell+q} .
-\eeqn
-
-\subsubsection{Global sections, an example}
-
-We give a concrete description of 2-CDO's on the manifold $X = \PP^1$.
-In this case there is a unique sheaf of 2-CDO's that we denote by $2\CDO_{\PP^1}$ (here we are using the holomorphic $\PP_2$ description as the cohomology of the observables of the $\beta\gamma$ system on a $2$-disc).
-Consider the standard description of $\PP^1 = U \cup V$ where $U = {\rm Spec}(\CC[\gamma])$ and $V = {\rm Spec}(\CC[\gamma^{-1}])$.
-
-On $U$, $2\CDO_{\PP^1}(U)$ is the graded polynomial algebra $\CC[\gamma[k,\ell], \beta[p,q]]$. 
-On the intersection $U \cup V$ we glue by the transition function
-\begin{align*}
-\Tilde{\gamma} [k,\ell] & \define \gamma^{-1} [k,\ell] \\
-\Tilde{\beta} [p,q] & \define - \sum_{i+j+k=p} \sum_{i'+j'+k'=q} \gamma[i,i'] \gamma[j,j'] \beta[k,k'] + 2 \gamma[p+1, q] + 2 \gamma[p, q+1] .
-\end{align*}
-\brian{need to fix that I think}
-
-We can gain further insight into the structure of $2\CDO_{\PP^1}$ by the following result. 
-Classically, the target $\PP^1$ has an obvious geometric symmetry by the Lie algebra $\sl(2)$ which further lifts to a symmetry by the dg Lie algebra $\fa_2 \otimes \sl(2)$.
-
-\begin{prop}
-The graded vector space $H^\bu \big(\PP^1 \; , \; 2 \CDO_{\PP^1}\big)$ is a module for the graded Lie algebra $H^\bu(\sfA_2) \otimes \sl(2)$
-\end{prop}
-
-\begin{rmk}
-This result is to be contrasted with the case of ordinary CDO's on $\PP^1$. 
-Classically, the one-dimensional $\beta\gamma$ system of maps $\CC \to \PP^1$ has a symmetry by the current algebra $\sfA_1 \otimes \sl(2) = \sl(2)[z,z^{-1}]$. 
-At the quantum level, the global sections of ordinary CDO's over $\PP^1$ is a representation for affine Kac--Moody algebra $\Hat{\sl}_2$ at the {\em critical level} \cite[Theorem 5.7]{MSV}. 
-In fact, it is isomorphic to a direct sum of two copies of the vacuum representation at the critical level.
-This proposition shows that the classical $\sl(2)$-valued $S^3$-currents of global sections of 2-CDO's on $\PP^1$ acquire no such central extension. 
-\end{rmk}
-
-Instead of $\PP^1$ let's consider $\PP^2$ thought of as the Grassmannian of lines in $\CC^3$. 
-Since $\ch_3(\T_{\PP^2})$ is trivial
-the $\beta\gamma$ system of maps $\CC^2 \to \PP^2$ exists at the quantum level and we get a sheaf of 2-CDO's that we denote $2\CDO_{\PP^2}$.
-\footnote{The sheaf of ordinary CDO's is {\em not defined} on $\PP^2$.}
-
-The classical $\beta\gamma$ system has, as a symmetry algebra, the $\sl(3)$-valued $S^3$ currents $\sfA_2 \otimes \sl(3)$. 
-This is {\em not} a symmetry at the quantum level, rather a {\em higher dimensional Kac--Moody algebra} acts instead.
-
-Let $\theta \in {\rm Sym}^3(\sl(3))$ denote the invariant polynomial $(A,B,C) \mapsto {\rm tr}(ABC)$, where the trace is computed in the {\em defining} representation.
-Given $\theta$ we define, as in Section \ref{sec:KM}, the $2$-dimensional Kac--Moody algebra as the $L_\infty$ algebra central extension
-\[
-0 \to \CC K \to \Hat{\sl(3)}_{2,\theta} \to \sfA_2 \otimes \sl(3) \to 0 .
-\]
-
-\begin{prop}
-The graded vector space $H^\bu \big(\PP^2 \; , \; 2 \CDO_{\PP^2}\big)$ is a module for the $L_\infty$ algebra $\Hat{\sl(3)}_{2, \theta}$ whereby the central element $K$ acts by multiplication by some nonzero scalar.
-\end{prop}
-
-\subsubsection{Chiralization of the B-model}
-
-In a precise sense, one can view the higher dimensional $\beta\gamma$ system as a holomorphic refinement of a familiar algebra in topological field theory.
-
-\begin{prop}
-Let $X$ be a complex manifold with ${\rm ch}_{3}(\T_X) = 0$ and let $2\CDO_X$ be a sheaf of $2$-CDO's on $X$. 
-There is an equivalence of sheaves on $X$
-\[
-{\rm Zhu}_{\EE_2} \big(2\CDO_X) \simeq {\rm PV}^{\bu}_X \define \bigoplus_{i\geq 0} {\rm PV}^i_X [-i] .
-\]
-Furthermore, the underlying $\PP_2$-structure of the left hand side agrees with the standard Gerstenhaber structure on polyvector fields.
-\end{prop}
-
-\begin{rmk}
-In this sense, $2\CDO_X$ is a `chiralization' of the sheaf of polyvector fields.
-It is distinct from a more standard one coming from the holomorphic twist of the two-dimensional $\cN=(2,2)$ supersymmetric $\sigma$-model.
-\end{rmk}
-
-The expert reader will identify the sheaf appearing in the statement of this proposition as local observables of the topological $B$-model on $\RR^2$ with target $X$. 
-At the level of quantum field theories, the statement of this proposition is no surprise. 
-The key point is that the Zhu algebra (and its $\EE_n$ generalization) is an instance of ``dimensional reduction'' from a holomorphic theory to a topological one.
-
-On one hand, one considers the $\beta\gamma$ of maps from the two-dimensional complex manifold $\CC^\times \times \CC^\times$ with target manifold $X$:
-\[
-\T^*[-1] {\rm Map}\left(\CC_\dbar^\times \times \CC_\dbar^\times , X\right) \; \simeq \; {\rm Map}\left(\CC_\dbar^\times \times \CC_\dbar^\times , \T^*[1] X\right) .
-\]
-In this identification we have used the obvious Calabi--Yau form on $\CC^\times \times \CC^\times$. 
-The dimensional reduction of this mapping space along the `doubled' radial projection $\CC^\times \times \CC^\times \to \RR \times \RR$ is precisely the AKSZ description of the ordinary $B$-model with target $X$
-\[
-{\rm Map}\left(\RR^2_{\rm dR} , \T^*[1] X\right)
-\]
-in agreement with the proposition above.
-
-\subsubsection{Homogenous spaces}
-
-Suppose that $N$ is a unipotent subgroup of $G$.
-For $j \geq 1$ one has
-\[
-H^j \left( G / N \, ; \, \Omega^{n+1,cl}_{G/N} \right) \; \simeq \; H_{\rm dR}^{j+n+1} \big(G / N \big)
-\]
+\section{Constructing examples \& renormalization}
+
+\owen{We should review BW results and subsequent improvements by Gaiotto et al and Wang}
 
@@
 
-\subsubsection{The duality functor}
-
-There is a way to define the dual of any supersymmetric QCD theory with mesons that satisfies the following properties:
-\begin{itemize}
-\item In the case that there are no mesons in the original theory, like in the electric theory, the dual agrees with the magnetic theory.
-\item The dual of the magnetic theory is equivalent to the original electric theory. In other words, the double dual of the electric theory is equivalent to itself. 
-\end{itemize}
-%In fact, more generally, the double dual of any supersymmetric QCD with mesons returns the same theory (up to equivalence). 
-Let us briefly remark how this general duality looks classically in the holomorphic context.
-
-Suppose that we have a holomorphic QCD theory with $N$ colors, $F$ flavors, and with mesons $\mu$ valued in some vector space $V_M$. 
-The superpotential is $W(QQ^\dagger, \mu)$.
-The dual theory is again a holomorphic QCD theory with mesons.
-Precisely the dual theory is holomorphic QCD with $F-N$ colors, $F$ flavors, and mesons valued in 
-\beqn
-(\mu, \til \mu) \in V_M \oplus \C^{F^2} .
-\eeqn
-The superpotential of this dual holomorphic QCD theory (whose quarks we label by $\til Q$) is 
-\beqn
-\til W (\mu, \til \mu, \til Q) = W|_{\til \mu = Q Q^\dagger}(\mu, \til \mu) + \Tr \til{Q}^\dagger \til{\mu} \til{Q} .
-\eeqn
-Notice that when $V_M = 0, W=0$ this agrees with the dual magnetic theory that we introduced above.
-
-Now, let's suppose we start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
-The superpotential is $W = \Tr \check{Q}^\dagger \check{\mu} \check{Q}$. 
-Taking the dual of this theory we obtain holomorphic QCD with $N$ colors and $F$ flavors as expected.
-However, we have mesons $\check{\mu}$ and $\til \mu$ both valued in $\End(\C^F)$. 
-The superpotential is simply
-\beqn
-\til W = \Tr \check \mu \til \mu + \Tr \til Q^\dagger \check{\mu} \til Q .
-\eeqn
-The first term arises from substituting $\til \mu = \check Q \check Q^\dagger$ in the original magnetic superpotential. 
-This term has the effect of making both $\mu,\check \mu$ massive, and hence they can be integrated out to obtain the original electric theory. 
-(In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)
-
-\subsection{Evidence for holomorphic Seiberg duality}
-
-We now turn to examining evidence for the conjecture, which will, in turn, allow us to refine it.
-The first piece of evidence involves the classical field theories:
-\begin{enumerate}
-\item[(1)] Each theory has a moduli space of vacua, and there is a natural isomorphism between the spaces for theories dual according to the conjecture.
-\end{enumerate}
-This map determines a map of factorization algebras of classical observables,
-and it should deform to the map between the factorization algebras for the quantum theories.
-(There are some interesting geometric subtleties --- about stacks versus their affinizations --- that we discuss below.)
-
-As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{Whol}.
-There are then two further pieces of evidence when these quantum theories are examined:
-\begin{enumerate}
-\item[(2)] There are {\em flavor} symmetries by $SL(F)$ that act on the quarks and antiquarks of each theory, 
-and these can be matched under the duality. 
-For the classical holomorphic theories, these symmetries enhance to an action of infinite-dimensional algebra of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
-Under quantization, these have isomorphic anomalies.
-\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and these can be matched under duality.
-\end{enumerate}
-This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
-We now turn to fleshing out these assertions.
-
-\subsubsection{Moduli of vacua and quantization}
-
-It is fruitful, and standard in physics, to identify the simplest solutions to the equations of motion for a theory.
-Here that means a solution that is translation-invariant on $\CC^2$ (i.e., a constant solution),
-and we call such a solution a {\em classical vacuum}.
-Thus each theory has an associated {\em moduli space of classical vacua},
-which we describe below.
-Each vacuum determines a perturbative field theory that one could try to quantize,
-and we have shown the following.
-(Many arguments are close cousins of~\cite{EGW}, where we quantize every twist over a moduli of vacua of the $\cN=4$ supersymmetric Yang--Mills theory.)
-
-\begin{thm}
-Both $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F, \check{N})$ exist at the quantum level for any choice of classical vacuum. 
-That is, the anomaly to a perturbative BV quantization vanishes.
-In fact, the quantization is one-loop exact. 
-\end{thm}
-
-It is common in physics to study field theories defined on the spacetime $\RR^n$.
-As the underlying spacetime $\RR^n$ is a group under addition (i.e., it is the translation group),
-it is natural to ask for field theories with an action by translations.
-That is, since the fields are sections of a fiber bundle over $\RR^n$,
-one can ask for an equivariant fiber bundle and ask for the equations of motion (or action functional) to be equivariant under translations.
-In practice, physicists often work with field theories whose equations of motion are differential equations with constant coefficients.
-(Nearly all the examples we've discussed in this survey satisfy this condition.)
-
-Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
-A {\em classical vacuum} for the theory is a solution that is translation-invariant,
-i.e., a constant solution.
-As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
-\[
-\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
-\]
-given by the substack of constant solutions.
-We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.
-
-Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
-For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
-\[
-\cM_{\rm vac} \cong T^*[1-d]X.
-\]
-(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
-For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
-\[
-\cM_{\rm vac} \cong [V/G]
-\]
-where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
-The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
-the quotient by $G$ arises from the gauge transformation.
-For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
-\[
-\cM_{\rm vac} \cong [\fg^*/G],
-\]
-the coadjoint quotient stack of the group.
-\brian{The paragraph began with holomorphic theories, do you want to say twist of 4d N=1?}
-(We are working in a $\ZZ/2$-graded world here.)
-Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
-For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
-\[
-\cM_{\rm vac} \cong [X/G]
-\]
-where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.
-
-In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
-Instead, they have worked with a GIT quotient.
-For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
-\[
-V\Sslash G = \Spec(\cO(V)^G),
-\]
-the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
-This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
-This affinization might be seen as parametrizing ``states'' rather than solutions, 
-as it is defined via functions on the solutions (see Remark~\ref{sols vs states} for more on this aspect).
-
-We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
-Note that the font of M changes between stack and space.
-
-\begin{rmk}
-In practice physicists work with ordinary schemes (i.e., without any derived directions), 
-although one can also study the derived affine scheme that is the best approximation to a derived stack.
-Below we will always provide an ordinary scheme as the moduli {\em space},
-following the physicists.
-\end{rmk}
-
-It is familiar to geometers that this affinization forgets interesting information about the stack because an invariant function must be constant on the closure of any orbit.
-The canonical map
-\[
-[V/G] \to V\Sslash G
-\]
-often collapses orbits together.
-An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$.
-Its affinization is
-\[
-\gl_N \Sslash GL_N \cong \CC^N
-\]
-by the Chevalley restriction theorem, 
-which says $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
-(The rightmost algebra is symmetric polynomials in the eigenvalues.)
-The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
-In other words, the canonical map collapses together Jordan blocks with the same diagonal entries.
-For this reason, it loses details about the classical vacua remembered by the stack quotient.
-
-\begin{rmk}\label{sols vs states}
-The physicists' focus on the moduli space is not unreasonable:
-one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
-The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
-In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
-On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
-and hence records much more about the classical theory; 
-the space cannot distinguish between some vacua because it collapses orbits.
-Moreover, the stack encodes much more data about the theory near each vacuum.
-For instance, it remembers ``enhanced symmetries'' (such as the residual gauge fields) at each vacuum.
-\end{rmk}
-
-For the holomorphic QCD theory with $F$ flavors and $N$ colors (without mesons), 
-the moduli stack of classical vacua is 
-\[
-\cM_{\rm vac}(\cT_{\sfE}(F,N)) \cong T^*[1] \left(V_Q \times V_Q^*/SL(N)\right).
-\]
-By contrast the moduli space $M_{\rm vac}$ is a variety already well-studied in classical algebraic geometry.
-Before we describe the full space, let's examine a simpler case involving just the quarks.
-A vacuum for the quark field is an element of $V_Q = \Hom(\CC^F, \CC^N)$,
-and it is a classic result of invariant theory that
-\[
-\Hom(\CC^F, \CC^N)\Sslash SL(N) \cong \widehat{{\rm Gr}(F, N)} \subset \Lambda^N \CC^F
-\]
-where ${\rm Gr}(F, N)$ denotes the Grassmannian of $N$-planes in $\CC^F$ and the hat indicates we take the affine cone with respect to this standard Pl\"ucker embedding.
-
-For the full problem, we have both quarks and antiquarks, so
-\begin{align*}
-M_{\rm vac}(\cT_{\sfE}(F,N)) 
-&\cong V_Q \times V_Q^*\Sslash SL(N) \\
-&= \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)\Sslash SL(N),
-\end{align*}
-whose ring of functions is also computed by the fundamental theorems of invariant theory.
-Those theorems tell us that the GIT quotient is a closed conical subvariety
-\[
-M_{\rm vac}(\cT_{\sfE}(F,N))  \hookrightarrow \Lambda^N \CC^F \times \Lambda^N (\CC^F)^* \times \End(\CC^F)
-\]
-where a pair of matrices $(X,Y) \in \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)$ goes to $(\Lambda^N X, \Lambda^N Y, YX)$, with $\Lambda^N X$ denoting the wedge product of the rows of $X$ (and of columns for $Y$).
-The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem, such as that the pairing of $\Lambda^N X$ and $\Lambda^N Y$ can be related to $\Lambda^N (YX)$.
-(See Chapter 2, Section C of \cite{Weyl}.)
-In other words, we have a closed subvariety
-\[
-M_{\rm vac}(\cT_{\sfE}(F,N)) \hookrightarrow \widehat{{\rm Gr}(F, N)} \times \widehat{{\rm Gr}(F, N)} \times {\rm R}(F,N)
-\]
-with ${\rm R}(F,N) \subset \End(\CC^F)$ the matrices with rank bounded above by~$N$.
-The moduli space for the magnetic theory is a bit more complicated but follows from classical invariant theory as well.
-
-Note that $\check{N} = F-N$, so ${\rm Gr}(F, N) \cong {\rm Gr}(F, \check{N})$ and a (partial) duality is apparent.
-On the other hand, ${\rm R}(F,N)$ is not isomorphic to ${\rm R}(F,\check{N})$ except when $N = \check{N}$.
-Hence one should not be optimistic that $M_{\rm vac}(\cT_{\sfE}(F,N)) \cong M_{\rm vac}(\cT_{\sfE}(F,N))$.
-To ``fix'' this issue, one might try to slightly modify the dual side, which Seiberg did by adding the meson fields.
-Hence the following holds.
-
-\begin{prop}
-Seiberg dual theories have isomorphic moduli spaces:
-\[
-M_{\rm vac}(\cT_{\sfE}(F,N)) \cong M_{\rm vac}(\cT_{\sfM}(F,\check{N})).
-\]
-\end{prop}
-
-This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
-The proof boils down to checking that the mesons and the superpotential on the magnetic side ensure the isomorphism.
-
-\begin{rmk}
-In the literature this isomorphism is given by explicitly matching gauge-invariant functions, 
-which physics paper often call mesons or baryons, 
-as they can be identified with the data that identifies such particles.
-These meson and baryons are precisely the usual generators of the ring of invariant functions, 
-so an isomorphism of generators determines the desired isomorphism of rings. 
-One must check that the relations are satisfied;
-this requirement explains the superpotential on the magnetic side.
-\end{rmk}
-
-We want to point out, however, that {\em the moduli stacks are not isomorphic}.
-A quick check is to note that there are orbits with different stabilizer groups.
-Consider, for instance, the origin in each vector space.
-On the electric side its stabilizer is $SL(N)$ and on the magnetic side it is $SL(\check{N})$.
-Thus each theory has a vacuum whose associated perturbative classical theory has no partner on the other side.
-Hence Seiberg duality cannot hold at the stack level for the classical theories.
-
-\subsubsection{Flavor symmetry enhancement}
-
-The quarks of the electric theory take values in $\Hom(\CC^F, \CC^N)$ and hence have a canonical action of $SL(F)$ by precomposition.
-We view each factor $\CC$ inside $\CC^F$ as a different ``flavor'' of quark, so this action mixes flavors.
-The antiquarks take values in $\Hom(\CC^N, \CC^F)$ and so have a canonical action of $SL(F)$ by postcomposition.
-The action functional is invariant for this action, and thus $SL(F)$ acts naturally on the space of solutions to the equations of motion.
-This symmetry is known as {\em flavor} symmetry.
-The magnetic theory has an analogous flavor symmetry, where $SL(F)$ acts on the mesons by conjugation.
-
-%We fix some notation for the fields of the electric and magnetic theories. 
-%The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$. 
-%
-%With respect to a basis for $\CC^{N_f}$ we denote the matter fields of the electric theory as
-%\[
-%Q^i\; , \; P_i \; , \; \Tilde{Q}_i \; , \; \Tilde{P}^i , \quad i = 1, \ldots, N_f.
-%\]
-%Each of these fields are Dolbeault forms that are valued in the fundamental $\SU(N_c)$ representation. 
-%
-%The matter fields of the magnetic theory will be denoted by lower case letters to avoid confusion
-%\[
-%q^i\; , \; p_i \; , \; \Tilde{q}_i \; , \; \Tilde{p}^i , \quad i = 1, \ldots, N_f.
-%\]
-%Again, each of these fields are Dolbeault valued but this time they each transform under the fundamental $\SU(N_f-N_c)$ representation. 
-%On the magnetic side one also has the `meson' fields $M_{i}^j$, which are scalars under the gauge group.
-%
-%Holomorphic QCD enjoys a few familiar holomorphic symmetries in the style that we discussed in this note.
-
-For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(F))$.
-It acts by wedging the forms and applying $\sl(F)$ to the relevant vector space, such as~$\Hom(\CC^F,\CC^N)$.
-On affine space, this dg Lie algebra is quasi-isomorphic to $\lie{sl}(F) \otimes \cO(\C^2)$, where $\cO(\C^2)$ denotes holomorphic functions on $\C^2$---this is like a current algebra in two complex dimensions.
-
-There is another dg Lie algebra obtained by evaluating the theory on punctured affine space $\C^2 - 0$.
-We recalled in \S \ref{sec:punctured} an algebraic model $\sfA_2$ for the dg algebra $\Omega^{0,\bu}(\C^2 - 0)$.
-The dg Lie algebra we assign to the punctured affine space, classically, is $\lie{sl}(F) \otimes \sfA_2$.
-Recall that we can think about elements of this algebra as being supported on three-spheres $S^3$ inside $\C^2 - 0$.
-This $S^3$-mode algebra acts on the local observables at the classical level.
-
-A natural question is whether this symmetry persists at the quantum level. 
-The answer is {\em yes}, but on both sides of the duality one must use a central extension of the current algebra as an $L_\infty$ algebra.
-The extension arises because the symmetry has an anomaly under quantization (on either side of the duality),
-and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
-(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(F)}_{2,\theta_{\sfE}}, \Hat{\sl(F)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - 0$.)
-
-\begin{prop}
-For both the electric and magnetic theories, there is an anomaly at the quantum level for the holomorphic flavor symmetry action.
-These anaomlies agree: they are labeled by the same cocycle 
-\[
-\theta_\sfE = \theta_\sfM.
-\] 
-In particular, the local observables $\Obs_{\sfE} (0), \Obs_{\sfM} (0)$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(F)}_{2,\theta}$ which is a central extension of the $S^3$-mode algebra $\sl(F) \otimes \sfA_2$.
-\end{prop}
-
-An analogous result holds for the flavor symmetry on the antiquarks.
-
-\begin{proof}[Sketch of proof]
-The argument boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
-For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
-The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,\bu}(\CC^2, \sl(F))$, which we treat as a background gauge field.
-In formulas, we couple the current algebra to both the electric and magnetic theory via interactions
-\[
-I^F_\sfE = \int (R, \sfa Q)  \qquad\text{and}\qquad I^F_\sfM = \int (\check{R}, \sfa \check{Q}) + \int (\check{\nu}, \sfa \check{\mu}),
-\]
-where we use parentheses $(-,-)$ to denote the pairings in BF and $\beta\gamma$ theories.
-
-In the electric case there are $N$ such diagrams, with all the internal edges are labeled by $Q-R$ propagators. 
-This gives rise to the local anomaly
-\beqn\label{eqn:electricflavor}
- \frac{N}{16 \pi^2} \int \op{tr}_{\underline{F}} \left(\sfa \, \partial \sfa \, \partial \sfa\right) 
-\eeqn
-where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.\footnote{The overall analytic coefficient can be explicitly determined, see \cite{GWkm} for related computations.}
-
-The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: 
-\begin{itemize}
-\item[(a)] those with  internal edges labeled by $\check{Q}-\check{R}$ propagators and 
-\item[(b)] those will internal edges labeled by $\check{\mu}-\check{\nu}$ propagators. 
-\end{itemize}
-There are $\check{N} = F - N$ copies of diagram (a), which gives rise to the term
-\[
- \frac{\check{N}}{16 \pi^2} \int \op{tr}_{\underline{F}^*} \left(\sfa \, \partial \sfa \, \partial \sfa\right) .
-\]
-Here, $\op{tr}_{\underline{F}^*}$ denotes the trace in the dual to the fundamental representation. 
-There are $F$ copies of diagram (b), which gives rise to the term
-\[
-\frac{F}{16\pi^2}\int \op{tr}_{\underline{F}} \left(\sfa\, \partial \sfa \, \partial \sfa\right).
-\]
-Since $\op{tr}_{\underline{F}^*} (T^3) = - \op{tr}_{\underline{F}} (T^3)$ for any $T \in \sl(F)$, 
-we see that the sum of these two terms agrees with \eqref{eqn:electricflavor} on the electric side.
-\end{proof}
-
-\subsubsection{Twisted superconformal symmetry}
-
-\owen{I'm now pretty lost in how this section discusses evidence for Seiberg duality.}
-
-A superconformal algebra is a simple super Lie algebra which contains both the ordinary algebra of infinitesimal conformal transformations and the super Lie algebra of supertranslations.
-It is a basic fact of life that all (super)conformal algebras in dimensions $\geq 3$ are finite-dimensional.
-Being a superconformal theory means that the theory admits a symmetry by a particular superconformal algebra---it is, generally speaking, a very rigid condition on a theory.
-
-The (complexified) $\cN=1$ superconformal in four-dimensions is $\sl(4|1)$.
-This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
-%The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
-Inside of this algebra is the Cartan generator $\Delta$ of which is an infinitesimal generator for scaling transformations in~$\RR^4$.
-
-Fix the same square-zero supercharge $\cQ$ inside of the four-dimensional $\cN=1$ supersymmetry algebra which we use to define the holomorphic twists of Seiberg dual gauge theories. 
-Naturally, such a $\cQ$ acts by the (super)commutator on the superconformal Lie algebra.
-There is a quasi-isomorphism of dg Lie algebras
-\[
-\bigg(\sl(4|1) \; , \; [\cQ, -] \bigg) \simeq \sl(3) ,
-\]
-see \cite{SWsuco}, for example.
-So, if one starts with a superconformal theory, the Lie algebra $\sl(3)$ is guaranteed to act on the holomorphically twisted theory. 
-In this sense, $\sl(3)$ is the residual superconformal symmetry of this twist. 
-The entire algebra $\sl(3)$ naturally embeds inside of the Lie algebra of holomorphic vector fields on $\CC^2$,
-where we view $\CC^2$ as an open subset of $\CC \PP^2$ as an $SL(3)$-homogenous space.
-(In a moment we will discuss how all holomorphic vector fields act on the theories.)
-Inside of this twisted algebra $\sl(3)$, we have the ``holomorphic scaling'' operator 
-\beqn
-\Delta^{hol} = z_1 \del_{z_1} + z_2 \del_{z_2},
-\eeqn 
-which is simply the holomorphic Euler vector field.  
-We focus on this scaling operator as it is closely related to questions of renormalization group flow in the original, untwisted theory.
-
-Let's consider just a free theory consisting of a single chiral multiplet, for the moment.
-Here, the $R$-symmetry group is $U(1)$.
-The holomorphic supercharges breaks the $SO(4;\C)$ symmetry down to the group $MU(2)$, a double cover of $U(2)$.
-To perform the twist of a theory there are always two steps: the first is to `twist' the fields of the theory using the $R$-symmetry and the second is to deform the action by the supercharge $\cQ$.
-To have a consistent data to twist, one usually imposes the condition that with respect to the twisted $R$-symmetry action the supercharge $Q$ is invariant.
-The odd part of the four-dimensional $\cN = 1$ algebra is given by 
-\beqn
-S_+ \otimes W \oplus S_- \otimes W^*
-\eeqn
-where $W \cong \C$ is just a one-dimensional vector space and $S_{\pm}$ are the positive and negative semi-chiral spin representations of $\lie{so}(4;\C)$.
-We will take the square-zero supercharge to live in $\cQ \in S_+ \otimes W$.
-As an $MU(2)$ representation one has $S_+ \cong \det(L)^{+1/2} \oplus \det(L)^{-1/2}$.
-Thus, if $\cQ$ lies in the first summand, in order to make $\cQ$-invariant we must twist by the condition that $W$ has weight $-1/2$ under the $R$-symmetry.
-We will fix this twisting data.
-
-The basic components of the chiral multiplet is a pair of bosons $(\phi,\Bar{\phi})$, and a pair of fermions $(\psi_+,\psi_-)$ where $\psi_{+}$ takes values in $S_+$ and $\psi_-$ takes values in $S_-$.
-For a free theory, we may assign any $R$-charge to $\psi_+$ and this determines the $R$-charges of all remaining fields. 
-For example, if the $R$-charge of $\psi_+$ is $r$ then the $R$-charge of $\phi$ is $r+1$, the $R$-charge of $\psi_-$ is $-r$, and the $R$-charge of $\Bar{\phi}$ is $-r - 1$.
-
-If we twist using the data where $\cQ$ is invariant, then the particular choice of $r$ will dictate how the holomorphic scaling operator $\Delta^{hol}$ acts on the theory.
-One finds that the holomorphic twist of the free chiral theory (which is just a single quark in the above terminology) has fundamental field
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2}) 
-\] 
-where $K$ denotes the holomorphic canonical bundle.
-Of course, the canonical bundle on $\C^2$ is trivializable, so we obtain a theory with isomorphic space of fields for any choice of $r$; what changes is how the twisted superconformal symmetry algebra $\lie{sl}(3)$ acts.
-
-Now, let's consider the electric theory.
-We assume that the fermions in the quarks and anti-quark multiplets have the same $R$-charges.
-If this $R$-charge is $r$, then the twisted quarks and anti-quarks take the form
-\[
-Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q) \quad\text{and}\quad Q^\dagger \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{(r+1)/2} \otimes V_Q^*)
-\]
-where $V_Q \cong \C^{NF}$.
-In the untwisted theory the value $r$ is fixed by the condition that the $R$-symmetry is anomaly-free.
-In the twisted theory, the value of $r$ is fixed by the condition that the action by the holomorphic scaling operator is anomaly-free.
-This anomaly comes from a one-loop diagram with a single vertex labeled by $\Delta^{hol}$, and it leads to the constraint 
-\beqn
-N + F r = 0 .
-\eeqn
-In other words, $r = - N / F$. 
-This condition matches the corresponding condition for $R$-symmetry to be anomaly-free in the untwisted theory. 
-On the magnetic side the condition is $r = N/F - 1$.
-
-In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories are expected to flow to the same superconformal fixed point in the infrared limit. 
-This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
-(Note that it is preserved under swapping $N \leftrightarrow F-N$.)
-It would be interesting to explore how it appears from the point of view of holomorphic QCD.
-
-\begin{cor}
-{\em Divergence-free} holomorphic vector fields are a symmetry at the quantum level for any values of $F$ and~$N$.
-Only when $F = 3N$ do {\em all} holomorphic vector fields lift to a symmetry lifts at the quantum level.
-\end{cor}
-
-%
-%This action of $\sl(3)$ extends to the quantizations, on both sides of the putative duality, by direct verification.
-%In fact it holds for all holomorphic QCD theories, not just those in the superconformal window.
-
-%\begin{lem}
-%The action of $\sl(3)$ on $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$ extends to their quantizations.
-%\end{lem}
-%
-
-%In the holomorphic twist as a classical theory,
-%this $\sl(3)$-symmetry {\em enhances} to a symmetry by an infinite dimensional dg Lie algebra.
-%In fact, this enhancement also works for all holomorphic QCD theories, not just those in the superconformal window.
-%\owen{Am I understanding that correctly?}
-%
-%\begin{thm}[\cite{SWsuco}] 
-%\label{thm:swsuco}
-%Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
-%This local Lie algebra is a classical symmetry of {\em any} holomorphic QCD theory. 
-%\end{thm}
-%
-%We now ask when this classical symmetry persists at the quantum level, and an interesting anomaly emerges.
-%
-%\begin{prop}
-%For an electric theory $\cT_{\sfE}(F,N)$,
-%the symmetry by the local Lie algebra of holomorphic vector fields, described by Theorem~\ref{thm:swsuco}
-%has an anomaly to lift to the quantum level. 
-%It is proportional to the local functional
-%\[
-%\frac{F - 3N}{2} \int {\rm div}(X) \op{Tr} (\partial A \, \partial A)  .
-%\]
-%where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form-valued vector field and $A$ is a gauge field.
-%\end{prop}
-%
-%The first factor ${\rm div}(X)$ denotes the divergence $\sum_i\partial_{z_i} X_i$ of the vector field~$X$.
-%We thus deduce the following.
-%
-%\begin{cor}
-%Only when $F = 3N$ do all holomorphic vector fields lift to a symmetry lifts at the quantum level.
-%There is, however, a symmetry of {\em divergence-free} holomorphic vector fields at the quantum level for any values of $F$ and~$N$.
-%\end{cor}
-%
-%We will discuss how these enhanced symmetries might intertwine with duality below.
-%
-%\owen{Should we check that the quantum magnetic theory also has a divergence-free symmetry?}
-
-\subsubsection{The special case of $SU(2)$ SQCD}
-
-\owen{I like the idea of analyzing a special case, but I'm not sure what lesson the reader is supposed to learn.}
-
-Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
-In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
-\beqn
-(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
-\eeqn
-This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.
-
-On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
-\beqn
-V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
-\eeqn
-There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
-Again the flavor symmetry group admits an enhancement to $SU(2F)$.
-
-Let's further consider some special cases for small values of flavors.
-
-$\bullet \ul{F=2}$. \brian{I'm confused}
-
-$\bullet \ul{F=3}$. 
-In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
-\beqn
-(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
-\eeqn
-In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
-If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
-\beqn
-W = \frac16 \Phi \wedge \Phi \wedge \Phi .
-\eeqn
-We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
-The critical locus of $W$ is simply the space of solutions to the equation
-\beqn
-\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
-\eeqn
-This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.
-
-$\bullet \ul{F=4}$.
-This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
-On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
-On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.
-
-We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
-For $F \geq 4$ the
-
-%A duality 
-%
-%The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
-%The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
-%For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
-
-\subsection{A second pass at holomorphic Seiberg duality}
-
-In our attempts above to explore (and test) Eager's conjecture, we developed insights and highlighted issues that help to refine it.
-
-\subsubsection{Subtleties with vacua}
-
-We saw that the moduli stacks of classical vacua are not equivalent, due to points with interesting stabilizers.
-On the other hand, there is an open locus where the moduli stacks are equivalent:
-take the points of each moduli stack $\cM_{\rm vac}(\cT_{\sfE}(F,N))$ and $\cM_{\rm vac}(\cT_{\sfM}(F,\check{N}))$ where the stabilizer is a finite group,
-in other words, the stable locus.
-We use $\cM_{\rm vac}(\cT)^s$ to denote this open locus in the moduli stack of a theory~$\cT$.
-This locus agrees with a dense open subset of the affinization (or GIT quotient), 
-and the isomorphism of the moduli spaces determines an isomorphism between the stable locus of each stack.
-Let us try to unravel what this equivalence means for the field theories, both classical and quantum.
-
-Consider any stable point $x$ in $\cM_{\rm vac}(\cT)$ for some holomorphic QCD theory.
-We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
-For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the formal neighborhood of $x$ inside the moduli stack of vacua. 
-(This argument is a version of the Higgs mechanism, as phrased using the BV formalism.
-See \cite{EG} for an expository account.)
-We can assemble these perturbative theories into a holomorphic $\sigma$-model from $\CC^2$ into~$\cM_{\rm vac}^{s}$,
-using the methods of~\cite{GGW, WilThesis}.
-This emergence of a $\sigma$-model is reminiscent of chiral symmetry breaking.
-
-\begin{prop}
-For each holomorphic QCD theory $\cT$, 
-the stable locus $\cM_{\rm vac}(\cT)^s$ of its moduli stack parametrizes a family of holomorphic field theories on $\CC^2$, 
-and this family is isomorphic to the holomorphic $\sigma$-model from $\CC^2$ into~$\cM_{\rm vac}(\cT)^s$.
-\end{prop}
-
-This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in \owen{reference section of this paper}.
-\owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}
-\brian{that's a great question}
-
-The isomorphism of moduli spaces then ensures that there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$,
-because there is an explicit identification of the formal neighborhood of $x$ with the formal neighborhood of $x_D$. 
-Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
-Hence on the stable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.
-
-\begin{prop}
-There is an isomorphism of these holomorphic $\sigma$-models for the electric theory $\cT_{\sfE}(F,N)$ and the magnetic theory $\cT_{\sfM}(F,\check{N})$, lifting the isomorphism between their moduli spaces.
-
-This isomorphism determines an isomorphism between quantizations of these holomorphic $\sigma$-models, and hence between quantizations of the holomorphic QCD theories over the stable loci.
-\end{prop}
-
-In other words, Eager's conjecture is true over the stable loci: there is an isomorphism of sheaves of two-dimensional chiral differential operators.
-
-This identification breaks down on the non-stable locus, raising the following question:
-\begin{quote}
-At the quantum level, what happens on the non-stable locus? 
-\end{quote}
-Each non-stable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
-and hence its quantization is more involved that at a stable point and depends nontrivially the gauge group.
-The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.
-
-\subsubsection{A proposal}
-
-Recall that the moduli space arises from the moduli stack by affinization.
-In other words, we move from studying translation-invariant solutions (the stack) to studying ``states'' (multiplicative linear functionals on the stack of solutions).
-The moduli of classical states are isomorphic.
-We hope that something similar happens at the quantum level:
-there is a moduli stack of quantum vacua and a moduli space of quantum vacua,
-and we hope the spaces are isomorphic.
-We sketch the suggestion as follows.
-
-\begin{dfn}
-For a holomorphic QCD theory let the {\em moduli stack of quantum vacua} $\cM^q_{\rm vac}(F,N)$ mean the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf with values in factorization algebras on $\CC^2$.
-The value at a solution $x$ is a quantization of the observables for the classical perturbative theory labeled by~$x$.
-(One could focus, for simplicity, on the sheaf with values in polydiscs algebras.)
-\end{dfn}
-
-Bear in mind an important feature of this sheaf.
-Working on the stable locus $\cM_{\rm vac}(F,N)^{s}$, 
-we note that the sheaf of classical observables (as a sheaf with values in factorization algebras) has the property that its factorization homology on $\CC^2$ is the sheaf of {\em jets} of functions on $\cM_{\rm vac}(F,N)^{s}$.
-This sheaf has a natural flat connection, sometimes called the Grothendieck connection, and the horizontal sections are the structure sheaf $\cO$ of $\cM_{\rm vac}(F,N)^{s}$.
-In fact, as shown in \cite{GGW, WilThesis}, this flat connection makes sense even at the level of the factorization algebra,
-and not just on factorization homology.
-When we quantize, we wish to lift this flat connection as well.
-
-In fact, we expect that a version of this relationship extends to the whole stack $\cM_{\rm vac}(F,N)$,
-by using the methods of \cite{CPTVV}.
-In formulating the definition above, we are assuming that expectation holds.
-
-We now posit the following.
-
-\begin{dfn}
-Let the {\em moduli space of quantum vacua} $M^q_{\rm vac}(F,N)$ mean the global horizontal sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
-It is a factorization algebra on~$\CC^2$.
-(Again, one could focus, for simplicity, on the polydiscs algebra.)
-\end{dfn}
-
-We view $M^q_{\rm vac}(F,N)$ as an affinization of $\cM^q_{\rm vac}(F,N)$.
-Optimistically, we refine Eager's conjecture to the following.
-
-\begin{conj}
-Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
-There is an equivalence of 2-dimensional holomorphic factorization algebras
-\[
-M^q_{\rm vac}(F,N)_{\sfE} \simeq M^q_{\rm vac}(F,\check{N})_{\sfM}.
-\]
-\end{conj}
-
-We note that there may be many quantizations possible, but our experience in $\cN=4$ case suggests that there is an ``obvious'' one.
-
-\begin{rmk}
-We note that in the physics literature, there are a number of issues that are relevant in this setting.
-For instance, there are ``instanton corrections'' that cannot be found by perturbative techniques, although they can be treated in a mathematically precise way. 
-It is interesting to wonder how these would appear in the holomorphic setting.
-\end{rmk}
-
-\subsubsection{Two intriguing possibilities}
-
-In discussions with Costello and Gaiotto, there appeared two suggestions that, while optimistic, would make studying these theories and this duality much more tractable.
-\begin{enumerate}
-
-\item For any space $M$ and any point $p \in M$, there is a canonical algebra map $\cO(M) \to \cO(M)^\wedge_p$ sending a function on $M$ to its ``Taylor expansion'' at $p$. 
-Sometimes this map is injective. 
-Similarly, there is a map of holomorphic factorization algebras from the moduli space of quantum vacua to the observables of a perturbative theory (e.g., at a point $x$ in the stable locus).
-One might ask if this map retains all essential information. 
-If it does, then holomorphic Seiberg duality can be analyzed via the correspondence between points on the stable loci.
-(Of course, one must characterize ``essential'' here with precision.)
-
-\item We have described a quantum Noether map from the (enhanced) flavor symmetries to the observables of holomorphic QCD. 
-Optimistically, these symmetries might ``saturate'': this current map might be essentially surjective.
-In that case, these theories could be analyzed via the representation theory of the flavor symmetries.
-Such a situation would be reminiscent of minimal models in the one-dimensional chiral conformal setting.
-
-\end{enumerate}
-Exploring these possibilities would likely lead to substantially deeper understanding of holomorphic Seiberg duality.
-
-\subsection{Two-dimensional dualities by reduction}
+\subsection{A remark relating to homological projective duality}
 

### 2024-08-19 draft.tex
merge

--- 2023-01-27 draft.tex
@@
 A theory is usually described, in part, in terms of a space of fields which comprise some possibly nonlinear space like a mapping space or the space of connections. 
-In perturbative field theory, which describes the formal neighborhood of the theory at points in such spaces, the fields $\Phi$ are typically described by the smooth sections of a bundle on spacetime.
-The equations of motion which dictate the dynamics of the particular model are encoded by a partial differential equation heuristically of the form 
+In perturbative field theory, which describes the formal neighborhood of the theory at points in such spaces, the fields $\Phi$ are typically described by the smooth sections of a vector bundle on spacetime.
+The equations of motion which dictate the dynamics of the particular model are encoded by a series of partial differential equations of the form 
 \[
@@
 where $D_k$ is a $k$-ary polydifferential operator.
-As an example of a Euclidean theory, the $\phi^4$-theory on a Riemannian four-manifold $M$ is described by the equation
+As an example, the scalar $\phi^4$-theory on a Riemannian $M$ is described by the equation
 \[
@@
 where $\Phi = \phi$ is simply a smooth function on $M$.
+These equations of motion are natural to the Riemannian geometry of the manifold $M$, and can be derived from the Euler--Lagrange equations of the simple action functional $\int_M \phi \Delta \phi \, \op{dvol}$.
+
+As another example, consider perturbative Chern--Simons theory whose fields are a principal $G$-bundle $P$ on a smooth three-manifold $M$ equipped with a connection.
+The equations of motion is the condition that the connection is flat 
+\beqn
+F_\nabla = 0 .
+\eeqn
+Perturbatively, near the trivial flat connection, the fields are simply $\lie{g} = \op{Lie}(G)$-valued one-forms $A \in \Omega^1(M, \lie{g})$.
+The condition that perturbed connection $\d + A$ is flat is the Maurer--Cartan equation
+\beqn
+\d A + \frac12 [A,A] = 0.
+\eeqn
+These equations of motion are topological in the sense that they only depend on the smooth manifold~$M$.
+When $\lie{g}$ is equipped with a non-degenerate, invariant, bilinear form $\kappa$ (for example, if $G$ is semi-simple there is a standard choice) then these equations of motion can be derived from the famous Chern--Simons action functional $\int_M CS(A)$ where
+\beqn\label{eqn:CS}
+CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]) .
+\eeqn
 
 In a {\em holomorphic theory} one starts with a complex manifold $X$ as the spacetime.
-This means, in part, that the complexified tangent bundle of $X$ decomposes as a sum of vector bundles $\T_X \oplus \Bar{\T}_X$ where $\T_X$ (respectively $\Bar{T}_X$) is the holomorphic (respectively anti-holomorphic) tangent bundle.
-In local coordinates sections of $\T_X$ have the form $f^i \del / \del z_i$ whereas sections of $\Bar{\T}_X$ have the form $f^i \del / \del \zbar_i$.
-
+%This means, in part, that the complexified tangent bundle of $X$ decomposes as a sum of vector bundles $\T_X \oplus \Bar{\T}_X$ where $\T_X$ (respectively $\Bar{T}_X$) is the holomorphic (respectively anti-holomorphic) tangent bundle.
+%In local coordinates sections of $\T_X$ have the form $f^i \del / \del z_i$ whereas sections of $\Bar{\T}_X$ have the form $f^i \del / \del \zbar_i$. 
 Globally, holomorphic theories are described like in the usual case by mapping spaces or spaces of connections.
-The key feature in a holomorphic theory is that the equations of motion dictate that fields be holomorphic.
-Perturbatively, where fields are sections of some holomorphic vector bundle $V$, we can make this precise. 
+The key feature in a holomorphic theory is that the equations of motion dictate that fields be holomorphic in an appropriate sense.
+Perturbatively, where fields are sections of some (possibly graded) holomorphic vector bundle $V$, we can make this precise. 
 Prescribing a holomorphic structure on a vector bundle $V$ is equivalent to the data of a $\dbar$-operator
@@
 Holomorphicity of $V$ boils down to the requirement that $\dbar \circ \dbar = 0$.
-The Dolbeault complex of $V$ is the resulting complex $(\Omega^{0,\bu}(X, V), \dbar)$ where $\Omega^{0,q}(X,V)$ sits in degree $+q$.
+The Dolbeault complex of $V$ is
+\beqn
+\left(\Omega^{0,\bu}(X, V), \dbar \right) = \left(\oplus_{q \geq 0} \Omega^{0,q}(X, V)[-q], \dbar \right)
+\eeqn
+where (in the case that $V$ sits in degree zero) the space $\Omega^{0,q}(X,V)$ sits in degree $+q$.
 A standard result in complex geometry is that the Dolbeault complex is a resolution for the sheaf of holomorphic sections of the holomorphic vector bundle $V$.
-In the case that $V$ is the trivial bundle $\ul{\CC}$ the Dolbeault complex $\Omega^{0,\bu}(X)$ is a resolution for the sheaf of holomorphic functions on $X$.
-
-The fields of a holomorphic theory are given by elements of the Dolbeault complex $\Omega^{0,\bu}(X,V)$.
+%In the case that $V$ is the trivial bundle $\ul{\CC}$ the Dolbeault complex $\Omega^{0,\bu}(X)$ is a resolution for the sheaf of holomorphic functions on $X$.
+
+The fields of a holomorphic theory are given by elements of the Dolbeault complex $\Omega^{0,q}(X,V)$ for some $q$.
 The equations of motion in a holomorphic theory take the form
@@
 
+For a simple example, consider the following holomorphic analog of Chern--Simons theory.
+The fields are principal $G$-bundles on a three-dimensional \textit{complex} manifold $X$, and the equations of motion give the condition that the principal $G$-bundle is holomorphic.
+Perturbatively, near the trivial $G$-bundle, the fields of this holomorphic theory are $\lie{g}$-valued $(0,1)$-forms $A \in \Omega^{0,1}(X, \lie{g})$.
+The condition that $\d + A$ prescribes a holomorphic structure is again a Maurer--Cartan equation
+\beqn
+\dbar A + \frac12 [A,A] = 0 .
+\eeqn
+Like ordinary Chern--Simons theory, in order for this equation to arise from a principal of least action one needs to fix a non-degenerate, invariant, bilinear form $\kappa$ on $\lie{g}$.
+Additionally, one needs to fix a holomorphic volume form $\Omega$ on $X$; in other words, $X$ is a Calabi--Yau manifold.
+Then, the equations of motion is precisely the Euler--Lagrange equation for the action
+\beqn
+S_{hCS} (A) = \int_X \Omega \wedge CS(A) 
+\eeqn
+where $CS(A)$ is exactly as in \eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$ only the $\dbar$ operator contributes to the kinetic term and so the action can be written as $\int_X \Omega \wedge \left(\frac12 \kappa( A ,\dbar A ) + \frac16 \kappa(A , [A,A]) \right)$.}
+
 \subsection{Precise definitions}
-
-Let us begin with the example of holomorphic Chern--Simons theory, 
-which we have already said describes the moduli space of Maurer--Cartan elements describe deformations of the trivial holomorphic $G$-bundle. 
-When $X$ is a Calabi--Yau three-fold and $\fg$ is equipped with an invariant pairing $\<\cdot , \cdot \>$, 
-this formal moduli space has a very special property: 
-it arises from the variational problem of an action functional, namely
-\beqn
-S = \int_X \Omega \wedge {\rm CS}(A) 
-\eeqn
-where $\Omega$ is the holomorphic volume form and 
-\beqn
-{\rm CS}(A) = \frac12 \< A ,\d A \> + \frac16 \<A , [A,A]\>
-\eeqn
-is the Chern--Simons Lagrangian for the connection $(0,1)$-form $A$.
-Notice that due to the presence of the holomorphic volume form $\Omega$ on the $\dbar$ operator contributes to the kinetic term and so the action can be written as 
-\beqn
-S = \int_X \Omega \wedge \left(\frac12 \< A ,\dbar A \> + \frac16 \<A , [A,A]\>\right) .
-\eeqn
 
@@
 
-\subsubsection{Holomorphic scalar field theories}
-
-A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
-Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
-When $\Sigma$ is a surface this theory can be written in such a way that makes its complex structure apparent.
-First, we complexify the field $\phi$ which we can view as a pair of fields $\gamma, \Bar{\gamma}$.
-When we do this, we can split it up into its chiral and anti-chiral `sectors'.
-By chiral (anti-chiral) we mean part involving $\gamma$ ($\Bar{\gamma}$).
-The holomorphic part is described by the following action
-\beqn
-\int_\Sigma \beta \wedge \dbar \gamma
-\eeqn
-where $\beta$ is a $(1,0)$ form on $\Sigma$ and should be thought of as a Lagrange multiplier for the field $\del \Bar{\gamma}$ which we now think about as having its own degrees of freedom (this is called the first-order formalism).
-There is also a coupling between the chiral and anti-chiral sectors, 
-for more details we refer to \cite{Kapustin,GGW}. 
-This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta-\gamma$-\textit{system}.
-It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.
-
-There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta-\gamma$ system'.
-The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
-Above we took this bundle to be trivial.
-The fields of the theory consist of pairs 
+\subsubsection{Holomorphic gauge theories}
+
+We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
+There is a related holomorphic gauge theory which is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure.
+
+If $n$ is the complex dimension of $X$, the fields consist of pairs $(A,B)$ where $A$ is a $(0,1)$ connection on a principal $G$-bundle $P \to X$ and
+\beqn
+B \in \Omega^{n,n-2}(X, \fg_P^*) ,
+\eeqn
+where $\fg_P$ is the adjoint bundle of $P$. 
+The action functional is 
+\beqn
+S(A,B) = \int_X B \wedge F_A 
+\eeqn
+where $F_A$ is the curvature of the connection $A$.
+From this formula, it is clear that the model we are describing is a holomorphic analog of topological $BF$ theory. 
+Notice that by form types this action can be written as
+\beqn
+S(A,B) = \int_X B \wedge \left(\dbar A + \frac12 [A,A] \right) .
+\eeqn
+
+Holomorphic BF theory is easy to formulate classically, but it can admit peculiar properties at the quantum level.
+For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is almost topological.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory.}
+
+\subsubsection{Holomorphic $\sigma$-models}
+
+If $X,Y$ are any two complex manifolds there is a theory whose fields consist, in part, of the derived moduli space of smooth maps $\RR {\rm Map}(X,Y)$ and whose equations of motion dictate that such maps be holomorphic.
+
+This class of holomorphic field theories are simple higher-dimensional generalizations of the well-studied `$\beta-\gamma$ system' which appears in: superstring theory~\cite{Polchinski}, as the twist (see below)of the $\cN=(2,0)$ supersymmetric $\sigma$-model, and as the chiral part of the scalar field theory on a Riemann surface.
+
+Consider the case that $Y$ is simply $\C$ and suppose that $X$ is $n$-dimensional.
+The fields of the model are
 \begin{align*}
-\gamma & \in \Gamma(X,V)\\
-\beta & \in \Omega^{n,n-1}(X,V^*) .
+\gamma & \in \Gamma(X)\\
+\beta & \in \Omega^{n,n-1}(X) .
 \end{align*}
-The action functional is identical $\int_X \beta \wedge \dbar \gamma$.
-
-Notice that when $n = \dim_\C X > 1$ that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
+and the action is
+\beqn
+\int_\Sigma \beta \wedge \dbar \gamma .
+\eeqn
+There is a peculiarity of this theory when $n = \dim_\C X > 1$: in the case, there is a linear symmetry by shifting $\beta$ by a $\dbar$-exact form
 \beqn
@@
 This is one of the key differences between the ordinary $\beta-\gamma$ system and its higher dimensional version.
-Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.
-
-\subsubsection{Holomorphic gauge theories}
-
-We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
-There is a related holomorphic gauge theory which is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure.
-
-If $n$ is the complex dimension of $X$, the fields consist of pairs $(A,B)$ where $A$ is a $(0,1)$ connection on a principal $G$-bundle $P \to X$ and
-\beqn
-B \in \Omega^{n,n-2}(X, \fg_P^*) ,
-\eeqn
-where $\fg_P$ is the adjoint bundle of $P$. 
-The action functional is 
-\beqn
-S(A,B) = \int_X B \wedge F_A 
-\eeqn
-where $F_A$ is the curvature of the connection $A$.
-From this formula, it is clear that the model we are describing is a holomorphic analog of topological $BF$ theory. 
-Notice that by form types this action can be written as
-\beqn
-S(A,B) = \int_X B \wedge \left(\dbar A + \frac12 [A,A] \right) .
-\eeqn
-
-\subsubsection{Holomorphic $\sigma$-models}
-
-If $X,Y$ are any two complex manifolds there is a theory whose fields consist, in part, of the derived moduli space of smooth maps $\RR {\rm Map}(X,Y)$ and whose equations of motion dictate that such maps be holomorphic.
-This is a nonlinear generalization of the $\beta\gamma$ system we just introduced.
-
-The precise space of fields, in cohomological degree zero, consist of pairs $(\gamma, \beta)$ where $\gamma \colon X \to Y$ is a smooth map and 
+Nevertheless, many techniques we have for understanding free field theories can still be applied to this model.
+
+There is the following nonlinear generalization of the $\beta\gamma$ system when $Y$ is an arbitrary complex manifold.
+The space of fields consist of pairs $(\gamma, \beta)$ where $\gamma \colon X \to Y$ is a smooth map and 
 \[
@@
 Solutions to the equations of motion describe, in part, holomorphic maps $X \to Y$, but there is also derived information contained in this model.
+A detailed formulation of this theory has been developed in \cite{BWthesis}.
 
@@
 The action functional is very similar to the Chern--Simons action
-\beqn
+\beqn\label{eqn:KS1}
 S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
@@
 The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
+
+\subsubsection{Holomorphic scalar field theories / $\sigma$-models}
+
+A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
+Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
+We saved this example for last since its holomorphic analog is a bit more elusive than the previous examples.
+
+We start with complex dimension $1$.
+The usual scalar field theory can be written as $\int_{\Sigma} \phi \del \dbar \phi$, where $\Sigma$ is a Riemann surface.
+This theory is not holomorphic, but we can force it to be by demanding the constraint $\dbar \phi = 0$.
+Importantly, this constraint is \textit{not} imposed by an equation of motion.
+When we do this, we can express the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
+\beqn\label{eqn:scalar1}
+\int \alpha \dbar \del^{-1} \alpha .
+\eeqn
+This is formally similar to the kinetic term in the action functional of Kodaira--Spencer theory \eqref{eqn:KS1}.
+
+There is a higher-dimensional analog of the chiral sector of the scalar field.
+Suppose that $X$ is a complex manifold of \textit{odd} dimension $2n+1$.
+The fields are certain $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ which satisfy the constraint
+\beqn
+\del \alpha = 0.
+\eeqn
+Note that when $n=0$, so $X = \Sigma$ is simply a Riemann surface, this constraint is automatic.
+The action functional is the same \eqref{eqn:scalar1}.
+When $n=1$ this is identical to the kinetic part of the Kodaira--Spencer action.\footnote{Indeed, when $X$ is a Calabi--Yau three-fold there is an isomorphism $\Omega^{2,1}(X) \simeq \Omega^{0,1}(X, \T_X)$.}
+Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
+\beqn
+\int_X \|C\|^2 \op{dvol} = \int_X C \d \star \d C , \quad C \in \Omega^{2n+1}(X) .
+\eeqn
+For more details we refer to \cite{GRWwzw}.
+
 \subsection{Local version and examples from supersymmetric field theories}

### 2024-09-10 draft.tex
added reminders on what to include in completing the paper

--- 2024-08-19 draft.tex
@@
 
-\subsubsection{Holomorphic $\sigma$-models}
-
-If $X,Y$ are any two complex manifolds there is a theory whose fields consist, in part, of the derived moduli space of smooth maps $\RR {\rm Map}(X,Y)$ and whose equations of motion dictate that such maps be holomorphic.
-This is a nonlinear generalization of the $\beta\gamma$ system we just introduced.
-
-The precise space of fields, in cohomological degree zero, consist of pairs $(\gamma, \beta)$ where $\gamma \colon X \to Y$ is a smooth map and 
-\[
-\beta \in \Omega^{n,n-1}(X, f^* \T^*_Y) 
-\]
-where $\T^*_Y$ is the holomorphic cotangent bundle of $Y$. 
-The action functional is the familiar one
-\beqn
-\int_X \beta \dbar \gamma .
-\eeqn 
-Solutions to the equations of motion describe, in part, holomorphic maps $X \to Y$, but there is also derived information contained in this model.
+Holomorphic BF theory is easy to formulate classically, but it can admit peculiar properties at the quantum level.
+For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is almost topological.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory.}
 
@@
 The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
+
+\subsubsection{Holomorphic scalar field theories}
+
+A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
+Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
+We saved this example for last since its holomorphic analog is a bit more elusive than the previous examples.
+
+We start with complex dimension $1$.
+The usual scalar field theory can be written as $\int_{\Sigma} \phi \del \dbar \phi$, where $\Sigma$ is a Riemann surface.
+This theory is not holomorphic, but we can force it to be by demanding the constraint $\dbar \phi = 0$.
+Importantly, this constraint is \textit{not} imposed by an equation of motion.
+When we do this, we can express the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
+\beqn\label{eqn:scalar1}
+\int \alpha \dbar \del^{-1} \alpha .
+\eeqn
+This is formally similar to the kinetic term in the action functional of Kodaira--Spencer theory \eqref{eqn:KS1}.
+
+There is a higher-dimensional analog of the chiral sector of the scalar field.
+Suppose that $X$ is a complex manifold of \textit{odd} dimension $2n+1$.
+The fields are certain $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ which satisfy the constraint
+\beqn
+\del \alpha = 0.
+\eeqn
+Note that when $n=0$, so $X = \Sigma$ is simply a Riemann surface, this constraint is automatic.
+The action functional is the same \eqref{eqn:scalar1}.
+When $n=1$ this is identical to the kinetic part of the Kodaira--Spencer action.\footnote{Indeed, when $X$ is a Calabi--Yau three-fold there is an isomorphism $\Omega^{2,1}(X) \simeq \Omega^{0,1}(X, \T_X)$.}
+Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
+\beqn
+\int_X \|C\|^2 \op{dvol} = \int_X C \d \star \d C , \quad C \in \Omega^{2n+1}(X) .
+\eeqn
+For more details we refer to \cite{GRWwzw}.
 
@@
 
-\owen{discuss OPE and explain the shifted Poisson structure}
+\owen{discuss OPE, explain the shifted Poisson structure, and mention $\lambda$-brackets}
 
@@
 
-\owen{We should review BW results and subsequent improvements by Gaiotto et al and Wang}
+\owen{We discussed having the following:
+\begin{itemize}
+\item Quick overview for topological field theories (=analytic content is de Rham complex): 
+\begin{itemize}
+\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
+\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
+\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
+\end{itemize} 
+\item Overview the history of the holomorphic case, with citations
+\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
+\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
+\end{itemize}}
 

### 2024-09-11 draft.tex
implementing old remarks to myself (Owen) from a printed dfaft

@@
 A well-known example is holomorphic Chern-Simons theory,
-which lives on a Calabi-Yau 3-fold~$X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on~$X$.
-As a somewhat mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
+which lives on a Calabi-Yau 3-fold~$X$ and involves the moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on~$X$.
+(We add the prefix $\RR$ because it is best to use the {\em derived} moduli space.
+We do not assume the reader is versed in derived geometry and will offer motivations, glosses, and references throughout the survey.)
+As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
 (For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
-One can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
+In derived geoemtry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
 and this derived moduli space encodes solutions to
@@
 Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
-Other classes of examples are afforded by holomorphic variants of familiar AKSZ $\sigma$-models; the relevant moduli space being the derived mapping space between complex manifolds.
+Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformatino quantization); 
+the relevant moduli space being the derived mapping space between complex manifolds.
 
 A physical motivation comes from supersymmetric field theories, 
-which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a Lie supergroup known as a super Poincar\'e group.
+which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a super Lie group known as a super Poincar\'e group.
 %The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
@@
 The relevance to the models we study is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
-even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
+even when they do not admit twists to TFTs \cite{CosHol}. 
+(The famed A- and B-models of mirror symmetry are TFTs produced by twisting supersymmetric thories.)
 As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.
@@
 In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''
+It may be helpful to know that the role of derived geometry on the mathematical side is mirrored by the use of the BRST/BV formalism on the physics side;
+they are closely related and serve similar purposes.
 
@@
 It is natural to explore higher-dimensional analogs.
-
-The overarching goal of this paper is \owen{continue}
-a cluster of projects is to bring into sharp mathematical form some of the deep insights into gauge theory offered by physics.
-So far, most mathematical effort has focused on classical gauge theory,
+So far, most mathematical effort in this direction has focused on classical aspects of gauge theory,
 but the quantum aspects are profoundly interesting.
@@
 
+The overarching goal of this paper is to introduce the reader to this emerging domain where physics and mathematics meet,
+with an emphasis upon how key objects from physics, notably supersymmetric theories and conformal field theories, 
+interface with complex geometry in general and with mathematical methods of rather recent vintage,
+notably derived geometry and higher algebras.
+A community is forming, involving both mathematicians and physicists,
+to bring into sharp mathematical form some of the deep insights into gauge theory offered by physics.
+There is a lot to explore here.
+
 \subsection{Preliminary notions}
@@
 
-A theory is usually described, in part, in terms of a space of fields which comprise some possibly nonlinear space like a mapping space or the space of connections. 
-In perturbative field theory, which describes the formal neighborhood of the theory at points in such spaces, the fields $\Phi$ are typically described by the smooth sections of a vector bundle on spacetime.
-The equations of motion which dictate the dynamics of the particular model are encoded by a series of partial differential equations of the form 
+A physical field theory is usually described in terms of a space of fields that forms some possibly nonlinear space, like a mapping space $\Map(M,X)$ or the space of connections ${\rm Conn}_G(M)$ on a manifold.
+There is a manifold, called spacetime in physics, where the fields are some kind of functions out of it;
+in the examples just mentioned, it is denoted $M$.
+In perturbative field theory, which describes the formal neighborhood of the theory at a point in such spaces, 
+a field $\Phi$ is typically described by a smooth section of a vector bundle on spacetime.
+The equations of motion that dictate the dynamics of the particular model are encoded by a series of partial differential equations of the form 
 \[
@@
 where $\Phi = \phi$ is simply a smooth function on $M$.
-These equations of motion are natural to the Riemannian geometry of the manifold $M$, and can be derived from the Euler--Lagrange equations of the simple action functional $\int_M \phi \Delta \phi \, \op{dvol}$.
+These equations of motion are natural to the Riemannian geometry of the manifold $M$, 
+and they can be derived from the Euler--Lagrange equations of the  action functional $\int_M \phi \Delta \phi \, \op{dvol}$.
 
@@
 In traditional physics there are a few basic types of field theories, 
-and they can be assembled into combinations in natural ways,
+and they can be assembled into combinations,
 of which the Standard Model offers a nice example.
@@
 The Higgs boson appears as part of a scalar field theory.
-\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space or, typically, a section of a spinor bundle.
+\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space (in the sense of supermathematics), typically a section of a spinor bundle.
 Such theories are often used to describe matter, such as electron fields.
@@
 The Standard Model involves the first three types,
-and the different fields interact in intricate ways.
+and the different fields interact in intricate ways.\footnote{For instance, the scalar and fermionic fields are sections for associated bundles of the principal bundle appearing in the gauge theory.}
 
@@
 We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
-There is a related holomorphic gauge theory which is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure.
-
-If $n$ is the complex dimension of $X$, the fields consist of pairs $(A,B)$ where $A$ is a $(0,1)$ connection on a principal $G$-bundle $P \to X$ and
+There is a related holomorphic gauge theory that is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure. 
+Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra.
+
+If $n$ is the complex dimension of $X$, 
+the fields consist of pairs $(A,B)$ where $A$ denotes a $\dbar$-connection on a holomorphic principal $G$-bundle $P \to X$ and
 \beqn
@@
 \beqn
-S(A,B) = \int_X B \wedge F_A 
+S(A,B) = \int_X \langle B \wedge F_A \rangle
 \eeqn
 where $F_A$ is the curvature of the connection $A$.
-From this formula, it is clear that the model we are describing is a holomorphic analog of topological $BF$ theory. 
-Notice that by form types this action can be written as
-\beqn
-S(A,B) = \int_X B \wedge \left(\dbar A + \frac12 [A,A] \right) .
-\eeqn
+From this formula, one might see that the model is a holomorphic analog of topological $BF$ theory. 
+Notice that locally on $X$ and
+writing the connection at $\dbar + [A,-]$, this action can be written as
+\beqn
+S(A,B) = \int_X \langle B \wedge \left(\dbar A + \frac12 [A,A]  \right) \rangle.
+\eeqn
+The equations of motion are
+\[
+F_A^{0,2} = \dbar A + \frac12 [A,A] = 0 \text{ and } \dbar B + [A,B] = 0.
+\]
+In other words, a solution is a $\dbar$-connection on $P\to X$ and a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle.
 
 Holomorphic BF theory is easy to formulate classically, but it can admit peculiar properties at the quantum level.
-For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is almost topological.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory.}
+For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is a almost topological field theory.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory.
+\owen{Add specific location in text.}}
 
@@
 
-Perturbatively, any model of gravity describes, in part, deformations of the moduli space of metric structures on a given manifold. 
-There is a holomorphic avatar of this which describes deformations of complex structure which has first appeared in the literature in work related to topological string theory on Calabi--Yau threefolds~\cite{BCOV}.
+Any theory of gravity involves, in part, metric structure on a given manifold,
+so that solutions to the equations of motion produce metrics satisfying a PDE. 
+For a perturbative gravity theory,
+one studies deformations of some metric structure on a manifold.
+There is a holomorphic avatar of this situation: deformations of complex structure. 
+The first appearance of such a theory was motivated by topological string theory and involves complex structures on Calabi--Yau threefolds~\cite{BCOV}.
 Because of its relationship to complex structures, the theory is referred to as \textit{Kodaira--Spencer theory}.
-It has been mathematically championed in the works of Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
-In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; here we focus just on the more familiar three-dimensional version.
+It has been pursued mathematically by Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
+In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; here we focus just on the most familiar three-dimensional version.
 %The fields consist of pairs $(\mu, \eta)$ where
@@
 \beqn\label{eqn:KS1}
-S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
+S(\mu) = \int_X \left(\frac12 \mu\, \dbar \del^{-1} \mu + \frac13 \mu \wedge \mu \wedge \mu \right) .
 \eeqn
@@
 Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
-Forgoing the apparent global issues, we can still apply formal variational calculus to the action to obtain the equation of motion
+Setting aside the apparent global issues, 
+we apply formal variational calculus to this action to obtain the equation of motion
 \beqn
@@
 \eeqn
-where $[-,-]$ is the Schouten--Nijenhuis bracket (which reduces to just the natural bracket when restricted to vector fields).
-The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
+where $[-,-]$ is the Schouten--Nijenhuis bracket 
+(which reduces to just the Lie bracket when restricted to vector fields).
+The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
 
@@
 
-We start with complex dimension $1$.
-The usual scalar field theory can be written as $\int_{\Sigma} \phi \del \dbar \phi$, where $\Sigma$ is a Riemann surface.
+We start with complex dimension~$1$.
+The usual scalar field theory can be written as 
+\[
+\int_{\Sigma} \phi \wedge \del \dbar \phi, 
+\]
+where $\Sigma$ is a Riemann surface.
 This theory is not holomorphic, but we can force it to be by demanding the constraint $\dbar \phi = 0$.
 Importantly, this constraint is \textit{not} imposed by an equation of motion.
-When we do this, we can express the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
+When we impose this constract, we can rewrite the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
 \beqn\label{eqn:scalar1}
-\int \alpha \dbar \del^{-1} \alpha .
-\eeqn
+\int_\Sigma \alpha \wedge \dbar \del^{-1} \alpha ,
+\eeqn
+where $\alpha$ plays the role of $\partial \phi$.
+\owen{Am I interpreting that correctly?} 
 This is formally similar to the kinetic term in the action functional of Kodaira--Spencer theory \eqref{eqn:KS1}.
@@
 Suppose that $X$ is a complex manifold of \textit{odd} dimension $2n+1$.
-The fields are certain $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ which satisfy the constraint
+The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
 \beqn
@@
 \eeqn
-Note that when $n=0$, so $X = \Sigma$ is simply a Riemann surface, this constraint is automatic.
-The action functional is the same \eqref{eqn:scalar1}.
-When $n=1$ this is identical to the kinetic part of the Kodaira--Spencer action.\footnote{Indeed, when $X$ is a Calabi--Yau three-fold there is an isomorphism $\Omega^{2,1}(X) \simeq \Omega^{0,1}(X, \T_X)$.}
+Note that when $n=0$, so $X$ is simply a Riemann surface~$\Sigma$, this constraint is automatic.
+The action functional is the same as~\eqref{eqn:scalar1}.
+When $n=1$ this functional is identical to the kinetic part of the Kodaira--Spencer action.\footnote{Indeed, when $X$ is a Calabi--Yau three-fold there is an isomorphism $\Omega^{2,1}(X) \cong \Omega^{0,1}(X, \T_X)$.}
 Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
 \beqn
-\int_X \|C\|^2 \op{dvol} = \int_X C \d \star \d C , \quad C \in \Omega^{2n+1}(X) .
-\eeqn
-For more details we refer to \cite{GRWwzw}.
+\int_X \|C\|^2 \op{dvol} = \int_X C \wedge \d \star \d C , 
+\eeqn
+where $C \in \Omega^{2n+1}(X)$.
+For more details we refer to~\cite{GRWwzw}.
 
@@
 which allows us to connect directly to supersymmetric field theories. 
-Suppose that our spacetime is $\CC^n = \RR^{2n}$ and assume that the theory we are considering is translation invariant, meaning that there is an action buy the $2n$-dimensional Lie algebra spanned by the vector fields $\del / \del {z_i}, \del / \del {\zbar_i}$ for $i=1,\ldots,n$.
-In a holomorphic theory we require that the anti-holomorphic vector fields $\del / \del {\zbar_i}$ act homotopically trivial. 
-In the derived world this is prescribed by the data of homotopy trivializations for such vector fields.
-
-Any even dimensional supersymmetric field theory produces a holomorphic field theory through a process called twisting,
-so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.\footnote{Strictly speaking, this requires the existence of of more than two chiral supercharges.
-So, theories with 2d $\cN = (n,m)$ supersymmetry, $n,m \leq 1$, do not admit holomorphic twists.}
+Suppose that our spacetime is $\CC^n = \RR^{2n}$ and assume that the theory we are considering is translation invariant, 
+meaning that there is an action by the $2n$-dimensional Lie algebra spanned by the vector fields $\{\del / \del {z_i}, \del / \del {\zbar_i}\}$ for $i=1,\ldots,n$. 
+Such a theory is {\em holomorphic} if the anti-holomorphic vector fields $\del / \del {\zbar_i}$ act trivially. 
+In the derived world this condition is encoded by the data of chain homotopy trivializations for such vector fields.
+
+Any even dimensional supersymmetric field theory produces a holomorphic field theory through a process called {\em twisting},
+so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.\footnote{Strictly speaking, twisting requires the existence of of more than two chiral supercharges.Thus, two-dimensional theories with $\cN = (n,m)$ supersymmetry, and $n,m \leq 1$, do not admit holomorphic twists.}
 As we will explain later, many interesting phenomena for supersymmetric theories have analogs in holomorphic field theory.
@@
 Indeed, so long as a twisted supercharge is nonzero $\cQ \ne 0$ one see that the image of the map $[\cQ,-] = \Gamma(\cQ,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
-A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly $n$ and we declare the the image of $\cQ$ is spanned by the anti-holomorphic vector fields $\{\del / \del \zbar_i\}$.
-This fits with the local characterization mentioned at the beginning of the subsection since in this case there exists homotopies $\{\eta_i\}$ with the property that 
-\beqn
-[\cQ,\eta_i] = \frac{\del}{\del \zbar_i} .
-\eeqn
+A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly $n$, 
+and we declare the the image of $\cQ$ is spanned by the anti-holomorphic vector fields $\{\del / \del \zbar_i\}$.
+Thus there exist homotopies $\{\eta_i\}$ such that 
+\beqn
+[\cQ,\eta_i] = \frac{\del}{\del \zbar_i} ,
+\eeqn 
+recovering the characterization of holomorphic field theories mentioned at the beginning of the subsection.
 
@@
 The ordinary Weyl algebra on a symplectic vector space $V$ arises from the quantization of ordinary mechanics on the symplectic vector space $V$.
-We can also include a Hamiltonian $H \in \cO(V)$ which acts on the Weyl algebra by the commutator $[H,-]$.
+We can also include a Hamiltonian $H \in \cO(V)$ that acts on the Weyl algebra by the commutator $[H,-]$.
 If we understand the fields of this system as smooth maps $\phi = \phi(t)$ valued in $V$, then the Lagrangian description of this system is 
@@
 Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
-In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian which encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.
+In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian that encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.
 
@@
 Checking this computation is a straightforward exercise in algebraic geometry;
-for instance, use the cover by the affine opens which are the complements of the coordinate hyperplanes $\{z_i =0\}$.
+for instance, use the cover by the affine opens that are the complements of the coordinate hyperplanes $\{z_i =0\}$.
 The full cohomology has the structure of a commutative algebra. 
@@
 The right embedding replaces the inclusion of Laurent polynomials into the Dolbeault complex on $\CC^\times$.
-\item There is a higher residue map $\text{Res} \colon \sfA_d^{\bu} \to \CC[-d+1]$ which is compatible with integration over the $2d-1$ sphere
+\item There is a higher residue map $\text{Res} \colon \sfA_d^{\bu} \to \CC[-d+1]$ that is compatible with integration over the $2d-1$ sphere
 \beqn
@@
 They are given by the data of a $\fg$-invariant degree $d+1$ polynomial $\theta \in \Sym^{d+1}(\fg^*)^G$.
-The cocycle which defines the $L_\infty$ central extension is
+The cocycle that defines the $L_\infty$ central extension is
 \[
@@
 \]
-That is, the invariant degree $(d+1)$ polynomial on $\fg$ which determines the $L_\infty$ extension of the sphere algebra $\fg_d^\bu$ is given by ${\rm Tr}_V (x_0 \cdots x_{d})$.
+That is, the invariant degree $(d+1)$ polynomial on $\fg$ that determines the $L_\infty$ extension of the sphere algebra $\fg_d^\bu$ is given by ${\rm Tr}_V (x_0 \cdots x_{d})$.
 In this sense, the higher Kac-Moody algebras admit a higher free field realization,
@@
 Because the space of $(0,\bu)$ forms define a commutative dg algebra, 
-the complex $\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z))$ has the natural structure of a dg Lie algebra---the complex on the right hand side is the Chevalley--Eilenberg complex which computes the Lie algebra homology of this dg Lie algebra.
+the complex $\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z))$ has the natural structure of a dg Lie algebra---the complex on the right hand side is the Chevalley--Eilenberg complex that computes the Lie algebra homology of this dg Lie algebra.
 Using the formalism of factorization algebras (which we recall in the next section) it is shown in \cite{CG2} how to equip $A_{\lie{g}}$ with the structure of a holomorphic disc algebra.
@@
 Let $V$ be a vector space.
-Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
+Then, we can define a holomorphic disc algebra $A_V$ that corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
 To a disc $D = D_r(z)$ this assigns the following cochain complex
@@
 \eeqn
-where the differential is $\dbar + \triangle$ which we will explain momentarily. 
+where the differential is $\dbar + \triangle$ that we will explain momentarily. 
 We denote the linear generators of this symmetric algebra by $\gamma \in \Omega^{1,\bu}_c(D) \otimes V^* [1]$ and $\beta \in \Omega^{0,\bu}_c(D) \otimes V^* [1]$.
@@
 In this section we have mostly focused on disks.
-If we evaluate $A^{\lie{g}}_{d}$ on a punctured disk rather than a disk then we obtain a complex which receives a dense embedding from the complex
+If we evaluate $A^{\lie{g}}_{d}$ on a punctured disk rather than a disk then we obtain a complex that receives a dense embedding from the complex
 \beqn
@@
 Given an invariant polynomial $\theta \in \Sym^{d+1}(\lie{g}^*)^G$ as in \S \ref{s:alghigh} we can obtain a twisted version of this $d$-polydisks algebra $A^{\lie{g}}_{d,\theta}$.
-At the level of the punctured disk this corresponds to the higher Kac--Moody algebra which is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
+At the level of the punctured disk this corresponds to the higher Kac--Moody algebra that is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
 This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra \cite{GWkm}.
@@
 initially conjectured by Richard Eager.
-We will point out an enrichment of this conjecture which accounts for a large symmetry enhancement that both sides of the theory enjoy after performing the holomorphic twist.
+We will point out an enrichment of this conjecture that accounts for a large symmetry enhancement that both sides of the theory enjoy after performing the holomorphic twist.
 We explain our first efforts in this direction and how it offers evidence for the conjecture;
@@
 \item
-The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ which take values in $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
+The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ that take values in $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
 (and $\check{\nu}$ for the partner field to $\check{\mu}$).
@@
 Our discussion here is ahistorical.
-Witten initiated this vein of research for twists which are topological \cite{WittenTwist},
+Witten initiated this vein of research for twists that are topological \cite{WittenTwist},
 and Costello advocated holomorphic twists \cite{CostelloHol}.  
@@
 The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
-where $z,w$ are formal loop parameters which we imagine as describing the winding of the two circles we have compactified. 
+where $z,w$ are formal loop parameters that we imagine as describing the winding of the two circles we have compactified. 
 The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.

### 2024-09-12 draft.tex
renorm

@@
 
+The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.
+One can apply the same sort of techniques to produce holomorphic quantum field theories, and the higher algebraic structures associated to them.
+A key feature of holomorphic theories is the absence of (possibly scheme-dependent) counterterms which can make typical quantum field theories difficult to access.
+
+Counterterms are perturbative quantum effects that typically must be introduced to the action functional in order to circumvent ultra-violet (UV, high energy) divergences which arise when studying the path integral.
+From Feynman, we know that the path integral can be formally expressed in terms of graphs. 
+More precisely, given a graph $\Gamma$ (whose exact shape depends on the theory), there is a prescription for assigning to it a functional $W_\Gamma$ on the fields (a distribution) which we can understand as term in the quantum action; typically in the form of an integral over $|V(\Gamma)|$ copies of spacetime where $V(\Gamma)$ is the vertex set of the graph.
+Unfortunately, this prescription is not always well-posed, as there are infinities which can arise due to presence of overlapping supports of certain distributions.
+Counterterms can be constructed by carefully understanding the nature of these divergences through some regularization scheme.
+
+For topological quantum field theories, it is known from the work of Axelrod, Singer, Kontsevich, Cattaneo, and others \cite{???} that such Feynman graphs return finite answers and hence there is no need to introduce such complications.
+The method used to prove this interprets such Feynman graph integrals as integrals over configuration space and then showing that the weights $W_\Gamma$ can be extended to some compactification.
+A different regularization scheme based on the heat equation was used by Costello \cite{CosRenormPaper} to arrive at the same result for topological quantum field theories.
+
+The configuration space method traditionally used to study topological theories does not admit an immediate generalization to holomorphic theories.
+Nevertheless, it is known that the renormalization for holomorphic field theories is equally well-behaved.
+
+The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
+Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
+In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
+There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
+In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
+The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
+Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
+In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
+
+The discussion so far in this section was about the analytic issues which are present when trying to make the path integral precise.
+For interesting quantum field theories, like gauge theories, there is another issue which could prevent the theory from being well-posed; these are called anomalies.
+An anomaly is the measure of the failure of the quantum path integral to enjoy the same symmetries as the underlying classical field theory.
+In gauge theory, for instance, there could be an obstruction for the perturbative renormalization to be gauge invariant.
+In topological theories, it is known that these sort of anomalies are absent.
+For holomorphic theories, however, anomalies are present.\footnote{Anomalies in holomorphic field theory are related to, but distinct from, familiar anomalies such as `chiral anomalies' in theories of Weyl fermions.}
+Since renormalization is so well-behaved, however, such anomalies are amenable to explicit characterization.
+For example, at one-loop in perturbation theory, an explicit formula for such anomalies for holomorphic theories on $\C^d$ is given in \cite{Whol}.
+It involves a sum over Feynman weights $W_\Gamma$ where $\Gamma$ is a polygon with $(d+1)$-vertices.
+
 \section{Vista: Seiberg duality and its consequences}

### 2024-09-13 draft.tex
i thought i had committed but i guess i needed to
mostly relabeling sections

@@
 
-\subsection{Preliminary notions}
+\subsection{How to read this paper}
+
+\subsection{Acknowledgements}
+
+\section{Holomorphic field theories}
 
@@
 
-\subsection{The local definition, and examples from supersymmetric field theories}
+\subsection{From supersymmetric field theories to holomorphic field theories}
 
@@
 
-\owen{give a nice version of their statement, with this as a first attempt}
-
-\begin{thm}[\cite{EllSaf},\owen{precise location}]
+\owen{Rewrite this first attempt to be more accurate.}
+
+\begin{thm}[\cite{EllSaf}]
+\label{thm: EllSaf}
 Let $\cT$ be a classical field theory on $\RR^d$ in the sense of~\cite{CosBook},
-and let its observables be constructed following~\cite{CG2}.
-If the theory satisfies 
+and let its observables $\Obs_\cT$ be constructed following~\cite{CG2}.
+
+If the theory $\cT$ satisfies 
 \begin{enumerate}
-\item[(i)] $\cT$ is equivariant under the action of the translation group,
-\item[(ii)] the action of the translation Lie algebra is homotopically trivialized, and
+\item[(i)] it is equivariant under the action of the translation group,
+\item[(ii)] the action of the translation Lie algebra is homotopically trivialized,\footnote{View the translation algebra $\RR^d$ as spanned by the basis $\{\partial_j\}$ of constant vector fields, and let $\rho: \RR^d \to \Der(\Obs_\cT)$ denote the translation action on observables.
+By a homotopical trivialization, we mean here that there is a linear map $\eta: \RR^d \to \Der(\Obs_\cT)$ of degree $-1$ such that $[\d_{\cT}, \eta(\partial_j)] = \rho(\partial_j)$.
+In other words, $\eta$ provides a chain homotopy trivialization of the action~$\rho$.} 
+and
 \item[(iii)] the extension of observables along an inclusion of discs is a quasi-isomorphism,
@@
 
+This theorem applies to many well-known examples from physics:
+\begin{itemize}
+\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra.
+It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
+\item The Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
+\item The Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
+\item The Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$.
+\end{itemize}
+It applies to other examples of topological AKSZ theories, such as BF theories and the Poisson $\sigma$-model.
+In all these examples, the underlying elliptic complex appearing in the field theory is a version of the de Rham complex,
+so that the chain homotopy $\eta$ is easily constructed by contracting a vector field with differential forms.
+
+This theorem builds an explicit bridge between topology and physics. 
+Thanks to the theorem of Elliott and Safronov, we know that most topological field theories in the physicist's sense provide $E_n$ algebras (with the examples above as evidence),
+but they can thus be analyzed using the powerful machinery of modern homotopy theory. 
+Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. 
+Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.
+(See Section~\ref{sec: reln to functorial TFT} for the relation with the Atiyah-Segal approach to TFT.)
+
+Let us comment on some aspects of the theorem and its proof.
 The notion from \cite{CosBook} articulates Lagrangian field theories whose linearized equations of motion are elliptic in nature;
@@
 and the observables are a dg commutative algebra given a symmetric algebra on the linear dual to the fields and equipped with a differential $d_\cT$ that is determined by the Lagrangian density of the theory.
-Item (ii) above then means that each vector field $\partial_i$ acts by a degree 0 cochain map $D_i$ on the observables and there is a degree one cochain homotopy $\eta_i$ on the observables such that $[d_\cT, \eta_i]~=~D_i$.
-
-\owen{Actually say what kind of $d$-discs algebras one gets.}
-This theorem applies to many well-known examples from physics:
-\begin{itemize}
-\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra.
-It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
-\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
-\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
-\item Each Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming the coadjoint quotient stack~$\fg^*/G$.
-\end{itemize}
-It applies to other examples of topological AKSZ theories, such as BF theories.
-In all these examples, the underlying elliptic complex is a version of the de Rham complex.
+Item (ii) above then means that each vector field $\partial_j$ acts by a degree 0 cochain map $D_j$ on the observables and there is a degree one cochain homotopy $\eta$ on the observables such that $[d_\cT, \eta(\partial_j)]~=~D_j$.
 
@@
 so that many familiar constructions from the physical approach to TFTs fit cleanly and easily into this framework.
-
-\owen{Stuff about formality? functorial field theories?}
-
-This theorem builds an explicit bridge between topology and physics. 
-Thanks to the theorem of Elliott and Safronov, we know that most topological field theories in the physicist's sense provide $E_n$ algebras,
-but they can thus be analyzed using the powerful machinery of modern homotopy theory. 
-Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. 
-Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.
 
@@
 \[
-\Omega^{0,\bu}(X) \widehat{\otimes}_\pi \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
+\Omega^{0,\bu}(X) \,\widehat{\otimes}_\pi\, \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
 \]
@@
 For an extensive discussion of these issues, see the appendices of~\cite{CG1}.
-From hereon we will ignore function-analytic aspects and write $\otimes$,
-with an appropriate symmetric monoidal category left implicit.
+From hereon we will ignore function-analytic aspects and write~$\otimes$,
+with an appropriate choice of symmetric monoidal category left implicit.
 
@@
 \subsubsection{Relating to the Atiyah-Segal approach to TFTs}
+\label{sec: reln to functorial TFT}
 
@@
 \begin{cor}
-For any Lagrangian field theory satisfying the hypotheses of Theorem~\ref{}, 
+For any Lagrangian field theory satisfying the hypotheses of Theorem~\ref{thm: EllSaf}, 
 there is a fully extended framed $d$-dimensional field theory 
@@
 
-\section{Constructing examples \& renormalization}
+\section{Renormalization \& anomalies: constructing examples}
 

### 2024-09-14 draft.tex
testing at MPIM
revised intro

@@
 just as complex variables is a particularly beautiful wing of analysis.
-In essence, such {\em holomorphic} field theories have variational partial differential equations (i.e., ``equations of motion'') that are holomorphic:
-the PDE only involves derivatives in the holomorphic coordinates (i.e., the $\partial/\partial z_j$) and has holomorphic coefficients.
+In essence, such {\em holomorphic} field theories have variational partial differential equations (i.e., ``equations of motion'') that are holomorphic.
 These theories admit independent motivations from mathematics and physics,
@@
 for most classical holomorphic field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
-and it is natural to hope that its quantization is equally interesting.
+and one might hope that the quantization of this moduli space is equally interesting.
 A well-known example is holomorphic Chern-Simons theory,
@@
 We do not assume the reader is versed in derived geometry and will offer motivations, glosses, and references throughout the survey.)
+
 As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
 (For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
-In derived geoemtry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
+In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
 and this derived moduli space encodes solutions to
-a theory known as the $\beta\gamma$ system with target $V$.
-(The name is silly: it's due to the original notation people used.)
+a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it's due to the original notation people used.}
 Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
@@
 Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.
-The relevance to the models we study is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
+The relevance to this survey is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
 even when they do not admit twists to TFTs \cite{CosHol}. 
 (The famed A- and B-models of mirror symmetry are TFTs produced by twisting supersymmetric thories.)
-As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.
-It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one,
+As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, 
+but it does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.
+
+It is natural to wonder how the myriad tools and computations deployed on a supersymmetric theory carry over to this twist 
+and, conversely, whether information can flow back from a holomorphically twisted theory to the original supersymmetric theory, 
 much as TFTs have enriched the understanding of supersymmetric theories.
 In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''
-It may be helpful to know that the role of derived geometry on the mathematical side is mirrored by the use of the BRST/BV formalism on the physics side;
+To aid translation between mathematics and physics, 
+it may be helpful to know that the role of derived geometry on the mathematical side is mirrored by the use of the BRST/BV formalism on the physics side;
 they are closely related and serve similar purposes.
 
-As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), holomorphic field theories appear as chiral conformal field theories (CFTs) on two-dimensional manifolds --- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- and have had a strong impact in mathematics.
-It is natural to explore higher-dimensional analogs.
-So far, most mathematical effort in this direction has focused on classical aspects of gauge theory,
+As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), 
+holomorphic field theories appear as chiral conformal field theories (CFTs) on Riemann surfaces. 
+The study of CFTs--- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- have had a strong impact in mathematics,
+so it is natural to explore higher-dimensional analogs.
+So far, most mathematical effort in this direction has focused on (essentially) classical aspects of gauge theory,
 but the quantum aspects are profoundly interesting.
@@
 with an emphasis upon how key objects from physics, notably supersymmetric theories and conformal field theories, 
-interface with complex geometry in general and with mathematical methods of rather recent vintage,
+interface with complex geometry and especially with mathematical methods of rather recent vintage,
 notably derived geometry and higher algebras.
@@
 
+Section~\ref{sec: HFT} is devoted to describing holomorphic field theories, primarily by offering a bounty of examples, including holomorphic analogs of gauge and gravity theories.
+We outline as well how to obtain holomorphic field theories from supersymmetric field theories,
+a rich source of examples to explore.
+
+The next three sections are, in a sense, the core of the survey,
+as they describe increasingly general types of higher algebras and how these capture the observables of holomorphic field theories.
+Section~\ref{sec: algebra} revisits the relationship between quantum mechanics and associative algebras,
+chiral conformal field theory and vertex algebras,
+and holomorphic field theories and higher-dimensional generalizations of vertex algebras.
+Section~\ref{sec: config} offers a useful framework for studying these higher vertex algebras,
+using operads,
+and it develops powerful analogies to the little $n$-disks operad $E_n$ that plays an important role in contemporary topology.
+Section~\ref{sec: fact alg} introduces factorization algebras,
+providing a local-to-global principle to describe the observables on complex manifolds beyond affine spaces.
+In particular, by pushing forward factorization algebras,
+one can relate field theories of different dimension,
+i.e., a version of the physicist's ``compactification.''
+
+A reader could read this core section independently of the rest of the paper,
+as it focuses on algebra and geometry and requires no substantial knowledge of field theory {\it per se}.
+
+Section~\ref{sec: renorm} describes recent work that allows one to produce examples:
+there is now a convenient framework for renormalization of holomorphic field theories on $\CC^n$,
+and so the field theories of Section~\ref{sec: HFT} generate higher algebras of the form described in Sections~\ref{sec: algebra},~\ref{sec: config}, and~\ref{sec: fact alg}.
+The reader could skip to this section directly from Section~\ref{sec: HFT}.
+
+We conclude the paper by describing the kind of fascinating mathematical questions
+that arise by taking physical conjectures (e.g., dualities of supersymmetric theories) and twisting them into conjectures about holomorphic field theories. 
+Section~\ref{sec: seiberg} explores the holomorphic cousin of Seiberg duality,
+which suggests a remarkable correspondence between a gauge theory with group $SL(N)$ and a gauge theory with group $SL(M)$, where $M \neq N$.
+It is a kind of enhancement of Weyl's invariant theory and has close connections with topics like homological projective duality.
+
 \subsection{Acknowledgements}
 
+\owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum}
+
 \section{Holomorphic field theories}
+\label{sec: HFT}
 
@@
 
-\subsection{Precise definitions}
+\subsection{Definitions}
 
@@
 
-\begin{dfn}
+\begin{dfn}t 
 A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is
@@
 \section{Algebra and holomorphic field theories}
+\label{sec: algebra}
 
@@
 \section{Algebraic structures parametrized by configuration spaces}
+\label{sec: config}
 
@@
 \section{Factorization algebras and holomorphic field theories}
-\label{prefactorization_algebras}
+\label{sec: fact alg}
 
@@
 \section{Renormalization \& anomalies: constructing examples}
+\label{sec: renorm}
 

### 2024-09-14 draft.tex
rearranging holo field theory section

@@
 
-A reader could read this core section independently of the rest of the paper,
+A reader could read this core portion independently of the rest of the paper,
 as it focuses on algebra and geometry and requires no substantial knowledge of field theory {\it per se}.
@@
 
-\brian{complex geometry, dolbeault, dg stuff.}
+\owen{I rearranged this section somewhat.
+Our discussion of examples did not involve any BRST/BV stuff, so I put it right after the impressionistic opening.
+The "definitions" section seemed to be purely perturbative and to use notions from derived geometry, so I put it next.
+It should be fleshed out a little (e.g., a mention of the "fundamental theorem of deformaiton theory" and maybe show how to write one of the examples in that language).}
+
+We begin by sketching what a classical field theory is, somewhat impressionistically, and then offer some concrete examples.
 
@@
 where $CS(A)$ is exactly as in \eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$ only the $\dbar$ operator contributes to the kinetic term and so the action can be written as $\int_X \Omega \wedge \left(\frac12 \kappa( A ,\dbar A ) + \frac16 \kappa(A , [A,A]) \right)$.}
-
-\subsection{Definitions}
-
-We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.
-
-\begin{dfn}t 
-A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is
-\begin{itemize}
-\item a graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$, and
-\item a holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$.
-\end{itemize}
-This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
-\end{dfn}
-
-Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
-If $V$ is a holomorphic dg Lie algebra, 
-then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
-The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
-Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on $X$.
-
-Formal moduli spaces arise from the space of Maurer--Cartan elements of a dg Lie algebra.
-In our case, this dg Lie algebra will always be of the form $\Omega^{0,\bu}(X, V)$.
-For example, the Maurer--Cartan elements of the dg Lie algebra $\Omega^{0,\bu}(X, \fg)$ recovers formal deformations of the trivial holomorphic $G$-bundle.  
-This arises from the holomorphic Lie algebra on $X$ whose underlying vector bundle is trivial with fiber $\fg$.
-
-As another example, consider the holomorphic tangent bundle $V = \T_X$. 
-The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
-A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
-\[
-\dbar \mu + \frac12 [\mu,\mu] = 0 .
-\]
-This recovers the classical picture describing formal deformations of complex structures on~$X$.
-
-%this section aimed at mathematicians
-%emphasize connection with (derived) complex geometry
 
@@
 For more details we refer to~\cite{GRWwzw}.
+
+\subsection{Perturbative field theories via derived deformations}
+
+We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.
+
+\begin{dfn}t 
+A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is
+\begin{itemize}
+\item a graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$, and
+\item a holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$.
+\end{itemize}
+This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
+\end{dfn}
+
+Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
+If $V$ is a holomorphic dg Lie algebra, 
+then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
+The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
+Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on $X$.
+
+Formal moduli spaces arise from the space of Maurer--Cartan elements of a dg Lie algebra.
+In our case, this dg Lie algebra will always be of the form $\Omega^{0,\bu}(X, V)$.
+For example, the Maurer--Cartan elements of the dg Lie algebra $\Omega^{0,\bu}(X, \fg)$ recovers formal deformations of the trivial holomorphic $G$-bundle.  
+This arises from the holomorphic Lie algebra on $X$ whose underlying vector bundle is trivial with fiber $\fg$.
+
+As another example, consider the holomorphic tangent bundle $V = \T_X$. 
+The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
+A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
+\[
+\dbar \mu + \frac12 [\mu,\mu] = 0 .
+\]
+This recovers the classical picture describing formal deformations of complex structures on~$X$.
+
+%this section aimed at mathematicians
+%emphasize connection with (derived) complex geometry
 

### 2024-09-14 draft.tex
reworking the intro to holo field theory section

@@
 
-A physical field theory is usually described in terms of a space of fields that forms some possibly nonlinear space, like a mapping space $\Map(M,X)$ or the space of connections ${\rm Conn}_G(M)$ on a manifold.
-There is a manifold, called spacetime in physics, where the fields are some kind of functions out of it;
-in the examples just mentioned, it is denoted $M$.
-In perturbative field theory, which describes the formal neighborhood of the theory at a point in such spaces, 
-a field $\Phi$ is typically described by a smooth section of a vector bundle on spacetime.
-The equations of motion that dictate the dynamics of the particular model are encoded by a series of partial differential equations of the form 
-\[
-\sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
-\]
-where $D_k$ is a $k$-ary polydifferential operator.
-As an example, the scalar $\phi^4$-theory on a Riemannian $M$ is described by the equation
-\[
-\Delta \phi + \frac{1}{3!} \phi^3 = 0 
-\]
-where $\Phi = \phi$ is simply a smooth function on $M$.
-These equations of motion are natural to the Riemannian geometry of the manifold $M$, 
-and they can be derived from the Euler--Lagrange equations of the  action functional $\int_M \phi \Delta \phi \, \op{dvol}$.
-
-As another example, consider perturbative Chern--Simons theory whose fields are a principal $G$-bundle $P$ on a smooth three-manifold $M$ equipped with a connection.
-The equations of motion is the condition that the connection is flat 
+In physics, a classical field theory is usually described in terms of a few pieces of data:
+\begin{itemize}
+\item a manifold $M$ that plays the role of ``spacetime,''
+\item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
+\item a system of PDE for the fields, known as the equations of motion.
+\end{itemize}
+These equations of motion are variational: 
+they are the Euler-Lagrange equations of an action functional on the space a fields.
+An action functional is written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
+A few examples will illuminate this sketch.
+
+\begin{eg}[Massless scalar field theory]
+Let $M$ be a smooth manifold and equip it with a Riemannian metric~$g$.
+Let $\Delta_g$ denote the associated Laplace-Beltrami operator, 
+and let $\d{\rm vol}_g$ denote the associated volume form.
+Let the space of fields be the smooth functions $C^\infty(M)$.
+A smooth function $\phi$ is called, in physics, a {\em scalar} field.
+The action functional
+\[
+S(\phi) = \int_M \phi \Delta_g \phi \, \d{\rm vol}_g
+\]
+corresponds to the equation of motion $\Delta_g \phi = 0$. 
+Thus this scalar field theory has the moduli space of {\em harmonic functions} as its space of solutions.
+\end{eg}
+
+The preceding example exhibits how a moduli space of central interest in differential geometry --- the harmonic functions --- appears naturally as a basic example in physics (the ``free massless scalar field'').
+More complicated moduli spaces show up too.
+
+\begin{eg}[$\phi^4$ theory]
+As a small variant of the example just given,
+consider the action functional
+\[
+S(\phi) = \int_M \phi \Delta_g \phi + \frac{1}{4!} \phi^4\, \d{\rm vol}_g.
+\]
+Its equation of motion is the nonlinear PDE 
+\[
+\Delta_g \phi + \frac{1}{3!} \phi^3 = 0.
+\] 
+Thus this scalar field theory has a more complicated, nonlinear moduli space of solutions.
+\end{eg}
+
+We now describe an example of a theory whose space of solutions is a moduli space of interest in geometric topology.
+
+\begin{eg}[Chern-Simons theory]
+Pick a compact Lie group $G$ and equip it with an invariant metric,
+which induces a $G$-invariant inner product $\kappa$ on its Lie algebra~$\fg$.
+(The standard choice is the Killing form.)
+Take an oriented smooth 3-manifold $M$, 
+and consider the space of connections on the trivial principal $G$-bundle on $M$.
+This space of fields is isomorphic to $\Omega^1(M, \fg)$, the $\fg$-valued one-forms, 
+by viewing $\d + A$ as a connection where $A \in \Omega^1(M, \fg)$.
+The equation of motion is the zero-curvature equation
+\[
+F_A = 0,
+\]
+which can be expressed equivalently as the Maurer-Cartan equation
+\[
+\d A + \frac{1}{2} [A,A] = 0.
+\]
+These equations arise as the Euler-Lagrange equation for the action functional
 \beqn
-F_\nabla = 0 .
-\eeqn
-Perturbatively, near the trivial flat connection, the fields are simply $\lie{g} = \op{Lie}(G)$-valued one-forms $A \in \Omega^1(M, \lie{g})$.
-The condition that perturbed connection $\d + A$ is flat is the Maurer--Cartan equation
+\label{eqn:CS}
+CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]),
+\eeqn
+the integral of a Chern-Simons form.
+Hence this theory is known as {\em Chern-Simons theory}.\footnote{Note that $M$ needs to be an oriented 3-manifold for this action functional to make sense.
+The equation of motion exists for a principal bundle on any manifold of any dimension,
+but it is only variational for oriented 3-manifolds.}
+These equations do not depend on a metric on $M$ or any other geometric structure,
+and hence define a ``topological'' field theory in the sense that they are independent of geometry.
+This theory is interesting because the moduli space of solutions consists of the flat $G$-bundles on $M$,
+a topic of deep interest in geometry and topology.
+For physicists, it is interesting because it does not involve geometry, 
+by contrast to earlier examples of field theories,
+and yet exhibits rich phenomena (notably applications to the quantum Hall effect and 3-dimensional gravity).
+\end{eg}
+
+\begin{rmk}
+In the Chern-Simons example, there is an important aspect we did not yet acknowledge:
+we need to identify different solutions related by gauge transformations.
+In other words, the correct moduli space is the quotient stack
+\[
+\left[ \{ A \,:\, F_A = 0\}/\Map(M,G) \right].
+\]
+The usual mode of description of a field theory, by specifying fields and an action functional (or equations of motion), 
+must be supplemented by specifying whether to quotient by some group of symmetries of the space of solutions.
+More generally, a field theory ought to present some kind of derived moduli stack.
+\end{rmk}
+
+We are now in a good position to offer an example of a {\em holomorphic field theory}:
+the holomorphic analog of Chern-Simons theory.
+
+%In a {\em holomorphic theory} one starts with a complex manifold $X$ as the spacetime.
+%%This means, in part, that the complexified tangent bundle of $X$ decomposes as a sum of vector bundles $\T_X \oplus \Bar{\T}_X$ where $\T_X$ (respectively $\Bar{T}_X$) is the holomorphic (respectively anti-holomorphic) tangent bundle.
+%%In local coordinates sections of $\T_X$ have the form $f^i \del / \del z_i$ whereas sections of $\Bar{\T}_X$ have the form $f^i \del / \del \zbar_i$. 
+%Globally, holomorphic theories are described like in the usual case by mapping spaces or spaces of connections.
+%The key feature in a holomorphic theory is that the equations of motion dictate that fields be holomorphic in an appropriate sense.
+%Perturbatively, where fields are sections of some (possibly graded) holomorphic vector bundle $V$, we can make this precise. 
+%Prescribing a holomorphic structure on a vector bundle $V$ is equivalent to the data of a $\dbar$-operator
+%\beqn
+%\dbar \colon \Omega^{0,q}(X, V) \to \Omega^{0,q+1}(X,V) 
+%\eeqn
+%where $\Omega^{0,q}(X,V)$ is the space of smooth sections of the vector bundle $\wedge^q\Bar{T}_X^* \otimes V$. 
+%Holomorphicity of $V$ boils down to the requirement that $\dbar \circ \dbar = 0$.
+%The Dolbeault complex of $V$ is
+%\beqn
+%\left(\Omega^{0,\bu}(X, V), \dbar \right) = \left(\oplus_{q \geq 0} \Omega^{0,q}(X, V)[-q], \dbar \right)
+%\eeqn
+%where (in the case that $V$ sits in degree zero) the space $\Omega^{0,q}(X,V)$ sits in degree $+q$.
+%A standard result in complex geometry is that the Dolbeault complex is a resolution for the sheaf of holomorphic sections of the holomorphic vector bundle $V$.
+%%In the case that $V$ is the trivial bundle $\ul{\CC}$ the Dolbeault complex $\Omega^{0,\bu}(X)$ is a resolution for the sheaf of holomorphic functions on $X$.
+%
+%The fields of a holomorphic theory are given by elements of the Dolbeault complex $\Omega^{0,q}(X,V)$ for some $q$.
+%The equations of motion in a holomorphic theory take the form
+%\beqn
+%\dbar \Phi + \sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
+%\eeqn
+%where $D_k$ are $k$-ary {\em holomorphic} polydifferential operators.
+%This means that in local coordinates $D_k$ only depend on the holomorphic coordinates $\{z_i\}$ and involve only holomorphic derivatives $\del / \del z_i$.
+
+\begin{eg}[Holomorphic Chern-Simons theory]
+\owen{This feels rather convoluted. Can we make it simpler?}
+Pick a {\em complex} Lie group $G$, 
+and equip its Lie algebra $\fg$ with a complex-linear, $G$-invariant nondegenerate symmetric bilinear form~$\kappa$.
+Let $M$ be a three-dimensional \textit{complex} manifold
+equipped with a holomorphic volume form $\Omega \in \Omega^{3,0}(M)$; 
+in other words, $M$ is a Calabi--Yau manifold.
+(This condition is analogous to being an oriented 3-manifold.)
+Given a smooth principal $G$-bundle $P \to M$,
+there is a moduli space of holomorphic structures on~$P$.
+Suppose there exists at least one holomorphic structure $\cP \to M$,
+which has an associated Dolbeault operator (or $\dbar$-connection) $\dbar_{\cP}$.
+Any other holomorphic bundle structure determines a Dolbeault operator,
+but our reference point $\dbar_{\cP}$ provides an isomorphism
+\[
+{\rm Conn}^\dbar_G(P) \cong \Omega^{0,1}(M, {\rm ad}(P)),
+\]
+i.e., we express another $\dbar$-connection as $\dbar_{\cP} + A$ where $A$ is a $(0,1)$-form valued in the adjoint bundle.
+The equation of motion is again a Maurer--Cartan equation
 \beqn
-\d A + \frac12 [A,A] = 0.
-\eeqn
-These equations of motion are topological in the sense that they only depend on the smooth manifold~$M$.
-When $\lie{g}$ is equipped with a non-degenerate, invariant, bilinear form $\kappa$ (for example, if $G$ is semi-simple there is a standard choice) then these equations of motion can be derived from the famous Chern--Simons action functional $\int_M CS(A)$ where
-\beqn\label{eqn:CS}
-CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]) .
-\eeqn
-
-In a {\em holomorphic theory} one starts with a complex manifold $X$ as the spacetime.
-%This means, in part, that the complexified tangent bundle of $X$ decomposes as a sum of vector bundles $\T_X \oplus \Bar{\T}_X$ where $\T_X$ (respectively $\Bar{T}_X$) is the holomorphic (respectively anti-holomorphic) tangent bundle.
-%In local coordinates sections of $\T_X$ have the form $f^i \del / \del z_i$ whereas sections of $\Bar{\T}_X$ have the form $f^i \del / \del \zbar_i$. 
-Globally, holomorphic theories are described like in the usual case by mapping spaces or spaces of connections.
-The key feature in a holomorphic theory is that the equations of motion dictate that fields be holomorphic in an appropriate sense.
-Perturbatively, where fields are sections of some (possibly graded) holomorphic vector bundle $V$, we can make this precise. 
-Prescribing a holomorphic structure on a vector bundle $V$ is equivalent to the data of a $\dbar$-operator
-\beqn
-\dbar \colon \Omega^{0,q}(X, V) \to \Omega^{0,q+1}(X,V) 
-\eeqn
-where $\Omega^{0,q}(X,V)$ is the space of smooth sections of the vector bundle $\wedge^q\Bar{T}_X^* \otimes V$. 
-Holomorphicity of $V$ boils down to the requirement that $\dbar \circ \dbar = 0$.
-The Dolbeault complex of $V$ is
-\beqn
-\left(\Omega^{0,\bu}(X, V), \dbar \right) = \left(\oplus_{q \geq 0} \Omega^{0,q}(X, V)[-q], \dbar \right)
-\eeqn
-where (in the case that $V$ sits in degree zero) the space $\Omega^{0,q}(X,V)$ sits in degree $+q$.
-A standard result in complex geometry is that the Dolbeault complex is a resolution for the sheaf of holomorphic sections of the holomorphic vector bundle $V$.
-%In the case that $V$ is the trivial bundle $\ul{\CC}$ the Dolbeault complex $\Omega^{0,\bu}(X)$ is a resolution for the sheaf of holomorphic functions on $X$.
-
-The fields of a holomorphic theory are given by elements of the Dolbeault complex $\Omega^{0,q}(X,V)$ for some $q$.
-The equations of motion in a holomorphic theory take the form
-\beqn
-\dbar \Phi + \sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
-\eeqn
-where $D_k$ are $k$-ary {\em holomorphic} polydifferential operators.
-This means that in local coordinates $D_k$ only depend on the holomorphic coordinates $\{z_i\}$ and involve only holomorphic derivatives $\del / \del z_i$.
-
-For a simple example, consider the following holomorphic analog of Chern--Simons theory.
-The fields are principal $G$-bundles on a three-dimensional \textit{complex} manifold $X$, and the equations of motion give the condition that the principal $G$-bundle is holomorphic.
-Perturbatively, near the trivial $G$-bundle, the fields of this holomorphic theory are $\lie{g}$-valued $(0,1)$-forms $A \in \Omega^{0,1}(X, \lie{g})$.
-The condition that $\d + A$ prescribes a holomorphic structure is again a Maurer--Cartan equation
-\beqn
-\dbar A + \frac12 [A,A] = 0 .
-\eeqn
-Like ordinary Chern--Simons theory, in order for this equation to arise from a principal of least action one needs to fix a non-degenerate, invariant, bilinear form $\kappa$ on $\lie{g}$.
-Additionally, one needs to fix a holomorphic volume form $\Omega$ on $X$; in other words, $X$ is a Calabi--Yau manifold.
-Then, the equations of motion is precisely the Euler--Lagrange equation for the action
+\dbar_{\cP} A + \frac12 [A,A] = 0 ,
+\eeqn
+or equivalently the $(0,2)$-term of the curvature vanishes.
+This PDE is the Euler--Lagrange equation for the action
 \beqn
@@
 \eeqn
-where $CS(A)$ is exactly as in \eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$ only the $\dbar$ operator contributes to the kinetic term and so the action can be written as $\int_X \Omega \wedge \left(\frac12 \kappa( A ,\dbar A ) + \frac16 \kappa(A , [A,A]) \right)$.}
+where $CS(A)$ is exactly as in~\eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$, only the $\dbar A$ component of $\d A$ contributes to the integrand of the action functional, because $\Omega \wedge \partial A$ vanishes.}
+As in the case of Chern-Simons theory, one must quotient by the appropriate group of gauge transformations to obtain the correct moduli space, 
+which is here the moduli stack of holomorphic principal $G$-bundles whose underlying smooth structure is given by $P \to M$.
+\end{eg}
+
+For a systematic introduction to classical field theory in a style amenable to a complex geometer,
+we suggest \cite{FreedDeligne},
+although there are many other sources, such as \cite{}.
+For a detailed development of field theory in dialogue with derived geometry,
+see \cite{Steffens},
+and for a motivational discussion, likely more accessible to physicists, see \cite{AlfonsoYoung?}.
+In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
+(i.e., studying formal deformations of a fixed solution to the equations of motion),
+which we will use to produce examples of higher algebras.
 
 \subsection{Examples}
+
+In this section we describe several examples of holomorphic field theories,
+close to the style we used for holomorphic Chern-Simons theory.
 
@@
 We do not offer a thorough justification of the dictionary, for which see \owen{cite who?}
+
+\owen{Somewhere cite Donaldson and Thomas.}
 
@@
 \subsection{Perturbative field theories via derived deformations}
+\label{sec: pert dfn}
 

### 2024-09-16 draft.tex
continue to tinker with intro

@@
 
-\owen{mention some history (e.g., Manin!
-Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
+\owen{mention some history (e.g., Manin, Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, Kapranov, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
 
 \owen{Notation to explain: dg = differential graded, PDE = partial differential equations}
-
-\brian{we need to make sure to cite nekrasov}
 
@@
 
-The overarching goal of this paper is to introduce the reader to this emerging domain where physics and mathematics meet,
-with an emphasis upon how key objects from physics, notably supersymmetric theories and conformal field theories, 
-interface with complex geometry and especially with mathematical methods of rather recent vintage,
-notably derived geometry and higher algebras.
-A community is forming, involving both mathematicians and physicists,
-to bring into sharp mathematical form some of the deep insights into gauge theory offered by physics.
-There is a lot to explore here.
+\subsection{The aims of this survey}
+
+Over the last few decades there has been a vigorous dialogue between complex geometry and theoretical physics,
+around topics like mirror symmetry, enumerative algebraic geometry, moduli of Calabi-Yau manifolds, the geometric Langlands program, and integrable systems, among others.
+Our focus will be narrow:
+it is about higher dimensional versions of the relationship between geometry and algebraic structures like Lie algebras, Poisson algebras, and vertex algebras.
+We will emphasize analogies to TFTs (such as the Gerstenhaber algebras appearing in mirror symmetry) and CFTs (such as the affine Lie algebras relating to moduli of $G$-bundles on Riemann surfaces),
+but our primary interest is on complex manifolds above dimension one.
+Experience suggests that higher dimensions require higher algebra,
+i.e., algebraic methods that involve cochain complexes.
+Thus differential graded (dg) algebras and categories,
+as well as fellow travelers like derived geometry, appear.
+
+A community has formed, involving both mathematicians and physicists, to explore and exploit these relationships,
+and it continues to grow as there is a lot to explore here.
+Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, \cite{Vicedo}, \cite{BeemBZEtAl}, 
+where our own background and interests (and unfortunately, our ignorance) have shaped this list.
+
+We will not discuss important directions like mirror symmetry, the geometric Langlands program, the BPS/CFT correspondence, Donaldson-Thomas theory, or other, more global and geometric, areas,
+although we expect there are rich connections with the topics we do discuss.
+Not including these topics is primarily because our core theme already swelled to more pages than we expected, 
+because a concise discussion of any of those topics does not yet seem possible with respect to our theme,
+and because of our lack of background in these areas.
 
@@
 
-For a systematic introduction to classical field theory in a style amenable to a complex geometer,
-we suggest \cite{FreedDeligne},
-although there are many other sources, such as \cite{}.
-For a detailed development of field theory in dialogue with derived geometry,
-see \cite{Steffens},
-and for a motivational discussion, likely more accessible to physicists, see \cite{AlfonsoYoung?}.
+For a systematic introduction to classical field theory, 
+in a style amenable to a complex geometer,
+we suggest \cite{FreedDeligne}.
+There are many other sources, such as \cite{}, because classical field theory is an old and deep subject.
+Recently there is an effort to revisit field theory with insights from derived geometry.
+See \cite{AlfonsoYoung?} for motivation and overview, 
+but for a detailed development, see \cite{Steffens}.
 In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
@@
 
-\subsection{Perturbative field theories via derived deformations}
+\subsection{Perturbative field theory as derived deformation theory}
 \label{sec: pert dfn}
@@
 
-\begin{dfn}t 
+\begin{dfn} 
 A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is

### 2024-09-16 draft.tex
chugging

@@
 In this section we describe several examples of holomorphic field theories,
-close to the style we used for holomorphic Chern-Simons theory.
+in the style we used for holomorphic Chern-Simons theory.
+Our aim here is to give a sense of how take physical ideas and find holomorphic analogs.
 
@@
 
-We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.
+We now turn to giving a mathematical definition that incorporates insights from derived geometry.
+We will stick with studying perturbative field theory: 
+we fix a solution $\phi_0$ to the equations of motion and study formal deformations of it.
+In other words, we want to study the formal derived geometry of the moduli of solutions to the equations of motion.
+
+Here we can exploit the heuristic principle that every derived deformation problem (in characteristic zero) is described by a dg Lie algebra.\footnote{Or, sometimes more conveniently, by an $L_\infty$ algebra.}
+That is, if $\cM$ is a derived stack and $p: \Spec(\CC) \to \cM$ is a point, 
+then the formal neighborhood $\cM^\wedge_p$ of $p$ is modeled by the Maurer-Cartan locus of some dg Lie algebra $\fg_p$.\footnote{More technically, the shifted tangent complex $\TT_p \cM[-1]$ comes equipped with a homotopy-coherent Lie algebra structure,
+and this determines a functor from small (i.e., artinian local) nonnegatively-graded dg algebras to the $\infty$-category of spaces.}
+This idea goes back, at least, to Deligne, Drinfeld, and Schlessinger-Stasheff, 
+but Hinich, Lurie, and Pridham have given a precise articulation of the {\em fundamental theorem of derived deformation theory}:
+there is an equivalence of $\infty$-categories between formal moduli spaces and dg Lie algebras.
+
+Applying this perspective to classical field theory was prominently and successfully advocated by Kontsevich, 
+and it is an essential component of the formalism developed by Costello.
+We mimic this approach here.
 
 \begin{dfn} 
-A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is
+A {\em holomorphic local Lie algebra} on a complex manifold $X$ is
 \begin{itemize}
@@
 \end{itemize}
-This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
+This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a sheaf of dg Lie algebras.
 \end{dfn}
+
+We view such a sheaf $\cL$ of dg Lie algebras as describing a sheaf of formal moduli spaces.
+To each open $U$, we study the formal moduli space associated to $\cL(U)$ and interpret it as ``deformations of a solution $\phi_0|_U$ to the equations of motion on~$U$.''
+
+We now rephrase this data in the style of complex differential geometry and then further into more physical terminology.
+\owen{Keep going!}
 

### 2024-09-16 draft.tex
small attempt at adding to renorm section

@@
 \def\C{{\mathbb{C}}}
+
+\DeclareMathOperator{\Schw}{Schw}
 
@@
 
+\owen{Laying out some of this stuff in an attempt to state Minghao's theorem}
+
+We will allow graphs with finitely many vertices and edges, 
+but also leaves (also known as hair or half-edges).\footnote{That is, a vertex may have, in addition to edges connecting it to other vertices, some incident edges that do not connect to another vertex.
+These will label inputs to an operation associated to the graph.}
+We allow multiple edges between vertices, as well as loops.
+
+For a graph $\gamma$, let $E(\gamma)$ denote the number of edges,
+$V(\gamma)$ denote the number of vertices,
+and $L(gamma)$ denote the number of leaves.
+
+\begin{dfn}
+For a graph $\gamma$, there is a space $\RR_+^{E(\gamma)}$ parametrizing the moduli space of lengths (all positive) given to the edges.
+This positive orthant has a the partial compactification $\Schw(\gamma)$, known as the {\em Schwinger space} of $\gamma$, 
+where \owen{define!} 
+\end{dfn}
+
+\begin{dfn}
+For a perturbative holomorphic field on $\CC^d$ with space of fields 
+\[
+\cV = \Gamma(\CC^d, \Omega^{0,\bullet}(V)),
+\] 
+as defined in Section~\ref{}, 
+there is a family of distributions
+\[
+w_{\gamma, t}: \cV_c^{L(\gamma)} \to \CC
+\]
+parametrized by $t \in \RR_+^{E(\gamma)}$,
+known as the {\em regularized weight of $\gamma$}.
+\end{dfn}
+
+This family of distributions is constructed as an integral over $\CC^{v(\gamma) d}$,
+where each edge $e$ is labeled by a smooth function $P_{t(e)}$ depending on the length of the edge and where each vertex is labeled by a distribution arising from an interaction term of the theory.
+For general theories, one cannot smoothly continue the regularized weight from the positive length values to zero lengths.
+The putative integrals become divergent.
+
+For holomorphic field theories, however, something remarkable happens.
+
+\begin{thm}[Wang, \owen{precise citations}]
+For every graph~$\gamma$,
+this family has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
+\end{thm}
+
+In other words, divergences do not appear.
+
+\owen{It would be good to explain why and indicate what is the appropriate "value" to use.}
+
 The discussion so far in this section was about the analytic issues which are present when trying to make the path integral precise.

### 2024-09-17 draft.tex
edits in examples of holo field theories

@@
 around topics like mirror symmetry, enumerative algebraic geometry, moduli of Calabi-Yau manifolds, the geometric Langlands program, and integrable systems, among others.
-Our focus will be narrow:
-it is about higher dimensional versions of the relationship between geometry and algebraic structures like Lie algebras, Poisson algebras, and vertex algebras.
+Covering all these topics would be difficult.
+Our survey's focus will be narrow:
+it is upon higher dimensional versions of the relationship between geometry and algebraic structures like Lie algebras, Poisson algebras, and vertex algebras.
 We will emphasize analogies to TFTs (such as the Gerstenhaber algebras appearing in mirror symmetry) and CFTs (such as the affine Lie algebras relating to moduli of $G$-bundles on Riemann surfaces),
@@
 
-We will not discuss important directions like mirror symmetry, the geometric Langlands program, the BPS/CFT correspondence, Donaldson-Thomas theory, or other, more global and geometric, areas,
+The material below focuses on connections with this work,
+and the examples from physics have a perturbative flavor.
+We will not discuss important directions like mirror symmetry, the geometric Langlands program, the BPS/CFT correspondence, Donaldson-Thomas theory, or other areas that are more global or more directly geometric,
 although we expect there are rich connections with the topics we do discuss.
@@
 and because of our lack of background in these areas.
+We hope the ideas surveyed here do connect profitably to these topics.
+\owen{Is that an overly negative paragraph?}
 
@@
 \begin{eg}[Massless scalar field theory]
+\label{eg: massless scalar}
 Let $M$ be a smooth manifold and equip it with a Riemannian metric~$g$.
@@
 of which the Standard Model offers a nice example.
-The basic types are\footnote{For the experts, we remark that we focus above on the core field content, and ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
+The basic types are\footnote{For the experts, we remark that we focus above on the field content that motivates or characterizes, and mostly ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
 \begin{itemize}
@@
 Such theories are often used to describe matter, such as electron fields.
-\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
+\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as nonlinear generalizations of scalar field theories.)
 \item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
@@
 The Standard Model involves the first three types,
-and the different fields interact in intricate ways.\footnote{For instance, the scalar and fermionic fields are sections for associated bundles of the principal bundle appearing in the gauge theory.}
+and the different fields interact in intricate ways.\footnote{For instance, the scalar and fermionic fields are sections of associated bundles to the principal bundle appearing in the gauge theory.}
 
 There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.
+and we now spell out some simple examples.\footnote{See \cite{Donaldson Thomas} for a pioneering and illuminating discussion of how to find such analogs.}
 To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
@@
 in terms of PDE and action functionals but also as moduli spaces.
-We do not offer a thorough justification of the dictionary, for which see \owen{cite who?}
-
-\owen{Somewhere cite Donaldson and Thomas.}
+We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
+and see \cite{AlfonsoYoung} and \cite{Steffens} for recent work on this topic.
 
@@
 see Section~\ref{sec: seiberg}.
-One motivation for us to explore holomorphic field theories is that one can translate physical insights and conjectures (such as Seiberg duality) into surprising predictions in the holomorphic setting,
-which is typically much cleaner and more accessible.
+
+A motivation for us to explore holomorphic field theories is that physical insights and conjectures, such as Seiberg duality, translate into surprising predictions in the holomorphic setting,
+which is typically more accessible for mathematics.
 (One might also hope that progress in the holomorphic setting then feeds back useful insights to physics.)
@@
 
-A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
-Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
-When $\Sigma$ is a surface this theory can be written in such a way that makes its complex structure apparent.
-First, we complexify the field $\phi$ which we can view as a pair of fields $\gamma, \Bar{\gamma}$.
-When we do this, we can split it up into its chiral and anti-chiral `sectors'.
-By chiral (anti-chiral) we mean part involving $\gamma$ ($\Bar{\gamma}$).
-The holomorphic part is described by the following action
+The standard example of a scalar field theory is the free massless exists on any Riemannian manifold,
+which we met in Example~\ref{eg: massless scalar}.
+Here the field $\phi$ a smooth function on a manifold $M$,
+its action functional is $\int_M \phi \Delta \phi$, where $\Delta$ is the Laplace-Beltrami operator, 
+and its equation of motion is $\Delta \phi = 0$.
+The moduli space of solutions is then the space of harmonic functions on~$M$
+
+When $M$ is two-dimensional and oriented,
+we can view $M$ as equipped with a complex structure.
+Every complex-valued harmonic function then decomposes as a sum of a holomorphic and anti-holomorphic function. 
+That is, if we complexify the scalar field $\phi$, 
+we can view it as a pair of fields $\gamma$ and $\Bar{\gamma}$,
+where the equation of motion of $\gamma$ is $\dbar \gamma = 0$ and the equation of motion is $\partial \Bar{\gamma} = 0$.
+These components are sometimes called the chiral and anti-chiral ``sectors.''
+
+Notice that we have shifted from a second-order differential operator $\Delta$ to first-order differential operators $\dbar$ and~$\partial$.
+Reworking a theory to express its equations of motion using first-order operators is sometimes called the first-order formalism.
+
+The holomorphic component can be seen as arising from the following action functional,
 \beqn
-\int_\Sigma \beta \wedge \dbar \gamma
-\eeqn
-where $\beta$ is a $(1,0)$ form on $\Sigma$ and should be thought of as a Lagrange multiplier for the field $\del \Bar{\gamma}$ which we now think about as having its own degrees of freedom (this is called the first-order formalism).
-There is also a coupling between the chiral and anti-chiral sectors, 
-for more details we refer to \cite{Kapustin,GGW}. 
-This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta\gamma$-\textit{system}.
-It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.
-
-There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta\gamma$ system'.
-The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
-Above we took this bundle to be trivial.
-The fields of the theory consist of pairs 
-\begin{align*}
-\gamma & \in \Gamma(X,V)\\
-\beta & \in \Omega^{n,n-1}(X,V^*) .
-\end{align*}
-The action functional is identical $\int_X \beta \wedge \dbar \gamma$.
-
-Notice that when $n = \dim_\C X > 1$ that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
-\beqn
-\beta \mapsto \beta + \dbar \eta , \quad \eta \in \Omega^{n,n-2}(X,V^*)
-\eeqn
-For this model to be well-posed at the quantum level we must include the ghosts $\eta$.
-Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
-This is one of the key differences between the ordinary $\beta\gamma$ system and its higher dimensional version.
-Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.
+\int \beta \wedge \dbar \gamma
+\eeqn
+where $\beta$ is a $(1,0)$-form on $M$ and should be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$,
+\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}
+which we now think about as having its own degrees of freedom. 
+Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
+so that $\beta$ should be a holomorphic $1$-form.
+
+This piece of the free boson is the simplest holomorphic field theory; it is often called the $\beta\gamma$-\textit{system}.
+It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.\owen{More precise location?}
+
+It should seem reasonable to view two solutions $\beta_1$ and $\beta_2$ as equivalent if they differ by a $\dbar$-exact term.
+If one imposes this equivalence relation (a kind of ``gauge symmetry''),
+then one is on the path towards setting up the theory in the Batalin-Vilkovisky formalism.
+
+Derived geometry is the mathematical version of BV formalism.
+From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
+\[
+T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\cT^{*{1,0}}),
+\]
+a rather natural space to study in complex geometry.
+
+\begin{rmk}
+We motivated the $\beta\gamma$ system as encoding a piece of the free boson.
+There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$ system as encoding the antichiral sector of the free boson.
+To recover the full boson, one must couple the chiral and anti-chiral sectors.
+See \cite{Kapustin,GGW} \owen{Where?} for more details. 
+\end{rmk}
+
+This example admits a natural generalization to an arbitrary complex manifold.
+The input data is a complex manifold $X$ of arbitrary complex dimension $n$, 
+together with a holomorphic vector bundle $V$ on~$X$.
+(Above we took this bundle to be trivial.)
+The fields of the theory consist of a pair $(\gamma,\beta)$ where 
+\[
+\gamma \in \Gamma(X,V) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(X,V^*) .
+\]
+The action functional is 
+\[
+\int_X \beta \wedge \dbar \gamma
+\]
+and the equations of motion are
+\[
+\dbar \gamma = 0 = \dbar \beta.
+\]
+We again suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
+
+We will not examine fermions here,
+but note that it is straightforward to consider super-holomorphic vector bundles,
+i.e., holomorphic $\ZZ/2$-graded vector bundles.
+In this way, one can develop analogs of fermions.
+
+\subsubsection{Holomorphic $\sigma$-models}
+
+\owen{Quickly explain the nonlinear analog of the $\beta\gamma$ system.}
 
@@
 
-\subsubsection{Holomorphic scalar field theories}
+\subsubsection{Holomorphic field theories as chiral sectors}
 
@@
 In \cite{FHK} they are shown to appear naturally in various contexts,
-notably in studying the derived moduli of $G$-bundles on a complex varieties of dimension~$d$.
+notably in studying the derived moduli space of $G$-bundles on a complex varieties of dimension~$d$.
 
@@
 \[
-x_0 \otimes f_0, \ldots, x_{d} \otimes f_{d} \mapsto \Tr_V( x_0 \cdots x_{d}) \Res(f_0 \partial f_1 \cdots \partial f_{d}).
+(x_0 \otimes f_0, \ldots, x_{d} \otimes f_{d}) \mapsto \Tr_V( x_0 \cdots x_{d}) \,\Res(f_0 \, \partial f_1 \wedge \cdots \wedge \partial f_{d}).
 \]
@@
 To each open interval $(a,b)$, we set $\cF_A( (a,b) ) = A$. 
-To any open set $U = \coprod_j I_j$, where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$.
+To any open set $U = \coprod_j I_j$, 
+where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$. 
 The structure maps simply arise from the multiplication map for $A$. 
 Figure ~\ref{fig:assasfact} displays the structure of $\cF_A$. 
-Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra.
-%(One takes an infinite tensor products of unital algebras, as follows.
-Given an infinite set $I$, consider the poset of finite subsets of $I$, ordered by inclusion.
-For each finite subset $J \subset I$, we can take the tensor product $A^J = \bigotimes_{j \in J} A$.
-For $J \hookrightarrow J'$, we define a map $A^J \to A^{J'}$ by tensoring with the identity $1 \in A$ for every $j \in J' \backslash J$.
-Then $A^I$ is the colimit over this poset.)
-~\hfill$\Diamond$
+Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra.~\hfill$\Diamond$
 \end{eg}
@@
 \begin{rmk}
-The reader fond of higher abstract nonsense will note that we could have factorization algebras take values in other target categories (better, $\infty$-categories),
+The reader fond of higher abstract nonsense will note that we could have factorization algebras take values in other target categories (or even better, $\infty$-categories),
 not just vector spaces or cochain complexes.
-For instance, one might assign an $\infty$-category to each open set.
+For instance, one might categorify the values: 
+$\cF$ might assign an $\infty$-category $\cF(U)$ to each open set~$U$.
 This generalization is fruitful.
-In the Beilinson-Drinfeld style, it leads to chiral categories, which play an increasingly central role in the geometric Langlands program.
+In the Beilinson-Drinfeld style, it leads to chiral categories, which play a key role in the geometric Langlands program.
 In the style advocated above, it would likewise be useful for capturing notions like defects or extended operators from quantum field theory.
 \end{rmk}
-
-%\subsection{Prefactorization algebras as algebras over an operad}
-%\label{sec:disj}
-%
-%The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
-%A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
-%See \owen{add citations}
-%
-%\begin{dfn}
-%Let $\Disj_M$ denote the following colored operad associated to~$M$: 
-%\begin{itemize}
-%\item The colors (or objects) consist of all open subsets of $M$. 
-%\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$.
-If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point.
-Otherwise, the set of maps is empty.
-%\item The composition of maps is defined in the obvious way. 
-%\end{itemize}
-%\end{dfn}
-%
-%\begin{dfn}
-%Let $\mc{C}$ be a colored operad. 
-%A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
-%\end{dfn}
-%
-%In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
-%Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories. 
-%
-%\begin{rmk} 
-%If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
-%Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
-%~\hfill$\Diamond$ 
-%\end{rmk}
-%
-%Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$. 
-%
-%\begin{dfn}
-%We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
-%\end{dfn}
-%
-%\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
-%\label{AssAsFact}
-%
-%We explained above how an associative algebra provides a prefactorization algebra on the real line.
-There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras.
-Here we will characterize those that do arise from associative algebras.
-% 
-%\begin{dfn}
-%Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
-%We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
-%\end{dfn}
-%
-%It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.
-%
-%\begin{lem}\label{locally_constant_is_associative}
-%Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
-%Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
-%\end{lem}
-%
-%One can got further, however, and also capture modules, essentially by marking the line with points.
-%For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.
-%
-%Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$.
-%We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure. 
-%
-%Pick a point $p \in \RR$.
-On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$.
-Likewise, on the half-line $\{x \in \RR \mid p < x\}$, $\cF_M$ is given by $\cF_B$.
-Intervals containing $p$ are determined, though, by $M$.
-When we consider an interval $I = (t_0,t_1)$ such that $t_0 < p < t_1$, we set $\cF_M(I)  = M$.
-The structure maps are also determined by the bimodule structure.
-For example, given
-%\[
-%s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
-%\]
-%we have
-%\begin{align*}
-%\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
-%&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
-%&= A \ot M \ot B
-%\end{align*}
-%and the inclusion of these three intervals into $(s_0,u_1)$ is the map
-%\[
-%\begin{array}{ccc}
-%\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
-%a \ot m \ot b & \mapsto & amb
-%\end{array}.
-%\]
-%The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.
-%
-%%\begin{figure}
-%%\begin{center}
-%% \begin{minipage}{3cm}
-%% \begin{tikzpicture}[scale=0.75]
-%% \begin{scope}[line cap=round,ultra thick]
-%% \draw (-2.5,0) -- (-1.5,0); 
-%% \draw (-1,0) -- (0.5,0); 
-%% \draw[fill=black] (0,0) circle (0.07);
-%% \draw (1.5,0) -- (2.5,0); 
-%% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
-%% \draw (-2.75,-2) -- (0.75,-2); 
-%% \draw[fill=black] (0,-2) circle (0.07);
-%% \draw (1.25,-2) -- (2.75,-2);  
-%% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
-%% \draw (-3,-4) -- (3,-4);
-%% \draw[fill=black] (0,-4) circle (0.07); 
-%% \end{scope}
-%% \end{tikzpicture}
-%% \end{minipage}
-%%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
-%% \begin{minipage}{8cm}
-%% \begin{tikzcd}[cramped,column sep=tiny]
-%%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
-%%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
-%%amb  & \in &M 
-%%\end{tikzcd}
-%%\end{minipage}
-%%\end{center}
-%%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
-%%\label{fig:bimodasfact}
-%%\end{figure}
-%
-%\begin{figure}
-%\begin{center}
-% \begin{tikzpicture}
-% \begin{scope}[line cap=round,ultra thick]
-% \draw (-2.5,1) -- (-1.5,1); 
-% \draw (-1,1) -- (0.5,1); 
-% \draw[fill=black] (0,1) circle (0.07);
-% \draw (1.5,1) -- (2.5,1); 
-% \draw[->,semithick] (0,0.75) -- (0,0.25);
-% \draw (-2.75,-0.1) -- (0.75,-0.1); 
-% \draw[fill=black] (0,-0.1) circle (0.07);
-% \draw (1.25,-0.1) -- (2.75,-0.1);  
-% \draw[->,semithick] (0,-0.35) -- (0,-0.85);
-% \draw (-3,-1.2) -- (3,-1.2);
-% \draw[fill=black] (0,-1.2) circle (0.07); 
-% \end{scope}
-%
-%\node at (4,0){$\rightsquigarrow$};
-%
-%\node at (7,0) {
-%\begin{tikzcd}[cramped,column sep=tiny]
-%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
-%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
-%amb  & \in &M 
-%\end{tikzcd}
-%};
-%
-%\end{tikzpicture}
-%\end{center}
-%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
-%\label{fig:bimodasfact}
-%\end{figure}
 
@@
 
-The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$. 
+The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. 
+We call it the {\em Weiss topology} of~$M$. 
 Note that Weiss covers are required to ``know'' about every configuration of finitely many points,
@@
 (If one has a metric on the manifold, one can work with unions of ``small'' discs.)
-
-%\begin{rmk}
-%A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens.
-It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$.
-For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection
-%\[
-%\{ U_i^n \mid i \in I\}
-%\]
-%provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
-%\end{rmk}
-%
-%\begin{eg}\label{WeissAsExponential}
-%For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$.
-One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
-Alternatively, the collection of opens $\{ M \setminus q \mcol q \in M\}$ is a Weiss cover of $M$.
-One can also produce a Weiss cover of a manifold with countably many elements.
-Fix a Riemannian metric on $M$.
-Pick a collection of points $\{q_n\in M \mcol n \in \NN\}$ such that the union of the unit ``discs'' $D_1(q_n) = \{ q \in M \mcol \d(q_n,q) < 1\}$ covers $M$.
-(Such an open may not be homeomorphic to a disc if the injectivity radius of $q_n$ is less than 1.)  Consider the collection of all ``discs'' $\fD = \{ D_{1/m}(q_n) \mcol m \in \NN, n \in \NN\}$.
-The collection of all finite, pairwise disjoint union of elements of $\fD$ is a countable Weiss cover.~\hfill $\Diamond$
-%\end{eg}
 
@@
 
-%Many examples of factorization algebras satisfy an additional and desirable property,
-%which motivates the name ``factorization algebra.''
-%
-%\begin{dfn}
-%A factorization algebra $\cF$ is \emph{multiplicative} if for every pair $U,V$ of disjoint open subsets of $M$, the structure map
-%$$
-%\cF(U) \otimes \cF(V) \to \cF(U \sqcup V) 
-%$$
-%is a quasi-isomorphism.
-%\end{dfn}
-
 \subsection{How factorization algebras appear in QFT}
-
-%Associative algebras are familiar to every mathematician, but as we have just seen, they reflect and encode one-dimensional geometry.
-%It is then natural to ask about higher-dimensional versions of algebra.
-%Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-discs operad,
-%which we now describe and relate to prefactorization algebras on~$\RR^n$.
-%In relation to the subject of this paper, we mention that $E_n$ algebras arise naturally from $n$-dimensional topological field theories;
-%we will soon introduce a holomorphic analog of $E_n$ algebras relevant to holomorphic field theories,
-%modeled on the discussion here.
-%
-%Fix a dimension $n$. 
-%Let $D^n(x,r)$ denote the open disc of radius $r$ centered at $x \in \RR^n$,
-%and let $D^n$ denote the unit disc~$D^n(0,1)$.
-%
-%\begin{dfn}
-%Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint discs:
-%\[
-%E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the discs $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disc $D^n$\end{tabular}}\right\}.
-%\]
-%\end{dfn}
-%
-%When $n = 1$, the operad encodes the idea of associative multiplication:
-%we get pictures much like those we drew earlier with intervals, 
-%except that now we can slide and stretch the intervals because we have a space of operations.
-%More accurately, $E_1$ is a model for associative algebras up to homotopy; 
-%it is closely related to the $A_\infty$ operad. \owen{Let me check how people compare these.}
-%
-%For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
-%If one fixes a direction, such as a coordinate axis, and works with discs lined up in this direction,
-%one sees an $E_1$ structure.
-%
-%\owen{Add picture? We drew 2d pictures earlier.}
-%
-%An algebra over this operad is called an {\em $E_n$-algebra}.
-%A classic example from topology is given by taking the $n$-fold based loop space
-%\[
-%\Omega^n_x(X) = \{ \gamma: \overline{D^n} \to X \mcol \gamma(\partial \overline{D^n}) = x\}
-%\]
-%of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disc.
-%Maps that send the boundary of a disc to the base point can be extended naturally to bigger discs: just send the rest of the big disc to the basepoint.
-%\owen{Should I spell out the structure of the algebra?}
-%Examples include \owen{What to mention?}
 
@@
 a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra and, by Lurie's work, a $G$-framed fully extended $d$-dimensional TFT.
-It is interesting to ask how these kinds of functorial field theories intertwine with the better-known examples.
+It is interesting to ask how these kinds of functorial field theories intertwine with the better-known constructions,
+such as the Reshetikhin-Turaev theories, 
+where the target category is not ${\rm Alg}_d$ but some other higher-categorical extensions of~$\Vect$.
 

### 2024-09-17 draft.tex
added subsections on fermionic theories and sigma models

@@
 (Above we took this bundle to be trivial.)
-The fields of the theory consist of a pair $(\gamma,\beta)$ where 
+Each field of the theory consists of a pair $(\gamma,\beta)$ where 
 \[
@@
 \]
-We again suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
-
-We will not examine fermions here,
-but note that it is straightforward to consider super-holomorphic vector bundles,
+Solutions consist of a holomorphic function $\gamma$ and a holomorphic $(n,n-1)$-form.
+We again suggest to identify solutions to the second equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
+
+\subsubsection{Holomorphic fermions}
+
+It is straightforward to modify the example above to allow super-holomorphic vector bundles,
 i.e., holomorphic $\ZZ/2$-graded vector bundles.
-In this way, one can develop analogs of fermions.
+
+For example, given a holomorphic vector bundle $V$ on a complex $n$-fold~$X$,
+let $\Pi V$ denote the parity-reversed vector bundle,
+i.e., we now give $V$ an odd grading.
+There is a $bc$ system that is the fermionic analog of the $\beta\gamma$ system.
+The fields of the theory consist of a pair $(c,b)$ where 
+\[
+c \in \Gamma(X,\Pi V) \quad\text{and}\quad b \in \Omega^{n,n-1}(X,\Pi V^*) .
+\]
+Thus, $b$ and $c$ are fermionic fields.
+The action functional is 
+\[
+\int_X b \wedge \dbar c,
+\]
+and the equations of motion are
+\[
+\dbar c = 0 = \dbar c.
+\]
+We again suggest to identify solutions to the equation $\dbar c = 0$ that differ by a $\dbar$-exact form.
+
+There is a special class of fermionic theories that is quite interesting.
+Let $X$ be a complex $n$-fold where
+\begin{itemize}
+\item $n = 2k+1$ is odd and
+\item there is a line bundle $L \to X$ such that $L^{\otimes 2} \cong K_X$,
+i.e., $L$ is a square root of the canonical bundle.
+\end{itemize}
+A field is a section
+\[
+\psi \in \Omega^{0,k}(X,\Pi L),
+\]
+the action functional is
+\[ 
+\int_X \psi \wedge \dbar \psi,
+\]
+and the equation of motion is
+\[
+\dbar \psi = 0.
+\]
+We suggest to identify solutions that differ by $\dbar$-exact terms.
+
+From the point of view of derived geometry, the cochain complex
+\[
+\Omega^{0,\bullet}(X, \Pi L)[k]
+\]
+presents a derived stack that should be viewed as the moduli of solutions for this theory.
+
+\owen{What do you think of this example?}
 
@@
 
-\owen{Quickly explain the nonlinear analog of the $\beta\gamma$ system.}
+A $\sigma$-model is a field theory whose space of fields contains a mapping space $\Map(M,N)$.
+When $N = \RR$, this mapping space simply becomes functions and so the $\sigma$-model reduces to a scalar field theory.
+
+There is a natural generalization of the $\beta\gamma$ system to a $\sigma$ model.
+Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
+The fields are a pair $(\gamma, \beta)$ where
+\[
+\gamma \in \Map(M,N) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(M,\gamma^* T^*_N) .
+\]
+Note that $\dbar \gamma$ lives in $\Omega^{0,1}(M, \gamma^* T_N)$, 
+a section of the pullback of the tangent bundle of the target.
+The action functional is 
+\[
+\int_X \beta \wedge \dbar \gamma,
+\]
+where we use the canonical evaluation pairing between the pullback of the tangent and cotangent bundles of the target.
+The equations of motion are
+\[
+\dbar \gamma = 0 = \dbar \beta,
+\]
+so that solutions consist of a holomorphic map $\gamma: M \to N$ and a holomorphic section $\beta$ of the pullback tangent bundle.
+As usual, we suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
+
+From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
+\[
+T^*[-1] \Map_\dbar(M,N) 
+\]
+a rather natural space to study in complex geometry.
 

### 2024-09-17 draft.tex
revising precise def

@@
 \begin{eg}[Holomorphic Chern-Simons theory]
+\label{eg: holCS}
 \owen{This feels rather convoluted. Can we make it simpler?}
@@
 and this determines a functor from small (i.e., artinian local) nonnegatively-graded dg algebras to the $\infty$-category of spaces.}
-This idea goes back, at least, to Deligne, Drinfeld, and Schlessinger-Stasheff, 
+This idea goes back to Deligne, Drinfeld, and Schlessinger-Stasheff, and perhaps farther, 
 but Hinich, Lurie, and Pridham have given a precise articulation of the {\em fundamental theorem of derived deformation theory}:
@@
 and it is an essential component of the formalism developed by Costello.
-We mimic this approach here.
+The idea is that if want to study the perturbation theory around some solution~$\phi_0$ on the whole spacetime manifold~$X$,
+then on each open set $U$ in~$X$,
+there is a formal moduli space describing deformations of the restriction~$\phi_0|_U$.
+In other words, there is a sheaf on $M$ with values in formal moduli spaces,
+and this sheaf describes the perturbative field theory.
+
+By the fundamental theorem, we can describe this sheaf of formal moduli spaces by supplying a sheaf of dg Lie algebras, which can often be quite convenient.
+We follow this approach here.
 
@@
 
-We view such a sheaf $\cL$ of dg Lie algebras as describing a sheaf of formal moduli spaces.
-To each open $U$, we study the formal moduli space associated to $\cL(U)$ and interpret it as ``deformations of a solution $\phi_0|_U$ to the equations of motion on~$U$.''
+Here is a quick example, as motivation.
+Let $X$ be a Calabi-Yau 3-fold equipped with a holomorphic principal $G$-bundle $P \to X$.
+There is an associated adjoint bundle $\fg_P \to X$, and hence a coherent sheaf $\cG_P$ of holomorphic sections of the adjoint bundle.
+Note that $\cG_P$ is a holomorphic local Lie algebra, using the fiberwise Lie bracket,
+and it describes the formal neighborhood of $P$ inside the space $\Bun_G(X)$.
+In other words, it encodes the perturbative part of holomorphic Chern-Simons theory of Example~\ref{eg: holCS}.
 
 We now rephrase this data in the style of complex differential geometry and then further into more physical terminology.
-\owen{Keep going!}
 
 Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
-If $V$ is a holomorphic dg Lie algebra, 
+If $V$ is a holomorphic local Lie algebra, 
 then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
-The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
-Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on $X$.
-
-Formal moduli spaces arise from the space of Maurer--Cartan elements of a dg Lie algebra.
-In our case, this dg Lie algebra will always be of the form $\Omega^{0,\bu}(X, V)$.
-For example, the Maurer--Cartan elements of the dg Lie algebra $\Omega^{0,\bu}(X, \fg)$ recovers formal deformations of the trivial holomorphic $G$-bundle.  
-This arises from the holomorphic Lie algebra on $X$ whose underlying vector bundle is trivial with fiber $\fg$.
-
-As another example, consider the holomorphic tangent bundle $V = \T_X$. 
-The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
-A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
-\[
-\dbar \mu + \frac12 [\mu,\mu] = 0 .
-\]
-This recovers the classical picture describing formal deformations of complex structures on~$X$.
+The differential is $\dbar + Q^{hol}$, 
+and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
+Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on~$X$.
+
+In the case of our running example, we obtain the dg Lie algebra
+\[
+\Omega^{0,\bu}(X,\fg_P)
+\]
+from the adjoint bundle of the holomorphic principal $G$-bundle on our Calabi-Yau 3-fold~$X$.
+A Maurer-Cartan element in this dg Lie algebra is a $(0,1)$-form $A$ such that
+\[
+\dbar_P A + \frac{1}{2}[A,A] = 0,
+\]
+meaning that $\dbar_P + [A,-]$ defines another $\dbar$-connection, and hence holomorphic structure, on the smooth bundle $P \to~X$.
+
+The take-away message is that the Dolbeault complex of a holomorphic Lie algebra leads to a PDE, by taking the Maurer-Cartan equation,
+and this PDE should be seen as the equation of motion.
+
+In this example the PDE arises from the variations of the action functional
+\[
+\int_X \Omega \wedge \left( \frac{1}{2}\langle A, \dbar A\rangle + \frac{1}{3!}\langle A, [A,A]\rangle \right).
+\]
+The PDE does not involve the choice of a holomorphic volume form $\Omega$ or a pairing on the Lie algebra $\fg$, 
+but the action functional did.
+
+In general, for a holomorphic local Lie algebra to arise from a field theory,
+it is necessary to provide more data so as to be able to write down an action functional.
+
+\begin{dfn}
+A {\em local cyclic structure} on a holomorphic local Lie algebra is a degree $-3$ map
+\[
+\langle -,-\rangle: V \otimes V \to K_X
+\]
+of holomorphic vector bundles\footnote{Here $\otimes$ denotes the Whitney tensor product of vector bundles on $X$.} such that 
+\begin{itemize}
+\item if $f, g$ are holomorphic sections of $V$, then 
+\[
+\langle Q^{hol}f, g \rangle + (-1)^{|f|} \langle f, Q^{hol} g \rangle = 0
+\]
+so that the pairing is a cochain map, and
+\item if $f, g, h$ are holomorphic sections of $V$, then 
+\[
+\langle f, [g,h] \rangle = (-1)^{|f|} \langle h,  \rangle
+\]
+so that the pairing is invariant for the bracket.
+\end{itemize}
+\owen{We must check the signs. Am I missing something.}
+\end{dfn}
+
+Given a local cyclic structure, there is an action functional
+\[
+\int_X \frac{1}{2} \langle f, \dbar f + Q^{hol} f \rangle + \frac{1}{3!} \langle f, [f,f] \rangle 
+\]
+whose equation of motion is the Maurer-Cartan equation
+\[
+\dbar f + Q^{hol}f + \frac{1}{2} [f,f] = 0.
+\]
+
+\owen{What else to say?}
+
+%
+%As another example, consider the holomorphic tangent bundle $V = \T_X$. 
+%The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
+%A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
+%\[
+%\dbar \mu + \frac12 [\mu,\mu] = 0 .
+%\]
+%This recovers the classical picture describing formal deformations of complex structures on~$X$.
 

### 2024-09-17 draft.tex
moving small things around

@@
 
-\def\brian#1{{\textcolor{blue!65!red}{BW: {#1}}}}
-\def\owen#1{{\textcolor{violet!65!black}{OG: {#1}}}}
+\def\brian#1{{\textcolor{blue!75!red}{BW: {#1}}}}
+\def\owen#1{{\textcolor{violet!50!black}{OG: {#1}}}}
 
@@
 \owen{Notation to explain: dg = differential graded, PDE = partial differential equations}
+
+\brian{Comparison}
 
@@
 but the techniques typically extend to more general complex manifolds.
-
-This foundational work was motivated in large part by our joint effort to generalize to complex $n$-folds results about chiral conformal theories on Riemann surfaces.
-A first fruit of our work \cite{GWcurr} is an examination of higher-dimensional {\em current algebras},
-which are factorization algebras that generalize the Kac-Moody vertex algebras that play a crucial role in contemporary representation theory.
-We show, for instance, that these current algebras arise as the quantization of symmetries of holomorphic field theories, 
-much as the affine Lie algebras are symmetries of CFTs on Riemann surfaces.
-In addition, we show that encoded in our factorization algebras are the higher Kac-Moody Lie algebras $\widehat{\g}_{d,\theta}$ of Faonte-Hennion-Kapranov~\cite{FHK}. 
-It is striking to find this rigid skeleton of algebra under the meat of our analysis,
-as our work is strongly differential-geometric in flavor.
-Moreover, as their work provides a direct connection with the derived algebraic geometry of $\RR Bun_G(X)$,
-there emerges a beautiful generalization of the fertile interactions between algebraic geometry, representation theory, and physics that have grown around bundles on Riemann surfaces.
-(The prospect looms that in higher dimensions,
-one might find a correspondence between conformal blocks and nonabelian theta functions.)
-
-A second fruit is a collaboration of Williams with the physicist Ingmar Saberi \cite{SabWil1,SabWil2}.
-They have carefully worked out the holomorphic twists of several supersymmetric theories
-and given a novel approach, via factorization algebras, to the results of Beem et al \cite{Beem}.
-Particularly important for this proposal,
-they have shown how important invariants (notably the ``supersymmetric index") of the untwisted, supersymmetric theory can be computed simply in the holomorphic twist.
 
@@
 
+\owen{Old copy that might be recycled into final version}
+
+So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
+In the topological setting, renormalization is very well-controlled.
+The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
+
+In other words, by a judicious choice of gauge-fixing, 
+we find that the one-loop Feynman diagrams have no UV divergences.
+Moreover, no higher loop diagrams appear (for combinatorial reasons),
+and the action functional satisfies the quantum master equation.
+See Section~\ref{sec: susytwist revisited} for some further discussion.
+
+Although holomorphic field theories had already appeared in practice,
+my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
+He did the following:
+\begin{itemize}
+\item established key analytic results about holomorphic renormalization, 
+showing that it is highly manageable, with no counterterms to 1-loop; and
+\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
+\end{itemize}
+These apply to all holomorphic theories on $\CC^n$,
+but the techniques typically extend to more general complex manifolds.
+
+\brian{Brian's stuff below}
+
 The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.

### 2024-09-17 draft.tex
i am writing in stereo
pert def has had a full pass

@@
 
-\brian{Comparison}
-
 \section{What is a holomorphic field theory? Why study them?}
@@
 Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
-Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformatino quantization); 
+Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformation quantization); 
 the relevant moduli space being the derived mapping space between complex manifolds.
@@
 \end{itemize}
-\owen{We must check the signs. Am I missing something.}
+\owen{We must check the signs. And am I missing anything?}
 \end{dfn}
@@
 \]
+Thus a holomorphic local Lie algebra with a local cyclic structure models a perturbative holomorphic field theory.
+
+The reader might notice that such Maurer-Cartan equations only ever involve quadratic and linear terms in the field.
+To incorporate cubic and higher terms in the equations of motion,
+one should define holomorphic local $L_\infty$ algebras and local cyclic structures,
+which are a modest and straightforward generalization, if one knows what $L_\infty$ algebra means.
+Such definitions can be found in~\cite{CG2}.
 

### 2024-09-17 draft.tex
quick prune of old stuff

@@
 \end{itemize}
-
-\subsection{An extended aside on perturbative quantization}
-
-\owen{I suggest we mostly move this to a later section and expand it substantially.}
-
-So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
-In the topological setting, renormalization is very well-controlled.
-The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
-
-In other words, by a judicious choice of gauge-fixing, 
-we find that the one-loop Feynman diagrams have no UV divergences.
-Moreover, no higher loop diagrams appear (for combinatorial reasons),
-and the action functional satisfies the quantum master equation.
-See Section~\ref{sec: susytwist revisited} for some further discussion.
-
-Although holomorphic field theories had already appeared in practice,
-my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
-He did the following:
-\begin{itemize}
-\item established key analytic results about holomorphic renormalization, 
-showing that it is highly manageable, with no counterterms to 1-loop; and
-\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
-\end{itemize}
-These apply to all holomorphic theories on $\CC^n$,
-but the techniques typically extend to more general complex manifolds.
 
@@
 For every graph~$\gamma$,
-this family has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
+this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
+That is, there is a smooth map
+\[
+w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
+\]
+where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.
 \end{thm}

### 2024-09-18 draft.tex
edits to gauge thy examples

@@
 We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
-There is a related holomorphic gauge theory that is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure. 
-Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra.
-
-If $n$ is the complex dimension of $X$, 
-the fields consist of pairs $(A,B)$ where $A$ denotes a $\dbar$-connection on a holomorphic principal $G$-bundle $P \to X$ and
+There is a another class of holomorphic gauge theories 
+defined on any complex manifold, with no restriction on dimension 
+and without the need for a Calabi--Yau structure.
+
+Let $X$ be a complex manifold of complex dimension~$n$.
+Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra~$\fg$.
+Fix a holomorphic principal $G$-bundle $P \to X$.
+The fields consist of pairs $(A,B)$ where 
+\[
+A \in \Omega^{0,1}(X, \fg_P)
+\] 
+where $\fg_P$ is the adjoint bundle of $P$ and
 \beqn
@@
 \eeqn
-where $\fg_P$ is the adjoint bundle of $P$. 
+where $\fg_P^*$ is the coadjoint bundle of $P$. 
 The action functional is 
@@
 where $F_A$ is the curvature of the connection $A$.
-From this formula, one might see that the model is a holomorphic analog of topological $BF$ theory. 
-Notice that locally on $X$ and
-writing the connection at $\dbar + [A,-]$, this action can be written as
-\beqn
-S(A,B) = \int_X \langle B \wedge \left(\dbar A + \frac12 [A,A]  \right) \rangle.
-\eeqn
 The equations of motion are
@@
 \]
-In other words, a solution is a $\dbar$-connection on $P\to X$ and a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle.
-
-Holomorphic BF theory is easy to formulate classically, but it can admit peculiar properties at the quantum level.
-For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is a almost topological field theory.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory.
-\owen{Add specific location in text.}}
+A solution to the first equation provides is a $\dbar$-connection 
+\[
+\dbar_A = \dbar_P + [A,-]
+\]
+on the underlying smooth bundle $P\to X$, 
+\owen{Am I doing that right? I believe a choice of holomorphic structure on $P$ automatically determines a Dolbeault operator, or $\dbar$-connection.}
+and a solution to the second equation is a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle associated to~$\dbar_A$.
+This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.
+
+\begin{rmk}
+Notice that this action functional resembles the $\beta\gamma$ system, 
+with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
+A physicist might also recognize this action functional as a holomorphic analog of topological $BF$ theory. 
+\end{rmk}
+
+It is natural to view two connections as equivalent if they are related by a gauge transformation
+and to identify $B$-solutions that are related by a $\dbar_A$-exact term.
+From the point of view of derived geometry,
+we thus see holomorphic BF theory as describing the moduli space
+\[
+T^*[-1] \Bun_G(X),
+\]
+if we run over all principal bundles.
+
+\begin{rmk}
+Holomorphic BF theory exhibits some interesting properties at the quantum level,
+at least perturbatively.
+For example, in \cite{semichiral} it is shown that on $X = \C^2$ 
+the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
+More precisely, to first-order in perturbation theory, 
+the stress tensor has a divergence-free component that is cohomologically trivial. 
+In other words, the quantum theory appears to be ``invariant'' under divergence-free vector fields,
+although not all vector fields (as in the case of a TFT).
+\owen{Add specific location in text.}
+\end{rmk}
 

### 2024-09-18 draft.tex
i am confused about KS theory and i think readers will be too so lets discuss it

@@
 The first appearance of such a theory was motivated by topological string theory and involves complex structures on Calabi--Yau threefolds~\cite{BCOV}.
-Because of its relationship to complex structures, the theory is referred to as \textit{Kodaira--Spencer theory}.
+It is known \textit{Kodaira--Spencer gravity} or the Kodaira-Spencer field theory,
+due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
 It has been pursued mathematically by Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
-In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; here we focus just on the most familiar three-dimensional version.
+In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
+here we focus just on the most familiar three-dimensional version.
 %The fields consist of pairs $(\mu, \eta)$ where
@@
 Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
-The primary field of Kodaira spencer theory is a $(0,1)$ form on $X$ with values in the holomorphic tangent bundle $\T_X$
+The primary field of Kodaira-Spencer theory is 
 \beqn
-\mu \in \Omega^{0,1}(X,\T_X) .
-\eeqn 
-A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
-The action functional is very similar to the Chern--Simons action
+\mu \in \Omega^{0,1}(X,\T_X),
+\eeqn 
+a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
+In contrast to examples above, a constraint is imposed on these sections:
+we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
+\[
+{\rm div}_\Omega(\mu) = 0,
+\]
+i.e., its divergence vanishes.
+In short, the fields are divergence-free vector fields.
+The equation of motion is 
+\beqn
+\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
+\eeqn
+where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket 
+(which, on vector fields, is simply the Lie bracket, and is the natural multilinear extension to polyvector fields).
+The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
+Formulating the action functional to obtain this equation of motion is a little involved.
+
+The action functional is similar to the Chern--Simons action:
 \beqn\label{eqn:KS1}
-S(\mu) = \int_X \left(\frac12 \mu\, \dbar \del^{-1} \mu + \frac13 \mu \wedge \mu \wedge \mu \right) .
-\eeqn
+S(\mu) = \int_X \left( \frac12 \mu\, \dbar \del^{-1} \mu + \frac13 \mu \wedge \mu \wedge \mu \right) .
+\eeqn
+\owen{Honestly I don't understand this formula. We need to unpack it more slowly in terms of explicit complex geometry.}
+To make sense of this, 
+note that $\Omega \in \Omega^{3,0}(X)$ and $\mu^3 \in \Omega^{0,3}(X, \cT^{\otimes 3})$.
 In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
@@
 Setting aside the apparent global issues, 
-we apply formal variational calculus to this action to obtain the equation of motion
-\beqn
-\dbar \mu + \frac12 [\mu,\mu] = 0 ,
-\eeqn
-where $[-,-]$ is the Schouten--Nijenhuis bracket 
-(which reduces to just the Lie bracket when restricted to vector fields).
-The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
+we apply formal variational calculus to this action to obtain the equation of motion.
 

### 2024-09-18 draft.tex
chiral sectors question
tidying up small things

@@
 These equations of motion are variational: 
-they are the Euler-Lagrange equations of an action functional on the space a fields.
-An action functional is written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
+they are the Euler-Lagrange equations of an action functional on the space of fields,
+so that solutions to these PDE are the critical points, in a sense, of some function.
+In practice an action functional is a formal expression, 
+written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
 A few examples will illuminate this sketch.
@@
 \subsubsection{Holomorphic field theories as chiral sectors}
+
+\owen{I'm a little lost about the motivation for this section, 
+given the earlier scalar field section. This C theory looks interest so maybe we can figure out a natural place to put it?}
 

### 2024-09-18 draft.tex
i guess i did not save and push at office last night

--- 2024-09-18 draft.tex
@@
 We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
-There is a another class of holomorphic gauge theories 
-defined on any complex manifold, with no restriction on dimension 
-and without the need for a Calabi--Yau structure.
-
-Let $X$ be a complex manifold of complex dimension~$n$.
-Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra~$\fg$.
-Fix a holomorphic principal $G$-bundle $P \to X$.
-The fields consist of pairs $(A,B)$ where 
-\[
-A \in \Omega^{0,1}(X, \fg_P)
-\] 
-where $\fg_P$ is the adjoint bundle of $P$ and
+There is a related holomorphic gauge theory that is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure. 
+Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra.
+
+If $n$ is the complex dimension of $X$, 
+the fields consist of pairs $(A,B)$ where $A$ denotes a $\dbar$-connection on a holomorphic principal $G$-bundle $P \to X$ and
 \beqn
@@
 \eeqn
-where $\fg_P^*$ is the coadjoint bundle of $P$. 
+where $\fg_P$ is the adjoint bundle of $P$. 
 The action functional is 
@@
 where $F_A$ is the curvature of the connection $A$.
+From this formula, one might see that the model is a holomorphic analog of topological $BF$ theory. 
+Notice that locally on $X$ and
+writing the connection at $\dbar + [A,-]$, this action can be written as
+\beqn
+S(A,B) = \int_X \langle B \wedge \left(\dbar A + \frac12 [A,A]  \right) \rangle.
+\eeqn
 The equations of motion are
@@
 \]
-A solution to the first equation provides is a $\dbar$-connection 
-\[
-\dbar_A = \dbar_P + [A,-]
-\]
-on the underlying smooth bundle $P\to X$, 
-\owen{Am I doing that right? I believe a choice of holomorphic structure on $P$ automatically determines a Dolbeault operator, or $\dbar$-connection.}
-and a solution to the second equation is a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle associated to~$\dbar_A$.
-This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.
-
-\begin{rmk}
-Notice that this action functional resembles the $\beta\gamma$ system, 
-with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
-A physicist might also recognize this action functional as a holomorphic analog of topological $BF$ theory. 
-\end{rmk}
-
-It is natural to view two connections as equivalent if they are related by a gauge transformation
-and to identify $B$-solutions that are related by a $\dbar_A$-exact term.
-From the point of view of derived geometry,
-we thus see holomorphic BF theory as describing the moduli space
-\[
-T^*[-1] \Bun_G(X),
-\]
-if we run over all principal bundles.
-
-\begin{rmk}
-Holomorphic BF theory exhibits some interesting properties at the quantum level,
-at least perturbatively.
-For example, in \cite{semichiral} it is shown that on $X = \C^2$ 
-the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
-More precisely, to first-order in perturbation theory, 
-the stress tensor has a divergence-free component that is cohomologically trivial. 
-In other words, the quantum theory appears to be ``invariant'' under divergence-free vector fields,
-although not all vector fields (as in the case of a TFT).
-\owen{Add specific location in text.}
-\end{rmk}
+In other words, a solution is a $\dbar$-connection on $P\to X$ and a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle.
+
+Holomorphic BF theory is easy to formulate classically, but it can admit peculiar properties at the quantum level.
+For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is a almost topological field theory.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory.
+\owen{Add specific location in text.}}
 
@@
 \]
-where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.
+where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.it 
 \end{thm}

### 2024-09-19 draft.tex
testing

--- 2024-09-18 draft.tex
@@
 
+It is possible to formulate holomorphic versions of higher abelian gauge theories,
+associated to moduli spaces of holomorphic $k$-gerbes with connection.
+\owen{Should we elaborate or just stop with a reference?}
+
 \subsubsection{Holomorphic ``gravity''}
@@
 
-There is the following local characterization of a holomorphic field theory, 
-which allows us to connect directly to supersymmetric field theories. 
-Suppose that our spacetime is $\CC^n = \RR^{2n}$ and assume that the theory we are considering is translation invariant, 
-meaning that there is an action by the $2n$-dimensional Lie algebra spanned by the vector fields $\{\del / \del {z_i}, \del / \del {\zbar_i}\}$ for $i=1,\ldots,n$. 
-Such a theory is {\em holomorphic} if the anti-holomorphic vector fields $\del / \del {\zbar_i}$ act trivially. 
-In the derived world this condition is encoded by the data of chain homotopy trivializations for such vector fields.
-
-Any even dimensional supersymmetric field theory produces a holomorphic field theory through a process called {\em twisting},
-so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.\footnote{Strictly speaking, twisting requires the existence of of more than two chiral supercharges.Thus, two-dimensional theories with $\cN = (n,m)$ supersymmetry, and $n,m \leq 1$, do not admit holomorphic twists.}
+This section offers a bridge from theories of physical interest to holomorphic field theories,
+and hence may be of particular interest to physicists.
+
+\subsubsection{Holomorphicity as a symmetry property}
+
+When physicists describe a classical field theory,
+they typically work with the ``spacetime'' manifold $M = \RR^n$,
+which is genuinely a spacetime when equipped with the Minkowski (pseudo)metric and is a space (with no time) when equipped with the Euclidean metric.\footnote{A theory on Minkowski spacetime is called {\it Lorentzian} and on Euclidean space is called {\it Euclidean},
+although people also use those terms for theories on nonlinear manifolds with Lorentzian pseudometrics or Riemannian metrics, respectively.}
+There is, in either case, a group of isometries (the Poincar\'e group or Euclidean group, respectively),
+and it is useful to work with theories that are equivariant for this group.
+That means the fields are sections of equivariant bundles,
+and the equations of motion must be equivariant as well.
+In fact, this ``covariance'' is typically viewed as a condition required of a good theory.
+
+It is possible to identify holomorphic theories on $\RR^{2n}$ in terms of this covariance.
+In fact, it suffices to focus on how the subgroup of translations acts, as follows.
+
+Equip $\RR^{2n}$ with a complex structure.
+Then the complexified Lie algebra of translations decomposes into holomorphic and anti-holomorphic derivatives:
+\[
+\CC \otimes_{\RR} \RR^{2n} 
+= \CC\left\{\frac{\partial}{\partial z_1}, \ldots, \frac{\partial}{\partial z_n}\right\} 
+\oplus \CC\left\{\frac{\partial}{\partial \zbar_1}, \ldots, \frac{\partial}{\partial \zbar_1}\right\}.
+\]
+We would like to say a translation-equivariant theory is {\em holomorphic} if the anti-holomorphic vector fields $\del / \del {\zbar_i}$ act trivially.
+More carefully, we can say there is Lie algebra map from real translations to vector fields on on the space of solutions to the equations of motion (i.e., to derivations on the algebra of observables),
+and when complexified, every anti-holomorphic translation $\partial/\partial \zbar_j$ acts by zero.
+In the derived world this condition is encoded by the data of chain homotopy trivialization of the action by the anti-holomorphic translations.
+
+Note that for the notion introduced in Section~\ref{sec: pert dfn},
+it is straightforward to provide such a homotopical trivialization: 
+the fields are encoded by a Dolbeault complex on $\CC^n$, 
+translations act by the Lie derivative $L_{\partial/\partial x_j}$,
+and so we trivialize the action $L_{\partial/\partial \zbar_j}$ by using the contraction $\iota_{\partial/\partial \zbar_j}$,
+thanks to Cartan's formula.
+
+We now turn to using this point of view in the setting of supersymmetric theories
+
+\subsubsection{Supersymmetry and twisting}
+
+The goal of this section is to show that any even dimensional supersymmetric field theory produces a holomorphic field theory through a process called {\em twisting}.
+This process provides us with a wealth of examples that are intimately connected to theories of genuine interest in physics.\footnote{Strictly speaking, twisting requires the existence of of more than two chiral supercharges.Thus, two-dimensional theories with $\cN = (n,m)$ supersymmetry, and $n,m \leq 1$, do not admit holomorphic twists.}
 As we will explain later, many interesting phenomena for supersymmetric theories have analogs in holomorphic field theory.

### 2024-09-19 draft.tex
merge

--- 2024-09-18 draft.tex
@@
 
-\DeclareMathOperator{\Schw}{Schw}
-
 \renewcommand{\op}{\operatorname}
@@
 
-\def\brian#1{{\textcolor{blue!75!red}{BW: {#1}}}}
-\def\owen#1{{\textcolor{violet!50!black}{OG: {#1}}}}
+\def\brian#1{{\textcolor{blue!65!red}{BW: {#1}}}}
+\def\owen#1{{\textcolor{violet!65!black}{OG: {#1}}}}
 
@@
 
-\owen{mention some history (e.g., Manin, Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, Kapranov, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
+\owen{mention some history (e.g., Manin!
+Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
 
 \owen{Notation to explain: dg = differential graded, PDE = partial differential equations}
+
+\brian{we need to make sure to cite nekrasov}
 
@@
 just as complex variables is a particularly beautiful wing of analysis.
-In essence, such {\em holomorphic} field theories have variational partial differential equations (i.e., ``equations of motion'') that are holomorphic.
+In essence, such {\em holomorphic} field theories have variational partial differential equations (i.e., ``equations of motion'') that are holomorphic:
+the PDE only involves derivatives in the holomorphic coordinates (i.e., the $\partial/\partial z_j$) and has holomorphic coefficients.
 These theories admit independent motivations from mathematics and physics,
@@
 for most classical holomorphic field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
-and one might hope that the quantization of this moduli space is equally interesting.
+and it is natural to hope that its quantization is equally interesting.
 A well-known example is holomorphic Chern-Simons theory,
@@
 We do not assume the reader is versed in derived geometry and will offer motivations, glosses, and references throughout the survey.)
-
 As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
 (For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
-In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
+In derived geoemtry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
 and this derived moduli space encodes solutions to
-a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it's due to the original notation people used.}
+a theory known as the $\beta\gamma$ system with target $V$.
+(The name is silly: it's due to the original notation people used.)
 Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
-Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformation quantization); 
+Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformatino quantization); 
 the relevant moduli space being the derived mapping space between complex manifolds.
@@
 Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.
-The relevance to this survey is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
+The relevance to the models we study is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
 even when they do not admit twists to TFTs \cite{CosHol}. 
 (The famed A- and B-models of mirror symmetry are TFTs produced by twisting supersymmetric thories.)
-As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, 
-but it does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.
-
-It is natural to wonder how the myriad tools and computations deployed on a supersymmetric theory carry over to this twist 
-and, conversely, whether information can flow back from a holomorphically twisted theory to the original supersymmetric theory, 
+As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.
+It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one,
 much as TFTs have enriched the understanding of supersymmetric theories.
 In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''
-To aid translation between mathematics and physics, 
-it may be helpful to know that the role of derived geometry on the mathematical side is mirrored by the use of the BRST/BV formalism on the physics side;
+It may be helpful to know that the role of derived geometry on the mathematical side is mirrored by the use of the BRST/BV formalism on the physics side;
 they are closely related and serve similar purposes.
 
-As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), 
-holomorphic field theories appear as chiral conformal field theories (CFTs) on Riemann surfaces. 
-The study of CFTs--- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- have had a strong impact in mathematics,
-so it is natural to explore higher-dimensional analogs.
-So far, most mathematical effort in this direction has focused on (essentially) classical aspects of gauge theory,
+As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), holomorphic field theories appear as chiral conformal field theories (CFTs) on two-dimensional manifolds --- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- and have had a strong impact in mathematics.
+It is natural to explore higher-dimensional analogs.
+So far, most mathematical effort in this direction has focused on classical aspects of gauge theory,
 but the quantum aspects are profoundly interesting.
@@
 
-\subsection{The aims of this survey}
-
-Over the last few decades there has been a vigorous dialogue between complex geometry and theoretical physics,
-around topics like mirror symmetry, enumerative algebraic geometry, moduli of Calabi-Yau manifolds, the geometric Langlands program, and integrable systems, among others.
-Covering all these topics would be difficult.
-Our survey's focus will be narrow:
-it is upon higher dimensional versions of the relationship between geometry and algebraic structures like Lie algebras, Poisson algebras, and vertex algebras.
-We will emphasize analogies to TFTs (such as the Gerstenhaber algebras appearing in mirror symmetry) and CFTs (such as the affine Lie algebras relating to moduli of $G$-bundles on Riemann surfaces),
-but our primary interest is on complex manifolds above dimension one.
-Experience suggests that higher dimensions require higher algebra,
-i.e., algebraic methods that involve cochain complexes.
-Thus differential graded (dg) algebras and categories,
-as well as fellow travelers like derived geometry, appear.
-
-A community has formed, involving both mathematicians and physicists, to explore and exploit these relationships,
-and it continues to grow as there is a lot to explore here.
-Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, \cite{Vicedo}, \cite{BeemBZEtAl}, 
-where our own background and interests (and unfortunately, our ignorance) have shaped this list.
-
-The material below focuses on connections with this work,
-and the examples from physics have a perturbative flavor.
-We will not discuss important directions like mirror symmetry, the geometric Langlands program, the BPS/CFT correspondence, Donaldson-Thomas theory, or other areas that are more global or more directly geometric,
-although we expect there are rich connections with the topics we do discuss.
-Not including these topics is primarily because our core theme already swelled to more pages than we expected, 
-because a concise discussion of any of those topics does not yet seem possible with respect to our theme,
-and because of our lack of background in these areas.
-We hope the ideas surveyed here do connect profitably to these topics.
-\owen{Is that an overly negative paragraph?}
-
-\subsection{How to read this paper}
-
-Section~\ref{sec: HFT} is devoted to describing holomorphic field theories, primarily by offering a bounty of examples, including holomorphic analogs of gauge and gravity theories.
-We outline as well how to obtain holomorphic field theories from supersymmetric field theories,
-a rich source of examples to explore.
-
-The next three sections are, in a sense, the core of the survey,
-as they describe increasingly general types of higher algebras and how these capture the observables of holomorphic field theories.
-Section~\ref{sec: algebra} revisits the relationship between quantum mechanics and associative algebras,
-chiral conformal field theory and vertex algebras,
-and holomorphic field theories and higher-dimensional generalizations of vertex algebras.
-Section~\ref{sec: config} offers a useful framework for studying these higher vertex algebras,
-using operads,
-and it develops powerful analogies to the little $n$-disks operad $E_n$ that plays an important role in contemporary topology.
-Section~\ref{sec: fact alg} introduces factorization algebras,
-providing a local-to-global principle to describe the observables on complex manifolds beyond affine spaces.
-In particular, by pushing forward factorization algebras,
-one can relate field theories of different dimension,
-i.e., a version of the physicist's ``compactification.''
-
-A reader could read this core portion independently of the rest of the paper,
-as it focuses on algebra and geometry and requires no substantial knowledge of field theory {\it per se}.
-
-Section~\ref{sec: renorm} describes recent work that allows one to produce examples:
-there is now a convenient framework for renormalization of holomorphic field theories on $\CC^n$,
-and so the field theories of Section~\ref{sec: HFT} generate higher algebras of the form described in Sections~\ref{sec: algebra},~\ref{sec: config}, and~\ref{sec: fact alg}.
-The reader could skip to this section directly from Section~\ref{sec: HFT}.
-
-We conclude the paper by describing the kind of fascinating mathematical questions
-that arise by taking physical conjectures (e.g., dualities of supersymmetric theories) and twisting them into conjectures about holomorphic field theories. 
-Section~\ref{sec: seiberg} explores the holomorphic cousin of Seiberg duality,
-which suggests a remarkable correspondence between a gauge theory with group $SL(N)$ and a gauge theory with group $SL(M)$, where $M \neq N$.
-It is a kind of enhancement of Weyl's invariant theory and has close connections with topics like homological projective duality.
-
-\subsection{Acknowledgements}
-
-\owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum}
-
-\section{Holomorphic field theories}
-\label{sec: HFT}
-
-\owen{I rearranged this section somewhat.
-Our discussion of examples did not involve any BRST/BV stuff, so I put it right after the impressionistic opening.
-The "definitions" section seemed to be purely perturbative and to use notions from derived geometry, so I put it next.
-It should be fleshed out a little (e.g., a mention of the "fundamental theorem of deformaiton theory" and maybe show how to write one of the examples in that language).}
-
-We begin by sketching what a classical field theory is, somewhat impressionistically, and then offer some concrete examples.
-
-In physics, a classical field theory is usually described in terms of a few pieces of data:
+The overarching goal of this paper is to introduce the reader to this emerging domain where physics and mathematics meet,
+with an emphasis upon how key objects from physics, notably supersymmetric theories and conformal field theories, 
+interface with complex geometry in general and with mathematical methods of rather recent vintage,
+notably derived geometry and higher algebras.
+A community is forming, involving both mathematicians and physicists,
+to bring into sharp mathematical form some of the deep insights into gauge theory offered by physics.
+There is a lot to explore here.
+
+\subsection{Preliminary notions}
+
+\brian{complex geometry, dolbeault, dg stuff.}
+
+A physical field theory is usually described in terms of a space of fields that forms some possibly nonlinear space, like a mapping space $\Map(M,X)$ or the space of connections ${\rm Conn}_G(M)$ on a manifold.
+There is a manifold, called spacetime in physics, where the fields are some kind of functions out of it;
+in the examples just mentioned, it is denoted $M$.
+In perturbative field theory, which describes the formal neighborhood of the theory at a point in such spaces, 
+a field $\Phi$ is typically described by a smooth section of a vector bundle on spacetime.
+The equations of motion that dictate the dynamics of the particular model are encoded by a series of partial differential equations of the form 
+\[
+\sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
+\]
+where $D_k$ is a $k$-ary polydifferential operator.
+As an example, the scalar $\phi^4$-theory on a Riemannian $M$ is described by the equation
+\[
+\Delta \phi + \frac{1}{3!} \phi^3 = 0 
+\]
+where $\Phi = \phi$ is simply a smooth function on $M$.
+These equations of motion are natural to the Riemannian geometry of the manifold $M$, 
+and they can be derived from the Euler--Lagrange equations of the  action functional $\int_M \phi \Delta \phi \, \op{dvol}$.
+
+As another example, consider perturbative Chern--Simons theory whose fields are a principal $G$-bundle $P$ on a smooth three-manifold $M$ equipped with a connection.
+The equations of motion is the condition that the connection is flat 
+\beqn
+F_\nabla = 0 .
+\eeqn
+Perturbatively, near the trivial flat connection, the fields are simply $\lie{g} = \op{Lie}(G)$-valued one-forms $A \in \Omega^1(M, \lie{g})$.
+The condition that perturbed connection $\d + A$ is flat is the Maurer--Cartan equation
+\beqn
+\d A + \frac12 [A,A] = 0.
+\eeqn
+These equations of motion are topological in the sense that they only depend on the smooth manifold~$M$.
+When $\lie{g}$ is equipped with a non-degenerate, invariant, bilinear form $\kappa$ (for example, if $G$ is semi-simple there is a standard choice) then these equations of motion can be derived from the famous Chern--Simons action functional $\int_M CS(A)$ where
+\beqn\label{eqn:CS}
+CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]) .
+\eeqn
+
+In a {\em holomorphic theory} one starts with a complex manifold $X$ as the spacetime.
+%This means, in part, that the complexified tangent bundle of $X$ decomposes as a sum of vector bundles $\T_X \oplus \Bar{\T}_X$ where $\T_X$ (respectively $\Bar{T}_X$) is the holomorphic (respectively anti-holomorphic) tangent bundle.
+%In local coordinates sections of $\T_X$ have the form $f^i \del / \del z_i$ whereas sections of $\Bar{\T}_X$ have the form $f^i \del / \del \zbar_i$. 
+Globally, holomorphic theories are described like in the usual case by mapping spaces or spaces of connections.
+The key feature in a holomorphic theory is that the equations of motion dictate that fields be holomorphic in an appropriate sense.
+Perturbatively, where fields are sections of some (possibly graded) holomorphic vector bundle $V$, we can make this precise. 
+Prescribing a holomorphic structure on a vector bundle $V$ is equivalent to the data of a $\dbar$-operator
+\beqn
+\dbar \colon \Omega^{0,q}(X, V) \to \Omega^{0,q+1}(X,V) 
+\eeqn
+where $\Omega^{0,q}(X,V)$ is the space of smooth sections of the vector bundle $\wedge^q\Bar{T}_X^* \otimes V$. 
+Holomorphicity of $V$ boils down to the requirement that $\dbar \circ \dbar = 0$.
+The Dolbeault complex of $V$ is
+\beqn
+\left(\Omega^{0,\bu}(X, V), \dbar \right) = \left(\oplus_{q \geq 0} \Omega^{0,q}(X, V)[-q], \dbar \right)
+\eeqn
+where (in the case that $V$ sits in degree zero) the space $\Omega^{0,q}(X,V)$ sits in degree $+q$.
+A standard result in complex geometry is that the Dolbeault complex is a resolution for the sheaf of holomorphic sections of the holomorphic vector bundle $V$.
+%In the case that $V$ is the trivial bundle $\ul{\CC}$ the Dolbeault complex $\Omega^{0,\bu}(X)$ is a resolution for the sheaf of holomorphic functions on $X$.
+
+The fields of a holomorphic theory are given by elements of the Dolbeault complex $\Omega^{0,q}(X,V)$ for some $q$.
+The equations of motion in a holomorphic theory take the form
+\beqn
+\dbar \Phi + \sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
+\eeqn
+where $D_k$ are $k$-ary {\em holomorphic} polydifferential operators.
+This means that in local coordinates $D_k$ only depend on the holomorphic coordinates $\{z_i\}$ and involve only holomorphic derivatives $\del / \del z_i$.
+
+For a simple example, consider the following holomorphic analog of Chern--Simons theory.
+The fields are principal $G$-bundles on a three-dimensional \textit{complex} manifold $X$, and the equations of motion give the condition that the principal $G$-bundle is holomorphic.
+Perturbatively, near the trivial $G$-bundle, the fields of this holomorphic theory are $\lie{g}$-valued $(0,1)$-forms $A \in \Omega^{0,1}(X, \lie{g})$.
+The condition that $\d + A$ prescribes a holomorphic structure is again a Maurer--Cartan equation
+\beqn
+\dbar A + \frac12 [A,A] = 0 .
+\eeqn
+Like ordinary Chern--Simons theory, in order for this equation to arise from a principal of least action one needs to fix a non-degenerate, invariant, bilinear form $\kappa$ on $\lie{g}$.
+Additionally, one needs to fix a holomorphic volume form $\Omega$ on $X$; in other words, $X$ is a Calabi--Yau manifold.
+Then, the equations of motion is precisely the Euler--Lagrange equation for the action
+\beqn
+S_{hCS} (A) = \int_X \Omega \wedge CS(A) 
+\eeqn
+where $CS(A)$ is exactly as in \eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$ only the $\dbar$ operator contributes to the kinetic term and so the action can be written as $\int_X \Omega \wedge \left(\frac12 \kappa( A ,\dbar A ) + \frac16 \kappa(A , [A,A]) \right)$.}
+
+\subsection{Precise definitions}
+
+We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.
+
+\begin{dfn}
+A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is
 \begin{itemize}
-\item a manifold $M$ that plays the role of ``spacetime,''
-\item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
-\item a system of PDE for the fields, known as the equations of motion.
+\item a graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$, and
+\item a holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$.
 \end{itemize}
-These equations of motion are variational: 
-they are the Euler-Lagrange equations of an action functional on the space a fields.
-An action functional is written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
-A few examples will illuminate this sketch.
-
-\begin{eg}[Massless scalar field theory]
-\label{eg: massless scalar}
-Let $M$ be a smooth manifold and equip it with a Riemannian metric~$g$.
-Let $\Delta_g$ denote the associated Laplace-Beltrami operator, 
-and let $\d{\rm vol}_g$ denote the associated volume form.
-Let the space of fields be the smooth functions $C^\infty(M)$.
-A smooth function $\phi$ is called, in physics, a {\em scalar} field.
-The action functional
-\[
-S(\phi) = \int_M \phi \Delta_g \phi \, \d{\rm vol}_g
-\]
-corresponds to the equation of motion $\Delta_g \phi = 0$. 
-Thus this scalar field theory has the moduli space of {\em harmonic functions} as its space of solutions.
-\end{eg}
-
-The preceding example exhibits how a moduli space of central interest in differential geometry --- the harmonic functions --- appears naturally as a basic example in physics (the ``free massless scalar field'').
-More complicated moduli spaces show up too.
-
-\begin{eg}[$\phi^4$ theory]
-As a small variant of the example just given,
-consider the action functional
-\[
-S(\phi) = \int_M \phi \Delta_g \phi + \frac{1}{4!} \phi^4\, \d{\rm vol}_g.
-\]
-Its equation of motion is the nonlinear PDE 
-\[
-\Delta_g \phi + \frac{1}{3!} \phi^3 = 0.
-\] 
-Thus this scalar field theory has a more complicated, nonlinear moduli space of solutions.
-\end{eg}
-
-We now describe an example of a theory whose space of solutions is a moduli space of interest in geometric topology.
-
-\begin{eg}[Chern-Simons theory]
-Pick a compact Lie group $G$ and equip it with an invariant metric,
-which induces a $G$-invariant inner product $\kappa$ on its Lie algebra~$\fg$.
-(The standard choice is the Killing form.)
-Take an oriented smooth 3-manifold $M$, 
-and consider the space of connections on the trivial principal $G$-bundle on $M$.
-This space of fields is isomorphic to $\Omega^1(M, \fg)$, the $\fg$-valued one-forms, 
-by viewing $\d + A$ as a connection where $A \in \Omega^1(M, \fg)$.
-The equation of motion is the zero-curvature equation
-\[
-F_A = 0,
-\]
-which can be expressed equivalently as the Maurer-Cartan equation
-\[
-\d A + \frac{1}{2} [A,A] = 0.
-\]
-These equations arise as the Euler-Lagrange equation for the action functional
-\beqn
-\label{eqn:CS}
-CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]),
-\eeqn
-the integral of a Chern-Simons form.
-Hence this theory is known as {\em Chern-Simons theory}.\footnote{Note that $M$ needs to be an oriented 3-manifold for this action functional to make sense.
-The equation of motion exists for a principal bundle on any manifold of any dimension,
-but it is only variational for oriented 3-manifolds.}
-These equations do not depend on a metric on $M$ or any other geometric structure,
-and hence define a ``topological'' field theory in the sense that they are independent of geometry.
-This theory is interesting because the moduli space of solutions consists of the flat $G$-bundles on $M$,
-a topic of deep interest in geometry and topology.
-For physicists, it is interesting because it does not involve geometry, 
-by contrast to earlier examples of field theories,
-and yet exhibits rich phenomena (notably applications to the quantum Hall effect and 3-dimensional gravity).
-\end{eg}
-
-\begin{rmk}
-In the Chern-Simons example, there is an important aspect we did not yet acknowledge:
-we need to identify different solutions related by gauge transformations.
-In other words, the correct moduli space is the quotient stack
-\[
-\left[ \{ A \,:\, F_A = 0\}/\Map(M,G) \right].
-\]
-The usual mode of description of a field theory, by specifying fields and an action functional (or equations of motion), 
-must be supplemented by specifying whether to quotient by some group of symmetries of the space of solutions.
-More generally, a field theory ought to present some kind of derived moduli stack.
-\end{rmk}
-
-We are now in a good position to offer an example of a {\em holomorphic field theory}:
-the holomorphic analog of Chern-Simons theory.
-
-%In a {\em holomorphic theory} one starts with a complex manifold $X$ as the spacetime.
-%%This means, in part, that the complexified tangent bundle of $X$ decomposes as a sum of vector bundles $\T_X \oplus \Bar{\T}_X$ where $\T_X$ (respectively $\Bar{T}_X$) is the holomorphic (respectively anti-holomorphic) tangent bundle.
-%%In local coordinates sections of $\T_X$ have the form $f^i \del / \del z_i$ whereas sections of $\Bar{\T}_X$ have the form $f^i \del / \del \zbar_i$. 
-%Globally, holomorphic theories are described like in the usual case by mapping spaces or spaces of connections.
-%The key feature in a holomorphic theory is that the equations of motion dictate that fields be holomorphic in an appropriate sense.
-%Perturbatively, where fields are sections of some (possibly graded) holomorphic vector bundle $V$, we can make this precise. 
-%Prescribing a holomorphic structure on a vector bundle $V$ is equivalent to the data of a $\dbar$-operator
-%\beqn
-%\dbar \colon \Omega^{0,q}(X, V) \to \Omega^{0,q+1}(X,V) 
-%\eeqn
-%where $\Omega^{0,q}(X,V)$ is the space of smooth sections of the vector bundle $\wedge^q\Bar{T}_X^* \otimes V$. 
-%Holomorphicity of $V$ boils down to the requirement that $\dbar \circ \dbar = 0$.
-%The Dolbeault complex of $V$ is
-%\beqn
-%\left(\Omega^{0,\bu}(X, V), \dbar \right) = \left(\oplus_{q \geq 0} \Omega^{0,q}(X, V)[-q], \dbar \right)
-%\eeqn
-%where (in the case that $V$ sits in degree zero) the space $\Omega^{0,q}(X,V)$ sits in degree $+q$.
-%A standard result in complex geometry is that the Dolbeault complex is a resolution for the sheaf of holomorphic sections of the holomorphic vector bundle $V$.
-%%In the case that $V$ is the trivial bundle $\ul{\CC}$ the Dolbeault complex $\Omega^{0,\bu}(X)$ is a resolution for the sheaf of holomorphic functions on $X$.
-%
-%The fields of a holomorphic theory are given by elements of the Dolbeault complex $\Omega^{0,q}(X,V)$ for some $q$.
-%The equations of motion in a holomorphic theory take the form
-%\beqn
-%\dbar \Phi + \sum_{k \geq 1} D_k(\Phi,\ldots,\Phi) = 0 ,
-%\eeqn
-%where $D_k$ are $k$-ary {\em holomorphic} polydifferential operators.
-%This means that in local coordinates $D_k$ only depend on the holomorphic coordinates $\{z_i\}$ and involve only holomorphic derivatives $\del / \del z_i$.
-
-\begin{eg}[Holomorphic Chern-Simons theory]
-\label{eg: holCS}
-\owen{This feels rather convoluted. Can we make it simpler?}
-Pick a {\em complex} Lie group $G$, 
-and equip its Lie algebra $\fg$ with a complex-linear, $G$-invariant nondegenerate symmetric bilinear form~$\kappa$.
-Let $M$ be a three-dimensional \textit{complex} manifold
-equipped with a holomorphic volume form $\Omega \in \Omega^{3,0}(M)$; 
-in other words, $M$ is a Calabi--Yau manifold.
-(This condition is analogous to being an oriented 3-manifold.)
-Given a smooth principal $G$-bundle $P \to M$,
-there is a moduli space of holomorphic structures on~$P$.
-Suppose there exists at least one holomorphic structure $\cP \to M$,
-which has an associated Dolbeault operator (or $\dbar$-connection) $\dbar_{\cP}$.
-Any other holomorphic bundle structure determines a Dolbeault operator,
-but our reference point $\dbar_{\cP}$ provides an isomorphism
-\[
-{\rm Conn}^\dbar_G(P) \cong \Omega^{0,1}(M, {\rm ad}(P)),
-\]
-i.e., we express another $\dbar$-connection as $\dbar_{\cP} + A$ where $A$ is a $(0,1)$-form valued in the adjoint bundle.
-The equation of motion is again a Maurer--Cartan equation
-\beqn
-\dbar_{\cP} A + \frac12 [A,A] = 0 ,
-\eeqn
-or equivalently the $(0,2)$-term of the curvature vanishes.
-This PDE is the Euler--Lagrange equation for the action
-\beqn
-S_{hCS} (A) = \int_X \Omega \wedge CS(A) 
-\eeqn
-where $CS(A)$ is exactly as in~\eqref{eqn:CS}.\footnote{Notice that due to the presence of the holomorphic volume form $\Omega$, only the $\dbar A$ component of $\d A$ contributes to the integrand of the action functional, because $\Omega \wedge \partial A$ vanishes.}
-As in the case of Chern-Simons theory, one must quotient by the appropriate group of gauge transformations to obtain the correct moduli space, 
-which is here the moduli stack of holomorphic principal $G$-bundles whose underlying smooth structure is given by $P \to M$.
-\end{eg}
-
-For a systematic introduction to classical field theory, 
-in a style amenable to a complex geometer,
-we suggest \cite{FreedDeligne}.
-There are many other sources, such as \cite{}, because classical field theory is an old and deep subject.
-Recently there is an effort to revisit field theory with insights from derived geometry.
-See \cite{AlfonsoYoung?} for motivation and overview, 
-but for a detailed development, see \cite{Steffens}.
-In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
-(i.e., studying formal deformations of a fixed solution to the equations of motion),
-which we will use to produce examples of higher algebras.
+This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
+\end{dfn}
+
+Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
+If $V$ is a holomorphic dg Lie algebra, 
+then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
+The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
+Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on $X$.
+
+Formal moduli spaces arise from the space of Maurer--Cartan elements of a dg Lie algebra.
+In our case, this dg Lie algebra will always be of the form $\Omega^{0,\bu}(X, V)$.
+For example, the Maurer--Cartan elements of the dg Lie algebra $\Omega^{0,\bu}(X, \fg)$ recovers formal deformations of the trivial holomorphic $G$-bundle.  
+This arises from the holomorphic Lie algebra on $X$ whose underlying vector bundle is trivial with fiber $\fg$.
+
+As another example, consider the holomorphic tangent bundle $V = \T_X$. 
+The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
+A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
+\[
+\dbar \mu + \frac12 [\mu,\mu] = 0 .
+\]
+This recovers the classical picture describing formal deformations of complex structures on~$X$.
+
+%this section aimed at mathematicians
+%emphasize connection with (derived) complex geometry
 
 \subsection{Examples}
-
-In this section we describe several examples of holomorphic field theories,
-in the style we used for holomorphic Chern-Simons theory.
-Our aim here is to give a sense of how take physical ideas and find holomorphic analogs.
 
@@
 of which the Standard Model offers a nice example.
-The basic types are\footnote{For the experts, we remark that we focus above on the field content that motivates or characterizes, and mostly ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
+The basic types are\footnote{For the experts, we remark that we focus above on the core field content, and ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
 \begin{itemize}
@@
 Such theories are often used to describe matter, such as electron fields.
-\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as nonlinear generalizations of scalar field theories.)
+\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
 \item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
@@
 The Standard Model involves the first three types,
-and the different fields interact in intricate ways.\footnote{For instance, the scalar and fermionic fields are sections of associated bundles to the principal bundle appearing in the gauge theory.}
+and the different fields interact in intricate ways.\footnote{For instance, the scalar and fermionic fields are sections for associated bundles of the principal bundle appearing in the gauge theory.}
 
 There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.\footnote{See \cite{Donaldson Thomas} for a pioneering and illuminating discussion of how to find such analogs.}
+and we now spell out some simple examples.
 To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
@@
 in terms of PDE and action functionals but also as moduli spaces.
-We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
-and see \cite{AlfonsoYoung} and \cite{Steffens} for recent work on this topic.
+We do not offer a thorough justification of the dictionary, for which see \owen{cite who?}
 
@@
 see Section~\ref{sec: seiberg}.
-
-A motivation for us to explore holomorphic field theories is that physical insights and conjectures, such as Seiberg duality, translate into surprising predictions in the holomorphic setting,
-which is typically more accessible for mathematics.
+One motivation for us to explore holomorphic field theories is that one can translate physical insights and conjectures (such as Seiberg duality) into surprising predictions in the holomorphic setting,
+which is typically much cleaner and more accessible.
 (One might also hope that progress in the holomorphic setting then feeds back useful insights to physics.)
@@
 
-The standard example of a scalar field theory is the free massless exists on any Riemannian manifold,
-which we met in Example~\ref{eg: massless scalar}.
-Here the field $\phi$ a smooth function on a manifold $M$,
-its action functional is $\int_M \phi \Delta \phi$, where $\Delta$ is the Laplace-Beltrami operator, 
-and its equation of motion is $\Delta \phi = 0$.
-The moduli space of solutions is then the space of harmonic functions on~$M$
-
-When $M$ is two-dimensional and oriented,
-we can view $M$ as equipped with a complex structure.
-Every complex-valued harmonic function then decomposes as a sum of a holomorphic and anti-holomorphic function. 
-That is, if we complexify the scalar field $\phi$, 
-we can view it as a pair of fields $\gamma$ and $\Bar{\gamma}$,
-where the equation of motion of $\gamma$ is $\dbar \gamma = 0$ and the equation of motion is $\partial \Bar{\gamma} = 0$.
-These components are sometimes called the chiral and anti-chiral ``sectors.''
-
-Notice that we have shifted from a second-order differential operator $\Delta$ to first-order differential operators $\dbar$ and~$\partial$.
-Reworking a theory to express its equations of motion using first-order operators is sometimes called the first-order formalism.
-
-The holomorphic component can be seen as arising from the following action functional,
-\beqn
-\int \beta \wedge \dbar \gamma
-\eeqn
-where $\beta$ is a $(1,0)$-form on $M$ and should be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$,
-\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}
-which we now think about as having its own degrees of freedom. 
-Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
-so that $\beta$ should be a holomorphic $1$-form.
-
-This piece of the free boson is the simplest holomorphic field theory; it is often called the $\beta\gamma$-\textit{system}.
-It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.\owen{More precise location?}
-
-It should seem reasonable to view two solutions $\beta_1$ and $\beta_2$ as equivalent if they differ by a $\dbar$-exact term.
-If one imposes this equivalence relation (a kind of ``gauge symmetry''),
-then one is on the path towards setting up the theory in the Batalin-Vilkovisky formalism.
-
-Derived geometry is the mathematical version of BV formalism.
-From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
-\[
-T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\cT^{*{1,0}}),
-\]
-a rather natural space to study in complex geometry.
-
-\begin{rmk}
-We motivated the $\beta\gamma$ system as encoding a piece of the free boson.
-There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$ system as encoding the antichiral sector of the free boson.
-To recover the full boson, one must couple the chiral and anti-chiral sectors.
-See \cite{Kapustin,GGW} \owen{Where?} for more details. 
-\end{rmk}
-
-This example admits a natural generalization to an arbitrary complex manifold.
-The input data is a complex manifold $X$ of arbitrary complex dimension $n$, 
-together with a holomorphic vector bundle $V$ on~$X$.
-(Above we took this bundle to be trivial.)
-Each field of the theory consists of a pair $(\gamma,\beta)$ where 
-\[
-\gamma \in \Gamma(X,V) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(X,V^*) .
-\]
-The action functional is 
-\[
-\int_X \beta \wedge \dbar \gamma
-\]
-and the equations of motion are
-\[
-\dbar \gamma = 0 = \dbar \beta.
-\]
-Solutions consist of a holomorphic function $\gamma$ and a holomorphic $(n,n-1)$-form.
-We again suggest to identify solutions to the second equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
-
-\subsubsection{Holomorphic fermions}
-
-It is straightforward to modify the example above to allow super-holomorphic vector bundles,
-i.e., holomorphic $\ZZ/2$-graded vector bundles.
-
-For example, given a holomorphic vector bundle $V$ on a complex $n$-fold~$X$,
-let $\Pi V$ denote the parity-reversed vector bundle,
-i.e., we now give $V$ an odd grading.
-There is a $bc$ system that is the fermionic analog of the $\beta\gamma$ system.
-The fields of the theory consist of a pair $(c,b)$ where 
-\[
-c \in \Gamma(X,\Pi V) \quad\text{and}\quad b \in \Omega^{n,n-1}(X,\Pi V^*) .
-\]
-Thus, $b$ and $c$ are fermionic fields.
-The action functional is 
-\[
-\int_X b \wedge \dbar c,
-\]
-and the equations of motion are
-\[
-\dbar c = 0 = \dbar c.
-\]
-We again suggest to identify solutions to the equation $\dbar c = 0$ that differ by a $\dbar$-exact form.
-
-There is a special class of fermionic theories that is quite interesting.
-Let $X$ be a complex $n$-fold where
-\begin{itemize}
-\item $n = 2k+1$ is odd and
-\item there is a line bundle $L \to X$ such that $L^{\otimes 2} \cong K_X$,
-i.e., $L$ is a square root of the canonical bundle.
-\end{itemize}
-A field is a section
-\[
-\psi \in \Omega^{0,k}(X,\Pi L),
-\]
-the action functional is
-\[ 
-\int_X \psi \wedge \dbar \psi,
-\]
-and the equation of motion is
-\[
-\dbar \psi = 0.
-\]
-We suggest to identify solutions that differ by $\dbar$-exact terms.
-
-From the point of view of derived geometry, the cochain complex
-\[
-\Omega^{0,\bullet}(X, \Pi L)[k]
-\]
-presents a derived stack that should be viewed as the moduli of solutions for this theory.
-
-\owen{What do you think of this example?}
-
-\subsubsection{Holomorphic $\sigma$-models}
-
-A $\sigma$-model is a field theory whose space of fields contains a mapping space $\Map(M,N)$.
-When $N = \RR$, this mapping space simply becomes functions and so the $\sigma$-model reduces to a scalar field theory.
-
-There is a natural generalization of the $\beta\gamma$ system to a $\sigma$ model.
-Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
-The fields are a pair $(\gamma, \beta)$ where
-\[
-\gamma \in \Map(M,N) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(M,\gamma^* T^*_N) .
-\]
-Note that $\dbar \gamma$ lives in $\Omega^{0,1}(M, \gamma^* T_N)$, 
-a section of the pullback of the tangent bundle of the target.
-The action functional is 
-\[
-\int_X \beta \wedge \dbar \gamma,
-\]
-where we use the canonical evaluation pairing between the pullback of the tangent and cotangent bundles of the target.
-The equations of motion are
-\[
-\dbar \gamma = 0 = \dbar \beta,
-\]
-so that solutions consist of a holomorphic map $\gamma: M \to N$ and a holomorphic section $\beta$ of the pullback tangent bundle.
-As usual, we suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
-
-From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
-\[
-T^*[-1] \Map_\dbar(M,N) 
-\]
-a rather natural space to study in complex geometry.
+A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
+Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
+When $\Sigma$ is a surface this theory can be written in such a way that makes its complex structure apparent.
+First, we complexify the field $\phi$ which we can view as a pair of fields $\gamma, \Bar{\gamma}$.
+When we do this, we can split it up into its chiral and anti-chiral `sectors'.
+By chiral (anti-chiral) we mean part involving $\gamma$ ($\Bar{\gamma}$).
+The holomorphic part is described by the following action
+\beqn
+\int_\Sigma \beta \wedge \dbar \gamma
+\eeqn
+where $\beta$ is a $(1,0)$ form on $\Sigma$ and should be thought of as a Lagrange multiplier for the field $\del \Bar{\gamma}$ which we now think about as having its own degrees of freedom (this is called the first-order formalism).
+There is also a coupling between the chiral and anti-chiral sectors, 
+for more details we refer to \cite{Kapustin,GGW}. 
+This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta\gamma$-\textit{system}.
+It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.
+
+There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta\gamma$ system'.
+The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
+Above we took this bundle to be trivial.
+The fields of the theory consist of pairs 
+\begin{align*}
+\gamma & \in \Gamma(X,V)\\
+\beta & \in \Omega^{n,n-1}(X,V^*) .
+\end{align*}
+The action functional is identical $\int_X \beta \wedge \dbar \gamma$.
+
+Notice that when $n = \dim_\C X > 1$ that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
+\beqn
+\beta \mapsto \beta + \dbar \eta , \quad \eta \in \Omega^{n,n-2}(X,V^*)
+\eeqn
+For this model to be well-posed at the quantum level we must include the ghosts $\eta$.
+Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
+This is one of the key differences between the ordinary $\beta\gamma$ system and its higher dimensional version.
+Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.
 
@@
 
-\subsubsection{Holomorphic field theories as chiral sectors}
+\subsubsection{Holomorphic scalar field theories}
 
@@
 
-\subsection{Perturbative field theory as derived deformation theory}
-\label{sec: pert dfn}
-
-We now turn to giving a mathematical definition that incorporates insights from derived geometry.
-We will stick with studying perturbative field theory: 
-we fix a solution $\phi_0$ to the equations of motion and study formal deformations of it.
-In other words, we want to study the formal derived geometry of the moduli of solutions to the equations of motion.
-
-Here we can exploit the heuristic principle that every derived deformation problem (in characteristic zero) is described by a dg Lie algebra.\footnote{Or, sometimes more conveniently, by an $L_\infty$ algebra.}
-That is, if $\cM$ is a derived stack and $p: \Spec(\CC) \to \cM$ is a point, 
-then the formal neighborhood $\cM^\wedge_p$ of $p$ is modeled by the Maurer-Cartan locus of some dg Lie algebra $\fg_p$.\footnote{More technically, the shifted tangent complex $\TT_p \cM[-1]$ comes equipped with a homotopy-coherent Lie algebra structure,
-and this determines a functor from small (i.e., artinian local) nonnegatively-graded dg algebras to the $\infty$-category of spaces.}
-This idea goes back to Deligne, Drinfeld, and Schlessinger-Stasheff, and perhaps farther, 
-but Hinich, Lurie, and Pridham have given a precise articulation of the {\em fundamental theorem of derived deformation theory}:
-there is an equivalence of $\infty$-categories between formal moduli spaces and dg Lie algebras.
-
-Applying this perspective to classical field theory was prominently and successfully advocated by Kontsevich, 
-and it is an essential component of the formalism developed by Costello.
-The idea is that if want to study the perturbation theory around some solution~$\phi_0$ on the whole spacetime manifold~$X$,
-then on each open set $U$ in~$X$,
-there is a formal moduli space describing deformations of the restriction~$\phi_0|_U$.
-In other words, there is a sheaf on $M$ with values in formal moduli spaces,
-and this sheaf describes the perturbative field theory.
-
-By the fundamental theorem, we can describe this sheaf of formal moduli spaces by supplying a sheaf of dg Lie algebras, which can often be quite convenient.
-We follow this approach here.
-
-\begin{dfn} 
-A {\em holomorphic local Lie algebra} on a complex manifold $X$ is
-\begin{itemize}
-\item a graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$, and
-\item a holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$.
-\end{itemize}
-This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a sheaf of dg Lie algebras.
-\end{dfn}
-
-Here is a quick example, as motivation.
-Let $X$ be a Calabi-Yau 3-fold equipped with a holomorphic principal $G$-bundle $P \to X$.
-There is an associated adjoint bundle $\fg_P \to X$, and hence a coherent sheaf $\cG_P$ of holomorphic sections of the adjoint bundle.
-Note that $\cG_P$ is a holomorphic local Lie algebra, using the fiberwise Lie bracket,
-and it describes the formal neighborhood of $P$ inside the space $\Bun_G(X)$.
-In other words, it encodes the perturbative part of holomorphic Chern-Simons theory of Example~\ref{eg: holCS}.
-
-We now rephrase this data in the style of complex differential geometry and then further into more physical terminology.
-
-Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
-If $V$ is a holomorphic local Lie algebra, 
-then $\Omega^{0,\bu}(X, V)$ is a dg Lie algebra. 
-The differential is $\dbar + Q^{hol}$, 
-and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms. 
-Notice that this dg Lie algebra has the appealing feature that it is the $C^\infty$-sections of a smooth vector bundle on~$X$.
-
-In the case of our running example, we obtain the dg Lie algebra
-\[
-\Omega^{0,\bu}(X,\fg_P)
-\]
-from the adjoint bundle of the holomorphic principal $G$-bundle on our Calabi-Yau 3-fold~$X$.
-A Maurer-Cartan element in this dg Lie algebra is a $(0,1)$-form $A$ such that
-\[
-\dbar_P A + \frac{1}{2}[A,A] = 0,
-\]
-meaning that $\dbar_P + [A,-]$ defines another $\dbar$-connection, and hence holomorphic structure, on the smooth bundle $P \to~X$.
-
-The take-away message is that the Dolbeault complex of a holomorphic Lie algebra leads to a PDE, by taking the Maurer-Cartan equation,
-and this PDE should be seen as the equation of motion.
-
-In this example the PDE arises from the variations of the action functional
-\[
-\int_X \Omega \wedge \left( \frac{1}{2}\langle A, \dbar A\rangle + \frac{1}{3!}\langle A, [A,A]\rangle \right).
-\]
-The PDE does not involve the choice of a holomorphic volume form $\Omega$ or a pairing on the Lie algebra $\fg$, 
-but the action functional did.
-
-In general, for a holomorphic local Lie algebra to arise from a field theory,
-it is necessary to provide more data so as to be able to write down an action functional.
-
-\begin{dfn}
-A {\em local cyclic structure} on a holomorphic local Lie algebra is a degree $-3$ map
-\[
-\langle -,-\rangle: V \otimes V \to K_X
-\]
-of holomorphic vector bundles\footnote{Here $\otimes$ denotes the Whitney tensor product of vector bundles on $X$.} such that 
-\begin{itemize}
-\item if $f, g$ are holomorphic sections of $V$, then 
-\[
-\langle Q^{hol}f, g \rangle + (-1)^{|f|} \langle f, Q^{hol} g \rangle = 0
-\]
-so that the pairing is a cochain map, and
-\item if $f, g, h$ are holomorphic sections of $V$, then 
-\[
-\langle f, [g,h] \rangle = (-1)^{|f|} \langle h,  \rangle
-\]
-so that the pairing is invariant for the bracket.
-\end{itemize}
-\owen{We must check the signs. And am I missing anything?}
-\end{dfn}
-
-Given a local cyclic structure, there is an action functional
-\[
-\int_X \frac{1}{2} \langle f, \dbar f + Q^{hol} f \rangle + \frac{1}{3!} \langle f, [f,f] \rangle 
-\]
-whose equation of motion is the Maurer-Cartan equation
-\[
-\dbar f + Q^{hol}f + \frac{1}{2} [f,f] = 0.
-\]
-Thus a holomorphic local Lie algebra with a local cyclic structure models a perturbative holomorphic field theory.
-
-The reader might notice that such Maurer-Cartan equations only ever involve quadratic and linear terms in the field.
-To incorporate cubic and higher terms in the equations of motion,
-one should define holomorphic local $L_\infty$ algebras and local cyclic structures,
-which are a modest and straightforward generalization, if one knows what $L_\infty$ algebra means.
-Such definitions can be found in~\cite{CG2}.
-
-\owen{What else to say?}
-
-%
-%As another example, consider the holomorphic tangent bundle $V = \T_X$. 
-%The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
-%A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
-%\[
-%\dbar \mu + \frac12 [\mu,\mu] = 0 .
-%\]
-%This recovers the classical picture describing formal deformations of complex structures on~$X$.
-
-%this section aimed at mathematicians
-%emphasize connection with (derived) complex geometry
-
-\subsection{From supersymmetric field theories to holomorphic field theories}
+\subsection{The local definition, and examples from supersymmetric field theories}
 
@@
 
+\subsection{An extended aside on perturbative quantization}
+
+\owen{I suggest we mostly move this to a later section and expand it substantially.}
+
+So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
+In the topological setting, renormalization is very well-controlled.
+The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
+
+In other words, by a judicious choice of gauge-fixing, 
+we find that the one-loop Feynman diagrams have no UV divergences.
+Moreover, no higher loop diagrams appear (for combinatorial reasons),
+and the action functional satisfies the quantum master equation.
+See Section~\ref{sec: susytwist revisited} for some further discussion.
+
+Although holomorphic field theories had already appeared in practice,
+my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
+He did the following:
+\begin{itemize}
+\item established key analytic results about holomorphic renormalization, 
+showing that it is highly manageable, with no counterterms to 1-loop; and
+\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
+\end{itemize}
+These apply to all holomorphic theories on $\CC^n$,
+but the techniques typically extend to more general complex manifolds.
+
+This foundational work was motivated in large part by our joint effort to generalize to complex $n$-folds results about chiral conformal theories on Riemann surfaces.
+A first fruit of our work \cite{GWcurr} is an examination of higher-dimensional {\em current algebras},
+which are factorization algebras that generalize the Kac-Moody vertex algebras that play a crucial role in contemporary representation theory.
+We show, for instance, that these current algebras arise as the quantization of symmetries of holomorphic field theories, 
+much as the affine Lie algebras are symmetries of CFTs on Riemann surfaces.
+In addition, we show that encoded in our factorization algebras are the higher Kac-Moody Lie algebras $\widehat{\g}_{d,\theta}$ of Faonte-Hennion-Kapranov~\cite{FHK}. 
+It is striking to find this rigid skeleton of algebra under the meat of our analysis,
+as our work is strongly differential-geometric in flavor.
+Moreover, as their work provides a direct connection with the derived algebraic geometry of $\RR Bun_G(X)$,
+there emerges a beautiful generalization of the fertile interactions between algebraic geometry, representation theory, and physics that have grown around bundles on Riemann surfaces.
+(The prospect looms that in higher dimensions,
+one might find a correspondence between conformal blocks and nonabelian theta functions.)
+
+A second fruit is a collaboration of Williams with the physicist Ingmar Saberi \cite{SabWil1,SabWil2}.
+They have carefully worked out the holomorphic twists of several supersymmetric theories
+and given a novel approach, via factorization algebras, to the results of Beem et al \cite{Beem}.
+Particularly important for this proposal,
+they have shown how important invariants (notably the ``supersymmetric index") of the untwisted, supersymmetric theory can be computed simply in the holomorphic twist.
+
 \section{Algebra and holomorphic field theories}
-\label{sec: algebra}
 
@@
 In \cite{FHK} they are shown to appear naturally in various contexts,
-notably in studying the derived moduli space of $G$-bundles on a complex varieties of dimension~$d$.
+notably in studying the derived moduli of $G$-bundles on a complex varieties of dimension~$d$.
 
@@
 \[
-(x_0 \otimes f_0, \ldots, x_{d} \otimes f_{d}) \mapsto \Tr_V( x_0 \cdots x_{d}) \,\Res(f_0 \, \partial f_1 \wedge \cdots \wedge \partial f_{d}).
+x_0 \otimes f_0, \ldots, x_{d} \otimes f_{d} \mapsto \Tr_V( x_0 \cdots x_{d}) \Res(f_0 \partial f_1 \cdots \partial f_{d}).
 \]
@@
 \section{Algebraic structures parametrized by configuration spaces}
-\label{sec: config}
 
@@
 
-\owen{Rewrite this first attempt to be more accurate.}
-
-\begin{thm}[\cite{EllSaf}]
-\label{thm: EllSaf}
+\owen{give a nice version of their statement, with this as a first attempt}
+
+\begin{thm}[\cite{EllSaf},\owen{precise location}]
 Let $\cT$ be a classical field theory on $\RR^d$ in the sense of~\cite{CosBook},
-and let its observables $\Obs_\cT$ be constructed following~\cite{CG2}.
-
-If the theory $\cT$ satisfies 
+and let its observables be constructed following~\cite{CG2}.
+If the theory satisfies 
 \begin{enumerate}
-\item[(i)] it is equivariant under the action of the translation group,
-\item[(ii)] the action of the translation Lie algebra is homotopically trivialized,\footnote{View the translation algebra $\RR^d$ as spanned by the basis $\{\partial_j\}$ of constant vector fields, and let $\rho: \RR^d \to \Der(\Obs_\cT)$ denote the translation action on observables.
-By a homotopical trivialization, we mean here that there is a linear map $\eta: \RR^d \to \Der(\Obs_\cT)$ of degree $-1$ such that $[\d_{\cT}, \eta(\partial_j)] = \rho(\partial_j)$.
-In other words, $\eta$ provides a chain homotopy trivialization of the action~$\rho$.} 
-and
+\item[(i)] $\cT$ is equivariant under the action of the translation group,
+\item[(ii)] the action of the translation Lie algebra is homotopically trivialized, and
 \item[(iii)] the extension of observables along an inclusion of discs is a quasi-isomorphism,
@@
 
-This theorem applies to many well-known examples from physics:
-\begin{itemize}
-\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra.
-It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
-\item The Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
-\item The Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
-\item The Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$.
-\end{itemize}
-It applies to other examples of topological AKSZ theories, such as BF theories and the Poisson $\sigma$-model.
-In all these examples, the underlying elliptic complex appearing in the field theory is a version of the de Rham complex,
-so that the chain homotopy $\eta$ is easily constructed by contracting a vector field with differential forms.
-
-This theorem builds an explicit bridge between topology and physics. 
-Thanks to the theorem of Elliott and Safronov, we know that most topological field theories in the physicist's sense provide $E_n$ algebras (with the examples above as evidence),
-but they can thus be analyzed using the powerful machinery of modern homotopy theory. 
-Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. 
-Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.
-(See Section~\ref{sec: reln to functorial TFT} for the relation with the Atiyah-Segal approach to TFT.)
-
-Let us comment on some aspects of the theorem and its proof.
 The notion from \cite{CosBook} articulates Lagrangian field theories whose linearized equations of motion are elliptic in nature;
@@
 and the observables are a dg commutative algebra given a symmetric algebra on the linear dual to the fields and equipped with a differential $d_\cT$ that is determined by the Lagrangian density of the theory.
-Item (ii) above then means that each vector field $\partial_j$ acts by a degree 0 cochain map $D_j$ on the observables and there is a degree one cochain homotopy $\eta$ on the observables such that $[d_\cT, \eta(\partial_j)]~=~D_j$.
+Item (ii) above then means that each vector field $\partial_i$ acts by a degree 0 cochain map $D_i$ on the observables and there is a degree one cochain homotopy $\eta_i$ on the observables such that $[d_\cT, \eta_i]~=~D_i$.
+
+\owen{Actually say what kind of $d$-discs algebras one gets.}
+This theorem applies to many well-known examples from physics:
+\begin{itemize}
+\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra.
+It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
+\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
+\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
+\item Each Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming the coadjoint quotient stack~$\fg^*/G$.
+\end{itemize}
+It applies to other examples of topological AKSZ theories, such as BF theories.
+In all these examples, the underlying elliptic complex is a version of the de Rham complex.
 
@@
 so that many familiar constructions from the physical approach to TFTs fit cleanly and easily into this framework.
+
+\owen{Stuff about formality? functorial field theories?}
+
+This theorem builds an explicit bridge between topology and physics. 
+Thanks to the theorem of Elliott and Safronov, we know that most topological field theories in the physicist's sense provide $E_n$ algebras,
+but they can thus be analyzed using the powerful machinery of modern homotopy theory. 
+Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. 
+Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.
 
@@
 \[
-\Omega^{0,\bu}(X) \,\widehat{\otimes}_\pi\, \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
+\Omega^{0,\bu}(X) \widehat{\otimes}_\pi \Omega^{0,\bu}(Y) \to \Omega^{0,\bu}(X \times Y)
 \]
@@
 For an extensive discussion of these issues, see the appendices of~\cite{CG1}.
-From hereon we will ignore function-analytic aspects and write~$\otimes$,
-with an appropriate choice of symmetric monoidal category left implicit.
+From hereon we will ignore function-analytic aspects and write $\otimes$,
+with an appropriate symmetric monoidal category left implicit.
 
@@
 \section{Factorization algebras and holomorphic field theories}
-\label{sec: fact alg}
+\label{prefactorization_algebras}
 
@@
 To each open interval $(a,b)$, we set $\cF_A( (a,b) ) = A$.
-To any open set $U = \coprod_j I_j$, 
-where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$. 
+To any open set $U = \coprod_j I_j$, where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$.
 The structure maps simply arise from the multiplication map for $A$.
 Figure ~\ref{fig:assasfact} displays the structure of $\cF_A$.
-Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra.~\hfill$\Diamond$
+Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra.
+%(One takes an infinite tensor products of unital algebras, as follows.
+Given an infinite set $I$, consider the poset of finite subsets of $I$, ordered by inclusion.
+For each finite subset $J \subset I$, we can take the tensor product $A^J = \bigotimes_{j \in J} A$.
+For $J \hookrightarrow J'$, we define a map $A^J \to A^{J'}$ by tensoring with the identity $1 \in A$ for every $j \in J' \backslash J$.
+Then $A^I$ is the colimit over this poset.)
+~\hfill$\Diamond$
 \end{eg}
@@
 \begin{rmk}
-The reader fond of higher abstract nonsense will note that we could have factorization algebras take values in other target categories (or even better, $\infty$-categories),
+The reader fond of higher abstract nonsense will note that we could have factorization algebras take values in other target categories (better, $\infty$-categories),
 not just vector spaces or cochain complexes.
-For instance, one might categorify the values: 
-$\cF$ might assign an $\infty$-category $\cF(U)$ to each open set~$U$.
+For instance, one might assign an $\infty$-category to each open set.
 This generalization is fruitful.
-In the Beilinson-Drinfeld style, it leads to chiral categories, which play a key role in the geometric Langlands program.
+In the Beilinson-Drinfeld style, it leads to chiral categories, which play an increasingly central role in the geometric Langlands program.
 In the style advocated above, it would likewise be useful for capturing notions like defects or extended operators from quantum field theory.
 \end{rmk}
+
+%\subsection{Prefactorization algebras as algebras over an operad}
+%\label{sec:disj}
+%
+%The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
+%A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
+%See \owen{add citations}
+%
+%\begin{dfn}
+%Let $\Disj_M$ denote the following colored operad associated to~$M$: 
+%\begin{itemize}
+%\item The colors (or objects) consist of all open subsets of $M$. 
+%\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$.
+If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point.
+Otherwise, the set of maps is empty.
+%\item The composition of maps is defined in the obvious way. 
+%\end{itemize}
+%\end{dfn}
+%
+%\begin{dfn}
+%Let $\mc{C}$ be a colored operad. 
+%A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
+%\end{dfn}
+%
+%In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
+%Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories. 
+%
+%\begin{rmk} 
+%If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
+%Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
+%~\hfill$\Diamond$ 
+%\end{rmk}
+%
+%Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$. 
+%
+%\begin{dfn}
+%We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
+%\end{dfn}
+%
+%\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
+%\label{AssAsFact}
+%
+%We explained above how an associative algebra provides a prefactorization algebra on the real line.
+There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras.
+Here we will characterize those that do arise from associative algebras.
+% 
+%\begin{dfn}
+%Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
+%We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
+%\end{dfn}
+%
+%It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.
+%
+%\begin{lem}\label{locally_constant_is_associative}
+%Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
+%Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
+%\end{lem}
+%
+%One can got further, however, and also capture modules, essentially by marking the line with points.
+%For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.
+%
+%Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$.
+%We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure. 
+%
+%Pick a point $p \in \RR$.
+On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$.
+Likewise, on the half-line $\{x \in \RR \mid p < x\}$, $\cF_M$ is given by $\cF_B$.
+Intervals containing $p$ are determined, though, by $M$.
+When we consider an interval $I = (t_0,t_1)$ such that $t_0 < p < t_1$, we set $\cF_M(I)  = M$.
+The structure maps are also determined by the bimodule structure.
+For example, given
+%\[
+%s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
+%\]
+%we have
+%\begin{align*}
+%\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
+%&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
+%&= A \ot M \ot B
+%\end{align*}
+%and the inclusion of these three intervals into $(s_0,u_1)$ is the map
+%\[
+%\begin{array}{ccc}
+%\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
+%a \ot m \ot b & \mapsto & amb
+%\end{array}.
+%\]
+%The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.
+%
+%%\begin{figure}
+%%\begin{center}
+%% \begin{minipage}{3cm}
+%% \begin{tikzpicture}[scale=0.75]
+%% \begin{scope}[line cap=round,ultra thick]
+%% \draw (-2.5,0) -- (-1.5,0); 
+%% \draw (-1,0) -- (0.5,0); 
+%% \draw[fill=black] (0,0) circle (0.07);
+%% \draw (1.5,0) -- (2.5,0); 
+%% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
+%% \draw (-2.75,-2) -- (0.75,-2); 
+%% \draw[fill=black] (0,-2) circle (0.07);
+%% \draw (1.25,-2) -- (2.75,-2);  
+%% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
+%% \draw (-3,-4) -- (3,-4);
+%% \draw[fill=black] (0,-4) circle (0.07); 
+%% \end{scope}
+%% \end{tikzpicture}
+%% \end{minipage}
+%%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
+%% \begin{minipage}{8cm}
+%% \begin{tikzcd}[cramped,column sep=tiny]
+%%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
+%%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
+%%amb  & \in &M 
+%%\end{tikzcd}
+%%\end{minipage}
+%%\end{center}
+%%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
+%%\label{fig:bimodasfact}
+%%\end{figure}
+%
+%\begin{figure}
+%\begin{center}
+% \begin{tikzpicture}
+% \begin{scope}[line cap=round,ultra thick]
+% \draw (-2.5,1) -- (-1.5,1); 
+% \draw (-1,1) -- (0.5,1); 
+% \draw[fill=black] (0,1) circle (0.07);
+% \draw (1.5,1) -- (2.5,1); 
+% \draw[->,semithick] (0,0.75) -- (0,0.25);
+% \draw (-2.75,-0.1) -- (0.75,-0.1); 
+% \draw[fill=black] (0,-0.1) circle (0.07);
+% \draw (1.25,-0.1) -- (2.75,-0.1);  
+% \draw[->,semithick] (0,-0.35) -- (0,-0.85);
+% \draw (-3,-1.2) -- (3,-1.2);
+% \draw[fill=black] (0,-1.2) circle (0.07); 
+% \end{scope}
+%
+%\node at (4,0){$\rightsquigarrow$};
+%
+%\node at (7,0) {
+%\begin{tikzcd}[cramped,column sep=tiny]
+%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
+%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
+%amb  & \in &M 
+%\end{tikzcd}
+%};
+%
+%\end{tikzpicture}
+%\end{center}
+%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
+%\label{fig:bimodasfact}
+%\end{figure}
 
@@
 
-The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. 
-We call it the {\em Weiss topology} of~$M$. 
+The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$. 
 Note that Weiss covers are required to ``know'' about every configuration of finitely many points,
@@
 (If one has a metric on the manifold, one can work with unions of ``small'' discs.)
+
+%\begin{rmk}
+%A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens.
+It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$.
+For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection
+%\[
+%\{ U_i^n \mid i \in I\}
+%\]
+%provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
+%\end{rmk}
+%
+%\begin{eg}\label{WeissAsExponential}
+%For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$.
+One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
+Alternatively, the collection of opens $\{ M \setminus q \mcol q \in M\}$ is a Weiss cover of $M$.
+One can also produce a Weiss cover of a manifold with countably many elements.
+Fix a Riemannian metric on $M$.
+Pick a collection of points $\{q_n\in M \mcol n \in \NN\}$ such that the union of the unit ``discs'' $D_1(q_n) = \{ q \in M \mcol \d(q_n,q) < 1\}$ covers $M$.
+(Such an open may not be homeomorphic to a disc if the injectivity radius of $q_n$ is less than 1.)  Consider the collection of all ``discs'' $\fD = \{ D_{1/m}(q_n) \mcol m \in \NN, n \in \NN\}$.
+The collection of all finite, pairwise disjoint union of elements of $\fD$ is a countable Weiss cover.~\hfill $\Diamond$
+%\end{eg}
 
@@
 
+%Many examples of factorization algebras satisfy an additional and desirable property,
+%which motivates the name ``factorization algebra.''
+%
+%\begin{dfn}
+%A factorization algebra $\cF$ is \emph{multiplicative} if for every pair $U,V$ of disjoint open subsets of $M$, the structure map
+%$$
+%\cF(U) \otimes \cF(V) \to \cF(U \sqcup V) 
+%$$
+%is a quasi-isomorphism.
+%\end{dfn}
+
 \subsection{How factorization algebras appear in QFT}
+
+%Associative algebras are familiar to every mathematician, but as we have just seen, they reflect and encode one-dimensional geometry.
+%It is then natural to ask about higher-dimensional versions of algebra.
+%Topologists developed such a systematic generalization, often called $E_n$ algebras or algebras over the little $n$-discs operad,
+%which we now describe and relate to prefactorization algebras on~$\RR^n$.
+%In relation to the subject of this paper, we mention that $E_n$ algebras arise naturally from $n$-dimensional topological field theories;
+%we will soon introduce a holomorphic analog of $E_n$ algebras relevant to holomorphic field theories,
+%modeled on the discussion here.
+%
+%Fix a dimension $n$. 
+%Let $D^n(x,r)$ denote the open disc of radius $r$ centered at $x \in \RR^n$,
+%and let $D^n$ denote the unit disc~$D^n(0,1)$.
+%
+%\begin{dfn}
+%Let $E_n$ denote the colored operad with a single color $D^n$ and a topological space $E_n(k)$ of maps from $k$ copies of $D^n$ to itself given by configurations of $k$ disjoint discs:
+%\[
+%E_n(k) = \left\{ \begin{matrix}(x_1, \ldots, x_k) \in (D^n(0,1))^k,\\ (r_1, \ldots, r_k) \in (0,1)^k\end{matrix} \,\bigg|\, \text{\begin{tabular}{c}the discs $D^n(x_i,r_i)$ are pairwise disjoint\\ but each contained in the unit disc $D^n$\end{tabular}}\right\}.
+%\]
+%\end{dfn}
+%
+%When $n = 1$, the operad encodes the idea of associative multiplication:
+%we get pictures much like those we drew earlier with intervals, 
+%except that now we can slide and stretch the intervals because we have a space of operations.
+%More accurately, $E_1$ is a model for associative algebras up to homotopy; 
+%it is closely related to the $A_\infty$ operad. \owen{Let me check how people compare these.}
+%
+%For arbitrary $n$, this definition encodes concretely the idea of $n$ directions of multiplication.
+%If one fixes a direction, such as a coordinate axis, and works with discs lined up in this direction,
+%one sees an $E_1$ structure.
+%
+%\owen{Add picture? We drew 2d pictures earlier.}
+%
+%An algebra over this operad is called an {\em $E_n$-algebra}.
+%A classic example from topology is given by taking the $n$-fold based loop space
+%\[
+%\Omega^n_x(X) = \{ \gamma: \overline{D^n} \to X \mcol \gamma(\partial \overline{D^n}) = x\}
+%\]
+%of a based space $(X,x)$ (i.e., a topological space with a distinguished point) and $\overline{D^n}$ denotes the closed unit $n$-disc.
+%Maps that send the boundary of a disc to the base point can be extended naturally to bigger discs: just send the rest of the big disc to the basepoint.
+%\owen{Should I spell out the structure of the algebra?}
+%Examples include \owen{What to mention?}
 
@@
 \subsubsection{Relating to the Atiyah-Segal approach to TFTs}
-\label{sec: reln to functorial TFT}
 
@@
 \begin{cor}
-For any Lagrangian field theory satisfying the hypotheses of Theorem~\ref{thm: EllSaf}, 
+For any Lagrangian field theory satisfying the hypotheses of Theorem~\ref{}, 
 there is a fully extended framed $d$-dimensional field theory 
@@
 a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra and, by Lurie's work, a $G$-framed fully extended $d$-dimensional TFT.
-It is interesting to ask how these kinds of functorial field theories intertwine with the better-known constructions,
-such as the Reshetikhin-Turaev theories, 
-where the target category is not ${\rm Alg}_d$ but some other higher-categorical extensions of~$\Vect$.
+It is interesting to ask how these kinds of functorial field theories intertwine with the better-known examples.
 
@@
 
-\section{Renormalization \& anomalies: constructing examples}
-\label{sec: renorm}
+\section{Constructing examples \& renormalization}
 
@@
 
-\owen{Old copy that might be recycled into final version}
-
-So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
-In the topological setting, renormalization is very well-controlled.
-The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
-
-In other words, by a judicious choice of gauge-fixing, 
-we find that the one-loop Feynman diagrams have no UV divergences.
-Moreover, no higher loop diagrams appear (for combinatorial reasons),
-and the action functional satisfies the quantum master equation.
-See Section~\ref{sec: susytwist revisited} for some further discussion.
-
-Although holomorphic field theories had already appeared in practice,
-my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
-He did the following:
-\begin{itemize}
-\item established key analytic results about holomorphic renormalization, 
-showing that it is highly manageable, with no counterterms to 1-loop; and
-\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
-\end{itemize}
-These apply to all holomorphic theories on $\CC^n$,
-but the techniques typically extend to more general complex manifolds.
-
-\brian{Brian's stuff below}
-
 The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.
@@
 There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
-In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
+In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
@@
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
-
-\owen{Laying out some of this stuff in an attempt to state Minghao's theorem}
-
-We will allow graphs with finitely many vertices and edges, 
-but also leaves (also known as hair or half-edges).\footnote{That is, a vertex may have, in addition to edges connecting it to other vertices, some incident edges that do not connect to another vertex.
-These will label inputs to an operation associated to the graph.}
-We allow multiple edges between vertices, as well as loops.
-
-For a graph $\gamma$, let $E(\gamma)$ denote the number of edges,
-$V(\gamma)$ denote the number of vertices,
-and $L(gamma)$ denote the number of leaves.
-
-\begin{dfn}
-For a graph $\gamma$, there is a space $\RR_+^{E(\gamma)}$ parametrizing the moduli space of lengths (all positive) given to the edges.
-This positive orthant has a the partial compactification $\Schw(\gamma)$, known as the {\em Schwinger space} of $\gamma$, 
-where \owen{define!} 
-\end{dfn}
-
-\begin{dfn}
-For a perturbative holomorphic field on $\CC^d$ with space of fields 
-\[
-\cV = \Gamma(\CC^d, \Omega^{0,\bullet}(V)),
-\] 
-as defined in Section~\ref{}, 
-there is a family of distributions
-\[
-w_{\gamma, t}: \cV_c^{L(\gamma)} \to \CC
-\]
-parametrized by $t \in \RR_+^{E(\gamma)}$,
-known as the {\em regularized weight of $\gamma$}.
-\end{dfn}
-
-This family of distributions is constructed as an integral over $\CC^{v(\gamma) d}$,
-where each edge $e$ is labeled by a smooth function $P_{t(e)}$ depending on the length of the edge and where each vertex is labeled by a distribution arising from an interaction term of the theory.
-For general theories, one cannot smoothly continue the regularized weight from the positive length values to zero lengths.
-The putative integrals become divergent.
-
-For holomorphic field theories, however, something remarkable happens.
-
-\begin{thm}[Wang, \owen{precise citations}]
-For every graph~$\gamma$,
-this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
-That is, there is a smooth map
-\[
-w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
-\]
-where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.it 
-\end{thm}
-
-In other words, divergences do not appear.
-
-\owen{It would be good to explain why and indicate what is the appropriate "value" to use.}
 

### 2024-09-19 draft.tex
minghao

@@
 and the action functional satisfies the quantum master equation.
+\brian{this comment does not apply in general, only for cotangent theories.}
 See Section~\ref{sec: susytwist revisited} for some further discussion.
@@
 From Feynman, we know that the path integral can be formally expressed in terms of graphs. 
-More precisely, given a graph $\Gamma$ (whose exact shape depends on the theory), there is a prescription for assigning to it a functional $W_\Gamma$ on the fields (a distribution) which we can understand as term in the quantum action; typically in the form of an integral over $|V(\Gamma)|$ copies of spacetime where $V(\Gamma)$ is the vertex set of the graph.
+More precisely, given a graph $\gamma$ (whose exact shape depends on the theory), there is a prescription for assigning to it a functional $W_\gamma$ on the fields (a distribution) which we can understand as term in the quantum action; typically in the form of an integral over $|V(\gamma)|$ copies of spacetime where $V(\gamma)$ is the vertex set of the graph.
 Unfortunately, this prescription is not always well-posed, as there are infinities which can arise due to presence of overlapping supports of certain distributions.
@@
 For topological quantum field theories, it is known from the work of Axelrod, Singer, Kontsevich, Cattaneo, and others \cite{???} that such Feynman graphs return finite answers and hence there is no need to introduce such complications.
-The method used to prove this interprets such Feynman graph integrals as integrals over configuration space and then showing that the weights $W_\Gamma$ can be extended to some compactification.
+The method used to prove this interprets such Feynman graph integrals as integrals over configuration space and then showing that the weights $W_\gamma$ can be extended to some compactification.
 A different regularization scheme based on the heat equation was used by Costello \cite{CosRenormPaper} to arrive at the same result for topological quantum field theories.
@@
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
-Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
+
+Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
-
-\owen{Laying out some of this stuff in an attempt to state Minghao's theorem}
+We briefly recall the approach to this regulation scheme.
 
@@
 These will label inputs to an operation associated to the graph.}
-We allow multiple edges between vertices, as well as loops.
+We allow multiple edges between vertices, as well as loops, the precise form of which are determined by the interactions of the theory.
 
@@
 $V(\gamma)$ denote the number of vertices,
-and $L(gamma)$ denote the number of leaves.
+and $L(\gamma)$ denote the number of leaves.
+The scheme begins with the familiar Wilsonian approach to renormalization which involves introducing an IR `cut-off' length scale $L > 0$.
+The \textit{Schwinger space} associated to a graph $\gamma$ and a length $L$ is the non-compact manifold with corners $(0,L]^{E(\gamma)}$, which we will denote $\op{Schw}(\gamma)$ below.
+The desired Feynman graph weight $W_\gamma$ of a graph $\gamma$ is obtained as the integral over  Scwhinger space.
 
 \begin{dfn}
-For a graph $\gamma$, there is a space $\RR_+^{E(\gamma)}$ parametrizing the moduli space of lengths (all positive) given to the edges.
-This positive orthant has a the partial compactification $\Schw(\gamma)$, known as the {\em Schwinger space} of $\gamma$, 
-where \owen{define!} 
+For a perturbative field theory with space of fields $\cE$, there is a distribution valued in forms on Schwinger space
+\[
+w_{\gamma} \colon \cE^{L(\gamma)}_c \to \Omega^\bu \left( \op{Schw}(\gamma) \right)
+\]
+which we call the {\em regularized weight of $\gamma$}.
 \end{dfn}
 
-\begin{dfn}
-For a perturbative holomorphic field on $\CC^d$ with space of fields 
-\[
-\cV = \Gamma(\CC^d, \Omega^{0,\bullet}(V)),
-\] 
-as defined in Section~\ref{}, 
-there is a family of distributions
-\[
-w_{\gamma, t}: \cV_c^{L(\gamma)} \to \CC
-\]
-parametrized by $t \in \RR_+^{E(\gamma)}$,
-known as the {\em regularized weight of $\gamma$}.
-\end{dfn}
-
+The possibly ill-defined weight $W_\gamma$ is obtained by integration of $w_\gamma$ over Schwinger space.
 This family of distributions is constructed as an integral over $\CC^{v(\gamma) d}$,
@@
 For general theories, one cannot smoothly continue the regularized weight from the positive length values to zero lengths.
-The putative integrals become divergent.
-
-For holomorphic field theories, however, something remarkable happens.
+The putative integrals become divergent, which is reflected by the non-compactness of Schwinger space from this perspective.
+
+For holomorphic field theories (and generally topological-holomorphic theories, see \cite{WWthf}) however, something remarkable happens.
 
 \begin{thm}[Wang, \owen{precise citations}]
-For every graph~$\gamma$,
-this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
-That is, there is a smooth map
-\[
-w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
-\]
-where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.it 
+Let $\cE$ be the space of fields underlying a holomorphic field theory on $\C^n$.
+For every graph~$\gamma$, $w_{\gamma}$ has a natural smooth extension $\til {w_\gamma}$ to a compactification $\til{\op{Schw}(\gamma)}$ of Schwinger space.
+In particular, the weight
+\[
+W_\gamma \colon \cE^{L(\gamma)}_c \xto{\til{w_\gamma}}\Omega^\bu \left( \til{\op{Schw}(\gamma)} \right) \xto{\int} \C
+\]
+is a continuous linear functional on $\cE_c^{L(\gamma)}$.
 \end{thm}

### 2024-09-19 draft.tex
first full pass thru holo FT section

--- 2024-09-19 draft.tex
@@
 \subsubsection{Holomorphic gauge theories}
+\label{sec: hol BF dfn}
 
@@
 the fields are encoded by a Dolbeault complex on $\CC^n$, 
-translations act by the Lie derivative $L_{\partial/\partial x_j}$,
+a real translation $\partial/\partial x_j$ acts by the Lie derivative $L_{\partial/\partial x_j}$,
 and so we trivialize the action $L_{\partial/\partial \zbar_j}$ by using the contraction $\iota_{\partial/\partial \zbar_j}$,
@@
 
-We now turn to using this point of view in the setting of supersymmetric theories
+We now turn to using this point of view in the setting of supersymmetric theories.
 
@@
 We focus on Euclidean field theories and work in Riemannian signature,
-hence for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
+so for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
 $\mathfrak{so}(d) \ltimes \ft$
@@
 a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
-The classification of twisting supercharges is a completely algebraic question,
-and we refer to~\autocite{ESsusy} for a complete classification for supersymmetry algebras in dimensions from $1$ to~$10$.
-
-If a Lagrangian field theory $\cT$ has $\ft$ as a symmetry, 
+The classification of twisting supercharges is a completely algebraic question:
+see~\autocite{ESsusy} for a complete classification in dimensions from $1$ to~$10$.
+
+In even dimensions $d = 2n$, basic properties of the supersymmetry algebra guarantee that there exists a twist that provides a complex structure to $\RR^{2n}$.\footnote{This claim fails in exactly one example, namely for $\cN=(1,0)$ supersymmetry in two dimensions, as the dimension and amount of supersymmetry are too small.}
+Indeed, so long as a twisted supercharge $\cQ$ is nonzero, 
+one finds that the image of the map $[\cQ,-] = \Gamma(\cQ,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
+A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly~$n$,
+and we declare the image of $\cQ$ as spanned by the anti-holomorphic vector fields~$\{\del / \del \zbar_i\}$.
+
+If a classical field theory $\cT$ has $\ft$ as a symmetry, 
 then a choice of twist $\cQ$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^\cQ$.
@@
 (the $\cdots$ leaves room for terms non-linear in $\cQ$).
-For extensive details on how the twisted theory is defined we refer to~\autocite{CostelloHolomorphic, ESW}.
+For a systematic discussion of how the twisted theory is defined, 
+we refer to~\autocite{CostelloHolomorphic, ESW}.
 
 Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}.
-These twisted theories are analogs of BF theory and Chern--Simons theory, so long as one includes purely topological and purely holomorphic theories.
-In even dimensions $d = 2n$, basic properties of the supersymmetry algebra guarantee that there exists a twist rendering the theory holomorphic.\footnote{This fails in one example where the dimension and amount of supersymmetry is too small, namely for $\cN=(1,0)$ supersymmetry in two dimensions.}
-Indeed, so long as a twisted supercharge is nonzero $\cQ \ne 0$ one see that the image of the map $[\cQ,-] = \Gamma(\cQ,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
-A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly $n$, 
-and we declare the the image of $\cQ$ is spanned by the anti-holomorphic vector fields $\{\del / \del \zbar_i\}$.
-Thus there exist homotopies $\{\eta_i\}$ such that 
+These twisted theories are BF theorires or Chern--Simons theories, possibly along with other fields in associated bundle; 
+depending on the twist, that might mean a purely topological or purely holomorphic BF or Chern-Simons theory.
+In even dimensions $d = 2n$, a minimal twist renders the theory holomorphic.
+$\cQ$ itself determines the homotopies $\{\eta_i\}$ such that 
 \beqn
@@
 
-%For our purposes here, a crucial property of a twist $Q$ is the dimension $k_Q$ of its image ${\rm Im} \; \Gamma(Q, \cdot) \subset \RR^d$,
-%which we call the number of {\em invariant} directions of~$Q$.
-%By the non-degeneracy of the pairing $\Gamma$, it follows that $k_Q \geq \frac{d}{2}$.
-%If the number of invariant directions is maximal with $k_Q = d$, then the twisted theory $\cT^Q$ is purely topological. 
-%If the number of invariant directions is minimal with $k_Q = \frac{d}{2}$, then the twisted theory $\cT^Q$ is purely holomorphic.
-
-As a representative example of how twisting behaves, 
-consider pure four-dimensional supersymmetric Yang--Mills theory with $\cN=1$ supersymmetry.
-The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional and there exists a unique holomorphic twist $\cQ$ (up to equivalence).
-In this dimension, with this amount of supersymmetry, there does not exist a topological twist.
-The holomorphic twist of the theory with respect to $\cQ$ is equivalent to holomorphic BF theory on $\CC^2$.
-
-This ends our discussion of twisting supersymmetric gauge theories.
+As a representative example of twisting, 
+consider four-dimensional space $\RR^4$ with $\cN=1$ supersymmetry.
+The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional, 
+and every nonzero twist is minimal and gives us a copy of $\CC^2$.\footnote{And in a natural sense, they are all equivalent.}
+That is, with this amount of supersymmetry, there does {\it not} exist a topological twist.
+consider the fundamental example of pure four-dimensional supersymmetric Yang--Mills theory with $\cN=1$ supersymmetry. 
+Its holomorphic twist is equivalent to holomorphic BF theory on~$\CC^2$ described in Section~\ref{sec: hol BF dfn}.
+
 There are many other appearances of holomorphic field theories in the context of supersymmetry.
-Here is a (very) non-exhaustive list.
-
+Here is a (very) non-exhaustive list:
 \begin{itemize}
-\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
-For instance, the closed string field theory of the topological B-model on a Calabi--Yau threefold is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
-This theory is defined on any Calabi--Yau manifold. 
+\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
+For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
 The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
 \item
-It is possible to make sense of Kodaira--Spencer theory in other dimensions.
+It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
 In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
-\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
-Often, the theory you start with on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
+\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
+Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
 \item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
@@
 \end{itemize}
+We recommend \og{is there some other place to point?}
 
@@
 There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
-In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
+In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

### 2024-09-19 draft.tex

@@
 There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
-In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
+In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
-Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
+
+Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
-
-\owen{Laying out some of this stuff in an attempt to state Minghao's theorem}
+We briefly recall the approach to this regulation scheme.
 

### 2024-09-19 draft.tex
merge

--- 2024-09-19 draft.tex
@@
 
-\owen{We discussed having the following:
-\begin{itemize}
-\item Quick overview for topological field theories (=analytic content is de Rham complex): 
-\begin{itemize}
-\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
-\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
-\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
-\end{itemize} 
-\item Overview the history of the holomorphic case, with citations
-\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
-\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
-\end{itemize}}
-
-\owen{Old copy that might be recycled into final version}
-
-So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
-In the topological setting, renormalization is very well-controlled.
-The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
-
-In other words, by a judicious choice of gauge-fixing, 
-we find that the one-loop Feynman diagrams have no UV divergences.
-Moreover, no higher loop diagrams appear (for combinatorial reasons),
-and the action functional satisfies the quantum master equation.
-\brian{this comment does not apply in general, only for cotangent theories.}
-See Section~\ref{sec: susytwist revisited} for some further discussion.
-
-Although holomorphic field theories had already appeared in practice,
-my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
-He did the following:
-\begin{itemize}
-\item established key analytic results about holomorphic renormalization, 
-showing that it is highly manageable, with no counterterms to 1-loop; and
-\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
-\end{itemize}
-These apply to all holomorphic theories on $\CC^n$,
-but the techniques typically extend to more general complex manifolds.
-
-\brian{Brian's stuff below}
-
 The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.

### 2024-09-20 draft.tex
merge

--- 2024-09-19 draft.tex
@@
 
-For an example that mixes several types and that is a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks,
-see Section~\ref{sec: seiberg}.
+For an example that mixes several types, see Section~\ref{sec: seiberg}
+where we discuss a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks.
 
@@
 \end{itemize}
-We recommend \og{is there some other place to point?}
+We recommend \owen{is there some other place to point?} for more discussion.
 
@@
 and the action functional satisfies the quantum master equation.
-\brian{this comment does not apply in general, only for cotangent theories.}
 See Section~\ref{sec: susytwist revisited} for some further discussion.
@@
 From Feynman, we know that the path integral can be formally expressed in terms of graphs. 
-More precisely, given a graph $\gamma$ (whose exact shape depends on the theory), there is a prescription for assigning to it a functional $W_\gamma$ on the fields (a distribution) which we can understand as term in the quantum action; typically in the form of an integral over $|V(\gamma)|$ copies of spacetime where $V(\gamma)$ is the vertex set of the graph.
+More precisely, given a graph $\Gamma$ (whose exact shape depends on the theory), there is a prescription for assigning to it a functional $W_\Gamma$ on the fields (a distribution) which we can understand as term in the quantum action; typically in the form of an integral over $|V(\Gamma)|$ copies of spacetime where $V(\Gamma)$ is the vertex set of the graph.
 Unfortunately, this prescription is not always well-posed, as there are infinities which can arise due to presence of overlapping supports of certain distributions.
@@
 For topological quantum field theories, it is known from the work of Axelrod, Singer, Kontsevich, Cattaneo, and others \cite{???} that such Feynman graphs return finite answers and hence there is no need to introduce such complications.
-The method used to prove this interprets such Feynman graph integrals as integrals over configuration space and then showing that the weights $W_\gamma$ can be extended to some compactification.
+The method used to prove this interprets such Feynman graph integrals as integrals over configuration space and then showing that the weights $W_\Gamma$ can be extended to some compactification.
 A different regularization scheme based on the heat equation was used by Costello \cite{CosRenormPaper} to arrive at the same result for topological quantum field theories.
@@
 There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
-In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
+In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
-
-Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
+Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
-We briefly recall the approach to this regulation scheme.
+
+\owen{Laying out some of this stuff in an attempt to state Minghao's theorem}
 
@@
 These will label inputs to an operation associated to the graph.}
-We allow multiple edges between vertices, as well as loops, the precise form of which are determined by the interactions of the theory.
+We allow multiple edges between vertices, as well as loops.
 
@@
 $V(\gamma)$ denote the number of vertices,
-and $L(\gamma)$ denote the number of leaves.
-The scheme begins with the familiar Wilsonian approach to renormalization which involves introducing an IR `cut-off' length scale $L > 0$.
-The \textit{Schwinger space} associated to a graph $\gamma$ and a length $L$ is the non-compact manifold with corners $(0,L]^{E(\gamma)}$, which we will denote $\op{Schw}(\gamma)$ below.
-The desired Feynman graph weight $W_\gamma$ of a graph $\gamma$ is obtained as the integral over  Scwhinger space.
+and $L(gamma)$ denote the number of leaves.
 
 \begin{dfn}
-For a perturbative field theory with space of fields $\cE$, there is a distribution valued in forms on Schwinger space
-\[
-w_{\gamma} \colon \cE^{L(\gamma)}_c \to \Omega^\bu \left( \op{Schw}(\gamma) \right)
-\]
-which we call the {\em regularized weight of $\gamma$}.
+For a graph $\gamma$, there is a space $\RR_+^{E(\gamma)}$ parametrizing the moduli space of lengths (all positive) given to the edges.
+This positive orthant has a the partial compactification $\Schw(\gamma)$, known as the {\em Schwinger space} of $\gamma$, 
+where \owen{define!} 
 \end{dfn}
 
-The possibly ill-defined weight $W_\gamma$ is obtained by integration of $w_\gamma$ over Schwinger space.
+\begin{dfn}
+For a perturbative holomorphic field on $\CC^d$ with space of fields 
+\[
+\cV = \Gamma(\CC^d, \Omega^{0,\bullet}(V)),
+\] 
+as defined in Section~\ref{}, 
+there is a family of distributions
+\[
+w_{\gamma, t}: \cV_c^{L(\gamma)} \to \CC
+\]
+parametrized by $t \in \RR_+^{E(\gamma)}$,
+known as the {\em regularized weight of $\gamma$}.
+\end{dfn}
+
 This family of distributions is constructed as an integral over $\CC^{v(\gamma) d}$,
@@
 For general theories, one cannot smoothly continue the regularized weight from the positive length values to zero lengths.
-The putative integrals become divergent, which is reflected by the non-compactness of Schwinger space from this perspective.
-
-For holomorphic field theories (and generally topological-holomorphic theories, see \cite{WWthf}) however, something remarkable happens.
+The putative integrals become divergent.
+
+For holomorphic field theories, however, something remarkable happens.
 
 \begin{thm}[Wang, \owen{precise citations}]
-Let $\cE$ be the space of fields underlying a holomorphic field theory on $\C^n$.
-For every graph~$\gamma$, $w_{\gamma}$ has a natural smooth extension $\til {w_\gamma}$ to a compactification $\til{\op{Schw}(\gamma)}$ of Schwinger space.
-In particular, the weight
-\[
-W_\gamma \colon \cE^{L(\gamma)}_c \xto{\til{w_\gamma}}\Omega^\bu \left( \til{\op{Schw}(\gamma)} \right) \xto{\int} \C
-\]
-is a continuous linear functional on $\cE_c^{L(\gamma)}$.
+For every graph~$\gamma$,
+this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
+That is, there is a smooth map
+\[
+w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
+\]
+where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.it 
 \end{thm}
@@
 
-\subsection{Holomorphic QCD}
+\subsection{Holomorphic chromodynamics and steps towards holomorphic QCD}
 

### 2024-09-20 draft.tex
minghao2

--- 2024-09-19 draft.tex
@@
 
+\owen{We discussed having the following:
+\begin{itemize}
+\item Quick overview for topological field theories (=analytic content is de Rham complex): 
+\begin{itemize}
+\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
+\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
+\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
+\end{itemize} 
+\item Overview the history of the holomorphic case, with citations
+\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
+\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
+\end{itemize}}
+
+\owen{Old copy that might be recycled into final version}
+
+So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
+In the topological setting, renormalization is very well-controlled.
+The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
+
+In other words, by a judicious choice of gauge-fixing, 
+we find that the one-loop Feynman diagrams have no UV divergences.
+Moreover, no higher loop diagrams appear (for combinatorial reasons),
+and the action functional satisfies the quantum master equation.
+\brian{this comment does not apply in general, only for cotangent theories.}
+See Section~\ref{sec: susytwist revisited} for some further discussion.
+
+Although holomorphic field theories had already appeared in practice,
+my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
+He did the following:
+\begin{itemize}
+\item established key analytic results about holomorphic renormalization, 
+showing that it is highly manageable, with no counterterms to 1-loop; and
+\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
+\end{itemize}
+These apply to all holomorphic theories on $\CC^n$,
+but the techniques typically extend to more general complex manifolds.
+
+\brian{Brian's stuff below}
+
 The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.

### 2024-09-20 draft.tex
must have done some stuff

--- 2024-09-20 draft.tex
@@
 
-\epigraph{\itshape The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
+\epigraph{The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
 

### 2024-09-20 draft.tex
switching computers might be a mistake for me

--- 2024-09-20 draft.tex
@@
 
-For an example that mixes several types, see Section~\ref{sec: seiberg}
-where we discuss a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks.
+For an example that mixes several types and that is a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks,
+see Section~\ref{sec: seiberg}.
 
@@
 
-\subsection{Holomorphic chromodynamics and steps towards holomorphic QCD}
+\subsection{Holomorphic QCD}
 

### 2024-09-20 draft.tex
rearranging subsections in 2.2 and adding subsections in 6

--- 2024-09-20 draft.tex
@@
 
-\epigraph{The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
+\epigraph{The mathematical language of classical physics is based upon real numbers \dots.
+The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
 
@@
 \[
-{\rm Conn}^\dbar_G(P) \cong \Omega^{0,1}(M, {\rm ad}(P)),
+{\rm Conn}^\dbar_G(P) \cong \Omega^{0,1}(M, \fg_P),
 \]
@@
 \beqn
-S_{hCS} (A) = \int_X \Omega \wedge CS(A) 
+S_{hCS} (A) = \int_M \Omega \wedge CS(A) 
 \eeqn
@@
 \owen{Should we elaborate or just stop with a reference?}
+
+\subsubsection{Interlude on holomorphic field theories as chiral sectors}
+
+Every holomorphic theory we have introduced so far has a ``kinetic term'' (the quadratic term in the action functional) that only involves $\dbar$.
+Thus the linearized equations of motion always have the form $\dbar \phi = 0$,
+so that they manifestly relate to holomorphic functions (or sections).
+There are, however, holomorphic theories with a different flavor.
+
+\begin{comment}
+A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
+Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
+We saved this example for last since its holomorphic analog is a bit more elusive than the previous examples.
+\end{comment}
+
+We start with complex dimension~$1$.
+The usual scalar field theory can be written as 
+\[
+\int_{\Sigma} \phi \wedge \del \dbar \phi, 
+\]
+where $\Sigma$ is a Riemann surface.
+Using integration by parts, one can use instead the action functional
+\[
+\int_{\Sigma} \partial \phi \wedge \dbar \phi.
+\]
+This theory is not holomorphic, but we can force it to be holomorphic by demanding that $\dbar \phi = 0$.
+Importantly, this constraint is \textit{not} an equation of motion.
+When we impose this constraint, we can rewrite the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
+\beqn\label{eqn:scalar1}
+\int_\Sigma \alpha \wedge \dbar (\del^{-1} \alpha) ,
+\eeqn
+where $\alpha$ plays the role of $\partial \phi$.
+In this theory the kinetic term is the whole action,
+and it has a rather different flavor from the examples we have seen so far.\footnote{This action functional is a precursor to the ``holomorphic gravity'' theory we meet next, 
+known as Kodaira--Spencer theory.}
+One might call this the {\em chiral sector} of the free scalar theory,
+as it consists of the complex-valued scalar fields satisfying a ``chiral'' constraint.
+
+There is a higher-dimensional analog of the chiral sector of the scalar field.
+Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
+The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
+\beqn
+\del \alpha = 0.
+\eeqn
+(When $n=0$ and $X$ is simply a Riemann surface, 
+this constraint is automatic.)
+The action functional is the same as~\eqref{eqn:scalar1}.
+Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
+\beqn
+\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
+\eeqn
+where $C \in \Omega^{2n+1}(X)$.
+For more details we refer to~\cite{GRWwzw}.
 
@@
 
-\subsubsection{Holomorphic field theories as chiral sectors}
-
-\owen{I'm a little lost about the motivation for this section, 
-given the earlier scalar field section. This C theory looks interest so maybe we can figure out a natural place to put it?}
-
-A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
-Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
-We saved this example for last since its holomorphic analog is a bit more elusive than the previous examples.
-
-We start with complex dimension~$1$.
-The usual scalar field theory can be written as 
-\[
-\int_{\Sigma} \phi \wedge \del \dbar \phi, 
-\]
-where $\Sigma$ is a Riemann surface.
-This theory is not holomorphic, but we can force it to be by demanding the constraint $\dbar \phi = 0$.
-Importantly, this constraint is \textit{not} imposed by an equation of motion.
-When we impose this constract, we can rewrite the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
-\beqn\label{eqn:scalar1}
-\int_\Sigma \alpha \wedge \dbar \del^{-1} \alpha ,
-\eeqn
-where $\alpha$ plays the role of $\partial \phi$.
-\owen{Am I interpreting that correctly?} 
-This is formally similar to the kinetic term in the action functional of Kodaira--Spencer theory \eqref{eqn:KS1}.
-
-There is a higher-dimensional analog of the chiral sector of the scalar field.
-Suppose that $X$ is a complex manifold of \textit{odd} dimension $2n+1$.
-The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
-\beqn
-\del \alpha = 0.
-\eeqn
-Note that when $n=0$, so $X$ is simply a Riemann surface~$\Sigma$, this constraint is automatic.
-The action functional is the same as~\eqref{eqn:scalar1}.
-When $n=1$ this functional is identical to the kinetic part of the Kodaira--Spencer action.\footnote{Indeed, when $X$ is a Calabi--Yau three-fold there is an isomorphism $\Omega^{2,1}(X) \cong \Omega^{0,1}(X, \T_X)$.}
-Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
-\beqn
-\int_X \|C\|^2 \op{dvol} = \int_X C \wedge \d \star \d C , 
-\eeqn
-where $C \in \Omega^{2n+1}(X)$.
-For more details we refer to~\cite{GRWwzw}.
-
 \subsection{Perturbative field theory as derived deformation theory}
@@
 so that in the final subsection, we can rapidly sketch these higher Kac-Moody and Weyl algebras.
+
+\owen{In this section, or maybe the next, we should mention the recent papers by physicists (notably Gaiotto) about higher bracket structures, and we should indicate how to connect with our approach here.}
 
@@
 
+\subsection{No divergences}
+
 We will allow graphs with finitely many vertices and edges, 
@@
 \owen{It would be good to explain why and indicate what is the appropriate "value" to use.}
+
+\subsection{Anomalies that obstruct quantization}
 

### 2024-09-20 draft.tex
tweaked BCOV subsection

@@
 The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
-Formulating the action functional to obtain this equation of motion is a little involved.
-
-The action functional is similar to the Chern--Simons action:
-\beqn\label{eqn:KS1}
-S(\mu) = \int_X \left( \frac12 \mu\, \dbar \del^{-1} \mu + \frac13 \mu \wedge \mu \wedge \mu \right) .
-\eeqn
-\owen{Honestly I don't understand this formula. We need to unpack it more slowly in terms of explicit complex geometry.}
-To make sense of this, 
-note that $\Omega \in \Omega^{3,0}(X)$ and $\mu^3 \in \Omega^{0,3}(X, \cT^{\otimes 3})$.
-In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
-The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
-Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
-Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
-Setting aside the apparent global issues, 
-we apply formal variational calculus to this action to obtain the equation of motion.
+Formulating the action functional to obtain this equation of motion is a little involved, 
+and we refer to \cite{CLbcov1} for a systematic discussion.
+
+\begin{rmk}
+The kinetic term has the form
+\[
+\int_X \frac12 \mu\, \dbar \del^{-1} \mu
+\]
+and hence resembles the chiral sector of the scalar, which we just discussed.
+\end{rmk}
 

### 2024-09-20 draft.tex
not sure this is worth it

--- 2024-09-20 draft.tex
@@
 
-\epigraph{\itshape The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
+\epigraph{The mathematical language of classical physics is based upon real numbers \dots  The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
 
@@
 
+\owen{We discussed having the following:
+\begin{itemize}
+\item Quick overview for topological field theories (=analytic content is de Rham complex): 
+\begin{itemize}
+\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
+\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
+\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
+\end{itemize} 
+\item Overview the history of the holomorphic case, with citations
+\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
+\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
+\end{itemize}}
+
+\owen{Old copy that might be recycled into final version}
+
+So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
+In the topological setting, renormalization is very well-controlled.
+The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
+
+In other words, by a judicious choice of gauge-fixing, 
+we find that the one-loop Feynman diagrams have no UV divergences.
+Moreover, no higher loop diagrams appear (for combinatorial reasons),
+and the action functional satisfies the quantum master equation.
+See Section~\ref{sec: susytwist revisited} for some further discussion.
+
+Although holomorphic field theories had already appeared in practice,
+my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
+He did the following:
+\begin{itemize}
+\item established key analytic results about holomorphic renormalization, 
+showing that it is highly manageable, with no counterterms to 1-loop; and
+\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
+\end{itemize}
+These apply to all holomorphic theories on $\CC^n$,
+but the techniques typically extend to more general complex manifolds.
+
+\brian{Brian's stuff below}
+
 The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.

### 2024-09-20 draft.tex
prophylactic protection from bad merges

--- 2024-09-20 draft.tex
@@
 
-\owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum}
+\owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum, Natalie Paquette, Nik Garner}
 

### 2024-09-20 draft.tex
adding bw stuff AGAIN

--- 2024-09-20 draft.tex
@@
 There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
-In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
+In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
 
-Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
+Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme that is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!

### 2024-09-26 draft.tex
update

@@
 Let $X$ be an algebraic variety defined over $\CC$, equipped with a symplectic form $\omega_X$.
-Then we posit for the relevant phase space, the ``symplectic space'' $LX$---the formal loop space of $X$.
+Then we posit for the relevant phase space, the ``symplectic space'' $LX$---the formal loop space of~$X$.
 This is the space of maps $\Hat{D}^\times \to X$ from the formal punctured disk to $X$.
@@
 
-The subspace of ``contractible formal loops" $V[[z]]$ inside $V((z))$ produces a module for $\cO(V((z)))$ given by $\cO(V[[z]])$. 
+The subspace of ``contractible formal loops'' $V[[z]]$ inside $V((z))$ produces a module for $\cO(V((z)))$ given by $\cO(V[[z]])$. 
 (This module is in fact a quotient algebra.)
@@
 
+We were driven, so far, by an example which started from the same data as in the non-holomorphic---the data of a symplectic vector space $V$.
+For another very natural example, one can consider a vector space $U$ which is equipped with a \textit{symmetric} pairing $\<-,-\>_U$.
+Then, the loop space $L(U^*)$ is equipped with a bivector
+\beqn
+(f,g) \mapsto \underset{z=0}{\text{Res}} \, \<f, \del g\>_U .
+\eeqn
+Notice that this bivector does \textit{not} correspond to a symplectic form, but nevertheless we can contemplate the deformation quantization of the $\infty$-dimensional Poisson space $L(U^*)$---or, more invariantly, the space of one-forms on the formal disk with values in $U^*$.
+The quantization of this Poisson algebra is the algebra with linear generators $f,g \in U((z))$ satisfying the relation
+\beqn
+[f,g] = \<f, \del g\>_U .
+\eeqn
+In the case $U=\C$, this is the associative algebra underlying the free chiral boson CFT.
+
 Let us briefly comment on how symmetries extend to the holomorphic setting.
@@
 but it requires a first step in the direction of derived geometry.
+The main idea is that we want to replace the algebra of Laurent series of a single variable with an appropriate algebra involving more than one variable.
 
@@
 
-\owen{We discussed having the following:
-\begin{itemize}
-\item Quick overview for topological field theories (=analytic content is de Rham complex): 
-\begin{itemize}
-\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
-\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
-\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
-\end{itemize} 
-\item Overview the history of the holomorphic case, with citations
-\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
-\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
-\end{itemize}}
-
-\owen{Old copy that might be recycled into final version}
-
-So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
-In the topological setting, renormalization is very well-controlled.
-The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
-
-In other words, by a judicious choice of gauge-fixing, 
-we find that the one-loop Feynman diagrams have no UV divergences.
-Moreover, no higher loop diagrams appear (for combinatorial reasons),
-and the action functional satisfies the quantum master equation.
-See Section~\ref{sec: susytwist revisited} for some further discussion.
-
-Although holomorphic field theories had already appeared in practice,
-my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
-He did the following:
-\begin{itemize}
-\item established key analytic results about holomorphic renormalization, 
-showing that it is highly manageable, with no counterterms to 1-loop; and
-\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
-\end{itemize}
-These apply to all holomorphic theories on $\CC^n$,
-but the techniques typically extend to more general complex manifolds.
-
-\brian{Brian's stuff below}
-
-The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.
+Renormalization is a key ingredient in Riemannian or Lorentzian quantum field theories.
 One can apply the same sort of techniques to produce holomorphic quantum field theories, and the higher algebraic structures associated to them.
@@
 Nevertheless, it is known that the renormalization for holomorphic field theories is equally well-behaved.
+
+\subsection{Heat kernel renormalization for holomorphic field theories}
 

### 2024-09-26 draft.tex
redid section 2

--- 2024-09-20 draft.tex
@@
 and this derived moduli space encodes solutions to
-a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it's due to the original notation people used.}
+a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it is due to the original notation people used.}
 Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
@@
 
-The standard example of a scalar field theory is the free massless exists on any Riemannian manifold,
-which we met in Example~\ref{eg: massless scalar}.
-Here the field $\phi$ a smooth function on a manifold $M$,
-its action functional is $\int_M \phi \Delta \phi$, where $\Delta$ is the Laplace-Beltrami operator, 
-and its equation of motion is $\Delta \phi = 0$.
-The moduli space of solutions is then the space of harmonic functions on~$M$
-
-When $M$ is two-dimensional and oriented,
+We met the standard example of a scalar field theory in Example~\ref{eg: massless scalar},
+where the field $\phi$ a smooth real-valued function on a manifold $M$
+and the equation of motion is $\Delta \phi = 0$,
+so that the moduli space of solutions is the space of harmonic functions on~$M$.
+
+A natural analogue is to have the field be a complex-valued function $\gamma$ on a complex manifold $M$ with an equation of motion $\dbar \gamma = 0$,
+so that the moduli space of solutions is the space of holomorphic functions on~$M$.
+
+Notice that we are shifting from a second-order differential operator $\Delta$ to first-order differential operators $\dbar$.
+Reworking a theory to express its equations of motion using first-order operators is sometimes called the first-order formalism.
+
+We will start with $M$ being a Riemann surface for simplicity.
+Consider the action functional
+\beqn
+\label{eqn: 1d betagamma}
+\int \beta \wedge \dbar \gamma
+\eeqn
+where $\beta$ is a $(1,0)$-form on $M$.\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
+which we now think about as having its own degrees of freedom. 
+\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
+Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
+so that $\beta$ should be a holomorphic $1$-form.
+
+It should seem reasonable to view two solutions $\beta_1$ and $\beta_2$ as equivalent if they differ by a $\dbar$-exact term.
+If one imposes this equivalence relation (a kind of ``gauge symmetry''),
+then one is on the path towards setting up the theory in the Batalin-Vilkovisky formalism.
+
+Derived geometry is the mathematical version of BV formalism.
+From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
+\[
+T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\cT^{*{1,0}}),
+\]
+a rather natural space to study in complex geometry.
+
+\begin{rmk}
+It is possible to directly relate the usual massless scalar field theory to this $\beta\gamma$-system as follows.
+
+When $M$ is two-dimensional, oriented and Riemannian,
 we can view $M$ as equipped with a complex structure.
@@
 
-Notice that we have shifted from a second-order differential operator $\Delta$ to first-order differential operators $\dbar$ and~$\partial$.
-Reworking a theory to express its equations of motion using first-order operators is sometimes called the first-order formalism.
-
-The holomorphic component can be seen as arising from the following action functional,
-\beqn
-\int \beta \wedge \dbar \gamma
-\eeqn
-where $\beta$ is a $(1,0)$-form on $M$ and should be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$,
-\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}
-which we now think about as having its own degrees of freedom. 
-Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
-so that $\beta$ should be a holomorphic $1$-form.
-
-This piece of the free boson is the simplest holomorphic field theory; it is often called the $\beta\gamma$-\textit{system}.
-It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.\owen{More precise location?}
-
-It should seem reasonable to view two solutions $\beta_1$ and $\beta_2$ as equivalent if they differ by a $\dbar$-exact term.
-If one imposes this equivalence relation (a kind of ``gauge symmetry''),
-then one is on the path towards setting up the theory in the Batalin-Vilkovisky formalism.
-
-Derived geometry is the mathematical version of BV formalism.
-From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
-\[
-T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\cT^{*{1,0}}),
-\]
-a rather natural space to study in complex geometry.
-
-\begin{rmk}
-We motivated the $\beta\gamma$ system as encoding a piece of the free boson.
-There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$ system as encoding the antichiral sector of the free boson.
+The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.\owen{More precise location?}
+There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$-system encoding the antichiral sector of the free boson.
 To recover the full boson, one must couple the chiral and anti-chiral sectors.
-See \cite{Kapustin,GGW} \owen{Where?} for more details. 
+See \cite{Kapustin,GGW} \owen{Where?} for more details.~\hfill$\Diamond$
 \end{rmk}
@@
 
-It is straightforward to modify the example above to allow super-holomorphic vector bundles,
+It is straightforward to modify the example above to allow holomorphic {\it super} vector bundles,
 i.e., holomorphic $\ZZ/2$-graded vector bundles.
@@
 \begin{itemize}
-\item $n = 2k+1$ is odd and
+\item $n \equiv 1 \mod 4$ (i.e., $n=4k+1$ for some $k$) and
 \item there is a line bundle $L \to X$ such that $L^{\otimes 2} \cong K_X$,
@@
 \[
-\psi \in \Omega^{0,k}(X,\Pi L),
+\psi \in \Omega^{0,2k}(X,\Pi L),
 \]
@@
 \[
-\Omega^{0,\bullet}(X, \Pi L)[k]
-\]
-presents a derived stack that should be viewed as the moduli of solutions for this theory.
-
-\owen{What do you think of this example?}
+\Omega^{0,\bullet}(X, \Pi L)[2k]
+\]
+presents a derived super stack that should be viewed as the moduli of solutions for this theory.
+
+\owen{I think I got the dimension condition correct. Can you double-check?}
 
@@
 \eeqn
-where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket 
-(which, on vector fields, is simply the Lie bracket, and is the natural multilinear extension to polyvector fields).
+where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket.\footnote{On vector fields, $[-,-]_{SN}$ is simply the Lie bracket, and it is the natural multilinear extension to polyvector fields.}
 The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
@@
 \]
-and hence resembles the chiral sector of the scalar, which we just discussed.
+and hence resembles the chiral sector of the scalar, which we just discussed in the preceding example.
 \end{rmk}

### 2024-09-26 draft.tex
just making sure it is all up to date

@@
 actually has holomorphic maps into $T^* \CC^n$ as the space of solutions.
-The algebraic maps are precisely $T^* \CC^n$-valued Laurent polynomials.
-\footnote{One can extract the algebraic model from the holomorphic model by taking formal power series expansions at the level of observables.}
+The algebraic maps are precisely $T^* \CC^n$-valued Laurent polynomials.\footnote{One can extract the algebraic model from the holomorphic model by taking formal power series expansions at the level of observables.}
 

### 2024-09-26 draft.tex
s 6

@@
 \def\owen#1{{\textcolor{violet!50!black}{OG: {#1}}}}
+
+%%% TIKZ STUFF
+\usepackage{tikz,tikz-cd}
+\usetikzlibrary{arrows,shapes}
+\usetikzlibrary{trees}
+\usetikzlibrary{matrix,arrows}
+\usetikzlibrary{positioning}
+\usetikzlibrary{calc,through}
+\usetikzlibrary{decorations.pathreplacing}
+\usepackage{pgffor}
+
+%%Feynman diagrams
+\usetikzlibrary{decorations.pathmorphing}
+\usetikzlibrary{decorations.markings}
+\tikzset{
+	% >=stealth', %%  Uncomment for more conventional arrows
+    vector/.style={decorate, decoration={snake}, draw},
+	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
+	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
+    fermion/.style={draw=black, postaction={decorate},
+        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
+    fermionbar/.style={draw=black, postaction={decorate},
+        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
+    fermionnoarrow/.style={draw=black},
+    gluon/.style={decorate, draw=black,
+        decoration={coil,amplitude=4pt, segment length=5pt}},
+    scalar/.style={dashed,draw=black, postaction={decorate},
+        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
+    scalarbar/.style={dashed,draw=black, postaction={decorate},
+        dwecoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
+    scalarnoarrow/.style={dashed,draw=black},
+    electron/.style={draw=black, postaction={decorate}/,
+        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
+	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
+}
 
@@
 \label{eg: holCS}
-\owen{This feels rather convoluted. Can we make it simpler?}
 Pick a {\em complex} Lie group $G$, 
@@
 in other words, $M$ is a Calabi--Yau manifold.
-(This condition is analogous to being an oriented 3-manifold.)
+(This condition is analogous to being an \textit{oriented} 3-manifold.)
 Given a smooth principal $G$-bundle $P \to M$,
@@
 
-There is a special class of fermionic theories that is quite interesting.
-Let $X$ be a complex $n$-fold where
+There is another class of fermionic theories that is quite interesting as they are more fundamental than the previous example.
+Let $X$ be a complex $n$-fold and $L \to X$ a line bundle on $X$ such that
 \begin{itemize}
 \item $n \equiv 1 \mod 4$ (i.e., $n=4k+1$ for some $k$) and
-\item there is a line bundle $L \to X$ such that $L^{\otimes 2} \cong K_X$,
-i.e., $L$ is a square root of the canonical bundle.
+\item $L$ is a square root of the canonical bundle $L^{\otimes 2} \cong K_X$.
 \end{itemize}
@@
 \]
-the action functional is
-\[ 
-\int_X \psi \wedge \dbar \psi,
-\]
-and the equation of motion is
-\[
-\dbar \psi = 0.
-\]
-We suggest to identify solutions that differ by $\dbar$-exact terms.
+and the action functional is
+\[ 
+\int_X \psi \wedge \dbar \psi .
+\]
+The equation of motion for this system is simply $\dbar \psi = 0$.
+To study the quantization of this system, it is necessary to identify solutions that differ by $\dbar$-exact terms (and identifying identifications that differ by $\dbar$-exact terms, etc.).
 
@@
 presents a derived super stack that should be viewed as the moduli of solutions for this theory.
-
-\owen{I think I got the dimension condition correct. Can you double-check?}
 
@@
 
-There is a natural generalization of the $\beta\gamma$ system to a $\sigma$ model.
+There is a natural generalization of the $\beta\gamma$ system to a $\sigma$-model.
 Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
@@
 The equations of motion are
-\[
-F_A^{0,2} = \dbar A + \frac12 [A,A] = 0 \text{ and } \dbar B + [A,B] = 0.
-\]
-A solution to the first equation provides is a $\dbar$-connection 
+\begin{align*}
+F_A^{0,2} = \dbar A + \frac12 [A,A] & = 0 \\
+ \dbar B + [A,B] & = 0.
+\end{align*}
+A solution to the first equation provides a new $\dbar$-connection 
 \[
@@
 \]
-on the underlying smooth bundle $P\to X$, 
-\owen{Am I doing that right? I believe a choice of holomorphic structure on $P$ automatically determines a Dolbeault operator, or $\dbar$-connection.}
-and a solution to the second equation is a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle associated to~$\dbar_A$.
+on $P$.
+A solution to the second equation is a $\dbar_A$-flat $(n,n-2)$-form-valued section of the coadjoint bundle.
 This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.
@@
 with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
-A physicist might also recognize this action functional as a holomorphic analog of topological $BF$ theory. 
+One also recognizes this action functional as a holomorphic analog of topological $BF$ theory. 
 \end{rmk}
@@
 at least perturbatively.
-For example, in \cite{semichiral} it is shown that on $X = \C^2$ 
+For example, in \cite[\S3.2]{semichiral} it is shown that on $X = \C^2$ 
 the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
 More precisely, to first-order in perturbation theory, 
-the stress tensor has a divergence-free component that is cohomologically trivial. 
-In other words, the quantum theory appears to be ``invariant'' under divergence-free vector fields,
+the divergence-free component of the stress tensor is rendered cohomologically trivial at one-loop in perturbation theory.
+In other words, the quantum theory appears to be totally ``invariant'' under divergence-free vector fields,
 although not all vector fields (as in the case of a TFT).
-\owen{Add specific location in text.}
 \end{rmk}
@@
 this constraint is automatic.)
-The action functional is the same as~\eqref{eqn:scalar1}.
+The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
 Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
@@
 For more details we refer to~\cite{GRWwzw}.
+
+The reader may (and should) be concerned with the apparent `non-local' form of the action functional in \eqref{eqn:scalar1}.
+This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint \cite{CLbcov1}.
 
@@
 %In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
-Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
+Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega$ the holomorphic volume form.
 The primary field of Kodaira-Spencer theory is 
@@
 a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
-In contrast to examples above, a constraint is imposed on these sections:
+A constraint is imposed on these sections:
 we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
@@
 In short, the fields are divergence-free vector fields.
-The equation of motion is 
+The classical equation of motion is 
 \beqn
@@
 \begin{rmk}
-The kinetic term has the form
-\[
-\int_X \frac12 \mu\, \dbar \del^{-1} \mu
+The kinetic term of this theory has the form
+\[
+\int_X \Omega \wedge \left[\Omega \vee \left(\frac12 \mu\, \dbar \del^{-1} \mu\right) \right]
 \]
@@
 The PDE does not involve the choice of a holomorphic volume form $\Omega$ or a pairing on the Lie algebra $\fg$, 
-but the action functional did.
+but the action functional does.
 
@@
 \[
-\langle -,-\rangle: V \otimes V \to K_X
+\langle -,-\rangle \colon V \otimes V \to K_X
 \]
@@
 \[
-\langle f, [g,h] \rangle = (-1)^{|f|} \langle h,  \rangle
+\langle f, [g,h] \rangle = (-1)^{|f|} \langle [g,f],h \rangle
 \]
@@
 \end{itemize}
-\owen{We must check the signs. And am I missing anything?}
 \end{dfn}
@@
 Such definitions can be found in~\cite{CG2}.
-
-\owen{What else to say?}
 
@@
 \item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
-For instance, holomorphic BF theory on (super) twistor space associated to $\RR^4$ is equivalent to a self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
+For instance, the Penrose corresponds relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
 \end{itemize}
@@
 \owen{It would be good to explain why and indicate what is the appropriate "value" to use.}
+\brian{What?}
 
@@
 It involves a sum over Feynman weights $W_\Gamma$ where $\Gamma$ is a polygon with $(d+1)$-vertices.
+
+As an example, consider holomorphic BF theory on $\C^2$, for some Lie algebra $\lie{g}$, coupled to the $\beta\gamma$ system on $\C^2$ valued in a representation $V$ of $\lie{g}$.
+There are two diagrams which contribute to the gauge anomaly, all of which come from various ways of labeling the vertices and edges of the wheel diagram with three vertices, see figure \ref{??}:
+\begin{itemize}
+\item The pure gauge anomaly.
+This part of the anomaly is proportional to the representation theoretic factor $\op{Tr}_{ad}(X^3)$, $X \in \lie{g}$.
+This vanishes when $\lie{g}$ is simple, for example, when $\lie{g} = \lie{sl}(n)$).
+\item This anomaly involves edges (propagators) labeled by the $\beta\gamma$ fields.
+This part of the anomaly is proportional to the representation theoretic factor $\op{Tr}_V(X^3)$, $X \in \lie{g}$.
+\end{itemize}
+These anomalies in complex two-dimensional holomorphic gauge theory are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory \cite{??}.
+In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly) we see an easy method to produce a non-anomalous holomorphic QFT: take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}
+	\begin{scope}
+%\pgfmathsetmacro{\ex}{0 }
+%\pgfmathsetmacro{\ey}{1}
+
+%\draw (\ex,\ey) ++(45:.8) arc (45:-45:.8);
+
+		\coordinate (O) at (0,0);
+		\node[draw] (ci) at (O) [circle through=(right:1)] {};
+		%\draw[fill=black] (0,0) circle (1cm);
+		%\draw[fill=white] (0,0) circle (0.99cm);
+		%\draw[line width=0.35mm,red] ++(145:0.995) arc (145:215:0.995);
+		%\node[red] at (180:0.7) {$K_\epsilon$};
+		\draw[fermion](45:2) -- (45:1);
+		\draw[fermion](180:2) -- (180:1);
+		\draw[fermion](315:2) -- (315:1);
+		\node at (45:2.2) {$A$};
+		\node at (180:2.2) {$A$};
+		\node at (315:2.2) {$A$};
+		\node at (130:1.4) {$P_{BF}$};
+		\node at (270:1.4) {$P_{BF}$};
+		\node at (0:1.4) {$P_{BF}$};
+	    	\clip (0,0) circle (1cm);
+		\end{scope}
+
+		\begin{scope}[shift={(6,0)}]
+				\coordinate (O) at (0,0);
+		\node[draw] (ci) at (O) [circle through=(right:1)] {};
+		%\draw[fill=black] (0,0) circle (1cm);
+		%\draw[fill=white] (0,0) circle (0.99cm);
+		%\draw[line width=0.35mm,red] ++(145:0.995) arc (145:215:0.995);
+		%\node[red] at (180:0.7) {$K_\epsilon$};
+		\draw[fermion](45:2) -- (45:1);
+		\draw[fermion](180:2) -- (180:1);
+		\draw[fermion](315:2) -- (315:1);
+		\node at (45:2.2) {$A$};
+		\node at (180:2.2) {$A$};
+		\node at (315:2.2) {$A$};
+		\node at (130:1.4) {$P_{\beta\gamma}$};
+		\node at (270:1.4) {$P_{\beta\gamma}$};
+		\node at (0:1.4) {$P_{\beta\gamma}$};
+	    	\clip (0,0) circle (1cm);
+ \end{scope}
+\end{tikzpicture}
+\caption{Diagrams which contribute to the anomaly in holomorphic gauge theory on $\C^2$}
+\label{fig:localization}
+\end{center}
+\end{figure}
 

### 2024-09-27 draft.tex
just looking at changes

@@
 
-In physics, the relationship between the Weyl algebra on generators $p,q$ and its loopy version $W[V]$ is through a process called `dimensional reduction'.
+In physics, the relationship between the Weyl algebra on generators $p, q$ and its loopy version $W[V]$ is by a process called {\it dimensional reduction}.
 The key idea is that to any quantum mechanical system there is an algebra of operators---the loopy version of the Weyl algebra arises from a quantum mechanical system on the infinite-dimensional space of loops in the symplectic vector space $V$.
@@
 
-We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of `compactification'. 
+We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of {\it compactification}. 
 It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
@@
 \beqn
-L_{1d}(\phi_k, k \in \ZZ) = \sum_{k\in \ZZ} \phi_{-k} \d \phi_{k} + k \phi_k \phi_{-k} \d t .
+L_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
 \eeqn 
@@
 To invest the map $\alpha$ with more meaning, 
-pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
+pick a real, closed submanifold 
+\[
+T \subset \PDisc_d(r_1, \ldots, r_n| R)
+\]
+along which one can integrate $(0,k)$-forms.
 For instance, for any inputs $a_i \in A(r_i)$, we get an element in $A(R)$~by
@@
 \[
-{\rm Map}(X , \left( \fg_\CC^*\times {\rm Crit}^d(W) \right)/ G_\CC), 
+{\rm Map}(X , [( \fg_\CC^*\times {\rm Crit}^d(W))/ G_\CC]), 
 \]
@@
 We call one side {\em electric} and the other {\em magnetic}.
-These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, which justifies our terminology.
+These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, 
+which motivates our terminology.
 
@@
 
-\begin{conj}[\cite{Eager}]
+\begin{conj*}[\cite{Eager}]
 Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
@@
 where these are the observables of the electric and magnetic theories, respectively.
-\end{conj}
+\end{conj*}
 

### 2024-09-30 draft.tex
going through early sections and tweaking

@@
 
+\owen{Add my thoughts about Manin}
+
 \section{Holomorphic field theories}
 \label{sec: HFT}
-
-\owen{I rearranged this section somewhat.
-Our discussion of examples did not involve any BRST/BV stuff, so I put it right after the impressionistic opening.
-The "definitions" section seemed to be purely perturbative and to use notions from derived geometry, so I put it next.
-It should be fleshed out a little (e.g., a mention of the "fundamental theorem of deformaiton theory" and maybe show how to write one of the examples in that language).}
 
@@
 
+\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}
+
 \subsection{A loopy version}
@@
 Let us indicate one possible answer before we motivate it from the point of view of holomorphic field theory.
-Roughly, the idea is that associated to any finite-dimensional symplectic space is another, infinite-dimensional, symplectic space of `loops' into the original symplectic space.
+Roughly, the idea is that associated to any finite-dimensional symplectic space is another, infinite-dimensional, symplectic space of ``loops'' into the original symplectic space.
 
@@
 
-In physics, the relationship between the Weyl algebra on generators $p, q$ and its loopy version $W[V]$ is by a process called {\it dimensional reduction}.
-The key idea is that to any quantum mechanical system there is an algebra of operators---the loopy version of the Weyl algebra arises from a quantum mechanical system on the infinite-dimensional space of loops in the symplectic vector space $V$.
-We will unpack this statement in the language of fields and Lagrangians.
+{\it Dimensional reduction}, an idea from physics, offers a view on how the Weyl algebra on generators $p, q$ relates to its loopy version.
+As we already discussed, mechanics (the Weyl algebra of $V$) has to do with a one-dimensional system, i.e., time-line, 
+while its loopy version ($W[V]$) has to do with a two-dimensional system, such as the punctured plane~$\CC^\times$.
+There is a familiar identification (e.g., polar coordinates)
+\[
+\CC^\times \cong \RR \times S^1
+\]
+and so
+\[
+\Map(\CC^\times,V) \cong \Map(\RR, \Map(S^1,V)) = \Map(\RR, LV).
+\]
+Dimensional reduction here means studying the two-dimensional physics as a one-dimensional system with a more complicated target, namely the loop space.\footnote{One can play this game whenever the spacetime manifold is product $X \times Y$ or a fiber bundle.
+Sometimes the term {\it compactification} is used instead, with reduction reserved for fixing the fiberwise fields to be constant.}
+There is, in this case, a kind of dual process that we call {\it chiralization},
+that turns a one-dimensional physical system (mechanics) into a holomorphic field theory.
+We will now describe this relationship in the language of fields and Lagrangians.
 
 The ordinary Weyl algebra on a symplectic vector space $V$ arises from the quantization of ordinary mechanics on the symplectic vector space $V$.
-We can also include a Hamiltonian $H \in \cO(V)$ that acts on the Weyl algebra by the commutator $[H,-]$.
-If we understand the fields of this system as smooth maps $\phi = \phi(t)$ valued in $V$, then the Lagrangian description of this system is 
-\[
-L_{1d} (\phi) = \omega(\phi , \d \phi) + H(\phi) \d t ,
+A Hamiltonian $H \in \cO(V)$ acts as a derivation of the Weyl algebra by the commutator $[H,-]$.
+The fields of this system are smooth maps $\phi = \phi(t)$ valued in $V$, 
+and the action functional is 
+\[
+S_{1d} (\phi) = \int \omega(\phi , \d \phi) + H(\phi) \d t ,
 \]
@@
 
-The chiral version of this setup is to look at fields $\phi = \phi(z,\zbar)$ valued in $V$ where $(z,\zbar) \in \CC^\times$.
+The chiralization of this setup goes as follows.
+Let a field $\phi = \phi(z,\zbar)$ be a smooth function valued in $V$, 
+where $(z,\zbar)$ are (anti)holomorphic coordinates on the manifold $\CC^\times$.
 The action functional is 
 \[
-L_{2d}(\phi) = \omega(\phi, \dbar \phi) \d z ,
+S_{2d}(\phi) = \int \omega(\phi, \dbar \phi) \d z ,
 \]
@@
 
-We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of {\it compactification}. 
-It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
-Then, compactification involves integrating out the remaining circle direction.
+{\it Reduction} goes from this holomorphic field theory to a mechanical system. 
+Take as this one-dimensional space the radial direction in $\CC^\times$.
 Concretely, any smooth function on $\CC^\times$ can be decomposed in polar coordinates as
@@
 where $\phi_k(r)$ is a smooth function depending only on the radius $r \in \RR_+$.
-Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
+Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the ``time'' parameter $t = \log r \in \RR$. 
 We interpret $\sum_{k \in \ZZ} \phi_k(r)$ as smooth map from $\RR$ to the formal loop space $LV$.
 
-At the level of Lagrangians we can integrate $L_{2d}(\phi)$ over $S^1$ to obtain the following infinite sum of one-dimensional Lagrangians
+At the level of action functionals, 
+we can integrate $S_{2d}(\phi)$ over the angular coordinate to obtain the following formal sum of one-dimensional action functionals
 \beqn
-L_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
+S_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
 \eeqn 
+\owen{The $H$ got dropped. Should we reintroduct it?}
 Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
 In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian that encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.
+
+\owen{A person might object that this isn't so well-defined analytically. Should we emphasize that it is rather formal, a kind of heuristic?}
 
@@
 
-\owen{Perhaps mention classic examples like $n$-fold loop spaces or Hochschild cohomology?}
+Examples appear very naturally from topology: for any space $X$ with a basepoint $x$, take the singular chains $C_\bu(\Omega^d X)$ of the $d$-fold based loop space $\Omega^d_x X$.
+A much more subtle source of examples was conjectured by Deligne and subsequently proven in many ways \cite{}: 
+for any associative algebra $A$, the Hochschild cochain complex ${\rm Hoch}^\bu(A,A)$ can be equipped naturally with an $E_2$-algebra structure.
 

### 2024-09-30 draft.tex
tiny changes to section 6

@@
 \begin{rmk}
-The reader fond of higher abstract nonsense will note that we could have factorization algebras take values in other target categories (or even better, $\infty$-categories),
+The reader fond of higher abstract nonsense will note that we could have prefactorization algebras take values in other target categories (or even better, $\infty$-categories),
 not just vector spaces or cochain complexes.
@@
 This generalization is fruitful.
-In the Beilinson-Drinfeld style, it leads to chiral categories, which play a key role in the geometric Langlands program.
+In the Beilinson-Drinfeld style, it leads to chiral categories, which play an important role in the geometric Langlands program.
 In the style advocated above, it would likewise be useful for capturing notions like defects or extended operators from quantum field theory.
@@
 To physicists, this claim should not be so surprising:
-the Weiss cosheaf condition offers a precise version of the idea that a quantum field theory can be fully encoded by all its $n$-point functions.
+the Weiss cosheaf condition offers a precise version of the idea that a quantum field theory can be fully encoded by all its $n$-point functions.\footnote{This idea is not seen as accurate when one takes into account some nonperturbative aspects of QFT, notably generalized global symmetries and higher-dimensional defects.
+We note that it is possible to enlarge the Weiss topology to accommodate those aspects.}
 
@@
 
-The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.
-One can apply the same sort of techniques to produce holomorphic quantum field theories, and the higher algebraic structures associated to them.
-A key feature of holomorphic theories is the absence of (possibly scheme-dependent) counterterms which can make typical quantum field theories difficult to access.
+In practice, quantum field theories are typically constructed using regularization and renormalization,
+by starting with a classical field theory specified by an action functional and then finding a way to extract sensible answers from the divergences that first appear out of the integrals associated to Feynman diagrams.
+One can apply similar techniques to produce holomorphic quantum field theories, and the higher algebraic structures associated to them.
+A key feature of holomorphic theories is the absence of counterterms (possibly scheme-dependent), 
+which can make typical quantum field theories challenging to work with.
+In this section we describe the current state of the art for renormalization and anomalies of holomorphic field theories,
+after reviewing some background and the similarly pleasant results for topological field theories.
+
+\subsection{Recollections}
 
@@
 initially conjectured by Richard Eager.
-We will point out an enrichment of this conjecture that accounts for a large symmetry enhancement that both sides of the theory enjoy after performing the holomorphic twist.
-We explain our first efforts in this direction and how it offers evidence for the conjecture;
-we then refine Eager's version.
 We also explain how this duality, when compactified along Riemann surfaces,

### 2024-09-30 draft.tex
first pass by OG through renorm section

@@
 \usepackage{epigraph}
+
+\usepackage[
+backend=biber,
+style=alphabetic,
+]{biblatex}
+\addbibresource{survey.bib}
 
@@
 \begin{cor}
+\label{cor: EllSaf}
 For any Lagrangian field theory satisfying the hypotheses of Theorem~\ref{thm: EllSaf}, 
@@
 \begin{itemize}
-\item Quick overview for topological field theories (=analytic content is de Rham complex): 
-\begin{itemize}
-\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
-\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
-\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
-\end{itemize} 
-\item Overview the history of the holomorphic case, with citations
-\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
 \item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
@@
 
-\owen{Old copy that might be recycled into final version}
-
-So far we have not discussed the issue of quantization and renormalization for holomorphic field theories.
-In the topological setting, renormalization is very well-controlled.
-The well-combed configuration space method pioneered by \cite{} has allowed for a rigorous construction of the path integral for many topological field theories.
-
-In other words, by a judicious choice of gauge-fixing, 
-we find that the one-loop Feynman diagrams have no UV divergences.
-Moreover, no higher loop diagrams appear (for combinatorial reasons),
-and the action functional satisfies the quantum master equation.
-See Section~\ref{sec: susytwist revisited} for some further discussion.
-
-Although holomorphic field theories had already appeared in practice,
-my collaborator Brian Williams was the first to lay a systematic, mathematical foundations (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}).
-He did the following:
+In practice, quantum field theories are typically constructed using regularization and renormalization,
+by starting with an action functional that defines a classical field theory and then finding a way to extract sensible answers from the yoga of Feynman diagrams (which naively produce divergent integrals).
+One can apply similar techniques to produce holomorphic quantum field theories, and the higher algebraic structures associated to them.
+A key feature of holomorphic theories is the absence of counterterms (possibly scheme-dependent), 
+which can make typical quantum field theories challenging to work with.
+In this section we describe the current state of the art for renormalization and anomalies of holomorphic field theories,
+after reviewing some background and the similarly pleasant results for topological field theories.
+
+\subsection{Overview and context}
+
+The dream is that a quantum field theory is specified by the path (or functional) integral,
+which is supposed to involve integrating a measure over the space of all fields.
+This path integral does not (usually) exist using conventional mathematical tools,
+so one mimics well-established asymptotic expansions for finite-dimensional oscillating integrals.
+Feynman explained how to label the terms in these expansions using graphs;
+there is an explicit algorithm that converts the action functional of the classical field theory into integrands (often distributional in nature) on the spacetime manifold $M$ and products $M^k$ of it.
+Unfortunately, these formal expressions are often ill-defined as they would involve multiplying distributions (and hence the putative integral would diverge).
+Regularization means a way of systematically working around these issues,
+often by adjusting the integrand or finding a clever way of extracting a finite answer.
+In short hand, one introduces {\it counterterms} that soak up the divergences and hence obtain useful values for the Feynman diagrams.
+Renormalization means assembling the data produced by the collection of Feynman diagrams to approximate the ``true'' path integral.
+
+To offer some notation, a graph $\gamma$ (whose exact shape depends on the theory) is expected to define a functional $W_\Gamma$ on the space of fields (i.e., a distribution).
+It is described, formally, by an an integral over the product manifold $M^{|V(\gamma)|}$,  
+where $V(\Gamma)$ is the vertex set of the graph.
+Unfortunately, this integrand, and the distribution it purports to encode, is often not integrable.
+
+These methods are essential --- and often quite convoluted --- for the theories that describe physical phenomena, 
+such as quantum electrodynamics,
+where Feynman first introduced his diagrammatics.
+For topological quantum field theories, like Chern-Simons theory,
+life is quite a bit simpler: Axelrod-Singer and Kontsevich developed a a very simple regularization method that removes all divergences.
+For these theories, the putative divergences always arise from distributional issues along the diagonals of the product space $M^k$.
+On the Fulton-MacPherson compactification of the configuration space of $k$ points in $M$ (i.e., takes the real blow-up along the diagonals),
+the integrand admits a {\em smooth} extension and the integrals become well-defined.\owen{Citations!}
+
+These results guarantee the existence of factorization algebras for topological field theories like Chern-Simons theory or the Poisson $\sigma$-model or the topological B-model by the main result (Theorem~\ref{main}) of \cite{CG2}.
+Thus these theories produce $E_d$ algebras by Theorem~\ref{thm: EllSaf} and Atiyah-Segal-style TFTs by Corollary~\ref{cor: EllSaf}.
+
+This configuration space method traditionally used to study topological theories does not admit an immediate generalization to holomorphic theories.
+Nevertheless, the renormalization for holomorphic field theories is equally well-behaved.
+
+Costello, inspired by the methods of Axelrod-Singer and Kontsevich,
+found a framework for perturbative renormalization that works with a large class of elliptic complexes.
+When applied to Dolbeault complexes arising in Kodaira-Spencer (or BCOV) theory, 
+he and Li found some remarkable simplifications and good behavior \cite{??}.
+In \cite{LiVertex} Li showed, by very clever analysis, that holomorphic field theories in complex dimension one (i.e., chiral conformal field theories) are finite to all orders in perturbation theory;
+this result was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
+Following up (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}), Williams laid a systematic mathematical foundations:
 \begin{itemize}
-\item established key analytic results about holomorphic renormalization, 
+\item he established key analytic results about holomorphic renormalization, 
 showing that it is highly manageable, with no counterterms to 1-loop; and
@@
 
-\brian{Brian's stuff below}
-
-In practice, quantum field theories are typically constructed using regularization and renormalization,
-by starting with a classical field theory specified by an action functional and then finding a way to extract sensible answers from the divergences that first appear out of the integrals associated to Feynman diagrams.
-One can apply similar techniques to produce holomorphic quantum field theories, and the higher algebraic structures associated to them.
-A key feature of holomorphic theories is the absence of counterterms (possibly scheme-dependent), 
-which can make typical quantum field theories challenging to work with.
-In this section we describe the current state of the art for renormalization and anomalies of holomorphic field theories,
-after reviewing some background and the similarly pleasant results for topological field theories.
-
-\subsection{Recollections}
-
-Counterterms are perturbative quantum effects that typically must be introduced to the action functional in order to circumvent ultra-violet (UV, high energy) divergences which arise when studying the path integral.
-From Feynman, we know that the path integral can be formally expressed in terms of graphs. 
-More precisely, given a graph $\Gamma$ (whose exact shape depends on the theory), there is a prescription for assigning to it a functional $W_\Gamma$ on the fields (a distribution) which we can understand as term in the quantum action; typically in the form of an integral over $|V(\Gamma)|$ copies of spacetime where $V(\Gamma)$ is the vertex set of the graph.
-Unfortunately, this prescription is not always well-posed, as there are infinities which can arise due to presence of overlapping supports of certain distributions.
-Counterterms can be constructed by carefully understanding the nature of these divergences through some regularization scheme.
-
-For topological quantum field theories, it is known from the work of Axelrod, Singer, Kontsevich, Cattaneo, and others \cite{???} that such Feynman graphs return finite answers and hence there is no need to introduce such complications.
-The method used to prove this interprets such Feynman graph integrals as integrals over configuration space and then showing that the weights $W_\Gamma$ can be extended to some compactification.
-A different regularization scheme based on the heat equation was used by Costello \cite{CosRenormPaper} to arrive at the same result for topological quantum field theories.
-
-The configuration space method traditionally used to study topological theories does not admit an immediate generalization to holomorphic theories.
-Nevertheless, it is known that the renormalization for holomorphic field theories is equally well-behaved.
-
-The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
-Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
-In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
-There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
+In the last few years,
+there has a been a buzz of recent activity on the renormalization of holomorphic field theories.
 In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
+\owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
 
-Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme that is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
+Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
@@
 and $L(\gamma)$ denote the number of leaves.
-The scheme begins with the familiar Wilsonian approach to renormalization which involves introducing an IR `cut-off' length scale $L > 0$.
-The \textit{Schwinger space} associated to a graph $\gamma$ and a length $L$ is the non-compact manifold with corners $(0,L]^{E(\gamma)}$, which we will denote $\op{Schw}(\gamma)$ below.
-The desired Feynman graph weight $W_\gamma$ of a graph $\gamma$ is obtained as the integral over  Scwhinger space.
+We fix a ``cut-off" length scale $L > 0$ that is used to remove the divergences that often come from integrating over a noncompact manifold (a so-called IR divergence), 
+which is a different kind of divergence (and much easier to resolve) than those that typically plague Feynman diagrammatics.
 
 \begin{dfn}
-For a perturbative field theory with space of fields $\cE$, there is a distribution valued in forms on Schwinger space
+The {\em Schwinger space} $\op{Schw}(\gamma)$ associated to a graph $\gamma$ and a length $L$ is the non-compact manifold with corners~$(0,L]^{E(\gamma)}$.
+\end{dfn}
+
+The desired Feynman graph weight $W_\gamma$ of a graph $\gamma$ is obtained as the integral over this Scwhinger space.
+
+\begin{dfn}
+For a perturbative field theory with space of fields $\cE$, there is a distribution valued in differential forms on Schwinger space
 \[
@@
 \]
-which we call the {\em regularized weight of $\gamma$}.
+that we call the {\em regularized weight of $\gamma$}.
 \end{dfn}
@@
 Let $\cE$ be the space of fields underlying a holomorphic field theory on $\C^n$.
-For every graph~$\gamma$, $w_{\gamma}$ has a natural smooth extension $\til {w_\gamma}$ to a compactification $\til{\op{Schw}(\gamma)}$ of Schwinger space.
-In particular, the weight
-\[
-W_\gamma \colon \cE^{L(\gamma)}_c \xto{\til{w_\gamma}}\Omega^\bu \left( \til{\op{Schw}(\gamma)} \right) \xto{\int} \C
-\]
-is a continuous linear functional on $\cE_c^{L(\gamma)}$.
+For every graph~$\gamma$, the differential form $w_{\gamma}$ has a natural smooth extension $\til {w_\gamma}$ to a compactification $\til{\op{Schw}(\gamma)}$ of Schwinger space.
+In particular, the composite
+\[
+\cE^{L(\gamma)}_c \xto{\til{w_\gamma}}\Omega^\bu \left( \til{\op{Schw}(\gamma)} \right) \xto{\int} \C
+\]
+is a continuous linear functional on $\cE_c^{L(\gamma)}$ and shows the desired weight~$W_\gamma$ is well-defined.
 \end{thm}
@@
 
-\owen{It would be good to explain why and indicate what is the appropriate "value" to use.}
-\brian{What?}
-
 \subsection{Anomalies that obstruct quantization}
 
-The discussion so far in this section was about the analytic issues which are present when trying to make the path integral precise.
-For interesting quantum field theories, like gauge theories, there is another issue which could prevent the theory from being well-posed; these are called anomalies.
-An anomaly is the measure of the failure of the quantum path integral to enjoy the same symmetries as the underlying classical field theory.
-In gauge theory, for instance, there could be an obstruction for the perturbative renormalization to be gauge invariant.
+The discussion so far concerned the analytic issues that are present when trying to make the path integral precise.
+For some quantum field theories, like gauge theories, there is another issue that could prevent the theory from being well-posed:
+these are called {\em anomalies}.
+An anomaly measures the failure of the path integral to enjoy the same symmetries as the underlying classical field theory.
+In gauge theory, for instance, the perturbative renormalization might not be gauge invariant, although the action functional is.
 In topological theories, it is known that these sort of anomalies are absent.
-For holomorphic theories, however, anomalies are present.\footnote{Anomalies in holomorphic field theory are related to, but distinct from, familiar anomalies such as `chiral anomalies' in theories of Weyl fermions.}
+\owen{I am confused by this comment. Aren't there TFTs with anomalies of some sort?}
+For holomorphic theories, however, anomalies are present.\footnote{Anomalies in holomorphic field theory are related to, but distinct from, anomalies well-known to physicists, such as ``chiral anomalies'' in theories of Weyl fermions.}
 Since renormalization is so well-behaved, however, such anomalies are amenable to explicit characterization.
 For example, at one-loop in perturbation theory, an explicit formula for such anomalies for holomorphic theories on $\C^d$ is given in \cite{Whol}.
-It involves a sum over Feynman weights $W_\Gamma$ where $\Gamma$ is a polygon with $(d+1)$-vertices.
+It involves a sum over Feynman weights $W_\Gamma$ where $\Gamma$ is a polygon with $(d+1)$~vertices.
 
 As an example, consider holomorphic BF theory on $\C^2$, for some Lie algebra $\lie{g}$, coupled to the $\beta\gamma$ system on $\C^2$ valued in a representation $V$ of $\lie{g}$.
-There are two diagrams which contribute to the gauge anomaly, all of which come from various ways of labeling the vertices and edges of the wheel diagram with three vertices, see figure \ref{??}:
+There are two diagrams which contribute to the gauge anomaly, all of which come from various ways of labeling the vertices and edges of the wheel diagram with three vertices, see figure~\ref{??}:
 \begin{itemize}
@@
 These anomalies in complex two-dimensional holomorphic gauge theory are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory \cite{??}.
-In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly) we see an easy method to produce a non-anomalous holomorphic QFT: take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
+In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly) there is an easy way to produce a non-anomalous holomorphic QFT: take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
 
@@
 
+\printbibliography
+
 \end{document}

### 2024-09-30 draft.tex
merge

--- 2024-09-30 draft.tex
@@
 
-\owen{Add my thoughts about Manin}
-
 \section{Holomorphic field theories}
 \label{sec: HFT}
+
+\owen{I rearranged this section somewhat.
+Our discussion of examples did not involve any BRST/BV stuff, so I put it right after the impressionistic opening.
+The "definitions" section seemed to be purely perturbative and to use notions from derived geometry, so I put it next.
+It should be fleshed out a little (e.g., a mention of the "fundamental theorem of deformaiton theory" and maybe show how to write one of the examples in that language).}
 
@@
 
-\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}
-
 \subsection{A loopy version}
@@
 Let us indicate one possible answer before we motivate it from the point of view of holomorphic field theory.
-Roughly, the idea is that associated to any finite-dimensional symplectic space is another, infinite-dimensional, symplectic space of ``loops'' into the original symplectic space.
+Roughly, the idea is that associated to any finite-dimensional symplectic space is another, infinite-dimensional, symplectic space of `loops' into the original symplectic space.
 
@@
 
-{\it Dimensional reduction}, an idea from physics, offers a view on how the Weyl algebra on generators $p, q$ relates to its loopy version.
-As we already discussed, mechanics (the Weyl algebra of $V$) has to do with a one-dimensional system, i.e., time-line, 
-while its loopy version ($W[V]$) has to do with a two-dimensional system, such as the punctured plane~$\CC^\times$.
-There is a familiar identification (e.g., polar coordinates)
-\[
-\CC^\times \cong \RR \times S^1
-\]
-and so
-\[
-\Map(\CC^\times,V) \cong \Map(\RR, \Map(S^1,V)) = \Map(\RR, LV).
-\]
-Dimensional reduction here means studying the two-dimensional physics as a one-dimensional system with a more complicated target, namely the loop space.\footnote{One can play this game whenever the spacetime manifold is product $X \times Y$ or a fiber bundle.
-Sometimes the term {\it compactification} is used instead, with reduction reserved for fixing the fiberwise fields to be constant.}
-There is, in this case, a kind of dual process that we call {\it chiralization},
-that turns a one-dimensional physical system (mechanics) into a holomorphic field theory.
-We will now describe this relationship in the language of fields and Lagrangians.
+In physics, the relationship between the Weyl algebra on generators $p,q$ and its loopy version $W[V]$ is through a process called `dimensional reduction'.
+The key idea is that to any quantum mechanical system there is an algebra of operators---the loopy version of the Weyl algebra arises from a quantum mechanical system on the infinite-dimensional space of loops in the symplectic vector space $V$.
+We will unpack this statement in the language of fields and Lagrangians.
 
 The ordinary Weyl algebra on a symplectic vector space $V$ arises from the quantization of ordinary mechanics on the symplectic vector space $V$.
-A Hamiltonian $H \in \cO(V)$ acts as a derivation of the Weyl algebra by the commutator $[H,-]$.
-The fields of this system are smooth maps $\phi = \phi(t)$ valued in $V$, 
-and the action functional is 
-\[
-S_{1d} (\phi) = \int \omega(\phi , \d \phi) + H(\phi) \d t ,
+We can also include a Hamiltonian $H \in \cO(V)$ that acts on the Weyl algebra by the commutator $[H,-]$.
+If we understand the fields of this system as smooth maps $\phi = \phi(t)$ valued in $V$, then the Lagrangian description of this system is 
+\[
+L_{1d} (\phi) = \omega(\phi , \d \phi) + H(\phi) \d t ,
 \]
@@
 
-The chiralization of this setup goes as follows.
-Let a field $\phi = \phi(z,\zbar)$ be a smooth function valued in $V$, 
-where $(z,\zbar)$ are (anti)holomorphic coordinates on the manifold $\CC^\times$.
+The chiral version of this setup is to look at fields $\phi = \phi(z,\zbar)$ valued in $V$ where $(z,\zbar) \in \CC^\times$.
 The action functional is 
 \[
-S_{2d}(\phi) = \int \omega(\phi, \dbar \phi) \d z ,
+L_{2d}(\phi) = \omega(\phi, \dbar \phi) \d z ,
 \]
@@
 
-{\it Reduction} goes from this holomorphic field theory to a mechanical system. 
-Take as this one-dimensional space the radial direction in $\CC^\times$.
+We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of `compactification'. 
+It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
+Then, compactification involves integrating out the remaining circle direction.
 Concretely, any smooth function on $\CC^\times$ can be decomposed in polar coordinates as
@@
 where $\phi_k(r)$ is a smooth function depending only on the radius $r \in \RR_+$.
-Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the ``time'' parameter $t = \log r \in \RR$. 
+Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
 We interpret $\sum_{k \in \ZZ} \phi_k(r)$ as smooth map from $\RR$ to the formal loop space $LV$.
 
-At the level of action functionals, 
-we can integrate $S_{2d}(\phi)$ over the angular coordinate to obtain the following formal sum of one-dimensional action functionals
+At the level of Lagrangians we can integrate $L_{2d}(\phi)$ over $S^1$ to obtain the following infinite sum of one-dimensional Lagrangians
 \beqn
-S_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
+L_{1d}(\phi_k, k \in \ZZ) = \sum_{k\in \ZZ} \phi_{-k} \d \phi_{k} + k \phi_k \phi_{-k} \d t .
 \eeqn 
-\owen{The $H$ got dropped. Should we reintroduct it?}
 Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
 In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian that encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.
-
-\owen{A person might object that this isn't so well-defined analytically. Should we emphasize that it is rather formal, a kind of heuristic?}
 
@@
 
-Examples appear very naturally from topology: for any space $X$ with a basepoint $x$, take the singular chains $C_\bu(\Omega^d X)$ of the $d$-fold based loop space $\Omega^d_x X$.
-A much more subtle source of examples was conjectured by Deligne and subsequently proven in many ways \cite{}: 
-for any associative algebra $A$, the Hochschild cochain complex ${\rm Hoch}^\bu(A,A)$ can be equipped naturally with an $E_2$-algebra structure.
+\owen{Perhaps mention classic examples like $n$-fold loop spaces or Hochschild cohomology?}
 
@@
 To invest the map $\alpha$ with more meaning, 
-pick a real, closed submanifold 
-\[
-T \subset \PDisc_d(r_1, \ldots, r_n| R)
-\]
-along which one can integrate $(0,k)$-forms.
+pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
 For instance, for any inputs $a_i \in A(r_i)$, we get an element in $A(R)$~by
@@
 
-\subsection{Toric (KK) reduction vs. chiralization}
-
-\owen{revisit this theme, and discuss the "modes" algebra}
+\subsection{Compactification and conformal blocks}
+
+In this subsection we discuss some global aspects of holomorphic factorization algebras.
+
+A map $f \colon X \to Y$ induces a pushforward between categories of factorization algebras.
+If $\cF$ is a factorization algebra on $X$, then the pushforward $f_* \cF$ is the factorization algebra on $Y$ which assigns to an open set $U \subset Y$ the value $\cF(f^{-1}(U))$.
+Suppose we are in the situation where $\cF$ is the factorization algebra of observables of some quantum field theory on $X$.
+In the case that $f$ is a smooth map with compact fibers, then $f_* \cF$ is the factorization algebra of observables for the \textit{compactification} of the quantum field theory along $f$.
+In the case $f \colon Z \times Y \to Y$ is the projection, one says that $f_* \cF$ is the compactification of $\cF$ along $Z$.
+
+Another special case of this is when $f$ is the map $X \to \star$.
+Then $f_* \cF = \int_X \cF$ is the global sections of the factorization algebra $\cF$ along $X$.
+In the case that $\cF$ is a locally constant factorization algebra this agrees with the factorization homology of $\cF$ along $X$.
+In the case that $\cF$ is a holomorphic factorization algebra on a Riemann surface $\Sigma$, the object $\int_\Sigma \cF$ is closely related to the chiral homology (or conformal blocks) of the chiral (or vertex) algebra associated to $\cF$ along $\Sigma$.
+
+In this way, when $X$ is a general complex manifold and $\cF$ is a holomorphic factorization algebra, then $\int_X \cF$ is a natural higher-dimensional generalization of the notion of conformal blocks of $\cF$.
+
+\brian{Hopf surfaces}
 
@@
 \[
-{\rm Map}(X , [( \fg_\CC^*\times {\rm Crit}^d(W))/ G_\CC]), 
+{\rm Map}(X , \left( \fg_\CC^*\times {\rm Crit}^d(W) \right)/ G_\CC), 
 \]
@@
 We call one side {\em electric} and the other {\em magnetic}.
-These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, 
-which motivates our terminology.
+These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, which justifies our terminology.
 
@@
 
-\begin{conj*}[\cite{Eager}]
+\begin{conj}[\cite{Eager}]
 Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
@@
 where these are the observables of the electric and magnetic theories, respectively.
-\end{conj*}
+\end{conj}
 

### 2024-09-30 draft.tex
hopf

@@
 
-Associative algebras arise in quantum mechanics, we have argued, because the spacetime of a mechanical system is a line (``time'').
+Associative algebras arise in quantum mechanics, we have argued, because the spacetime of a mechanical system is a line (``time'').\footnote{In the context of holomorphic field theory on $\C^n$, we have treated the radial direction as the ``time''.}
 If we organize the observables (or operators) by when they happen in time,
@@
 A natural question to ask then is what kind of higher algebraic structure captures how observables behave for theories in higher dimensions?
-The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in Section~\ref{sec fact alg},
+The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in \S~\ref{sec fact alg},
 but there are nice answers for two special classes of theories that we will develop now:
@@
 
+There is an explicit model for an algebra over the cohomology of the $E_d$-operad called a $P_d$-algebra.
+Essentially, these are graded commutative algebras with a Poisson bracket of cohomological degree $-d+1$.
+In \cite{CostelloScheimbauer} a parallel model for the cohomology of the holomorphic $\PDisc_d$ colored operad was proposed; though the exact axioms were not written down.
+In recent work, similar models to the one given in \cite{CostelloScheimbauer} have appeared using so-called (multivariable) `$\lambda$-brackets' \cite{BGKWY,GKW}.
+This work uses such an algebraic structure to give a beautiful proposal for computing Feynman diagrams in holomorphic (and mixed holomorphic-topological) field theories (see the next section for more on renormalization within the context of holomorphic QFT).
+Such models are similar in spirit to Lie conformal algebras which use the notion of single-variable $\lambda$-bracket to encode the `singular part' of the data of a vertex algebra.
+
 \subsection{Generalizing associative algebras for topological field theories}
@@
 \end{multline}
-\owen{I don't know how to eliminate the two numbers}
-\brian{I like using multline instead of align}
 when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
@@
 
-\brian{Hopf surfaces}
+For complex manifolds, and holomorphic factorization algebras on them, we consider an explicit example that generalizes a well-known concept in complex dimension one.
+First, consider a \textit{real} one-dimensional \textit{topological} factorization algebra $\cA$.
+If we identify $\cA$ with the associative algebra that it determines, then the factorization homology $\int_{S^1} \cA$ along the circle agrees with the Hochschild cohomology of the associative algebra $\cA$.
+In other words, it is the home for all of the `traces' which the algebra $\cA$ admits.
+It is well-known that the elliptic curve, or genus one, conformal blocks of a vertex algebra $\mathbb{V}$ is the natural `home' for the characters of the vertex algebra.
+The most basic character of a conformal vertex algebra is the $q$-character defined in terms of a trace:
+\beqn
+\op{char}_{\mathbb{V}} (q) = \op{Tr}_{\mathbb{V}} (q^{L_0-c/24}) ,
+\eeqn
+where $L_0$ denotes the action of the vector field $z \del_z$.
+The shift by the central charge guarantees that for $\mathbb{V}$ conformal that this expression has nice modularity properties.
+From the point of view of factorization algebras, we can understand this trace in terms of Hochschild homology of the \textit{modes} algebra associated to $\mathbb{V}$ as introduced in \S\ref{??}.
+Indeed, suppose we know that $\mathbb{V}$ corresponds to a holomorphic factorization algebra $\cF_{\mathbb{V}}$ on $\C$.
+Then, if $r \colon \C^\times \to \RR_{>0}$ is the radial projection, we have discussed how to extract the modes algebra from the one-dimensional factorization algebra $r_* \cF_{\mathbb{F}}$.
+If we further put this on the circle, we find Hochschild homology.
+Thus, for every modulus $q$ one has
+\beqn
+\int_{E_q} \cF_{\mathbb{V}} = \int_{S^1} r_* \cF_{\mathbb{V}} = \op{Hoch}(r_* \cF_{\mathbb{V}}) .
+\eeqn
+For more on this perspective see \cite{GuiLi}.
+From this point of view we hope it is clear how the factorization homology along an elliptic curve encodes characters in the sense of vertex algebras.
+
+In higher dimensions we can build a similar picture.
+The simplest so-called \textit{Hopf manifolds} are complex manifolds of the form
+\beqn
+H_{\mathbf{q}} = \left(\C^d - \{0\}\right) \slash \left((z_1,\ldots,z_d) \sim (q_1 z_1,\ldots,q_d z_d) \right)
+\eeqn
+where $\mathbf{q} = (q_1,\ldots,q_d)$ are complex numbers satisfying $0 < |q_i| < 1$.
+For generic $\mathbf{q}$ such a complex manifold is diffeomorphic to $S^{2d-1} \times S^1$.
+The factorization homology of a holomorphic factorization algebra $\cF$ along a Hopf surface of this kind can be identified with the Hochschild homology of the associative algebra of $S^{2n-1}$-modes:
+\beqn
+\int_{H_{\mathbf{q}}} \cF \simeq \op{Hoch}(r_* \cF)
+\eeqn
+where, again, $r\colon \C^d - \{0\} \to \RR_{>0}$ is the radius.
+Thus, we see that the factorization homology $\int_{H_{\mathbf{q}}} \cF$ naturally encodes traces of the $S^{2n-1}$-mode algebra associated to $\cF$.
+In \cite{SWchar}, we have shown how an important invariant called the \textit{supersymmetric index} (or supersymmetric partition function) of a supersymmetric theory along a sphere $S^{2n-1}$ be cast into this framework at the level the holomorphic twist.
 

### 2024-10-01 draft.tex
anomaly comments

@@
 \subsection{Examples}
+\label{sec: ex of theories}
 
@@
 
-As an example, consider holomorphic BF theory on $\C^2$, for some Lie algebra $\lie{g}$, coupled to the $\beta\gamma$ system on $\C^2$ valued in a representation $V$ of $\lie{g}$.
-There are two diagrams which contribute to the gauge anomaly, all of which come from various ways of labeling the vertices and edges of the wheel diagram with three vertices, see figure~\ref{??}:
+As an example, consider holomorphic BF theory on $\C^2$ with Lie algebra $\lie{g}$
+and couple it to the $\beta\gamma$ system on $\C^2$ valued in a representation $(V, \rho)$ of $\lie{g}$.
+The action functional is
+\[
+S(A,B, \beta, \gamma) = \int \langle B, \dbar A\rangle + \frac{1}{2} \langle B, [A,A]\rangle + \langle \beta, \dbar \gamma\rangle + \langle \beta, \rho(A)\gamma\rangle,
+\]
+where the final term encodes the ``coupling'' ({\it cf}. the discussion of these theories in Section~\ref{sec: ex of theories}).
+The second and fourth terms are cubic functions of the fields,
+and they provide trivalent vertices to build graphs with.
+The first and third terms are quadratic, and they control what labels the edges of graphs.
+
+There are two diagrams that contribute to the gauge anomaly,
+shown in Figure~\ref{fig:localization}:
 \begin{itemize}
-\item The pure gauge anomaly.
-This part of the anomaly is proportional to the representation theoretic factor $\op{Tr}_{ad}(X^3)$, $X \in \lie{g}$.
-This vanishes when $\lie{g}$ is simple, for example, when $\lie{g} = \lie{sl}(n)$).
-\item This anomaly involves edges (propagators) labeled by the $\beta\gamma$ fields.
-This part of the anomaly is proportional to the representation theoretic factor $\op{Tr}_V(X^3)$, $X \in \lie{g}$.
+\item The pure gauge anomaly: it is proportional to the representation-theoretic factor $\op{Tr}_{ad}(X^3)$, $X \in \lie{g}$.
+This expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$).
+\item The mixed anomaly: its edges (propagators) are labeled by the $\beta\gamma$ fields,
+and it is proportional to the representation-theoretic factor $\op{Tr}_V(X^3)$, $X \in \lie{g}$.
 \end{itemize}
-These anomalies in complex two-dimensional holomorphic gauge theory are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory \cite{??}.
-In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly) there is an easy way to produce a non-anomalous holomorphic QFT: take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
+These each come from ways of labeling the vertices and edges of the wheel (or polygon) diagram with three vertices.
+We have described the representation-theoretic factor but there is also an analytic factor.
+\owen{Should we just write it?}
+
+These anomalies of a holomorphic gauge theory on $\CC^4$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
+In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly), 
+there is an easy way to produce a non-anomalous holomorphic QFT: 
+take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
+
+\owen{There isn't a $K$-edge on the wheel?}
 

### 2024-10-01 draft.tex
just trucking along

@@
 
+\begin{rmk}
+In the $d=1$ case there is a lovely exploration of how the highly developed theory of vertex algebras relates to this perspective in the pair of papers by Bruegmann \cite{}.
+For a discussion of how conformal nets --- an alternative formalism for chiral CFT --- relates to our perspective, see \cite{Henriques}.
+\end{rmk}
+
 Before jumping into the main story, we mention a motivation for talking about $E_d$- and $\PDisc_d$-algebras in parallel.
@@
 We expect this correspondence to bear rich fruit.
-\owen{that metaphor's a bit fruity}
 
@@
 Essentially, these are graded commutative algebras with a Poisson bracket of cohomological degree $-d+1$.
-In \cite{CostelloScheimbauer} a parallel model for the cohomology of the holomorphic $\PDisc_d$ colored operad was proposed; though the exact axioms were not written down.
-In recent work, similar models to the one given in \cite{CostelloScheimbauer} have appeared using so-called (multivariable) `$\lambda$-brackets' \cite{BGKWY,GKW}.
-This work uses such an algebraic structure to give a beautiful proposal for computing Feynman diagrams in holomorphic (and mixed holomorphic-topological) field theories (see the next section for more on renormalization within the context of holomorphic QFT).
-Such models are similar in spirit to Lie conformal algebras which use the notion of single-variable $\lambda$-bracket to encode the `singular part' of the data of a vertex algebra.
+In \cite{CostelloScheimbauer} a parallel model for the cohomology of the holomorphic $\PDisc_d$ colored operad was proposed, 
+though axioms were not written down.
+In recent work, similar models to that one have appeared,
+using the nomenclature of $\lambda$-brackets \cite{BGKWY,GKW},
+following Kac's approach in the $d=1$ setting. 
+The multivariable $\lambda$-brackets are similar in spirit to Lie conformal algebras,
+which use the notion of single-variable $\lambda$-bracket to encode the ``singular part'' of the data of a vertex algebra.
+These papers use this algebraic structure to give a beautiful proposal for computing Feynman diagrams in holomorphic (and mixed holomorphic-topological) field theories (see Section~\ref{sec: renorm} for more on renormalization within the context of holomorphic QFT).
 
@@
 Finally, we describe some special features and interesting applications of factorization algebras of holomorphic field theories.
+
+A recent survey of factorization algebras, with a focus on their role in mathematical physics, can be found in~\cite{CosGwEMP}.
 
@@
 
-\owen{Somewhere we should mention Henriques' work connecting factorization algebras with conformal nets,
-Daniel Bruegmann's thesis, and how the web of 2d CFT stuff should fit together.}
+\owen{Not sure what to put here, honestly. Maybe it should be removed.}
 
@@
 For more on this perspective see \cite{GuiLi}.
-From this point of view we hope it is clear how the factorization homology along an elliptic curve encodes characters in the sense of vertex algebras.
+From this point of view, the factorization homology along an elliptic curve encodes characters in the sense of vertex algebras.
 
@@
 Thus, we see that the factorization homology $\int_{H_{\mathbf{q}}} \cF$ naturally encodes traces of the $S^{2n-1}$-mode algebra associated to $\cF$.
-In \cite{SWchar}, we have shown how an important invariant called the \textit{supersymmetric index} (or supersymmetric partition function) of a supersymmetric theory along a sphere $S^{2n-1}$ be cast into this framework at the level the holomorphic twist.
+In \cite{SWchar}, it is shown how an important invariant called the \textit{supersymmetric index} (or supersymmetric partition function) of a supersymmetric theory along a sphere $S^{2n-1}$ be cast into this framework at the level the holomorphic twist.
 
@@
 There are two diagrams that contribute to the gauge anomaly,
-shown in Figure~\ref{fig:localization}:
+shown in Figure~\ref{fig:localization}.
+\owen{There isn't a $K$-edge on the wheel?}
+These define functions on the space of fields:
 \begin{itemize}
-\item The pure gauge anomaly: it is proportional to the representation-theoretic factor $\op{Tr}_{ad}(X^3)$, $X \in \lie{g}$.
-This expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$).
+\item The pure gauge anomaly: it is proportional to the representation-theoretic factor $\op{Tr}_{ad}(X^3)$ for  $X \in \lie{g}$, which is an invariant function of~$\fg$.
+This expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
 \item The mixed anomaly: its edges (propagators) are labeled by the $\beta\gamma$ fields,
-and it is proportional to the representation-theoretic factor $\op{Tr}_V(X^3)$, $X \in \lie{g}$.
+and it is proportional to the representation-theoretic factor $\op{Tr}_V(X^3)$ for $X \in \lie{g}$.
 \end{itemize}
@@
 We have described the representation-theoretic factor but there is also an analytic factor.
-\owen{Should we just write it?}
+\owen{Should we just write out the formulas? What we write is kind of hard to parse, as it is shorthand. I can imagine a person asking "proportional ... how?"}
 
@@
 take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
-
-\owen{There isn't a $K$-edge on the wheel?}
 
@@
 \end{tikzpicture}
-\caption{Diagrams which contribute to the anomaly in holomorphic gauge theory on $\C^2$}
+\caption{Diagrams that contribute to the anomaly in holomorphic gauge theory on~$\C^2$}
 \label{fig:localization}
@@
 initially conjectured by Richard Eager.
-We also explain how this duality, when compactified along Riemann surfaces,
+We end by sketching how this duality, when compactified along Riemann surfaces,
 should produce equivalences between different kinds of 2-dimensional B-model theories;

### 2024-10-01 draft.tex
more small changes

@@
 
-In this subsection we discuss some global aspects of holomorphic factorization algebras.
-
-A map $f \colon X \to Y$ induces a pushforward between categories of factorization algebras.
-If $\cF$ is a factorization algebra on $X$, then the pushforward $f_* \cF$ is the factorization algebra on $Y$ which assigns to an open set $U \subset Y$ the value $\cF(f^{-1}(U))$.
-Suppose we are in the situation where $\cF$ is the factorization algebra of observables of some quantum field theory on $X$.
-In the case that $f$ is a smooth map with compact fibers, then $f_* \cF$ is the factorization algebra of observables for the \textit{compactification} of the quantum field theory along $f$.
-In the case $f \colon Z \times Y \to Y$ is the projection, one says that $f_* \cF$ is the compactification of $\cF$ along $Z$.
-
-Another special case of this is when $f$ is the map $X \to \star$.
+Factorization algebras yield interesting information when their global sections are computed,
+much as sheaf cohomology is a rich source of invariants and information.
+We focus here on some global aspects of holomorphic factorization algebras,
+connecting with important results about vertex algebras and with the physical notion of compactification.
+
+A map $f \colon X \to Y$ induces a pushforward functor between categories of factorization algebras.
+If $\cF$ is a factorization algebra on $X$, 
+then the pushforward $f_* \cF$ is the factorization algebra on $Y$ that assigns the value $\cF(f^{-1}(U))$ to an open set $U \subset Y$.
+
+Consider a situation where $\cF$ is the factorization algebra of observables of a quantum field theory on $X$.
+In the case that $f$ is a smooth map with compact fibers, 
+then $f_* \cF$ is the factorization algebra of observables for the \textit{compactification} of the quantum field theory along $f$.
+In the case $f \colon Z \times Y \to Y$ is the projection, 
+one says that $f_* \cF$ is the compactification of $\cF$ along~$Z$.
+\owen{We also used the terminology "dimensional reduction" earlier, so we should call back or distinguish these ideas.}
+
+Another special case is the map $f: X \to \star$.
 Then $f_* \cF = \int_X \cF$ is the global sections of the factorization algebra $\cF$ along $X$.
-In the case that $\cF$ is a locally constant factorization algebra this agrees with the factorization homology of $\cF$ along $X$.
-In the case that $\cF$ is a holomorphic factorization algebra on a Riemann surface $\Sigma$, the object $\int_\Sigma \cF$ is closely related to the chiral homology (or conformal blocks) of the chiral (or vertex) algebra associated to $\cF$ along $\Sigma$.
-
-In this way, when $X$ is a general complex manifold and $\cF$ is a holomorphic factorization algebra, then $\int_X \cF$ is a natural higher-dimensional generalization of the notion of conformal blocks of $\cF$.
-
-For complex manifolds, and holomorphic factorization algebras on them, we consider an explicit example that generalizes a well-known concept in complex dimension one.
+In the case that $\cF$ is a locally constant factorization algebra, 
+this computation agrees with the factorization homology of $\cF$ along $X$, as defined by Ayala-Francis and Lurie \cite{}.
+In the case that $\cF$ is a holomorphic factorization algebra on a Riemann surface $\Sigma$, 
+the global sections $\int_\Sigma \cF$ is closely related to the chiral homology (or conformal blocks) of the chiral (or vertex) algebra associated to $\cF$ along $\Sigma$.
+\owen{I want to assert "(It is the linear dual.)"}
+
+Thus, it is natural to view global sections as a higher-dimensional generalization of the notion of conformal blocks.
+That is, when $X$ is any complex manifold and $\cF$ is a holomorphic factorization algebra on $X$, 
+then $\int_X \cF$ plays the role of conformal blocks.
+One can then ask for analogs in higher dimensions of important results involving Riemann surfaces and vertex algebras.
+We sketch here an example of how the character of a (conformal) vertex algebra relates to the conformal blocks over the moduli of elliptic curves.
+
 First, consider a \textit{real} one-dimensional \textit{topological} factorization algebra $\cA$.
-If we identify $\cA$ with the associative algebra that it determines, then the factorization homology $\int_{S^1} \cA$ along the circle agrees with the Hochschild cohomology of the associative algebra $\cA$.
-In other words, it is the home for all of the `traces' which the algebra $\cA$ admits.
-It is well-known that the elliptic curve, or genus one, conformal blocks of a vertex algebra $\mathbb{V}$ is the natural `home' for the characters of the vertex algebra.
-The most basic character of a conformal vertex algebra is the $q$-character defined in terms of a trace:
+If we identify $\cA$ with the associative algebra that it determines, 
+then the factorization homology $\int_{S^1} \cA$ along the circle agrees with the Hochschild cohomology of the associative algebra~$\cA$.
+In other words, it is the home for all of the ``traces'' defined on the algebra~$\cA$.
+
+For a vertex algebra $\mathbb{V}$, the role of the circle is played by any elliptic curve,
+and the role of Hochschild homology is played by conformal blocks on that genus one curve. 
+Thus conformal blocks over elliptic curves provides the natural home for the characters of the vertex algebra.
+The most basic example of the character of a conformal vertex algebra is its $q$-character,
+which is defined in terms of a trace:
 \beqn
@@
 where $L_0$ denotes the action of the vector field $z \del_z$.
-The shift by the central charge guarantees that for $\mathbb{V}$ conformal that this expression has nice modularity properties.
+The shift by the central charge guarantees that this expression has nice modularity properties, i.e., we can view $q$ as parametrizing the moduli space of elliptic curves.
+\owen{Is that an ok turn of phrase?}
+
 From the point of view of factorization algebras, we can understand this trace in terms of Hochschild homology of the \textit{modes} algebra associated to $\mathbb{V}$ as introduced in \S\ref{??}.
-Indeed, suppose we know that $\mathbb{V}$ corresponds to a holomorphic factorization algebra $\cF_{\mathbb{V}}$ on $\C$.
+Indeed, suppose the conformal vertex algebra $\mathbb{V}$ arises from a holomorphic factorization algebra $\cF_{\mathbb{V}}$ on $\C$.
 Then, if $r \colon \C^\times \to \RR_{>0}$ is the radial projection, we have discussed how to extract the modes algebra from the one-dimensional factorization algebra $r_* \cF_{\mathbb{F}}$.
@@
 \eeqn
+\owen{I think $\int_{E_q}$ receives a map from $\op{Hoch}(r_* \cF_{\mathbb{V}})$ but I don't see why it's an isomorphism.
+On the other hand, given a conformal block (i.e., linear functional on $\int_{E_q}$, we can compose it with that map to define a trace on the modes algebra,
+which ought to be the character.}
 For more on this perspective see \cite{GuiLi}.
@@
 
-In higher dimensions we can build a similar picture.
-The simplest so-called \textit{Hopf manifolds} are complex manifolds of the form
+In higher dimensions we can build a similar picture,
+replacing the moduli of elliptic curves with the moduli of {\it Hopf manifolds}.
+Recall that a Hopf manifold is a quotient of the punctured affine plane
 \beqn
@@
 
-In other words, divergences do not appear.
+In other words, divergences do not appear when constructing the perturbative quantization of {\em any} holomorphic field theory on~$\CC^d$.
 
@@
 For holomorphic theories, however, anomalies are present.\footnote{Anomalies in holomorphic field theory are related to, but distinct from, anomalies well-known to physicists, such as ``chiral anomalies'' in theories of Weyl fermions.}
+(Within the context of Costello's formalism for perturbative QFT,
+these anomalies arise as obstructions to solving a Maurer-Cartan equation known as the quantum master equation.)
+
 Since renormalization is so well-behaved, however, such anomalies are amenable to explicit characterization.

### 2024-10-01 draft.tex
trying to get this bib to work

@@
 
-\usepackage{macros, setspace}
+\usepackage{macros}
 \usepackage{epigraph}
 
-\usepackage[
-backend=biber,
-style=alphabetic,
-]{biblatex}
 \addbibresource{survey.bib}
 
+\usepackage{setspace}
 \spacing{1.1}
@@
 
-%\usepackage[upint]{stix}
-
 \begin{document}
@@
 \section{What is a holomorphic field theory? Why study them?}
+
+\owen{Test references:} \cite{CG1}
 
@@
 \owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
+\brian{I think it would be more confusing to use a different term.
+But you can explain how it's the issue of `overlapping supports' of distributions; that is, it's an issue about `local integrability'.
+In fact, in their work Axelrod and Singer already use the term ultraviolet.}
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
@@
 
-The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
-\[
-{\rm Map}(X , [( \fg_\CC^*\times {\rm Crit}^d(W))/ G_\CC]), 
-\]
-where the target is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.
-
-We wish to study a holomorphic analog of supersymmetric chromodynamics.
-We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
-We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
-The matter fields will consist of two types: quarks and antiquarks.
-Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
-so $\underline{N} = \CC^N$ with its natural left action.
-\owen{That's kind of crappy notation. Let's discuss.}
-\brian{Does it help us much? Or are you trying to use this to disambiguate what $\CC^N$ means.}
+The holomorphic twist of a theory with both vector and matter multiplets can be described, globally, as a derived mapping space from $X$ to the target
+\beqn
+[( \fg_\CC^*\times {\rm Crit}^d(W))/ G_\CC] .
+\eeqn
+This is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.
+
+\textit{Supersymmetric quantum chromodynamics} (SQCD) refers to a specific sort of four-dimensional $\cN=1$ gauge theories.
+In the special, yet interesting, case that the gauge group is $G = SU(N)$ (and so $G_\CC = SL(N)$) the  matter fields consist of two types: quarks, valued in some number of copies of the fundamental (defining) representation, and antiquarks, valued in the same number of copies of the anti-fundamental (dual to the defining) representation.
+The number of fundamental representations that appear is called the number of \textit{flavors}, and will be denoted $F$.
+The number $N$ is called the number of \textit{colors}.
+The following theorem describes the holomorphic twist of SQCD (for $G = SU(N)$). 
+Henceforth, we will refer to the resulting holomorphic field theory as \textit{holomorphic QCD}.
 
@@
 
-\begin{dfn}
-A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
+\begin{thm}[\cite{ESW} \cite{SWchar}]
+The holomorphic twist of $G = SU(N)$ SQCD with $F$ flavors and super potential $W$ on $\C^2 = \RR^4$ is equivalent to the following holomorphic field theory:
 \begin{itemize}
@@
 \[
-S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag,
+S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag + \int\d^2 z \, W(Q) ,
 \]
@@
 %We will denote this theory by $\cT(N,F)$.
-\end{dfn}
+\end{thm}
+
+\begin{rmk}
+Notice that to write down the superpotential term, we are utilizing the holomorphic volume form~$\d^2 z$. 
+Relatedly, unless $W = 0$, this theory is only $\ZZ/2$-graded, so all fields are considered merely as even or odd.
+For instance the component of the gauge field $A^{0,1}$ is even while the component of the matter field $Q^{0,1}$ is odd. 
+When $W$ is homogenous one can lift the theory to a $\ZZ$-grading by making additional choices.
+\end{rmk}
 
 To formulate Seiberg duality, we will need to allow auxiliary matter fields that we call ``mesons.''
+As above, we fix $G_{\CC} = SL(N,\CC)$.
 
@@
 %, denoted $\cT(N,F, V_M, W)$, 
-is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
+is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, whose fields we denote by
 \[
@@
 \[
-S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, Q^\dag, \mu) .
-\] 
-Notice that to write down the superpotential term, we are utilizing the holomorphic volume form~$\Omega_X = \d^2 z$. 
+S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; \til W(Q, Q^\dag, \mu) .
+\] 
 \end{dfn}
@@
 Hence we use $\dbar$ rather than $\dbar_A$.
-The only coupling that the meson $\mu$ has to the other fields is through the superpotential~$W$.
-
-\begin{rmk}
-This theory is only $\ZZ/2$-graded, so all fields are considered merely as even or odd.
-For instance the component of the gauge field $A^{0,1}$ is even while the component of the matter field $Q^{0,1}$ is odd. 
-Only when $W = 0$ can one lift the theory to a $\ZZ$-grading.
-\end{rmk}
+The only coupling that the meson $\mu$ has to the other fields is through the new superpotential~$\til W$.
 
@@
 We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
+For simplicity, we don't consider any superpotential.
 \item
@@
 \beqn\label{eqn:checkW}
-\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q})
+\til W =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q})
 \eeqn
@@
 
-\subsection{A remark relating to homological projective duality}
-
-A standard maneuver used in physics is compactification:
-given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
-One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
-A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
-
-We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
-In other words, this is the $T^2$ compactification of the holomorphic theory.
-For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
-We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.
-
-Let's first consider the electric side, 
-which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
-The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
-The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
-where $z,w$ are formal loop parameters that we imagine as describing the winding of the two circles we have compactified. 
-The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
-Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
-In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
-As a derived mapping space, the moduli of solutions is given by
-\beqn
-{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
-\eeqn
-The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.
-
-On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
-What results is a Landau--Ginzburg B-model whose target is the stack
-\beqn
-\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
-\eeqn
-The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
-The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.
-
-Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
-or at least of $E_2$-algebras.
-
-\begin{conj}
-There is an equivalence of the following $E_2$ algebras:
-\begin{itemize} 
-\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
-\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
-\end{itemize}
-\end{conj}
-
-%\begin{conj}
-%There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
-%the compactifications of the electric and magnetic holomorphic QCD theories.
-%\end{conj}
-
-This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
-(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
-We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
-For instance, in this mathematical work, 
-one sees different choices of GIT quotients associated to the same stack yielding equivalent derived categories (and cousins),
-and these quotients only know about certain pieces of the stack,
-an issue we have flagged in our comparison of the moduli stack and the moduli space.
-
 \printbibliography

### 2024-10-02 draft.tex
keep on trucking

@@
 
-\owen{mention some history (e.g., Manin, Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, Kapranov, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
-
-\owen{Notation to explain: dg = differential graded, PDE = partial differential equations}
-
 \section{What is a holomorphic field theory? Why study them?}
@@
 and it continues to grow as there is a lot to explore here.
-Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, \cite{Vicedo}, \cite{BeemBZEtAl}, 
+Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, \cite{Vicedo}, \cite{BBBDN}, 
 where our own background and interests (and unfortunately, our ignorance) have shaped this list.
@@
 \owen{Is that an overly negative paragraph?}
+
+As complementary perspectives to that offered here, we recommend
+\begin{itemize}
+\item Kapranov's lectures \cite{KapLect} on factorization algebras in algebraic geometry,
+\item Costello's lectures \cite{CosScheim} on how holomorphic field theories emerge from supersymmetric theories, and
+\item a recent survey \cite{GKW} for physicists on how higher algebra appears in perturbative QFT, with a strong emphasis on the holomorphic examples.
+\end{itemize}
+Reading these would give a more well-rounded view of the subject and its possibilities.
 
@@
 \item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
-\item a system of PDE for the fields, known as the equations of motion.
+\item a system of partial differential equations (PDE) for the fields, known as the equations of motion.
 \end{itemize}
@@
 There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.\footnote{See \cite{Donaldson Thomas} for a pioneering and illuminating discussion of how to find such analogs.}
+and we now spell out some simple examples.\footnote{See \cite{Donaldson Thomas} for a pioneering and illuminating discussion of how to find such analogs.
+Nekrasov and collaborators also \owen{Say something and cite 1990s stuff.}}
 To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
@@
 
+Kapranov gave a lecture series explaining how factorization algebras fit into algebraic geometry \cite{KapLect}.
 A recent survey of factorization algebras, with a focus on their role in mathematical physics, can be found in~\cite{CosGwEMP}.

### 2024-10-02 draft.tex
merge

@@
 
-\subsection{A loopy version}
+\subsection{A loopy version: the algebra of modes}
 
@@
 If one axiomatizes the behavior of $Y$, one is led to the notion of a vertex algebra.
+The algebra $W[V]$ is known as the \textit{algebra of modes} associated to this vertex algebra.
 
@@
 \owen{The $H$ got dropped. Should we reintroduct it?}
+\brian{It's still there...}
 Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
@@
 There is a close relationship of the higher dimensional Weyl algebra to the higher dimensional $\beta\gamma$ system on $\CC^d - 0$ just as the loopy Weyl algebra is related to the $\beta\gamma$ system on~$\CC^\times$.
+In this sense, $W_d[V]$ is an example of a `mode algebra', where the modes are now parametrized by the cohomology of punctured $d$-dimensional affine space.
 
@@
 
-\owen{discuss OPE, explain the shifted Poisson structure, and mention $\lambda$-brackets}
-
-\subsubsection{From topological to holomorphic}
-
 We remark on a simple consequence of this toolkit that may nonetheless be useful:
@@
 In Section~\ref{???} we will examine another relationship --- generalizing the compactification/chiralization on $\CC$ --- that yields an $E_d$ algebra from a $\PDisc_d$-algebra.
+\brian{This is probably a trivializable PDisc algebra by degree reasons?}
+
+\brian{Maybe a better thing to say after this theorem is a `recognition' result.
+That is, given a holomorphic PDisc$_{d}$ algebra, when is it equivalent to a algebra over $E_{2d}$ (in the essential image of the functor you wrote)?
+Among possibly smaller things, this should require that the $\del_{\zbar}$'s are homotoped.}
 
@@
 where $L_0$ denotes the action of the vector field $z \del_z$.
-The shift by the central charge guarantees that this expression has nice modularity properties, i.e., we can view $q$ as parametrizing the moduli space of elliptic curves.
-\owen{Is that an ok turn of phrase?}
-
-From the point of view of factorization algebras, we can understand this trace in terms of Hochschild homology of the \textit{modes} algebra associated to $\mathbb{V}$ as introduced in \S\ref{??}.
-Indeed, suppose the conformal vertex algebra $\mathbb{V}$ arises from a holomorphic factorization algebra $\cF_{\mathbb{V}}$ on $\C$.
-Then, if $r \colon \C^\times \to \RR_{>0}$ is the radial projection, we have discussed how to extract the modes algebra from the one-dimensional factorization algebra $r_* \cF_{\mathbb{F}}$.
+The shift by the central charge guarantees that this expression has nice modularity properties, i.e., we can view $q$ as parametrizing the moduli of elliptic curves.
+
+From the point of view of factorization algebras, we can understand this trace in terms of Hochschild homology of the algebra of modes associated to $\mathbb{V}$.
+Indeed, suppose the conformal vertex algebra $\mathbb{V}$ arises from a holomorphic $S^1$-equivariant factorization algebra $\cF_{\mathbb{V}}$ on $\C$.
+If $r \colon \C^\times \to \RR_{>0}$ is the radial projection there is a procedure for extracting the associative algebra of modes from the one-dimensional factorization algebra $r_* \cF_{\mathbb{V}}$.
+Indeed, while $r_* \cF_{\mathbb{V}}$ may not be a locally constant factorization algebra, it always contains a dense subfactorization algebra which is locally constant.\footnote{To extract it, one assumes that $\cF$ is $S^1$-equivariant.
+For each interval $I \subset \RR_{>0}$ one then looks at the subspace of $\cF(\pi^{-1}(I))$ consisting of the eigenspaces for this $S^1$ action.
+The assignment of an interval $I$ to this subspace is a locally constant factorization algebra.}
+With slight abuse of notation, we will still denote $r_* \cF_{\mathbb{F}}$ the locally constant factorization algebra obtained from this compactification.
+
 If we further put this on the circle, we find Hochschild homology.
-Thus, for every modulus $q$ one has
+Thus, for each modulus~$q$ functoriality of factorization homology gives rise to a map
 \beqn
-\int_{E_q} \cF_{\mathbb{V}} = \int_{S^1} r_* \cF_{\mathbb{V}} = \op{Hoch}(r_* \cF_{\mathbb{V}}) .
-\eeqn
-\owen{I think $\int_{E_q}$ receives a map from $\op{Hoch}(r_* \cF_{\mathbb{V}})$ but I don't see why it's an isomorphism.
-On the other hand, given a conformal block (i.e., linear functional on $\int_{E_q}$, we can compose it with that map to define a trace on the modes algebra,
-which ought to be the character.}
-For more on this perspective see \cite{GuiLi}.
+\int_{S^1_{\sigma}} r_* \cF_{\mathbb{V}} = \op{Hoch}(r_* \cF_{\mathbb{V}}, \sigma) \to \int_{E_q} \cF_{\mathbb{V}} .
+\eeqn
+Here, $\sigma$ is an automorphism defined in terms of the given $S^1$-action on $\cF_{\mathbb{V}}$, and what appears on the left-hand side is the $\sigma$-twisted Hochschild homology.
+For free theories, this map is a quasi-isomorphism.
+On the other hand, given a conformal block (i.e., linear functional on $\int_{E_q} \cF_{\mathbb{V}}$) we can compose it with that map to define a trace on the modes algebra.
 From this point of view, the factorization homology along an elliptic curve encodes characters in the sense of vertex algebras.
+For more on this perspective see \cite{GuiLi}, where they carefully develop the notion of a trace for chiral/vertex algebras.
 
@@
 \beqn
-\int_{H_{\mathbf{q}}} \cF \simeq \op{Hoch}(r_* \cF)
-\eeqn
-where, again, $r\colon \C^d - \{0\} \to \RR_{>0}$ is the radius.
+\op{Hoch}(r_* \cF , \sigma) \to \int_{H_{\mathbf{q}}} \cF 
+\eeqn
+where, again, $r\colon \C^d - \{0\} \to \RR_{>0}$ is the radius and $\sigma$ is an automorphism of $\cF$ induced from the $S^1$-equivariant structure of $\cF$.
 Thus, we see that the factorization homology $\int_{H_{\mathbf{q}}} \cF$ naturally encodes traces of the $S^{2n-1}$-mode algebra associated to $\cF$.

### 2024-10-04 draft.tex
adding more refs

@@
 
-\owen{Test references:} \cite{CG1}
-
 The most important field theories in physics involve a metric on a manifold (whether Riemannian or Lorentzian), and hence geometry has long had a clear role in physics.
@@
 The relevance to this survey is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
-even when they do not admit twists to TFTs \cite{CosHol}. 
+even when they do not admit twists to TFTs \cite{CosSUSY}. 
 (The famed A- and B-models of mirror symmetry are TFTs produced by twisting supersymmetric thories.)
@@
 and it continues to grow as there is a lot to explore here.
-Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, \cite{Vicedo}, \cite{BBBDN}, 
+Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, and \cite{BBBDN}, 
 where our own background and interests (and unfortunately, our ignorance) have shaped this list.
@@
 
+\subsection{About Manin and his influence}
+
+Yuri Manin was a pioneer into this intellectual region where field theory, complex geometry, and homotopical algebra meet,
+and his work --- beyond the beautiful results --- also gestured at rich possibilities for novel and powerful forms of geometry and physics and algebra,
+summoning these possibilities towards their current unfolding today into derived geometry and operadic structures in a broad sense.
+We quote \cite{ManFrob} in our epigraph, which synthesizes stacks and operads and Frobenius structures into a beautiful and coherent view on mirror symmetry.
+His \cite{ManGauge} is rich with deep reformulations of supersymmetric field theory that connect it to complex geometry,
+and it is a source of many inspirations;
+we are also quite fond of \cite{BeiMan, ManNewDim} from roughly the same era.
+Anyone interested in mathematics and physics and, especially, their relationship will delight in~\cite{ManMP}.
+
+Beyond his writing, however, we have also benefited throughout our careers from the attitudes and atmosphere that his persona modeled and spread among mathematicians:
+a generosity with ideas but also poetry and literature, an exquisite care and sensitivity to organizing and explaining mathematics (and much else),
+and a kindness in conversation, where he brought his whole attention to you.
+While a graduate student at Northwestern, 
+OG had the unbelievable luck to overlap with Manin and thus to take several courses and have many conversations with him, 
+getting to witness the personification of the Platonic idea of mathematician as intellectual.
+We both spent extensive time, for example, at the Max Planck Institute for Mathematics,
+which is suffused with his spirit.
+We wish we had the chance to discuss the ideas from this survey with Manin;
+we offer it as a small gift in gratitude for all he shared with us.
+
 \subsection{Acknowledgements}
@@
 \owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum, Natalie Paquette, Nik Garner}
-
-\owen{Add my thoughts about Manin}
 
@@
 in a style amenable to a complex geometer,
-we suggest \cite{FreedDeligne}.
+we suggest \cite{DeligneFreed}.
 There are many other sources, such as \cite{}, because classical field theory is an old and deep subject.
 Recently there is an effort to revisit field theory with insights from derived geometry.
-See \cite{AlfonsoYoung?} for motivation and overview, 
-but for a detailed development, see \cite{Steffens}.
+See \cite{AlfonsiYoung} for motivation and overview, 
+but for a detailed development, see \cite{Steffens23, Steffens24}.
 In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
@@
 There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.\footnote{See \cite{Donaldson Thomas} for a pioneering and illuminating discussion of how to find such analogs.
-Nekrasov and collaborators also \owen{Say something and cite 1990s stuff.}}
+and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs.
+See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.
+\owen{What do you think of this?}}
 To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
@@
 We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
-and see \cite{AlfonsoYoung} and \cite{Steffens} for recent work on this topic.
+and see \cite{AlfonsiYoung} and \cite{Steffens23} for recent work on this topic.
 
@@
 at least perturbatively.
-For example, in \cite[\S3.2]{semichiral} it is shown that on $X = \C^2$ 
+For example, in \cite[\S3.2]{BGKWWY} it is shown that on $X = \C^2$ 
 the perturbative quantization of holomorphic BF theory is almost a topological field theory. 

### 2024-10-05 draft.tex
working on bib

@@
 where $C \in \Omega^{2n+1}(X)$.
-For more details we refer to~\cite{GRWwzw}.
+For more details we refer to~\cite{GRW_WZW}.
 
@@
 When applied to Dolbeault complexes arising in Kodaira-Spencer (or BCOV) theory, 
-he and Li found some remarkable simplifications and good behavior \cite{??}.
-In \cite{LiVertex} Li showed, by very clever analysis, that holomorphic field theories in complex dimension one (i.e., chiral conformal field theories) are finite to all orders in perturbation theory;
-this result was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
-Following up (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}), Williams laid a systematic mathematical foundations:
+he and Li found some remarkable simplifications and good behavior \cite{CLbcov}.
+In \cite{LiVertex} Li showed, by clever analysis, that holomorphic field theories in complex dimension one (i.e., chiral conformal field theories) are finite to all orders in perturbation theory; 
+this result was later extended to arbitrary Riemann surfaces in \cite{LiZhou}.
+Following up (cf. his thesis \cite{BWthesis} and its offshoot \cite{Wrenorm}), Williams laid a systematic mathematical foundations:
 \begin{itemize}
@@
 \end{itemize}
-These apply to all holomorphic theories on $\CC^n$,
+These apply to all holomorphic theories on~$\CC^n$,
 but the techniques typically extend to more general complex manifolds.
@@
 In fact, in their work Axelrod and Singer already use the term ultraviolet.}
+\owen{I agree that UV is a term many people use, but not among most of our target audience, which I view as algebraic geometers and higher algebra folks.
+Why not just say that we're showing no divergences appear and hence counterterms are not needed?}
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
@@
 The answer to this question has been studied by Surya Raghavendran and Philsang Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}.
-A further localization of $S$-duality has also been studied by Costello and Gaiotto \cite{CGholography}.
+A further localization of $S$-duality has also been studied by Costello and Gaiotto~\cite{CGholography}.
 
@@
 Witten initiated this vein of research for twists that are topological \cite{WittenTwist},
-and Costello advocated holomorphic twists \cite{CostelloHol}.  
-Costello and Li initiated the use of holomorphic twists to study dualities particularly in the setting of the topological B-model \cite{CLbcov1,CLbcov2,CLbcov3}, and further extended this to non-topological strings \cite{CLsugra}.
-Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
+and Costello advocated holomorphic twists \cite{CosSUSY}.  
+Costello and Li initiated the use of holomorphic twists to study dualities particularly in the setting of the topological B-model (see \cite{CLbcov} and follow ups), and further extended these ideas to non-topological strings \cite{CLsugra}.
 These ideas are extensively used in the program of twisted holography, which is growing rapidly at the moment.
 (The interested reader might track the papers that cite those we have mentioned.)
+Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
 \end{rmk}

### 2024-10-05 draft.tex
small additions

@@
 For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
-The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
+The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CLbcov, CLtypeI}.
 \item
@@
 At the level of the punctured disk this corresponds to the higher Kac--Moody algebra that is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
-This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra \cite{GWkm}.
+This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra~\cite{GWonKM}.
 
@@
 We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do.
-A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}.~\hfill $\Diamond$
+A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in~\cite{KSW}.~\hfill $\Diamond$
 \end{rmk}

### 2024-10-06 draft.tex
more ref stuff

@@
 
-The reader may (and should) be concerned with the apparent `non-local' form of the action functional in \eqref{eqn:scalar1}.
-This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint \cite{CLbcov1}.
+The reader may (and should) be concerned with the apparent ``non-local'' form of the action functional in \eqref{eqn:scalar1}.
+This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint~\cite{CLbcov}.
 
@@
 due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
-It has been pursued mathematically by Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
+It has been pursued mathematically by Costello and Li as an approach to the quantum higher genus $B$-model, starting with \cite{CLbcov} and continuing in a series of papers.
 In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
@@
 The classification of twisting supercharges is a completely algebraic question:
-see~\autocite{ESsusy} for a complete classification in dimensions from $1$ to~$10$.
+see~\autocite{EllSaf} for a complete classification in dimensions from $1$ to~$10$.
 
@@
 For a systematic discussion of how the twisted theory is defined, 
-we refer to~\autocite{CostelloHolomorphic, ESW}.
+we refer to~\autocite{CosSUSY, ESW}.
 
@@
 \begin{itemize}
-\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra.
+\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ yields an $E_2$ algebra.
 It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
-\item The Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
-\item The Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
-\item The Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$.
+(The quantization was constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies.)
+\item The Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality. 
+(The quantization was constructed, essentially, by Axelrod-Singer \cite{AxeSing1,AxeSing2} and Kontsevich \cite{KonECM} but articulated in this setting by Costello~\cite{CosBook}.) 
+\item The Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold yields an $E_3$ algebra. (The quantization was constructed by Chan, Leung, and Li~\cite{ChanLeungLi}.)
+\item The Kapustin-Witten gauge theory for oriented 4-manifolds yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$, (The quantization was constructed in~\cite{EGW}.)
 \end{itemize}
@@
 For $M = \RR$, we have already discussed how locally constant factorization algebras relate to associative algebras, starting with Example~\ref{ex:associativealgebra}.
-Lurie has shown the following vast extension of this example. (See section 5.4.5 of \cite{LurieHA}, particularly Theorem 5.4.5.9.)
+Lurie has shown the following vast extension of this example. (See section 5.4.5 of \cite{LurieHA}, particularly Theorem~5.4.5.9.)
 
@@
 This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra.
-In fact, in \cite{GLL,Si Kai and Zhengping} it is shown how BV quantization for one-dimensional quantum field theories connects with the ordinary theory of deformation quantization.
+In fact, in \cite{GLL,GLX} it is shown how BV quantization for one-dimensional quantum field theories connects with the ordinary theory of deformation quantization.
 
@@
 In the case that $\cF$ is a locally constant factorization algebra, 
-this computation agrees with the factorization homology of $\cF$ along $X$, as defined by Ayala-Francis and Lurie \cite{}.
+this computation agrees with the factorization homology of $\cF$ along $X$, as defined by Ayala-Francis and Lurie.
 In the case that $\cF$ is a holomorphic factorization algebra on a Riemann surface $\Sigma$, 
@@
 this result was later extended to arbitrary Riemann surfaces in \cite{LiZhou}.
-Following up (cf. his thesis \cite{BWthesis} and its offshoot \cite{Wrenorm}), Williams laid a systematic mathematical foundations:
+Following up (cf. his thesis \cite{Wthesis} and its offshoot \cite{Wrenorm}), Williams laid a systematic mathematical foundations:
 \begin{itemize}
@@
 
-For holomorphic field theories (and generally topological-holomorphic theories, see \cite{WWthf}) however, something remarkable happens.
+For holomorphic field theories, however, something remarkable happens.
 
@@
 In other words, divergences do not appear when constructing the perturbative quantization of {\em any} holomorphic field theory on~$\CC^d$.
+(Similar results hold for topological-holomorphic theories~\cite{WWthf}.)
 
@@
 Since renormalization is so well-behaved, however, such anomalies are amenable to explicit characterization.
-For example, at one-loop in perturbation theory, an explicit formula for such anomalies for holomorphic theories on $\C^d$ is given in \cite{Whol}.
+For example, at one-loop in perturbation theory, an explicit formula for such anomalies for holomorphic theories on $\C^d$ is given in \cite{Wrenorm}.
 It involves a sum over Feynman weights $W_\Gamma$ where $\Gamma$ is a polygon with $(d+1)$~vertices.

### 2024-10-07 draft.tex
comments

@@
 
-\subsection{Examples of holomorphic factorization algebras}
-
-\owen{Not sure what to put here, honestly. Maybe it should be removed.}
+%\subsection{Examples of holomorphic factorization algebras}
+%
+%\owen{Not sure what to put here, honestly. Maybe it should be removed.}
+%
 
@@
 one says that $f_* \cF$ is the compactification of $\cF$ along~$Z$.
-\owen{We also used the terminology "dimensional reduction" earlier, so we should call back or distinguish these ideas.}
+This is akin to the famous Kaluza--Klein compactification in physics and should not be confused with the notion of ``dimensional reduction'', which only includes some of the Kaluza--Klein fields.
 
@@
 In the case that $\cF$ is a holomorphic factorization algebra on a Riemann surface $\Sigma$, 
-the global sections $\int_\Sigma \cF$ is closely related to the chiral homology (or conformal blocks) of the chiral (or vertex) algebra associated to $\cF$ along $\Sigma$.
-\owen{I want to assert "(It is the linear dual.)"}
+the global sections $\int_\Sigma \cF$ is related to a familiar invariant within the theory of vertex/chiral algebras called the ``space of conformal blocks'' \cite[\S 8]{FBZ}.
+Precisely, the zeroth homology of $\int_\Sigma \cF$ is linearly dual to the space of (ordinary, non-derived) conformal blocks.
 
@@
 An anomaly measures the failure of the path integral to enjoy the same symmetries as the underlying classical field theory.
-In gauge theory, for instance, the perturbative renormalization might not be gauge invariant, although the action functional is.
+In gauge theory, for instance, the perturbative renormalization might not be gauge invariant, although the classical action functional is.
+Specifically, the gauge variation of a particular Feynman graph integral may be nonzero---this leads to an anomaly in the quantum theory.
 In topological theories, it is known that these sort of anomalies are absent.
@@
 
-There are two diagrams that contribute to the gauge anomaly,
-shown in Figure~\ref{fig:localization}.
-\owen{There isn't a $K$-edge on the wheel?}
-These define functions on the space of fields:
+The gauge variation of the two diagrams which contribute to the gauge anomaly are shown in Figure~\ref{fig:localization}.
+The difference between these two diagrams is how we label the internal edges: in the first diagram they are labeled by $A-B$ fields and in the second they are labeled by $\beta-\gamma$ fields.
+An anomaly can be represented by a (local) functional on the space of fields.
+In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ is of the form
+\beqn
+c \int \op{Tr}_M (A \del A \del A)
+\eeqn
+where $c$ is some nonzero constant and $M$ is some representation of $\lie{g}$ (the value of $c$ is the same for both diagrams, in this example).
+Specifically:
 \begin{itemize}
-\item The pure gauge anomaly: it is proportional to the representation-theoretic factor $\op{Tr}_{ad}(X^3)$ for  $X \in \lie{g}$, which is an invariant function of~$\fg$.
-This expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
-\item The mixed anomaly: its edges (propagators) are labeled by the $\beta\gamma$ fields,
-and it is proportional to the representation-theoretic factor $\op{Tr}_V(X^3)$ for $X \in \lie{g}$.
+\item In the first diagram the representation $M$ is the adjoint representation. 
+So, this expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
+\item In the second diagram the representation is $M = V$ (the representation which labels the $\beta-\gamma$ system).
 \end{itemize}
-These each come from ways of labeling the vertices and edges of the wheel (or polygon) diagram with three vertices.
-We have described the representation-theoretic factor but there is also an analytic factor.
-\owen{Should we just write out the formulas? What we write is kind of hard to parse, as it is shorthand. I can imagine a person asking "proportional ... how?"}
-
-These anomalies of a holomorphic gauge theory on $\CC^4$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
+Thus, the total anomaly is $c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)$.
+
+These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
 In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly), 
@@
 take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
+
+\owen{Owen's comments that I've tried to address:
+\begin{itemize}
+\item There isn't a $K$-edge on the wheel?
+\item Should we just write out the formulas? What we write is kind of hard to parse, as it is shorthand. I can imagine a person asking "proportional ... how?".
+\end{itemize}
+}
 
@@
 \end{tikzpicture}
-\caption{Diagrams that contribute to the anomaly in holomorphic gauge theory on~$\C^2$}
+\caption{Diagrams whose gauge variation contribute to the anomaly in holomorphic gauge theory on~$\C^2$}
 \label{fig:localization}
@@
 
-\begin{thm}[\cite{ESW} \cite{SWchar}]
+\begin{thm}[\cite{ESW,SWchar}]
 The holomorphic twist of $G = SU(N)$ SQCD with $F$ flavors and super potential $W$ on $\C^2 = \RR^4$ is equivalent to the following holomorphic field theory:

### 2024-10-08 draft.tex
these must be minor

--- 2024-10-06 draft.tex
@@
 where one simultaneously generalizes the circle to an arbitrary closed manifold and an algebra to a factorization algebra.
+
+\og{Discuss twist along circle by automorphism of algebra. Forward ref to example later.}
 
@@
 One might can also ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
-The answer to this question has been studied by Surya Raghavendran and Philsang Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}.
+The answer to this question has been studied by Raghavendran and Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}.
 A further localization of $S$-duality has also been studied by Costello and Gaiotto~\cite{CGholography}.

### 2024-10-08 draft.tex
merge

--- 2024-10-07 draft.tex
@@
 \setlength{\parindent}{0cm}
+\setcounter{tocdepth}{1}
 
@@
 \def\brian#1{{\textcolor{blue!75!red}{BW: {#1}}}}
-\def\owen#1{{\textcolor{violet!50!black}{OG: {#1}}}}
+\def\owen#1{{\textcolor{red!50!black}{OG: {#1}}}}
 
@@
 and it continues to grow as there is a lot to explore here.
-Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, and \cite{BBBDN}, 
+Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CosWG2,CosYangian,CosTwistor}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, and \cite{BBBDN},
 where our own background and interests (and unfortunately, our ignorance) have shaped this list.
+\brian{Maybe add more...}
 
@@
 We hope the ideas surveyed here do connect profitably to these topics.
-\owen{Is that an overly negative paragraph?}
 
@@
 we suggest \cite{DeligneFreed}.
-There are many other sources, such as \cite{}, because classical field theory is an old and deep subject.
 Recently there is an effort to revisit field theory with insights from derived geometry.
@@
 
-\subsection{Examples}
+\subsection{More examples}
 \label{sec: ex of theories}
@@
 and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs.
-See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.
-\owen{What do you think of this?}}
+See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.}
 To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
@@
 \eeqn
-where $\beta$ is a $(1,0)$-form on $M$.\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
-which we now think about as having its own degrees of freedom. 
-\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
+where $\beta$ is a $(1,0)$-form on $M$.%\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
+%which we now think about as having its own degrees of freedom. 
+%\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
 Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
@@
 Derived geometry is the mathematical version of BV formalism.
-From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
-\[
-T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\cT^{*{1,0}}),
-\]
-a rather natural space to study in complex geometry.
+From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
+\[
+T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\Omega^1_{hol}),
+\]
+where $\Omega^1_{hol}$ is the sheaf of holomorphic one-forms.
 
@@
 
-The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.\owen{More precise location?}
+The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite[Chapter 3]{Polchinski}.
 There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$-system encoding the antichiral sector of the free boson.
 To recover the full boson, one must couple the chiral and anti-chiral sectors.
-See \cite{Kapustin,GGW} \owen{Where?} for more details.~\hfill$\Diamond$
+See \cite{Kapustin:2005pt,GGW} for more details.~\hfill$\Diamond$
 \end{rmk}
@@
 
-From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
-\[
-T^*[-1] \Map_\dbar(M,N) 
-\]
-a rather natural space to study in complex geometry.
+From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
+\[
+T^*[-1] \Map_\dbar(M,N) ,
+\]
+where $\Map_\dbar(M,N)$ is the derived stack of holomorphic maps $M \to N$.
+This is a natural space to study in complex geometry.
 
@@
 It is possible to formulate holomorphic versions of higher abelian gauge theories,
-associated to moduli spaces of holomorphic $k$-gerbes with connection.
-\owen{Should we elaborate or just stop with a reference?}
+associated to moduli spaces of holomorphic $k$-gerbes with connection, see \cite{SWtensor,BWfive}.
 
@@
 Formulating the action functional to obtain this equation of motion is a little involved, 
-and we refer to \cite{CLbcov1} for a systematic discussion.
+and we refer to \cite{CLbcov} for a systematic discussion.
 
@@
 and hence may be of particular interest to physicists.
+In his work on Donaldson invariants of four-manifolds, Witten introduced the idea of a topological twist of a supersymmetric field theory \cite{WittenTwist}.
+The topological twist of a supersymmetric field theory (when it exists) can be attacked mathematically using the path integral.
+A key feature, however, of topological field theories is that they are amenable to a functorial paradigm.
+This firmly establishes their meaning and importance within pure mathematics.
+Slightly after Witten's work, the first shadows of what would later be called \textit{holomorphic twists} of supersymmetric field theories appeared, see \cite{Johansen:1994aw,Johansen:1994ud,NekThesis,Losev:1996up,Losev:1995cr,Johansen:2003hw,Eager:2018oww}.
+Originally, this work did not garner the same attention as the parallel works on topological twists; especially in mathematics.
+Much later, Costello introduced the precise notion of a holomorphic twist, and focused on examples in dimensions two and four \cite{CosSUSY}.
+The characterization of all holomorphic, topological, and mixed holomorphic-topological theories of Yang--Mills type in dimensions $2 \leq d \leq 10$ appears in \cite{ESW}.
+Holomorphic twists of more exotic quantum field theories, such as theories of supergravity and higher form gauge fields, have recently been studied in \cite{CLsugra,SWtensor,SWpure,Raghavendran:2021qbh,Eager:2021ufo,Garner:2023wrc}.
 
@@
 \item
-It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
+It is possible to make sense of Kodaira--Spencer theory outside of three complex dimensions.
 In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
-\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
+Holomorphic field theory has also appeared in applications to (twisted) holography through the lens of Koszul duality, see \cite{CLsugra, CGholography, CostelloPaquette}.
+\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall:2001dx, Berkovits:2005bt}, see also \cite{Eager:2018dsx,perspectives}, starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
 Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
 \item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
-For instance, the Penrose corresponds relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
+Such work can be viewed as extending (and enhancing) the original Penrose correspondence which relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose:1969ae, Penrose}---see \cite{adamo2018lecturestwistortheory} for a modern review.
+See \cite{Mason, Mason_2009, CostelloTwistor,Bittleston_2023,garner2024scatteringtwistoriallinedefects} for recent work on the twistor correspondence in QFT.
 \end{itemize}
-We recommend \owen{is there some other place to point?} for more discussion.
+
+We recommend \cite{bah2024panoramaphysicalmathematicsc} for more discussion and references.
 
@@
 
-\owen{In this section, or maybe the next, we should mention the recent papers by physicists (notably Gaiotto) about higher bracket structures, and we should indicate how to connect with our approach here.}
-
 \subsection{Algebras in mechanics}
@@
 describe deformations of its commutative algebra of functions to an associative algebra with the requirement that, to first order,  the commutator recovers the Poisson bracket.
-Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics (see, e.g., \owen{what?} as a starting place).
-
-Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\owen{ref the general overview}), 
+Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics.
+
+Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\ref{s:factinqft}), 
 and it might help the reader to bear in mind a variant of this question:
@@
 
-\brian{something about states}
-So far we've recalled how quantization looks like for algebras.
-There is also a quantization for modules.
-Let $L \subset M$ be a Lagrangian submanifold.
-Then, functions $C^\infty(L)$ on $L$ are naturally a module for $C^\infty(M)$.
-The Fock module $F(L)$ associated to $L$ is defined to be the quotient of
-
-\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}
+%\brian{something about states}
+%So far we've recalled how quantization looks like for algebras.
+%There is also a quantization for modules.
+%Let $L \subset M$ be a Lagrangian submanifold.
+%Then, functions $C^\infty(L)$ on $L$ are naturally a module for $C^\infty(M)$.
+%The Fock module $F(L)$ associated to $L$ is defined to be the quotient of 
+%
+%\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}
 
@@
 Dimensional reduction here means studying the two-dimensional physics as a one-dimensional system with a more complicated target, namely the loop space.\footnote{One can play this game whenever the spacetime manifold is product $X \times Y$ or a fiber bundle.
-Sometimes the term {\it compactification} is used instead, with reduction reserved for fixing the fiberwise fields to be constant.}
+Sometimes the term {\it compactification} is used instead, with reduction reserved for fixing the fiberwise fields to be constant---for a discussion of compactification within the setting of factorization algebras see Section~\ref{s:compact}.}
 There is, in this case, a kind of dual process that we call {\it chiralization},
@@
 \beqn
-S_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
-\eeqn 
-\owen{The $H$ got dropped. Should we reintroduct it?}
-\brian{It's still there...}
+S_{red}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
+\eeqn 
 Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
@@
 
-\owen{A person might object that this isn't so well-defined analytically. Should we emphasize that it is rather formal, a kind of heuristic?}
+%\owen{A person might object that this isn't so well-defined analytically. Should we emphasize that it is rather formal, a kind of heuristic?}
 
@@
 it is a graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k \colon L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi identity.
-For an overview (and an actual definition!) we recommend \owen{add citations}.
+For an overview (and an actual definition!) we recommend \cite{LV}.
 In our setting the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
@@
 A natural question to ask then is what kind of higher algebraic structure captures how observables behave for theories in higher dimensions?
-The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in \S~\ref{sec fact alg},
+The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in Section~\ref{sec: fact alg}
 but there are nice answers for two special classes of theories that we will develop now:
@@
 Essentially, these are graded commutative algebras with a Poisson bracket of cohomological degree $-d+1$.
-In \cite{CostelloScheimbauer} a parallel model for the cohomology of the holomorphic $\PDisc_d$ colored operad was proposed, 
+In \cite{CosScheim} a parallel model for the cohomology of the holomorphic $\PDisc_d$ colored operad was proposed, 
 though axioms were not written down.
@@
 so we will gloss the key ideas of operads briefly and then turn to describing the operads relevant to TFTs.
-A more extensive discussion can be found in \cite{CG1}, with \cite{ES} studying the topological setting in an elegant way.
+A more extensive discussion can be found in \cite{CG1}, with \cite{EllSaf} studying the topological setting in an elegant way.
 
@@
 \label{thm: EllSaf}
-Let $\cT$ be a classical field theory on $\RR^d$ in the sense of~\cite{CosBook},
+Let $\cT$ be a classical field theory on $\RR^d$
 and let its observables $\Obs_\cT$ be constructed following~\cite{CG2}.
@@
 \item The Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold yields an $E_3$ algebra. (The quantization was constructed by Chan, Leung, and Li~\cite{ChanLeungLi}.)
-\item The Kapustin-Witten gauge theory for oriented 4-manifolds yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$, (The quantization was constructed in~\cite{EGW}.)
+\item The Kapustin-Witten gauge theory for oriented 4-manifolds yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$.
+(The quantization was constructed in~\cite{EGW}.)
 \end{itemize}
@@
 
-\owen{Improve!}
 An algebra $A$ over this cooperad means that for each radius~$r$, 
@@
 
-\begin{thm}[\cite{CG1},\owen{precise location}]
-Let $\cT$ be a classical field theory on $\CC^d$ in the sense of~\cite{CosBook},
+\begin{thm}[see Chapter 5 of \cite{CG1}]
+Let $\cT$ be a classical field theory on $\CC^d$,
 and let its observables be constructed following~\cite{CG2}.
@@
 
-\subsection{Operator product expansion and holomorphic Poisson algebras}
-
-We remark on a simple consequence of this toolkit that may nonetheless be useful:
-one can view a topological field theory on $\RR^{2d}$ as a special kind of holomorphic field theory on~$\CC^{d}$.
-This situation has been exploited to good effect in the $d=1$ case,
-where people sometimes present an $E_2$-algebra as a dg vertex algebra with extra data and special properties \owen{citations? discussion of applications?}.
-
-The essential idea is simple.
-On a complex manifold $X$, there is a cochain map
-\[
-\Omega^\bu(X) \to \Omega^{0,\bu}(X)
-\]
-where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
-If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
-we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
-Hence an algebra over the cooperad $\Omega^\bu(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
-Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
-\begin{enumerate}
-\item algebras over the dg operad $C_\bu(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^\bu(\PDisc_d)$, as $\infty$-categories, and
-\item $E_{2d}$-algebras are equivalent to the algebras over $C_\bu(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
-\end{enumerate}
-The second item holds because any configuration space of polydiscs is weakly equivalent, as a topological space, to the analogous configuration space of discs.
-Thus we have sketched the following result.
-
-\begin{thm}
-There is a forgetful functor
-\[
-\Alg_{E_{2d}} \to  \Alg_{\PDisc_2}.
-\]
-\end{thm}
-
-The primary interest for us is the following consequence.
-
-\begin{cor}
-The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
-\end{cor}
-
-In Section~\ref{???} we will examine another relationship --- generalizing the compactification/chiralization on $\CC$ --- that yields an $E_d$ algebra from a $\PDisc_d$-algebra.
-\brian{This is probably a trivializable PDisc algebra by degree reasons?}
-
-\brian{Maybe a better thing to say after this theorem is a `recognition' result.
-That is, given a holomorphic PDisc$_{d}$ algebra, when is it equivalent to a algebra over $E_{2d}$ (in the essential image of the functor you wrote)?
-Among possibly smaller things, this should require that the $\del_{\zbar}$'s are homotoped.}
+\begin{itemize}
+\item ??
+\end{itemize}
+
+%\subsection{Operator product expansion and holomorphic Poisson algebras}
+%
+%We remark on a simple consequence of this toolkit that may nonetheless be useful:
+%one can view a topological field theory on $\RR^{2d}$ as a special kind of holomorphic field theory on~$\CC^{d}$.
+%This situation has been exploited to good effect in the $d=1$ case,
+%where people sometimes present an $E_2$-algebra as a dg vertex algebra with extra data and special properties \owen{citations? discussion of applications?}.
+%
+%The essential idea is simple.
+%On a complex manifold $X$, there is a cochain map
+%\[
+%\Omega^\bu(X) \to \Omega^{0,\bu}(X)
+%\]
+%where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
+%If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
+%we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
+%Hence an algebra over the cooperad $\Omega^\bu(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
+%Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
+%\begin{enumerate}
+%\item algebras over the dg operad $C_\bu(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^\bu(\PDisc_d)$, as $\infty$-categories, and
+%\item $E_{2d}$-algebras are equivalent to the algebras over $C_\bu(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
+%\end{enumerate}
+%The second item holds because any configuration space of polydiscs is weakly equivalent, as a topological space, to the analogous configuration space of discs.
+%Thus we have sketched the following result.
+%
+%\begin{thm}
+%There is a forgetful functor
+%\[
+%\Alg_{E_{2d}} \to  \Alg_{\PDisc_2}.
+%\]
+%\end{thm}
+%
+%The primary interest for us is the following consequence.
+%
+%\begin{cor}
+%The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
+%\end{cor}
+%
+%In Section~\ref{???} we will examine another relationship --- generalizing the compactification/chiralization on $\CC$ --- that yields an $E_d$ algebra from a $\PDisc_d$-algebra.
+%\brian{This is probably a trivializable PDisc algebra by degree reasons?}
+%
+%\brian{Maybe a better thing to say after this theorem is a `recognition' result.
+%That is, given a holomorphic PDisc$_{d}$ algebra, when is it equivalent to a algebra over $E_{2d}$ (in the essential image of the functor you wrote)?
+%Among possibly smaller things, this should require that the $\del_{\zbar}$'s are homotoped.}
 
@@
 \label{sec: fact alg}
-
-\owen{Some of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}
-
-\owen{My main concerns are (1) to mention working on arbitrary complex manifolds and not just $\CC^d$, (2) to mention Beilinson-Drinfeld's approach, and (3) to explain chiralization/reduction for $d > 1$.}
 
@@
 but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
-(See, however, section \owen{fill out } of \cite{HenKap} for important steps in that direction.)
+(See, however, the last section of \cite{HenKap} for important steps in that direction.)
 \end{rmk}
@@
 \subsection{How factorization algebras appear in QFT}
+\label{s:factinqft}
 
@@
 This theorem is also a key connection between field theories and higher algebras.
-\owen{I feel like I should say a little more, but not a lot more. I've commented out some old versions of this.}
+Indeed, a the value of a locally constant factorization algebra on a $d$-disk has the structure of a $\op{Disk}_d$-algebra.
+The value of a holomorphic factorization algebra on a complex $d$-dimensional polydisk has the structure of a $\op{PDisk}_d$-algebra.
 
@@
 
-\subsection{Compactification and conformal blocks}
+\subsection{Compactification and conformal blocks}\label{s:compact}
 
@@
 \label{sec: renorm}
-
-\owen{We discussed having the following:
-\begin{itemize}
-\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
-\end{itemize}}
 
@@
 On the Fulton-MacPherson compactification of the configuration space of $k$ points in $M$ (i.e., takes the real blow-up along the diagonals),
-the integrand admits a {\em smooth} extension and the integrals become well-defined.\owen{Citations!}
+the integrand admits a {\em smooth} extension and the integrals become well-defined.
 
@@
 this result was later extended to arbitrary Riemann surfaces in \cite{LiZhou}.
-Following up (cf. his thesis \cite{Wthesis} and its offshoot \cite{Wrenorm}), Williams laid a systematic mathematical foundations:
+Following up, the second author laid out systematic mathematical foundations:
 \begin{itemize}
@@
 showing that it is highly manageable, with no counterterms to 1-loop; and
-\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
+\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization),
 \end{itemize}
+see  \cite{Wthesis,Wrenorm}.
 These apply to all holomorphic theories on~$\CC^n$,
-but the techniques typically extend to more general complex manifolds.
+but some of the techniques should extend to more general complex manifolds.
 
@@
 
-\subsection{No divergences}
+\subsection{No divergences: Wang's approach}
 
@@
 
-\begin{thm}[Wang, \owen{precise citations}]
+\begin{thm}[\cite{Wang}]
 Let $\cE$ be the space of fields underlying a holomorphic field theory on $\C^n$.
@@
 In other words, divergences do not appear when constructing the perturbative quantization of {\em any} holomorphic field theory on~$\CC^d$.
-(Similar results hold for topological-holomorphic theories~\cite{WWthf}.)
-
+(Similar results hold for topological-holomorphic theories~\cite{WangWilliams}.)
+Thus, using the quantization of holomorphic field theories 
 \subsection{Anomalies that obstruct quantization}
@@
 \owen{I am confused by this comment. Aren't there TFTs with anomalies of some sort?}
-For holomorphic theories, however, anomalies are present.\footnote{Anomalies in holomorphic field theory are related to, but distinct from, anomalies well-known to physicists, such as ``chiral anomalies'' in theories of Weyl fermions.}
+For holomorphic theories, however, anomalies are present.
 (Within the context of Costello's formalism for perturbative QFT,
@@
 
-There will be two holomorphic theories on $\CC^2$. 
+The proposed duality involves two holomorphic theories on $\CC^2$. 
 We call one side {\em electric} and the other {\em magnetic}.
@@
 
+\subsection{A remark relating to homological projective duality}
+
+A standard maneuver used in physics is compactification:
+given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
+A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
+
+We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
+In other words, this is the $T^2$ compactification of the holomorphic theory.
+For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
+We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.
+
+Let's first consider the electric side, 
+which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
+The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
+The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
+where $z,w$ are formal loop parameters that we imagine as describing the winding of the two circles we have compactified. 
+The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
+Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
+In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
+As a derived mapping space, the moduli of solutions is given by
+\beqn
+{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
+\eeqn
+The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.
+
+On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
+What results is a Landau--Ginzburg B-model whose target is the stack
+\beqn
+\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
+\eeqn
+The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
+The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.
+
+Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
+or at least of $E_2$-algebras.
+
+\begin{conj}
+There is an equivalence of the following $E_2$ algebras:
+\begin{itemize} 
+\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
+\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
+\end{itemize}
+\end{conj}
+
+%\begin{conj}
+%There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
+%the compactifications of the electric and magnetic holomorphic QCD theories.
+%\end{conj}
+
+This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
+(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
+We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
+For instance, in this mathematical work, 
+one sees different choices of GIT quotients associated to the same stack yielding equivalent derived categories (and cousins),
+and these quotients only know about certain pieces of the stack,
+an issue we have flagged in our comparison of the moduli stack and the moduli space.
+
 \printbibliography

### 2024-10-11 draft.tex
more refs

@@
 Examples appear very naturally from topology: for any space $X$ with a basepoint $x$, take the singular chains $C_\bu(\Omega^d X)$ of the $d$-fold based loop space $\Omega^d_x X$.
-A much more subtle source of examples was conjectured by Deligne and subsequently proven in many ways \cite{}: 
+A much more subtle source of examples was conjectured by Deligne and subsequently proven in many ways: 
 for any associative algebra $A$, the Hochschild cochain complex ${\rm Hoch}^\bu(A,A)$ can be equipped naturally with an $E_2$-algebra structure.
@@
 There is a setting where a precise version of this statement was proven, by Elliott and Safronov, for a mathematically well-defined class of Lagrangian field theories.
-
-\owen{Rewrite this first attempt to be more accurate.}
 
@@
 These approaches share a common spirit but have important technical differences.
-A detailed comparison between the versions for locally constant factorization algebras exists \owen{good refs?},
+A detailed comparison between the versions for locally constant factorization algebras exists~\owen{KSW},
 but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
@@
 which are prefactorization algebras whose behavior on large open sets is determined by their behavior on small open sets.
-To give a precise description, we introduce a Grothendieck topology due to Michael Weiss~\owen{cite  \cite{Weiss} and it is explained nicely and further developed in \cite{BoavidaWeiss}}.
+To give a precise description, we introduce a Grothendieck topology due to Michael Weiss, 
+which is explained nicely and further developed in~\cite{BoavidaWeiss}.
 
@@
 
-\begin{thm}[\owen{citations}]
+\begin{thm}[\cite{LurieHA, AF,KSW}]
 The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
@@
 
-\og{Discuss twist along circle by automorphism of algebra. Forward ref to example later.}
+\owen{Discuss twist along circle by automorphism of algebra. Forward ref to example later.}
 

### 2024-10-12 draft.tex
oh boy some unpushed stuff

--- 2024-10-08 draft.tex
@@
 \setlength{\parindent}{0cm}
-\setcounter{tocdepth}{1}
 
@@
 \def\brian#1{{\textcolor{blue!75!red}{BW: {#1}}}}
-\def\owen#1{{\textcolor{red!50!black}{OG: {#1}}}}
+\def\owen#1{{\textcolor{violet!50!black}{OG: {#1}}}}
 
@@
 
+\owen{mention some history (e.g., Manin, Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, Kapranov, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}
+
+\owen{Notation to explain: dg = differential graded, PDE = partial differential equations}
+
 \section{What is a holomorphic field theory? Why study them?}
+
+\owen{Test references:} \cite{CG1,ManFrob}
 
@@
 The relevance to this survey is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
-even when they do not admit twists to TFTs \cite{CosSUSY}. 
+even when they do not admit twists to TFTs \cite{CosHol}. 
 (The famed A- and B-models of mirror symmetry are TFTs produced by twisting supersymmetric thories.)
@@
 and it continues to grow as there is a lot to explore here.
-Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CosWG2,CosYangian,CosTwistor}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, and \cite{BBBDN},
+Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, \cite{Vicedo}, \cite{BeemBZEtAl}, 
 where our own background and interests (and unfortunately, our ignorance) have shaped this list.
-\brian{Maybe add more...}
 
@@
 We hope the ideas surveyed here do connect profitably to these topics.
-
-As complementary perspectives to that offered here, we recommend
-\begin{itemize}
-\item Kapranov's lectures \cite{KapLect} on factorization algebras in algebraic geometry,
-\item Costello's lectures \cite{CosScheim} on how holomorphic field theories emerge from supersymmetric theories, and
-\item a recent survey \cite{GKW} for physicists on how higher algebra appears in perturbative QFT, with a strong emphasis on the holomorphic examples.
-\end{itemize}
-Reading these would give a more well-rounded view of the subject and its possibilities.
+\owen{Is that an overly negative paragraph?}
 
@@
 
-\subsection{About Manin and his influence}
-
-Yuri Manin was a pioneer into this intellectual region where field theory, complex geometry, and homotopical algebra meet,
-and his work --- beyond the beautiful results --- also gestured at rich possibilities for novel and powerful forms of geometry and physics and algebra,
-summoning these possibilities towards their current unfolding today into derived geometry and operadic structures in a broad sense.
-We quote \cite{ManFrob} in our epigraph, which synthesizes stacks and operads and Frobenius structures into a beautiful and coherent view on mirror symmetry.
-His \cite{ManGauge} is rich with deep reformulations of supersymmetric field theory that connect it to complex geometry,
-and it is a source of many inspirations;
-we are also quite fond of \cite{BeiMan, ManNewDim} from roughly the same era.
-Anyone interested in mathematics and physics and, especially, their relationship will delight in~\cite{ManMP}.
-
-Beyond his writing, however, we have also benefited throughout our careers from the attitudes and atmosphere that his persona modeled and spread among mathematicians:
-a generosity with ideas but also poetry and literature, an exquisite care and sensitivity to organizing and explaining mathematics (and much else),
-and a kindness in conversation, where he brought his whole attention to you.
-While a graduate student at Northwestern, 
-OG had the unbelievable luck to overlap with Manin and thus to take several courses and have many conversations with him, 
-getting to witness the personification of the Platonic idea of mathematician as intellectual.
-We both spent extensive time, for example, at the Max Planck Institute for Mathematics,
-which is suffused with his spirit.
-We wish we had the chance to discuss the ideas from this survey with Manin;
-we offer it as a small gift in gratitude for all he shared with us.
-
 \subsection{Acknowledgements}
@@
 \owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum, Natalie Paquette, Nik Garner}
+
+\owen{Add my thoughts about Manin}
 
@@
 \item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
-\item a system of partial differential equations (PDE) for the fields, known as the equations of motion.
+\item a system of PDE for the fields, known as the equations of motion.
 \end{itemize}
@@
 in a style amenable to a complex geometer,
-we suggest \cite{DeligneFreed}.
+we suggest \cite{FreedDeligne}.
+There are many other sources, such as \cite{}, because classical field theory is an old and deep subject.
 Recently there is an effort to revisit field theory with insights from derived geometry.
-See \cite{AlfonsiYoung} for motivation and overview, 
-but for a detailed development, see \cite{Steffens23, Steffens24}.
+See \cite{AlfonsoYoung?} for motivation and overview, 
+but for a detailed development, see \cite{Steffens}.
 In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
@@
 
-\subsection{More examples}
+\subsection{Examples}
 \label{sec: ex of theories}
@@
 There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs.
-See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.}
+and we now spell out some simple examples.\footnote{See \cite{Donaldson Thomas} for a pioneering and illuminating discussion of how to find such analogs.}
 To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
@@
 We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
-and see \cite{AlfonsiYoung} and \cite{Steffens23} for recent work on this topic.
+and see \cite{AlfonsoYoung} and \cite{Steffens} for recent work on this topic.
 
@@
 \eeqn
-where $\beta$ is a $(1,0)$-form on $M$.%\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
-%which we now think about as having its own degrees of freedom. 
-%\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
+where $\beta$ is a $(1,0)$-form on $M$.\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
+which we now think about as having its own degrees of freedom. 
+\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
 Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
@@
 Derived geometry is the mathematical version of BV formalism.
-From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
-\[
-T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\Omega^1_{hol}),
-\]
-where $\Omega^1_{hol}$ is the sheaf of holomorphic one-forms.
+From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
+\[
+T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\cT^{*{1,0}}),
+\]
+a rather natural space to study in complex geometry.
 
@@
 
-The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite[Chapter 3]{Polchinski}.
+The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.\owen{More precise location?}
 There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$-system encoding the antichiral sector of the free boson.
 To recover the full boson, one must couple the chiral and anti-chiral sectors.
-See \cite{Kapustin:2005pt,GGW} for more details.~\hfill$\Diamond$
+See \cite{Kapustin,GGW} \owen{Where?} for more details.~\hfill$\Diamond$
 \end{rmk}
@@
 
-From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
-\[
-T^*[-1] \Map_\dbar(M,N) ,
-\]
-where $\Map_\dbar(M,N)$ is the derived stack of holomorphic maps $M \to N$.
-This is a natural space to study in complex geometry.
+From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
+\[
+T^*[-1] \Map_\dbar(M,N) 
+\]
+a rather natural space to study in complex geometry.
 
@@
 at least perturbatively.
-For example, in \cite[\S3.2]{BGKWWY} it is shown that on $X = \C^2$ 
+For example, in \cite[\S3.2]{semichiral} it is shown that on $X = \C^2$ 
 the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
@@
 It is possible to formulate holomorphic versions of higher abelian gauge theories,
-associated to moduli spaces of holomorphic $k$-gerbes with connection, see \cite{SWtensor,BWfive}.
+associated to moduli spaces of holomorphic $k$-gerbes with connection.
+\owen{Should we elaborate or just stop with a reference?}
 
@@
 where $C \in \Omega^{2n+1}(X)$.
-For more details we refer to~\cite{GRW_WZW}.
-
-The reader may (and should) be concerned with the apparent ``non-local'' form of the action functional in \eqref{eqn:scalar1}.
-This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint~\cite{CLbcov}.
+For more details we refer to~\cite{GRWwzw}.
+
+The reader may (and should) be concerned with the apparent `non-local' form of the action functional in \eqref{eqn:scalar1}.
+This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint \cite{CLbcov1}.
 
@@
 due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
-It has been pursued mathematically by Costello and Li as an approach to the quantum higher genus $B$-model, starting with \cite{CLbcov} and continuing in a series of papers.
+It has been pursued mathematically by Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
 In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
@@
 Formulating the action functional to obtain this equation of motion is a little involved, 
-and we refer to \cite{CLbcov} for a systematic discussion.
+and we refer to \cite{CLbcov1} for a systematic discussion.
 
@@
 and hence may be of particular interest to physicists.
-In his work on Donaldson invariants of four-manifolds, Witten introduced the idea of a topological twist of a supersymmetric field theory \cite{WittenTwist}.
-The topological twist of a supersymmetric field theory (when it exists) can be attacked mathematically using the path integral.
-A key feature, however, of topological field theories is that they are amenable to a functorial paradigm.
-This firmly establishes their meaning and importance within pure mathematics.
-Slightly after Witten's work, the first shadows of what would later be called \textit{holomorphic twists} of supersymmetric field theories appeared, see \cite{Johansen:1994aw,Johansen:1994ud,NekThesis,Losev:1996up,Losev:1995cr,Johansen:2003hw,Eager:2018oww}.
-Originally, this work did not garner the same attention as the parallel works on topological twists; especially in mathematics.
-Much later, Costello introduced the precise notion of a holomorphic twist, and focused on examples in dimensions two and four \cite{CosSUSY}.
-The characterization of all holomorphic, topological, and mixed holomorphic-topological theories of Yang--Mills type in dimensions $2 \leq d \leq 10$ appears in \cite{ESW}.
-Holomorphic twists of more exotic quantum field theories, such as theories of supergravity and higher form gauge fields, have recently been studied in \cite{CLsugra,SWtensor,SWpure,Raghavendran:2021qbh,Eager:2021ufo,Garner:2023wrc}.
 
@@
 The classification of twisting supercharges is a completely algebraic question:
-see~\autocite{EllSaf} for a complete classification in dimensions from $1$ to~$10$.
+see~\autocite{ESsusy} for a complete classification in dimensions from $1$ to~$10$.
 
@@
 For a systematic discussion of how the twisted theory is defined, 
-we refer to~\autocite{CosSUSY, ESW}.
+we refer to~\autocite{CostelloHolomorphic, ESW}.
 
@@
 For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
-The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CLbcov, CLtypeI}.
+The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
 \item
-It is possible to make sense of Kodaira--Spencer theory outside of three complex dimensions.
+It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
 In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
-Holomorphic field theory has also appeared in applications to (twisted) holography through the lens of Koszul duality, see \cite{CLsugra, CGholography, CostelloPaquette}.
-\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall:2001dx, Berkovits:2005bt}, see also \cite{Eager:2018dsx,perspectives}, starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
+\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories.
 Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
 \item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
-Such work can be viewed as extending (and enhancing) the original Penrose correspondence which relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose:1969ae, Penrose}---see \cite{adamo2018lecturestwistortheory} for a modern review.
-See \cite{Mason, Mason_2009, CostelloTwistor,Bittleston_2023,garner2024scatteringtwistoriallinedefects} for recent work on the twistor correspondence in QFT.
+For instance, the Penrose corresponds relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
 \end{itemize}
-
-We recommend \cite{bah2024panoramaphysicalmathematicsc} for more discussion and references.
+We recommend \owen{is there some other place to point?} for more discussion.
 
@@
 
+\owen{In this section, or maybe the next, we should mention the recent papers by physicists (notably Gaiotto) about higher bracket structures, and we should indicate how to connect with our approach here.}
+
 \subsection{Algebras in mechanics}
@@
 describe deformations of its commutative algebra of functions to an associative algebra with the requirement that, to first order,  the commutator recovers the Poisson bracket.
-Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics.
-
-Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\ref{s:factinqft}), 
+Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics (see, e.g., \owen{what?} as a starting place).
+
+Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\owen{ref the general overview}), 
 and it might help the reader to bear in mind a variant of this question:
@@
 
-%\brian{something about states}
-%So far we've recalled how quantization looks like for algebras.
-%There is also a quantization for modules.
-%Let $L \subset M$ be a Lagrangian submanifold.
-%Then, functions $C^\infty(L)$ on $L$ are naturally a module for $C^\infty(M)$.
-%The Fock module $F(L)$ associated to $L$ is defined to be the quotient of 
-%
-%\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}
-
-\subsection{A loopy version: the algebra of modes}
+\brian{something about states}
+So far we've recalled how quantization looks like for algebras.
+There is also a quantization for modules.
+Let $L \subset M$ be a Lagrangian submanifold.
+Then, functions $C^\infty(L)$ on $L$ are naturally a module for $C^\infty(M)$.
+The Fock module $F(L)$ associated to $L$ is defined to be the quotient of
+
+\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}
+
+\subsection{A loopy version}
 
@@
 If one axiomatizes the behavior of $Y$, one is led to the notion of a vertex algebra.
-The algebra $W[V]$ is known as the \textit{algebra of modes} associated to this vertex algebra.
 
@@
 Dimensional reduction here means studying the two-dimensional physics as a one-dimensional system with a more complicated target, namely the loop space.\footnote{One can play this game whenever the spacetime manifold is product $X \times Y$ or a fiber bundle.
-Sometimes the term {\it compactification} is used instead, with reduction reserved for fixing the fiberwise fields to be constant---for a discussion of compactification within the setting of factorization algebras see Section~\ref{s:compact}.}
+Sometimes the term {\it compactification} is used instead, with reduction reserved for fixing the fiberwise fields to be constant.}
 There is, in this case, a kind of dual process that we call {\it chiralization},
@@
 \beqn
-S_{red}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
-\eeqn 
+S_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
+\eeqn 
+\owen{The $H$ got dropped. Should we reintroduct it?}
 Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
@@
 
-%\owen{A person might object that this isn't so well-defined analytically. Should we emphasize that it is rather formal, a kind of heuristic?}
+\owen{A person might object that this isn't so well-defined analytically. Should we emphasize that it is rather formal, a kind of heuristic?}
 
@@
 There is a close relationship of the higher dimensional Weyl algebra to the higher dimensional $\beta\gamma$ system on $\CC^d - 0$ just as the loopy Weyl algebra is related to the $\beta\gamma$ system on~$\CC^\times$.
-In this sense, $W_d[V]$ is an example of a `mode algebra', where the modes are now parametrized by the cohomology of punctured $d$-dimensional affine space.
 
@@
 it is a graded vector space $L$ equipped with a countable collection of ``higher brackets'' $[-]_k \colon L^{\otimes k} \to L$ that satisfy a system of equations generalizing the Jacobi identity.
-For an overview (and an actual definition!) we recommend \cite{LV}.
+For an overview (and an actual definition!) we recommend \owen{add citations}.
 In our setting the usual bracket (the 2-bracket) of $\fg^\bullet_d$ is unchanged but there is now a nontrivial $d$-bracket defined by~$\theta_{\rm FHK}$.
@@
 A natural question to ask then is what kind of higher algebraic structure captures how observables behave for theories in higher dimensions?
-The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in Section~\ref{sec: fact alg}
+The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in \S~\ref{sec fact alg},
 but there are nice answers for two special classes of theories that we will develop now:
@@
 Essentially, these are graded commutative algebras with a Poisson bracket of cohomological degree $-d+1$.
-In \cite{CosScheim} a parallel model for the cohomology of the holomorphic $\PDisc_d$ colored operad was proposed, 
+In \cite{CostelloScheimbauer} a parallel model for the cohomology of the holomorphic $\PDisc_d$ colored operad was proposed, 
 though axioms were not written down.
@@
 so we will gloss the key ideas of operads briefly and then turn to describing the operads relevant to TFTs.
-A more extensive discussion can be found in \cite{CG1}, with \cite{EllSaf} studying the topological setting in an elegant way.
+A more extensive discussion can be found in \cite{CG1}, with \cite{ES} studying the topological setting in an elegant way.
 
@@
 \label{thm: EllSaf}
-Let $\cT$ be a classical field theory on $\RR^d$
+Let $\cT$ be a classical field theory on $\RR^d$ in the sense of~\cite{CosBook},
 and let its observables $\Obs_\cT$ be constructed following~\cite{CG2}.
@@
 \begin{itemize}
-\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ yields an $E_2$ algebra.
+\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra.
 It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
-(The quantization was constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies.)
-\item The Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality. 
-(The quantization was constructed, essentially, by Axelrod-Singer \cite{AxeSing1,AxeSing2} and Kontsevich \cite{KonECM} but articulated in this setting by Costello~\cite{CosBook}.) 
-\item The Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold yields an $E_3$ algebra. (The quantization was constructed by Chan, Leung, and Li~\cite{ChanLeungLi}.)
-\item The Kapustin-Witten gauge theory for oriented 4-manifolds yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$.
-(The quantization was constructed in~\cite{EGW}.)
+\item The Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
+\item The Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
+\item The Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming functions on the coadjoint quotient stack~$\fg^*/G$.
 \end{itemize}
@@
 At the level of the punctured disk this corresponds to the higher Kac--Moody algebra that is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
-This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra~\cite{GWonKM}.
+This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra \cite{GWkm}.
 
@@
 
-\begin{thm}[see Chapter 5 of \cite{CG1}]
-Let $\cT$ be a classical field theory on $\CC^d$,
+\begin{thm}[\cite{CG1},\owen{precise location}]
+Let $\cT$ be a classical field theory on $\CC^d$ in the sense of~\cite{CosBook},
 and let its observables be constructed following~\cite{CG2}.
@@
 
-\begin{itemize}
-\item ??
-\end{itemize}
-
-%\subsection{Operator product expansion and holomorphic Poisson algebras}
-%
-%We remark on a simple consequence of this toolkit that may nonetheless be useful:
-%one can view a topological field theory on $\RR^{2d}$ as a special kind of holomorphic field theory on~$\CC^{d}$.
-%This situation has been exploited to good effect in the $d=1$ case,
-%where people sometimes present an $E_2$-algebra as a dg vertex algebra with extra data and special properties \owen{citations? discussion of applications?}.
-%
-%The essential idea is simple.
-%On a complex manifold $X$, there is a cochain map
-%\[
-%\Omega^\bu(X) \to \Omega^{0,\bu}(X)
-%\]
-%where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
-%If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
-%we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
-%Hence an algebra over the cooperad $\Omega^\bu(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
-%Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
-%\begin{enumerate}
-%\item algebras over the dg operad $C_\bu(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^\bu(\PDisc_d)$, as $\infty$-categories, and
-%\item $E_{2d}$-algebras are equivalent to the algebras over $C_\bu(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
-%\end{enumerate}
-%The second item holds because any configuration space of polydiscs is weakly equivalent, as a topological space, to the analogous configuration space of discs.
-%Thus we have sketched the following result.
-%
-%\begin{thm}
-%There is a forgetful functor
-%\[
-%\Alg_{E_{2d}} \to  \Alg_{\PDisc_2}.
-%\]
-%\end{thm}
-%
-%The primary interest for us is the following consequence.
-%
-%\begin{cor}
-%The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
-%\end{cor}
-%
-%In Section~\ref{???} we will examine another relationship --- generalizing the compactification/chiralization on $\CC$ --- that yields an $E_d$ algebra from a $\PDisc_d$-algebra.
-%\brian{This is probably a trivializable PDisc algebra by degree reasons?}
-%
-%\brian{Maybe a better thing to say after this theorem is a `recognition' result.
-%That is, given a holomorphic PDisc$_{d}$ algebra, when is it equivalent to a algebra over $E_{2d}$ (in the essential image of the functor you wrote)?
-%Among possibly smaller things, this should require that the $\del_{\zbar}$'s are homotoped.}
+\subsection{Operator product expansion and holomorphic Poisson algebras}
+
+\owen{discuss OPE, explain the shifted Poisson structure, and mention $\lambda$-brackets}
+
+\subsubsection{From topological to holomorphic}
+
+We remark on a simple consequence of this toolkit that may nonetheless be useful:
+one can view a topological field theory on $\RR^{2d}$ as a special kind of holomorphic field theory on~$\CC^{d}$.
+This situation has been exploited to good effect in the $d=1$ case,
+where people sometimes present an $E_2$-algebra as a dg vertex algebra with extra data and special properties \owen{citations? discussion of applications?}.
+
+The essential idea is simple.
+On a complex manifold $X$, there is a cochain map
+\[
+\Omega^\bu(X) \to \Omega^{0,\bu}(X)
+\]
+where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
+If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
+we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
+Hence an algebra over the cooperad $\Omega^\bu(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
+Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
+\begin{enumerate}
+\item algebras over the dg operad $C_\bu(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^\bu(\PDisc_d)$, as $\infty$-categories, and
+\item $E_{2d}$-algebras are equivalent to the algebras over $C_\bu(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
+\end{enumerate}
+The second item holds because any configuration space of polydiscs is weakly equivalent, as a topological space, to the analogous configuration space of discs.
+Thus we have sketched the following result.
+
+\begin{thm}
+There is a forgetful functor
+\[
+\Alg_{E_{2d}} \to  \Alg_{\PDisc_2}.
+\]
+\end{thm}
+
+The primary interest for us is the following consequence.
+
+\begin{cor}
+The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
+\end{cor}
+
+In Section~\ref{???} we will examine another relationship --- generalizing the compactification/chiralization on $\CC$ --- that yields an $E_d$ algebra from a $\PDisc_d$-algebra.
 
@@
 \label{sec: fact alg}
+
+\owen{Some of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}
+
+\owen{My main concerns are (1) to mention working on arbitrary complex manifolds and not just $\CC^d$, (2) to mention Beilinson-Drinfeld's approach, and (3) to explain chiralization/reduction for $d > 1$.}
 
@@
 
-Kapranov gave a lecture series explaining how factorization algebras fit into algebraic geometry \cite{KapLect}.
 A recent survey of factorization algebras, with a focus on their role in mathematical physics, can be found in~\cite{CosGwEMP}.
@@
 but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
-(See, however, the last section of \cite{HenKap} for important steps in that direction.)
+(See, however, section \owen{fill out } of \cite{HenKap} for important steps in that direction.)
 \end{rmk}
@@
 \subsection{How factorization algebras appear in QFT}
-\label{s:factinqft}
 
@@
 For $M = \RR$, we have already discussed how locally constant factorization algebras relate to associative algebras, starting with Example~\ref{ex:associativealgebra}.
-Lurie has shown the following vast extension of this example. (See section 5.4.5 of \cite{LurieHA}, particularly Theorem~5.4.5.9.)
+Lurie has shown the following vast extension of this example. (See section 5.4.5 of \cite{LurieHA}, particularly Theorem 5.4.5.9.)
 
@@
 We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do.
-A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in~\cite{KSW}.~\hfill $\Diamond$
+A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}.~\hfill $\Diamond$
 \end{rmk}
@@
 This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra.
-In fact, in \cite{GLL,GLX} it is shown how BV quantization for one-dimensional quantum field theories connects with the ordinary theory of deformation quantization.
+In fact, in \cite{GLL,Si Kai and Zhengping} it is shown how BV quantization for one-dimensional quantum field theories connects with the ordinary theory of deformation quantization.
 
 This theorem is also a key connection between field theories and higher algebras.
-Indeed, a the value of a locally constant factorization algebra on a $d$-disk has the structure of a $\op{Disk}_d$-algebra.
-The value of a holomorphic factorization algebra on a complex $d$-dimensional polydisk has the structure of a $\op{PDisk}_d$-algebra.
+\owen{I feel like I should say a little more, but not a lot more. I've commented out some old versions of this.}
 
@@
 
-%\subsection{Examples of holomorphic factorization algebras}
-%
-%\owen{Not sure what to put here, honestly. Maybe it should be removed.}
-%
-
-\subsection{Compactification and conformal blocks}\label{s:compact}
+\subsection{Examples of holomorphic factorization algebras}
+
+\owen{Not sure what to put here, honestly. Maybe it should be removed.}
+
+\subsection{Compactification and conformal blocks}
 
@@
 one says that $f_* \cF$ is the compactification of $\cF$ along~$Z$.
-This is akin to the famous Kaluza--Klein compactification in physics and should not be confused with the notion of ``dimensional reduction'', which only includes some of the Kaluza--Klein fields.
+\owen{We also used the terminology "dimensional reduction" earlier, so we should call back or distinguish these ideas.}
 
@@
 In the case that $\cF$ is a locally constant factorization algebra, 
-this computation agrees with the factorization homology of $\cF$ along $X$, as defined by Ayala-Francis and Lurie.
+this computation agrees with the factorization homology of $\cF$ along $X$, as defined by Ayala-Francis and Lurie \cite{}.
 In the case that $\cF$ is a holomorphic factorization algebra on a Riemann surface $\Sigma$, 
-the global sections $\int_\Sigma \cF$ is related to a familiar invariant within the theory of vertex/chiral algebras called the ``space of conformal blocks'' \cite[\S 8]{FBZ}.
-Precisely, the zeroth homology of $\int_\Sigma \cF$ is linearly dual to the space of (ordinary, non-derived) conformal blocks.
+the global sections $\int_\Sigma \cF$ is closely related to the chiral homology (or conformal blocks) of the chiral (or vertex) algebra associated to $\cF$ along $\Sigma$.
+\owen{I want to assert "(It is the linear dual.)"}
 
@@
 where $L_0$ denotes the action of the vector field $z \del_z$.
-The shift by the central charge guarantees that this expression has nice modularity properties, i.e., we can view $q$ as parametrizing the moduli of elliptic curves.
-
-From the point of view of factorization algebras, we can understand this trace in terms of Hochschild homology of the algebra of modes associated to $\mathbb{V}$.
-Indeed, suppose the conformal vertex algebra $\mathbb{V}$ arises from a holomorphic $S^1$-equivariant factorization algebra $\cF_{\mathbb{V}}$ on $\C$.
-If $r \colon \C^\times \to \RR_{>0}$ is the radial projection there is a procedure for extracting the associative algebra of modes from the one-dimensional factorization algebra $r_* \cF_{\mathbb{V}}$.
-Indeed, while $r_* \cF_{\mathbb{V}}$ may not be a locally constant factorization algebra, it always contains a dense subfactorization algebra which is locally constant.\footnote{To extract it, one assumes that $\cF$ is $S^1$-equivariant.
-For each interval $I \subset \RR_{>0}$ one then looks at the subspace of $\cF(\pi^{-1}(I))$ consisting of the eigenspaces for this $S^1$ action.
-The assignment of an interval $I$ to this subspace is a locally constant factorization algebra.}
-With slight abuse of notation, we will still denote $r_* \cF_{\mathbb{F}}$ the locally constant factorization algebra obtained from this compactification.
-
+The shift by the central charge guarantees that this expression has nice modularity properties, i.e., we can view $q$ as parametrizing the moduli space of elliptic curves.
+\owen{Is that an ok turn of phrase?}
+
+From the point of view of factorization algebras, we can understand this trace in terms of Hochschild homology of the \textit{modes} algebra associated to $\mathbb{V}$ as introduced in \S\ref{??}.
+Indeed, suppose the conformal vertex algebra $\mathbb{V}$ arises from a holomorphic factorization algebra $\cF_{\mathbb{V}}$ on $\C$.
+Then, if $r \colon \C^\times \to \RR_{>0}$ is the radial projection, we have discussed how to extract the modes algebra from the one-dimensional factorization algebra $r_* \cF_{\mathbb{F}}$.
 If we further put this on the circle, we find Hochschild homology.
-Thus, for each modulus~$q$ functoriality of factorization homology gives rise to a map
+Thus, for every modulus $q$ one has
 \beqn
-\int_{S^1_{\sigma}} r_* \cF_{\mathbb{V}} = \op{Hoch}(r_* \cF_{\mathbb{V}}, \sigma) \to \int_{E_q} \cF_{\mathbb{V}} .
-\eeqn
-Here, $\sigma$ is an automorphism defined in terms of the given $S^1$-action on $\cF_{\mathbb{V}}$, and what appears on the left-hand side is the $\sigma$-twisted Hochschild homology.
-For free theories, this map is a quasi-isomorphism.
-On the other hand, given a conformal block (i.e., linear functional on $\int_{E_q} \cF_{\mathbb{V}}$) we can compose it with that map to define a trace on the modes algebra.
+\int_{E_q} \cF_{\mathbb{V}} = \int_{S^1} r_* \cF_{\mathbb{V}} = \op{Hoch}(r_* \cF_{\mathbb{V}}) .
+\eeqn
+\owen{I think $\int_{E_q}$ receives a map from $\op{Hoch}(r_* \cF_{\mathbb{V}})$ but I don't see why it's an isomorphism.
+On the other hand, given a conformal block (i.e., linear functional on $\int_{E_q}$, we can compose it with that map to define a trace on the modes algebra,
+which ought to be the character.}
+For more on this perspective see \cite{GuiLi}.
 From this point of view, the factorization homology along an elliptic curve encodes characters in the sense of vertex algebras.
-For more on this perspective see \cite{GuiLi}, where they carefully develop the notion of a trace for chiral/vertex algebras.
 
@@
 \beqn
-\op{Hoch}(r_* \cF , \sigma) \to \int_{H_{\mathbf{q}}} \cF 
-\eeqn
-where, again, $r\colon \C^d - \{0\} \to \RR_{>0}$ is the radius and $\sigma$ is an automorphism of $\cF$ induced from the $S^1$-equivariant structure of $\cF$.
+\int_{H_{\mathbf{q}}} \cF \simeq \op{Hoch}(r_* \cF)
+\eeqn
+where, again, $r\colon \C^d - \{0\} \to \RR_{>0}$ is the radius.
 Thus, we see that the factorization homology $\int_{H_{\mathbf{q}}} \cF$ naturally encodes traces of the $S^{2n-1}$-mode algebra associated to $\cF$.
@@
 \label{sec: renorm}
+
+\owen{We discussed having the following:
+\begin{itemize}
+\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
+\end{itemize}}
 
@@
 On the Fulton-MacPherson compactification of the configuration space of $k$ points in $M$ (i.e., takes the real blow-up along the diagonals),
-the integrand admits a {\em smooth} extension and the integrals become well-defined.
+the integrand admits a {\em smooth} extension and the integrals become well-defined.\owen{Citations!}
 
@@
 When applied to Dolbeault complexes arising in Kodaira-Spencer (or BCOV) theory, 
-he and Li found some remarkable simplifications and good behavior \cite{CLbcov}.
-In \cite{LiVertex} Li showed, by clever analysis, that holomorphic field theories in complex dimension one (i.e., chiral conformal field theories) are finite to all orders in perturbation theory; 
-this result was later extended to arbitrary Riemann surfaces in \cite{LiZhou}.
-Following up, the second author laid out systematic mathematical foundations:
+he and Li found some remarkable simplifications and good behavior \cite{??}.
+In \cite{LiVertex} Li showed, by very clever analysis, that holomorphic field theories in complex dimension one (i.e., chiral conformal field theories) are finite to all orders in perturbation theory;
+this result was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
+Following up (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}), Williams laid a systematic mathematical foundations:
 \begin{itemize}
@@
 showing that it is highly manageable, with no counterterms to 1-loop; and
-\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization),
+\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
 \end{itemize}
-see  \cite{Wthesis,Wrenorm}.
-These apply to all holomorphic theories on~$\CC^n$,
-but some of the techniques should extend to more general complex manifolds.
+These apply to all holomorphic theories on $\CC^n$,
+but the techniques typically extend to more general complex manifolds.
 
@@
 \owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
-\brian{I think it would be more confusing to use a different term.
-But you can explain how it's the issue of `overlapping supports' of distributions; that is, it's an issue about `local integrability'.
-In fact, in their work Axelrod and Singer already use the term ultraviolet.}
-\owen{I agree that UV is a term many people use, but not among most of our target audience, which I view as algebraic geometers and higher algebra folks.
-Why not just say that we're showing no divergences appear and hence counterterms are not needed?}
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
@@
 
-\subsection{No divergences: Wang's approach}
+\subsection{No divergences}
 
@@
 
-For holomorphic field theories, however, something remarkable happens.
-
-\begin{thm}[\cite{Wang}]
+For holomorphic field theories (and generally topological-holomorphic theories, see \cite{WWthf}) however, something remarkable happens.
+
+\begin{thm}[Wang, \owen{precise citations}]
 Let $\cE$ be the space of fields underlying a holomorphic field theory on $\C^n$.
@@
 In other words, divergences do not appear when constructing the perturbative quantization of {\em any} holomorphic field theory on~$\CC^d$.
-(Similar results hold for topological-holomorphic theories~\cite{WangWilliams}.)
-Thus, using the quantization of holomorphic field theories 
+
 \subsection{Anomalies that obstruct quantization}
@@
 An anomaly measures the failure of the path integral to enjoy the same symmetries as the underlying classical field theory.
-In gauge theory, for instance, the perturbative renormalization might not be gauge invariant, although the classical action functional is.
-Specifically, the gauge variation of a particular Feynman graph integral may be nonzero---this leads to an anomaly in the quantum theory.
+In gauge theory, for instance, the perturbative renormalization might not be gauge invariant, although the action functional is.
 In topological theories, it is known that these sort of anomalies are absent.
 \owen{I am confused by this comment. Aren't there TFTs with anomalies of some sort?}
-For holomorphic theories, however, anomalies are present.
+For holomorphic theories, however, anomalies are present.\footnote{Anomalies in holomorphic field theory are related to, but distinct from, anomalies well-known to physicists, such as ``chiral anomalies'' in theories of Weyl fermions.}
 (Within the context of Costello's formalism for perturbative QFT,
@@
 Since renormalization is so well-behaved, however, such anomalies are amenable to explicit characterization.
-For example, at one-loop in perturbation theory, an explicit formula for such anomalies for holomorphic theories on $\C^d$ is given in \cite{Wrenorm}.
+For example, at one-loop in perturbation theory, an explicit formula for such anomalies for holomorphic theories on $\C^d$ is given in \cite{Whol}.
 It involves a sum over Feynman weights $W_\Gamma$ where $\Gamma$ is a polygon with $(d+1)$~vertices.
@@
 
-The gauge variation of the two diagrams which contribute to the gauge anomaly are shown in Figure~\ref{fig:localization}.
-The difference between these two diagrams is how we label the internal edges: in the first diagram they are labeled by $A-B$ fields and in the second they are labeled by $\beta-\gamma$ fields.
-An anomaly can be represented by a (local) functional on the space of fields.
-In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ is of the form
-\beqn
-c \int \op{Tr}_M (A \del A \del A)
-\eeqn
-where $c$ is some nonzero constant and $M$ is some representation of $\lie{g}$ (the value of $c$ is the same for both diagrams, in this example).
-Specifically:
+There are two diagrams that contribute to the gauge anomaly,
+shown in Figure~\ref{fig:localization}.
+\owen{There isn't a $K$-edge on the wheel?}
+These define functions on the space of fields:
 \begin{itemize}
-\item In the first diagram the representation $M$ is the adjoint representation. 
-So, this expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
-\item In the second diagram the representation is $M = V$ (the representation which labels the $\beta-\gamma$ system).
+\item The pure gauge anomaly: it is proportional to the representation-theoretic factor $\op{Tr}_{ad}(X^3)$ for  $X \in \lie{g}$, which is an invariant function of~$\fg$.
+This expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
+\item The mixed anomaly: its edges (propagators) are labeled by the $\beta\gamma$ fields,
+and it is proportional to the representation-theoretic factor $\op{Tr}_V(X^3)$ for $X \in \lie{g}$.
 \end{itemize}
-Thus, the total anomaly is $c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)$.
-
-These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
+These each come from ways of labeling the vertices and edges of the wheel (or polygon) diagram with three vertices.
+We have described the representation-theoretic factor but there is also an analytic factor.
+\owen{Should we just write out the formulas? What we write is kind of hard to parse, as it is shorthand. I can imagine a person asking "proportional ... how?"}
+
+These anomalies of a holomorphic gauge theory on $\CC^4$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
 In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly), 
@@
 take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.
-
-\owen{Owen's comments that I've tried to address:
-\begin{itemize}
-\item There isn't a $K$-edge on the wheel?
-\item Should we just write out the formulas? What we write is kind of hard to parse, as it is shorthand. I can imagine a person asking "proportional ... how?".
-\end{itemize}
-}
 
@@
 \end{tikzpicture}
-\caption{Diagrams whose gauge variation contribute to the anomaly in holomorphic gauge theory on~$\C^2$}
+\caption{Diagrams that contribute to the anomaly in holomorphic gauge theory on~$\C^2$}
 \label{fig:localization}
@@
 
-The holomorphic twist of a theory with both vector and matter multiplets can be described, globally, as a derived mapping space from $X$ to the target
-\beqn
-[( \fg_\CC^*\times {\rm Crit}^d(W))/ G_\CC] .
-\eeqn
-This is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.
-
-\textit{Supersymmetric quantum chromodynamics} (SQCD) refers to a specific sort of four-dimensional $\cN=1$ gauge theories.
-In the special, yet interesting, case that the gauge group is $G = SU(N)$ (and so $G_\CC = SL(N)$) the  matter fields consist of two types: quarks, valued in some number of copies of the fundamental (defining) representation, and antiquarks, valued in the same number of copies of the anti-fundamental (dual to the defining) representation.
-The number of fundamental representations that appear is called the number of \textit{flavors}, and will be denoted $F$.
-The number $N$ is called the number of \textit{colors}.
-The following theorem describes the holomorphic twist of SQCD (for $G = SU(N)$). 
-Henceforth, we will refer to the resulting holomorphic field theory as \textit{holomorphic QCD}.
+The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
+\[
+{\rm Map}(X , [( \fg_\CC^*\times {\rm Crit}^d(W))/ G_\CC]), 
+\]
+where the target is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.
+
+We wish to study a holomorphic analog of supersymmetric chromodynamics.
+We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
+We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
+The matter fields will consist of two types: quarks and antiquarks.
+Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
+so $\underline{N} = \CC^N$ with its natural left action.
+\owen{That's kind of crappy notation. Let's discuss.}
+\brian{Does it help us much? Or are you trying to use this to disambiguate what $\CC^N$ means.}
 
@@
 
-\begin{thm}[\cite{ESW,SWchar}]
-The holomorphic twist of $G = SU(N)$ SQCD with $F$ flavors and super potential $W$ on $\C^2 = \RR^4$ is equivalent to the following holomorphic field theory:
+\begin{dfn}
+A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
 \begin{itemize}
@@
 \[
-S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag + \int\d^2 z \, W(Q) ,
+S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag,
 \]
@@
 %We will denote this theory by $\cT(N,F)$.
-\end{thm}
-
-\begin{rmk}
-Notice that to write down the superpotential term, we are utilizing the holomorphic volume form~$\d^2 z$. 
-Relatedly, unless $W = 0$, this theory is only $\ZZ/2$-graded, so all fields are considered merely as even or odd.
-For instance the component of the gauge field $A^{0,1}$ is even while the component of the matter field $Q^{0,1}$ is odd. 
-When $W$ is homogenous one can lift the theory to a $\ZZ$-grading by making additional choices.
-\end{rmk}
+\end{dfn}
 
 To formulate Seiberg duality, we will need to allow auxiliary matter fields that we call ``mesons.''
-As above, we fix $G_{\CC} = SL(N,\CC)$.
 
@@
 %, denoted $\cT(N,F, V_M, W)$, 
-is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, whose fields we denote by
+is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
 \[
@@
 \[
-S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; \til W(Q, Q^\dag, \mu) .
-\] 
+S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, Q^\dag, \mu) .
+\] 
+Notice that to write down the superpotential term, we are utilizing the holomorphic volume form~$\Omega_X = \d^2 z$. 
 \end{dfn}
@@
 Hence we use $\dbar$ rather than $\dbar_A$.
-The only coupling that the meson $\mu$ has to the other fields is through the new superpotential~$\til W$.
+The only coupling that the meson $\mu$ has to the other fields is through the superpotential~$W$.
+
+\begin{rmk}
+This theory is only $\ZZ/2$-graded, so all fields are considered merely as even or odd.
+For instance the component of the gauge field $A^{0,1}$ is even while the component of the matter field $Q^{0,1}$ is odd. 
+Only when $W = 0$ can one lift the theory to a $\ZZ$-grading.
+\end{rmk}
 
@@
 
-The proposed duality involves two holomorphic theories on $\CC^2$. 
+There will be two holomorphic theories on $\CC^2$. 
 We call one side {\em electric} and the other {\em magnetic}.
@@
 We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
-For simplicity, we don't consider any superpotential.
 \item
@@
 \beqn\label{eqn:checkW}
-\til W =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q})
+\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q})
 \eeqn
@@
 The answer to this question has been studied by Surya Raghavendran and Philsang Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}.
-A further localization of $S$-duality has also been studied by Costello and Gaiotto~\cite{CGholography}.
+A further localization of $S$-duality has also been studied by Costello and Gaiotto \cite{CGholography}.
 
@@
 Witten initiated this vein of research for twists that are topological \cite{WittenTwist},
-and Costello advocated holomorphic twists \cite{CosSUSY}.  
-Costello and Li initiated the use of holomorphic twists to study dualities particularly in the setting of the topological B-model (see \cite{CLbcov} and follow ups), and further extended these ideas to non-topological strings \cite{CLsugra}.
+and Costello advocated holomorphic twists \cite{CostelloHol}.  
+Costello and Li initiated the use of holomorphic twists to study dualities particularly in the setting of the topological B-model \cite{CLbcov1,CLbcov2,CLbcov3}, and further extended this to non-topological strings \cite{CLsugra}.
+Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
 These ideas are extensively used in the program of twisted holography, which is growing rapidly at the moment.
 (The interested reader might track the papers that cite those we have mentioned.)
-Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
 \end{rmk}

### 2024-10-12 draft.tex

--- 2024-10-11 draft.tex
@@
 \subsection{Reduction vs. chiralization}
+\label{sec: red vs chiral}
 
@@
 there has a been a buzz of recent activity on the renormalization of holomorphic field theories.
-In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
-\owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
-\brian{I think it would be more confusing to use a different term.
-But you can explain how it's the issue of `overlapping supports' of distributions; that is, it's an issue about `local integrability'.
-In fact, in their work Axelrod and Singer already use the term ultraviolet.}
-\owen{I agree that UV is a term many people use, but not among most of our target audience, which I view as algebraic geometers and higher algebra folks.
-Why not just say that we're showing no divergences appear and hence counterterms are not needed?}
+Budzik, Gaiotto, Kulp, Wu, and Yu developed a strategy for proving that in a holomorphic quantum field theory,
+certain graphs (called Laman graphs) do not produce divergences~\cite{BGKWY}.
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
 
-Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
+Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is divergence-free to \textit{all} orders in perturbation theory \cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
@@
 (Similar results hold for topological-holomorphic theories~\cite{WangWilliams}.)
-Thus, using the quantization of holomorphic field theories 
+
+This result ensures the existence of myriad examples of the higher algebraic structures we've discussed:
+it provides the analysis to quantize the kinds of examples from Section~\ref{sec: ex of theories} and hence to produce polydiscs algebras and factorization algebras.
+
 \subsection{Anomalies that obstruct quantization}
@@
 In topological theories, it is known that these sort of anomalies are absent.
-\owen{I am confused by this comment. Aren't there TFTs with anomalies of some sort?}
 For holomorphic theories, however, anomalies are present.
@@
 An anomaly can be represented by a (local) functional on the space of fields.
-In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ is of the form
+In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ and has the form
 \beqn
-c \int \op{Tr}_M (A \del A \del A)
-\eeqn
-where $c$ is some nonzero constant and $M$ is some representation of $\lie{g}$ (the value of $c$ is the same for both diagrams, in this example).
-Specifically:
+c \int \op{Tr}_V (A \wedge \del A \wedge \del A)
+\eeqn
+where $c$ is some nonzero constant and $V$ is some representation of $\lie{g}$.\footnote{In this example, the value of $c$ is the same for both diagrams.}
+Specifically, we have:
 \begin{itemize}
-\item In the first diagram the representation $M$ is the adjoint representation. 
-So, this expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
-\item In the second diagram the representation is $M = V$ (the representation which labels the $\beta-\gamma$ system).
+\item In the first diagram the representation $V$ is the adjoint representation. 
+Thus, this expression vanishes when $\lie{g}$ is simple, e.g., when $\lie{g} = \lie{sl}(n)$.
+\item In the second diagram the representation is that used in defining the $\beta\gamma$ system.
 \end{itemize}
-Thus, the total anomaly is $c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)$.
-
-These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
+The sum 
+\[
+c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)
+\]
+is the total anomaly for this field theory.
+These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on~$\RR^4$.
+
 In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly), 
@@
 and one of his leading contributions is referred to as {\em Seiberg duality}.
-It has had a large impact in theoretical physics \owen{give the citation number on that paper},
+It has had a large impact in theoretical physics,
 but the impact in mathematics is much more muted,
-possibly due to the lack of a topological twist for any $\cN=1$ theory.
+possibly due to the lack of a topological twist for any $\cN=1$ theory.\footnote{Although citations offer only coarse insight into impact, Seiberg's paper introducing the conjecture \cite{Seiberg} has over 1800 citations listed on Inspire but less than 60 citations listed on MathSciNet.}
 Such theories do admit {\em holomorphic} twists, however, 
@@
 should produce equivalences between different kinds of 2-dimensional B-model theories;
-these reductions are related to work of Hori and Hori--Tong \owen{citations} and its mathematical development by Ed Segal, \owen{list others}.
+these reductions are related to work of Hori and Hori--Tong and its mathematical development, notably by Segal and collaborators~\cite{Hori, HoriTong, HMSegRen, ADS}.
 
@@
 A standard maneuver used in physics is compactification:
-given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
-One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
-A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
-
-We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
-In other words, this is the $T^2$ compactification of the holomorphic theory.
-For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
-We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.
-
-Let's first consider the electric side, 
-which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
-The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
+given a field theory $\cT$ in $n$ dimensions, one takes compact ($n$-$k$)-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+One then considers the push forward of the theory along the projection map $N \times \Sigma \to \Sigma$, to obtain a theory along $\Sigma$.
+(A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along~$N$.)
+
+We now apply this maneuver to holomorphic Seiberg duality:
+by compactifying along a Riemann surface, we should generate a conjectural equivalence between two-dimensional field theories.
+As we will see, this new conjecture resembles the Hori-Tong dualities that have led to Hori-mological mirror symmetry~\cite{Hori, HoriTong, HMSegRen}.
+
+Consider a holomorphic theory defined on $\C^\times \times \C^\times$ 
+and push forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ 
+that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
+In other words, take the torus compactification of the holomorphic theory.
+For a holomorphic factorization algebra $\cF$, 
+the pushforward $\rho_* \cF$ contains a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$ (in essence, by taking the Fourier modes on the torus fibers).
+This locally constant factorization algebra corresponds to an $E_2$-algebra.\footnote{Recall Section~\ref{sec: red vs chiral}, where we compactified on a circle and then broke things up using Fourier modes.
+This construction extracted an associative ($E_1)$ algebra that is a Weyl algebra of a formal loop space from a holomorphic field theory on~$C^\times$.}
+
+Let's start with holomorphic QCD and see what Seiberg duality would imply.
+On the electric side, 
+we have a two-dimensional holomorphic BF theory coupled to a complex two-dimensional $\beta\gamma$ system.
+By itself, the $\beta\gamma$ system with target $\C^{NF}$ yields, by torus compactification, 
+the topological B-model theory whose target is the formal double loop space~$L^2\C^{NF}$. 
 The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
 where $z,w$ are formal loop parameters that we imagine as describing the winding of the two circles we have compactified. 
-The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
-Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
-In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
+The dimensional reduction then picks out the constant modes along each circle, 
+so we find a topological B-model with target $\C^{NF}$.
+Similarly, holomorphic BF theory dimensionally-reduces to topological BF theory,
+which can be viewed as the B-model with target the classifying space~$BGL(N)$.
+In sum, the dimensional reduction of electric holomorphic QCD is the topological B-model with target the stack $\C^{NF} / GL(N)$.
 As a derived mapping space, the moduli of solutions is given by
@@
 \eeqn
-The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.
+Dimensional reduction of the factorization algebra of observables produces the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.
 
@@
 \beqn
-\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
+\left(\C^{(F-N)F} / GL(F-N) \right) \times \C^{F^2} .
 \eeqn
 The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
-The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.
-
-Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
+The potential for the Landau--Ginzburg model is precisely the potential $\check{W}$ seen in~\eqref{eqn:checkW}.
+This procedure produces an $E_2$ algebra by deforming the differential on the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$, 
+namely use the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
+
+Holomorphic Seiberg duality thus predicts an equivalence of two-dimensional topological field theories,
 or at least of $E_2$-algebras.
 
-\begin{conj}
-There is an equivalence of the following $E_2$ algebras:
+\begin{conj*}
+There is an equivalence of $E_2$ algebras between
 \begin{itemize} 
-\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
-\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
+\item the {\em electric} $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
+\item the {\em magnetic} $E_2$ algebra of polyvector fields on the stack $(\C^{(F-N)F} / GL(F-N)) \times \C^{F^2}$ with differential~$\{\check{W},-\}$. 
 \end{itemize}
-\end{conj}
+\end{conj*}
 
@@
 
-This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
-(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
-We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
-For instance, in this mathematical work, 
-one sees different choices of GIT quotients associated to the same stack yielding equivalent derived categories (and cousins),
-and these quotients only know about certain pieces of the stack,
-an issue we have flagged in our comparison of the moduli stack and the moduli space.
+This conjectured equivalence resembles Hori-Tong dualities.
+Note that it is often said that Hori-Tong dualities are like Seiberg dualities!
+We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{KuzHPD, ThomasHPD, Perry} --- might apply here, and also feed back towards holomorphic Seiberg duality.
 

### 2024-10-12 draft.tex
almost there

@@
 and it continues to grow as there is a lot to explore here.
-Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CosWG2,CosYangian,CosTwistor}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, and \cite{BBBDN},
+Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, and \cite{BBBDN}, 
 where our own background and interests (and unfortunately, our ignorance) have shaped this list.
-\brian{Maybe add more...}
 
@@
 
-\owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum, Natalie Paquette, Nik Garner}
+This survey attempts to summarize the efforts and insights of a large body of researchers.
+So much of our understanding is shaped by conversations and interactions with them,
+and we thank them for their generosity with ideas and examples.
+We owe particular thanks to Kevin Costello, Richard Eager, Chris Elliott, Davide Gaiotto, Nik Garner, Vasily Gorbounov, Zhengping Gui, Benjamin Hennion, Mikhail Kapranov, Si Li,  Natalie Paquette, Nik Rozenblyum,  Ingmar Saberi,  Pavel Safronov,  Matt Szczesny, Ed Segal,  Johannes Walcher, Minghao Wang, and Jie Zhou.
+\owen{Kasia Budzik? Kulp?}
 
@@
 Hence, for any $G$-manifold $M$, it is natural to ask whether there is a representation $\fg \to D_M$ deforming the canonical Poisson representation.
-In this spirit, we will search for analogues of the kind of mathematics that has grown out of results by Beilinson-Bernstein \owen{cite}, Kashiwara \owen{cite}, and others.
+In this spirit, we will search for analogues of the kind of mathematics that has grown out of results by Beilinson-Bernstein \cite{BB}, Brylinski-Kashiwara \cite{BryKash}, Kostant \cite{Kostant} and others.
 
@@
 \begin{rmk}
-In the $d=1$ case there is a lovely exploration of how the highly developed theory of vertex algebras relates to this perspective in the pair of papers by Bruegmann \cite{}.
-For a discussion of how conformal nets --- an alternative formalism for chiral CFT --- relates to our perspective, see \cite{Henriques}.
+In the $d=1$ case there is a lovely exploration of how the highly developed theory of vertex algebras relates to this perspective in the pair of papers by Bruegmann \cite{Bruegmann1,Bruegmann2}.
+For a discussion of how conformal nets --- an alternative formalism for chiral CFT --- relates to our perspective, see~\cite{Henriques, BPS}.
 \end{rmk}
@@
 \nu \circ_i \mu: & V^{\otimes m+n-1} & \to & V\\
-& v_1 \otimes \cdots \otimes v_{m+n-1} & \mapsto & \nu(v_1 \otimes \cdots \otimes \mu(v_i, \ldots, v_m), v_{m+1}, \ldots, v_{m+n-1})
+& v_1 \otimes \cdots \otimes v_{m+n-1} & \mapsto & \nu(v_1 \, \ldots, \mu(v_i, \ldots, v_m), v_{m+1}, \ldots, v_{m+n-1})
 \end{array}
 \]
-\owen{finish the formula! make it agree with conventional formulas}
 where $i$ can run over any index between 1 and $n$.
@@
 For motivational introductions, we recommend \cite{StashAMS} and \cite{Val12}.
-For systematic development of the theory, one might start with \cite{LodVal}, \owen{others}
+For systematic development of the theory, one might start with \cite{LodVal,Fresse,LurieHA}.
 Operads now have an extensive literature, and there is a body of deep results (such as Koszul duality) with far-reaching consequences throughout mathematics.
@@
 In the case $d=1$, it is possible to relate polydiscs algebras to vertex algebras.
-More precisely, when the polydisc algebra has a nice action of the rotation group~$U(1)$,
-one can extract a vertex algebra: 
-see Chapter 5 of~\cite{CG1} for a detailed treatment and examples like the free $\beta\gamma$ system and the Kac-Moody vertex algebras.
-Here we will analyze the cohomology of the cooperad and what kind of information it encodes, with a view towards motivating the relationship to vertex algebras.
+More precisely, there is a functor from a class of 1-polydiscs algebras to vertex algebras,
+developed in Chapter 5 of~\cite{CG1}.
+In essence, a polydisc algebra is in this class if it has a nice action of the rotation group~$U(1)$,
+so that one can extract ``modes'' (or Fourier components) from it.
+Examples like the free $\beta\gamma$ system and the Kac-Moody vertex algebras are analyzed in~\cite{CG1}.
+
+Here we will analyze the cohomology of the cooperad and what kind of information it encodes, 
+with a view towards motivating the relationship to vertex algebras.
+The takeaway from the discussion below is that one can read off the modes $a_{(n)}$ that assemble into the vertex operator $Y(a,z)$ using a $1$-polydiscs algebra.
 
@@
 \]
-
-\owen{I think I should swap the location of $a$ and $b$ to match VOA conventions.
-I want to explain that taking the extremal radii means we cannot compose, which leads to the complicated VOA formulas.}
+Thus we have worked out the modes $a_{(n)}$, as promised.
+
+This construction also gives insight into some challenges with the formalism of vertex algebras,
+such as the fact that one cannot simply compose vertex operators but must describe a 3-point product and track the geometry between the insertion points $0$, $z$, and $w$.
+For instance, to obtain the modes, we took the outgoing radius to be infinite,
+so it cannot be inserted into any finite radius disk.
 
@@
 
+A number of examples from Section~\ref{sec: ex of theories} have been developed in this framework, 
+analogous to the list of examples after Theorem~\ref{thm: EllSaf}:
 \begin{itemize}
-\item ??
+\item The curved $\beta\gamma$ system for a Riemann surface into a complex manifold~$X$ was constructed in \cite{CosWG2}, and then \cite{GGW} demonstrates in detail how the vertex algebra of {\it chiral differential operators} of $X$ is recovered.
+\item In \cite{Wthesis} these methods were extended to holomorphic $\sigma$-models from $\CC^d$ to a complex manifold $X$, 
+yielding $d$-polydics algebras of chiral differential operators on~$X$.
+\item Costello and Li quantized BCOV theory, yielding a 3-polydiscs algebra for holomorphic gravity the Calabi-Yau 3-fold~$\CC^3$~\cite{CLbcov}.
+\owen{Please correct this ... I know there are subtleties here.}
+\item The holomorphic twists of 4-dimensional supersymmetric Yang-Mills theories are constructed and analyzed in~\cite{EGW}.
 \end{itemize}
+A number of examples of topological-holomorphic theories have also been constructed, and these yield polydiscs algebras.
+A highlight is Costello's discovery of a theory on $\CC \times \RR^2$ that encodes the Yangian, an infinite-dimensional quantum group~\cite{CosYangian}.
 
@@
 These approaches share a common spirit but have important technical differences.
-A detailed comparison between the versions for locally constant factorization algebras exists~\owen{KSW},
+A detailed comparison between the versions for locally constant factorization algebras exists~\cite{KSW},
 but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
@@
 
-\owen{Discuss twist along circle by automorphism of algebra. Forward ref to example later.}
+There is a variant on this result that plays a role in Section~\ref{s:compact} below.
+Recall that a locally constant sheaf on $S^1$ may have monodromy: 
+starting with a section on a small interval around the circle and then continuing it around the circle (by local constancy),
+it may not match,
+i.e., it may not extend to a global section.
+Instead, transporting values around the circle produces an automorphism of the stalk at a point, known as monodromy.
+Similarly, a locally constant factorization algebra $\cF$ on $S^1$ restricts to a locally constant factorization algebra on $S^1 - \{p\} \cong \RR$,
+so it corresponds to an associative algebra $A$.
+But in transporting elements of $A$ around the circle using this factorization algebra on $S^1$,
+we may find there is an algebra automorphism $\sigma$ appearing as monodromy.
+Then
+\[
+\int_{S^1} \cF = \cF (S^1) \simeq {\rm Hoch}_\bu(A, A_\sigma)
+\]
+where $A_\sigma$ denotes $A$ viewed a bimodule where $A$ acts from the left by multiplication and from the right by multiplication twisted by~$\sigma$.
+\owen{What do you think? Feel free to revise/tidy.}
 
@@
 
-\subsection{Compactification and conformal blocks}\label{s:compact}
+\subsection{Compactification and conformal blocks}
+\label{s:compact}
 
@@
 
-Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is divergence-free to \textit{all} orders in perturbation theory \cite{Wang}.
+Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is divergence-free to \textit{all} orders in perturbation theory~\cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!

### 2024-10-12 draft.tex
not sure what i did

--- 2024-10-12 draft.tex
@@
 \subsection{Reduction vs. chiralization}
-\label{sec: red vs chiral}
 
@@
 there has a been a buzz of recent activity on the renormalization of holomorphic field theories.
-Budzik, Gaiotto, Kulp, Wu, and Yu developed a strategy for proving that in a holomorphic quantum field theory,
-certain graphs (called Laman graphs) do not produce divergences~\cite{BGKWY}.
+In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
+\owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
+\brian{I think it would be more confusing to use a different term.
+But you can explain how it's the issue of `overlapping supports' of distributions; that is, it's an issue about `local integrability'.
+In fact, in their work Axelrod and Singer already use the term ultraviolet.}
+\owen{I agree that UV is a term many people use, but not among most of our target audience, which I view as algebraic geometers and higher algebra folks.
+Why not just say that we're showing no divergences appear and hence counterterms are not needed?}
 The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
 
-Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is divergence-free to \textit{all} orders in perturbation theory \cite{Wang}.
+Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
 In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
@@
 (Similar results hold for topological-holomorphic theories~\cite{WangWilliams}.)
-
-This result ensures the existence of myriad examples of the higher algebraic structures we've discussed:
-it provides the analysis to quantize the kinds of examples from Section~\ref{sec: ex of theories} and hence to produce polydiscs algebras and factorization algebras.
-
+Thus, using the quantization of holomorphic field theories 
 \subsection{Anomalies that obstruct quantization}
@@
 In topological theories, it is known that these sort of anomalies are absent.
+\owen{I am confused by this comment. Aren't there TFTs with anomalies of some sort?}
 For holomorphic theories, however, anomalies are present.
@@
 An anomaly can be represented by a (local) functional on the space of fields.
-In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ and has the form
+In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ is of the form
 \beqn
-c \int \op{Tr}_V (A \wedge \del A \wedge \del A)
-\eeqn
-where $c$ is some nonzero constant and $V$ is some representation of $\lie{g}$.\footnote{In this example, the value of $c$ is the same for both diagrams.}
-Specifically, we have:
+c \int \op{Tr}_M (A \del A \del A)
+\eeqn
+where $c$ is some nonzero constant and $M$ is some representation of $\lie{g}$ (the value of $c$ is the same for both diagrams, in this example).
+Specifically:
 \begin{itemize}
-\item In the first diagram the representation $V$ is the adjoint representation. 
-Thus, this expression vanishes when $\lie{g}$ is simple, e.g., when $\lie{g} = \lie{sl}(n)$.
-\item In the second diagram the representation is that used in defining the $\beta\gamma$ system.
+\item In the first diagram the representation $M$ is the adjoint representation. 
+So, this expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
+\item In the second diagram the representation is $M = V$ (the representation which labels the $\beta\gamma$ system).
 \end{itemize}
-The sum 
-\[
-c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)
-\]
-is the total anomaly for this field theory.
-These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on~$\RR^4$.
-
+Thus, the total anomaly is $c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)$.
+
+These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
 In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly), 
@@
 and one of his leading contributions is referred to as {\em Seiberg duality}.
-It has had a large impact in theoretical physics,
+It has had a large impact in theoretical physics \owen{give the citation number on that paper},
 but the impact in mathematics is much more muted,
-possibly due to the lack of a topological twist for any $\cN=1$ theory.\footnote{Although citations offer only coarse insight into impact, Seiberg's paper introducing the conjecture \cite{Seiberg} has over 1800 citations listed on Inspire but less than 60 citations listed on MathSciNet.}
+possibly due to the lack of a topological twist for any $\cN=1$ theory.
 Such theories do admit {\em holomorphic} twists, however, 
@@
 should produce equivalences between different kinds of 2-dimensional B-model theories;
-these reductions are related to work of Hori and Hori--Tong and its mathematical development, notably by Segal and collaborators~\cite{Hori, HoriTong, HMSegRen, ADS}.
+these reductions are related to work of Hori and Hori--Tong \owen{citations} and its mathematical development by Ed Segal, \owen{list others}.
 
@@
 
+\owen{Do we want $F > N+1$?
+The physicists break things into several cases.
+In particular, I think the moduli is unchanged under quantization only if $F$ is big enough relative to $N$ and $\check{N}$.}
+\brian{I expect we want a similar condition, but I was never able to understand how that appears at the level of factorization algebras.}
+
 \begin{rmk}
@@
 A standard maneuver used in physics is compactification:
-given a field theory $\cT$ in $n$ dimensions, one takes compact ($n$-$k$)-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
-One then considers the push forward of the theory along the projection map $N \times \Sigma \to \Sigma$, to obtain a theory along $\Sigma$.
-(A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along~$N$.)
-
-We now apply this maneuver to holomorphic Seiberg duality:
-by compactifying along a Riemann surface, we should generate a conjectural equivalence between two-dimensional field theories.
-As we will see, this new conjecture resembles the Hori-Tong dualities that have led to Hori-mological mirror symmetry~\cite{Hori, HoriTong, HMSegRen}.
-
-Consider a holomorphic theory defined on $\C^\times \times \C^\times$ 
-and push forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ 
-that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
-In other words, take the torus compactification of the holomorphic theory.
-For a holomorphic factorization algebra $\cF$, 
-the pushforward $\rho_* \cF$ contains a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$ (in essence, by taking the Fourier modes on the torus fibers).
-This locally constant factorization algebra corresponds to an $E_2$-algebra.\footnote{Recall Section~\ref{sec: red vs chiral}, where we compactified on a circle and then broke things up using Fourier modes.
-This construction extracted an associative ($E_1)$ algebra that is a Weyl algebra of a formal loop space from a holomorphic field theory on~$C^\times$.}
-
-Let's start with holomorphic QCD and see what Seiberg duality would imply.
-On the electric side, 
-we have a two-dimensional holomorphic BF theory coupled to a complex two-dimensional $\beta\gamma$ system.
-By itself, the $\beta\gamma$ system with target $\C^{NF}$ yields, by torus compactification, 
-the topological B-model theory whose target is the formal double loop space~$L^2\C^{NF}$. 
+given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
+One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
+A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
+
+We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
+In other words, this is the $T^2$ compactification of the holomorphic theory.
+For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
+We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.
+
+Let's first consider the electric side, 
+which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
+The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
 The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
 where $z,w$ are formal loop parameters that we imagine as describing the winding of the two circles we have compactified. 
-The dimensional reduction then picks out the constant modes along each circle, 
-so we find a topological B-model with target $\C^{NF}$.
-Similarly, holomorphic BF theory dimensionally-reduces to topological BF theory,
-which can be viewed as the B-model with target the classifying space~$BGL(N)$.
-In sum, the dimensional reduction of electric holomorphic QCD is the topological B-model with target the stack $\C^{NF} / GL(N)$.
+The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
+Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
+In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
 As a derived mapping space, the moduli of solutions is given by
@@
 \eeqn
-Dimensional reduction of the factorization algebra of observables produces the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.
+The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.
 
@@
 \beqn
-\left(\C^{(F-N)F} / GL(F-N) \right) \times \C^{F^2} .
+\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
 \eeqn
 The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
-The potential for the Landau--Ginzburg model is precisely the potential $\check{W}$ seen in~\eqref{eqn:checkW}.
-This procedure produces an $E_2$ algebra by deforming the differential on the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$, 
-namely use the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
-
-Holomorphic Seiberg duality thus predicts an equivalence of two-dimensional topological field theories,
+The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.
+
+Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
 or at least of $E_2$-algebras.
 
-\begin{conj*}
-There is an equivalence of $E_2$ algebras between
+\begin{conj}
+There is an equivalence of the following $E_2$ algebras:
 \begin{itemize} 
-\item the {\em electric} $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
-\item the {\em magnetic} $E_2$ algebra of polyvector fields on the stack $(\C^{(F-N)F} / GL(F-N)) \times \C^{F^2}$ with differential~$\{\check{W},-\}$. 
+\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
+\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
 \end{itemize}
-\end{conj*}
+\end{conj}
 
@@
 
-This conjectured equivalence resembles Hori-Tong dualities.
-Note that it is often said that Hori-Tong dualities are like Seiberg dualities!
-We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{KuzHPD, ThomasHPD, Perry} --- might apply here, and also feed back towards holomorphic Seiberg duality.
+This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
+(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
+We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
+For instance, in this mathematical work, 
+one sees different choices of GIT quotients associated to the same stack yielding equivalent derived categories (and cousins),
+and these quotients only know about certain pieces of the stack,
+an issue we have flagged in our comparison of the moduli stack and the moduli space.
 

### 2024-10-12 draft.tex

--- 2024-10-12 draft.tex
@@
 
-\owen{Draw some 2d pictures and unpack a little. Mention pair of pants \& OPE} 
-In this sense, it captures the dependence on the discs.
+To illustrate the idea, we take $d=2$ and draw a point in the configuration space~$\Disc_2(2)$:
+\begin{center}
+  \begin{tikzpicture}
+   \draw[semithick] (0,0) circle (2.5);
+   \draw[semithick] (0,0) circle (0.75);
+   \draw[semithick] (1,1) circle (0.5);
+   \fill (0,0) circle (0.05) node [below right] {$0$};
+   \fill (1,1) circle (0.05) node [below right] {$p$};
+\end{tikzpicture}
+\end{center}
+where there is a disc centered at the origin with larger radius and a disc centered at a point~$p$ with smaller radius.
+This picture clearly resembles the ``pair of pants" product from two-dimensional topological field theories, but pressed flat.
+To a physicist, this picture encodes a way of multiplying an operator with support near 0 by an operator with support near $p$ to get an operator with support near the origin (although the support is larger);
+they use the term {\em operator product expansion} when they express this multiplication in formulas.
 

### 2024-10-13 draft.tex
added abstract and improved pair of pants

@@
 The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
+
+\begin{abstract}
+Aimed at complex geometers and representation theorists, this survey explores higher dimensional analogues of the rich interplay between Riemann surfaces, Virasoro and Kac-Moody Lie algebras, and conformal blocks.
+We introduce a rich source of examples from physics --- field theories that are holomorphic in nature, such as holomorphic Chern-Simons theory --- and interpret them as (derived) moduli spaces in complex geometry;
+no comfort with physics is presumed.
+We then describe frameworks for quantizing such moduli spaces, 
+offering a systematic generalization of vertex algebras and conformal blocks via factorization algebras,
+and we explain how holomorphic field theories provide examples of these higher algebraic structures.
+We finish by describing how the conjecture of Seiberg duality predicts a surprising relationship between holomorphic gauge theories on algebraic surfaces and how it suggests analogues of the Hori-Tong dualities already studied by algebraic geometers.
+\end{abstract}
 
@@
    \draw[semithick] (0,0) circle (2.5);
-   \draw[semithick] (0,0) circle (0.75);
+   \draw[semithick] (-0.5,0) circle (1);
    \draw[semithick] (1,1) circle (0.5);
-   \fill (0,0) circle (0.05) node [below right] {$0$};
-   \fill (1,1) circle (0.05) node [below right] {$p$};
+   \fill (-0.5,0) circle (0.05) node [below right] {$p$};
+   \fill (1,1) circle (0.05) node [below right] {$q$};
 \end{tikzpicture}
 \end{center}
-where there is a disc centered at the origin with larger radius and a disc centered at a point~$p$ with smaller radius.
+where the outermost disc is the unit disc,
+the input disc centered at the point~$p$ has larger radius, 
+and the input disc centered at the point~$q$ has smaller radius.
+By varying the locations of $p$ and $q$ and by varying the radii of the inner circles,
+we move through~$\Disc_2(2)$.
+%A bit of thought reveals that $\Disc_2(2)$ is homotopy equivalent to~$S^1$.
+
 This picture clearly resembles the ``pair of pants" product from two-dimensional topological field theories, but pressed flat.
@@
 
-This operad was invented by algebraic topologists to capture the rich structure of the $d$-fold based loop space $\Omega^d X$ of a pointed space $(X,x)$.
+This operad was invented by algebraic topologists to capture the rich algebraic structure of the $d$-fold based loop space $\Omega^d X$ of a pointed space $(X,x)$.
 (The usual homotopy group $\pi_d(X)$ is a shadow of this richer structure.)
@@
 Here we will analyze the cohomology of the cooperad and what kind of information it encodes, 
-with a view towards motivating the relationship to vertex algebras.
+aimed at relating it to vertex algebras.
 The takeaway from the discussion below is that one can read off the modes $a_{(n)}$ that assemble into the vertex operator $Y(a,z)$ using a $1$-polydiscs algebra.
@@
 so it cannot be inserted into any finite radius disk.
+Nonetheless, the associativity of composition in $\PDisc_1$ casts the shadow of the Cousin property or Borcherds product in vertex algebras.
 

### 2024-10-13 draft.tex
last stuff

@@
 Aimed at complex geometers and representation theorists, this survey explores higher dimensional analogues of the rich interplay between Riemann surfaces, Virasoro and Kac-Moody Lie algebras, and conformal blocks.
-We introduce a rich source of examples from physics --- field theories that are holomorphic in nature, such as holomorphic Chern-Simons theory --- and interpret them as (derived) moduli spaces in complex geometry;
+We introduce a panoply of examples from physics --- field theories that are holomorphic in nature, such as holomorphic Chern-Simons theory --- and interpret them as (derived) moduli spaces in complex geometry;
 no comfort with physics is presumed.
@@
 offering a systematic generalization of vertex algebras and conformal blocks via factorization algebras,
-and we explain how holomorphic field theories provide examples of these higher algebraic structures.
+and we explain how holomorphic field theories generate examples of these higher algebraic structures.
 We finish by describing how the conjecture of Seiberg duality predicts a surprising relationship between holomorphic gauge theories on algebraic surfaces and how it suggests analogues of the Hori-Tong dualities already studied by algebraic geometers.
@@
 and it continues to grow as there is a lot to explore here.
-Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, and \cite{BBBDN}, 
+Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, \cite{BBBDN}, and \cite{AlfonsiYoungHC},
 where our own background and interests (and unfortunately, our ignorance) have shaped this list.
@@
 Yuri Manin was a pioneer into this intellectual region where field theory, complex geometry, and homotopical algebra meet,
-and his work --- beyond the beautiful results --- also gestured at rich possibilities for novel and powerful forms of geometry and physics and algebra,
-summoning these possibilities towards their current unfolding today into derived geometry and operadic structures in a broad sense.
-We quote \cite{ManFrob} in our epigraph, which synthesizes stacks and operads and Frobenius structures into a beautiful and coherent view on mirror symmetry.
-His \cite{ManGauge} is rich with deep reformulations of supersymmetric field theory that connect it to complex geometry,
-and it is a source of many inspirations;
-we are also quite fond of \cite{BeiMan, ManNewDim} from roughly the same era.
-Anyone interested in mathematics and physics and, especially, their relationship will delight in~\cite{ManMP}.
+and his work --- beyond the beautiful results --- also gestured at rich possibilities for novel and powerful forms of geometry and physics and algebra.
+His writing summoned these possibilities out the realm of dreams and towards their current unfolding today into derived geometry and higher operadic structures.
+To whit, our epigraph comes from \cite{ManFrob}, which synthesizes stacks and operads and Frobenius structures into a beautiful and coherent view on mirror symmetry.
+But we could equally well have quoted his \cite{ManGauge}, which is rich with deep reformulations of supersymmetric field theory that connect it to complex geometry,
+or his \cite{BeiMan, ManNewDim} from roughly the same era.
+Anyone interested in mathematics and physics, and especially their relationship, will delight in~\cite{ManMP}.
 
@@
 OG had the unbelievable luck to overlap with Manin and thus to take several courses and have many conversations with him, 
-getting to witness the personification of the Platonic idea of mathematician as intellectual.
+getting to witness his personification of the Platonic idea of mathematician as intellectual in the broadest sense.
 We both spent extensive time, for example, at the Max Planck Institute for Mathematics,
@@
 and we thank them for their generosity with ideas and examples.
-We owe particular thanks to Kevin Costello, Richard Eager, Chris Elliott, Davide Gaiotto, Nik Garner, Vasily Gorbounov, Zhengping Gui, Benjamin Hennion, Mikhail Kapranov, Si Li,  Natalie Paquette, Nik Rozenblyum,  Ingmar Saberi,  Pavel Safronov,  Matt Szczesny, Ed Segal,  Johannes Walcher, Minghao Wang, and Jie Zhou.
-\owen{Kasia Budzik? Kulp?}
+We owe particular thanks to Kasia Budzik, Dylan Butson, Kevin Costello, Richard Eager, Chris Elliott, Davide Gaiotto, Nik Garner, Vasily Gorbounov, Zhengping Gui, Benjamin Hennion, Mikhail Kapranov, Justin Kulp, Si Li,  Natalie Paquette, Surya Raghavendran, Nick Rozenblyum,  Ingmar Saberi,  Pavel Safronov,  Matt Szczesny, Ed Segal,  Johannes Walcher, Minghao Wang, Jingxiang Wu, Philsang Yoo, and Jie Zhou.
 
@@
 yielding $d$-polydics algebras of chiral differential operators on~$X$.
-\item Costello and Li quantized BCOV theory, yielding a 3-polydiscs algebra for holomorphic gravity the Calabi-Yau 3-fold~$\CC^3$~\cite{CLbcov}.
-\owen{Please correct this ... I know there are subtleties here.}
+\item Costello and Li quantized BCOV theory, yielding a 3-polydiscs algebra for holomorphic gravity on the Calabi-Yau 3-fold~$\CC^3$~\cite{CLbcovOC}.
 \item The holomorphic twists of 4-dimensional supersymmetric Yang-Mills theories are constructed and analyzed in~\cite{EGW}.
@@
 where $A_\sigma$ denotes $A$ viewed a bimodule where $A$ acts from the left by multiplication and from the right by multiplication twisted by~$\sigma$.
-\owen{What do you think? Feel free to revise/tidy.}
+%\owen{What do you think? Feel free to revise/tidy.}
 

### 2024-10-15 draft.tex
improved acknowledgments

@@
 We owe particular thanks to Kasia Budzik, Dylan Butson, Kevin Costello, Richard Eager, Chris Elliott, Davide Gaiotto, Nik Garner, Vasily Gorbounov, Zhengping Gui, Benjamin Hennion, Mikhail Kapranov, Justin Kulp, Si Li,  Natalie Paquette, Surya Raghavendran, Nick Rozenblyum,  Ingmar Saberi,  Pavel Safronov,  Matt Szczesny, Ed Segal,  Johannes Walcher, Minghao Wang, Jingxiang Wu, Philsang Yoo, and Jie Zhou.
+
+The prompt to write this survey came from Andrey Lazarev, and we thank him for his patience and encouragement during the long period of putting it together.
+
+The National Science Foundation supported O.G. through DMS Grant 2042052 during the writing of this paper.
+The Max Planck Institute for Mathematics has hosted both O.G. and B.W. throughout their careers, and it provided a wonderful environment for O.G. during the last stages of writing.
 

### 2025-01-10 draft_preMinyong.tex
o begins to implememt minhyongs suggestions

--- 2024-10-15 draft.tex
@@
 As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
-(For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
+(For $Y = V$ a complex vector space, a ``derived'' enhancement includes the higher dimensional  cohomology $H^*(X, \cO) \otimes V$.)
 In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,

### 2025-01-10 draft.tex
the seal is broken

@@
 \usepackage{epigraph}
+
+\setlength\epigraphwidth{.8\textwidth}
 
@@
 \setlength{\parindent}{0cm}
-\setcounter{tocdepth}{1}
+\setcounter{tocdepth}{2}
 
@@
 
-\def\g{{\mathfrak g}}
-\def\U{{\rm U}}
-\def\mc{\mathcal}
-\def\mcol{\, | \,}
-\def\ot{\otimes}
-\def\Disj{\operatorname{Disj}}
-\def\Open{\operatorname{Open}}
-\def\Vect{\operatorname{Vect}}
-\def\jou{{\mathtt{j}}}
-\def\bgamma{{\mathbf{\gamma}}}
-\def\bbeta{{\mathbf{\beta}}}
-\def\CDO{{\cC\cD}}
-\def\SU{{\rm SU}}
-\def\sfa{\mathsf{a}}
-\def\del{\partial}
-\def\til{\Tilde}
-\def\Sol{\text{Sol}}
-\def\Spec{\text{Spec}}
-\def\C{{\mathbb{C}}}
-
 \DeclareMathOperator{\Schw}{Schw}
@@
 \def\owen#1{{\textcolor{red!50!black}{OG: {#1}}}}
-
-%%% TIKZ STUFF
-\usepackage{tikz,tikz-cd}
-\usetikzlibrary{arrows,shapes}
-\usetikzlibrary{trees}
-\usetikzlibrary{matrix,arrows}
-\usetikzlibrary{positioning}
-\usetikzlibrary{calc,through}
-\usetikzlibrary{decorations.pathreplacing}
-\usepackage{pgffor}
-
-%%Feynman diagrams
-\usetikzlibrary{decorations.pathmorphing}
-\usetikzlibrary{decorations.markings}
-\tikzset{
-	% >=stealth', %%  Uncomment for more conventional arrows
-    vector/.style={decorate, decoration={snake}, draw},
-	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
-	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
-    fermion/.style={draw=black, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
-    fermionbar/.style={draw=black, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
-    fermionnoarrow/.style={draw=black},
-    gluon/.style={decorate, draw=black,
-        decoration={coil,amplitude=4pt, segment length=5pt}},
-    scalar/.style={dashed,draw=black, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
-    scalarbar/.style={dashed,draw=black, postaction={decorate},
-        dwecoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
-    scalarnoarrow/.style={dashed,draw=black},
-    electron/.style={draw=black, postaction={decorate}/,
-        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
-	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
-}
 
@@
 As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
-(For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
-In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
-and this derived moduli space encodes solutions to
-a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it is due to the original notation people used.}
-Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
-Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformation quantization); 
-the relevant moduli space being the derived mapping space between complex manifolds.
+For $Y = V$ a complex vector space, this ``derived'' enhancement is simply the entire  cohomology $H^*(X, \cO) \otimes V$, and not just the global functions $H^0(X,\cO) \otimes V$.
+There are holomorphic theories whose derived moduli spaces are encoded by cohomology groups of holomorphic vector bundles.
+(A physicist might view them as analogs of scalar field theories.)
 
@@
 
-It is natural to wonder how the myriad tools and computations deployed on a supersymmetric theory carry over to this twist 
+It is natural to wonder how the myriad tools and computations deployed on a supersymmetric theory carry over to this holomorphic twist 
 and, conversely, whether information can flow back from a holomorphically twisted theory to the original supersymmetric theory, 
-much as TFTs have enriched the understanding of supersymmetric theories.
+much as TFTs have enriched physicists' understanding of supersymmetric theories.
 In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''
@@
 
-As a final motivational remark, we note in one complex dimension (i.e., working on Riemann surfaces), 
+As a final motivational remark, we note that in one complex dimension (i.e., working on Riemann surfaces), 
 holomorphic field theories appear as chiral conformal field theories (CFTs) on Riemann surfaces. 
-The study of CFTs--- whose manifestations in mathematics include vertex algebras, affine Lie algebras, and loop groups --- have had a strong impact in mathematics,
+The study of CFTs --- whose manifestations in mathematics include vertex algebras, affine Lie algebras, nonabelian theta functions, and loop groups --- have had a strong impact in mathematics,
 so it is natural to explore higher-dimensional analogs.
@@
 Our survey's focus will be narrow:
-it is upon higher dimensional versions of the relationship between geometry and algebraic structures like Lie algebras, Poisson algebras, and vertex algebras.
+it is upon higher dimensional versions of the relationship between complex geometry and algebraic structures like Lie algebras, Poisson algebras, and vertex algebras.
 We will emphasize analogies to TFTs (such as the Gerstenhaber algebras appearing in mirror symmetry) and CFTs (such as the affine Lie algebras relating to moduli of $G$-bundles on Riemann surfaces),
@@
 A community has formed, involving both mathematicians and physicists, to explore and exploit these relationships,
-and it continues to grow as there is a lot to explore here.
+and it continues to grow as there is a lot to explore.
 Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, \cite{BBBDN}, and \cite{AlfonsiYoungHC},
@@
 Beyond his writing, however, we have also benefited throughout our careers from the attitudes and atmosphere that his persona modeled and spread among mathematicians:
-a generosity with ideas but also poetry and literature, an exquisite care and sensitivity to organizing and explaining mathematics (and much else),
+a generosity with mathematical ideas but also the sharing of poetry and literature, 
+an exquisite care and sensitivity to organizing and explaining mathematics (and much else),
 and a kindness in conversation, where he brought his whole attention to you.
@@
 getting to witness his personification of the Platonic idea of mathematician as intellectual in the broadest sense.
-We both spent extensive time, for example, at the Max Planck Institute for Mathematics,
+We also both spent extensive time, for example, at the Max Planck Institute for Mathematics,
 which is suffused with his spirit.
@@
 
-We begin by sketching what a classical field theory is, somewhat impressionistically, and then offer some concrete examples.
+We begin by explaining the basic framework of classical field theory, with a few examples.
+For a mathematician, the key point might be that physics suggests certain systems of equations are particularly important and studies their spaces of solutions, 
+often unearthing aspects that might not catch a mathematician's eye.
+In other words, physics can be a source of interesting moduli spaces.
+
+We then offer a quick overview of derived geometry, aiming to motivate and not to give a systematic treatment.
+For this survey, comfort with basic homological algebra and sheaf cohomology will suffice, 
+so we will explain how our terminology relates to those notions.
+In
+
+\subsection{A first pass}
 
@@
 \item a manifold $M$ that plays the role of ``spacetime,''
-\item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
-\item a system of partial differential equations (PDE) for the fields, known as the equations of motion.
+\item a space of ``fields,'' typically the sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
+\item a system of partial differential equations (PDE) for the fields, known as the ``equations of motion.''
 \end{itemize}
 These equations of motion are variational: 
-they are the Euler-Lagrange equations of an action functional on the space of fields,
-so that solutions to these PDE are the critical points, in a sense, of some function.
+the solutions to these PDE are the critical points, in a sense, of some function,
+called an ``action functional.''
+(Variational PDE are often called Euler-Lagrange equations.)
 In practice an action functional is a formal expression, 
 written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
+
 A few examples will illuminate this sketch.
+We begin by giving two examples that depend on Riemannian geometry, 
+then give an example of a topological field theory,
+and finally give an example of a holomorphic field theory.
+All the equations that show up are well-known to geometers.
 
@@
 and let $\d{\rm vol}_g$ denote the associated volume form.
+In the case $M = \RR^n$ with the Euclidean inner product, the Laplace-Beltrami operator is the differential operator
+\[
+\Delta = \frac{\partial^2}{\partial x_1^2} + \cdots + \frac{\partial^2}{\partial x_n^2}.
+\]
 Let the space of fields be the smooth functions $C^\infty(M)$.
@@
 
-We now describe an example of a theory whose space of solutions is a moduli space of interest in geometric topology.
+We now describe an example of a theory whose space of solutions is a moduli space of interest in geometric topology: character varieties.
 
@@
 we suggest \cite{DeligneFreed}.
+In the appendix we describe many more examples of holomorphic field theories and describe their spaces of solutions using the language of derived geometry, which we discuss next.
+
+\subsection{A dose of derived geometry}
+\label{sec: DAG}
+
 Recently there is an effort to revisit field theory with insights from derived geometry.
@@
 which we will use to produce examples of higher algebras.
-
-\subsection{More examples}
-\label{sec: ex of theories}
-
-In this section we describe several examples of holomorphic field theories,
-in the style we used for holomorphic Chern-Simons theory.
-Our aim here is to give a sense of how take physical ideas and find holomorphic analogs.
-
-In traditional physics there are a few basic types of field theories, 
-and they can be assembled into combinations,
-of which the Standard Model offers a nice example.
-The basic types are\footnote{For the experts, we remark that we focus above on the field content that motivates or characterizes, and mostly ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
-\begin{itemize}
-\item {\em Scalar} field theories where the fields are maps from $M$ to a vector space $V$, or natural generalizations like taking sections of a vector bundle $V \to M$.
-The Higgs boson appears as part of a scalar field theory.
-\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space (in the sense of supermathematics), typically a section of a spinor bundle.
-Such theories are often used to describe matter, such as electron fields.
-\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as nonlinear generalizations of scalar field theories.)
-\item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
-\item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
-\end{itemize}
-The Standard Model involves the first three types,
-and the different fields interact in intricate ways.\footnote{For instance, the scalar and fermionic fields are sections of associated bundles to the principal bundle appearing in the gauge theory.}
-
-There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs.
-See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.}
-To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
-we describe them in several ways: 
-in terms of PDE and action functionals but also as moduli spaces.
-We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
-and see \cite{AlfonsiYoung} and \cite{Steffens23} for recent work on this topic.
-
-For an example that mixes several types, see Section~\ref{sec: seiberg}
-where we discuss a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks.
-
-A motivation for us to explore holomorphic field theories is that physical insights and conjectures, such as Seiberg duality, translate into surprising predictions in the holomorphic setting,
-which is typically more accessible for mathematics.
-(One might also hope that progress in the holomorphic setting then feeds back useful insights to physics.)
-
-\subsubsection{Holomorphic scalar field theories}
-
-We met the standard example of a scalar field theory in Example~\ref{eg: massless scalar},
-where the field $\phi$ a smooth real-valued function on a manifold $M$
-and the equation of motion is $\Delta \phi = 0$,
-so that the moduli space of solutions is the space of harmonic functions on~$M$.
-
-A natural analogue is to have the field be a complex-valued function $\gamma$ on a complex manifold $M$ with an equation of motion $\dbar \gamma = 0$,
-so that the moduli space of solutions is the space of holomorphic functions on~$M$.
-
-Notice that we are shifting from a second-order differential operator $\Delta$ to first-order differential operators $\dbar$.
-Reworking a theory to express its equations of motion using first-order operators is sometimes called the first-order formalism.
-
-We will start with $M$ being a Riemann surface for simplicity.
-Consider the action functional
-\beqn
-\label{eqn: 1d betagamma}
-\int \beta \wedge \dbar \gamma
-\eeqn
-where $\beta$ is a $(1,0)$-form on $M$.%\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
-%which we now think about as having its own degrees of freedom. 
-%\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
-Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
-so that $\beta$ should be a holomorphic $1$-form.
-
-It should seem reasonable to view two solutions $\beta_1$ and $\beta_2$ as equivalent if they differ by a $\dbar$-exact term.
-If one imposes this equivalence relation (a kind of ``gauge symmetry''),
-then one is on the path towards setting up the theory in the Batalin-Vilkovisky formalism.
-
-Derived geometry is the mathematical version of BV formalism.
-From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
-\[
-T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\Omega^1_{hol}),
-\]
-where $\Omega^1_{hol}$ is the sheaf of holomorphic one-forms.
-
-\begin{rmk}
-It is possible to directly relate the usual massless scalar field theory to this $\beta\gamma$-system as follows.
-
-When $M$ is two-dimensional, oriented and Riemannian,
-we can view $M$ as equipped with a complex structure.
-Every complex-valued harmonic function then decomposes as a sum of a holomorphic and anti-holomorphic function. 
-That is, if we complexify the scalar field $\phi$, 
-we can view it as a pair of fields $\gamma$ and $\Bar{\gamma}$,
-where the equation of motion of $\gamma$ is $\dbar \gamma = 0$ and the equation of motion is $\partial \Bar{\gamma} = 0$.
-These components are sometimes called the chiral and anti-chiral ``sectors.''
-
-The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite[Chapter 3]{Polchinski}.
-There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$-system encoding the antichiral sector of the free boson.
-To recover the full boson, one must couple the chiral and anti-chiral sectors.
-See \cite{Kapustin:2005pt,GGW} for more details.~\hfill$\Diamond$
-\end{rmk}
-
-This example admits a natural generalization to an arbitrary complex manifold.
-The input data is a complex manifold $X$ of arbitrary complex dimension $n$, 
-together with a holomorphic vector bundle $V$ on~$X$.
-(Above we took this bundle to be trivial.)
-Each field of the theory consists of a pair $(\gamma,\beta)$ where 
-\[
-\gamma \in \Gamma(X,V) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(X,V^*) .
-\]
-The action functional is 
-\[
-\int_X \beta \wedge \dbar \gamma
-\]
-and the equations of motion are
-\[
-\dbar \gamma = 0 = \dbar \beta.
-\]
-Solutions consist of a holomorphic function $\gamma$ and a holomorphic $(n,n-1)$-form.
-We again suggest to identify solutions to the second equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
-
-\subsubsection{Holomorphic fermions}
-
-It is straightforward to modify the example above to allow holomorphic {\it super} vector bundles,
-i.e., holomorphic $\ZZ/2$-graded vector bundles.
-
-For example, given a holomorphic vector bundle $V$ on a complex $n$-fold~$X$,
-let $\Pi V$ denote the parity-reversed vector bundle,
-i.e., we now give $V$ an odd grading.
-There is a $bc$ system that is the fermionic analog of the $\beta\gamma$ system.
-The fields of the theory consist of a pair $(c,b)$ where 
-\[
-c \in \Gamma(X,\Pi V) \quad\text{and}\quad b \in \Omega^{n,n-1}(X,\Pi V^*) .
-\]
-Thus, $b$ and $c$ are fermionic fields.
-The action functional is 
-\[
-\int_X b \wedge \dbar c,
-\]
-and the equations of motion are
-\[
-\dbar c = 0 = \dbar c.
-\]
-We again suggest to identify solutions to the equation $\dbar c = 0$ that differ by a $\dbar$-exact form.
-
-There is another class of fermionic theories that is quite interesting as they are more fundamental than the previous example.
-Let $X$ be a complex $n$-fold and $L \to X$ a line bundle on $X$ such that
-\begin{itemize}
-\item $n \equiv 1 \mod 4$ (i.e., $n=4k+1$ for some $k$) and
-\item $L$ is a square root of the canonical bundle $L^{\otimes 2} \cong K_X$.
-\end{itemize}
-A field is a section
-\[
-\psi \in \Omega^{0,2k}(X,\Pi L),
-\]
-and the action functional is
-\[ 
-\int_X \psi \wedge \dbar \psi .
-\]
-The equation of motion for this system is simply $\dbar \psi = 0$.
-To study the quantization of this system, it is necessary to identify solutions that differ by $\dbar$-exact terms (and identifying identifications that differ by $\dbar$-exact terms, etc.).
-
-From the point of view of derived geometry, the cochain complex
-\[
-\Omega^{0,\bullet}(X, \Pi L)[2k]
-\]
-presents a derived super stack that should be viewed as the moduli of solutions for this theory.
-
-\subsubsection{Holomorphic $\sigma$-models}
-
-A $\sigma$-model is a field theory whose space of fields contains a mapping space $\Map(M,N)$.
-When $N = \RR$, this mapping space simply becomes functions and so the $\sigma$-model reduces to a scalar field theory.
-
-There is a natural generalization of the $\beta\gamma$ system to a $\sigma$-model.
-Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
-The fields are a pair $(\gamma, \beta)$ where
-\[
-\gamma \in \Map(M,N) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(M,\gamma^* T^*_N) .
-\]
-Note that $\dbar \gamma$ lives in $\Omega^{0,1}(M, \gamma^* T_N)$, 
-a section of the pullback of the tangent bundle of the target.
-The action functional is 
-\[
-\int_X \beta \wedge \dbar \gamma,
-\]
-where we use the canonical evaluation pairing between the pullback of the tangent and cotangent bundles of the target.
-The equations of motion are
-\[
-\dbar \gamma = 0 = \dbar \beta,
-\]
-so that solutions consist of a holomorphic map $\gamma: M \to N$ and a holomorphic section $\beta$ of the pullback tangent bundle.
-As usual, we suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
-
-From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
-\[
-T^*[-1] \Map_\dbar(M,N) ,
-\]
-where $\Map_\dbar(M,N)$ is the derived stack of holomorphic maps $M \to N$.
-This is a natural space to study in complex geometry.
-
-\subsubsection{Holomorphic gauge theories}
-\label{sec: hol BF dfn}
-
-We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
-There is a another class of holomorphic gauge theories 
-defined on any complex manifold, with no restriction on dimension 
-and without the need for a Calabi--Yau structure.
-
-Let $X$ be a complex manifold of complex dimension~$n$.
-Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra~$\fg$.
-Fix a holomorphic principal $G$-bundle $P \to X$.
-The fields consist of pairs $(A,B)$ where 
-\[
-A \in \Omega^{0,1}(X, \fg_P)
-\] 
-where $\fg_P$ is the adjoint bundle of $P$ and
-\beqn
-B \in \Omega^{n,n-2}(X, \fg_P^*) ,
-\eeqn
-where $\fg_P^*$ is the coadjoint bundle of $P$. 
-The action functional is 
-\beqn
-S(A,B) = \int_X \langle B \wedge F_A \rangle
-\eeqn
-where $F_A$ is the curvature of the connection $A$.
-The equations of motion are
-\begin{align*}
-F_A^{0,2} = \dbar A + \frac12 [A,A] & = 0 \\
- \dbar B + [A,B] & = 0.
-\end{align*}
-A solution to the first equation provides a new $\dbar$-connection 
-\[
-\dbar_A = \dbar_P + [A,-] 
-\]
-on $P$.
-A solution to the second equation is a $\dbar_A$-flat $(n,n-2)$-form-valued section of the coadjoint bundle.
-This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.
-
-\begin{rmk}
-Notice that this action functional resembles the $\beta\gamma$ system, 
-with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
-One also recognizes this action functional as a holomorphic analog of topological $BF$ theory. 
-\end{rmk}
-
-It is natural to view two connections as equivalent if they are related by a gauge transformation
-and to identify $B$-solutions that are related by a $\dbar_A$-exact term.
-From the point of view of derived geometry,
-we thus see holomorphic BF theory as describing the moduli space
-\[
-T^*[-1] \Bun_G(X),
-\]
-if we run over all principal bundles.
-
-\begin{rmk}
-Holomorphic BF theory exhibits some interesting properties at the quantum level,
-at least perturbatively.
-For example, in \cite[\S3.2]{BGKWWY} it is shown that on $X = \C^2$ 
-the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
-More precisely, to first-order in perturbation theory, 
-the divergence-free component of the stress tensor is rendered cohomologically trivial at one-loop in perturbation theory.
-In other words, the quantum theory appears to be totally ``invariant'' under divergence-free vector fields,
-although not all vector fields (as in the case of a TFT).
-\end{rmk}
-
-It is possible to formulate holomorphic versions of higher abelian gauge theories,
-associated to moduli spaces of holomorphic $k$-gerbes with connection, see \cite{SWtensor,BWfive}.
-
-\subsubsection{Interlude on holomorphic field theories as chiral sectors}
-
-Every holomorphic theory we have introduced so far has a ``kinetic term'' (the quadratic term in the action functional) that only involves $\dbar$.
-Thus the linearized equations of motion always have the form $\dbar \phi = 0$,
-so that they manifestly relate to holomorphic functions (or sections).
-There are, however, holomorphic theories with a different flavor.
-
-\begin{comment}
-A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
-Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
-We saved this example for last since its holomorphic analog is a bit more elusive than the previous examples.
-\end{comment}
-
-We start with complex dimension~$1$.
-The usual scalar field theory can be written as 
-\[
-\int_{\Sigma} \phi \wedge \del \dbar \phi, 
-\]
-where $\Sigma$ is a Riemann surface.
-Using integration by parts, one can use instead the action functional
-\[
-\int_{\Sigma} \partial \phi \wedge \dbar \phi.
-\]
-This theory is not holomorphic, but we can force it to be holomorphic by demanding that $\dbar \phi = 0$.
-Importantly, this constraint is \textit{not} an equation of motion.
-When we impose this constraint, we can rewrite the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
-\beqn\label{eqn:scalar1}
-\int_\Sigma \alpha \wedge \dbar (\del^{-1} \alpha) ,
-\eeqn
-where $\alpha$ plays the role of $\partial \phi$.
-In this theory the kinetic term is the whole action,
-and it has a rather different flavor from the examples we have seen so far.\footnote{This action functional is a precursor to the ``holomorphic gravity'' theory we meet next, 
-known as Kodaira--Spencer theory.}
-One might call this the {\em chiral sector} of the free scalar theory,
-as it consists of the complex-valued scalar fields satisfying a ``chiral'' constraint.
-
-There is a higher-dimensional analog of the chiral sector of the scalar field.
-Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
-The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
-\beqn
-\del \alpha = 0.
-\eeqn
-(When $n=0$ and $X$ is simply a Riemann surface, 
-this constraint is automatic.)
-The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
-Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
-\beqn
-\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
-\eeqn
-where $C \in \Omega^{2n+1}(X)$.
-For more details we refer to~\cite{GRW_WZW}.
-
-The reader may (and should) be concerned with the apparent ``non-local'' form of the action functional in \eqref{eqn:scalar1}.
-This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint~\cite{CLbcov}.
-
-\subsubsection{Holomorphic ``gravity''}
-
-Any theory of gravity involves, in part, metric structure on a given manifold,
-so that solutions to the equations of motion produce metrics satisfying a PDE. 
-For a perturbative gravity theory,
-one studies deformations of some metric structure on a manifold.
-There is a holomorphic avatar of this situation: deformations of complex structure. 
-The first appearance of such a theory was motivated by topological string theory and involves complex structures on Calabi--Yau threefolds~\cite{BCOV}.
-It is known \textit{Kodaira--Spencer gravity} or the Kodaira-Spencer field theory,
-due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
-It has been pursued mathematically by Costello and Li as an approach to the quantum higher genus $B$-model, starting with \cite{CLbcov} and continuing in a series of papers.
-In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
-here we focus just on the most familiar three-dimensional version.
-%The fields consist of pairs $(\mu, \eta)$ where
-%\begin{align*}
-%\mu & \in \Omega^{0,1}(X, \T_X) \\
-%\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
-%\end{align*}
-%The action functional is
-%\beqn
-%\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
-%\eeqn
-%where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.
-
-%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
-Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega$ the holomorphic volume form.
-The primary field of Kodaira-Spencer theory is 
-\beqn
-\mu \in \Omega^{0,1}(X,\T_X),
-\eeqn 
-a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
-A constraint is imposed on these sections:
-we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
-\[
-{\rm div}_\Omega(\mu) = 0,
-\]
-i.e., its divergence vanishes.
-In short, the fields are divergence-free vector fields.
-The classical equation of motion is 
-\beqn
-\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
-\eeqn
-where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket.\footnote{On vector fields, $[-,-]_{SN}$ is simply the Lie bracket, and it is the natural multilinear extension to polyvector fields.}
-The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
-Formulating the action functional to obtain this equation of motion is a little involved, 
-and we refer to \cite{CLbcov} for a systematic discussion.
-
-\begin{rmk}
-The kinetic term of this theory has the form
-\[
-\int_X \Omega \wedge \left[\Omega \vee \left(\frac12 \mu\, \dbar \del^{-1} \mu\right) \right]
-\]
-and hence resembles the chiral sector of the scalar, which we just discussed in the preceding example.
-\end{rmk}
 
@@
 
+\section*{Appendix: A zoo of holomorphic field theories}
+\label{sec: ex of theories}
+
+In this section we describe several examples of holomorphic field theories,
+in the style we used for holomorphic Chern-Simons theory.
+Our aim here is to give a sense of how take physical ideas and find holomorphic analogs.
+
+In traditional physics there are a few basic types of field theories, 
+and they can be assembled into combinations,
+of which the Standard Model offers a nice example.
+The basic types are\footnote{For the experts, we remark that we focus above on the field content that motivates or characterizes, and mostly ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
+\begin{itemize}
+\item {\em Scalar} field theories where the fields are maps from $M$ to a vector space $V$, or natural generalizations like taking sections of a vector bundle $V \to M$.
+The Higgs boson appears as part of a scalar field theory.
+\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space (in the sense of supermathematics), typically a section of a spinor bundle.
+Such theories are often used to describe matter, such as electron fields.
+\item $\sigma$-{\em models} where the fields are maps from $M$ into a manifold~$X$. (One can view these as nonlinear generalizations of scalar field theories.)
+\item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
+\item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
+\end{itemize}
+The Standard Model involves the first three types,
+and the different fields interact in intricate ways.\footnote{For instance, the scalar and fermionic fields are sections of associated bundles to the principal bundle appearing in the gauge theory.}
+
+There are holomorphic versions of all these basic types, 
+and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs.
+See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.}
+To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
+we describe them in several ways: 
+in terms of PDE and action functionals but also as moduli spaces.
+We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
+and see \cite{AlfonsiYoung} and \cite{Steffens23} for recent work on this topic.
+
+For an example that mixes several types, see Section~\ref{sec: seiberg}
+where we discuss a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks.
+
+A motivation for us to explore holomorphic field theories is that physical insights and conjectures, such as Seiberg duality, translate into surprising predictions in the holomorphic setting,
+which is typically more accessible for mathematics.
+(One might also hope that progress in the holomorphic setting then feeds back useful insights to physics.)
+
+\subsubsection{Holomorphic scalar field theories}
+
+We met the standard example of a scalar field theory in Example~\ref{eg: massless scalar},
+where the field $\phi$ a smooth real-valued function on a manifold $M$
+and the equation of motion is $\Delta \phi = 0$,
+so that the moduli space of solutions is the space of harmonic functions on~$M$.
+
+A natural analogue is to have the field be a complex-valued function $\gamma$ on a complex manifold $M$ with an equation of motion $\dbar \gamma = 0$,
+so that the moduli space of solutions is the space of holomorphic functions on~$M$.
+
+Notice that we are shifting from a second-order differential operator $\Delta$ to first-order differential operators $\dbar$.
+Reworking a theory to express its equations of motion using first-order operators is sometimes called the first-order formalism.
+
+We will start with $M$ being a Riemann surface for simplicity.
+Consider the action functional
+\beqn
+\label{eqn: 1d betagamma}
+\int \beta \wedge \dbar \gamma
+\eeqn
+where $\beta$ is a $(1,0)$-form on $M$.%\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
+%which we now think about as having its own degrees of freedom. 
+%\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
+Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
+so that $\beta$ should be a holomorphic $1$-form.
+
+It should seem reasonable to view two solutions $\beta_1$ and $\beta_2$ as equivalent if they differ by a $\dbar$-exact term.
+If one imposes this equivalence relation (a kind of ``gauge symmetry''),
+then one is on the path towards setting up the theory in the Batalin-Vilkovisky formalism.
+
+Derived geometry is the mathematical version of BV formalism.
+From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
+\[
+T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\Omega^1_{hol}),
+\]
+where $\Omega^1_{hol}$ is the sheaf of holomorphic one-forms.
+
+\begin{rmk}
+It is possible to directly relate the usual massless scalar field theory to this $\beta\gamma$-system as follows.
+
+When $M$ is two-dimensional, oriented and Riemannian,
+we can view $M$ as equipped with a complex structure.
+Every complex-valued harmonic function then decomposes as a sum of a holomorphic and anti-holomorphic function. 
+That is, if we complexify the scalar field $\phi$, 
+we can view it as a pair of fields $\gamma$ and $\Bar{\gamma}$,
+where the equation of motion of $\gamma$ is $\dbar \gamma = 0$ and the equation of motion is $\partial \Bar{\gamma} = 0$.
+These components are sometimes called the chiral and anti-chiral ``sectors.''
+
+The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite[Chapter 3]{Polchinski}.
+There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$-system encoding the antichiral sector of the free boson.
+To recover the full boson, one must couple the chiral and anti-chiral sectors.
+See \cite{Kapustin:2005pt,GGW} for more details.~\hfill$\Diamond$
+\end{rmk}
+
+This example admits a natural generalization to an arbitrary complex manifold.
+The input data is a complex manifold $X$ of arbitrary complex dimension $n$, 
+together with a holomorphic vector bundle $V$ on~$X$.
+(Above we took this bundle to be trivial.)
+Each field of the theory consists of a pair $(\gamma,\beta)$ where 
+\[
+\gamma \in \Gamma(X,V) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(X,V^*) .
+\]
+The action functional is 
+\[
+\int_X \beta \wedge \dbar \gamma
+\]
+and the equations of motion are
+\[
+\dbar \gamma = 0 = \dbar \beta.
+\]
+Solutions consist of a holomorphic function $\gamma$ and a holomorphic $(n,n-1)$-form.
+We again suggest to identify solutions to the second equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
+
+\subsubsection{Holomorphic fermions}
+
+It is straightforward to modify the example above to allow holomorphic {\it super} vector bundles,
+i.e., holomorphic $\ZZ/2$-graded vector bundles.
+
+For example, given a holomorphic vector bundle $V$ on a complex $n$-fold~$X$,
+let $\Pi V$ denote the parity-reversed vector bundle,
+i.e., we now give $V$ an odd grading.
+There is a $bc$ system that is the fermionic analog of the $\beta\gamma$ system.
+The fields of the theory consist of a pair $(c,b)$ where 
+\[
+c \in \Gamma(X,\Pi V) \quad\text{and}\quad b \in \Omega^{n,n-1}(X,\Pi V^*) .
+\]
+Thus, $b$ and $c$ are fermionic fields.
+The action functional is 
+\[
+\int_X b \wedge \dbar c,
+\]
+and the equations of motion are
+\[
+\dbar c = 0 = \dbar c.
+\]
+We again suggest to identify solutions to the equation $\dbar c = 0$ that differ by a $\dbar$-exact form.
+
+There is another class of fermionic theories that is quite interesting as they are more fundamental than the previous example.
+Let $X$ be a complex $n$-fold and $L \to X$ a line bundle on $X$ such that
+\begin{itemize}
+\item $n \equiv 1 \mod 4$ (i.e., $n=4k+1$ for some $k$) and
+\item $L$ is a square root of the canonical bundle $L^{\otimes 2} \cong K_X$.
+\end{itemize}
+A field is a section
+\[
+\psi \in \Omega^{0,2k}(X,\Pi L),
+\]
+and the action functional is
+\[ 
+\int_X \psi \wedge \dbar \psi .
+\]
+The equation of motion for this system is simply $\dbar \psi = 0$.
+To study the quantization of this system, it is necessary to identify solutions that differ by $\dbar$-exact terms (and identifying identifications that differ by $\dbar$-exact terms, etc.).
+
+From the point of view of derived geometry, the cochain complex
+\[
+\Omega^{0,\bullet}(X, \Pi L)[2k]
+\]
+presents a derived super stack that should be viewed as the moduli of solutions for this theory.
+
+\subsubsection{Holomorphic $\sigma$-models}
+
+A $\sigma$-model is a field theory whose space of fields contains a mapping space $\Map(M,N)$.
+When $N = \RR$, this mapping space simply becomes functions and so the $\sigma$-model reduces to a scalar field theory.
+
+There is a natural generalization of the $\beta\gamma$ system to a $\sigma$-model.
+Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
+The fields are a pair $(\gamma, \beta)$ where
+\[
+\gamma \in \Map(M,N) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(M,\gamma^* T^*_N) .
+\]
+Note that $\dbar \gamma$ lives in $\Omega^{0,1}(M, \gamma^* T_N)$, 
+a section of the pullback of the tangent bundle of the target.
+The action functional is 
+\[
+\int_X \beta \wedge \dbar \gamma,
+\]
+where we use the canonical evaluation pairing between the pullback of the tangent and cotangent bundles of the target.
+The equations of motion are
+\[
+\dbar \gamma = 0 = \dbar \beta,
+\]
+so that solutions consist of a holomorphic map $\gamma: M \to N$ and a holomorphic section $\beta$ of the pullback tangent bundle.
+As usual, we suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.
+
+From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
+\[
+T^*[-1] \Map_\dbar(M,N) ,
+\]
+where $\Map_\dbar(M,N)$ is the derived stack of holomorphic maps $M \to N$.
+This is a natural space to study in complex geometry.
+
+\subsubsection{Holomorphic gauge theories}
+\label{sec: hol BF dfn}
+
+We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
+There is a another class of holomorphic gauge theories 
+defined on any complex manifold, with no restriction on dimension 
+and without the need for a Calabi--Yau structure.
+
+Let $X$ be a complex manifold of complex dimension~$n$.
+Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra~$\fg$.
+Fix a holomorphic principal $G$-bundle $P \to X$.
+The fields consist of pairs $(A,B)$ where 
+\[
+A \in \Omega^{0,1}(X, \fg_P)
+\] 
+where $\fg_P$ is the adjoint bundle of $P$ and
+\beqn
+B \in \Omega^{n,n-2}(X, \fg_P^*) ,
+\eeqn
+where $\fg_P^*$ is the coadjoint bundle of $P$. 
+The action functional is 
+\beqn
+S(A,B) = \int_X \langle B \wedge F_A \rangle
+\eeqn
+where $F_A$ is the curvature of the connection $A$.
+The equations of motion are
+\begin{align*}
+F_A^{0,2} = \dbar A + \frac12 [A,A] & = 0 \\
+ \dbar B + [A,B] & = 0.
+\end{align*}
+A solution to the first equation provides a new $\dbar$-connection 
+\[
+\dbar_A = \dbar_P + [A,-] 
+\]
+on $P$.
+A solution to the second equation is a $\dbar_A$-flat $(n,n-2)$-form-valued section of the coadjoint bundle.
+This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.
+
+\begin{rmk}
+Notice that this action functional resembles the $\beta\gamma$ system, 
+with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
+One also recognizes this action functional as a holomorphic analog of topological $BF$ theory. 
+\end{rmk}
+
+It is natural to view two connections as equivalent if they are related by a gauge transformation
+and to identify $B$-solutions that are related by a $\dbar_A$-exact term.
+From the point of view of derived geometry,
+we thus see holomorphic BF theory as describing the moduli space
+\[
+T^*[-1] \Bun_G(X),
+\]
+if we run over all principal bundles.
+
+\begin{rmk}
+Holomorphic BF theory exhibits some interesting properties at the quantum level,
+at least perturbatively.
+For example, in \cite[\S3.2]{BGKWWY} it is shown that on $X = \C^2$ 
+the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
+More precisely, to first-order in perturbation theory, 
+the divergence-free component of the stress tensor is rendered cohomologically trivial at one-loop in perturbation theory.
+In other words, the quantum theory appears to be totally ``invariant'' under divergence-free vector fields,
+although not all vector fields (as in the case of a TFT).
+\end{rmk}
+
+It is possible to formulate holomorphic versions of higher abelian gauge theories,
+associated to moduli spaces of holomorphic $k$-gerbes with connection, see \cite{SWtensor,BWfive}.
+
+\subsubsection{Interlude on holomorphic field theories as chiral sectors}
+
+Every holomorphic theory we have introduced so far has a ``kinetic term'' (the quadratic term in the action functional) that only involves $\dbar$.
+Thus the linearized equations of motion always have the form $\dbar \phi = 0$,
+so that they manifestly relate to holomorphic functions (or sections).
+There are, however, holomorphic theories with a different flavor.
+
+\begin{comment}
+A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
+Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
+We saved this example for last since its holomorphic analog is a bit more elusive than the previous examples.
+\end{comment}
+
+We start with complex dimension~$1$.
+The usual scalar field theory can be written as 
+\[
+\int_{\Sigma} \phi \wedge \del \dbar \phi, 
+\]
+where $\Sigma$ is a Riemann surface.
+Using integration by parts, one can use instead the action functional
+\[
+\int_{\Sigma} \partial \phi \wedge \dbar \phi.
+\]
+This theory is not holomorphic, but we can force it to be holomorphic by demanding that $\dbar \phi = 0$.
+Importantly, this constraint is \textit{not} an equation of motion.
+When we impose this constraint, we can rewrite the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
+\beqn\label{eqn:scalar1}
+\int_\Sigma \alpha \wedge \dbar (\del^{-1} \alpha) ,
+\eeqn
+where $\alpha$ plays the role of $\partial \phi$.
+In this theory the kinetic term is the whole action,
+and it has a rather different flavor from the examples we have seen so far.\footnote{This action functional is a precursor to the ``holomorphic gravity'' theory we meet next, 
+known as Kodaira--Spencer theory.}
+One might call this the {\em chiral sector} of the free scalar theory,
+as it consists of the complex-valued scalar fields satisfying a ``chiral'' constraint.
+
+There is a higher-dimensional analog of the chiral sector of the scalar field.
+Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
+The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
+\beqn
+\del \alpha = 0.
+\eeqn
+(When $n=0$ and $X$ is simply a Riemann surface, 
+this constraint is automatic.)
+The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
+Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
+\beqn
+\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
+\eeqn
+where $C \in \Omega^{2n+1}(X)$.
+For more details we refer to~\cite{GRW_WZW}.
+
+The reader may (and should) be concerned with the apparent ``non-local'' form of the action functional in \eqref{eqn:scalar1}.
+This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint~\cite{CLbcov}.
+
+\subsubsection{Holomorphic ``gravity''}
+
+Any theory of gravity involves, in part, metric structure on a given manifold,
+so that solutions to the equations of motion produce metrics satisfying a PDE. 
+For a perturbative gravity theory,
+one studies deformations of some metric structure on a manifold.
+There is a holomorphic avatar of this situation: deformations of complex structure. 
+The first appearance of such a theory was motivated by topological string theory and involves complex structures on Calabi--Yau threefolds~\cite{BCOV}.
+It is known \textit{Kodaira--Spencer gravity} or the Kodaira-Spencer field theory,
+due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
+It has been pursued mathematically by Costello and Li as an approach to the quantum higher genus $B$-model, starting with \cite{CLbcov} and continuing in a series of papers.
+In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
+here we focus just on the most familiar three-dimensional version.
+%The fields consist of pairs $(\mu, \eta)$ where
+%\begin{align*}
+%\mu & \in \Omega^{0,1}(X, \T_X) \\
+%\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
+%\end{align*}
+%The action functional is
+%\beqn
+%\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
+%\eeqn
+%where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.
+
+%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
+Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega$ the holomorphic volume form.
+The primary field of Kodaira-Spencer theory is 
+\beqn
+\mu \in \Omega^{0,1}(X,\T_X),
+\eeqn 
+a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
+A constraint is imposed on these sections:
+we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
+\[
+{\rm div}_\Omega(\mu) = 0,
+\]
+i.e., its divergence vanishes.
+In short, the fields are divergence-free vector fields.
+The classical equation of motion is 
+\beqn
+\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
+\eeqn
+where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket.\footnote{On vector fields, $[-,-]_{SN}$ is simply the Lie bracket, and it is the natural multilinear extension to polyvector fields.}
+The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
+Formulating the action functional to obtain this equation of motion is a little involved, 
+and we refer to \cite{CLbcov} for a systematic discussion.
+
+\begin{rmk}
+The kinetic term of this theory has the form
+\[
+\int_X \Omega \wedge \left[\Omega \vee \left(\frac12 \mu\, \dbar \del^{-1} \mu\right) \right]
+\]
+and hence resembles the chiral sector of the scalar, which we just discussed in the preceding example.
+\end{rmk}
+
 \printbibliography

### 2025-01-23 draft.tex
incorporated survey of DAG

@@
 \epigraph{The mathematical language of classical physics is based upon real numbers \dots.
-The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
+The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds,\\ Quantum Cohomology, and Moduli Spaces}}
 
@@
 so we will explain how our terminology relates to those notions.
-In
+In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
+(i.e., studying formal deformations of a fixed solution to the equations of motion),
+which we will use to produce examples of higher algebras.
 
@@
 we suggest \cite{DeligneFreed}.
-In the appendix we describe many more examples of holomorphic field theories and describe their spaces of solutions using the language of derived geometry, which we discuss next.
+In the appendix (see Section~\ref{sec: ex of theories}) we describe many more examples of holomorphic field theories and describe their spaces of solutions using the language of derived geometry, which we discuss next.
+
+\begin{rmk}
+Recently there is a substantial effort to revisit field theory with insights from derived geometry.
+See \cite{AlfonsiYoung} for motivation and overview, 
+but for a detailed development, see \cite{Steffens23, Steffens24}.
+\end{rmk}
 
@@
 
-Recently there is an effort to revisit field theory with insights from derived geometry.
-See \cite{AlfonsiYoung} for motivation and overview, 
-but for a detailed development, see \cite{Steffens23, Steffens24}.
-In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
-(i.e., studying formal deformations of a fixed solution to the equations of motion),
-which we will use to produce examples of higher algebras.
+Derived geometry is a sophisticated subject but the motivations and first steps are surprisingly simple,
+as we now attempt to explain.
+In this paper we only need the reader to understand the rough outline of derived geometry to follow our discussion,
+but there are several, much more substantial expositions now available.
+(For algebraic geometers consider \cite{TV, Lurie}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce, Carchedi, Steffens}; and for representation theorists consider \cite{BZNad, GaiRoz, Raskin}.)
+
+Before saying anything technical, we indicate how derived geometry generalizes more familiar topics.
+The starting place is the theory of vector spaces, which is very concrete and provides a rich source of both geometric intuitions and algebraic tools.
+This linear setting generalizes in two directions:
+\begin{itemize}
+\item the geometry of nonlinear spaces, whether in the style of algebraic geometry or in the style of differential geometry, and
+\item homological algebra, or differential graded vector spaces (and modules, sheaves, and so on).
+\end{itemize} 
+Both of these generalizations pass back to linear algebra in natural ways:
+\begin{itemize}
+\item at a point on a manifold or variety, the tangent space offers the best linear approximation to the space at that point (where it makes sense), and
+\item given a (ochain complex $(V,d)$, any cohomology group $H_k(V)$ is a vector space encoding essential information about the complex.
+\end{itemize} 
+As a first pass at derived geometry, one might say that it seeks a common generalization of nonlinear geometry and homological algebra.
+With slightly more precision, one might ask for a notion of space such that each point has a tangent {\em complex}, i.e., the linearization of a point yields a cochain complex.
+
+Note that there will be different versions of derived geometry, depending on the kind of nonlinear geometry concerned: 
+there is derived algebraic geometry, derived differential geometry, derived symplectic geometry, and so on.
+A desideratum of derived geometry is then that 
+\begin{itemize}
+\item an ordinary scheme or manifold (or whatever class of underived space) should provide an example of a derived space, and
+\item any cochain complex should provide an example of a derived space.
+\end{itemize}
+That is, derived geometry contains both the domains it seeks to generalize.
+
+There is an interesting subtlety here: quasi-isomorphic cochain complexes should present the same derived space, just as they present the ``same'' object in homological algebra.
+This requirement means that the true home for homological algebra is the derived category,
+obtained by localizing cochain complexes at quasi-isomorphisms.
+Similarly, the true home of derived geometry is also typically presented somewhat indirectly,
+with different descriptions provided of the same derived space.
+To do this carefully requires the theory of $\infty$-categories (or related tools like model categories).
+We will not dwell on this aspect of the subject,
+but we hope the comparison with the derived category gives a sense of the issues involved.
+(It also explains the terminology: it is the same use of ``derived'' for category and for geometry.)
+
+To present a derived space, two approaches are used and they mimic familiar methods for manifolds or schemes:
+\begin{itemize}
+\item a topological space equipped with a structure sheaf, here a sheaf of dg commutative algebras, or
+\item a functor of points, i.e., as a moduli space.
+\end{itemize}
+The devil is in the details of pinning down, for example, what kind of sheaves appear as structure sheaves or what the source and target categories appear for the functor of points,
+but let us postpone dealing with the devil and discuss a few examples used in this paper.
+We will use complex algebraic geometry as our model for nonlinear spaces, for simplicity,
+and we will emphasize the first style of describing a space.
+
+\subsubsection{Derived baby steps}
+
+Recall that the $n$-dimensional vector space $V = \CC^n$ determines a complex variety $\AA^n$ called an affine space.
+All the essential information is encoded in its algebra of functions
+\[
+\Gamma(\AA^n, \cO) = \Sym(V^*) = \CC[x_1,\ldots, x_n],
+\]
+a polynomial ring in $n$ generators, where the generators form a basis for the dual vector space $V^*$ to~$V$.
+We can view $\AA^n$ as a ringed space whose underlying topological space is $\CC^n$ with the Zariski topology
+and whose structure sheaf is obtained by localizing the polynomial ring accordingly.
+In derived geometry, a $\ZZ$-graded vector space 
+\[
+V = ( \ldots, V^{-1}, V^0, V^1, \ldots)
+\]
+should likewise present a derived space.
+(We assume $V$ has finite total dimension, for simplicity.) 
+The essential information is encoded in its graded algebra of functions
+\[
+\Sym(V^*) = \bigoplus_{n \geq 0} \Sym^n(V^*)
+\]
+where $V^*$ is the dual graded vector space with $(V^*)^k = (V^{-k})^*$ and where the symmetric powers involve the Koszul sign rule.
+That is, if $k$ is odd, then the $n$th symmetric power $\Sym^n(V^k)$ is concentrated in degree~$nk$ 
+but it is isomorphic to the $n$th exterior power of the {\em un}\/graded vector space~$V^k$.
+In other words, $\Sym(V^*)$ is a graded-commutative version of a polynomial ring.
+One can view this derived ``affine space'' as a ringed space whose underlying topological space is $V^0$ with the Zariski topology 
+and whose structure sheaf is obtained by localizing $\Sym(V^*)$ accordingly.
+
+Let's complicate this example a little.
+
+Let $X$ be a smooth complex variety, and let $V \to X$ be an algebraic vector bundle.
+It can be viewed as a family of complex vector spaces parametrized by~$X$.
+Similarly, we could pick an integer $k$ and consider the graded vector bundle $V[k] \to X$ whose fiber $V[k]_x$ at a point $x \in X$ is the shift by $k$ by the fiber $V_x$.
+(For us, $V[k]$ is placed in degree $-k$ so that $V[k]^m = V^{k+m}$. 
+In particular, $V[1]$ is in degree~$-1$.)
+But we can also talk about the total space of a vector bundle $V \to X$ as a complex variety in its own right.
+In derived geometry, we can view this graded vector bundle $V[k] \to X$ as a derived space.
+Its graded algebra of functions is 
+\[
+\Gamma(X,\Sym_{\cO_X}(\cV^*[-k])) = \bigoplus_{n \geq 0} \Gamma(X, \Sym^n_{\cO_X}(\cV^*[-k]))
+\] 
+where $V^*$ is the dual vector bundle, $\cV^*$ denotes the sheaf of sections of this vector bundle, and the symmetric powers involve the Koszul sign rule.
+That is, if $k$ is odd, then 
+\[
+\Sym^n(W[k]) \cong (\Lambda^n W)[kn]
+\]
+for $W$ concentrated in degree~0.
+Notice that when $k = 0$, we recover the usual ring of functions for the total space of~$V \to X$.
+
+This class of examples appears often in our paper.
+In particular, we often work with $T[k]X$, the total space of the shifted tangent bundle $TX[k] \to X$ of a complex variety~$X$,
+or with $T^*[k]X$, the total space of the shifted cotangent bundle of a complex variety~$X$.
+
+These shifted cotangent bundles admit natural {\em shifted} symplectic structures,
+just as the unshifted cotangent bundle $T^*X$ has a natural symplectic structure.
+The symplectic form is exactly the same, locally of the form
+\[
+\omega = \sum_j \d p_j \wedge \d x_j,
+\]
+where the $x_j$ are coordinates on $X$ and the $p_j = \partial/\partial x_j$ are the associated coordinates for cotangent direction.
+Here the $p_j$ have cohomological degree $-k$ [CHECK], so $\omega$ is a 2-form (in the de Rham complex of $T^*[k]X$) of cohomological degree~$-k$.
+(Note that the cohomological degree need not coincide with the form degree.)
+Implicit in this discussion is the fact that one can construct a de Rham complex with dg commutative algebra\footnote{The 1-forms are built by taking the derived functor of K\"ahler differentials, and the rest follows the usual process (e.g., take exterior powers over the dg commutative algebra, using the derived tensor product).
+The de Rham complex will be bigraded, with a form grading and a cohomological grading.}
+and that many maneuvers and definitions carry over {\it mutatis mutandis}.
+
+So far we have only worked with graded-commutative algebras,
+as a stepping stone in the derived direction.
+Let's now see something fully derived.
+
+\subsubsection{Derived intersections and stacky quotients}
+
+Algebraic geometry has already experienced a vast extension of the notion of space via {\it stacks}.
+These appeared, in essence, to provide a more pliable and informative approach to taking a quotient of a scheme (or algebraic space) by a group action,
+and this framework is the appropriate place for studying important moduli spaces, like moduli of algebraic curves or vector bundles.
+From a rather abstract point of view, we replace the category of schemes by a bigger category where the colimits (a quotient is an example of a colimit) remember more information.
+Derived geometry arises by asking for a (yet) bigger category where the {\it limits} remember more information.
+The key geometric example of a limit is the intersection of two subvarieties in an ambient variety (i.e., the fiber product);
+derived geometry changes what the intersection is.
+
+The essential idea is very simple.
+In algebraic geometry, if we have two schemes mapping to another scheme
+\[
+\Spec(A) \to \Spec(C) \leftarrow \Spec(B),
+\]
+then the fiber product is
+\[
+\Spec(A) \times_{\Spec(C)} \Spec(B) = \Spec(A \otimes_C B).
+\]
+Derived algebraic geometry says that the derived fiber product should be encoded by the derived tensor product~$A \otimes_C^{\LL} B$ instead.
+(This insight was first sharply articulated by Serre~\cite{}.)
+Thus the underlying underived intersection is encoded in 
+\[
+H^0(A \otimes_C^{\LL} B) = A \otimes_C B
+\]
+but there are sometimes ``derived corrections'' in negative cohomological degrees.
+
+For example, given a {\em non}\/regular sequence of irreducible [????] polynomials $(f_1,\ldots,f_k) \in \CC[x_1,\ldots,x_n]$, 
+then the underived intersection of the hypersurfaces $V_j = \{f_j = 0\}$ is some quite singular subvariety $X$ of $\AA^n$.
+A resolution of its algebra $\CC[X]$ over the polynomials is very complicated.
+By contrast the derived intersection is encoded by the Koszul complex determined by the $f$s,
+which is a very simple cochain complex (in fact, a semi-free dg commutative algebra). 
+It remembers information about the hypersurfaces (and hence the $f$s), whereas the underived intersection only knows about the ideal generated by the~$f$s.
+In this sense it is a ``smarter'' or less ``forgetful'' limit.
+KOSZUL HOMOLOGY?
+
+Notice that such derived tensor products will naturally produce dg commutative algebras concentrated in nonpositive degrees,
+as they have the nature of resolutions.
+We thus generalize commutative algebras $\CAlg$ by nonpositively graded dg commutative algebras~$\CAlg^{\dg}_{\leq 0}$, rather than the bigger category of all dg commutative algebras~$\CAlg^{\dg}$.
+The category of derived affine schemes is defined, then, as the category of nonpositively graded dg commutative algebras, up to quasi-isomorphism.\footnote{In fact, one works with the $\infty$-category, which is not just the localization at quasi-isomorphisms, but remembers how quasi-isomorphisms relate up to homotopy, etc.}
+Each derived affine scheme $\dSpec(A)$ has a truncation to an affine scheme, which is $\Spec(H^0(A))$.
+A derived scheme can be understood as ringed space patched together from derived affine schemes.\footnote{Up to some subtleties, one can think of derived manifolds in terms of manifolds equipped with structure sheaves that are nonpositively graded dg commutative algebras built from $C^\infty$-modules.}
+
+Derived stacks then arise from derived schemes by intelligently taking quotients and, more generally, colimits.
+Recall that a scheme in algebraic geometry has a functor of points valued in $\Sets$ while a stack has a functor of points valued in $\Gpds$, 
+the category of groupoids.\footnote{Every equivalence relation determines a groupoid where the relation gives the morphisms.
+This groupoid knows a lot more than the underlying quotient set, which is known as the ``connected components'' of this groupoid.
+In this way, groupoids offer a refinement of traditional quotients.}
+More accurately we work with groupoids localized at Morita equivalence ({\it cf.} quasi-isomorphism of cochain complexes and the derived category).
+In derived geometry we push farther and work with topological spaces up to weak homotopy equivalences (or simplicial sets up to weak homotopy equivalence),
+which remembers more;
+every topological space has an underlying fundamental groupoid.
+Thus the nature of derived geometry is indicated by the (co)domains of the functors of points:
+\[
+\begin{tikzcd}[column sep=large]
+\CAlg^{\dg}_{\leq 0} \arrow[dd, bend right=40, "H^0"'] \arrow[rr, "\text{derived stack}"] & & \Spaces \arrow[d, bend left=40, "\Pi_{\leq 1}"]\\
+&& \Gpds \arrow[d, bend left=40,  "\pi_0"] \arrow[u, hook]\\
+\CAlg \arrow[uu, hook] \arrow[rr, "\text{scheme}" near end] \arrow[urr, "\text{stack}"] && \Sets \arrow[u, hook]
+\end{tikzcd}
+\]
+(This diagram is purloined from the wonderful (and short!) ``What is derived algebraic geometry?''~\cite{VezAMS}.)
+A derived stack admits a truncation to an ordinary stack by restricting the domain category and mapping down to groupoids as the codomain category.
+
+To ``derive'' a notion from traditional geometry, one typically needs to recast it using the functor of points and then ponder how its features might generalize to derived affine schemes and~$\Spaces$.
+By now many such notions have received such a treatment, including analytic geometry~\cite{} and Poisson geometry~\cite{}.
+
+\subsubsection{On deriving classical field theory}
+
+The basic ingredients of classical field theory are a ``spacetime'' manifold $M$, the ``fields'' given by sections of some fiber bundle $E \to M$, and a system of PDE on the fields known as the ``equations of motion.''
+The essential goal is to describe the space of solutions to these equations of motion.
+All these features admit derived versions: one can replace the manifold $M$ by a derived space $\MM$ of some kind and the fiber bundle by a map of derived spaces $\EE \to \MM$ and the fields by sections thereof.
+The theory of differential equations admits a generalization too (perhaps most cleanly by using the perspective of $D$-modules and its outgrowths).
+In practice, as we'll see in this paper, many of the moduli spaces are variants of spaces already studied by geometers.
+In fact, they are often ``derived enhancements'' of well-known moduli spaces: we work with a derived stack whose truncation is a stack already known.
+For example, holomorphic Chern-Simons theory is best viewed as studying the derived enhancement of the moduli space of $G$-bundles on a Calabi-Yau 3-fold~$M$, where $G$ is a reductive complex algebraic group.
+
+There is an important feature that we have not discussed so far:
+the equations of motion arise from ``variational calculus.''
+Loosely speaking, these equations identify the critical points of some function on the space of fields.
+When approached from a derived perspective, 
+the space of solutions typically obtains a natural $-1$-shifted symplectic structure.\footnote{The derived critical locus of a function $f$ on an ordinary smooth variety $X$ is the derived intersection inside $T^*X$ of the graph of $\d f$ and the zero section.
+The structure sheaf can be modeled by functions $\cO(T^*[-1]X)$ equipped with a differential determined by~$f$.
+The shifted symplectic structure on $T^*[-1]X$ carries over to this derived critical locus.}
+Hence derived field theories lead to $-1$-shifted symplectic derived stacks,
+and we have examples like $T^*[-1]\Bun_G(M)$ or~$T^*[-1] \RR\Map(M,X)$.
 
@@
 and hence may be of particular interest to physicists.
+Those without a strong interest in physical examples can skip this section without issue.
+
 In his work on Donaldson invariants of four-manifolds, Witten introduced the idea of a topological twist of a supersymmetric field theory \cite{WittenTwist}.

### 2025-01-23 draft.tex
edits to derived sections

@@
 \item at a point on a manifold or variety, the tangent space offers the best linear approximation to the space at that point (where it makes sense), and
-\item given a (ochain complex $(V,d)$, any cohomology group $H_k(V)$ is a vector space encoding essential information about the complex.
+\item given a cochain complex $(V,d)$, any cohomology group $H_k(V)$ is a vector space encoding essential information about the complex.
 \end{itemize} 
@@
 \[
-\Gamma(\AA^n, \cO) = \Sym(V^*) = \CC[x_1,\ldots, x_n],
+\Gamma(\AA^n, \cO) = \CC[x_1,\ldots, x_n] = \Sym(V^*)
 \]
@@
 In derived geometry, we can view this graded vector bundle $V[k] \to X$ as a derived space.
-Its graded algebra of functions is 
+Its graded algebra of functions is (by definition)
 \[
@@
 \] 
-where $V^*$ is the dual vector bundle, $\cV^*$ denotes the sheaf of sections of this vector bundle, and the symmetric powers involve the Koszul sign rule.
-That is, if $k$ is odd, then 
-\[
-\Sym^n(W[k]) \cong (\Lambda^n W)[kn]
-\]
-for $W$ concentrated in degree~0.
+where $V^*$ is the dual vector bundle, $\cV^*$ denotes the sheaf of sections of this vector bundle, and the symmetric powers again involve the Koszul sign rule.
+%That is, if $k$ is odd, then 
+%\[
+%\Sym^n(W[k]) \cong (\Lambda^n W)[kn]
+%\]
+%for $W$ concentrated in degree~0.
 Notice that when $k = 0$, we recover the usual ring of functions for the total space of~$V \to X$.
 
-This class of examples appears often in our paper.
+This class of examples appears often throughout this paper.
 In particular, we often work with $T[k]X$, the total space of the shifted tangent bundle $TX[k] \to X$ of a complex variety~$X$,
@@
 just as the unshifted cotangent bundle $T^*X$ has a natural symplectic structure.
-The symplectic form is exactly the same, locally of the form
+The symplectic form on $T^*[k] X$ is given by exactly the same formula, locally
 \[
@@
 where the $x_j$ are coordinates on $X$ and the $p_j = \partial/\partial x_j$ are the associated coordinates for cotangent direction.
-Here the $p_j$ have cohomological degree $-k$ [CHECK], so $\omega$ is a 2-form (in the de Rham complex of $T^*[k]X$) of cohomological degree~$-k$.
-(Note that the cohomological degree need not coincide with the form degree.)
+The difference with the standard case is that now the $p_j$ carry cohomological degree $k$, so $\omega$ is a 2-form (in the de Rham complex of $T^*[k]X$) of cohomological degree~$k$.
+(Note that in a derived setting cohomological degree need not coincide with form degree.)
+One says that $T^* [k] X$ is a $k$-shifted symplectic space.
 Implicit in this discussion is the fact that one can construct a de Rham complex with dg commutative algebra\footnote{The 1-forms are built by taking the derived functor of K\"ahler differentials, and the rest follows the usual process (e.g., take exterior powers over the dg commutative algebra, using the derived tensor product).
@@
 \]
-then the fiber product is
+then the fiber product, or intersection, is
 \[
@@
 
-For example, given a {\em non}\/regular sequence of irreducible [????] polynomials $(f_1,\ldots,f_k) \in \CC[x_1,\ldots,x_n]$, 
+For example, given a {\em non}\/regular sequence of irreducible [????] polynomials $\mathbf{f} = (f_1,\ldots,f_k) \in \CC[x_1,\ldots,x_n]$, 
 then the underived intersection of the hypersurfaces $V_j = \{f_j = 0\}$ is some quite singular subvariety $X$ of $\AA^n$.
 A resolution of its algebra $\CC[X]$ over the polynomials is very complicated.
-By contrast the derived intersection is encoded by the Koszul complex determined by the $f$s,
+By contrast the derived intersection is encoded by the Koszul complex determined by the sequence $\mathbf{f}$,
 which is a very simple cochain complex (in fact, a semi-free dg commutative algebra). 
-It remembers information about the hypersurfaces (and hence the $f$s), whereas the underived intersection only knows about the ideal generated by the~$f$s.
+It remembers information about the hypersurfaces (and hence $\mathbf{f}$), whereas the underived intersection only knows about the ideal generated by~$\mathbf{f}$.
 In this sense it is a ``smarter'' or less ``forgetful'' limit.
@@
 \end{dfn}
+
+In quantum field theory, it is essential that the operator $Q^{hol}$ be elliptic.
+We will not explicitly mention any consequences of ellipticity in this note, so we will not emphasize this condition.
 

### 2025-01-28 draft.tex
modest edits plus refs

@@
 (We add the prefix $\RR$ because it is best to use the {\em derived} moduli space.
-We do not assume the reader is versed in derived geometry and will offer motivations, glosses, and references throughout the survey.)
+We do not assume the reader is versed in derived geometry and will offer motivations, glosses, and references throughout the survey.
+See Section~\ref{sec: DAG} for a start.)
 
@@
 These equations of motion are variational: 
-the solutions to these PDE are the critical points, in a sense, of some function,
-called an ``action functional.''
-(Variational PDE are often called Euler-Lagrange equations.)
+the solutions to these PDE are the critical points of some function on the space of fields,
+called an ``action functional,''
+and such PDE are often called Euler-Lagrange equations.
+(One must take a little care in interpreting the claim of taking critical points.)
 In practice an action functional is a formal expression, 
@@
 \]
-corresponds to the equation of motion $\Delta_g \phi = 0$. 
+yields the equation of motion $\Delta_g \phi = 0$. 
 Thus this scalar field theory has the moduli space of {\em harmonic functions} as its space of solutions.
@@
 These equations arise as the Euler-Lagrange equation for the action functional
+\[
+S(A) = \int_M CS(A)
+\]
+where $CS$ denotes the Chern-Simons form
 \beqn
 \label{eqn:CS}
-CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]),
-\eeqn
-the integral of a Chern-Simons form.
+CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]).
+\eeqn
 Hence this theory is known as {\em Chern-Simons theory}.\footnote{Note that $M$ needs to be an oriented 3-manifold for this action functional to make sense.
@@
 but there are several, much more substantial expositions now available.
-(For algebraic geometers consider \cite{TV, Lurie}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce, Carchedi, Steffens}; and for representation theorists consider \cite{BZNad, GaiRoz, Raskin}.)
-
-Before saying anything technical, we indicate how derived geometry generalizes more familiar topics.
+(For algebraic geometers consider \cite{Toen,PridEug}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce}; and for representation theorists consider \cite{BZNad, GaiRoz, Raskin}.)
+
+Before saying anything technical, we indicate how derived geometry generalizes more familiar bits of mathematics.
 The starting place is the theory of vector spaces, which is very concrete and provides a rich source of both geometric intuitions and algebraic tools.
@@
 Derived algebraic geometry says that the derived fiber product should be encoded by the derived tensor product~$A \otimes_C^{\LL} B$ instead.
-(This insight was first sharply articulated by Serre~\cite{}.)
 Thus the underlying underived intersection is encoded in 
@@
 
-For example, given a {\em non}\/regular sequence of irreducible [????] polynomials $\mathbf{f} = (f_1,\ldots,f_k) \in \CC[x_1,\ldots,x_n]$, 
+For example, given a {\em non}\/regular sequence of irreducible polynomials $\mathbf{f} = (f_1,\ldots,f_k) \in \CC[x_1,\ldots,x_n]$, 
 then the underived intersection of the hypersurfaces $V_j = \{f_j = 0\}$ is some quite singular subvariety $X$ of $\AA^n$.
@@
 In this sense it is a ``smarter'' or less ``forgetful'' limit.
-KOSZUL HOMOLOGY?
 
@@
 There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs.
+and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs, by mathematicians.
 See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.}

### 2025-01-29 draft.tex
another pass

@@
 \begin{itemize}
-\item at a point on a manifold or variety, the tangent space offers the best linear approximation to the space at that point (where it makes sense), and
-\item given a cochain complex $(V,d)$, any cohomology group $H_k(V)$ is a vector space encoding essential information about the complex.
+\item at a point $x$ on a manifold $M$ (or variety), the tangent space $T_xM$ offers the best linear approximation to the space at that point (where it makes sense), and
+\item given a cochain complex $(V,d)$, a cohomology group $H^0(V)$ is a vector space encoding essential information about the complex.
 \end{itemize} 
 As a first pass at derived geometry, one might say that it seeks a common generalization of nonlinear geometry and homological algebra.
-With slightly more precision, one might ask for a notion of space such that each point has a tangent {\em complex}, i.e., the linearization of a point yields a cochain complex.
-
+With slightly more precision, one might ask for a notion of derived space $M$ such that
+\begin{itemize} 
+\item each point $x$ in $M$ has a tangent {\em complex} $\TT_x M$, i.e., the linearization of a point yields a cochain complex, and
+\item $M$ should have a truncation $\tau(M)$ to an ordinary space.
+\end{itemize}
 Note that there will be different versions of derived geometry, depending on the kind of nonlinear geometry concerned: 
 there is derived algebraic geometry, derived differential geometry, derived symplectic geometry, and so on.
-A desideratum of derived geometry is then that 
+
+\begin{center}
+\begin{tikzcd}
+&\text{linear algebra} \arrow[squiggly, dr] \arrow[squiggly, dl] &\\
+\text{homological algebra} \arrow[squiggly, dr] \arrow[ur, bend left, "H^0"] &&\text{nonlinear geometry}\arrow[squiggly, dl] \arrow[ul, bend right, "\rm{T}"']\\
+&\text{derived geometry} \arrow[ul, bend left, "\TT"] \arrow[ur, bend right, "\tau"']&
+\end{tikzcd}
+\end{center}
+
+A related desideratum of derived geometry is that 
 \begin{itemize}
@@
 \]
-(This diagram is purloined from the wonderful (and short!) ``What is derived algebraic geometry?''~\cite{VezAMS}.)
+(This diagram is purloined from Vezzosi's wonderful (and short!) ``What is \dots a derived stack?''~\cite{VezAMS}.)
 A derived stack admits a truncation to an ordinary stack by restricting the domain category and mapping down to groupoids as the codomain category.
@@
 To ``derive'' a notion from traditional geometry, one typically needs to recast it using the functor of points and then ponder how its features might generalize to derived affine schemes and~$\Spaces$.
-By now many such notions have received such a treatment, including analytic geometry~\cite{} and Poisson geometry~\cite{}.
+By now many such notions have received such a treatment, including analytic geometry~\cite{Porta} and Poisson geometry~\cite{CPTVV}.
 
@@
 In practice, as we'll see in this paper, many of the moduli spaces are variants of spaces already studied by geometers.
-In fact, they are often ``derived enhancements'' of well-known moduli spaces: we work with a derived stack whose truncation is a stack already known.
+In fact, they are often ``derived enhancements'' of well-known moduli spaces: we work with a derived stack whose truncation is a stack already known.\footnote{In \cite{STV} a number of important moduli spaces, like moduli of stable maps of curves or moduli of perfect complexes, receive derived enhancements.}
 For example, holomorphic Chern-Simons theory is best viewed as studying the derived enhancement of the moduli space of $G$-bundles on a Calabi-Yau 3-fold~$M$, where $G$ is a reductive complex algebraic group.
@@
 The structure sheaf can be modeled by functions $\cO(T^*[-1]X)$ equipped with a differential determined by~$f$.
-The shifted symplectic structure on $T^*[-1]X$ carries over to this derived critical locus.}
+The shifted symplectic structure on $T^*[-1]X$ carries over to this derived critical locus.
+See \cite{VezdCrit} for more discussion.}
 Hence derived field theories lead to $-1$-shifted symplectic derived stacks,

### 2025-01-29 draft.tex
finished with refs

@@
 but there are several, much more substantial expositions now available.
-(For algebraic geometers consider \cite{Toen,PridEug}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce}; and for representation theorists consider \cite{BZNad, GaiRoz, Raskin}.)
+(For algebraic geometers consider \cite{Toen,PridEug}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce}; and for representation theorists consider \cite{GaiRoz}.)
 

### 2025-01-31 draft.tex
relabeled appendix
merge

--- 2025-01-28 draft.tex
@@
 (We add the prefix $\RR$ because it is best to use the {\em derived} moduli space.
-We do not assume the reader is versed in derived geometry and will offer motivations, glosses, and references throughout the survey.
-See Section~\ref{sec: DAG} for a start.)
+We do not assume the reader is versed in derived geometry and will offer motivations, glosses, and references throughout the survey.)
 
@@
 These equations of motion are variational: 
-the solutions to these PDE are the critical points of some function on the space of fields,
-called an ``action functional,''
-and such PDE are often called Euler-Lagrange equations.
-(One must take a little care in interpreting the claim of taking critical points.)
+the solutions to these PDE are the critical points, in a sense, of some function,
+called an ``action functional.''
+(Variational PDE are often called Euler-Lagrange equations.)
 In practice an action functional is a formal expression, 
@@
 \]
-yields the equation of motion $\Delta_g \phi = 0$. 
+corresponds to the equation of motion $\Delta_g \phi = 0$. 
 Thus this scalar field theory has the moduli space of {\em harmonic functions} as its space of solutions.
@@
 These equations arise as the Euler-Lagrange equation for the action functional
-\[
-S(A) = \int_M CS(A)
-\]
-where $CS$ denotes the Chern-Simons form
 \beqn
 \label{eqn:CS}
-CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]).
-\eeqn
+CS(A) = \frac12 \kappa(A, \d A) + \frac16 \kappa(A, [A,A]),
+\eeqn
+the integral of a Chern-Simons form.
 Hence this theory is known as {\em Chern-Simons theory}.\footnote{Note that $M$ needs to be an oriented 3-manifold for this action functional to make sense.
@@
 but there are several, much more substantial expositions now available.
-(For algebraic geometers consider \cite{Toen,PridEug}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce}; and for representation theorists consider \cite{BZNad, GaiRoz, Raskin}.)
-
-Before saying anything technical, we indicate how derived geometry generalizes more familiar bits of mathematics.
+(For algebraic geometers consider \cite{TV, Lurie}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce, Carchedi, Steffens}; and for representation theorists consider \cite{BZNad, GaiRoz, Raskin}.)
+
+Before saying anything technical, we indicate how derived geometry generalizes more familiar topics.
 The starting place is the theory of vector spaces, which is very concrete and provides a rich source of both geometric intuitions and algebraic tools.
@@
 Derived algebraic geometry says that the derived fiber product should be encoded by the derived tensor product~$A \otimes_C^{\LL} B$ instead.
+(This insight was first sharply articulated by Serre~\cite{}.)
 Thus the underlying underived intersection is encoded in 
@@
 
-For example, given a {\em non}\/regular sequence of irreducible polynomials $\mathbf{f} = (f_1,\ldots,f_k) \in \CC[x_1,\ldots,x_n]$, 
+For example, given a {\em non}\/regular sequence of irreducible [????] polynomials $\mathbf{f} = (f_1,\ldots,f_k) \in \CC[x_1,\ldots,x_n]$, 
 then the underived intersection of the hypersurfaces $V_j = \{f_j = 0\}$ is some quite singular subvariety $X$ of $\AA^n$.
@@
 In this sense it is a ``smarter'' or less ``forgetful'' limit.
+KOSZUL HOMOLOGY?
 
@@
 There are holomorphic versions of all these basic types, 
-and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs, by mathematicians.
+and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs.
 See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.}
@@
 This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint~\cite{CLbcov}.
+The essential bit is that the sheaf of holomorphic differentials is equipped with a (shifted) Poisson bivector essentially given by the holomorphic de Rham operator $\del \colon \cO_\Sigma \to \Omega^1_\Sigma$.
 
@@
 due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
-It has been pursued mathematically by Costello and Li as an approach to the quantum higher genus $B$-model, starting with \cite{CLbcov} and continuing in a series of papers.
-In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
+It has been pursued mathematically by Costello and Li as an approach to the quantum higher genus $B$-model, starting with \cite{CLbcov} and continuing in a series of papers by Costello and Li.
+In these works, the authors also provide a generalization of the theory that makes sense in any complex dimension; 
 here we focus just on the most familiar three-dimensional version.

### 2025-01-31 draft.tex

--- 2025-01-29 draft.tex
@@
 
-\section*{Appendix: A zoo of holomorphic field theories}
+\section{Appendix: A zoo of holomorphic field theories}
 \label{sec: ex of theories}
